### 2015-05-06 MS.tex
initial import

\documentclass[a4paper]{article}\usepackage[]{graphicx}\usepackage[]{color}
\usepackage{alltt}
\usepackage{amssymb,amsmath}
\usepackage{palatino}
\usepackage{framed}
\usepackage{parskip}
\usepackage{graphicx}
\usepackage{fixltx2e}
\usepackage[default,osfigures,scale=0.95]{opensans}
\usepackage{geometry}
\usepackage{longtable}
\usepackage{authblk}
\usepackage[colorinlistoftodos]{todonotes}
\geometry{verbose,tmargin=2cm,bmargin=2cm,lmargin=2cm,rmargin=2.5cm}
\linespread{1.5}

%appendix
\usepackage[title,titletoc,toc]{appendix}

% allows for number referencing, as required by updated ecol letters style
\usepackage{etoolbox}
\newbool{MyRefNumbers}
\booltrue{MyRefNumbers} % comment to remove numbers in reference list

\usepackage{natbib}
\bibliographystyle{ecol_let}
\setcitestyle{authoryear,open={(},close={)}}

\begin{document}

\section*{Cover letter (303 on 300 words)}\label{Proposal}

Editor-in-Chief Ecology letters

Dear Dr Holyoak,

May we please submit for Ecology Letters a manuscript titled “Plant species traits and growth rates: meta-analysis shows correlations change with plant size as predicted”? We would be grateful if you would consider it for publication.

The work is meta-analysis, but we suggest it should be considered as a Letter more so than under the heading of Reviews and Syntheses. It reports original conclusions based on new data analysis, and does not attempt broad review. But of course if you prefer to consider it as a review, then we are in your hands.

May we please raise with you an issue about the literature cited? (It need not affect the review process.) We strongly believe that authors whose data publications enter into meta-analyses deserve to get credit via citation. But because of the restriction on citations in the main text, these citations are in appendices in the current draft, rather than in the main list of Literature Cited. We hope you may have a solution to situations of this kind? We understand some journals now make provision for literature cited in appendices or supp info to be scanned by ISI and other cite-counting agencies? Or perhaps the restrictions on number of papers cited can be relaxed for meta-analyses?

\textbf{Novelty statement:}
In a nutshell, this paper sorts out the differences across plant species in potential growth rates. We believe it's a very substantial advance. Growth rates are obviously really important for ecology. They have been seen as a core element of plant ecological strategies going back to Grime and Hunt 1975. Over the past 20 years much ecological strategy research has shifted into "trait ecology", using traits such as SLA and wood density and seed mass as indicators of ecological strategy. Yet empirical reports of the correlations between traits and growth rates have been inconsistent. Our manuscript first spells out reasons why traits should influence growth differently depending what size the individual plant has achieved -- in other words, traits should influence growth trajectories rather than simply making species fast-growing versus slow-growing throughout life. Then second, we provide meta-analysis of correlations that have been reported between traits and growth rate. To the extent data are available, these correlations are shown to shift depending on plant size consistently with the reasons explained and the predictions made in the first part of the paper.

We are excited by this work and look forward to your evaluation of the paper.

Sincerely

Anais Gibert on behalf of all authors

\newpage

\title{Plant species traits and growth rates: meta-analysis shows correlations change with plant size as predicted}

\author[1]{Anais Gibert}
\author[1]{Emma F. Gray}
\author[1]{Mark Westoby}
\author[1]{Ian J. Wright}
\author[1]{Daniel S. Falster}
\affil[1]{Dept of Biological Sciences, Macquarie University, Sydney, NSW 2109, Australia}

\maketitle

\textbf{Running title (36/45 characters)} Trait influence on growth along plant size

\textbf{Keywords (8/10)} asymptotic maximum height, maximum photosynthetic rate, plant ontogenetic stage, plant functional traits, plant growth strategy, seed mass, specific leaf area, wood density

\textbf{Type of article} Letters

\textbf{Number of words in the abstract} 148

\textbf{Number of words in the main text (excluding abstract, acknowledgements, references, table and figure legends)}

\textbf{Number of words in each text box} 0

\textbf{Number of general references}

\textbf{Number of data source references} 108

\textbf{the number of figures} 2

\textbf{the number of tables} 0

\textbf{the number of text boxes} 0

\textbf{the name and complete mailing address (including telephone and fax numbers and e-mail address) of the person to whom correspondence should be sent}

\todo[inline,color=white]{Tentatively for Ecology Letters [length limits: maximum of 5000 words (main text), 2/6 figures, tables or boxes, and 64/50 references.] (4667 word  /5000)}

\todo[inline,color=white]{1. need to delete references 57/50}

\todo[inline,color=white]{2. need to reduce nb words abstract 148/150: DONE}

\todo[inline,color=white]{3. the bibliography style needs to be changed to fit with the new style of Ecology letters: journal abbreviation}

\todo[inline, color=white] {4. to re write Appendix A growth equation : do we keep equation? information about plant size?}

\todo[inline, color=white] {5. to write a "Read.me" file for the dataset/guithub}

\todo[inline, color=white] {6. to add the list of traits/stage categoreis combiation for which we identified a need of more data in the last paragrph of the discussion: DONE}

\todo[inline, color=white] {7. to add subsections in Discussion: DONE}

\newpage

\section*{Abstract (148 words/150)}\label{abstract}

\begin{enumerate}

\item
The literature is inconsistent about empirical correlations between functional traits and plant growth rate (GR), casting doubt on the capacity of traits to predict growth.

\item
Traits should influence growth in a size-dependent manner. We outline mechanisms and hypotheses based on new theory, and test these predictions for five traits using a meta-analysis of 108 studies (\textgreater{} 500 correlations).

\item
Results were consistent with predictions. Specific leaf area was correlated with GR in small but not large plants. Correlations of GR with wood density and assimilation rate were not affected by size. Maximum height and seed mass were correlated with GR only in one plant size category.

\item
We show that correlations between traits and GR change in a predictable way as a function of plant size. Our understanding of plant strategies should shift away from attributing slow vs fast growth to species throughout life, in favour of attributing growth trajectories.

\end{enumerate}

\section*{Introduction}\label{introduction}

The phrase "plant ecological strategy" refers to how species face the challenge they all share:  to acquire sufficient water, nutrients and light for individual growth and to live long enough to replace themselves with offspring. An idea that strategy differences might involve fast vs slow growth goes back at least to Grime and Hunt \citeyearpar{Grime:1975gr}, who measured a wide spread of relative growth rates for seedlings during early exponential growth under favourable conditions. Seedling potential RGR has continued to be used as a major strategy indicator within the Sheffield CSR (Competitor - Stress tolerator - Ruderal) scheme and its "Integrated Screening Program" (e.g. \citealt{grime1979plant, Grime:1997wm}). Meanwhile partitioning of seedling RGR into its components showed that specific leaf area (SLA = 1/leaf mass per area LMA) was typically the strongest source of variation between species \citep{Poorter:1989tx}. From the 1990s a new style of "trait ecology" arose whereby measurable traits including SLA were used directly as strategy axes \citep{Westoby:1998ug,Weiher:1999js, Westoby:2002ft}. An approach via measurable traits made broad comparisons possible across continents and latitudes and thousands of species. Traits have been seen as constructive approaches to understanding plant growth strategies \citep{Grime:1977kc,Chapin:1980gz}, community composition \citep{Lavorel:2002ff,Shipley:2006ie}, global vegetation dynamics \citep{Scheiter:2013ed} and ecosystem processes \citep{Lavorel:2002ff}.

Currently two main spectra of variation are widely cited as underpinning differences between species in vegetative growth rates. The `leaf economic spectrum' \citep{Wright:2004jb} and the 'wood economic spectrum' \citep{Chave:2009iy} reflect tissue construction costs (for specific leaf area and for wood volume respectively) trading off with tissue turnover rates or mortality risks. It has been widely expected that species with low tissue construction cost will typically have fast growth rates at least in favourable physical environments (e.g. \citealt{MullerLandau:2004dc,Wright:2004jb,Poorter:2006kw,Poorter:2008iu,Chave:2009iy,Larjavaara:2010bn,Iida:2012jb,Paine:2015df}). Yet a growing number of empirical studies indicate the correlation between traits and growth is not as consistent as that. Consider SLA as an illustration. Species with high SLA can deploy more canopy area for a given dry mass investment in leaves \citep{Poorter:1999wd, Reich:1992wm}. In addition, SLA is correlated with high photosynthetic rates and high nitrogen (N) or phosphorus concentrations in the leaf \citep{Wright:2004jb}. For seedling relative growth rates under favourable conditions, high SLA has repeatedly been found to be a strong predictor regardless of vegetation type or growth form \citep{Lambers:1992bj,Reich:1992wm,Grime:1997wm,Poorter:1999wd,Wright:1999ds}. Yet for adult plants, this correlation appears weaker or absent \citep{coomes_comparison_1998,Poorter:2008iu,Aiba:2009ft,Easdale:2009gv,Wright:2010tp}. The growing discrepancy between theoretical expectation and empirical results has led some to question whether traits are even useful for understanding growth \citep{Wright:2010tp, Paine:2015df}.

Meanwhile the possibility has been raised that trait-growth correlations may change systematically with size \citep{Iida:2014ep,Iida:2014hq,Ruger:2012jv,Falster:2011ii}.Recent theory suggests that the absence of a correlation between SLA and growth at larger sizes may be expected, when  potential influences of traits on plant function are considered \citep{Falster:2011ii, falster:2013} (Appendix \ref{app:growth}). At larger sizes the low-cost deployment benefits of high SLA may be offset or even outweighed by the high costs of rapid leaf turnover.

Here we review published literature reporting on relationships between
plant growth and five prominent traits (specific leaf area SLA, wood or stem tissue density WD, maximum leaf photosynthetic capacity per unit area Aarea,  maximum height Hmax, and seed mass SM), in order to assess the following questions.

\begin{enumerate}
  \item How general is the tendency for correlations between traits and growth rate to vary with plant size?
  \item Do the observed relationships conform to predictions (outlined below) from a recently developed  mechanistic
model \citep{Falster:2011ii, falster:2013}(Appendix \ref{app:growth})?
\end{enumerate}

While most studies on traits have not been concerned with effects of plant stage or size, they have reported trait-growth correlations for identifiable size classes. We gathered correlation coefficients r between trait and growth from studies that gave explicit information about the size or stage of the plants. Meta-analysis allowed us to generalize about trait influences on growth.

\section*{Theoretical expectations}\label{theory}

Recent theoretical work \citep{Falster:2011ii} allows hypotheses to be formulated about relationships between traits and growth. Below we provide a verbal description for each of the hypotheses; for a mathematical description see Appendix \ref{app:growth}.

\textbf{H1: The relationship between specific leaf area (SLA) and growth rate is expected to shift from positive in seedlings to non-significant or negative in adult plants, regardless of the growth measurement used}

Plants with high SLA can deploy more leaf area per unit of mass invested. However, high-SLA species also have shorter leaf lifespan and faster leaf turnover rate \citep{Wright:2004jb}. Whether plant growth increases with SLA depends on the relative magnitude of the leaf construction and leaf turnover effects of SLA. During early life while leaf comprises a large part of the plant, decreasing leaf construction cost has a positive effect on growth rate. As plants increase in size and leaf mass fraction decreases, the benefit of cheaper leaf construction diminishes; thus the cost of replacing leaf turnover becomes more important.

\textbf{H2: The relationship between wood or stem density (WD) and growth rate is expected to be negative across all plant sizes}

Low WD decreases the cost of building stem tissue, which should result in faster growth. Although cheaper wood carries a risk of increased mortality, this cost is not reflected in growth outcomes. Thus decreasing WD is predicted to increase growth across the entire size range.

\textbf{H3: The relationship between maximum photosynthetic rate (Aarea) and growth rate is expected to be positive across all plant sizes, at least under high-light conditions}

We expect greater photosynthetic capacity to translate into faster growth rates, at least at high light where Aarea is measured. It is uncertain how much this might translate to faster growth in low light.

\textbf{H4: The relationship between asymptotic maximum height (Hmax) and growth rate is expected to be absent in seedlings but to strengthen with increasing plant size.}

As plants approach maximum height they increasingly divert energy away from growth and into reproduction (see \citealt{Wenk:2014jz, Falster:2011ii,Thomas:1996do}). For seedlings, where all individuals are investing solely in growth, we expect no influence of Hmax on growth. As plants become larger, species with smaller Hmax are expected to be allocating more to reproduction and less to growth, because at any given size they are closer to their Hmax.

\textbf{H5: The relationship between seed mass (SM) and relative growth rate is negative in seedlings, but weakens with increasing size.}

The main effect of increased seed size is to produce a larger overall seedling. Generally relative growth rate decreases with size, and as such larger seedlings are predicted to have a lower relative growth rate during the earliest phases of growth \citet{Turnbull:2012ew}. However, among larger plants we expect the effect of this initial size to be minimal, and thus the correlation between seed size and growth rate should disappear.

\section*{Materials and methods}\label{material-and-methods}

We aimed to identify studies that measured the correlation between a functional trait and a growth measurement, and searched for relevant studies using a three step procedure. First, we identified traits for which a substantial number of studies would be available, using a literature snapshot in Web of Science. While Web of Science guarantees a relatively stable and reproducible search environment, with clearly defined lists of indexed journals, its searches are restricted to metadata, such as title, keywords and abstracts \citep{Falagas:2008gtb,Beckmann:2012hn}. This limitation does not apply to Google Scholar, where, theoretically, all text that is electronically available on the Internet will be indexed. Thus, our second step was to systematically read documents returned by Google scholar for a restricted set of traits. Finally, we identified and recorded other possible data sources using our own knowledge as researchers in the field. (This included adding data from an as-yet unpublished study by Gleason et al). The complete list of studies where we inspected the full text is given in Appendix \ref{app:supp_info_files}.

\subsection*{Literature snapshot}\label{literature-snapshot}

We focused on an initial list of 20 traits (Fig. \ref{Fig1}): the five for which we had prior expectations, plus 15 others which capture different aspects of plant species strategies. Specific leaf area (SLA), leaf area, leaf nitrogen and phosphorus concentration, net (mass) assimilation rates (NAR), and assimilation rate of CO$_2$ (Aarea) are traits involved in species leaf economic strategy \citep{Wright:2004jb,Wright:2010tp}. Seed mass (SM), and maximum plant height (Hmax) capture information about reproductive strategy \citep{Falster:2005bw,Moles:2006ft}. Wood density (WD) and sapwood area per leaf area (SA/LA), vessel size and density, and stem specific conductance are all involved in species wood economic strategy \citep{Chave:2009iy}. Here WD and SA/LA are also considered as indicators of stem construction cost \citep{Falster:2011ii}, whereas SLA and leaf thickness capture crucial information about leaf construction cost \citep{Wright:2004jb}. Finally, the leaf area ratio and leaf mass ratio are indicators of resource allocation to leaf \citep{Lambers:1992bj}. We used the literature snapshot to identify traits which i) were most likely to return a substantial number of articles , and ii) shared a large proportion of their literature list with other traits. The Web of Science database (Thomson Reuters) was searched between March and June 2014 using a range of Boolean search terms in English. Search terms were as follows: (``NAME'' AND (``growth rate'' OR ``relative growth rate'')) AND (``tree*'' OR ``woody*''), ``NAME'' was one of trait names listed in Table \ref{TableA1}. According to this snapshot, 62\% of the literature for the 20 traits (or 82\% for the 5 traits for which we have clear predictions) is captured by searching only on two traits: SLA and WD.

\subsection*{Systematic search}\label{systematic-search}

Google Scholar database was searched using the range of Boolean search terms for SLA and WD. Search terms were as follows: ((``SLA'' OR ``LMA'' OR ``specific leaf area'' OR ``leaf mass area'' OR ``wood density'' OR ``WD'' OR ``wood specific gravity'' OR ``stem density'' OR ``stem specific density'') AND (``growth rate'' OR ``relative growth rate'')) AND (tree* OR woody*). The keyword search in Google Scholar returns approx. 18900 papers. For comparison, with the same keyword search Web of Science returns 541 papers. Thus, in Google Scholar we displayed papers by relevance and examined the first 750 items.

Each study had to meet some basic criteria to be included in our analysis. We restricted our meta-analysis to documents reporting: i) the relationship between growth and trait as a correlation coefficient, ii) the sample size and the number of species used to perform the correlation, and iii) the size/stage of plants. Where available we also recorded the geographic coordinates, number of sites, experiment type (greenhouse, field experiment, forest, shade-house etc.), growth measure (relative or absolute growth rate measured using plant diameter, height or mass), vegetation type, life form (tree, woody or mixed with herbaceous species etc.), biological scale (interspecific, intraspecific or intragenus), and experimental treatments (e.g.~fertilization, shade, salt stress). Ultimately data was included from 108 different studies \citep{Aiba:1997ho, Aiba:2009ft, Antunez:2001gk, Atkin:1998in, augspurger_light_1984, baltzer_physiological_2007, baraloto_differential_2006, baraloto_seed_2005, Bloor:2003fa, Bohlman:2006eo, Broncano:1998ck, Brown:1996ks, Bruhn:2000jz, Cai:2007ie, CamaraZapata:2003df, CastroDiez:1998gz, CastroDiez:2003jd, Cernusak:2008ds, Chao:2008hg, Chaturvedi:2011jx, Chave:2009iy, Cochard:2007bn, Coley:1983hk, Comas:2002wt, Comas:2004jza, coomes_comparison_1998, coomes_greater_2009, cornelissen_seedling_1996, Cornelissen:1997fd, Cornelissen:1998ta, Dalling:2004gs, DeBell:1994ix, Easdale:2009gv, fan_hydraulic_2012, Fayolle:2012bx, Fujimoto:2006fg, Galmes:2005fa, gleeson_plant_1994, grotkopp_toward_2002, Grubb:1996kr, Herault:2011dd, Huante:1995fd, Huante:1995tl, Huante:1998bk, HUNT:1997ge, Iida:2014ep, Iida:2014hq, king_influence_1994, king_tree_2005, King:2006dg, King:2006he, Kitajima:1994ez, Kohyama:2003dk, Kruger:2006fq, Lamers:2006dl, LopezIglesias:2014dk, Loveys:2002hj, Lusk:1997ga, Lusk:2002fma, Lusk:2013bq, Lusk:2013hz, MartinezVilalta:2010iq, McCormack:2012ch, Moya:2008ep, MullerLandau:2004dc, Nascimento:2005kl, Osone:2008dr, Osunkoya:1994ip, Osunkoya:2010ef, Paz:2005kx, Poorter:1999fp, Poorter:2001fj, Poorter:2006vb, Poorter:2008iu, Poorter:2010co, Popma:1988tv, Prior:2004cv, Read:2011du, Reich:1998ir, Reich:1998ja, Reich:1998vb, Rossatto:2009gq, RuizRobleto:2005hc, Sack:2004hm, saldana-acosta_seedling_2009, SalgadoLuarte:2012ci, Saverimuttu:1996ih, Schulze:2006ww, Shen:2014fw, Shipley:2002fs, Stratton:2001ck, Thomas:1996do, Tjoelker:1999gp, Tobner:2013cv, Tomlinson:2014im, Veneklaas:2002dt, Villagra:2013do, walters_are_1996, Walters:1993eu, Walters:1993hf, Warren:2005bc, Westbrook:2011ja, Wright:1999ds, Wright:2000kw, Wright:2001gb, Wright:2003kb, Wright:2010tp, Zhang:1995bh}.

The number of species used to perform the correlation, the experimental conditions, and the concordance between stage used to measure trait and growth are clear criteria for assessing the quality of the data for addressing our hypotheses. Therefore, we stratified the data set into two subsets: one including exclusively interspecific studies under unstressed conditions ('ideal' dataset), and the other set including all studies ('complete' dataset). We excluded from the 'ideal' dataset studies where growth and traits were measured on plants from different stages, unless a particular stage is by definition required to measure a trait such as for seed mass (i.e. seed stage), or Hmax (i.e. adult stage). Finally, we weighted our data by number of species rather than the sample size for all statistical analyses (see Statistical analyses section).

\subsection*{Plant size categories}\label{plant-size-categories}

We adopted two approaches to address plant size/stage effect in this review.

First, plants were categorized into stages according to the authors categorization (i.e.seedling, juvenile, sapling, adult, mix). When the stage information was not explicitly given, data were recorded as 'mix'. While this approach is based on the expertise and the appreciation of the authors, by compiling data across multiple studies there is a risk of assigning plants of similar size to different categories.

Second, we re-assigned plants to three stage categories (`juvenile', `sapling' and `adult') according to size and age cutoffs established by looking at the range values observed across all studies (Fig. \ref{FigA1}). We preferred the term `juvenile' to `seedling', because for a portion of the scientific community `seedling' also refers to a particular experimental condition (a greenhouse experiment). Overall, the different studies were largely consistent in their classification of plants into `juvenile', `sapling' and `adult' groups  (Fig. \ref{FigA1}). In particular, there was a clear break between juveniles and saplings in both age (at 1 yr) and height (at 0.5m); there was also a clear break between saplings and adults in diameter (at 10cm). The distinctions between sapling-adult in age and height, and between seedling-sapling in diameter were less pronounced. To ensure consistency across studies we used simple allometric relationships from the Biomass And Allometry Database (BAAD) \citep{Falster:2015} to match between age, diameter and height ranges for each stage category (Fig. \ref{FigA2}). Thus, we established the following rules: i) `juveniles' are plants of {[}0,0.5) m in height , or {[}0,0.2{]} cm in diameter, or $\leq$ 1 yrs old; ii) `saplings' are plants of {[}0.5-5{]} m , or (0.2,10{]} cm in diameter, or (1-30{]} yrs, and iii) `adult' are plants \textgreater{}5 m in height, or \textgreater{}10 cm in diameter, or \textgreater{} 30 yrs and/or in the reproductive stage. We attributed the study to a new stage category when 95\% of the recorded range of sizes for that study lay within the new category. We attributed a study to the adult stage when the authors identified the plants as reproductive regardless the plant size or age.

In the main text we report the results using the second approach, i.e. standardized categories. Results using the first approach are similar and are available in Fig. \ref{FigA7}.

\subsection*{Effect size calculation}\label{effect-size-calculation}

We used the cross-species Pearson product-moment correlation coefficient r between growth rate and species trait as our measure of effect size, weighted by the number of species contributing. When studies did not report r values but another coefficient such as coefficient of determination (R2), Spearman's rho rank correlation or Kendall's tau rank correlation, we converted these to correlation coefficients  \citep{Lajeunesse:2013tm} (see code in Appendix \ref{app:supp_info_files} for details). When the magnitude of Pearson's correlation coefficient approaches +/- 1, its distribution becomes skewed. Accordingly we transformed the correlation r into a metric with desirable statistical properties using Fisher's z-transformation,

\[ z = \frac{1}{2} \ln \frac{1+r}{1-r} \]

which has a variance estimate

\[ v_z= \frac{1}{n-3} \]

n being the number of species.

\subsection*{Statistical analyses}\label{statistical-analyses}

We tested size/stage effect on traits for which \textgreater{}20 correlation coefficients across at least two stages were recorded. We used a mixed-effect model of meta-analysis, in which it is assumed that studies within a stage share a common mean effect but that there is also random variation among studies in a stage, in addition to sampling variation. This random effect allows us to account for the heterogeneity among studies (e.g.~experimental type, vegetation type, error, etc.). For each trait, we established if stage could explain variance in the coefficient correlation by comparing models with the stage variable to the null model using log-likelihood ratios  \citep{Srivastava:2009we}. If the log-likelihood test returned a significant p-value, the stage model fitted the data better than the null model. Effects of other variables (vegetation type, experiment type and growth measurement) were also tested individually (results shown in the Fig. \ref{FigA7}). Estimates of the effect size for each stage were considered significant if the 95\% confidence intervals did not overlap with zero. In the case of multiple comparisons within a study, we used the method proposed by \citet{Borenstein:2009um}: we calculated the mean correlation coefficient by trait and by study, and re-calculated the effect size (see \citealt{Pere:2013gr}). Finally, we checked the dataset for publication bias with funnel plots (\citealt{Koricheva:2013tz}, Fig. \ref{FigA8}). A publication bias toward significant results creates an asymmetric funnel with small studies with non-significant effects missing from the mouth of the funnel on the side opposite to the true effect. In addition, to avoid publication bias due to selective reporting of significant results within published articles (e.g.~particular case of a `failure to publish bias' see \citealt{Jennions:2013ta}), we asked the authors for additional information when they reported a non-significant correlation between growth and trait without reporting an r value. All meta-analyses were conducted with R software \citep{Ralanguageanden:2014wf}.

\section*{Results}\label{results}

\subsection*{Main effects}

For both SLA and SM, the correlation between growth rate and the trait  changed significantly with plant size in the manner expected. Model fits improved when stage was incorporated (see log likelihood ratio tests, Fig. \ref{Fig2} a and d; average values for the coefficients r ($r_{\textrm{mean}}$) in Fig. \ref{FigA5}). The correlation between growth and SLA shifted from strongly positive at juvenile stage $r_{\textrm{mean}}=0.6 \pm 0.08$, Mean +SD) to not significantly different from zero at adult stage ($r_{\textrm{mean}}= -0.01 \pm 0.07$, CI 95\% overlapping zero in Fig. \ref{Fig2} a). The correlation between growth and SM shifted from negative at juvenile stage ($r_{\textrm{mean}}= -0.59 \pm 0.07$) to not significantly different from zero at adult stage ($r_{\textrm{mean}}= -0.09 \pm 0.02$, , CI 95\% overlapping zero in Fig. \ref{Fig2} d). For both traits,  correlation coefficients recorded at sapling stage were intermediate between juvenile and adult stages.

For WD, Hmax and Aarea, correlations with growth were also reasonably consistent with expectations, though with limitations arising from very unequal numbers of observations between growth stages. For Hmax, the expectation was for a correlation with growth to be absent for small plants but present at intermediate and larger sizes, the mechanism being increased relative allocation to reproduction as Hmax is approached. Indeed Hmax was positively correlated with growth at adult stage ($r_{\textrm{mean}}= 0.38 \pm 0.05$, n=18). At sapling and juvenile stages, the correlation between Hmax and growth was not significantly different from that observed at adult stage (model fit not improved when stage was incorporated, see log likelihood ratio tests in Fig. \ref{Fig2}c), but also was consistent with no correlation (Fig \ref{Fig2}c, confidence intervals overlapping zero), due to much smaller numbers of replicate studies. Similarly for WD and for Aarea, results were consistent with negative (WD) and positive (Aarea) correlations with growth across all plant sizes (Fig 2 b and e, model fit not improved when stage was incorporated). However, at the same time confidence intervals of r often spanned zero especially where there were small numbers of studies for particular growth stages.

\subsection*{Coverage of dataset}

Given our basic conclusion that reported correlations responded to plant size in a manner consistent with expectations from theory, we assess now the coverage of the available data, to determine if biased sampling could have erroneously generated the above results. The results reported were confined to correlations across species and under non-stressed conditions. A "complete" dataset (n=328 vs n=198) also included correlations measured at within-species level, and under stressed conditions, and spanning different plant stages. This "complete" dataset generated similar effect sizes to those reported above from the "ideal" dataset, and led to similar conclusions (Fig. \ref{Fig2} grey points). Differences concerned often the confidence intervals around particular mean effect sizes in Fig. 2. These differences in CI were not easily attributed to any single cause. For instance, the correlation between growth and WD at juvenile stage shifted from negative to non significant (i.e CI95\% included zero) due to 2 positive correlation coefficients from \citet{Augspurger:1984ct};  these correlations unlike others used wood density values from adult plants together with growth from juveniles. For Aarea, the comparison between complete and ideal data showed no signal of an effect of low light on the correlation with growth at seedling stage; the correlation was still positive between Aarea and growth even with 7 additional correlations measured under low light conditions.

Finally, our results were unlikely to be biased by dominance of one or a few studies that measured a large number of responses, since when multiple responses were condensed into a single average within a trait and within a study, outcomes were very similar (Fig. \ref{FigA6}) .

We were pleasantly surprised to find that correlations had been reported for at least two different stages across 18 traits out of the 20 targeted (Fig. \ref{Fig1}). We had thought it likely that for some traits correlations would be reported only for one size class, or only mixed across different sizes. However these limitations applied only for LAR and NARmass, where studies appeared confined to juvenile stages.

We found 108 studies published between between 1983 and 2014 that met our requirements. Climate zones spanned from temperate regions to  tropics (map in Fig. \ref{FigA3}). Different experiment types (laboratory, field, plantation or greenhouse) and growth measurements were included (see Fig. \ref{FigA7} for analyses of how these factors affected  correlations between growth and traits). Given this variety, it was not surprising to find wide ranges of r reported for all traits. For instance,  r varied from -0.98 to 0.99 for SLA, and from -0.74 to 0.74 for WD (Fig. \ref{FigA4}). Number of species used for each correlation ranged from 1 to 300 species with average  31. As expected the correlation coefficient varied less widely as sample size increased (funnel plots Fig. \ref{FigA8}). In the analyses described in Figs 2, A5 and A6 coefficients were weighted according to sample size, making the small-sample extremes less influential. Funnel plots exhibited a typical funnel shape for all five functional traits analyzed, showing no evidence for publication bias (Fig. \ref{FigA8}).

\section*{Discussion}\label{discussion}

The meta-analysis reported here demonstrates that the influence of traits on growth rates changes as plants grow from small to large, for several key traits. Plant growth rates change with size through ontogeny  \citep{Condit:1993hd, Clark:1999ed, Herault:2011dd} - \textit{they follow a trajectory of growth} - and species traits should be understood as influencing this trajectory and consequently rearranging the ranking of growth rates with size, rather than as rendering species fast-growing or slow-growing throughout life.

\subsection*{Traits influence on growth along plant size}

Further, for five prominent traits, the patterns observed are consistent with specific predictions from a mechanistic growth model. This indicates provisionally that the mechanisms through which traits affect growth are correctly understood in the model. For specific leaf area (SLA) and for seed mass (SM) the meta-analysis confirms quite strongly the predicted influence of plant size on the trait-growth correlation. For wood density (WD), assimilation rate of CO2 (Aarea) and maximum height (Hmax) results were consistent with predictions, but coverage was limited and additional studies would be helpful for some trait-growth-stage relationships.

It has previously been noted that the correlation of SLA with growth disappears among saplings and larger trees (\citealt{Wright:2010tp} for Barro Colorado Island forest, Panama), and this meta-analysis generalises that result. Several authors have suggested that the disappearance of SLA's influence on growth is associated with increasing total leaf area \citep{Reich:1992wm,Poorter:2008iu,Wright:2010tp}. In the model described here, the mechanism is slightly different: high-SLA species incur faster leaf and other tissues turnovers, the cost of which outweighs the benefits of cheap leaf construction at larger sizes.

% * <ian.wright@mq.edu.au> 2015-04-29T07:20:39.057Z:
%
% did all these authors really report that GR-SLA relationships diminish in strength with plant size? That is how it reads, but I don't think that's true???
%

%% Anais:
% wright et al 2010 "There is a strong negative relationship between LMA and early seedling growth rates; however, direct limitation of growth rates by large LMA decreases in importance as trees mature and leaf number increases (Lambers and Poorter 1992, Reich et al. 1992, Poorter et al. 2009).

% Poorter et al 2008: "Specific leaf area may be important for the performance of small plants, as leaf removal has a large impact on their survival (e.g., Pearson et al. 2003), but less important for the performance of large trees that have substantial reserves to recuperate from photosynthetic biomass loss (Wu ̈ rth et al. 2005). Similarly, SLA may be more important for light interception of saplings for which it determines to a large extent the total leaf area and leaf area ratio, but less so for large trees, for which leaf area and light interception are largely determined by branching patterns, the number of meristems, and tree architecture (Sterck and Bongers 2001)."

% Reich et al (1992): "Leaf mass per area illustrates two of the reasons that trait–demography relationships might be inherently weak at the sapling stage. The first is ontogenetic. There is a strong negative relationship between LMA and early seedling growth rates; however, direct limitation of growth rates by large LMA decreases in importance as trees mature and leaf number increases (Lambers and Poorter 1992, Reich et al. 1992, Poorter et al. 2009)."

%

For seedlings our meta-analyses showed as expected a negative relationship between seed mass and relative growth rate (in mass or height or volume) that disappeared across plant stage. This negative relationship arises because seedlings from larger seeds are larger to begin with, as extensively discussed in the literature \citep[reviewed by][]{Turnbull:2012ew}. It applies only to RGR not to absolute growth rate, but for seedlings growth is most often reported as RGR (Appendix FigA9 d).

For WD the meta-analysis showed negative correlation with growth across all plant stages, as previously reported from individual studies \citep{Wright:2010tp,Ruger:2012jv}. It should be noted however that there are few tests of this proposition at seedling stage. In our model (Appendix \ref{app:growth}) cheaper stem construction is responsible for the predicted negative correlation. Lower xylem conductance and associated lower photosynthetic potential have also been suggested \citep[reviewed by][]{Chave:2009iy}.

For the correlation between Aarea and growth, to our knowledge no study has previously assessed this in relation to plant size. In the growth model (Appendix \ref{app:growth}), a consistent correlation irrespective of size arises from a direct effect of Aarea on plant growth rate. We noted no signal of an effect of low light on the positive correlation between Aarea and growth rate in juvenile plants.

Meta-analysis showed a positive correlation between Hmax and growth for adult stage, but not for saplings and juveniles. The trend for tall stature species to grow faster at a given tree size than small stature species has been noted across several tree size classes and forest types \citep{Kohyama:2003dk,Poorter:2008iu,MartinezVilalta:2010iq,Wright:2010tp,Herault:2011dd,Ruger:2012jv, Iida:2014ep}. In \citet{Wright:2010tp}, Hmax was considered as the weakest predictor of growth rates of saplings; however it was the strongest predictor of growth rates of large trees. \citet{Poorter:2008iu} speculated that the Hmax-RGR relationship among large trees might arise from including small tree species with maximum size not much larger than the  10cm dbh lower threshold used to define large trees. In our growth equations, Hmax affects growth via the fraction of energy diverted to reproduction. At a given tree size, species closer to their Hmax are expected to be allocating relatively less to vegetative growth. However this applies only at sizes where some of the species have begun to reproduce, and should not affect sapling and juvenile growth rates.

\subsection*{No signal of cross-correlations among different traits}

It is notable that the expected correlations between traits and growth do not appear to be much overridden by cross-correlations among different traits. A recurring issue in trait ecology is how many of the observed correlations arise directly from mechanisms, versus how many from secondary cross-correlation. For example, several papers have suggested that correlations between Hmax and growth rate may arise via cross-correlation with other traits such as WD \citep{Thomas:1996do, Poorter:2006vb, Wright:2010tp}. Similarly, effects of SM on growth have been suspected to be mediated via other traits \citep{Shipley:1990js,Westoby:2002ft,Poorter:2006vb}. Secondary cross-correlation might also potentially have the effect of suppressing a correlation that would otherwise be present. While such effects may still be observed within individual studies, across the range of studies reported we found that the available data were consistent with predictions arising directly from mechanisms.

\subsection*{Future research directions}

Light and water micro-environments can affect growth values, and might modify correlations with traits in relation to plant size. For example, instead of a positive relationship that disappeared with plant size, \citet{Iida:2014ep} found SLA was negatively correlated with RGR at small size and positively correlated with RGR at larger sizes. Similarly, instead of a negative correlation between WD and growth across all plant stages, \citep{Iida:2014ep,Iida:2014hq} found a negative correlation at small size that disappeared when trees were larger. \citet{Iida:2014hq} explained the switch in directionality by changes in light and water condition up the vertical profile within a forest: larger trees reached a position in the canopy where they were released from light limitations, other resources such as water may have become limiting, and the performance of trees may then have been regulated by different traits. Note that in \citet{Iida:2014hq}, the shift in the correlation between growth and WD occurred for trees larger than 22-26 cm dbh. This points to one of the possible limitations in our meta-analysis, where trees with height above 5 m were pooled as "adult".

Clearly there is much scope for strengthening our understanding of correlations between traits and growth through (1) adding further empirical studies for traits and size-classes with weaker representation, (2) accounting more satisfactorily for variables such as light, and (3) expressing plant sizes on continuous scales of mass or height rather than through the approximate and partly subjective categories unavoidably adopted here. Additional data are specifically required in small plants (juvenile and sapling) for WD and Hmax, and in large plants (adult and sapling) for Aarea and more broadly for all traits requiring a measure of whole plant biomass (e.g. LMR, LAR, NAR). Nevertheless the existing published evidence, even with all its limitations, is consistent with predictions from a simple growth model, and this suggests that species traits can shed light on their growth trajectories, and hence on the changing growth rate rankings across species as individuals become larger.

\section*{Acknowledgements}\label{Acknowledgment}

We thank Andrea Stephens for helpful comments on the meta-analyses, and Sean Gleason et al for pre-publication access to their data. Charles Warren and Jordi Martìnez-Vilalta kindly provided additional information about their published results. This work was funded by the Australian Research Council through a fellowship to Westoby.

\clearpage
\linespread{1}

\bibliography{references/complete}\label{references}

\newpage
\section*{Figures}

\begin{figure}[htbp]
\centering
\includegraphics{output/Fig1.pdf}
\caption{\textbf{Number of correlations between trait and growth for each plant stage recorded in our dataset.} Shown here are 'complete dataset' (recorded at both interspecific and intraspecific level, under unstressed and stressed conditions). Bar colors: red for adult stage, orange for sapling, grey for juvenile. Aarea (or Amass) = rate of $CO_{2}$ assimilation per unit leaf area (or leaf mass) = maximum photosynthetic rate, Hmax= asymptotic maximum height,  Ks =stem hydraulic conductance, LA = leaf area, LMR = leaf mass ratio, NARarea (or NARmass) = net mass assimilation rate per unit of leaf area (or leaf mass), Nmass (or Narea) = nitrogen content per unit of leaf mass (or leaf area), Pmass = phosphorus content per unit of leaf mass, SA/LA = sapwood area per leaf area, SLA = specific leaf area, thickness = leaf thickness, Vessel size = stem conduit size, vessel density = stem conduit density, WD = wood density}
\label{Fig1}
\end{figure}

\begin{figure}[htbp]
\centering
\includegraphics{output/Fig2.pdf}
\caption{\textbf{The relationship between growth rates and SLA or seed mass changes with plant stage.} Plots show the effect size (+ 95\%CI) of the correlation between growth rate and five functional traits for plant stage comparisons. \textbf{a)} Specific leaf area (SLA), \textbf{b)} Wood density (WD), \textbf{c)} Asymptotic height (Hmax) \textbf{d)} Seed mass and \textbf{e)} Assimilation rate of CO2 (Aarea). Effect size is a standardized measure of the deviation of the correlation coefficient from zero (Fisher's z-transformed). Effects are significant if confidence intervals (+ 95\%CI) for a given stage do not overlap with zero.  Black symbols for "ideal" data (using only interspecific correlations, growth under control conditions), grey symbols using "complete" data (see Methods for further explanation). 'n' indicates number of correlations contributing to each effect. Likelihood Ratio Tests (LRT, for ideal data only) compared maximum-likelihood fits between a pooled model and one separated by stage. If the LRT returned a significant p-value, the stage model fitted the data better than the null model.
}
\label{Fig2}

% Is it Ecol Lett style to have a declarative first sentence in Fig legends stating the main result? -- or should the explanation be more deadpan, relying on the main text to make the point?

\end{figure}

\newpage

\begin{appendices} \label{sec:appendices}

\renewcommand{\thefigure}{A\arabic{figure}}
\renewcommand{\thetable}{A\arabic{table}}

\setcounter{figure}{0}
\setcounter{table}{0}

\section{Derivation of hypotheses from growth equations}\label{app:growth}

We adapted growth equations from \cite{Falster:2011ii} and \cite{falster:2013} to generate hypotheses on both absolute and relative growth rates in biomass (b, eqn \ref{eq:eq1}), height (H, eqn \ref{eq:eq2}) and diameter (D, eqn \ref{eq:eq4}). These size dimensions are measured on seedling and adult plants. Here we provide a brief overview of the model; an upcoming publication will elaborate further on the predicted relationships between traits and growth rate.

Let $m_i$ denote the mass, $r_i$ the mass-specific respiration rate, and $k_i$ the turnover rate of different plant tissues, with the subscripts $i=l,s,r,t$ referring to leaves, sapwood and bark, roots, and total plant. Similarly let $a_i$ denote areas, of leaves ($i=l$) and of cross-sections of total stem, sapwood and heartwood ($i= st,ss,sh$) respectively.

The rate at which biomass $b$ of the plant increases is given by
%MW: phrasing changed here and a bit under the equations because I would say that "biomass originating from the plant" should be regarded as including turnover
\begin{equation}\label{eq:eq1}
\underbrace{\frac{db}{dt}}_{\text{biomass increase rate}} = \underbrace{y}_{\text{yield}}  \big(\underbrace{a_{l} A_{\textrm{area}}}_{\text{photosynthesis}} - \underbrace{\sum_{i=l,s,r} m_{i} r_{i}}_{\text{respiration}}\big) - \underbrace{ \sum_{i=l,s,r} m_{i} k_{i}}_{\text{turnover}},
\end{equation}
where $y$ is the fraction of assimilated carbon fixed into biomass,  and  $A_{\textrm{area}}$ is the assimilation rate of CO$_{2}$ per leaf area. Height growth rate can then be expressed as
\begin{equation}\label{eq:eq2}
\underbrace{\frac{dH}{dt}}_{\text{growth rate in height}} = \underbrace{\frac{dH}{da_{l}}}_{\text{architecture layout}} \times \underbrace{\frac{da_{l}}{dm_{t}}}_{\text{leaf deployment per mass}} \times \underbrace{\frac{dm_t}{db}}_{\text{allocation to growth}}  \times \underbrace{\frac{db}{dt}}_{\text{biomass increase rate}}.
\end{equation}

where allocation to growth is the fraction of biomass increase that goes to vegetative growth rather than to seed production. Similarly basal area growth can be expressed as
\begin{equation}\label{eq:eq3}
\underbrace{\frac{da_{st}}{dt}}_{\text{basal area increment}} = \underbrace{\frac{da_{ss}}{da_{l}}}_{\text{sapwood area per leaf area}} \times \frac{da_{l}}{dm_{t}} \times\frac{dm_t}{db} \times\frac{db}{dt} +  \underbrace{ k_{s} a_s }_{\text{sapwood turnover}}.
\end{equation}

The growth rate in diameter is then given by the geometric relationship between diameter and area applied to stem:
\begin{equation}\label{eq:eq4}
\frac{dD}{dt} = \sqrt[]{\frac{\Pi}{a_{st}}} \times \frac{da_{st}}{dt}.
\end{equation}

For the case of seedlings, eqn \ref{eq:eq1} can be simplified considerably. Turnover of tissues has not yet begun. It is common also to ignore respiration of non-leaf tissues and to let leaf respiration rate be proportional to leaf area. Biomass growth rate then becomes a linear function of leaf area:
%MW: I wonder whether it might be better to think of this as letting total respiration (including roots) be proportional to leaf area?
\begin{equation}\label{eq:eq1_seedlings}
\frac{db}{dt}  \approx  a_{l} \, y \, (A_{\textrm{area}} - r_{l}).
\end{equation}
A relative growth rate (RGR) in mass can be obtained by dividing both sides of this simplified eq \ref{eq:eq1_seedlings} by the total mass of living tissues $m_{t} = m_{l} + m_{s} + m_{r}$. The outcome is equivalent to the classical partitioning of RGR \citep{Lambers:1992bj, Cornelissen:1998ta}:
\begin{equation}\label{eq:eq1_seedlings_RGR}
\textrm{RGR}  \approx \textrm{NAR} \times  \textrm{SLA} \times  \textrm{LMF},
\end{equation}
 where NAR is net assimilation rate ($y \, (A_{\textrm{area}} - r_{l})$), SLA = $a_{l}/ m_{l}$ and LMF is leaf mass fraction ($m_{l}/ m_{t}$).

The predicted effects of different traits on growth can then be understood by considering the influence of trait variation on elements of equations  \ref{eq:eq1}-\ref{eq:eq4} and how these may interact with plant size.

\begin{table}[ht]
\centering
\caption{\textbf{ Hypothesised effect of traits on components of growth. Arrows indicate the effect an increase in trait value would have on elements of growth (as described  in Eqs. \ref{eq:eq1}-\ref{eq:eq4}) and other aspects of life history.}}
  \begin{tabular}[c]{l|c|cccc|c|c}
  \multicolumn{8}{c}{}\\ \hline
  & \multicolumn{7}{c}{\textbf{Effect of trait on}}\\
  & \textbf{Birth} & \multicolumn{4}{c|}{\textbf{Growth}} & \textbf{Survival} & \textbf{Fecundity} \\
  & \textbf{size}
  & $\frac{\textrm{d}a_\textrm{l}}{\textrm{d}m_\textrm{t}}$
  & $\frac{\textrm{d}m_\textrm{t}}{\textrm{d}b}$
  & $\frac{\textrm{d}b}{\textrm{d}t}$
  & $k_s$ & &  \\\hline
  Seed size & $\uparrow$ & & & & & & $\downarrow$ \\
  Aarea & & & & $\uparrow$& &  \\
Leaf mass per area & & $\downarrow$ & & $\uparrow$ & &  \\
  Wood density& & $\downarrow$ &  & & & $\uparrow$  \\
  Maximum height & & &$\uparrow$ & & & & $\downarrow$  \\
\hline
%MW I'm struggling to understand why db/dt should be one of the terms listed under "growth" -- surely it just is growth, not one of the contributing terms in a growth eqn?
%MW I think this probably should be done in terms of SLA rather than LMA -- that's the way most of the rest of the paper is done from memory, and especially the immediate next para
%MW does SLA not affect leaf turnover rates? (also the text does actually slightly refer to WD affecting sapwood turnover, but this is complicated and I can appreciate it may be better to evade this issue here)
%MW the up-and-down for Aarea seems too complicated (see comment below) -- have replaced with a simple up
%MW I'm inclined to think the columns for birth size, survival and fecundity don't help here -- I understand the logic, but mostly we don't discuss or explain them and so they're distracting
  \end{tabular}
\label{tab:trade-offs}
\end{table}

First, the relationship between SLA and growth rate is predicted to shift from positive for seedlings to non-significant or negative in adult plants, regardless of the growth measurement used.  For seedlings (eq. \ref{eq:eq1_seedlings_RGR}) cheaper leaf construction (high SLA) should translate directly into faster relative growth rate in mass. For larger plants (eq. \ref{eq:eq1}-\ref{eq:eq4}), SLA is expected to affect growth rate positively through more cost-efficient deployment of leaf area (via $da_l/dm_t$); the same effect as in seedlings), but also negatively via increased leaf turnover (eqn 1; Table \ref{tab:trade-offs}). The effect of SLA on $da_l/dm_t$ decreases as plant size increases and increasing amounts of the plant are wood. Consequently the effect of turnover costs in slowing growth comes to dominate at larger sizes.
%MW: I suggest we should not use phrases like "regardless of the growth measurement used" except in cases where we're actually going to explain properly. Currently eqns 1-5 are expressed as absolute growth rate and eqn 6 as RGR. But nowhere do we make explicit comparisons of an absolute growth eqn with a relative growth eqn
Second, the relationship between WD and growth rate is predicted to be negative across all plant sizes. Cheaper stem construction (low WD or stem density) also increases the marginal rate of leaf deployment per total mass increment (via $da_l/dm_t$), and consequently increases growth rate in leaf area, height and diameter (eqs. \ref{eq:eq2}-\ref{eq:eq4}). Disadvantages associated with cheap stem construction take the form of higher mortality and so are not reflected in growth equations (Table \ref{tab:trade-offs}). Under this scenario, wood density is negatively correlated to growth rate across all plant stages. Because the relative expenditure on stem compared to leaf is expected to increase as plants grow larger, the relationship between WD and growth may also strengthen in larger plants.

Third, the relationship between height at maturation (Hmax) and growth rate is predicted to be positive in adults, whereas no correlation is expected for seedlings and juveniles. Hmax affects growth via the fraction of energy allocated to vegetative growth versus to seed production  (dmt/db in eqn 2; Table \ref{tab:trade-offs}). For juveniles and seedlings this fraction is 1 for all species and so no effect is expected. But once some species begin to produce seed, then species closer to their Hmax value are expected to be allocating more to seed production and less to vegetative growth. Hence when comparing across plants at a given size, species with smaller Hmax are expected to show slower vegetative growth rates.

Fourth, the relationship between seed mass and relative growth rate is predicted to be negative in seedlings. This is because the relative growth rate slows as plants grow larger, and large-seeded species begin larger as seedlings. For larger plants, seed mass is not expected to have any distinct influence on growth rates  (Table \ref{tab:trade-offs}).
%MW: in my opinion the -ve correlation expectation applies only to RGR not to absolute growth rate
Finally, the relationship between Aarea and growth should be positive across all plant sizes (eqn 1). The effects of benefits (higher assimilation) and costs (higher respiration) of increased Area occur within the same element of equations 1 and 5, and assimilation must outweigh respiration for there to be growth, so the net effect will be positive (Table \ref{tab:trade-offs}).
%MW is that what the up-and-down arrows in the table are meant to convey? Too complicated I suggest -- and also it doesn't actually explain why r'ship is positive, though it does explain why it's consistent across sizes. Have suggested a rewrite.

\newpage

\section{Supporting files}\label{app:supp_info_files}

The following files are provided:

\begin{itemize}
  \item "references\_metaanalyses.bib": reference library containing all references used in eventual metanalysis (in bibtex format)
  \item "code.zip": the data and analysis code used to generate the results in this paper. A copy of the complete data set is also available from the Dryad Digital Repository.
\end{itemize}

\newpage
\section{Supporting tables}\label{app:supp_info_tables}

\begin{table}[ht]
\centering
\caption{\textbf{List of the twenty traits targeted}. Abbreviation,
definition and search term used in the meta-analysis}
\label{TableA1}
\vspace{0.5cm}
\begin{tabular}{p{3cm}p{3cm}p{8cm}}
  \hline
Trait & Definition & Search terms \\
  \hline
Aarea & Photosynthetic rate per area & "photosynthetic rate per area" OR "rate of CO2 assimilation per area" OR "Aarea" OR "Amax" OR "photosynthetic capacity per area" \\
  Amass & Photosynthetic rate per mass & "photosynthetic rate per mass" OR "rate of CO2 assimilation per mass" OR "Amass" OR "Amax" \\
  Hmax & Maximum height & "potential height" OR "maximum height" OR "Hmax" \\
  Ks & Stem specific conductance & "Ks" OR "stem specific conductance" OR "stem hydraulic conductance" OR "sapwood conductance" \\
  LA & Leaf lamina area & "leaf length" OR "leaf lamina area" OR "leaf width" OR "leaf size" \\
  LAR & Leaf area ratio & "leaf area ratio" \\
  LMR & Leaf mass ratio & "leaf mass ratio" OR "leaf mass fraction" \\
  NARarea & Net assimilation rate per area &  "net assimilation rate per area" OR "rate of dry mass increament per area" OR "NARarea" OR "NAR" \\
  Narea & Leaf nitrogen content per area & "Narea" OR "nitrogen per area" OR "N/area" OR "leaf nitrogen content per area" OR "LNCarea" OR "leaf nitrogen content" \\
  NARmass & Net assimilation rate per mass &  "net assimilation rate per mass" OR "rate of dry mass increament per mass" OR "NARmass" OR "NAR" \\
  Nmass & Leaf nitrogen content per mass & "Nmass" OR "nitrogen per mass" OR "N/mass" OR "leaf nitrogen content per mass" OR "LNCmass" OR "leaf nitrogen content" \\
  Parea & Leaf phosphorus content per area & "Parea" OR "leaf P" OR  "leaf phosphorus content per area"  OR "leaf phosphorus content" \\
  Pmass & Leaf phosphorus content per mass & "Pmass" OR "leaf P" OR  "leaf phosphorus content per mass" OR "leaf phosphorus content" \\
  SA/LA & Sapwood area per leaf area & "sapwood area per leaf area" OR "huber value" OR "leaf area per sapwood area" \\
  Seed mass & Seed mass & "seed mass" OR "seed size" OR "seed volume" \\
  SLA & Specific Leaf Area & "leaf mass per area" OR "specific leaf area" OR "leaf construction cost" \\
  Thickness & Leaf thickness & "leaf thickness"  OR "leaf tissue density" \\
  Vessel density & Vessel density & "vessel density" OR "stem conduit density" \\
  Vessel size & Vessel area or diameter & "conduit area" OR "stem conduit area" OR "vessel diameter" OR "vessel size" OR "conduit size"   \\
  WD & Wood density & "wood density" OR"WD" OR "wood specific gravity" OR "stem density" OR "stem specific density" OR "SSD" \\
   \hline
\end{tabular}
\end{table}

\newpage
\section{Supporting figures}\label{app:supp_info_figures}

\begin{figure}[htbp]
\centering
\includegraphics{output/FigA1.pdf}
\caption{\textbf{Range of plant size in \textbf{a)} age, \textbf{b)} height and \textbf{c)} diameter and their assigned plant stage} Each segment represents the plant size range addressed in our dataset. ID is the reference number of the article in our dataset. The colors represents the stage information given by the authors (green: seedling, blue:juvenile, orange: sapling, red: adult, grey: mix), and the vertical line the limit we choose to established our stage categories. Shown here are complete dataset (recorded at both interspecific and intraspecific level and under unstressed and stressed conditions). }
\label{FigA1}
\end{figure}

\begin{figure}[htbp]
\centering
\includegraphics{output/FigA2.pdf}
\caption{\textbf{Allometric relationships between a) age and diameter (m), b) age and height (m), and c) diameter and height in trees according to the BAAD database}. Green and red lines are the cutoffs between stage categories used in the meta-analyses. Green lines corresponds to limits between juveniles and saplings, red lines to limits between saplings and adults.}
\label{FigA2}
\end{figure}

\begin{figure}[htbp]
\centering
\includegraphics{output/FigA3.pdf}
\caption{\textbf{Geographical distribution of site locations from studies performed in the field used in the meta-analysis.} Shown here are complete dataset (recorded at both interspecific and intraspecific level and under unstressed and stressed conditions).}
\label{FigA3}
\end{figure}

\begin{figure}[htbp]
\centering
\includegraphics{output/FigA4.pdf}
\caption{\textbf{Range of the correlation of correlations (r) between
growth and trait across the world} Coefficients of correlation (r)
between the plant growth and \textbf{a)} Specific leaf area (SLA, n=
111), \textbf{b)} Wood density (WD, n=64), \textbf{c)} Asymptotic
maximum height (Hmax, n=23), \textbf{d)} Seed mass (Seedmass, n=36 and
\textbf{e)} Rate of CO2 assimilation (Aarea, n=24) reported from 108
articles. Shown here are complete dataset (recorded at both interspecific and intraspecific level and under unstressed and stressed conditions). Each bubble represents a r value, the diameter of the bubble
is proportional to its weights in the meta-analysis. The colors
correspond to the stage for which the r values have been recorded: red
points corresponds adult stage, orange points to saplings, and grey
points to juveniles.}
\label{FigA4}
\end{figure}

\begin{figure}[htbp]
\centering
\includegraphics{output/FigA5.pdf}
\caption{\textbf{Mean coefficient correlation r (+SD) between growth
rate and traits, established from 107 published articles.} The mean
coefficents are weighted by sample size (i.e number of species used to
perform the correlation), and calculated both across all plant stages
and for each stage. Each panel correponds to a functional trait:
\textbf{a)} Specific leaf area (SLA), \textbf{b)} Wood density (WD),
\textbf{c)} Net assimilation rate (NARarea), \textbf{d)} Seed mass,
\textbf{e)} Asymptotic height (Hmax) and \textbf{f)} Assimilation rate
of CO2 (Aarea). Shown here are ideal dataset (recorded at interspecific level and under unstressed  conditions)}
\label{FigA5}
\end{figure}

\begin{figure}[htbp]
\centering
\includegraphics{output/FigA6.pdf}
\caption{\textbf{Effect size (+ 95\%CI)of plant stage on the
correlations between growth rate and five functional traits, with a data set averaging multiple comparisons by trait and by study.} Effects size are calculated from a reduced dataset; in the case of multiple comparisons within a study, we calculated the mean correlation coefficient by trait and by study. a) Specific leaf area (SLA), b) Wood density (WD), c) Net assimilation rate (NARarea), d) Seed mass, e) Asymptotic height (Hmax) and f) Assimilation rate of CO2 (Aarea). Effect size is a standardized measure of the magnitude of the relationship between a particular stage and the correlation coefficient z (Fisher's z-transformed). Effects are significants if confidence intervals (+CI95\%) do not overlap with zero. LRT: likelihood Ratio Test compared the fit between null model and stage model, both models are fitted by Maximum Likelihood. Black point: ideal data (at interspecific level \& under control conditions), grey points: all the data. `n' indicate the number of independent comparisons for each effect.}
\label{FigA6}
\end{figure}

\begin{figure}[htbp]
\centering
\includegraphics{output/FigA7a.pdf}
\end{figure}

\begin{figure}[htbp]
\centering
\includegraphics{output/FigA7b.pdf}
\end{figure}

\begin{figure}[htbp]
\centering
\includegraphics{output/FigA7e.pdf}
\end{figure}

\begin{figure}[htbp]
\centering
\includegraphics{output/FigA7c.pdf}
\end{figure}

\begin{figure}[htbp]
\centering
\includegraphics{output/FigA7d.pdf}
\caption{\textbf{Effects size on the correlation between growth and
traits of plant stage (mod1, as recorded by the authors), vegetation type
(mod2), growth measurement (mod3) and experiment type (mod4).} The effect size
(z) is reported for each class, with its 95\%CI and models are fitted by
restricted max likelihood (REML). n= number of correlation r reported.
(Abbreviation: boreal\&temp = mix boreal and temperate deciduous forest,
med= Mediterranean, across veg = correlation performed on species from
more than 2 vegetation types, temp\&med = mix between temperate
deciduous and Mediterranean forest, temp= temperate deciduous forest,
temp rain= temperate rain forest, trop rain= tropical rain forest, trop
seas = tropical seasonal forest, GR(D)= growth rate measure in diameter,
GR(H) = growth rate in height, GR(M)= growth rate in Mass, RGR(CSA)=
relative growth rate in cross section area, etc). AIC: Akaike
information criterion corresponds to the quality of each model, and
allow a comparison between model. Smallest is the AIC better is the
model. Shown here are complete dataset (recorded at both interspecific and intraspecific level and under unstressed and stressed conditions).}
\label{FigA7}
\end{figure}

\begin{figure}[htbp]
\centering
\includegraphics{output/FigA8.pdf}
\caption{\textbf{Funnel plots showing transformed correlation coefficient z between growth and the traits a) Specific leaf area
(SLA), b) Wood density (WD), c) Asymptotic height (Hmax), d) Seed mass and e) Assimilation rate of CO2 (Aarea)}. Shown here are complete dataset (recorded at both interspecific and intraspecific level and under unstressed and stressed conditions). The color of the points corresponds to the stage for which the correlation was measured (Red points : adult, orange point : sapling, grey: juvenile). Note that in these plots the x axis is the number of species included in the correlation, not the replication for the correlation. The number of species is sometimes as low as 1, and these are within-species correlations. The number of replicates used for the correlation coefficient was often much greater than the number of species, especially for studies involving 5 or less species. Nevertheless  the characteristic shape of funnel plots is observed, with correlations involving few species showing much wider variation even though within-species replication was sometimes high.}

\label{FigA8}
\end{figure}

\begin{figure}[htbp]
\centering
\includegraphics{output/FigA9.pdf}
\caption{\textbf{Growth measurement used by traits and by size.} Shown here are complete dataset (recorded at both interspecific and intraspecific level and under unstressed and stressed conditions). The colors correspond to the stage for which the r values have been recorded: red bars corresponds adult stage, orange bars to saplings, and grey bars to juveniles.}
\label{FigA9}
\end{figure}

\end{appendices}
\end{document}

### 2015-05-06 R/data_processing.R

@@ -1,0 +1,338 @@
+clean_raw_data <- function(filename = "data/CompileData.csv") {
+
+  Table <- read.csv(filename, sep = ";", dec = ",")
+
+  for(f in c("id","ref","idcor","authors","stress","RGR","trait","coef.type","experiment.type",
+    "veg.type","measure.size","trait.stage","stage","RGR.stage","relation.sign","stage.simi")) {
+   Table[[f]] <- as.factor(Table[[f]])
+  }
+
+  for(f in c("size.min","size.max","size.mean.range","sample.size","nb.sp.reported","coef",
+    "RGR.min","RGR.max","trait.min","trait.max")) {
+   Table[[f]] <- as.numeric(Table[[f]])
+  }
+
+  ### Transformation of raw data ####
+
+  ## Transformation LMA en SLA
+  fun_LMA <- function(x) (x * -1)
+
+  for (i in 1:length(Table$coef)) {
+    if (Table$trait[i] == "LMA") {
+      Table$coef[i] <- fun_LMA(x = Table$coef[i])
+    }
+  }
+  Table$trait[Table$trait == "LMA"] <- "SLA"
+
+  # Transformation seedvolume in seedmass
+  Table$trait[Table$trait == "SeedVolume"] <- "Seedmass"
+
+  # Transformation of correlation sign in correlation significance
+  Table["sign"] <- "NA"
+  Table$sign[Table$relation.sign == "P"] <- "S"
+  Table$sign[Table$relation.sign == "N"] <- "S"
+  Table$sign[Table$relation.sign == "O"] <- "NS"
+
+  # Nb of species used to performed the correlation
+  names(Table)[names(Table) == "nb.sp.reported"] <- "nb.sp"
+
+  i <- Table$nb.sp > Table$sample.size
+  Table$nb.sp[i] <- Table$sample.size[i]
+
+  i <- Table$bio.scale == "intrasp"
+  Table$nb.sp[i] <- 1
+
+  ## Clean the data trait stage
+  Table["stageTrait"] <- NA
+  Table$stageTrait <- Table$trait.stage
+  Table$stageTrait[Table$trait.stage == "adult?"] <- "adult"
+  Table$stageTrait[Table$trait.stage == "sapling?"] <- "sapling"
+  Table$stageTrait[Table$trait.stage == "juvenile?"] <- "juvenile"
+  Table$stageTrait[Table$trait.stage == "seedling?"] <- "seedling"
[…]

### 2015-05-06 R/model.R

@@ -1,0 +1,204 @@
+
+# function for calculating effect size and intercept of the model with and
+# without the explanatory variable : stage
+
+fun_model <- function(x, y) {
+  # models for x ('ideal' dataset) and y ('complete' datatset)
+  null <- lmer(corr.z ~ 1 + (1 | id), data = x, weights = nb.sp, REML = TRUE, 
+    control = lmerControl(check.nobs.vs.nlev = "ignore", check.nobs.vs.rankZ = "ignore", 
+      check.nobs.vs.nRE = "ignore"))  # modele null cad sans la variable que je veux analyser
+  m <- lmer(corr.z ~ stage + (1 | id), data = x, weights = nb.sp, REML = TRUE, 
+    control = lmerControl(check.nobs.vs.nlev = "ignore", check.nobs.vs.rankZ = "ignore", 
+      check.nobs.vs.nRE = "ignore"))  # model avec la variable
+  m1 <- lmer(corr.z ~ stage - 1 + (1 | id), data = x, weights = nb.sp, REML = TRUE, 
+    control = lmerControl(check.nobs.vs.nlev = "ignore", check.nobs.vs.rankZ = "ignore", 
+      check.nobs.vs.nRE = "ignore"))  # model avec les intercepts qui sont a 1
+  
+  null.s <- lmer(corr.z ~ 1 + (1 | id), data = y, weights = nb.sp, REML = TRUE, 
+    control = lmerControl(check.nobs.vs.nlev = "ignore", check.nobs.vs.rankZ = "ignore", 
+      check.nobs.vs.nRE = "ignore"))  # idem mais pour le jeux y
+  m.s <- lmer(corr.z ~ stage + (1 | id), data = y, weights = nb.sp, REML = TRUE, 
+    control = lmerControl(check.nobs.vs.nlev = "ignore", check.nobs.vs.rankZ = "ignore", 
+      check.nobs.vs.nRE = "ignore"))
+  m1.s <- lmer(corr.z ~ stage - 1 + (1 | id), data = y, weights = nb.sp, REML = TRUE, 
+    control = lmerControl(check.nobs.vs.nlev = "ignore", check.nobs.vs.rankZ = "ignore", 
+      check.nobs.vs.nRE = "ignore"))
[…]

### 2015-05-06 R/plots.R

@@ -1,0 +1,232 @@
+
+mytheme <- theme_bw() + theme(text = element_text(size = 9, colour = "black"),
+  title = element_text(size = 9, hjust = 0), axis.title = element_text(size = 9,
+    hjust = 0.5), axis.text = element_text(size = 8), axis.line = element_line(colour = "black"),
+  panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.border = element_blank(),
+  panel.background = element_blank(), legend.justification = c(1, 0), legend.position = c(1,
+    0))
+
+
+my_plot_1 <- function(title, ggobj, xlab = expression(paste("")), ylab = "Number of correlations extracted") {
+  p <- ggobj + geom_bar() + coord_cartesian(ylim = ylim) + coord_flip() + labs(title = title) +
+    xlab(xlab) + ylab(ylab) + scale_x_discrete() + theme(text = element_text(size = 9),
+    axis.text.x = element_text(size = 9, angle = 0, vjust = 1)) + mytheme +
+    theme(axis.title = element_text(size = 10, hjust = 0.5)) + scale_fill_manual(values = c(juvenile = "grey",
+    sapling = "orange", adult = "red"), breaks = c("juvenile", "sapling", "adult"),
+    labels = c("juvenile", "sapling", "adult"))
+  p
+}
+
+coeff.plot <- function(data, data.complete, data.ideal, LRT, PVAL, title = "",
+  significativite = "", round.value, limit.x.min, limit.x.max, limit.x.text,
+  limit.x.n, limit.y.text.l1, limit.y.text.l2, vjust.value, color1, color2) {
+  data.complete["x.coord"] <- limit.x.n
+  data.ideal["x.coord"] <- limit.x.n
+
+
+  my_size_effect_plot1 <- function(title, ggobj, xlab = "Effect size + CI (95%) ",
+    ylab = "Stages") {
+    p <- ggobj + labs(title = title) + xlab(xlab) + ylab(ylab) + geom_vline(yintercept = 0,
+      color = "white") + geom_hline(yintercept = 0, size = 0.3, linetype = "dashed") +
+      scale_x_discrete("stage", limit = c("juvenile", "sapling", "adult")) +
+      coord_flip() + mytheme + theme(legend.position = "none")
+    p
+  }
+
+  dodge <- position_dodge(width = 0.4)
+
[…]

### 2015-05-06 analysis.R

@@ -1,0 +1,117 @@
+
+# OPEN LIBRARY
+library(MASS, quietly=TRUE)
+library(car, quietly=TRUE)
+library(lsr, quietly=TRUE)
+library(lme4, quietly=TRUE)
+library(nlme)
+library(ape)
+library(boot)
+library(Hmisc)
+
+library(metafor)
+library(ade4, quietly=TRUE)
+library(ggplot2, quietly=TRUE)
+library(gridExtra, quietly=TRUE)
+library(MAc,quietly=TRUE)
+library(maptools)
+library(downloader)
+
+for( f in list.files("R", full.names=TRUE)) {
+  source(f)
+}
+
+CompileTable <- clean_raw_data()
+RawData <- standardise_data(CompileTable)
+CompleteData <- build_complete_data(RawData)
+IdealData  <- build_ideal_data(CompleteData)
+CoordTable <- build_map_data(RawData)
+
+## split datasets by trait - makes a list with named elements
+## given subset of data for each trait
+list_by_trait <- function(df) {
+  split(df, df$trait)
+}
+
+GC <- list_by_trait(CompleteData)
+GI <- list_by_trait(IdealData)
+
+## Create restricted Dataset: coefficient of correlation are averaged by study and by trait
+RC <- list_by_trait(EffectSizeSum(CompleteData))
+RI <- list_by_trait(EffectSizeSum(IdealData))
+
+## output directory
+
+dir.create("output", showWarnings =FALSE)
+
+## Export compiled dataset
+write.csv(RawData, "output/data.csv", row.names=FALSE)
+
+## Make output
+pdf("output/Fig1.pdf",height=3, width=4)
+  figure_1(RawData)
+dev.off()
+
+pdf("output/Fig2.pdf",height=6,width=5)
+  figure_2(GC, GI)
+dev.off()
+
+pdf("output/FigA1.pdf", height=6)
+  figure_A1(CompleteData)
+dev.off()
+
+
+pdf("output/FigA2.pdf", height=6, width=6)
+  figure_allometry()
+dev.off()
+
+pdf("output/FigA3.pdf", height=3, width=6)
+  figure_map(CoordTable)
+dev.off()
+
+pdf("output/FigA4.pdf",height=6,width=6)
[…]

### 2015-05-06 analysis.R
Add missing file

@@ -8,6 +8,7 @@ library(nlme)
 library(ape)
 library(boot)
 library(Hmisc)
+library(plyr)
 
 library(metafor)
 library(ade4, quietly=TRUE)

### 2015-05-06 MS.tex
Import latest from overleaf

@@
 \geometry{verbose,tmargin=2cm,bmargin=2cm,lmargin=2cm,rmargin=2.5cm}
-\linespread{1.5}
+\linespread{2}
+\usepackage{hyperref}
 
@@
 But of course if you prefer to consider it as a review, then we are in your hands.
-
-May we please raise with you an issue about the literature cited?
-(It need not affect the review process.) We strongly believe that authors whose data publications enter into meta-analyses deserve to get credit via citation.
-But because of the restriction on citations in the main text, these citations are in appendices in the current draft, rather than in the main list of Literature Cited.
-We hope you may have a solution to situations of this kind?
-We understand some journals now make provision for literature cited in appendices or supp info to be scanned by ISI and other cite-counting agencies?
-Or perhaps the restrictions on number of papers cited can be relaxed for meta-analyses?
 
@@
 
-\textbf{Keywords (8/10)} asymptotic maximum height, maximum photosynthetic rate, plant ontogenetic stage, plant functional traits, plant growth strategy, seed mass, specific leaf area, wood density
+\textit{Statement of authorship} MW, DF, IW, AG designed the study, IW and DF provided their bibliography database, AG and EG searched and collected the data, AG performed the meta-analyses, DF performed modeling work, AG wrote the first draft, MW improved substantially the manuscript, and all authors contributed to revisions.
 
-\textbf{Type of article} Letters
+\textit{Keywords (8/10)} asymptotic maximum height, maximum photosynthetic rate, plant ontogenetic stage, plant functional traits, plant growth strategy, seed mass, specific leaf area, wood density
 
-\textbf{Number of words in the abstract} 148
+\textit{Type of article} Letters
 
-\textbf{Number of words in the main text (excluding abstract, acknowledgements, references, table and figure legends)}
+\textit{Number of words in the abstract} 148
 
-\textbf{Number of words in each text box} 0
+\textit{Number of words in the main text (excluding abstract, acknowledgements, references, table and figure legends)} 4566/5000
 
-\textbf{Number of general references}
+\textit{Number of words in each text box} 0
 
-\textbf{Number of data source references} 108
+\textit{Number of general references} 50
 
-\textbf{the number of figures} 2
+\textit{Number of data source references} 108
 
-\textbf{the number of tables} 0
+\textit{Number of figures} 2
 
-\textbf{the number of text boxes} 0
+\textit{Number of tables} 0
 
-\textbf{the name and complete mailing address (including telephone and fax numbers and e-mail address) of the person to whom correspondence should be sent}
+\textit{Number of text boxes} 0
 
-\todo[inline,color=white]{Tentatively for Ecology Letters [length limits: maximum of 5000 words (main text), 2/6 figures, tables or boxes, and 64/50 references.] (4667 word  /5000)}
+\textit{corresponding author} Anais Gibert, anais.gibert@gmail.com, Dept of Biological Sciences, Macquarie University, Sydney, NSW 2109, Australia, tel: +61 2 9850 8194
 
-\todo[inline,color=white]{1. need to delete references 57/50}
+\todo[inline,color=white]{1. need to delete references 50/50: DONE}
 
@@
 
-\todo[inline,color=white]{3. the bibliography style needs to be changed to fit with the new style of Ecology letters: journal abbreviation}
+\todo[inline,color=white]{3. the bibliography style needs to be changed to fit with the new style of Ecology letters: journal abbreviation: DONE}
 
-\todo[inline, color=white] {4. to re write Appendix A growth equation : do we keep equation? information about plant size?}
+\todo[inline, color=white] {4.  re write Appendix A growth equation : DONE}
 
-\todo[inline, color=white] {5. to write a "Read.me" file for the dataset/guithub}
+\todo[inline, color=white] {5. to write a "Read.me" file for the dataset/guithub: DONE}
 
-\todo[inline, color=white] {6. to add the list of traits/stage categoreis combiation for which we identified a need of more data in the last paragrph of the discussion: DONE}
+\todo[inline, color=white] {6. to add the list of traits/stage categories combination for which we identified a need of more data in the last paragraph of the discussion: DONE}
 
 \todo[inline, color=white] {7. to add subsections in Discussion: DONE}
+
+\todo[inline, color=white] {8.
+list of preferred and non preferred reviewers, to list any editorial board members with whom one of the authors is in conflict: see the list \href{here}{http://onlinelibrary.wiley.com/journal/10.1111/(ISSN)1461-0248/homepage/EditorialBoard.html}}
+
+\todo[inline, color=white] {9. To add asterisk in front of the data-source references and cites them in the text}
+
+\todo[inline, color=white] {10. To delete discussion about references in coverletter: DONE}
+
+\todo[inline, color=white] {11.
+To add a clear statment in cover letter of how exactely the enclosed work is outstandingly novel relative to recent work by the author and co authors cited in the present submission}
+
+\todo[inline, color=white] {12. to check the number of word in figures legends (less than 150): DONE}
 
@@
 Meanwhile partitioning of seedling RGR into its components showed that specific leaf area (SLA = 1/leaf mass per area LMA) was typically the strongest source of variation between species \citep{Poorter:1989tx}.
-From the 1990s a new style of "trait ecology" arose whereby measurable traits including SLA were used directly as strategy axes \citep{Westoby:1998ug,Weiher:1999js, Westoby:2002ft}.
+From the 1990s a new style of "trait ecology" arose whereby measurable traits including SLA were used directly as strategy axes \citep{Westoby:2002ft}.
 An approach via measurable traits made broad comparisons possible across continents and latitudes and thousands of species.
@@
 It has been widely expected that species with low tissue construction cost will typically have fast growth rates at least in favourable physical environments (e.g.
-\citealt{MullerLandau:2004dc,Wright:2004jb,Poorter:2006kw,Poorter:2008iu,Chave:2009iy,Larjavaara:2010bn,Iida:2012jb,Paine:2015df}).
+\citealt{MullerLandau:2004dc,Wright:2004jb,Poorter:2008iu,Chave:2009iy,Larjavaara:2010bn,Iida:2012jb,Paine:2015df}).
 Yet a growing number of empirical studies indicate the correlation between traits and growth is not as consistent as that.
@@
 
-Meanwhile the possibility has been raised that trait-growth correlations may change systematically with size \citep{Iida:2014ep,Iida:2014hq,Ruger:2012jv,Falster:2011ii}.Recent theory suggests that the absence of a correlation between SLA and growth at larger sizes may be expected, when  potential influences of traits on plant function are considered \citep{Falster:2011ii, falster:2013} (Appendix \ref{app:growth}).
+Meanwhile the possibility has been raised that trait-growth correlations may change systematically with size \citep{Iida:2014ep,Iida:2014hq,Ruger:2012jv,Falster:2011ii}.Recent theory suggests that the absence of a correlation between SLA and growth at larger sizes may be expected, when  potential influences of traits on plant function are considered \citep{Falster:2011ii, falster:2013} (see Appendix \ref{app:growth} in Supporting Informations).
 At larger sizes the low-cost deployment benefits of high SLA may be offset or even outweighed by the high costs of rapid leaf turnover.
@@
 
-As plants approach maximum height they increasingly divert energy away from growth and into reproduction (see \citealt{Wenk:2014jz, Falster:2011ii,Thomas:1996do}).
+As plants approach maximum height they increasingly divert energy away from growth and into reproduction (see \citealt{Thomas:1996do, Falster:2011ii, Wenk:2014jz}).
 For seedlings, where all individuals are investing solely in growth, we expect no influence of Hmax on growth.
@@
 First, we identified traits for which a substantial number of studies would be available, using a literature snapshot in Web of Science.
-While Web of Science guarantees a relatively stable and reproducible search environment, with clearly defined lists of indexed journals, its searches are restricted to metadata, such as title, keywords and abstracts \citep{Falagas:2008gtb,Beckmann:2012hn}.
+While Web of Science guarantees a relatively stable and reproducible search environment, with clearly defined lists of indexed journals, its searches are restricted to metadata, such as title, keywords and abstracts \citep{Beckmann:2012hn}.
 This limitation does not apply to Google Scholar, where, theoretically, all text that is electronically available on the Internet will be indexed.
@@
 Where available we also recorded the geographic coordinates, number of sites, experiment type (greenhouse, field experiment, forest, shade-house etc.), growth measure (relative or absolute growth rate measured using plant diameter, height or mass), vegetation type, life form (tree, woody or mixed with herbaceous species etc.), biological scale (interspecific, intraspecific or intragenus), and experimental treatments (e.g.~fertilization, shade, salt stress).
-Ultimately data was included from 108 different studies \citep{Aiba:1997ho, Aiba:2009ft, Antunez:2001gk, Atkin:1998in, augspurger_light_1984, baltzer_physiological_2007, baraloto_differential_2006, baraloto_seed_2005, Bloor:2003fa, Bohlman:2006eo, Broncano:1998ck, Brown:1996ks, Bruhn:2000jz, Cai:2007ie, CamaraZapata:2003df, CastroDiez:1998gz, CastroDiez:2003jd, Cernusak:2008ds, Chao:2008hg, Chaturvedi:2011jx, Chave:2009iy, Cochard:2007bn, Coley:1983hk, Comas:2002wt, Comas:2004jza, coomes_comparison_1998, coomes_greater_2009, cornelissen_seedling_1996, Cornelissen:1997fd, Cornelissen:1998ta, Dalling:2004gs, DeBell:1994ix, Easdale:2009gv, fan_hydraulic_2012, Fayolle:2012bx, Fujimoto:2006fg, Galmes:2005fa, gleeson_plant_1994, grotkopp_toward_2002, Grubb:1996kr, Herault:2011dd, Huante:1995fd, Huante:1995tl, Huante:1998bk, HUNT:1997ge, Iida:2014ep, Iida:2014hq, king_influence_1994, king_tree_2005, King:2006dg, King:2006he, Kitajima:1994ez, Kohyama:2003dk, Kruger:2006fq, Lamers:2006dl, LopezIglesias:2014dk, Loveys:2002hj, Lusk:1997ga, Lusk:2002fma, Lusk:2013bq, Lusk:2013hz, MartinezVilalta:2010iq, McCormack:2012ch, Moya:2008ep, MullerLandau:2004dc, Nascimento:2005kl, Osone:2008dr, Osunkoya:1994ip, Osunkoya:2010ef, Paz:2005kx, Poorter:1999fp, Poorter:2001fj, Poorter:2006vb, Poorter:2008iu, Poorter:2010co, Popma:1988tv, Prior:2004cv, Read:2011du, Reich:1998ir, Reich:1998ja, Reich:1998vb, Rossatto:2009gq, RuizRobleto:2005hc, Sack:2004hm, saldana-acosta_seedling_2009, SalgadoLuarte:2012ci, Saverimuttu:1996ih, Schulze:2006ww, Shen:2014fw, Shipley:2002fs, Stratton:2001ck, Thomas:1996do, Tjoelker:1999gp, Tobner:2013cv, Tomlinson:2014im, Veneklaas:2002dt, Villagra:2013do, walters_are_1996, Walters:1993eu, Walters:1993hf, Warren:2005bc, Westbrook:2011ja, Wright:1999ds, Wright:2000kw, Wright:2001gb, Wright:2003kb, Wright:2010tp, Zhang:1995bh}.
+Ultimately data was included from 108 different studies \citep{Aiba:1997ho, Aiba:2009ft, Antunez:2001gk, Atkin:1998in, augspurger_light_1984, baltzer_physiological_2007, baraloto_differential_2006, baraloto_seed_2005, Bloor:2003fa, Bohlman:2006eo, Broncano:1998ck, Brown:1996ks, Bruhn:2000jz, Cai:2007ie, CamaraZapata:2003df, CastroDiez:1998gz, CastroDiez:2003jd, Cernusak:2008ds, Chao:2008hg, Chaturvedi:2011jx, Chave:2009iy, Cochard:2007bn, Coley:1983hk, Comas:2002wt, Comas:2004jz, coomes_comparison_1998, coomes_greater_2009, cornelissen_seedling_1996, Cornelissen:1997fd, Cornelissen:1998ta, Dalling:2004gs, DeBell:1994ix, Easdale:2009gv, fan_hydraulic_2012, Fayolle:2012bx, Fujimoto:2006fg, Galmes:2005fa, gleeson_plant_1994, grotkopp_toward_2002, Grubb:1996kr, Herault:2011dd, Huante:1995fd, Huante:1995tl, Huante:1998bk, HUNT:1997ge, Iida:2014ep, Iida:2014hq, king_influence_1994, king_tree_2005, King:2006dg, King:2006he, Kitajima:1994ez, Kohyama:2003dk, Kruger:2006fq, Lamers:2006dl, LopezIglesias:2014dk, Loveys:2002hj, Lusk:1997ga, Lusk:2002fma, Lusk:2013bq, Lusk:2013hz, MartinezVilalta:2010iq, McCormack:2012ch, Moya:2008ep, MullerLandau:2004dc, Nascimento:2005kl, Osone:2008dr, Osunkoya:1994ip, Osunkoya:2010ef, Paz:2005kx, Poorter:1999fp, Poorter:2001fj, Poorter:2006vb, Poorter:2008iu, Poorter:2010co, Popma:1988tv, Prior:2004cv, Read:2011du, Reich:1998ir, Reich:1998ja, Reich:1998vb, Rossatto:2009gq, RuizRobleto:2005hc, Sack:2004hm, saldana-acosta_seedling_2009, SalgadoLuarte:2012ci, Saverimuttu:1996ih, Schulze:2006ww, Shen:2014fw, Shipley:2002fs, Stratton:2001ck, Thomas:1996do, Tjoelker:1999gp, Tobner:2013cv, Tomlinson:2014im, Veneklaas:2002dt, Villagra:2013do, walters_are_1996, Walters:1993eu, Walters:1993hf, Warren:2005bc, Westbrook:2011ja, Wright:1999ds, Wright:2000kw, Wright:2001gb, Wright:2003kb, Wright:2010tp, Zhang:1995bh}.
 
@@
 This random effect allows us to account for the heterogeneity among studies (e.g.~experimental type, vegetation type, error, etc.).
-For each trait, we established if stage could explain variance in the coefficient correlation by comparing models with the stage variable to the null model using log-likelihood ratios  \citep{Srivastava:2009we}.
+For each trait, we established if stage could explain variance in the coefficient correlation by comparing models with the stage variable to the null model using log-likelihood ratios \citep{Zuur:2009cfa}.
 If the log-likelihood test returned a significant p-value, the stage model fitted the data better than the null model.
@@
 Estimates of the effect size for each stage were considered significant if the 95\% confidence intervals did not overlap with zero.
-In the case of multiple comparisons within a study, we used the method proposed by \citet{Borenstein:2009um}: we calculated the mean correlation coefficient by trait and by study, and re-calculated the effect size (see \citealt{Pere:2013gr}).
+In the case of multiple comparisons within a study, we used the method proposed by \citet{Borenstein:2009um}: we calculated the mean correlation coefficient by trait and by study, and re-calculated the effect size.
 Finally, we checked the dataset for publication bias with funnel plots (\citealt{Koricheva:2013tz}, Fig.
@@
 
-% * <ian.wright@mq.edu.au> 2015-04-29T07:20:39.057Z:
-%
-% did all these authors really report that GR-SLA relationships diminish in strength with plant size? That is how it reads, but I don't think that's true???
-%
-
-%% Anais:
-% wright et al 2010 "There is a strong negative relationship between LMA and early seedling growth rates; however, direct limitation of growth rates by large LMA decreases in importance as trees mature and leaf number increases (Lambers and Poorter 1992, Reich et al.
-1992, Poorter et al.
-2009).
-
-% Poorter et al 2008: "Specific leaf area may be important for the performance of small plants, as leaf removal has a large impact on their survival (e.g., Pearson et al.
-2003), but less important for the performance of large trees that have substantial reserves to recuperate from photosynthetic biomass loss (Wu ̈ rth et al.
-2005).
-Similarly, SLA may be more important for light interception of saplings for which it determines to a large extent the total leaf area and leaf area ratio, but less so for large trees, for which leaf area and light interception are largely determined by branching patterns, the number of meristems, and tree architecture (Sterck and Bongers 2001)."
-
-% Reich et al (1992): "Leaf mass per area illustrates two of the reasons that trait–demography relationships might be inherently weak at the sapling stage.
-The first is ontogenetic.
-There is a strong negative relationship between LMA and early seedling growth rates; however, direct limitation of growth rates by large LMA decreases in importance as trees mature and leaf number increases (Lambers and Poorter 1992, Reich et al.
-1992, Poorter et al.
-2009)."
-
-%
-
 For seedlings our meta-analyses showed as expected a negative relationship between seed mass and relative growth rate (in mass or height or volume) that disappeared across plant stage.
@@
 Meta-analysis showed a positive correlation between Hmax and growth for adult stage, but not for saplings and juveniles.
-The trend for tall stature species to grow faster at a given tree size than small stature species has been noted across several tree size classes and forest types \citep{Kohyama:2003dk,Poorter:2008iu,MartinezVilalta:2010iq,Wright:2010tp,Herault:2011dd,Ruger:2012jv, Iida:2014ep}.
+The trend for tall stature species to grow faster at a given tree size than small stature species has been noted across several tree size classes and forest types (e.g.
+\citealt{Poorter:2008iu,Wright:2010tp,Herault:2011dd,Ruger:2012jv,Iida:2014ep}).
 In \citet{Wright:2010tp}, Hmax was considered as the weakest predictor of growth rates of saplings; however it was the strongest predictor of growth rates of large trees.
@@
 
-\section*{Acknowledgements}\label{Acknowledgment}
+\section*{Acknowledgments}\label{Acknowledgment}
 
@@
 \caption{\textbf{Number of correlations between trait and growth for each plant stage recorded in our dataset.} Shown here are 'complete dataset' (recorded at both interspecific and intraspecific level, under unstressed and stressed conditions).
-Bar colors: red for adult stage, orange for sapling, grey for juvenile.
+Bar colors: red for adult, orange for sapling, grey for juvenile.
 Aarea (or Amass) = rate of $CO_{2}$ assimilation per unit leaf area (or leaf mass) = maximum photosynthetic rate, Hmax= asymptotic maximum height,  Ks =stem hydraulic conductance, LA = leaf area, LMR = leaf mass ratio, NARarea (or NARmass) = net mass assimilation rate per unit of leaf area (or leaf mass), Nmass (or Narea) = nitrogen content per unit of leaf mass (or leaf area), Pmass = phosphorus content per unit of leaf mass, SA/LA = sapwood area per leaf area, SLA = specific leaf area, thickness = leaf thickness, Vessel size = stem conduit size, vessel density = stem conduit density, WD = wood density}
@@
 \textbf{a)} Specific leaf area (SLA), \textbf{b)} Wood density (WD), \textbf{c)} Asymptotic height (Hmax) \textbf{d)} Seed mass and \textbf{e)} Assimilation rate of CO2 (Aarea).
-Effect size is a standardized measure of the deviation of the correlation coefficient from zero (Fisher's z-transformed).
-Effects are significant if confidence intervals (+ 95\%CI) for a given stage do not overlap with zero.
-Black symbols for "ideal" data (using only interspecific correlations, growth under control conditions), grey symbols using "complete" data (see Methods for further explanation).
+Effect size is a standardized measure of the deviation of correlation coefficient from zero (Fisher's z-transformed).
+Effects are significant if confidence intervals (95\%CI) for a given stage do not overlap with zero.
+Black point: ideal data (at interspecific level \& under unstressed conditions), grey points: all the data.
 'n' indicates number of correlations contributing to each effect.
 Likelihood Ratio Tests (LRT, for ideal data only) compared maximum-likelihood fits between a pooled model and one separated by stage.
-If the LRT returned a significant p-value, the stage model fitted the data better than the null model.
+A significant p-value means the stage model fitted the data better than the null model.
 }
@@
 
-We adapted growth equations from \cite{Falster:2011ii} and \cite{falster:2013} to generate hypotheses on both absolute and relative growth rates in biomass (b, eqn \ref{eq:eq1}), height (H, eqn \ref{eq:eq2}) and diameter (D, eqn \ref{eq:eq4}).
-These size dimensions are measured on seedling and adult plants.
+We adapted growth equations from \cite{Falster:2011ii} and \cite{falster:2013} to generate hypotheses on both absolute and relative growth rates in biomass ($m_t$, eqn \ref{eq:eq1}), height (H, eqn \ref{eq:eq2}) and diameter (D, eqn \ref{eq:eq4}).
+These size dimensions are routinely measured on seedling and adult plants.
 Here we provide a brief overview of the model; an upcoming publication will elaborate further on the predicted relationships between traits and growth rate.
 
-Let $m_i$ denote the mass, $r_i$ the mass-specific respiration rate, and $k_i$ the turnover rate of different plant tissues, with the subscripts $i=l,s,r,t$ referring to leaves, sapwood and bark, roots, and total plant.
-Similarly let $a_i$ denote areas, of leaves ($i=l$) and of cross-sections of total stem, sapwood and heartwood ($i= st,ss,sh$) respectively.
+Let $m_i$ denote the mass, $r_i$ the mass-specific respiration rate, and $k_i$ the turnover rate of different plant tissues, with the subscripts $i=l,s,r,t$ referring to live biomass in leaves, sapwood and bark, roots, and in the plant.
+Similarly let $a_i$ denote areas, of leaves ($i=l$) and of cross-sections of total stem and sapwood ($i= st,ss$) respectively.
 
-The rate at which biomass $b$ of the plant increases is given by
-%MW: phrasing changed here and a bit under the equations because I would say that "biomass originating from the plant" should be regarded as including turnover
+The rate at which live biomass originating from the plant $b$ changes is given by
+\begin{equation}\label{eq:eq0}
+\underbrace{\frac{db}{dt}}_{\text{net live biomass production}} = \underbrace{y}_{\text{yield}}  \big(\underbrace{a_{l} A_{\textrm{area}}}_{\text{photosynthesis}} - \underbrace{\sum_{i=l,s,r} m_{i} r_{i}}_{\text{respiration}}\big) - \underbrace{ \sum_{i=l,s,r} m_{i} k_{i}}_{\text{turnover}},
+\end{equation}
+where $y$ is the fraction of assimilated carbon fixed into biomass,  and  $A_{\textrm{area}}$ is the assimilation rate of CO$_{2}$ per leaf area.
+The rate at which live biomass is accumulated on the plant is then
+
 \begin{equation}\label{eq:eq1}
-\underbrace{\frac{db}{dt}}_{\text{biomass increase rate}} = \underbrace{y}_{\text{yield}}  \big(\underbrace{a_{l} A_{\textrm{area}}}_{\text{photosynthesis}} - \underbrace{\sum_{i=l,s,r} m_{i} r_{i}}_{\text{respiration}}\big) - \underbrace{ \sum_{i=l,s,r} m_{i} k_{i}}_{\text{turnover}},
+\underbrace{\frac{dm_t}{dt}}_{\text{growth in live biomass}} = \underbrace{\frac{dm_t}{db}}_{\text{allocation to growth}}  \times \underbrace{\frac{db}{dt}}_{\text{net live biomass production}},
 \end{equation}
-where $y$ is the fraction of assimilated carbon fixed into biomass,  and  $A_{\textrm{area}}$ is the assimilation rate of CO$_{2}$ per leaf area. Height growth rate can then be expressed as
+where allocation to growth is the fraction of biomass increase that goes to vegetative growth rather than to seed production. Height growth rate can then be expressed as
 \begin{equation}\label{eq:eq2}
-\underbrace{\frac{dH}{dt}}_{\text{growth rate in height}} = \underbrace{\frac{dH}{da_{l}}}_{\text{architecture layout}} \times \underbrace{\frac{da_{l}}{dm_{t}}}_{\text{leaf deployment per mass}} \times \underbrace{\frac{dm_t}{db}}_{\text{allocation to growth}}  \times \underbrace{\frac{db}{dt}}_{\text{biomass increase rate}}.
+\underbrace{\frac{dH}{dt}}_{\text{growth rate in height}} = \underbrace{\frac{dH}{da_{l}}}_{\text{architecture layout}} \times \underbrace{\frac{da_{l}}{dm_{t}}}_{\text{leaf deployment per mass}} \times \frac{dm_t}{db} \times \frac{db}{dt}.
 \end{equation}
-
-where allocation to growth is the fraction of biomass increase that goes to vegetative growth rather than to seed production. Similarly basal area growth can be expressed as
+Similarly basal area growth can be expressed as
 \begin{equation}\label{eq:eq3}
@@
 
-For the case of seedlings, eqn \ref{eq:eq1} can be simplified considerably.
-Turnover of tissues has not yet begun.
-It is common also to ignore respiration of non-leaf tissues and to let leaf respiration rate be proportional to leaf area.
+For the case of seedlings, eqs.
+\ref{eq:eq0}-\ref{eq:eq1} can be simplified considerably.
+Turnover of tissues and allocation to reproduction have not yet begun.
+It is also common also to assume all respiration rates are proportional to leaf area.
 Biomass growth rate then becomes a linear function of leaf area:
-%MW: I wonder whether it might be better to think of this as letting total respiration (including roots) be proportional to leaf area?
 \begin{equation}\label{eq:eq1_seedlings}
-\frac{db}{dt}  \approx  a_{l} \, y \, (A_{\textrm{area}} - r_{l}).
+\frac{dm_t}{dt}  \approx  a_{l} \, y \, (A_{\textrm{area}} - r_{l}).
 \end{equation}
-A relative growth rate (RGR) in mass can be obtained by dividing both sides of this simplified eq \ref{eq:eq1_seedlings} by the total mass of living tissues $m_{t} = m_{l} + m_{s} + m_{r}$.
+A relative growth rate in mass $(\textrm{RGR}_{\textrm{mass}})$ can be obtained by dividing both sides of this simplified eq \ref{eq:eq1_seedlings} by the total mass of living tissues $m_{t}$.
 The outcome is equivalent to the classical partitioning of RGR \citep{Lambers:1992bj, Cornelissen:1998ta}:
 \begin{equation}\label{eq:eq1_seedlings_RGR}
-\textrm{RGR}  \approx \textrm{NAR} \times  \textrm{SLA} \times  \textrm{LMF},
+\textrm{RGR}_{\textrm{mass}}  \approx \textrm{NAR} \times  \textrm{SLA} \times  \textrm{LMF},
 \end{equation}
- where NAR is net assimilation rate ($y \, (A_{\textrm{area}} - r_{l})$), SLA = $a_{l}/ m_{l}$ and LMF is leaf mass fraction ($m_{l}/ m_{t}$).
+ where net assimilation rate NAR=$y \, (A_{\textrm{area}} - r)$, SLA = $a_{l}/ m_{l}$ and leaf mass fraction LMF = $m_{l}/ m_{t}$.
 
-The predicted effects of different traits on growth can then be understood by considering the influence of trait variation on elements of equations  \ref{eq:eq1}-\ref{eq:eq4} and how these may interact with plant size.
+The predicted effects of different traits on growth can then be understood by considering the influence of trait variation on elements of equations  \ref{eq:eq0}-\ref{eq:eq4} (Table \ref{tab:trade-offs}) and how these may interact with plant size.
 
@@
 \centering
-\caption{\textbf{ Hypothesised effect of traits on components of growth.
-Arrows indicate the effect an increase in trait value would have on elements of growth (as described  in Eqs.
-\ref{eq:eq1}-\ref{eq:eq4}) and other aspects of life history.}}
-  \begin{tabular}[c]{l|c|cccc|c|c}
-  \multicolumn{8}{c}{}\\ \hline
-  & \multicolumn{7}{c}{\textbf{Effect of trait on}}\\
-  & \textbf{Birth} & \multicolumn{4}{c|}{\textbf{Growth}} & \textbf{Survival} & \textbf{Fecundity} \\
-  & \textbf{size}
+\caption{\textbf{ Hypothesised effect of traits on components of growth.} Arrows indicate the effect an increase in trait value would have on the elements of eqs. \ref{eq:eq0}-\ref{eq:eq4}.}
+  \begin{tabular}[c]{lcccc}
   & $\frac{\textrm{d}a_\textrm{l}}{\textrm{d}m_\textrm{t}}$
@@
   & $\frac{\textrm{d}b}{\textrm{d}t}$
-  & $k_s$ & &  \\\hline
-  Seed size & $\uparrow$ & & & & & & $\downarrow$ \\
-  Aarea & & & & $\uparrow$& &  \\
-Leaf mass per area & & $\downarrow$ & & $\uparrow$ & &  \\
-  Wood density& & $\downarrow$ &  & & & $\uparrow$  \\
-  Maximum height & & &$\uparrow$ & & & & $\downarrow$  \\
+  & $k_s$ \\\hline
+  Seed size & & & & \\ 
+  Aarea & & & $\uparrow$ & \\
+  SLA &$\uparrow$ & & $\downarrow$& \\
+  Wood density & $\downarrow$ &  & & \\
+  Maximum height & &$\uparrow$ & & \\
 \hline
-%MW I'm struggling to understand why db/dt should be one of the terms listed under "growth" -- surely it just is growth, not one of the contributing terms in a growth eqn?
-%MW I think this probably should be done in terms of SLA rather than LMA -- that's the way most of the rest of the paper is done from memory, and especially the immediate next para
-%MW does SLA not affect leaf turnover rates?
-(also the text does actually slightly refer to WD affecting sapwood turnover, but this is complicated and I can appreciate it may be better to evade this issue here)
-%MW the up-and-down for Aarea seems too complicated (see comment below) -- have replaced with a simple up
-%MW I'm inclined to think the columns for birth size, survival and fecundity don't help here -- I understand the logic, but mostly we don't discuss or explain them and so they're distracting
   \end{tabular}
@@
 For larger plants (eq.
-\ref{eq:eq1}-\ref{eq:eq4}), SLA is expected to affect growth rate positively through more cost-efficient deployment of leaf area (via $da_l/dm_t$); the same effect as in seedlings), but also negatively via increased leaf turnover (eqn 1; Table \ref{tab:trade-offs}).
+\ref{eq:eq1}-\ref{eq:eq4}), SLA is expected to affect growth rate positively through more cost-efficient deployment of leaf area (via $da_l/dm_t$; the same effect as in seedlings), but also negatively via increased leaf turnover (eqn 1; Table \ref{tab:trade-offs}).
 The effect of SLA on $da_l/dm_t$ decreases as plant size increases and increasing amounts of the plant are wood.
 Consequently the effect of turnover costs in slowing growth comes to dominate at larger sizes.
-%MW: I suggest we should not use phrases like "regardless of the growth measurement used" except in cases where we're actually going to explain properly.
-Currently eqns 1-5 are expressed as absolute growth rate and eqn 6 as RGR.
-But nowhere do we make explicit comparisons of an absolute growth eqn with a relative growth eqn
+
 Second, the relationship between WD and growth rate is predicted to be negative across all plant sizes.
-Cheaper stem construction (low WD or stem density) also increases the marginal rate of leaf deployment per total mass increment (via $da_l/dm_t$), and consequently increases growth rate in leaf area, height and diameter (eqs.
+Cheaper stem construction (low WD or stem density) also increases the marginal rate of leaf deployment per total mass increment ($da_l/dm_t$), and consequently increases growth rate in leaf area, height and diameter (eqs.
 \ref{eq:eq2}-\ref{eq:eq4}).
@@
 Third, the relationship between height at maturation (Hmax) and growth rate is predicted to be positive in adults, whereas no correlation is expected for seedlings and juveniles.
-Hmax affects growth via the fraction of energy allocated to vegetative growth versus to seed production  (dmt/db in eqn 2; Table \ref{tab:trade-offs}).
+Hmax affects growth via the fraction of energy allocated to vegetative growth versus to seed production  ($dm_t/db$ in eq.
+\ref{eq:eq1}; Table \ref{tab:trade-offs}).
 For juveniles and seedlings this fraction is 1 for all species and so no effect is expected.
@@
 
-Fourth, the relationship between seed mass and relative growth rate is predicted to be negative in seedlings.
+Fourth, the relationship between seed mass and $\textrm{RGR}_{\textrm{mass}}$ is predicted to be negative in seedlings.
 This is because the relative growth rate slows as plants grow larger, and large-seeded species begin larger as seedlings.
 For larger plants, seed mass is not expected to have any distinct influence on growth rates  (Table \ref{tab:trade-offs}).
-%MW: in my opinion the -ve correlation expectation applies only to RGR not to absolute growth rate
+
 Finally, the relationship between Aarea and growth should be positive across all plant sizes (eqn 1).
-The effects of benefits (higher assimilation) and costs (higher respiration) of increased Area occur within the same element of equations 1 and 5, and assimilation must outweigh respiration for there to be growth, so the net effect will be positive (Table \ref{tab:trade-offs}).
-%MW is that what the up-and-down arrows in the table are meant to convey?
-Too complicated I suggest -- and also it doesn't actually explain why r'ship is positive, though it does explain why it's consistent across sizes.
-Have suggested a rewrite.
+The effects of benefits (higher assimilation) and costs (higher respiration) of increased Area occur within the same element of eq.
+\ref{eq:eq0}, and assimilation must outweigh respiration for there to be growth, so the net effect will be positive (Table \ref{tab:trade-offs}).
 
 \newpage
+
+\renewcommand{\thefigure}{S\arabic{figure}}
+\renewcommand{\thetable}{S\arabic{table}}
+
+\setcounter{figure}{0}
+\setcounter{table}{0}
 
@@
 
+\linespread{1}
+
 \begin{table}[ht]
 \centering
-\caption{\textbf{List of the twenty traits targeted}. Abbreviation,
+\caption{\linespread{2}\textbf{List of the twenty traits targeted}. Abbreviation,
 definition and search term used in the meta-analysis} 
@@
 \caption{\textbf{Mean coefficient correlation r (+SD) between growth
-rate and traits, established from 107 published articles.} The mean
+rate and traits, established from 108 articles.} The mean
 coefficents are weighted by sample size (i.e number of species used to
@@
 LRT: likelihood Ratio Test compared the fit between null model and stage model, both models are fitted by Maximum Likelihood.
-Black point: ideal data (at interspecific level \& under control conditions), grey points: all the data.
+Black point: ideal data (at interspecific level \& under unstressed conditions), grey points: all the data.
 `n' indicate the number of independent comparisons for each effect.}
@@
 \includegraphics{output/FigA7d.pdf}
-\caption{\textbf{Effects size on the correlation between growth and
-traits of plant stage (mod1, as recorded by the authors), vegetation type
-(mod2), growth measurement (mod3) and experiment type (mod4).} The effect size
-(z) is reported for each class, with its 95\%CI and models are fitted by
-restricted max likelihood (REML). n= number of correlation r reported.
-(Abbreviation: boreal\&temp = mix boreal and temperate deciduous forest,
-med= Mediterranean, across veg = correlation performed on species from
-more than 2 vegetation types, temp\&med = mix between temperate
-deciduous and Mediterranean forest, temp= temperate deciduous forest,
-temp rain= temperate rain forest, trop rain= tropical rain forest, trop
-seas = tropical seasonal forest, GR(D)= growth rate measure in diameter,
-GR(H) = growth rate in height, GR(M)= growth rate in Mass, RGR(CSA)=
-relative growth rate in cross section area, etc). AIC: Akaike
-information criterion corresponds to the quality of each model, and
-allow a comparison between model. Smallest is the AIC better is the
-model. Shown here are complete dataset (recorded at both interspecific and intraspecific level and under unstressed and stressed conditions).}
+\caption{\textbf{Effects size on the correlation between growth and traits of plant stage (mod1, as recorded by the authors), vegetation type (mod2), growth measurement (mod3) and experiment type (mod4).} The effect size (z + 95\%CI) is reported for each class, and models are fitted by restricted max likelihood (REML).
+n= number of correlation r reported.
+Abbreviation: across veg= more than 2 vegetation types, boreal\&temp= boreal and temperate deciduous forest, med= Mediterranean,  temp\&med = temperate deciduous and Mediterranean forests, temp= temperate deciduous, temp rain= temperate rain, trop rain= tropical rain, trop seas= tropical seasonal forests, GR= growth rate and RGR= relative growth rate, measured in diameter (D), height (H), mass(M), cross section area (CSA).
+AIC: Akaike information criterion corresponds to the quality of each model, and allow a comparison between models.
+Smallest is the AIC better is the model.
+Shown here are complete dataset (recorded at both interspecific and intraspecific level and under unstressed and stressed conditions).}
 \label{FigA7}
@@
 \includegraphics{output/FigA8.pdf}
-\caption{\textbf{Funnel plots showing transformed correlation coefficient z between growth and the traits a) Specific leaf area
-(SLA), b) Wood density (WD), c) Asymptotic height (Hmax), d) Seed mass and e) Assimilation rate of CO2 (Aarea)}.
+\caption{\textbf{Funnel plots showing transformed correlation coefficient z between growth and the traits a) Specific leaf area (SLA), b) Wood density (WD), c) Asymptotic height (Hmax), d) Seed mass and e) Assimilation rate of CO2 (Aarea)}.
 Shown here are complete dataset (recorded at both interspecific and intraspecific level and under unstressed and stressed conditions).
-The color of the points corresponds to the stage for which the correlation was measured (Red points : adult, orange point : sapling, grey: juvenile).
+Point colors: red for adult, orange for sapling, grey for juvenile.
 Note that in these plots the x axis is the number of species included in the correlation, not the replication for the correlation.
 The number of species is sometimes as low as 1, and these are within-species correlations.
-The number of replicates used for the correlation coefficient was often much greater than the number of species, especially for studies involving 5 or less species.
-Nevertheless  the characteristic shape of funnel plots is observed, with correlations involving few species showing much wider variation even though within-species replication was sometimes high.}
+The number of replicates used for the correlation coefficient was often much greater than the number of species.
+Nevertheless, the characteristic shape of funnel plots is observed, with correlations involving few species showing much wider variation even though within-species replication was sometimes high.}
 

### 2015-05-07 MS.tex
build combined reference list

@@
 Where available we also recorded the geographic coordinates, number of sites, experiment type (greenhouse, field experiment, forest, shade-house etc.), growth measure (relative or absolute growth rate measured using plant diameter, height or mass), vegetation type, life form (tree, woody or mixed with herbaceous species etc.), biological scale (interspecific, intraspecific or intragenus), and experimental treatments (e.g.~fertilization, shade, salt stress).
-Ultimately data was included from 108 different studies \citep{Aiba:1997ho, Aiba:2009ft, Antunez:2001gk, Atkin:1998in, augspurger_light_1984, baltzer_physiological_2007, baraloto_differential_2006, baraloto_seed_2005, Bloor:2003fa, Bohlman:2006eo, Broncano:1998ck, Brown:1996ks, Bruhn:2000jz, Cai:2007ie, CamaraZapata:2003df, CastroDiez:1998gz, CastroDiez:2003jd, Cernusak:2008ds, Chao:2008hg, Chaturvedi:2011jx, Chave:2009iy, Cochard:2007bn, Coley:1983hk, Comas:2002wt, Comas:2004jz, coomes_comparison_1998, coomes_greater_2009, cornelissen_seedling_1996, Cornelissen:1997fd, Cornelissen:1998ta, Dalling:2004gs, DeBell:1994ix, Easdale:2009gv, fan_hydraulic_2012, Fayolle:2012bx, Fujimoto:2006fg, Galmes:2005fa, gleeson_plant_1994, grotkopp_toward_2002, Grubb:1996kr, Herault:2011dd, Huante:1995fd, Huante:1995tl, Huante:1998bk, HUNT:1997ge, Iida:2014ep, Iida:2014hq, king_influence_1994, king_tree_2005, King:2006dg, King:2006he, Kitajima:1994ez, Kohyama:2003dk, Kruger:2006fq, Lamers:2006dl, LopezIglesias:2014dk, Loveys:2002hj, Lusk:1997ga, Lusk:2002fma, Lusk:2013bq, Lusk:2013hz, MartinezVilalta:2010iq, McCormack:2012ch, Moya:2008ep, MullerLandau:2004dc, Nascimento:2005kl, Osone:2008dr, Osunkoya:1994ip, Osunkoya:2010ef, Paz:2005kx, Poorter:1999fp, Poorter:2001fj, Poorter:2006vb, Poorter:2008iu, Poorter:2010co, Popma:1988tv, Prior:2004cv, Read:2011du, Reich:1998ir, Reich:1998ja, Reich:1998vb, Rossatto:2009gq, RuizRobleto:2005hc, Sack:2004hm, saldana-acosta_seedling_2009, SalgadoLuarte:2012ci, Saverimuttu:1996ih, Schulze:2006ww, Shen:2014fw, Shipley:2002fs, Stratton:2001ck, Thomas:1996do, Tjoelker:1999gp, Tobner:2013cv, Tomlinson:2014im, Veneklaas:2002dt, Villagra:2013do, walters_are_1996, Walters:1993eu, Walters:1993hf, Warren:2005bc, Westbrook:2011ja, Wright:1999ds, Wright:2000kw, Wright:2001gb, Wright:2003kb, Wright:2010tp, Zhang:1995bh}.
+Ultimately data was included from 108 different studies (starred references in bibliography).
 
@@
 
-\bibliography{references/complete}\label{references}
+\nocite{*}
+\bibliography{output/refs}\label{references}
 

### 2015-05-07 MS.tex
Add asterix to example references
MS change

--- 2015-05-06 MS.tex
@@
 
+This study is the first one of an upcoming series performed by the authors on the same thematic: the insertion of plant size in functional ecology.
+Daniel Falster will develop more deeply a growth model and tested hypotheses using expended dataset on growth and traits in one site.
+Emma Gray and Ian Wright are working on this thematic across all plant growth forms (tree, grass and shrub), and different environements.
+
 We are excited by this work and look forward to your evaluation of the paper.
@@
 \title{Plant species traits and growth rates: meta-analysis shows correlations change with plant size as predicted}
+
+shows predictable changes with plant size of the correlations
 
@@
 
-\todo[inline,color=white]{1. need to delete references 50/50: DONE}
-
-\todo[inline,color=white]{2. need to reduce nb words abstract 148/150: DONE}
-
-\todo[inline,color=white]{3. the bibliography style needs to be changed to fit with the new style of Ecology letters: journal abbreviation: DONE}
-
-\todo[inline, color=white] {4.  re write Appendix A growth equation : DONE}
-
-\todo[inline, color=white] {5. to write a "Read.me" file for the dataset/guithub: DONE}
-
-\todo[inline, color=white] {6. to add the list of traits/stage categories combination for which we identified a need of more data in the last paragraph of the discussion: DONE}
-
-\todo[inline, color=white] {7. to add subsections in Discussion: DONE}
-
 \todo[inline, color=white] {8.
@@
 
-\todo[inline, color=white] {10. To delete discussion about references in coverletter: DONE}
-
 \todo[inline, color=white] {11.
 To add a clear statment in cover letter of how exactely the enclosed work is outstandingly novel relative to recent work by the author and co authors cited in the present submission}
-
-\todo[inline, color=white] {12. to check the number of word in figures legends (less than 150): DONE}
 
@@
 For instance, the correlation between growth and WD at juvenile stage shifted from negative to non significant (i.e CI95\% included zero) due to 2 positive correlation coefficients from \citet{Augspurger:1984ct};  these correlations unlike others used wood density values from adult plants together with growth from juveniles.
-For Aarea, the comparison between complete and ideal data showed no signal of an effect of low light on the correlation with growth at seedling stage; the correlation was still positive between Aarea and growth even with 7 additional correlations measured under low light conditions.
+For Aarea, the comparison between complete and ideal data showed no signal of an effect of stress (here mainly low light) on the correlation with growth at seedling stage; the correlation was still positive between Aarea and growth even when 7 correlations measured under low light conditions were added.
 
@@
 In the growth model (Appendix \ref{app:growth}), a consistent correlation irrespective of size arises from a direct effect of Aarea on plant growth rate.
-We noted no signal of an effect of low light on the positive correlation between Aarea and growth rate in juvenile plants.
+In juvenile stage, where most of the data were, we noted no signal of an effect of low light on the positive correlation between Aarea and growth rate.
 
@@
 
-\begin{appendices} \label{sec:appendices}
+\begin{Appendix} \label{sec:textbox}
 
@@
 These size dimensions are routinely measured on seedling and adult plants.
-Here we provide a brief overview of the model; an upcoming publication will elaborate further on the predicted relationships between traits and growth rate.
 
@@
 \newpage
-
+\begin{Supplemnetary material}\label{sec:appendices}
 \renewcommand{\thefigure}{S\arabic{figure}}
@@
 \centering
-\includegraphics{output/FigA7e.pdf}
-\end{figure}
-
-\begin{figure}[htbp]
-\centering
 \includegraphics{output/FigA7c.pdf}
@@
 \includegraphics{output/FigA7d.pdf}
+\end{figure}
+
+\begin{figure}[htbp]
+\centering
+\includegraphics{output/FigA7e.pdf}
 \caption{\textbf{Effects size on the correlation between growth and traits of plant stage (mod1, as recorded by the authors), vegetation type (mod2), growth measurement (mod3) and experiment type (mod4).} The effect size (z + 95\%CI) is reported for each class, and models are fitted by restricted max likelihood (REML).

### 2015-05-07 MS.tex

@@
 \setcitestyle{authoryear,open={(},close={)}}
+
+\newcommand{\bibstar}{* }
 

### 2015-05-07 MS.tex
MS change statment of novelty of the study compared o other work by the authors Text box

@@
 
-This study is the first one of an upcoming series performed by the authors on the same thematic: the insertion of plant size in functional ecology.
-Daniel Falster will develop more deeply a growth model and tested hypotheses using expended dataset on growth and traits in one site.
-Emma Gray and Ian Wright are working on this thematic across all plant growth forms (tree, grass and shrub), and different environements.
+This study is the first one of an upcoming series of theoritical articles and empirical studies performed by the authors on the same thematic: the effect of plant size on plant strategies and functional traits.
 
@@
 
-\textbf{Running title (36/45 characters)} Trait influence on growth along plant size
-
-\textit{Statement of authorship} MW, DF, IW, AG designed the study, IW and DF provided their bibliography database, AG and EG searched and collected the data, AG performed the meta-analyses, DF performed modeling work, AG wrote the first draft, MW improved substantially the manuscript, and all authors contributed to revisions.
+\textit{Running title (36/45 characters)} Trait influence on growth along plant size
 
@@
 
-\textit{Number of words in the main text (excluding abstract, acknowledgements, references, table and figure legends)} 4566/5000
+\textit{Number of words in the main text} 4583
 
-\textit{Number of words in each text box} 0
+\textit{Number of words in each text box} 750
 
@@
 
-\textit{Number of tables} 0
+\textit{Number of tables} 1
 
-\textit{Number of text boxes} 0
+\textit{Number of text boxes} 1
 
@@
 
-\todo[inline, color=white] {8.
-list of preferred and non preferred reviewers, to list any editorial board members with whom one of the authors is in conflict: see the list \href{here}{http://onlinelibrary.wiley.com/journal/10.1111/(ISSN)1461-0248/homepage/EditorialBoard.html}}
-
-\todo[inline, color=white] {9. To add asterisk in front of the data-source references and cites them in the text}
-
-\todo[inline, color=white] {11.
-To add a clear statment in cover letter of how exactely the enclosed work is outstandingly novel relative to recent work by the author and co authors cited in the present submission}
+\textit{Statement of authorship} MW, DF, IW, AG designed the study, IW and DF provided their bibliography database, AG and EG searched and collected the data, AG performed the meta-analyses, DF performed modeling work, AG wrote the first draft, MW improved substantially the manuscript, and all authors contributed to revisions.
 
@@
 
-Meanwhile the possibility has been raised that trait-growth correlations may change systematically with size \citep{Iida:2014ep,Iida:2014hq,Ruger:2012jv,Falster:2011ii}.Recent theory suggests that the absence of a correlation between SLA and growth at larger sizes may be expected, when  potential influences of traits on plant function are considered \citep{Falster:2011ii, falster:2013} (see Appendix \ref{app:growth} in Supporting Informations).
+Meanwhile the possibility has been raised that trait-growth correlations may change systematically with size \citep{Iida:2014ep,Iida:2014hq,Ruger:2012jv,Falster:2011ii}.Recent theory suggests that the absence of a correlation between SLA and growth at larger sizes may be expected, when  potential influences of traits on plant function are considered \citep{Falster:2011ii, falster:2013} (see Text Box 1 \ref{app:growth} in Supporting Informations).
 At larger sizes the low-cost deployment benefits of high SLA may be offset or even outweighed by the high costs of rapid leaf turnover.
@@
   \item Do the observed relationships conform to predictions (outlined below) from a recently developed  mechanistic
-model \citep{Falster:2011ii, falster:2013}(Appendix \ref{app:growth})?
+model \citep{Falster:2011ii, falster:2013}(Text Box 1 \ref{app:growth})?
 \end{enumerate}
@@
 Recent theoretical work \citep{Falster:2011ii} allows hypotheses to be formulated about relationships between traits and growth.
-Below we provide a verbal description for each of the hypotheses; for a mathematical description see Appendix \ref{app:growth}.
+Below we provide a verbal description for each of the hypotheses; for a mathematical description see Text Box 1 \ref{app:growth}.
 
@@
 It should be noted however that there are few tests of this proposition at seedling stage.
-In our model (Appendix \ref{app:growth}) cheaper stem construction is responsible for the predicted negative correlation.
+In our model (Text Box 1 \ref{app:growth}) cheaper stem construction is responsible for the predicted negative correlation.
 Lower xylem conductance and associated lower photosynthetic potential have also been suggested \citep[reviewed by][]{Chave:2009iy}.
@@
 For the correlation between Aarea and growth, to our knowledge no study has previously assessed this in relation to plant size.
-In the growth model (Appendix \ref{app:growth}), a consistent correlation irrespective of size arises from a direct effect of Aarea on plant growth rate.
+In the growth model (Text Box 1 \ref{app:growth}), a consistent correlation irrespective of size arises from a direct effect of Aarea on plant growth rate.
 In juvenile stage, where most of the data were, we noted no signal of an effect of low light on the positive correlation between Aarea and growth rate.
@@
 
-\section*{Acknowledgments}\label{Acknowledgment}
+\section*{Acknowledgements}\label{Acknowledgment}
 
@@
 \newpage
+\section*{Table} \label{sec:table}
 
-\begin{Appendix} \label{sec:textbox}
+\begin{table}[ht]
+\centering
+\caption{\textbf{ Hypothesised effect of traits on components of growth.} Arrows indicate the effect an increase in trait value would have on the elements of eqs. \ref{eq:eq0}-\ref{eq:eq4}.}
+  \begin{tabular}[c]{lcccc}
+  & $\frac{\textrm{d}a_\textrm{l}}{\textrm{d}m_\textrm{t}}$
+  & $\frac{\textrm{d}m_\textrm{t}}{\textrm{d}b}$
+  & $\frac{\textrm{d}b}{\textrm{d}t}$
+  & $k_s$ \\\hline
+  Seed size & & & & \\ 
+  Aarea & & & $\uparrow$ & \\
+  SLA &$\uparrow$ & & $\downarrow$& \\
+  Wood density & $\downarrow$ &  & & \\
+  Maximum height & &$\uparrow$ & & \\
+\hline
+  \end{tabular}
+\label{tab:trade-offs}
+\end{table}
 
-\renewcommand{\thefigure}{A\arabic{figure}}
-\renewcommand{\thetable}{A\arabic{table}}
+\newpage
+\section*{Text Box} \label{app:growth}
 
-\setcounter{figure}{0}
-\setcounter{table}{0}
-
-\section{Derivation of hypotheses from growth equations}\label{app:growth}
+\subsection*{Derivation of hypotheses from growth equations}
 
@@
 
-For the case of seedlings, eqs.
-\ref{eq:eq0}-\ref{eq:eq1} can be simplified considerably.
-Turnover of tissues and allocation to reproduction have not yet begun.
-It is also common also to assume all respiration rates are proportional to leaf area.
-Biomass growth rate then becomes a linear function of leaf area:
+For the case of seedlings, eqs. \ref{eq:eq0}-\ref{eq:eq1} can be simplified considerably. Turnover of tissues and allocation to reproduction have not yet begun.
+
+% AG: you mean turnover of other tissue than leaf?%
+
+It is also common also to assume all respiration rates are proportional to leaf area. Biomass growth rate then becomes a linear function of leaf area:
 \begin{equation}\label{eq:eq1_seedlings}
@@
 
-\begin{table}[ht]
-\centering
-\caption{\textbf{ Hypothesised effect of traits on components of growth.} Arrows indicate the effect an increase in trait value would have on the elements of eqs. \ref{eq:eq0}-\ref{eq:eq4}.}
-  \begin{tabular}[c]{lcccc}
-  & $\frac{\textrm{d}a_\textrm{l}}{\textrm{d}m_\textrm{t}}$
-  & $\frac{\textrm{d}m_\textrm{t}}{\textrm{d}b}$
-  & $\frac{\textrm{d}b}{\textrm{d}t}$
-  & $k_s$ \\\hline
-  Seed size & & & & \\
-  Aarea & & & $\uparrow$ & \\
-  SLA &$\uparrow$ & & $\downarrow$& \\
-  Wood density & $\downarrow$ &  & & \\
-  Maximum height & &$\uparrow$ & & \\
-\hline
-  \end{tabular}
-\label{tab:trade-offs}
-\end{table}
-
-First, the relationship between SLA and growth rate is predicted to shift from positive for seedlings to non-significant or negative in adult plants, regardless of the growth measurement used.
-For seedlings (eq.
+\textbf{SLA:} For seedlings (eq.
 \ref{eq:eq1_seedlings_RGR}) cheaper leaf construction (high SLA) should translate directly into faster relative growth rate in mass.
@@
 
-Second, the relationship between WD and growth rate is predicted to be negative across all plant sizes.
-Cheaper stem construction (low WD or stem density) also increases the marginal rate of leaf deployment per total mass increment ($da_l/dm_t$), and consequently increases growth rate in leaf area, height and diameter (eqs.
+\textbf{WD:} Cheaper stem construction (low WD or stem density) increases the marginal rate of leaf deployment per total mass increment ($da_l/dm_t$), and consequently increases growth rate in leaf area, height and diameter (eqs.
 \ref{eq:eq2}-\ref{eq:eq4}).
@@
 
-Third, the relationship between height at maturation (Hmax) and growth rate is predicted to be positive in adults, whereas no correlation is expected for seedlings and juveniles.
-Hmax affects growth via the fraction of energy allocated to vegetative growth versus to seed production  ($dm_t/db$ in eq.
+\textbf{Hmax:} Hmax affects growth via the fraction of energy allocated to vegetative growth versus to seed production ($dm_t/db$ in eq.
 \ref{eq:eq1}; Table \ref{tab:trade-offs}).
@@
 
-Fourth, the relationship between seed mass and $\textrm{RGR}_{\textrm{mass}}$ is predicted to be negative in seedlings.
-This is because the relative growth rate slows as plants grow larger, and large-seeded species begin larger as seedlings.
+\textbf{Seed mass:} The $\textrm{RGR}_{\textrm{mass}}$ slows as plants grow larger, and large-seeded species begin larger as seedlings.
 For larger plants, seed mass is not expected to have any distinct influence on growth rates  (Table \ref{tab:trade-offs}).
 
-Finally, the relationship between Aarea and growth should be positive across all plant sizes (eqn 1).
-The effects of benefits (higher assimilation) and costs (higher respiration) of increased Area occur within the same element of eq.
+\textbf{Aarea:} The effects of benefits (higher assimilation) and costs (higher respiration) of increased Area occur within the same element of eq.
 \ref{eq:eq0}, and assimilation must outweigh respiration for there to be growth, so the net effect will be positive (Table \ref{tab:trade-offs}).
@@
 \newpage
-\begin{Supplemnetary material}\label{sec:appendices}
+\begin{appendices}\label{sec:appendices}
 \renewcommand{\thefigure}{S\arabic{figure}}
@@
 \centering
-\caption{\linespread{2}\textbf{List of the twenty traits targeted}. Abbreviation,
+\caption{\textbf{List of the twenty traits targeted}. Abbreviation,
 definition and search term used in the meta-analysis} 
@@
 \begin{figure}[htbp]
+\includegraphics{output/FigA7d.pdf}
 \centering
-\includegraphics{output/FigA7d.pdf}
 \end{figure}

### 2015-05-08 MS.tex
add * metanalyses file

@@
 
-This study is the first one of an upcoming series of theoritical articles and empirical studies performed by the authors on the same thematic: the effect of plant size on plant strategies and functional traits.
+This study is the first one of an upcoming series of theoritical and empirical studies performed by the authors on the same thematic: the effect of plant size on plant strategies and functional traits.
 

### 2015-05-08 analysis.R

@@ -125,6 +125,6 @@ dev.off()
 paper <- read.bib("references/paper.bib")
 meta <- read.bib("references/metaanalyses.bib")
 
-combined <- c(meta[setdiff(names(meta), names(paper))], paper)
+combined <- c(paper[setdiff(names(paper), names(meta))], meta)
 write.bib(combined[[sort(names(combined))]], file = "output/refs.bib")
 

### 2015-05-14 MS.tex
MS (update)

@@
 \linespread{2}
-\usepackage{hyperref}
+\usepackage{color}
 
-%appendix
 \usepackage[title,titletoc,toc]{appendix}
 
-% allows for number referencing, as required by updated ecol letters style
 \usepackage{etoolbox}
 \newbool{MyRefNumbers}
-\booltrue{MyRefNumbers} % comment to remove numbers in reference list
+\booltrue{MyRefNumbers}
 
 \usepackage{natbib}
+
 \bibliographystyle{ecol_let}
 \setcitestyle{authoryear,open={(},close={)}}
-
 \newcommand{\bibstar}{* }
@@
 
-\section*{Cover letter (303 on 300 words)}\label{Proposal}
-
-Editor-in-Chief Ecology letters
-
-Dear Dr Holyoak,
-
-May we please submit for Ecology Letters a manuscript titled “Plant species traits and growth rates: meta-analysis shows correlations change with plant size as predicted”?
-We would be grateful if you would consider it for publication.
-
-The work is meta-analysis, but we suggest it should be considered as a Letter more so than under the heading of Reviews and Syntheses.
-It reports original conclusions based on new data analysis, and does not attempt broad review.
-But of course if you prefer to consider it as a review, then we are in your hands.
-
-\textbf{Novelty statement:}
-In a nutshell, this paper sorts out the differences across plant species in potential growth rates.
-We believe it's a very substantial advance.
-Growth rates are obviously really important for ecology.
-They have been seen as a core element of plant ecological strategies going back to Grime and Hunt 1975.
-Over the past 20 years much ecological strategy research has shifted into "trait ecology", using traits such as SLA and wood density and seed mass as indicators of ecological strategy.
-Yet empirical reports of the correlations between traits and growth rates have been inconsistent.
-Our manuscript first spells out reasons why traits should influence growth differently depending what size the individual plant has achieved -- in other words, traits should influence growth trajectories rather than simply making species fast-growing versus slow-growing throughout life.
-Then second, we provide meta-analysis of correlations that have been reported between traits and growth rate.
-To the extent data are available, these correlations are shown to shift depending on plant size consistently with the reasons explained and the predictions made in the first part of the paper.
-
-This study is the first one of an upcoming series of theoritical and empirical studies performed by the authors on the same thematic: the effect of plant size on plant strategies and functional traits.
-
-We are excited by this work and look forward to your evaluation of the paper.
-
-Sincerely
-
-Anais Gibert on behalf of all authors
-
 \newpage
@@
 \title{Plant species traits and growth rates: meta-analysis shows correlations change with plant size as predicted}
-
-shows predictable changes with plant size of the correlations
 
@@
 
-\textit{Number of words in the abstract} 148
+\textit{Number of words in the abstract} 150
 
@@
 
-\textit{Number of words in each text box} 750
+\textit{Number of words in each text box} 770
 
@@
 
-\section*{Abstract (148 words/150)}\label{abstract}
+\section*{Abstract}\label{abstract}
 
@@
 \item 
-Traits should influence growth in a size-dependent manner.
+Traits should influence growth in a way that depend on individual plants size.
 We outline mechanisms and hypotheses based on new theory, and test these predictions for five traits using a meta-analysis of 108 studies (\textgreater{} 500 correlations).
@@
 \item 
-We show that correlations between traits and GR change in a predictable way as a function of plant size.
+We show that traits-GR correlations change in a predictable way as a function of plant size.
 Our understanding of plant strategies should shift away from attributing slow vs fast growth to species throughout life, in favour of attributing growth trajectories.
@@
 The phrase "plant ecological strategy" refers to how species face the challenge they all share:  to acquire sufficient water, nutrients and light for individual growth and to live long enough to replace themselves with offspring.
-An idea that strategy differences might involve fast vs slow growth goes back at least to Grime and Hunt \citeyearpar{Grime:1975gr}, who measured a wide spread of relative growth rates for seedlings during early exponential growth under favourable conditions.
+An idea that species strategy differences might involve fast vs slow growth goes back at least to Grime and Hunt \citeyearpar{Grime:1975gr}, who measured a wide spread of relative growth rates for seedlings during early exponential growth under favourable conditions.
 Seedling potential RGR has continued to be used as a major strategy indicator within the Sheffield CSR (Competitor - Stress tolerator - Ruderal) scheme and its "Integrated Screening Program" (e.g.
@@
 
-Meanwhile the possibility has been raised that trait-growth correlations may change systematically with size \citep{Iida:2014ep,Iida:2014hq,Ruger:2012jv,Falster:2011ii}.Recent theory suggests that the absence of a correlation between SLA and growth at larger sizes may be expected, when  potential influences of traits on plant function are considered \citep{Falster:2011ii, falster:2013} (see Text Box 1 \ref{app:growth} in Supporting Informations).
-At larger sizes the low-cost deployment benefits of high SLA may be offset or even outweighed by the high costs of rapid leaf turnover.
+Meanwhile the possibility has been raised that trait-growth correlations may change systematically with size \citep{Falster:2011ii, Ruger:2012jv, Iida:2014ep, Iida:2014hq}.
+Recent theory suggests that the absence of a correlation between SLA and growth at larger sizes may be expected, when  potential influences of traits on plant function are considered \citep{Falster:2011ii, falster:2013}.
+At larger sizes the low-cost deployment benefits of high SLA may be offset or even outweighed by the high costs of rapid leaf turnover (see Text Box 1\ref{sec:growth}).
 
-Here we review published literature reporting on relationships between
-plant growth and five prominent traits (specific leaf area SLA, wood or stem tissue density WD, maximum leaf photosynthetic capacity per unit area Aarea,  maximum height Hmax, and seed mass SM), in order to assess the following questions.
+Here, we review published literature reporting on relationships between
+plant growth and five prominent traits (specific leaf area = SLA, wood or stem tissue density = WD, maximum leaf photosynthetic capacity per unit area = Aarea,  maximum height= Hmax, and seed mass= SM), in order to assess the following questions.
 
@@
   \item Do the observed relationships conform to predictions (outlined below) from a recently developed  mechanistic
-model \citep{Falster:2011ii, falster:2013}(Text Box 1 \ref{app:growth})?
+model \citep{Falster:2011ii, falster:2013}?
 \end{enumerate}
@@
 While most studies on traits have not been concerned with effects of plant stage or size, they have reported trait-growth correlations for identifiable size classes.
-We gathered correlation coefficients r between trait and growth from studies that gave explicit information about the size or stage of the plants.
+We gathered correlation coefficients between trait and growth from studies that gave explicit information about the size or stage of the plants.
 Meta-analysis allowed us to generalize about trait influences on growth.
@@
 
-Recent theoretical work \citep{Falster:2011ii} allows hypotheses to be formulated about relationships between traits and growth.
-Below we provide a verbal description for each of the hypotheses; for a mathematical description see Text Box 1 \ref{app:growth}.
+Recent theoretical work \citep{Falster:2011ii} allows hypotheses to be formulated about relationships between traits and growth, based on a mathematical decomposition of plant growth rate.
+Specific predictions arise from considering the influence of traits on elements of these equations and how these effects may vary with size (see Text Box 1\ref{sec:growth}).
 
-\textbf{H1: The relationship between specific leaf area (SLA) and growth rate is expected to shift from positive in seedlings to non-significant or negative in adult plants, regardless of the growth measurement used}
+\textbf{H1: The relationship between specific leaf area (SLA) and growth rate is expected to shift from positive in seedlings to non-significant or negative in adult plants}
 
@@
 However, high-SLA species also have shorter leaf lifespan and faster leaf turnover rate \citep{Wright:2004jb}.
-Whether plant growth increases with SLA depends on the relative magnitude of the leaf construction and leaf turnover effects of SLA.
-During early life while leaf comprises a large part of the plant, decreasing leaf construction cost has a positive effect on growth rate.
+Whether plant growth increases with SLA depends on the relative magnitude of the leaf construction and leaf turnover effects of SLA (Table 1).
+During early life, while leaf comprises a large part of the plant, decreasing leaf construction cost has a positive effect on growth rate.
 As plants increase in size and leaf mass fraction decreases, the benefit of cheaper leaf construction diminishes; thus the cost of replacing leaf turnover becomes more important.
@@
 
-Low WD decreases the cost of building stem tissue, which should result in faster growth.
+Low WD decreases the cost of building stem tissue and thus the cost of deploying additional leaf area (Table 1), which should result in faster growth.
 Although cheaper wood carries a risk of increased mortality, this cost is not reflected in growth outcomes.
@@
 
-\textbf{H3: The relationship between maximum photosynthetic rate (Aarea) and growth rate is expected to be positive across all plant sizes, at least under high-light conditions}
-
-We expect greater photosynthetic capacity to translate into faster growth rates, at least at high light where Aarea is measured.
-It is uncertain how much this might translate to faster growth in low light.
-
-\textbf{H4: The relationship between asymptotic maximum height (Hmax) and growth rate is expected to be absent in seedlings but to strengthen with increasing plant size.}
+\textbf{H3: The relationship between asymptotic maximum height (Hmax) and growth rate is expected to be absent in seedlings but to strengthen with increasing plant size.}
 
@@
 For seedlings, where all individuals are investing solely in growth, we expect no influence of Hmax on growth.
-As plants become larger, species with smaller Hmax are expected to be allocating more to reproduction and less to growth, because at any given size they are closer to their Hmax.
+As plants become larger, species with smaller Hmax are expected to be allocating more to reproduction and less to growth, because at any given size they are closer to their Hmax (Table 1).
 
-\textbf{H5: The relationship between seed mass (SM) and relative growth rate is negative in seedlings, but weakens with increasing size.}
+\textbf{H4: The relationship between seed mass (SM) and relative growth rate is negative in seedlings, but weakens with increasing size.}
 
@@
 However, among larger plants we expect the effect of this initial size to be minimal, and thus the correlation between seed size and growth rate should disappear.
+
+\textbf{H5: The relationship between maximum photosynthetic rate (Aarea) and growth rate is expected to be positive across all plant sizes, at least under high-light conditions}
+
+We expect greater photosynthetic capacity to translate into faster growth rates by increasing the rate of biomass production (Table 1), at least at high light where Aarea is measured.
+It is uncertain how much this might translate to faster growth in low light.
 
@@
 (This included adding data from an as-yet unpublished study by Gleason et al).
-The complete list of studies where we inspected the full text is given in Appendix \ref{app:supp_info_files}.
+The complete list of studies where we inspected the full text is given in Appendix \ref{app:supp_info_files} in Supplementary material.
 
@@
 The Web of Science database (Thomson Reuters) was searched between March and June 2014 using a range of Boolean search terms in English.
-Search terms were as follows: (``NAME'' AND (``growth rate'' OR ``relative growth rate'')) AND (``tree*'' OR ``woody*''), ``NAME'' was one of trait names listed in Table \ref{TableA1}.
+Search terms were as follows: (``NAME'' AND (``growth rate'' OR ``relative growth rate'')) AND (``tree*'' OR ``woody*''), ``NAME'' was one of trait names listed in
+
+\ref{TableA1}.
 According to this snapshot, 62\% of the literature for the 20 traits (or 82\% for the 5 traits for which we have clear predictions) is captured by searching only on two traits: SLA and WD.
@@
 In addition, to avoid publication bias due to selective reporting of significant results within published articles (e.g.~particular case of a `failure to publish bias' see \citealt{Jennions:2013ta}), we asked the authors for additional information when they reported a non-significant correlation between growth and trait without reporting an r value.
-All meta-analyses were conducted with R software \citep{Ralanguageanden:2014wf}.
+
+\subsection*{Availability of code and data}\label{code}
+
+All analyses were conducted with R software \citep{Ralanguageanden:2014wf}.
+The code and data underpinning this paper is available at github.com/AnaisGibert/Growth\_trait\_metaanalysis.
+Archival copies are also included in Appendix \ref{app:supp_info_files} in Supplementary material.
 
@@
 For Aarea, the comparison between complete and ideal data showed no signal of an effect of stress (here mainly low light) on the correlation with growth at seedling stage; the correlation was still positive between Aarea and growth even when 7 correlations measured under low light conditions were added.
-
 Finally, our results were unlikely to be biased by dominance of one or a few studies that measured a large number of responses, since when multiple responses were condensed into a single average within a trait and within a study, outcomes were very similar (Fig.
@@
 It should be noted however that there are few tests of this proposition at seedling stage.
-In our model (Text Box 1 \ref{app:growth}) cheaper stem construction is responsible for the predicted negative correlation.
+In our model (Text Box 1 \ref{sec:growth}) cheaper stem construction is responsible for the predicted negative correlation.
 Lower xylem conductance and associated lower photosynthetic potential have also been suggested \citep[reviewed by][]{Chave:2009iy}.
@@
 For the correlation between Aarea and growth, to our knowledge no study has previously assessed this in relation to plant size.
-In the growth model (Text Box 1 \ref{app:growth}), a consistent correlation irrespective of size arises from a direct effect of Aarea on plant growth rate.
+In the growth model (Text Box 1 \ref{sec:growth}), a consistent correlation irrespective of size arises from a direct effect of Aarea on plant growth rate.
 In juvenile stage, where most of the data were, we noted no signal of an effect of low light on the positive correlation between Aarea and growth rate.
@@
 Charles Warren and Jordi Martìnez-Vilalta kindly provided additional information about their published results.
-This work was funded by the Australian Research Council through a fellowship to Westoby.
+This work was funded by the Australian Research Council through a fellowship to Westoby and a discovery grant to Falster.
 
@@
 \nocite{*}
+
 \bibliography{output/refs}\label{references}
@@
 \label{Fig2}
-
-% Is it Ecol Lett style to have a declarative first sentence in Fig legends stating the main result? -- or should the explanation be more deadpan, relying on the main text to make the point?
-
 \end{figure}
@@
 \centering
-\caption{\textbf{ Hypothesised effect of traits on components of growth.} Arrows indicate the effect an increase in trait value would have on the elements of eqs. \ref{eq:eq0}-\ref{eq:eq4}.}
-  \begin{tabular}[c]{lcccc}
-  & $\frac{\textrm{d}a_\textrm{l}}{\textrm{d}m_\textrm{t}}$
-  & $\frac{\textrm{d}m_\textrm{t}}{\textrm{d}b}$
-  & $\frac{\textrm{d}b}{\textrm{d}t}$
-  & $k_s$ \\\hline
-  Seed size & & & & \\ 
-  Aarea & & & $\uparrow$ & \\
-  SLA &$\uparrow$ & & $\downarrow$& \\
-  Wood density & $\downarrow$ &  & & \\
-  Maximum height & &$\uparrow$ & & \\
+\caption{\textbf{ Hypothesised effects of traits on key elements of plant function determining growth rate.} Arrows indicate the effect an increase in trait value would have on the main elements of growth eqs.
+\ref{eq:eq0}-\ref{eq:eq4} in Text box 1:  Leaf deployment per mass ($\frac{\textrm{d}a_\textrm{l}}{\textrm{d}m_\textrm{t}}$), Allocation to vegetative growth ($\frac{\textrm{d}m_\textrm{t}}{\textrm{d}b}$), Net live biomass production ($\frac{\textrm{d}b}{\textrm{d}t}$), Sapwood turnover ($k_s a_s$).
+SLA: Specific leaf area, WD: Wood density, Hmax: Asymptotic maximum height, SM: seed mass, Aarea: Maximum photosynthetic rate.
+For further details, see Text Box 1.}
+\vspace{1cm}
+  \begin{tabular}{l p{3cm} p{2cm}p{4cm} p{2cm}}
+  & Leaf deployment \newline per mass
+  & Allocation to vegetative growth
+  & Net live biomass \newline production
+  & Sapwood turnover\\
+  & & & &\\\hline
+  & & & & \\
+Increase in : & & & & \\ 
+  SLA &$\nearrow$ &$\_$ & $\searrow$ \newline (via $\nearrow$ of tissue turnover) &$\_$ \\
+  WD & $\searrow$ &$\_$  &$\_$ &$\_$ \\
+  Hmax &$\_$ &$\nearrow$ &$\_$ &$\_$ \\
+  SM &$\_$&$\_$&$\_$& $\_$\\ 
+  Aarea &$\_$ &$\_$ & $\nearrow$ &$\_$ \\
+
 \hline
@@
 \newpage
-\section*{Text Box} \label{app:growth}
+\section*{Text Box 1} \label{sec:growth}
 
@@
 
-We adapted growth equations from \cite{Falster:2011ii} and \cite{falster:2013} to generate hypotheses on both absolute and relative growth rates in biomass ($m_t$, eqn \ref{eq:eq1}), height (H, eqn \ref{eq:eq2}) and diameter (D, eqn \ref{eq:eq4}).
-These size dimensions are routinely measured on seedling and adult plants.
+We adapted growth equations from \cite{Falster:2011ii} and \cite{falster:2013} to generate hypotheses on both absolute and relative growth rates in mass (eqn \ref{eq:eq1}), height (eqn \ref{eq:eq2}) and diameter (eqn \ref{eq:eq4}).
 
-Let $m_i$ denote the mass, $r_i$ the mass-specific respiration rate, and $k_i$ the turnover rate of different plant tissues, with the subscripts $i=l,s,r,t$ referring to live biomass in leaves, sapwood and bark, roots, and in the plant.
-Similarly let $a_i$ denote areas, of leaves ($i=l$) and of cross-sections of total stem and sapwood ($i= st,ss$) respectively.
+The rate at which \textbf{live biomass} $b$ is produced by a plant is given by:
 
-The rate at which live biomass originating from the plant $b$ changes is given by
 \begin{equation}\label{eq:eq0}
-\underbrace{\frac{db}{dt}}_{\text{net live biomass production}} = \underbrace{y}_{\text{yield}}  \big(\underbrace{a_{l} A_{\textrm{area}}}_{\text{photosynthesis}} - \underbrace{\sum_{i=l,s,r} m_{i} r_{i}}_{\text{respiration}}\big) - \underbrace{ \sum_{i=l,s,r} m_{i} k_{i}}_{\text{turnover}},
+\underbrace{\color{green}\frac{db}{dt}}_{\text{net live biomass production}} = \underbrace{y}_{\text{yield}}  \big(\underbrace{a_{l} A_{\textrm{area}}}_{\text{photosynthesis}} - \underbrace{\sum_{i=l,s,r,f} m_{i} r_{i}}_{\text{respiration}}\big) - \underbrace{ \sum_{i=l,s,r,f} m_{i} k_{i}}_{\text{turnover}},
 \end{equation}
-where $y$ is the fraction of assimilated carbon fixed into biomass,  and  $A_{\textrm{area}}$ is the assimilation rate of CO$_{2}$ per leaf area.
-The rate at which live biomass is accumulated on the plant is then
+
+where $y$ is the ratio of carbon fixed in mass per carbon assimilated,  and  $A_{\textrm{area}}$ is the assimilation rate of CO$_{2}$ per leaf area.
+
+Here, and in the following equations, $m_i$ denotes the \textbf{live mass on the plant}, $r_i$ the mass-specific \textbf{respiration rate}, and $k_i$ the \textbf{turnover rate} of different plant tissues; the subscripts $i=l,s,r,t,f$ referring to leaves, sapwood and bark, roots, total of these vegetative tissues, and to the reproductive tissues (fruits, flowers etc.) (note that the live biomass $b= m_t +m_f$).
+Similarly $a_i$ denotes \textbf{areas}, of leaves ($i=l$) and of cross-sections of total stem and sapwood ($i= st,ss$) respectively.
+
+The \textbf{growth rate in mass}, being the increment in vegetative live mass ($m_t$), is then:
 
 \begin{equation}\label{eq:eq1}
-\underbrace{\frac{dm_t}{dt}}_{\text{growth in live biomass}} = \underbrace{\frac{dm_t}{db}}_{\text{allocation to growth}}  \times \underbrace{\frac{db}{dt}}_{\text{net live biomass production}},
-\end{equation}
-where allocation to growth is the fraction of biomass increase that goes to vegetative growth rather than to seed production. Height growth rate can then be expressed as
-\begin{equation}\label{eq:eq2}
-\underbrace{\frac{dH}{dt}}_{\text{growth rate in height}} = \underbrace{\frac{dH}{da_{l}}}_{\text{architecture layout}} \times \underbrace{\frac{da_{l}}{dm_{t}}}_{\text{leaf deployment per mass}} \times \frac{dm_t}{db} \times \frac{db}{dt}.
-\end{equation}
-Similarly basal area growth can be expressed as
-\begin{equation}\label{eq:eq3}
-\underbrace{\frac{da_{st}}{dt}}_{\text{basal area increment}} = \underbrace{\frac{da_{ss}}{da_{l}}}_{\text{sapwood area per leaf area}} \times \frac{da_{l}}{dm_{t}} \times\frac{dm_t}{db} \times\frac{db}{dt} +  \underbrace{ k_{s} a_s }_{\text{sapwood turnover}}.
+\underbrace{{\color{magenta}\frac{dm_t}{dt}}}_{\text{growth rate in mass}} = \underbrace{\color{blue}\frac{dm_t}{db}}_{\text{allocation to vegetative growth}}  \times \underbrace{\color{green}\frac{db}{dt}}_{\text{net live biomass production}},
 \end{equation}
 
-The growth rate in diameter is then given by the geometric relationship between diameter and area applied to stem:
-\begin{equation}\label{eq:eq4}
-\frac{dD}{dt} = \sqrt[]{\frac{\Pi}{a_{st}}} \times \frac{da_{st}}{dt}.
+where allocation to growth is the fraction of net live biomass increase that goes to vegetative growth rather than to reproductive tissue production.
+
+The \textbf{growth rate in height} can then be expressed as:
+
+\begin{equation}\label{eq:eq2}
+\underbrace{\frac{dH}{dt}}_{\text{growth rate in height}} = \underbrace{\frac{dH}{da_{l}}}_{\text{architecture layout}} \times \underbrace{{\color{orange}\frac{da_{l}}{dm_{t}}}}_{\text{leaf deployment per mass}} \times {\color{blue}\frac{dm_t}{db}} \times {\color{green}\frac{db}{dt}}.
 \end{equation}
 
-For the case of seedlings, eqs. \ref{eq:eq0}-\ref{eq:eq1} can be simplified considerably. Turnover of tissues and allocation to reproduction have not yet begun.
+Similarly \textbf{growth rate in basal area} can be expressed as:
 
-% AG: you mean turnover of other tissue than leaf?%
+\begin{equation}\label{eq:eq3}
+\underbrace{{\color{cyan}\frac{da_{st}}{dt}}}_{\text{basal area growth rate}} = \underbrace{\frac{da_{ss}}{da_{l}}}_{\text{sapwood area per leaf area}} \times {\color{orange}\frac{da_{l}}{dm_{t}}} \times  {\color{blue}\frac{dm_t}{db}} \times {\color{green}\frac{db}{dt}} +  \underbrace{ k_{s} a_s }_{\text{sapwood turnover}}.
+\end{equation}
 
-It is also common also to assume all respiration rates are proportional to leaf area. Biomass growth rate then becomes a linear function of leaf area:
+The \textbf{growth rate in diameter} is then given by the geometric relationship between diameter and area applied to stem:
+\begin{equation}\label{eq:eq4}
+\underbrace{\frac{dD}{dt}}_{\text{growth rate in diameter}} = \sqrt[]{\frac{\Pi}{a_{st}}} \times {\color{cyan}\frac{da_{st}}{dt}}.
+\end{equation}
+
+For the case of seedlings, eqs.
+\ref{eq:eq0}-\ref{eq:eq1} can be simplified considerably.
+Turnover of all tissues and allocation to reproduction have not yet begun.
+It is also common to assume all respiration rates are proportional to leaf area.
+Biomass growth rate in seedling then becomes a linear function of leaf area:
+
 \begin{equation}\label{eq:eq1_seedlings}
-\frac{dm_t}{dt}  \approx  a_{l} \, y \, (A_{\textrm{area}} - r_{l}).
+{\color{magenta}\frac{dm_t}{dt}}  \approx  a_{l} \, y \, (A_{\textrm{area}} - r_{l}).
 \end{equation}
-A relative growth rate in mass $(\textrm{RGR}_{\textrm{mass}})$ can be obtained by dividing both sides of this simplified eq \ref{eq:eq1_seedlings} by the total mass of living tissues $m_{t}$.
+
+The \textbf{relative growth rate in mass} $(\textrm{RGR}_{\textrm{mass}})$ in seedlings can be obtained by dividing both sides of this simplified eq \ref{eq:eq1_seedlings} by the total mass of living tissues $m_{t}$.
 The outcome is equivalent to the classical partitioning of RGR \citep{Lambers:1992bj, Cornelissen:1998ta}:
@@
 
-The predicted effects of different traits on growth can then be understood by considering the influence of trait variation on elements of equations  \ref{eq:eq0}-\ref{eq:eq4} (Table \ref{tab:trade-offs}) and how these may interact with plant size.
+The predicted effects of different traits on growth can then be understood by considering the influence of trait variation on elements of equations  \ref{eq:eq0}-\ref{eq:eq1_seedlings_RGR} (see Table \ref{tab:trade-offs}) and how these may interact with plant size.
 
-\textbf{SLA:} For seedlings (eq.
-\ref{eq:eq1_seedlings_RGR}) cheaper leaf construction (high SLA) should translate directly into faster relative growth rate in mass.
+\textbf{Specific leaf area (SLA):} For seedlings (eq.
+\ref{eq:eq1_seedlings_RGR}), cheaper leaf construction (high SLA) should translate directly into faster relative growth rate in mass.
 For larger plants (eq.
@@
 
-\textbf{WD:} Cheaper stem construction (low WD or stem density) increases the marginal rate of leaf deployment per total mass increment ($da_l/dm_t$), and consequently increases growth rate in leaf area, height and diameter (eqs.
-\ref{eq:eq2}-\ref{eq:eq4}).
-Disadvantages associated with cheap stem construction take the form of higher mortality and so are not reflected in growth equations (Table \ref{tab:trade-offs}).
+\textbf{Wood density (WD):} Cheaper stem construction (low WD or stem density) increases the marginal rate of leaf deployment per total mass increment ($da_l/dm_t$), and consequently increases growth rate in leaf area, height and diameter (eqs.
+\ref{eq:eq2}-\ref{eq:eq4}; Table \ref{tab:trade-offs}).
+Disadvantages associated with cheap stem construction take the form of higher mortality and so are not reflected in growth equations.
 Under this scenario, wood density is negatively correlated to growth rate across all plant stages.
-Because the relative expenditure on stem compared to leaf is expected to increase as plants grow larger, the relationship between WD and growth may also strengthen in larger plants.
+Because the relative expenditure on stem compared to leaf is increases as plants grow larger, the relationship between WD and growth may also strengthen in larger plants.
 
-\textbf{Hmax:} Hmax affects growth via the fraction of energy allocated to vegetative growth versus to seed production ($dm_t/db$ in eq.
+\textbf{Maximum height (Hmax):} Hmax affects growth via the fraction of energy allocated to vegetative growth versus to seed production ($dm_t/db$ in eq.
 \ref{eq:eq1}; Table \ref{tab:trade-offs}).
@@
 \ref{eq:eq0}, and assimilation must outweigh respiration for there to be growth, so the net effect will be positive (Table \ref{tab:trade-offs}).
+
+Note that the predicted relationship between growth and either SLA or seed mass in seedlings differs if absolute growth rate in mass is used instead of $RGR_{mass}$ (i.e.
+becomes negative for SLA, positive for SM).
+In our study, all data recorded for these trait-stage combinations have been measured on a RGR base for mass (see Fig S9).
 
@@
 \begin{itemize}
-  \item "references\_metaanalyses.bib": reference library containing all references used in eventual metanalysis (in bibtex format)
   \item "code.zip": the data and analysis code used to generate the results in this paper. A copy of the complete data set is also available from the Dryad Digital Repository.
@@
 rate and traits, established from 108 articles.} The mean
-coefficents are weighted by sample size (i.e number of species used to
+coefficients are weighted by sample size (i.e number of species used to
 perform the correlation), and calculated both across all plant stages
-and for each stage. Each panel correponds to a functional trait:
+and for each stage. Each panel corresponds to a functional trait:
 \textbf{a)} Specific leaf area (SLA), \textbf{b)} Wood density (WD),
@@
 Effect size is a standardized measure of the magnitude of the relationship between a particular stage and the correlation coefficient z (Fisher's z-transformed).
-Effects are significants if confidence intervals (+CI95\%) do not overlap with zero.
+Effects are significant if confidence intervals (+CI95\%) do not overlap with zero.
 LRT: likelihood Ratio Test compared the fit between null model and stage model, both models are fitted by Maximum Likelihood.

### 2015-07-08 MS.tex
References added: in ms (112 instead of 108 articles used in the meta-analyses) in references bibtex (in read and meta-analyses)

@@
 
-\textit{Number of data source references} 108
+\textit{Number of data source references} 112
 
@@
 Traits should influence growth in a way that depend on individual plants size.
-We outline mechanisms and hypotheses based on new theory, and test these predictions for five traits using a meta-analysis of 108 studies (\textgreater{} 500 correlations).
+We outline mechanisms and hypotheses based on new theory, and test these predictions for five traits using a meta-analysis of 112 studies (\textgreater{} 500 correlations).
 
@@
 
-We found 108 studies published between between 1983 and 2014 that met our requirements.
+We found 112 studies published between between 1983 and 2014 that met our requirements.
 Climate zones spanned from temperate regions to  tropics (map in Fig.
@@
 maximum height (Hmax, n=23), \textbf{d)} Seed mass (Seedmass, n=36 and
-\textbf{e)} Rate of CO2 assimilation (Aarea, n=24) reported from 108
+\textbf{e)} Rate of CO2 assimilation (Aarea, n=24) reported from 112
 articles.
@@
 \caption{\textbf{Mean coefficient correlation r (+SD) between growth
-rate and traits, established from 108 articles.} The mean
+rate and traits, established from 112 articles.} The mean
 coefficients are weighted by sample size (i.e number of species used to

### 2015-07-15 MS.tex
Fix intraspecific and interspecific scale in Fig - Add a figure (A6) - Do all Fig in main text at interspecific level -change fig title -change nb fig in ms

@@
 
-We adopted two approaches to address plant size/stage effect in this review.
+Across the 112 article used in our meta-analyses, plants were categorized into four stages according to the expertise and the apprciation of the authors (i.e.seedling, juvenile, sapling, adult). 
+While by compiling data across multiple studies there is a risk of assigning plants of similar size to different categories, the thershold size is standardized for a plant stage across the 112 studies ().
 
-First, plants were categorized into stages according to the authors categorization (i.e.seedling, juvenile, sapling, adult, mix).
 When the stage information was not explicitly given, data were recorded as 'mix'.
-While this approach is based on the expertise and the appreciation of the authors, by compiling data across multiple studies there is a risk of assigning plants of similar size to different categories.
 
-Second, we re-assigned plants to three stage categories (`juvenile', `sapling' and `adult') according to size and age cutoffs established by looking at the range values observed across all studies (Fig.
+Second, we re-assigned plants to three stage categories ("juvenile", "sapling" and "adult") according to size and age cutoffs established by looking at the range values observed across all the 112 studies (Fig.
 \ref{FigA1}).
-We preferred the term `juvenile' to `seedling', because for a portion of the scientific community `seedling' also refers to a particular experimental condition (a greenhouse experiment).
-Overall, the different studies were largely consistent in their classification of plants into `juvenile', `sapling' and `adult' groups  (Fig.
+We preferred the term "juvenile" to "seedling", because for a portion of the scientific community "seedling" also refers to a particular experimental condition (a greenhouse experiment).
+Overall, the different studies were largely consistent in their classification of plants into "juvenile", "sapling" and "adult" groups  (Fig.
 \ref{FigA1}).
@@
 \ref{FigA2}).
+
 Thus, we established the following rules: i) `juveniles' are plants of {[}0,0.5) m in height , or {[}0,0.2{]} cm in diameter, or $\leq$ 1 yrs old; ii) `saplings' are plants of {[}0.5-5{]} m , or (0.2,10{]} cm in diameter, or (1-30{]} yrs, and iii) `adult' are plants \textgreater{}5 m in height, or \textgreater{}10 cm in diameter, or \textgreater{} 30 yrs and/or in the reproductive stage.
@@
 
-In the main text we report the results using the second approach, i.e. standardized categories. Results using the first approach are similar and are available in Fig. \ref{FigA7}.
+In the main text we report the results using the second approach, i.e. standardized categories. Results using the first approach are similar and are available in Fig. \ref{FigA8}.
 
@@
 Effects of other variables (vegetation type, experiment type and growth measurement) were also tested individually (results shown in the Fig.
-\ref{FigA7}).
+\ref{FigA8}).
 Estimates of the effect size for each stage were considered significant if the 95\% confidence intervals did not overlap with zero.
@@
 Finally, we checked the dataset for publication bias with funnel plots (\citealt{Koricheva:2013tz}, Fig.
-\ref{FigA8}).
+\ref{FigA9}).
 A publication bias toward significant results creates an asymmetric funnel with small studies with non-significant effects missing from the mouth of the funnel on the side opposite to the true effect.
@@
 Finally, our results were unlikely to be biased by dominance of one or a few studies that measured a large number of responses, since when multiple responses were condensed into a single average within a trait and within a study, outcomes were very similar (Fig.
-\ref{FigA6}) .
+\ref{FigA7}) .
 
@@
 Different experiment types (laboratory, field, plantation or greenhouse) and growth measurements were included (see Fig.
-\ref{FigA7} for analyses of how these factors affected  correlations between growth and traits).
+\ref{FigA8} for analyses of how these factors affected  correlations between growth and traits).
 Given this variety, it was not surprising to find wide ranges of r reported for all traits.
@@
 As expected the correlation coefficient varied less widely as sample size increased (funnel plots Fig.
-\ref{FigA8}).
+\ref{FigA9}).
 In the analyses described in Figs 2, A5 and A6 coefficients were weighted according to sample size, making the small-sample extremes less influential.
 Funnel plots exhibited a typical funnel shape for all five functional traits analyzed, showing no evidence for publication bias (Fig.
-\ref{FigA8}).
+\ref{FigA9}).
 
@@
 This negative relationship arises because seedlings from larger seeds are larger to begin with, as extensively discussed in the literature \citep[reviewed by][]{Turnbull:2012ew}.
-It applies only to RGR not to absolute growth rate, but for seedlings growth is most often reported as RGR (Appendix FigA9 d).
+It applies only to RGR not to absolute growth rate, but for seedlings growth is most often reported as RGR (Appendix FigA10 d).
 
@@
 \includegraphics{output/Fig1.pdf}
-\caption{\textbf{Number of correlations between trait and growth for each plant stage recorded in our dataset.} Shown here are 'complete dataset' (recorded at both interspecific and intraspecific level, under unstressed and stressed conditions).
+\caption{\textbf{Number of correlations between trait and growth for each plant stage recorded in our dataset.} Shown here are \textcolor{red}{'raw} dataset' (recorded at both interspecific and intraspecific level, under unstressed and stressed conditions).
 Bar colors: red for adult, orange for sapling, grey for juvenile.
@@
 \includegraphics{output/Fig2.pdf}
-\caption{\textbf{The relationship between growth rates and SLA or seed mass changes with plant stage.} Plots show the effect size (+ 95\%CI) of the correlation between growth rate and five functional traits for plant stage comparisons.
+\caption{\textbf{The relationship between growth rates and SLA or seed mass changes with plant stage.} Plots show the effect size (+ 95\%CI) of the correlation \textcolor{red}{across species} between growth rate and five functional traits for plant stage comparisons.
 \textbf{a)} Specific leaf area (SLA), \textbf{b)} Wood density (WD), \textbf{c)} Asymptotic height (Hmax) \textbf{d)} Seed mass and \textbf{e)} Assimilation rate of CO2 (Aarea).
@@
 Effects are significant if confidence intervals (95\%CI) for a given stage do not overlap with zero.
-Black point: ideal data (at interspecific level \& under unstressed conditions), grey points: all the data.
+Black point: ideal data (under unstressed conditions), grey points: all the data.
 'n' indicates number of correlations contributing to each effect.
@@
 The colors represents the stage information given by the authors (green: seedling, blue:juvenile, orange: sapling, red: adult, grey: mix), and the vertical line the limit we choose to established our stage categories.
-Shown here are complete dataset (recorded at both interspecific and intraspecific level and under unstressed and stressed conditions).
+Shown here are the \textcolor{red}{"raw} dataset" (recorded at both interspecific and intraspecific level and under unstressed and stressed conditions).
 }
@@
 \includegraphics{output/FigA3.pdf}
-\caption{\textbf{Geographical distribution of site locations from studies performed in the field used in the meta-analysis.} Shown here are complete dataset (recorded at both interspecific and intraspecific level and under unstressed and stressed conditions).}
+\caption{\textbf{Geographical distribution of site locations from studies performed in the field used in the meta-analysis.} Shown here are the \textcolor{red}{"raw} dataset" (recorded at both interspecific and intraspecific level and under unstressed and stressed conditions).}
 \label{FigA3}
@@
 \caption{\textbf{Range of the correlation of correlations (r) between
-growth and trait across the world} Coefficients of correlation (r)
+growth and trait \textcolor{red}{from 112 articles}.} Coefficients of correlation (r)
 between the plant growth and \textbf{a)} Specific leaf area (SLA, n=
@@
 \textbf{e)} Rate of CO2 assimilation (Aarea, n=24) reported from 112
-articles.
-Shown here are complete dataset (recorded at both interspecific and intraspecific level and under unstressed and stressed conditions).
-Each bubble represents a r value, the diameter of the bubble
+articles. \textcolor{red} {The x abcissa represents the articles sorted by the average coefficient value r reported}.
+Shown here are the \textcolor{red}{"raw} dataset" (recorded at both interspecific
+and intraspecific level and under unstressed and stressed conditions). Each bubble represents a r value, the diameter of the bubble
 is proportional to its weights in the meta-analysis. The colors
@@
 points corresponds adult stage, orange points to saplings, and grey
-points to juveniles.}
+points to juveniles. the \textcolor{red}{The x abciss represents the study ID} }
 \label{FigA4}
@@
 \includegraphics{output/FigA6.pdf}
-\caption{\textbf{Effect size (+ 95\%CI)of plant stage on the
-correlations between growth rate and five functional traits, with a data set averaging multiple comparisons by trait and by study.} Effects size are calculated from a reduced dataset; in the case of multiple comparisons within a study, we calculated the mean correlation coefficient by trait and by study.
-a) Specific leaf area (SLA), b) Wood density (WD), c) Net assimilation rate (NARarea), d) Seed mass, e) Asymptotic height (Hmax) and f) Assimilation rate of CO2 (Aarea).
+\caption{\textbf{Effect size (+ 95\%CI) of plant stage on the
+correlations between growth rate and five functional traits \textcolor{red}{across and between species}} Effects size are calculated for a) Specific leaf area (SLA), b) Wood density (WD), c) Net assimilation rate (NARarea), d) Seed mass, e) Asymptotic height (Hmax) and f) Assimilation rate of CO2 (Aarea).
 Effect size is a standardized measure of the magnitude of the relationship between a particular stage and the correlation coefficient z (Fisher's z-transformed).
@@
 LRT: likelihood Ratio Test compared the fit between null model and stage model, both models are fitted by Maximum Likelihood.
-Black point: ideal data (at interspecific level \& under unstressed conditions), grey points: all the data.
-`n' indicate the number of independent comparisons for each effect.}
+Black point: ideal data (at interspecific level and under unstressed conditions), grey points: raw data (at both intra and interspecific level and under both stress and unstressed conditions).
+'n' indicate the number of independent comparisons for each effect.
+}
 \label{FigA6}
@@
 \centering
-\includegraphics{output/FigA7a.pdf}
+\includegraphics{output/FigA7.pdf}
+\caption{\textbf{Effect size (+ 95\%CI) of plant stage on the
+correlations between growth rate and five functional traits \textcolor{red}{across species}, with a data set averaging multiple comparisons by trait and by study.} Effects size are calculated from a reduced dataset; in the case of multiple comparisons within a study, we calculated the mean correlation coefficient by trait and by study.
+a) Specific leaf area (SLA), b) Wood density (WD), c) Net assimilation rate (NARarea), d) Seed mass, e) Asymptotic height (Hmax) and f) Assimilation rate of CO2 (Aarea).
+Effect size is a standardized measure of the magnitude of the relationship between a particular stage and the correlation coefficient z (Fisher's z-transformed).
+Effects are significant if confidence intervals (+CI95\%) do not overlap with zero.
+LRT: likelihood Ratio Test compared the fit between null model and stage model, both models are fitted by Maximum Likelihood.
+Black point: ideal data (under unstressed conditions), grey points: all the data.
+'n' indicate the number of independent comparisons for each effect.}
+\label{FigA7}
 \end{figure}
@@
 \centering
-\includegraphics{output/FigA7b.pdf}
+\includegraphics{output/FigA8a.pdf}
 \end{figure}
@@
 \centering
-\includegraphics{output/FigA7c.pdf}
+\includegraphics{output/FigA8b.pdf}
 \end{figure}
@@
 \begin{figure}[htbp]
-\includegraphics{output/FigA7d.pdf}
+\centering
+\includegraphics{output/FigA8c.pdf}
+\end{figure}
+
+\begin{figure}[htbp]
+\includegraphics{output/FigA8d.pdf}
 \centering
@@
 \centering
-\includegraphics{output/FigA7e.pdf}
-\caption{\textbf{Effects size on the correlation between growth and traits of plant stage (mod1, as recorded by the authors), vegetation type (mod2), growth measurement (mod3) and experiment type (mod4).} The effect size (z + 95\%CI) is reported for each class, and models are fitted by restricted max likelihood (REML).
+\includegraphics{output/FigA8e.pdf}
+\caption{\textbf{Effects size on the correlation between growth and traits of plant stage (mod1), vegetation type (mod2), growth measurement (mod3) and experiment type (mod4).} The effect size (z + 95\%CI) is reported for each class, and models are fitted by restricted max likelihood (REML).
 n= number of correlation r reported.
@@
 Smallest is the AIC better is the model.
-Shown here are complete dataset (recorded at both interspecific and intraspecific level and under unstressed and stressed conditions).}
-\label{FigA7}
+Shown here are "ideal dataset" (recorded at interspecific and under unstressed condition) and "raw dataset" (recorded at both interspecific and intraspecific level and under unstressed and stressed conditions).}
+\label{FigA8}
 \end{figure}
@@
 \centering
-\includegraphics{output/FigA8.pdf}
+\includegraphics{output/FigA9.pdf}
 \caption{\textbf{Funnel plots showing transformed correlation coefficient z between growth and the traits a) Specific leaf area (SLA), b) Wood density (WD), c) Asymptotic height (Hmax), d) Seed mass and e) Assimilation rate of CO2 (Aarea)}.
@@
 
-\label{FigA8}
+\label{FigA9}
 \end{figure}
@@
 \centering
-\includegraphics{output/FigA9.pdf}
+\includegraphics{output/FigA10.pdf}
 \caption{\textbf{Growth measurement used by traits and by size.} Shown here are complete dataset (recorded at both interspecific and intraspecific level and under unstressed and stressed conditions).
 The colors correspond to the stage for which the r values have been recorded: red bars corresponds adult stage, orange bars to saplings, and grey bars to juveniles.}
-\label{FigA9}
+\label{FigA10}
 \end{figure}

### 2015-07-15 R/data_processing.R

@@ -130,7 +130,6 @@ clean_raw_data <- function(filename = "data/CompileData.csv") {
     sign, coef, coef.type))
 }
 
-
 standardise_data <- function(CompileTable) {
   RawData <- subset(CompileTable, CompileTable$trait %in% c("SLA", "WD", "Amass",
     "Aarea", "Nmass", "Narea", "Hmax", "LA", "Pmass", "Seedmass", "LMR", "LAR",
@@ -212,9 +211,9 @@ standardise_data <- function(CompileTable) {
   RawData
 }
 
-
 build_complete_data <- function(RawData) {
   #### Complete data set: focus on 5 traits:
+  
   CompleteData <- subset(RawData,
       RawData$trait %in% c("SLA", "WD", "Aarea", "Hmax", "Seedmass"))
   CompleteData$trait <- factor(CompleteData$trait,
@@ -230,8 +229,26 @@ build_complete_data <- function(RawData) {
   CompleteData
 }
 
+Build_intersp_complete_data <- function(RawData) {
+  #### Complete data set: focus on 5 traits:
+  
+  CompleteData <- subset(RawData,
+                         RawData$trait %in% c("SLA", "WD", "Aarea", "Hmax", "Seedmass") & RawData$bio.scale=="intersp")
+  CompleteData$trait <- factor(CompleteData$trait,
+                               levels = c("SLA", "WD", "Aarea","Hmax", "Seedmass"))
+  
+  # select the column of interest
+  CompleteData <- subset(CompleteData, select = c(id, idcor, authors, year, ref,
+                                                  doi, experiment, stress, veg.type, bio.scale, nb.sp, RGR, RGR.min, RGR.max,
+                                                  RGR.unit, stageRGR, similarity, stageTrait, stage, trait, trait.min, trait.max,
+                                                  measure.size, size.min, size.max, size.mean.range, coef, sample.size, corr.r,
+                                                  corr.z, vr.z, wi.z))
+  CompleteData$id <- as.factor(CompleteData$id)
+  CompleteData
+}
+
 # Ideal data set: only the correlation coefficient measured at interspecific
-# level, under unstressed conditionm and for measurement of growth and trait
+# level, under unstressed conditions and for measurement of growth and trait
 # perfomed at the same plant stage
 build_ideal_data <- function(CompleteData) {
 

### 2015-07-15 R/figures.R

@@ -6,7 +6,6 @@ to.pdf <- function(expr, filename, ..., verbose=TRUE) {
   eval.parent(substitute(expr))
 }
 
-
 figure_1 <- function(RawData) {
   p2 <- my_plot_1("",
           ggplot(RawData, aes(x=reorder(factor(trait), factor(trait), function(x) length(x)*1), fill=stage, order=stage)))
@@ -87,8 +86,7 @@ figure_map <- function(CoordTable) {
   coordinate.map
 }
 
-
-  figure_2 <- function(GC, GI) {
+figure_2 <- function(GC, GI) {
   CoefModel.SLA<-fun_model(GI[["SLA"]],GC[["SLA"]])
     CoefModel.SLA["trait"] <- "SLA"
     CoefModel.SLA.s <- subset(CoefModel.SLA,stress=='complete')
@@ -173,7 +171,7 @@ figure_map <- function(CoordTable) {
                    limit.x.n=2.5, vjust.value=1,
                    color1="grey",color2="black") +
     scale_fill_discrete(name="",breaks=c("ideal", "complete"),
-                        labels=c("ideal dataset", "complete dataset"))+
+                        labels=c("ideal", "complete"))+
                   theme (legend.title=element_blank(),
                          legend.justification=c(0,0),
                          legend.position=c(1.2,0.5),
@@ -221,7 +219,6 @@ figure_A1 <- function(CompleteData) {
   print(p_diam ,vp=vpc_)
 }
 
-
 figure_A4 <- function(GC) {
   GC[["SLA"]]  <- GC[["SLA"]] [!is.na(GC[["SLA"]] [,"corr.r"]),]
   GC[["WD"]] <- GC[["WD"]] [!is.na(GC[["WD"]] [,"corr.r"]),]
@@ -263,7 +260,7 @@ figure_A5 <- function(GI) {
     grid.arrange(p1,p2,p3,p4,p5,ncol=2, nrow=3,widths=c(1.2,1))
 }
 
-figure_A6 <- function(RI, RC) {
+figure_A7 <- function(RI, RC) {
   CoefModel.SLA<-fun_model(RI[["SLA"]],RC[["SLA"]])
   CoefModel.SLA.s <- subset(CoefModel.SLA,stress=='complete')
   CoefModel.SLA.opt <- subset(CoefModel.SLA,stress=='ideal')
[…]

### 2015-07-15 R/model.R

@@ -133,10 +133,14 @@ table_overall <- function(y) {
 fun_OneLR <- function(x) {
   null <- lmer(corr.z ~ 1 + (1 | id), data = x, weights = nb.sp, REML = FALSE, 
     control = lmerControl(check.nobs.vs.nlev = "ignore", check.nobs.vs.rankZ = "ignore", 
-      check.nobs.vs.nRE = "ignore"))
+      check.nobs.vs.nRE = "ignore", optimizer="bobyqa",check.conv.grad = .makeCC("ignore", tol = 2e-3, relTol = NULL),
+      check.conv.singular = .makeCC(action = "ignore",  tol = 1e-4),
+      check.conv.hess = .makeCC(action = "ignore", tol = 1e-6)))
   m <- lmer(corr.z ~ stage + (1 | id), data = x, weights = nb.sp, REML = FALSE, 
     control = lmerControl(check.nobs.vs.nlev = "ignore", check.nobs.vs.rankZ = "ignore", 
-      check.nobs.vs.nRE = "ignore"))
+      check.nobs.vs.nRE = "ignore", optimizer="bobyqa", check.conv.grad = .makeCC("ignore", tol = 2e-3, relTol = NULL),
+      check.conv.singular = .makeCC(action = "ignore",  tol = 1e-4),
+      check.conv.hess = .makeCC(action = "ignore", tol = 1e-6)))
   sum <- summary(m)
   ## log likelihood ratio test, anova makes sure to use the ML criterion, even
   ## though the models were fit with REML
@@ -146,10 +150,14 @@ fun_OneLR <- function(x) {
 fun_Onepvalue <- function(x) {
   null <- lmer(corr.z ~ 1 + (1 | id), data = x, weights = nb.sp, REML = FALSE, 
     control = lmerControl(check.nobs.vs.nlev = "ignore", check.nobs.vs.rankZ = "ignore", 
-      check.nobs.vs.nRE = "ignore"))
+      check.nobs.vs.nRE = "ignore", optimizer="bobyqa",check.conv.grad = .makeCC("ignore", tol = 2e-3, relTol = NULL),
+      check.conv.singular = .makeCC(action = "ignore",  tol = 1e-4),
+      check.conv.hess = .makeCC(action = "ignore", tol = 1e-6)))
   m <- lmer(corr.z ~ stage + (1 | id), data = x, weights = nb.sp, REML = FALSE, 
[…]

### 2015-07-15 R/plots.R

@@ -50,6 +50,7 @@ coeff.plot <- function(data, data.complete, data.ideal, LRT, PVAL, title = "",
     label = paste("p.value =", round(PVAL, round.value), significativite),
     size = 2)
 }
+
 coeff.plot.ideal <- function(data.ideal, LRT, PVAL, title = "", significativite = "",
   round.value, limit.x.min, limit.x.max, limit.x.text, limit.x.n, limit.y.text.l1,
   limit.y.text.l2, vjust.value, color1) {
@@ -77,6 +78,7 @@ coeff.plot.ideal <- function(data.ideal, LRT, PVAL, title = "", significativite 
     label = paste("p.value =", round(PVAL, round.value), significativite),
     size = 2)
 }
+
 plot_stage <- function(title, xlab, ggobj, ylab = "ID") {
   p <- ggobj + labs(title = title) + xlab(xlab) + ylab(ylab) + geom_errorbarh(aes(xmin = size.min,
     xmax = size.max, y = id), size = 0.7, width = 0.05, height = 0.2) + mytheme +
@@ -87,7 +89,6 @@ plot_stage <- function(title, xlab, ggobj, ylab = "ID") {
     legend.position = "none")
   p
 }
-
 
 my_plot_corr.r <- function(data1, title = "", xlab = "Case studies ranked by coefficient of correlation r") {
 
@@ -134,11 +135,9 @@ coeff.plot.multiple <- function(data, params, labels = NA, xlab = "Effect size (
   # creation d une liste avec le nombre de valeurs dans chaque categories
   # (seedling, sapling etc.)
   fun_List_N <- function(data) {c(
-      length(na.omit(data$coef[data$stageRGR == "seedling"])),
-      length(na.omit(data$coef[data$stageRGR == "juvenile"])),
-      length(na.omit(data$coef[data$stageRGR == "sapling"])),
-      length(na.omit(data$coef[data$stageRGR == "adult"])),
-      length(na.omit(data$coef[data$stageRGR == "mix"])),
+      length(na.omit(data$coef[data$stage == "juvenile"])),
+      length(na.omit(data$coef[data$stage == "sapling"])),
+      length(na.omit(data$coef[data$stage == "adult"])),
       length(na.omit(data$coef[data$veg.type == "boreal and temperate deciduous forest"])),
       length(na.omit(data$coef[data$veg.type == "boreal forest"])),
[…]

### 2015-07-15 analysis.R

@@ -29,7 +29,8 @@ for( f in list.files("R", full.names=TRUE)) {
 CompileTable <- clean_raw_data()
 RawData <- standardise_data(CompileTable)
 CompleteData <- build_complete_data(RawData)
-IdealData  <- build_ideal_data(CompleteData)
+CompleteData_inter <- Build_intersp_complete_data (RawData)
+IdealData_inter  <- build_ideal_data(CompleteData)
 CoordTable <- build_map_data(RawData)
 
 ## split datasets by trait - makes a list with named elements
@@ -39,11 +40,14 @@ list_by_trait <- function(df) {
 }
 
 GC <- list_by_trait(CompleteData)
-GI <- list_by_trait(IdealData)
+GCi <- list_by_trait(CompleteData_inter)
+GIi <- list_by_trait(IdealData_inter)
+
 
 ## Create restricted Dataset: coefficient of correlation are averaged by study and by trait
 RC <- list_by_trait(EffectSizeSum(CompleteData))
-RI <- list_by_trait(EffectSizeSum(IdealData))
+RCi <- list_by_trait(EffectSizeSum(CompleteData_inter))
+RIi <- list_by_trait(EffectSizeSum(IdealData_inter))
 
 ## output directory
 
@@ -58,7 +62,7 @@ pdf("output/Fig1.pdf",height=3, width=4)
 dev.off()
 
 pdf("output/Fig2.pdf",height=6,width=5)
-  figure_2(GC, GI)
+  figure_2(GCi, GIi)
 dev.off()
 
 pdf("output/FigA1.pdf", height=6)
@@ -80,45 +84,50 @@ dev.off()
 
 
 pdf("output/FigA5.pdf",height=6,width=5)
-  figure_A5(GI)
+  figure_A5(GIi)
 dev.off()
 
 
-pdf("output/FigA6.pdf",  height=6, width=5)
-  figure_A6(RI, RC)
+pdf("output/FigA6.pdf",height=6,width=5)
+figure_2(GC, GIi)
 dev.off()
 
 
-pdf("output/FigA7a.pdf")
-  figure_A7(GI, GC, "SLA", c("a","b"))
+pdf("output/FigA7.pdf",  height=6, width=5)
+  figure_A7(RIi, RCi)
 dev.off()
 
 
[…]

### 2015-07-16 MS.tex
Add Fig11 (model growth and measurment)

@@
 
-Across the 112 article used in our meta-analyses, plants were categorized into four stages according to the expertise and the apprciation of the authors (i.e.seedling, juvenile, sapling, adult). 
-While by compiling data across multiple studies there is a risk of assigning plants of similar size to different categories, the thershold size is standardized for a plant stage across the 112 studies ().
+Across the 112 article used in our meta-analyses, plants were categorized into four stages according to the expertise and the appreciation of the authors (i.e.seedling, juvenile, sapling, adult).
+While by compiling data across multiple studies there is a risk of assigning plants of similar size to different categories, the threshold in size/age used by the authors to defined a plant stage are quite standardized across the 112 studies (Fig.
+\ref{FigA1}).
 
@@
 LRT: likelihood Ratio Test compared the fit between null model and stage model, both models are fitted by Maximum Likelihood.
-Black point: ideal data (at interspecific level and under unstressed conditions), grey points: raw data (at both intra and interspecific level and under both stress and unstressed conditions).
+\textcolor{red}{Shown here are the "raw dataset" (recorded at both interspecific and intraspecific level and under unstressed and stressed conditions)}.
 'n' indicate the number of independent comparisons for each effect.

### 2015-07-16 R/data_processing.R

@@ -3,7 +3,7 @@ clean_raw_data <- function(filename = "data/CompileData.csv") {
   Table <- read.csv(filename, sep = ";", dec = ",")
 
   for(f in c("id","ref","idcor","authors","stress","RGR","trait","coef.type","experiment.type",
-    "veg.type","measure.size","trait.stage","stage","RGR.stage","relation.sign","stage.simi")) {
+    "veg.type","measure.size","trait.stage","stage","RGR.stage","relation.sign","stage.simi","life.form")) {
    Table[[f]] <- as.factor(Table[[f]])
   }
 
@@ -32,6 +32,22 @@ clean_raw_data <- function(filename = "data/CompileData.csv") {
   Table$sign[Table$relation.sign == "P"] <- "S"
   Table$sign[Table$relation.sign == "N"] <- "S"
   Table$sign[Table$relation.sign == "O"] <- "NS"
+  
+  # Add variable for growth and growth measurmemnt
+  levels(Table$RGR)
+  
+  Table["growth"] <- "NA"
+  Table$growth[Table$RGR %in% c("RGR(?)","RGR(CSAi)","RGR(Di)","RGR(Hi)","RGR(Mi)","RGR(Vi)")] <- "RGR"
+  Table$growth[Table$RGR %in% c("GR(Di)","GR(Hi)","GR(Mi)","GR(Shoot)")] <- "AbGR"
+
+  
+  Table["measurement"] <- "NA"
+  Table$measurement[Table$RGR %in% c("RGR(Di)","GR(Di)")] <- "Diameter"
+  Table$measurement[Table$RGR %in% c("RGR(Hi)","GR(Hi)")] <- "Height"
+  Table$measurement[Table$RGR %in% c("RGR(Mi)","GR(Mi)","GR(Shoot)")] <- "Mass"
+  Table$measurement[Table$RGR %in% c("RGR(?)","RGR(Vi)","RGR(CSAi)")] <- "Other"
+  
+  
 
   # Nb of species used to performed the correlation
   names(Table)[names(Table) == "nb.sp.reported"] <- "nb.sp"
@@ -114,17 +130,19 @@ clean_raw_data <- function(filename = "data/CompileData.csv") {
   Table$experiment.coord[Table$experiment.type == "mix.field.database"] <- "nature"
   Table$experiment.coord[Table$experiment.type == "mix.glasshouse.database"] <- "control"
 
[…]

### 2015-07-16 R/figures.R

@@ -134,7 +134,7 @@ figure_2 <- function(GC, GI) {
 
   p1 <- coeff.plot(data=CoefModel.SLA, data.complete=CoefModel.SLA.s, data.ideal=CoefModel.SLA.opt,
                    LRT=LRT.sla, PVAL= PVAL.sla, title="a) SLA",
-                   significativite="***",round.value=7,
+                   significativite="***",round.value=4,
                    limit.x.min=-0.5,limit.x.max=1.5,
                    limit.x.n=1, vjust.value=1,
                    limit.x.text=-0.1,limit.y.text.l1=0.5, limit.y.text.l2=0.25,
@@ -157,7 +157,7 @@ figure_2 <- function(GC, GI) {
 
   p4 <- coeff.plot(data=CoefModel.Seedmass, data.complete=CoefModel.Seedmass.s, data.ideal=CoefModel.Seedmass.opt,
                    LRT=LRT.sm, PVAL= PVAL.sm, title="d) Seed mass",
-                   significativite="***",round.value=4,
+                   significativite="***",round.value=3,
                    limit.x.min=-1.5,limit.x.max=1,
                    limit.x.text=-1,limit.y.text.l1=0.5, limit.y.text.l2=0.25,
                    limit.x.n=0.7, vjust.value=1,
@@ -194,19 +194,19 @@ figure_A1 <- function(CompleteData) {
   sd <- subset(s,s$measure.size=="diameter")
 
   p_diam <-  plot_stage("c)", xlab= "basal diameter (cm)",ylab="",
-                        ggplot(sd,aes(x= size.mean.range, y=id, xmin = size.min, xmax= size.max, color=factor(stageRGR))))+
+                        ggplot(sd,aes(x= size.mean.range, y=id, xmin = size.min, xmax= size.max, color=factor(stageRGR), lty=factor(life.form))))+
                         geom_vline(xintercept = 10, color = "grey", lty=5)
 
   p_height<- plot_stage("b)", xlab= "height (m)",
-                        ggplot(sh,aes(x= size.mean.range, y=id, xmin = size.min, xmax= size.max, color=factor(stageRGR)))) +
[…]

### 2015-07-16 R/model.R

@@ -99,6 +99,202 @@ fun_model <- function(x, y) {
   CoefModel
 }
 
+fun_model2 <- function(x) {
+  # models for x ('ideal' dataset) and y ('complete' datatset)
+  null <- lmer(corr.z ~ 1 + (1 | id), data = x, weights = nb.sp, REML = TRUE, 
+               control = lmerControl(check.nobs.vs.nlev = "ignore", check.nobs.vs.rankZ = "ignore", 
+                                     check.nobs.vs.nRE = "ignore"))  # modele null cad sans la variable que je veux analyser
+  m <- lmer(corr.z ~ stage + (1 | id), data = x, weights = nb.sp, REML = TRUE, 
+            control = lmerControl(check.nobs.vs.nlev = "ignore", check.nobs.vs.rankZ = "ignore", 
+                                  check.nobs.vs.nRE = "ignore"))  # model avec la variable
+  m1 <- lmer(corr.z ~ stage - 1 + (1 | id), data = x, weights = nb.sp, REML = TRUE, 
+             control = lmerControl(check.nobs.vs.nlev = "ignore", check.nobs.vs.rankZ = "ignore", 
+                                   check.nobs.vs.nRE = "ignore"))  # model avec les intercepts qui sont a 1
+  
+  summ.m <- summary(m)
+  
+  # extraction intercept of fixed parameters
+  FP <- as.data.frame(fixef(m1))
+  FP["stage"] <- "NA"
+  FP["stage"] <- names(fixef(m1))
+  
+  FixSEdiag <- vcov(m1, useScale = FALSE)
+  FixSE <- as.data.frame(sqrt(diag(FixSEdiag)))
+  FixSE["stage"] <- "NA"
+  FixSE["stage"] <- names(fixef(m1))
+  
+ 
+  # new table with extracted data from models
+  l <- (length(FP$stage)) 
+  l1 <- (length(FP$stage))
+  
+  a <- (l1 + 1)
+  
+  name <- list(1:l, c("stage", "stress", "Inte", "SE", "CIupper", "CIlower"))
+  CoefModel <- as.data.frame(matrix(nrow = length(name[[1]]), ncol = length(name[[2]]), 
+                                    dimnames = name))
+  CoefModel[1:l1, 1] <- c((FP$stage))
+  CoefModel[1:l1, 2] <- "raw"
+
+  
+  for (i in 1:l1) {
+    CoefModel[i, 3] <- FP[i, 1]
+    CoefModel[i, 4] <- FixSE[i, 1]
[…]

### 2015-07-16 R/plots.R

@@ -85,7 +85,9 @@ plot_stage <- function(title, xlab, ggobj, ylab = "ID") {
     scale_colour_manual(limits = c("seedling", "juvenile", "sapling", "adult",
       "mix"), values = c(seedling = "green", juvenile = "blue", sapling = "orange",
       adult = "red", mix = "grey"), name = "stage", breaks = c("seedling",
-      "juvenile", "sapling", "adult", "mix")) + theme(axis.text = element_text(size = 6),
+      "juvenile", "sapling", "adult", "mix"))+
+    scale_linetype_manual(limits=c("tree","woody","mix"), values=c("solid","dashed","dotted"), name="life.form",breaks=c("tree","woody","mix"))+
+    theme(axis.text = element_text(size = 6),
     legend.position = "none")
   p
 }
@@ -221,6 +223,84 @@ coeff.plot.multiple <- function(data, params, labels = NA, xlab = "Effect size (
   box()
   text(paste("n=", rev(List_N)), x = dat$lower - 0.5, y = seq_len(nrow(dat)),
     cex = 0.5)
+  text(paste("AIC=", aic$value), x = aic$x, y = aic$y, cex = 0.7)
+  mtext(xlab, side = 1, line = 0.5, cex = 0.8)
+  mtext(title, side = 3, line = 0.5, cex = 0.9, at = 0.5)
+}
+
+
+coeff.plot.multiple2 <- function(data, params, labels = NA, xlab = "Effect size (z) +CI 95%",
+                                title = "") {
+  # creation d une liste avec le nombre de valeurs dans chaque categories
+  # (seedling, sapling etc.)
+  fun_List_N <- function(data) {c(
+    length(na.omit(data$coef[data$stage == "juvenile"])),
+    length(na.omit(data$coef[data$stage == "sapling"])),
+    length(na.omit(data$coef[data$stage == "adult"])),
+    length(na.omit(data$coef[data$growth == "AbGR"])),
+    length(na.omit(data$coef[data$growth == "RGR"])),
+    length(na.omit(data$coef[data$measurement == "Height"])),
+    length(na.omit(data$coef[data$measurement == "Mass"])),
+    length(na.omit(data$coef[data$measurement == "Diameter"])),
+    length(na.omit(data$coef[data$measurement == "Other"]))
+  )}
+  
+  
+  fun_AICm <- function(data) {
+    # modele null cad sans la variable que je veux analyser
[…]

### 2015-07-16 analysis.R

@@ -9,6 +9,7 @@ library(ape)
 library(boot)
 library(Hmisc)
 library(plyr)
+library(stringr) # Trim whitespace from start and end of string
 
 library(metafor)
 library(ade4, quietly=TRUE)
@@ -89,7 +90,7 @@ dev.off()
 
 
 pdf("output/FigA6.pdf",height=6,width=5)
-figure_2(GC, GIi)
+  figure_A6(GC)
 dev.off()
 
 
@@ -128,6 +129,27 @@ dev.off()
 
 pdf("output/FigA10.pdf")
   figure_A10(GC)
+dev.off()
+
+
+pdf("output/FigA11a.pdf")
+figure_A11(GIi, GC, "SLA", c("a","b"))
+dev.off()
+
+pdf("output/FigA11b.pdf")
+figure_A11(GIi, GC, "WD", c("c","d"))
+dev.off()
+
+pdf("output/FigA11c.pdf")
+figure_A11(GIi, GC, "Hmax",  c("e","f"))
+dev.off()
+
+pdf("output/FigA11d.pdf")
+figure_A11(GIi, GC, "Seedmass", c("g","h"))
+dev.off()
+
+pdf("output/FigA11e.pdf")
+figure_A11(GIi, GC, "Aarea", c("i","j"))
 dev.off()
 
 # Reference list

### 2015-07-30 MS.tex
Change according to reviwers comments (different graph and new paragraph)

--- 2015-07-15 MS.tex
@@
 Traits should influence growth in a way that depend on individual plants size.
-We outline mechanisms and hypotheses based on new theory, and test these predictions for five traits using a meta-analysis of 112 studies (\textgreater{} 500 correlations).
+We outline mechanisms and hypotheses based on new theory, and test these predictions in tree species for five traits using a meta-analysis of 112 studies (> 500 correlations).
 
@@
 
-Meanwhile the possibility has been raised that trait-growth correlations may change systematically with size \citep{Falster:2011ii, Ruger:2012jv, Iida:2014ep, Iida:2014hq}.
-Recent theory suggests that the absence of a correlation between SLA and growth at larger sizes may be expected, when  potential influences of traits on plant function are considered \citep{Falster:2011ii, falster:2013}.
+Meanwhile the possibility has been raised that trait-growth correlations may change systematically with size \citep{Falster:2011ii, Ruger:2012jv, Iida:2014ep, Iida:2014hq}.ADD REF  Recent theory suggests that the absence of a correlation between SLA and growth at larger sizes may be expected, when potential influences of traits on plant function are considered \citep{Falster:2011ii, falster:2013}.
 At larger sizes the low-cost deployment benefits of high SLA may be offset or even outweighed by the high costs of rapid leaf turnover (see Text Box 1\ref{sec:growth}).
 
-Here, we review published literature reporting on relationships between
-plant growth and five prominent traits (specific leaf area = SLA, wood or stem tissue density = WD, maximum leaf photosynthetic capacity per unit area = Aarea,  maximum height= Hmax, and seed mass= SM), in order to assess the following questions.
+Here, we review published literature reporting on relationships between plant growth and five prominent traits (specific leaf area = SLA, wood or stem tissue density = WD, maximum leaf photosynthetic capacity per unit area = Aarea,  maximum height= Hmax, and seed mass= SM) in tree or woody species in order to assess the following questions.
 
@@
 The main effect of increased seed size is to produce a larger overall seedling.
-Generally relative growth rate decreases with size, and as such larger seedlings are predicted to have a lower relative growth rate during the earliest phases of growth \citet{Turnbull:2012ew}.
+Generally relative growth rate decreases with size (REF Enquist et al 1999 Nature, Tilman 1988?), and as such larger seedlings are predicted to have a lower relative growth rate during the earliest phases of growth \citet{Turnbull:2012ew}.
 However, among larger plants we expect the effect of this initial size to be minimal, and thus the correlation between seed size and growth rate should disappear.
@@
 
+\textbf{Effect on absolute (AbsGR) and relative growth rate (RGR}
+Tree growth is the increase in dimensions (i.e.
+diameter, height or mass) of an individual tree through time.
+While plant functional traits measurements are standardized across plant ontogeny, plant growth is commonly expressed differently according to the plant size/stage considered.
+Thus, mass and height are both used for smaller plants, whereas height and diamater are more convenient measures for larger tree.
+In addition, the growth increment (i.e.
+rate of change of a dimension per unit time) can be expressed in either absolute or relative terms.
+Relative growth rate (RGR, the change in a dimension per time interval relative to initial size) is commonly used for smaller plants, but is less useful for larger-plants because there is a very rapid decline in RGR with increasing tree size due to accumulation of support tissues (bark, branches etc).
+According to the growth model, the correlation between trait and growth is predicted to revert according to the growth measurement used, for both SLA and seed mass (TABLE?).
+The predicted relationship between growth and either SLA or seed mass in seedlings differs if absolute growth rate in mass is used instead of $RGR_{mass}$ (i.e.
+becomes negative for SLA, positive for SM).
+
 \section*{Materials and methods}\label{material-and-methods}
@@
 We aimed to identify studies that measured the correlation between a functional trait and a growth measurement, and searched for relevant studies using a three step procedure.
-First, we identified traits for which a substantial number of studies would be available, using a literature snapshot in Web of Science.
+First, we identified traits for which a substantial number of studies would be available using a literature snapshot in Web of Science.
 While Web of Science guarantees a relatively stable and reproducible search environment, with clearly defined lists of indexed journals, its searches are restricted to metadata, such as title, keywords and abstracts \citep{Beckmann:2012hn}.
@@
 Thus, our second step was to systematically read documents returned by Google scholar for a restricted set of traits.
-Finally, we identified and recorded other possible data sources using our own knowledge as researchers in the field.
-(This included adding data from an as-yet unpublished study by Gleason et al).
+Finally, we identified and recorded other possible data sources using our own knowledge as researchers in the field (this included adding data from an as-yet unpublished study by Gleason et al).
 The complete list of studies where we inspected the full text is given in Appendix \ref{app:supp_info_files} in Supplementary material.
@@
 We focused on an initial list of 20 traits (Fig.
-\ref{Fig1}): the five for which we had prior expectations, plus 15 others which capture different aspects of plant species strategies.
+\ref{Fig1}) which capture different aspects of plant species strategies.
 Specific leaf area (SLA), leaf area, leaf nitrogen and phosphorus concentration, net (mass) assimilation rates (NAR), and assimilation rate of CO$_2$ (Aarea) are traits involved in species leaf economic strategy \citep{Wright:2004jb,Wright:2010tp}.
@@
 
-Across the 112 article used in our meta-analyses, plants were categorized into four stages according to the expertise and the apprciation of the authors (i.e.seedling, juvenile, sapling, adult). 
-While by compiling data across multiple studies there is a risk of assigning plants of similar size to different categories, the thershold size is standardized for a plant stage across the 112 studies ().
+While it would be more appropriate to address plant size as a continous variable, the limited quantity of data available in the literature steered us to focus on plant size as a categorical variable (i.e.
+plant stages).
+The authors of the 112 articles reported in our meta-analyses, categorized plants into four differents stages (i.e.
+seedling, juvenile, sapling, adult).
+They also reported plant size informations in diameter, height or age; generally the authors give the size of the smallest and the biggest plants species used in their analyses.
+While the stage categories have been established according to the expertise and the appreciation of the authors, by compiling data across multiple studies and across different growth form (tree, woody, etc), there is a risk of assigning plants of similar size to different categories.
+Thus, we tested how consistent were the range values in size/age attributed to each stage across the 112 studies, and across the different growth form (tree, woody and across growth form, Fig.
+A1).
+Suprisingly, the threshold in size/age used by the authors to defined a plant stage are quite steady across the 112 studies (Fig.
+A1).
+In particular, there was a clear break between seedlings and saplings in both age (at 1 yr) and height (at 0.5 m); there was also a clear break between saplings and adults in diameter (at 10 cm).
+The distinctions between sapling-adult in age (around 5 yrs) and height (around 2 m), and between seedling-sapling in diameter (around 1cm) were less pronounced.
+We used simple allometric relationships from the Biomass And Allometry Database (BAAD) \citep{Falster:2015} to ensure that these size/stage cutoffs match across the different size measurements (i.e.
+diameter, height and age, Fig.
+A2).
+For instance, we showed according to BAAD that a sapling with a diameter < 10 cm would have a height < 1 m.
+Thus, according to the size/stage threshold established across 112 studies, the plant will be assigned to the sapling stage whatever we focused on its diamter or height (see Fig.
+A2 c).
 
-When the stage information was not explicitly given, data were recorded as 'mix'.
+There were an ambiguity on the plant stage attribution for less than 5\% of the studies (i.e.
+5 studies on 112).
+We re-red carefully each of these studies, looking at any particular reason addressed by authors that could explained these discrepancies.
+Interestingly, these discrepancies were not due to a differences between growth form; all the ambiguous cases corresponds to studies focusing exclusively on tree species (Fig.
+A1).
+In fact, we identified two main explanations.
+First, the term "juvenile" was vague enough to cover either seedling or sapling stages according to the authors.
+Second, the reproductive state of a plant is not strictly correlated to plant size; some plants with a large stature are not assessed as adult because the authors selected them to be non reproductive (See ID 50, 52 and 105 in Fig.
+A1).
+Thus, we attributed a study to a new stage category when 95\% of the recorded range of sizes for that study lay within a new category.
+And, we attributed a study to the adult stage when the authors identified the plants as reproductive regardless the plant size or age.
+The size/stage threshold defined across the 112 articles, allowed us to attribute straightforwardly a stage category to studies for which no stage have been distinctly mentionned by the authors (5\% of the data, noted as 'mix' in Fig.
+A1).
+Finally, we run the analyses with both the old and the standardized categories to ensure that the different stage attribution will not disturb our results.
 
-Second, we re-assigned plants to three stage categories ("juvenile", "sapling" and "adult") according to size and age cutoffs established by looking at the range values observed across all the 112 studies (Fig.
-\ref{FigA1}).
-We preferred the term "juvenile" to "seedling", because for a portion of the scientific community "seedling" also refers to a particular experimental condition (a greenhouse experiment).
-Overall, the different studies were largely consistent in their classification of plants into "juvenile", "sapling" and "adult" groups  (Fig.
-\ref{FigA1}).
-In particular, there was a clear break between juveniles and saplings in both age (at 1 yr) and height (at 0.5m); there was also a clear break between saplings and adults in diameter (at 10cm).
-The distinctions between sapling-adult in age and height, and between seedling-sapling in diameter were less pronounced.
-To ensure consistency across studies we used simple allometric relationships from the Biomass And Allometry Database (BAAD) \citep{Falster:2015} to match between age, diameter and height ranges for each stage category (Fig.
-\ref{FigA2}).
-
-Thus, we established the following rules: i) `juveniles' are plants of {[}0,0.5) m in height , or {[}0,0.2{]} cm in diameter, or $\leq$ 1 yrs old; ii) `saplings' are plants of {[}0.5-5{]} m , or (0.2,10{]} cm in diameter, or (1-30{]} yrs, and iii) `adult' are plants \textgreater{}5 m in height, or \textgreater{}10 cm in diameter, or \textgreater{} 30 yrs and/or in the reproductive stage.
-We attributed the study to a new stage category when 95\% of the recorded range of sizes for that study lay within the new category.
-We attributed a study to the adult stage when the authors identified the plants as reproductive regardless the plant size or age.
-
-In the main text we report the results using the second approach, i.e. standardized categories. Results using the first approach are similar and are available in Fig. \ref{FigA8}.
+Results using the categories established by the authors are similar than the one using the standardized categories and are available in Fig.
+A8.
+In the main text, we report the results using the standardized categories.
+In the rest of the mansucript, we preferred the term "juvenile" to "seedling", because for a portion of the scientific community "seedling" also refers to a particular experimental condition (a greenhouse experiment).
 
@@
 
-We tested size/stage effect on traits for which \textgreater{}20 correlation coefficients across at least two stages were recorded.
+We tested size/stage effect on traits for which > 15 correlation coefficients across at least two stages were recorded.
 We used a mixed-effect model of meta-analysis, in which it is assumed that studies within a stage share a common mean effect but that there is also random variation among studies in a stage, in addition to sampling variation.
@@
 Effects of other variables (vegetation type, experiment type and growth measurement) were also tested individually (results shown in the Fig.
-\ref{FigA8}).
+A8).
 Estimates of the effect size for each stage were considered significant if the 95\% confidence intervals did not overlap with zero.
@@
 Finally, we checked the dataset for publication bias with funnel plots (\citealt{Koricheva:2013tz}, Fig.
-\ref{FigA9}).
+A9).
 A publication bias toward significant results creates an asymmetric funnel with small studies with non-significant effects missing from the mouth of the funnel on the side opposite to the true effect.
-In addition, to avoid publication bias due to selective reporting of significant results within published articles (e.g.~particular case of a `failure to publish bias' see \citealt{Jennions:2013ta}), we asked the authors for additional information when they reported a non-significant correlation between growth and trait without reporting an r value.
+In addition, to avoid publication bias due to selective reporting of significant results within published articles (e.g.~particular case of a 'failure to publish bias' see \citealt{Jennions:2013ta}), we asked the authors for additional information when they reported a non-significant correlation between growth and trait without reporting an r value.
 
@@
 \ref{Fig2} a and d; average values for the coefficients r ($r_{\textrm{mean}}$) in Fig.
-\ref{FigA5}).
+A5).
 The correlation between growth and SLA shifted from strongly positive at juvenile stage $r_{\textrm{mean}}=0.6 \pm 0.08$, Mean +SD) to not significantly different from zero at adult stage ($r_{\textrm{mean}}= -0.01 \pm 0.07$, CI 95\% overlapping zero in Fig.
@@
 Given our basic conclusion that reported correlations responded to plant size in a manner consistent with expectations from theory, we assess now the coverage of the available data, to determine if biased sampling could have erroneously generated the above results.
-The results reported were confined to correlations across species and under non-stressed conditions.
-A "complete" dataset (n=328 vs n=198) also included correlations measured at within-species level, and under stressed conditions, and spanning different plant stages.
+The results reported were confined to correlations across species, and under non-stressed conditions (n=176).
+A "complete" dataset (n=216) also included correlations measured under stressed conditions, and spanning different plant stages between the growth and trait measurements.
 This "complete" dataset generated similar effect sizes to those reported above from the "ideal" dataset, and led to similar conclusions (Fig.
@@
 Finally, our results were unlikely to be biased by dominance of one or a few studies that measured a large number of responses, since when multiple responses were condensed into a single average within a trait and within a study, outcomes were very similar (Fig.
-\ref{FigA7}) .
+A7).
+While we were mainly interested by the relationships between traits and growth across species, around 9 percent of the litterature reports a correlation measured within species.
+The number of correlations recorded is too few to test our hypotheses at within species level.
+Yet, a 'raw' dataset (n=263) including correlations across and within species and under both non-stressed and all conditions generated similar results to those reported across species exclusively (Fig.
+A6).
 
@@
 Climate zones spanned from temperate regions to  tropics (map in Fig.
-\ref{FigA3}).
+A3).
 Different experiment types (laboratory, field, plantation or greenhouse) and growth measurements were included (see Fig.
-\ref{FigA8} for analyses of how these factors affected  correlations between growth and traits).
+A8 for analyses of how these factors affected  correlations between growth and traits).
 Given this variety, it was not surprising to find wide ranges of r reported for all traits.
 For instance,  r varied from -0.98 to 0.99 for SLA, and from -0.74 to 0.74 for WD (Fig.
-\ref{FigA4}).
+A4).
 Number of species used for each correlation ranged from 1 to 300 species with average  31.
 As expected the correlation coefficient varied less widely as sample size increased (funnel plots Fig.
-\ref{FigA9}).
+A9).
 In the analyses described in Figs 2, A5 and A6 coefficients were weighted according to sample size, making the small-sample extremes less influential.
 Funnel plots exhibited a typical funnel shape for all five functional traits analyzed, showing no evidence for publication bias (Fig.
-\ref{FigA9}).
+A9).
 
@@
 The meta-analysis reported here demonstrates that the influence of traits on growth rates changes as plants grow from small to large, for several key traits.
-Plant growth rates change with size through ontogeny  \citep{Condit:1993hd, Clark:1999ed, Herault:2011dd} - \textit{they follow a trajectory of growth} - and species traits should be understood as influencing this trajectory and consequently rearranging the ranking of growth rates with size, rather than as rendering species fast-growing or slow-growing throughout life.
+While this point has been made recently in smaller scale studies, it is the first time that mechanistic hypotheses are confirmed across a large number of studies.
+Meta-analysis allowed us to generalize about trait influences on growth using the literature already available on traits.
+Thus, plant growth rates change with size through ontogeny \citep{Condit:1993hd, Clark:1999ed, Herault:2011dd} - \textit{they follow a trajectory of growth} - and species traits should be understood as influencing this trajectory and consequently rearranging the ranking of growth rates with size, rather than as rendering species fast-growing or slow-growing throughout life.
 
@@
 It has previously been noted that the correlation of SLA with growth disappears among saplings and larger trees (\citealt{Wright:2010tp} for Barro Colorado Island forest, Panama), and this meta-analysis generalises that result.
-Several authors have suggested that the disappearance of SLA's influence on growth is associated with increasing total leaf area \citep{Reich:1992wm,Poorter:2008iu,Wright:2010tp}.
-In the model described here, the mechanism is slightly different: high-SLA species incur faster leaf and other tissues turnovers, the cost of which outweighs the benefits of cheap leaf construction at larger sizes.
+Several authors have suggested that the disappearance of SLA's influence on growth might be due to a disproportionate accumulation of leaf area by low SLA species \citep{Reich:1992wm,Poorter:2008iu,Wright:2010tp}, yet it remain uncear whether such a mechanism works as intended.
+More importantly, the assumed empirical relationship between SLA and total leaf area does not hold true across large number of species (Duursma and Falster, in review).In the model described here, the mechanism is slightly different: high-SLA species incur faster leaf and other tissues turnovers, the cost of which outweighs the benefits of cheap leaf construction at larger sizes.
 
@@
 \includegraphics{output/Fig1.pdf}
-\caption{\textbf{Number of correlations between trait and growth for each plant stage recorded in our dataset.} Shown here are \textcolor{red}{'raw} dataset' (recorded at both interspecific and intraspecific level, under unstressed and stressed conditions).
+\caption{Number of correlations between trait and growth for each plant stage recorded in our dataset.
+Shown here are 'raw dataset' (recorded both across and within species, under unstressed and stressed conditions).
 Bar colors: red for adult, orange for sapling, grey for juvenile.
@@
 \includegraphics{output/Fig2.pdf}
-\caption{\textbf{The relationship between growth rates and SLA or seed mass changes with plant stage.} Plots show the effect size (+ 95\%CI) of the correlation \textcolor{red}{across species} between growth rate and five functional traits for plant stage comparisons.
+\caption{The relationship between growth rates and SLA or seed mass changes with plant stage.
+Plots show the effect size (+ 95\%CI) of the correlation across species between growth rate and five functional traits for plant stage comparisons.
 \textbf{a)} Specific leaf area (SLA), \textbf{b)} Wood density (WD), \textbf{c)} Asymptotic height (Hmax) \textbf{d)} Seed mass and \textbf{e)} Assimilation rate of CO2 (Aarea).
@@
 Effects are significant if confidence intervals (95\%CI) for a given stage do not overlap with zero.
-Black point: ideal data (under unstressed conditions), grey points: all the data.
+Shown here are 'across species dataset' (recorded only across species, and under both unstressed and stressed conditions).
+Black point: unstressed conditions, grey points: all the data.
 'n' indicates number of correlations contributing to each effect.
-Likelihood Ratio Tests (LRT, for ideal data only) compared maximum-likelihood fits between a pooled model and one separated by stage.
+Likelihood Ratio Tests (LRT, for unstressed conditions only) compared maximum-likelihood fits between a pooled model and one separated by stage.
 A significant p-value means the stage model fitted the data better than the null model.
@@
 
-\begin{itemize}
-  \item "code.zip": the data and analysis code used to generate the results in this paper. A copy of the complete data set is also available from the Dryad Digital Repository.
-\end{itemize}
+"code.zip": the data and analysis code used to generate the results in this paper. A copy of the complete data set is also available from the Dryad Digital Repository.
 
@@
 \includegraphics{output/FigA1.pdf}
-\caption{\textbf{Range of plant size in \textbf{a)} age, \textbf{b)} height and \textbf{c)} diameter and their assigned plant stage} Each segment represents the plant size range addressed in our dataset.
+\caption{Range of plant size in \textbf{a)} age, \textbf{b)} height and \textbf{c)} diameter and the plant stage assigned by the authors of the articles used in the meta-analyses.
+Each segment represents the plant size range (max and min values) of the species used to measure the correlation between growth and traits in each article.
 ID is the reference number of the article in our dataset.
-The colors represents the stage information given by the authors (green: seedling, blue:juvenile, orange: sapling, red: adult, grey: mix), and the vertical line the limit we choose to established our stage categories.
-Shown here are the \textcolor{red}{"raw} dataset" (recorded at both interspecific and intraspecific level and under unstressed and stressed conditions).
-}
+The colors represents the stage information given by the authors (green: seedling, blue: juvenile, orange: sapling, red: adult, grey: unspecified by the authors), the vertical line represents the most likely limits between stage categories, the horizontal line styles corresponds to the species growth form used in each study (solid line: exclusively tree, dashed line: woody species , dotted line: tree mixed with another growth form).
+Shown here are the "raw dataset" (recorded both across and within species, and under unstressed and stressed conditions).}
 \label{FigA1}
@@
 \includegraphics{output/FigA2.pdf}
-\caption{\textbf{Allometric relationships between a) age and diameter (m), b) age and height (m), and c) diameter and height in trees according to the BAAD database}.
-Green and red lines are the cutoffs between stage categories used in the meta-analyses.
+\caption{Allometric relationships between a) age and diameter (m), b) age and height (m), and c) diameter and height in trees according to the BAAD database.
+Green and red lines are the cutoffs between stage categories used in the literature.
 Green lines corresponds to limits between juveniles and saplings, red lines to limits between saplings and adults.}
@@
 \includegraphics{output/FigA3.pdf}
-\caption{\textbf{Geographical distribution of site locations from studies performed in the field used in the meta-analysis.} Shown here are the \textcolor{red}{"raw} dataset" (recorded at both interspecific and intraspecific level and under unstressed and stressed conditions).}
+\caption{Geographical distribution of site locations from studies performed in the field used in the meta-analysis.
+Shown here are the "raw dataset" (recorded both across and within species, and under unstressed and stressed conditions).}
 \label{FigA3}
@@
 \includegraphics{output/FigA4.pdf}
-\caption{\textbf{Range of the correlation of correlations (r) between
-growth and trait \textcolor{red}{from 112 articles}.} Coefficients of correlation (r)
+\caption{Range of correlations (r) between
+growth and trait reported in the literature (112 articles). Plots shown the coefficients of correlation (r)
 between the plant growth and \textbf{a)} Specific leaf area (SLA, n=
@@
 \textbf{e)} Rate of CO2 assimilation (Aarea, n=24) reported from 112
-articles. \textcolor{red} {The x abcissa represents the articles sorted by the average coefficient value r reported}.
-Shown here are the \textcolor{red}{"raw} dataset" (recorded at both interspecific
-and intraspecific level and under unstressed and stressed conditions). Each bubble represents a r value, the diameter of the bubble
-is proportional to its weights in the meta-analysis. The colors
+articles. The x abcissa represents the articles ID sorted by the average coefficient value r reported.
+Shown here are the "raw dataset" (recorded both across and within species
+and under unstressed and stressed conditions). Each bubble represents a r value, the diameter of the bubble
+is proportional to its weights in the meta-analysis (i.e. number of species used). The colors
 correspond to the stage for which the r values have been recorded: red
 points corresponds adult stage, orange points to saplings, and grey
-points to juveniles. the \textcolor{red}{The x abciss represents the study ID} }
+points to juveniles.}
 \label{FigA4}
@@
 \includegraphics{output/FigA5.pdf}
-\caption{\textbf{Mean coefficient correlation r (+SD) between growth
-rate and traits, established from 112 articles.} The mean
-coefficients are weighted by sample size (i.e number of species used to
-perform the correlation), and calculated both across all plant stages
-and for each stage. Each panel corresponds to a functional trait:
-\textbf{a)} Specific leaf area (SLA), \textbf{b)} Wood density (WD),
-\textbf{c)} Net assimilation rate (NARarea), \textbf{d)} Seed mass,
-\textbf{e)} Asymptotic height (Hmax) and \textbf{f)} Assimilation rate
-of CO2 (Aarea). Shown here are ideal dataset (recorded at interspecific level and under unstressed conditions)}
+\caption{\textbf{Mean coefficient correlation r (+SD) between growth rate and traits, established from 112 articles.} The mean coefficients are weighted by sample size (i.e number of species used to perform the correlation), and calculated both across all plant stages and for each stage.
+Each panel corresponds to a functional trait: \textbf{a)} Specific leaf area (SLA), \textbf{b)} Wood density (WD), \textbf{c)} Net assimilation rate (NARarea), \textbf{d)} Seed mass, \textbf{e)} Asymptotic height (Hmax) and \textbf{f)} Assimilation rate of CO2 (Aarea).
+Shown here are the "unstressed dataset" (recorded across species and under unstressed conditions).}
 \label{FigA5}
@@
 \includegraphics{output/FigA6.pdf}
-\caption{\textbf{Effect size (+ 95\%CI) of plant stage on the
-correlations between growth rate and five functional traits \textcolor{red}{across and between species}} Effects size are calculated for a) Specific leaf area (SLA), b) Wood density (WD), c) Net assimilation rate (NARarea), d) Seed mass, e) Asymptotic height (Hmax) and f) Assimilation rate of CO2 (Aarea).
+\caption{Effect size (+ 95\%CI) of plant stage on the correlations between growth rate and five functional traits across and between species.
+Effects size are calculated for a) Specific leaf area (SLA), b) Wood density (WD), c) Net assimilation rate (NARarea), d) Seed mass, e) Asymptotic height (Hmax) and f) Assimilation rate of CO2 (Aarea).
 Effect size is a standardized measure of the magnitude of the relationship between a particular stage and the correlation coefficient z (Fisher's z-transformed).
@@
 LRT: likelihood Ratio Test compared the fit between null model and stage model, both models are fitted by Maximum Likelihood.
-Black point: ideal data (at interspecific level and under unstressed conditions), grey points: raw data (at both intra and interspecific level and under both stress and unstressed conditions).
+Shown here are the "raw dataset" (recorded both across and within species and under unstressed and stressed conditions).
 'n' indicate the number of independent comparisons for each effect.
@@
 \includegraphics{output/FigA7.pdf}
-\caption{\textbf{Effect size (+ 95\%CI) of plant stage on the
-correlations between growth rate and five functional traits \textcolor{red}{across species}, with a data set averaging multiple comparisons by trait and by study.} Effects size are calculated from a reduced dataset; in the case of multiple comparisons within a study, we calculated the mean correlation coefficient by trait and by study.
+\caption{\textbf{Effect size (+ 95\%CI) of plant stage on the correlations between growth rate and five functional traits across species, with a data set averaging multiple comparisons by trait and by study.} Effects size are calculated from a reduced dataset; in the case of multiple comparisons within a study, we calculated the mean correlation coefficient by trait and by study.
 a) Specific leaf area (SLA), b) Wood density (WD), c) Net assimilation rate (NARarea), d) Seed mass, e) Asymptotic height (Hmax) and f) Assimilation rate of CO2 (Aarea).
@@
 \includegraphics{output/FigA10.pdf}
-\caption{\textbf{Growth measurement used by traits and by size.} Shown here are complete dataset (recorded at both interspecific and intraspecific level and under unstressed and stressed conditions).
+\caption{\textbf{Growth measurement used by traits and by size.} Shown here are complete dataset (recorded at both across and within species and under unstressed and stressed conditions).
 The colors correspond to the stage for which the r values have been recorded: red bars corresponds adult stage, orange bars to saplings, and grey bars to juveniles.}

### 2015-07-30 R/data_processing.R

@@ -40,6 +40,8 @@ clean_raw_data <- function(filename = "data/CompileData.csv") {
   Table$growth[Table$RGR %in% c("RGR(?)","RGR(CSAi)","RGR(Di)","RGR(Hi)","RGR(Mi)","RGR(Vi)")] <- "RGR"
   Table$growth[Table$RGR %in% c("GR(Di)","GR(Hi)","GR(Mi)","GR(Shoot)")] <- "AbGR"
 
+  Table$growth <- factor(Table$growth, levels = c("RGR", "AbGR"))
+  Table$growth <- as.factor(Table$growth)
   
   Table["measurement"] <- "NA"
   Table$measurement[Table$RGR %in% c("RGR(Di)","GR(Di)")] <- "Diameter"
@@ -47,8 +49,12 @@ clean_raw_data <- function(filename = "data/CompileData.csv") {
   Table$measurement[Table$RGR %in% c("RGR(Mi)","GR(Mi)","GR(Shoot)")] <- "Mass"
   Table$measurement[Table$RGR %in% c("RGR(?)","RGR(Vi)","RGR(CSAi)")] <- "Other"
   
+  Table["growth.form"] <- "NA"
+  Table$growth.form[Table$life.form %in% c("tree", "tree ")] <- "tree"
+  Table$growth.form[Table$life.form %in% c("tree, shrub" , "woody" , "woody and semi-woody", "woody vines")] <- "woody"
+  Table$growth.form[Table$life.form %in% c("liana and tree" , "shrub and tree" , "tree and herbs" , "tree, herbs",  "tree, shrub, herbs" , "woody and herbs", "woody, forbs, herbs" ,"woody, shrub, perennial herbs")] <- "across growth form"
   
-
+  Table$growth.form <- as.factor(Table$growth.form)
   # Nb of species used to performed the correlation
   names(Table)[names(Table) == "nb.sp.reported"] <- "nb.sp"
 
@@ -138,7 +144,7 @@ clean_raw_data <- function(filename = "data/CompileData.csv") {
   Table <- rename(Table, c(stage.simi = "similarity"))
 
   subset(Table, select = c(id, idcor, authors, year, ref, doi, experiment, experiment.coord,
-    stress, life.form, veg.type, bio.scale, nb.sp, location, nb.site, names.s1, names.s2,
[…]

### 2015-07-30 R/figures.R

@@ -171,7 +171,7 @@ figure_2 <- function(GC, GI) {
                    limit.x.n=2.5, vjust.value=1,
                    color1="grey",color2="black") +
     scale_fill_discrete(name="",breaks=c("ideal", "complete"),
-                        labels=c("ideal", "complete"))+
+                        labels=c("ideal"="ideal", "complete"="complete"))+
                   theme (legend.title=element_blank(),
                          legend.justification=c(0,0),
                          legend.position=c(1.2,0.5),
@@ -194,15 +194,15 @@ figure_A1 <- function(CompleteData) {
   sd <- subset(s,s$measure.size=="diameter")
 
   p_diam <-  plot_stage("c)", xlab= "basal diameter (cm)",ylab="",
-                        ggplot(sd,aes(x= size.mean.range, y=id, xmin = size.min, xmax= size.max, color=factor(stageRGR), lty=factor(life.form))))+
+                        ggplot(sd,aes(x= size.mean.range, y=id, xmin = size.min, xmax= size.max, color=factor(stageRGR), lty=factor(growth.form))))+
                         geom_vline(xintercept = 10, color = "grey", lty=5)
 
   p_height<- plot_stage("b)", xlab= "height (m)",
-                        ggplot(sh,aes(x= size.mean.range, y=id, xmin = size.min, xmax= size.max, color=factor(stageRGR), lty=factor(life.form)))) +
+                        ggplot(sh,aes(x= size.mean.range, y=id, xmin = size.min, xmax= size.max, color=factor(stageRGR), lty=factor(growth.form)))) +
                         geom_vline(xintercept = 0.5, color = "grey", lty=5)
 
   p_age <- plot_stage("a)", xlab= "age (yr)",
-                        ggplot(sa,aes(x= size.mean.range, y=id, xmin = size.min, xmax= size.max, color=factor(stageRGR), lty=factor(life.form)))) +
[…]

### 2015-07-30 R/model.R

@@ -175,7 +175,7 @@ fun_model_multiple <- function(x) {
                                      check.nobs.vs.nRE = "ignore", optimizer="bobyqa", check.conv.grad = .makeCC("ignore", tol = 2e-3, relTol = NULL),
                                      check.conv.singular = .makeCC(action = "ignore",  tol = 1e-4),
                                      check.conv.hess = .makeCC(action = "ignore", tol = 1e-6)))  # modele null cad sans la variable que je veux analyser
-  m1 <- lmer(corr.z ~ stage - 1 + (1 | id), data = x, weights = nb.sp, REML = TRUE, 
+  m1 <- lmer(corr.z ~ stageRGR - 1 + (1 | id), data = x, weights = nb.sp, REML = TRUE, 
              control = lmerControl(check.nobs.vs.nlev = "ignore", check.nobs.vs.rankZ = "ignore", 
                                    check.nobs.vs.nRE = "ignore", optimizer="bobyqa", check.conv.grad = .makeCC("ignore", tol = 2e-3, relTol = NULL),
                                    check.conv.singular = .makeCC(action = "ignore",  tol = 1e-4),
@@ -294,6 +294,7 @@ fun_model_multiple2 <- function(x) {
   
   dat
 } 
+
 
 # Weighted correlation
 table_overall.stage <- function(y) {

### 2015-07-30 R/plots.R

@@ -3,9 +3,7 @@ mytheme <- theme_bw() + theme(text = element_text(size = 9, colour = "black"),
   title = element_text(size = 9, hjust = 0), axis.title = element_text(size = 9,
     hjust = 0.5), axis.text = element_text(size = 8), axis.line = element_line(colour = "black"),
   panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.border = element_blank(),
-  panel.background = element_blank(), legend.justification = c(1, 0), legend.position = c(1,
-    0))
-
+  panel.background = element_blank(), legend.justification = c(1, 0), legend.position = c(1,0))
 
 my_plot_1 <- function(title, ggobj, xlab = expression(paste("")), ylab = "Number of correlations extracted") {
   p <- ggobj + geom_bar() + coord_cartesian(ylim = ylim) + coord_flip() + labs(title = title) +
@@ -20,40 +18,38 @@ my_plot_1 <- function(title, ggobj, xlab = expression(paste("")), ylab = "Number
 coeff.plot <- function(data, data.complete, data.ideal, LRT, PVAL, title = "",
   significativite = "", round.value, limit.x.min, limit.x.max, limit.x.text,
   limit.x.n, limit.y.text.l1, limit.y.text.l2, vjust.value, color1, color2) {
-  data.complete["x.coord"] <- limit.x.n
-  data.ideal["x.coord"] <- limit.x.n
+          data.complete["x.coord"] <- limit.x.n
+          
+          data.ideal["x.coord"] <- limit.x.n
+          
+          my_size_effect_plot1 <- function(title, ggobj, xlab = "Effect size + CI (95%) ",
+            ylab = "Stages") {
+            p <- ggobj + labs(title = title) + xlab(xlab) + ylab(ylab) + geom_vline(yintercept = 0,color = "white") + 
+              geom_hline(yintercept = 0, size = 0.3, linetype = "dashed") +
+              scale_x_discrete("stage", limit = c("juvenile", "sapling", "adult")) +
+              coord_flip() + mytheme + theme(legend.position = "none")
+            p }
 
-
-  my_size_effect_plot1 <- function(title, ggobj, xlab = "Effect size + CI (95%) ",
-    ylab = "Stages") {
[…]

### 2015-07-30 analysis.R

@@ -33,7 +33,8 @@ CompleteData <- build_complete_data(RawData)
 CompleteData_inter <- Build_intersp_complete_data (RawData)
 IdealData_inter  <- build_ideal_data(CompleteData)
 CoordTable <- build_map_data(RawData)
-
+IdealData_rgr <- subset(IdealData_inter,IdealData_inter$growth=="RGR")
+IdealData_agr <- subset(IdealData_inter,IdealData_inter$growth=="AbGR")
 ## split datasets by trait - makes a list with named elements
 ## given subset of data for each trait
 list_by_trait <- function(df) {
@@ -43,6 +44,9 @@ list_by_trait <- function(df) {
 GC <- list_by_trait(CompleteData)
 GCi <- list_by_trait(CompleteData_inter)
 GIi <- list_by_trait(IdealData_inter)
+GIrgr <- list_by_trait(IdealData_rgr)
+GIagr <- list_by_trait(IdealData_agr)
+
 
 
 ## Create restricted Dataset: coefficient of correlation are averaged by study and by trait
@@ -66,6 +70,7 @@ pdf("output/Fig2.pdf",height=6,width=5)
   figure_2(GCi, GIi)
 dev.off()
 
+
 pdf("output/FigA1.pdf", height=6)
   figure_A1(CompleteData)
 dev.off()
@@ -88,6 +93,10 @@ pdf("output/FigA5.pdf",height=6,width=5)
   figure_A5(GIi)
 dev.off()
 
+pdf("output/FigA5b.pdf",height=6,width=5)
+figure_A5b(GIrgr, GIagr)
+dev.off()
+
 
 pdf("output/FigA6.pdf",height=6,width=5)
   figure_A6(GC)
@@ -102,7 +111,6 @@ dev.off()
 pdf("output/FigA8a.pdf")
   figure_A8(GIi, GC, "SLA", c("a","b"))
 dev.off()
-
 
 pdf("output/FigA8b.pdf")
   figure_A8(GIi, GC, "WD", c("c","d"))
@@ -122,13 +130,33 @@ pdf("output/FigA8e.pdf")
 dev.off()
 
 
+
+pdf("output/FigA82.a.pdf")
+figure_A8b(GC, "SLA","WD", c("a","b"))
+dev.off()
+
+
+pdf("output/FigA82.b.pdf")
[…]

### 2015-08-04 MS.tex
Heterogenity analysis

@@
 We outline mechanisms and hypotheses based on new theory, and test these predictions in tree species for five traits using a meta-analysis of 112 studies (> 500 correlations).
+As an approximation of plants size, we analysed the shift in the correlations between growth and traits across plant stages.
 
@@
 \section*{Introduction}\label{introduction}
+Plant growth is an important aspect of ecosystem productivity
+Plant species vary considerably in the growth rate they can achieve under favourable growing conditions (Grime and Hunt 1975; Shipley and Keddy 1988; Poorter and Retakes 1990; Lambers and Poorter 1992).
+This variation is important both because potential RGR is an important aspect of ecological performance, and because slow potential RGR is thought to be part of a nexus of adaptations to unfavourable growing conditions (e.g.
+Grime et al.
+1988; Reich et al.
+1992; Chapin et al.
+1993; Aerts and van der Pijl 1993; van der Werf et al.
+1993).
 
@@
 An idea that species strategy differences might involve fast vs slow growth goes back at least to Grime and Hunt \citeyearpar{Grime:1975gr}, who measured a wide spread of relative growth rates for seedlings during early exponential growth under favourable conditions.
-Seedling potential RGR has continued to be used as a major strategy indicator within the Sheffield CSR (Competitor - Stress tolerator - Ruderal) scheme and its "Integrated Screening Program" (e.g.
+Seedling potential relative growth rate (RGR, the change in a mass/height or diamater per time interval relative to initial size) has continued to be used as a major strategy indicator within the CSR (Competitor - Stress tolerator - Ruderal) scheme and its "Integrated Screening Program" (e.g.
 \citealt{grime1979plant, Grime:1997wm}).
-Meanwhile partitioning of seedling RGR into its components showed that specific leaf area (SLA = 1/leaf mass per area LMA) was typically the strongest source of variation between species \citep{Poorter:1989tx}.
+Meanwhile partitioning of seedling RGR into its components (see equation X in Appendix 1) showed that specific leaf area (SLA = 1/leaf mass per area LMA) was typically the strongest source of variation between species \citep{Poorter:1989tx}.
 From the 1990s a new style of "trait ecology" arose whereby measurable traits including SLA were used directly as strategy axes \citep{Westoby:2002ft}.
@@
 rate of change of a dimension per unit time) can be expressed in either absolute or relative terms.
-Relative growth rate (RGR, the change in a dimension per time interval relative to initial size) is commonly used for smaller plants, but is less useful for larger-plants because there is a very rapid decline in RGR with increasing tree size due to accumulation of support tissues (bark, branches etc).
-According to the growth model, the correlation between trait and growth is predicted to revert according to the growth measurement used, for both SLA and seed mass (TABLE?).
+Relative growth rate (RGR) is commonly used for smaller plants, but is less useful for larger-plants because there is a very rapid decline in RGR with increasing tree size due to accumulation of support tissues (bark, branches etc).
+According to the growth model used here, the correlation between trait and growth is predicted to revert according to the growth measurement used for both SLA and seed mass.
 The predicted relationship between growth and either SLA or seed mass in seedlings differs if absolute growth rate in mass is used instead of $RGR_{mass}$ (i.e.
@@
 
-We aimed to identify studies that measured the correlation between a functional trait and a growth measurement, and searched for relevant studies using a three step procedure.
+To test how general is the tendency for correlations between traits and growth rate to vary with plant size, we focused on an initial list of 20 traits (Fig.
+\ref{Fig1}).
+These traits have been selected because they capture different aspects of plant species strategies, and are commonly addressed in the functional traits litterature.
+Specific leaf area (SLA), leaf area, leaf nitrogen and phosphorus concentration, net (mass) assimilation rates (NAR), and assimilation rate of CO$_2$ (Aarea) are traits involved in species leaf economic strategy \citep{Wright:2004jb,Wright:2010tp}.
+Seed mass (SM), and maximum plant height (Hmax) capture information about reproductive strategy \citep{Falster:2005bw,Moles:2006ft}.
+Wood density (WD) and sapwood area per leaf area (SA/LA), vessel size and density, and stem specific conductance are all involved in species wood economic strategy \citep{Chave:2009iy}.
+Here WD and SA/LA are also considered as indicators of stem construction cost \citep{Falster:2011ii}, whereas SLA and leaf thickness capture crucial information about leaf construction cost \citep{Wright:2004jb}.
+Finally, the leaf area ratio and leaf mass ratio are indicators of resource allocation to leaf \citep{Lambers:1992bj}.
+
+We aimed to identify studies that measured the correlation between a functional trait and a growth measurement across species.
+We searched for relevant studies using a three step procedure.
 First, we identified traits for which a substantial number of studies would be available using a literature snapshot in Web of Science.
@@
 
-We focused on an initial list of 20 traits (Fig.
-\ref{Fig1}) which capture different aspects of plant species strategies.
-Specific leaf area (SLA), leaf area, leaf nitrogen and phosphorus concentration, net (mass) assimilation rates (NAR), and assimilation rate of CO$_2$ (Aarea) are traits involved in species leaf economic strategy \citep{Wright:2004jb,Wright:2010tp}.
-Seed mass (SM), and maximum plant height (Hmax) capture information about reproductive strategy \citep{Falster:2005bw,Moles:2006ft}.
-Wood density (WD) and sapwood area per leaf area (SA/LA), vessel size and density, and stem specific conductance are all involved in species wood economic strategy \citep{Chave:2009iy}.
-Here WD and SA/LA are also considered as indicators of stem construction cost \citep{Falster:2011ii}, whereas SLA and leaf thickness capture crucial information about leaf construction cost \citep{Wright:2004jb}.
-Finally, the leaf area ratio and leaf mass ratio are indicators of resource allocation to leaf \citep{Lambers:1992bj}.
-We used the literature snapshot to identify traits which i) were most likely to return a substantial number of articles , and ii) shared a large proportion of their literature list with other traits.
 The Web of Science database (Thomson Reuters) was searched between March and June 2014 using a range of Boolean search terms in English.
-Search terms were as follows: (``NAME'' AND (``growth rate'' OR ``relative growth rate'')) AND (``tree*'' OR ``woody*''), ``NAME'' was one of trait names listed in
-
-\ref{TableA1}.
-According to this snapshot, 62\% of the literature for the 20 traits (or 82\% for the 5 traits for which we have clear predictions) is captured by searching only on two traits: SLA and WD.
+Search terms were as follows: (''NAME'' AND (''growth rate'' OR ''relative growth rate'')) AND (''tree*'' OR ''woody*''), ''NAME'' was one of trait names listed in \ref{TableA1}.
+According to this snapshot, 62\% of the literature for the 20 traits (or 82\% for the 5 traits for which we have clear predictions) is captured by searching only on SLA and WD.
 
@@
 Google Scholar database was searched using the range of Boolean search terms for SLA and WD.
-Search terms were as follows: ((``SLA'' OR ``LMA'' OR ``specific leaf area'' OR ``leaf mass area'' OR ``wood density'' OR ``WD'' OR ``wood specific gravity'' OR ``stem density'' OR ``stem specific density'') AND (``growth rate'' OR ``relative growth rate'')) AND (tree* OR woody*).
+Search terms were as follows: ((''SLA'' OR ''LMA'' OR ''specific leaf area'' OR ''leaf mass area'' OR ''wood density'' OR ''WD'' OR ''wood specific gravity'' OR ''stem density'' OR ''stem specific density'') AND (''growth rate'' OR ''relative growth rate'')) AND (tree* OR woody*).
 The keyword search in Google Scholar returns approx.
@@
 Where available we also recorded the geographic coordinates, number of sites, experiment type (greenhouse, field experiment, forest, shade-house etc.), growth measure (relative or absolute growth rate measured using plant diameter, height or mass), vegetation type, life form (tree, woody or mixed with herbaceous species etc.), biological scale (interspecific, intraspecific or intragenus), and experimental treatments (e.g.~fertilization, shade, salt stress).
-Ultimately data was included from 108 different studies (starred references in bibliography).
+Ultimately data was included from 112 different studies (starred references in bibliography).
+The articles laid aside because they did not meet our criteria are listed in Appendix \ref{app:supp_info_files} in Supplementary material.
 
 The number of species used to perform the correlation, the experimental conditions, and the concordance between stage used to measure trait and growth are clear criteria for assessing the quality of the data for addressing our hypotheses.
-Therefore, we stratified the data set into two subsets: one including exclusively interspecific studies under unstressed conditions ('ideal' dataset), and the other set including all studies ('complete' dataset).
+Therefore, we focused on correlation across species, and we stratified the data set into two subsets: one including exclusively studies under unstressed conditions ('ideal' dataset), and the other set including studies under all conditions ('complete' dataset).
 We excluded from the 'ideal' dataset studies where growth and traits were measured on plants from different stages, unless a particular stage is by definition required to measure a trait such as for seed mass (i.e.
@@
 
-While it would be more appropriate to address plant size as a continous variable, the limited quantity of data available in the literature steered us to focus on plant size as a categorical variable (i.e.
-plant stages).
+We acknowledge that it would be better to address plant size as a continous variable, but the limited number of correlations available in the literature along plant size steered us to focus on plant stage as an approximation.
 The authors of the 112 articles reported in our meta-analyses, categorized plants into four differents stages (i.e.
@@
 For instance, we showed according to BAAD that a sapling with a diameter < 10 cm would have a height < 1 m.
-Thus, according to the size/stage threshold established across 112 studies, the plant will be assigned to the sapling stage whatever we focused on its diamter or height (see Fig.
+Thus, according to the size/stage threshold established across 112 studies, the plant will be assigned to the sapling stage whatever we focused on its diameter or height (see Fig.
 A2 c).
@@
 
-We tested size/stage effect on traits for which > 15 correlation coefficients across at least two stages were recorded.
+We tested stage effect on traits for which > 15 correlation coefficients across at least two stages were recorded.
 We used a mixed-effect model of meta-analysis, in which it is assumed that studies within a stage share a common mean effect but that there is also random variation among studies in a stage, in addition to sampling variation.
@@
 If the log-likelihood test returned a significant p-value, the stage model fitted the data better than the null model.
-Effects of other variables (vegetation type, experiment type and growth measurement) were also tested individually (results shown in the Fig.
-A8).
 Estimates of the effect size for each stage were considered significant if the 95\% confidence intervals did not overlap with zero.
@@
 In addition, to avoid publication bias due to selective reporting of significant results within published articles (e.g.~particular case of a 'failure to publish bias' see \citealt{Jennions:2013ta}), we asked the authors for additional information when they reported a non-significant correlation between growth and trait without reporting an r value.
+Finally, we explored the temporal change im effect size, by testing the effect of year of publication within stage for each trait.
+In Table 2 in Appendix, we reported how and where (i.e in the main text and/or figures) we addressed the 14 methodological quality criteria for meta-analysis listed by Koricheva and Gurevitch (2014).
 
@@
 Differences concerned often the confidence intervals around particular mean effect sizes in Fig.
-2.
+\ref{Fig2}.
 These differences in CI were not easily attributed to any single cause.
@@
 A7).
-While we were mainly interested by the relationships between traits and growth across species, around 9 percent of the litterature reports a correlation measured within species.
-The number of correlations recorded is too few to test our hypotheses at within species level.
-Yet, a 'raw' dataset (n=263) including correlations across and within species and under both non-stressed and all conditions generated similar results to those reported across species exclusively (Fig.
-A6).
 
@@
 A3).
-Different experiment types (laboratory, field, plantation or greenhouse) and growth measurements were included (see Fig.
-A8 for analyses of how these factors affected  correlations between growth and traits).
+Different experiment types (laboratory, field, plantation or greenhouse), growth measurements and growth form (tree, woody or across growth form) were included.
 Given this variety, it was not surprising to find wide ranges of r reported for all traits.
@@
 A4).
-Number of species used for each correlation ranged from 1 to 300 species with average  31.
+The growth form, the experiment types and the growth measurement were not markedly best predictors of the data (results shown in the Fig.
+A8).
+Number of species used for each correlation ranged from 2 to 300 species with average 31.
 As expected the correlation coefficient varied less widely as sample size increased (funnel plots Fig.
@@
 The meta-analysis reported here demonstrates that the influence of traits on growth rates changes as plants grow from small to large, for several key traits.
-While this point has been made recently in smaller scale studies, it is the first time that mechanistic hypotheses are confirmed across a large number of studies.
-Meta-analysis allowed us to generalize about trait influences on growth using the literature already available on traits.
+While this point has been made recently in smaller scale studies, it is the first time that mechanistic hypotheses are confirmed across a large number of studies already available.
+Meta-analysis allowed us to generalize and help to reach a concensus about trait influences on growth.
 Thus, plant growth rates change with size through ontogeny \citep{Condit:1993hd, Clark:1999ed, Herault:2011dd} - \textit{they follow a trajectory of growth} - and species traits should be understood as influencing this trajectory and consequently rearranging the ranking of growth rates with size, rather than as rendering species fast-growing or slow-growing throughout life.
@@
 
+\begin{table}[ht]
+\centering
+\caption{\textbf{Checklist of quality criteria for meta-analysis in ecology developed by Koricheva and Gurevitch (2014)} 
+\label{TableA2}
+\vspace{0.5cm}
+\begin{tabular}{p{3cm}p{3cm}p{8cm}}
+  \hline
+Criteria & Addressed & \\
+  \hline
+Aarea & Photosynthetic rate per area & "photosynthetic rate per area" OR "rate of CO2 assimilation per area" OR "Aarea" OR "Amax" OR "photosynthetic capacity per area" \\
+  Amass & Photosynthetic rate per mass & "photosynthetic rate per mass" OR "rate of CO2 assimilation per mass" OR "Amass" OR "Amax" \\
+  Hmax & Maximum height & "potential height" OR "maximum height" OR "Hmax" \\
+  Ks & Stem specific conductance & "Ks" OR "stem specific conductance" OR "stem hydraulic conductance" OR "sapwood conductance" \\
+  LA & Leaf lamina area & "leaf length" OR "leaf lamina area" OR "leaf width" OR "leaf size" \\
+  LAR & Leaf area ratio & "leaf area ratio" \\
+  LMR & Leaf mass ratio & "leaf mass ratio" OR "leaf mass fraction" \\
+  NARarea & Net assimilation rate per area &  "net assimilation rate per area" OR "rate of dry mass increament per area" OR "NARarea" OR "NAR" \\
+  Narea & Leaf nitrogen content per area & "Narea" OR "nitrogen per area" OR "N/area" OR "leaf nitrogen content per area" OR "LNCarea" OR "leaf nitrogen content" \\
+  NARmass & Net assimilation rate per mass &  "net assimilation rate per mass" OR "rate of dry mass increament per mass" OR "NARmass" OR "NAR" \\
+  Nmass & Leaf nitrogen content per mass & "Nmass" OR "nitrogen per mass" OR "N/mass" OR "leaf nitrogen content per mass" OR "LNCmass" OR "leaf nitrogen content" \\
+  Parea & Leaf phosphorus content per area & "Parea" OR "leaf P" OR  "leaf phosphorus content per area"  OR "leaf phosphorus content" \\
+  Pmass & Leaf phosphorus content per mass & "Pmass" OR "leaf P" OR  "leaf phosphorus content per mass" OR "leaf phosphorus content" \\
+  SA/LA & Sapwood area per leaf area & "sapwood area per leaf area" OR "huber value" OR "leaf area per sapwood area" \\
+  Seed mass & Seed mass & "seed mass" OR "seed size" OR "seed volume" \\
+  SLA & Specific Leaf Area & "leaf mass per area" OR "specific leaf area" OR "leaf construction cost" \\
+  Thickness & Leaf thickness & "leaf thickness"  OR "leaf tissue density" \\
+  Vessel density & Vessel density & "vessel density" OR "stem conduit density" \\
+  Vessel size & Vessel area or diameter & "conduit area" OR "stem conduit area" OR "vessel diameter" OR "vessel size" OR "conduit size"   \\
+  WD & Wood density & "wood density" OR"WD" OR "wood specific gravity" OR "stem density" OR "stem specific density" OR "SSD" \\
+   \hline
+\end{tabular}
+\end{table}
+
+% we conducted two types of analyses to assess the reliability of our meta-analysis.
+First, we estimated heterogeneity using a modified version of the heterogeneity statistic I2 (originally defined by Higgins & Thompson, 2002; see Supporting information for details).
+Heterogeneity estimates the consistency of the results obtained from published stud- ies used in our meta-analysis.
+A low level of heteroge- neity means that discrepancies among the effects reported by the original studies are satisfactorily explained solely by sampling errors and are not the result of different methodologies or species characteris- tics (Higgins & Thompson, 2002; Higgins et al., 2003; Cooper & Hedges, 2009).
+Second, we assessed our data set for signs of publication bias by visually inspecting funnel plots (Sterne et al., 2005) and also by conducting Egger’s regressions (Egger et al., 1997; Peters et al., 2006).
+We applied an Egger’s regression design, modi- fied for lnOR to data points consisting of the residuals of the effect sizes plus their measurement errors
+% a 2012 THE AUTHORS. J. EVOL. BIOL. 25 (2012) 1911–1917
+% JOURNAL OF EVOLUTIONARY BIOLOGY a 2012 EUROPEAN SOCIETY FOR EVOLUTIONARY BIOLOGY
+% Meta-analysis of cost of parental care in birds 1913
+% 1914 E. S. A. SANTOS AND S. NAKAGAWA
+% (Peters et al., 2006; see Supporting information for details). If the intercept of the Egger’s regression is sig- nificantly different from zero, it is evidence of p
+
 \newpage

### 2015-08-04 R/data_processing.R

@@ -7,7 +7,7 @@ clean_raw_data <- function(filename = "data/CompileData.csv") {
    Table[[f]] <- as.factor(Table[[f]])
   }
 
-  for(f in c("size.min","size.max","size.mean.range","sample.size","nb.sp.reported","coef",
+  for(f in c("year","size.min","size.max","size.mean.range","sample.size","nb.sp.reported","coef",
     "RGR.min","RGR.max","trait.min","trait.max")) {
    Table[[f]] <- as.numeric(Table[[f]])
   }
@@ -50,7 +50,7 @@ clean_raw_data <- function(filename = "data/CompileData.csv") {
   Table$measurement[Table$RGR %in% c("RGR(?)","RGR(Vi)","RGR(CSAi)")] <- "Other"
   
   Table["growth.form"] <- "NA"
-  Table$growth.form[Table$life.form %in% c("tree", "tree ")] <- "tree"
+  Table$growth.form[Table$life.form %in% c("tree", "tree ","NA")] <- "tree"
   Table$growth.form[Table$life.form %in% c("tree, shrub" , "woody" , "woody and semi-woody", "woody vines")] <- "woody"
   Table$growth.form[Table$life.form %in% c("liana and tree" , "shrub and tree" , "tree and herbs" , "tree, herbs",  "tree, shrub, herbs" , "woody and herbs", "woody, forbs, herbs" ,"woody, shrub, perennial herbs")] <- "across growth form"
   
@@ -214,7 +214,7 @@ standardise_data <- function(CompileTable) {
   RawData$zscore <- fn_z(RawData$corr.z, RawData$nb.sp)
 
   RawData["vr.z"] <- NA
-  fn_vz <- function(x) 1/(x + 3)
+  fn_vz <- function(x) 1/(x - 3)
   RawData$vr.z <- fn_vz(RawData$nb.sp)
 
   RawData["se.z"] <- NA

### 2015-08-04 R/figures.R

@@ -186,6 +186,106 @@ figure_2 <- function(GC, GI) {
   grid.arrange(p1,p2,p3,p4,p5,ncol=2, nrow=3,widths=c(1.2,1))
 }
 
+figure_8 <- function(GCi, GIi) {
+  CoefModel.SLA<-fun_model3(GIi[["SLA"]],GCi[["SLA"]])
+  CoefModel.SLA["trait"] <- "SLA"
+  CoefModel.SLA.s <- subset(CoefModel.SLA,stress=='complete')
+  CoefModel.SLA.opt <- subset(CoefModel.SLA,stress=='ideal')
+  LRT.sla <- fun_OneLR2(GIi[["SLA"]])
+  LRT.sla.2 <- fun_OneLR2(GCi[["SLA"]])
+  PVAL.sla <- fun_Onepvalue2(GIi[["SLA"]])
+  PVAL.sla.2 <- fun_Onepvalue2(GCi[["SLA"]])
+  
+  CoefModel.WD<-fun_model3(GIi[["WD"]],GCi[["WD"]])
+  CoefModel.WD["trait"] <- "WD"
+  CoefModel.WD.s <- subset(CoefModel.WD,stress=='complete')
+  CoefModel.WD.opt <- subset(CoefModel.WD,stress=='ideal')
+  LRT.wd <- fun_OneLR2(GIi[["WD"]])
+  LRT.wd.2 <- fun_OneLR2(GCi[["WD"]])
+  PVAL.wd <- fun_Onepvalue2(GIi[["WD"]])
+  PVAL.wd.2 <- fun_Onepvalue2(GCi[["WD"]])
+  
+  CoefModel.Hmax<-fun_model3(GIi[["Hmax"]],GCi[["Hmax"]])
+  CoefModel.Hmax["trait"] <- "Hmax"
+  CoefModel.Hmax.s <- subset(CoefModel.Hmax,stress=='complete')
+  CoefModel.Hmax.opt <- subset(CoefModel.Hmax,stress=='ideal')
+  LRT.h <- fun_OneLR2(GIi[["Hmax"]])
+  LRT.h.2 <- fun_OneLR2(GCi[["Hmax"]])
+  PVAL.h <- fun_Onepvalue2(GIi[["Hmax"]])
+  PVAL.h.2 <- fun_Onepvalue2(GCi[["Hmax"]])
+  
[…]

### 2015-08-04 R/model.R

@@ -168,7 +168,318 @@ fun_model2 <- function(x) {
   CoefModel
 }
 
-fun_model_multiple <- function(x) {
+fun_model3 <- function(x, y) {
+  # models for x ('ideal' dataset) and y ('complete' datatset)
+  null <- lmer(corr.z ~ 1 + (1 | id), data = x, weights = nb.sp, REML = TRUE, 
+               control = lmerControl(check.nobs.vs.nlev = "ignore", check.nobs.vs.rankZ = "ignore", 
+                                     check.nobs.vs.nRE = "ignore"))  # modele null cad sans la variable que je veux analyser
+  m <- lmer(corr.z ~ stageRGR + (1 | id), data = x, weights = nb.sp, REML = TRUE, 
+            control = lmerControl(check.nobs.vs.nlev = "ignore", check.nobs.vs.rankZ = "ignore", 
+                                  check.nobs.vs.nRE = "ignore"))  # model avec la variable
+  m1 <- lmer(corr.z ~ stageRGR - 1 + (1 | id), data = x, weights = nb.sp, REML = TRUE, 
+             control = lmerControl(check.nobs.vs.nlev = "ignore", check.nobs.vs.rankZ = "ignore", 
+                                   check.nobs.vs.nRE = "ignore"))  # model avec les intercepts qui sont a 1
+  
+  null.s <- lmer(corr.z ~ 1 + (1 | id), data = y, weights = nb.sp, REML = TRUE, 
+                 control = lmerControl(check.nobs.vs.nlev = "ignore", check.nobs.vs.rankZ = "ignore", 
+                                       check.nobs.vs.nRE = "ignore"))  # idem mais pour le jeux y
+  m.s <- lmer(corr.z ~ stageRGR + (1 | id), data = y, weights = nb.sp, REML = TRUE, 
+              control = lmerControl(check.nobs.vs.nlev = "ignore", check.nobs.vs.rankZ = "ignore", 
+                                    check.nobs.vs.nRE = "ignore"))
+  m1.s <- lmer(corr.z ~ stageRGR - 1 + (1 | id), data = y, weights = nb.sp, REML = TRUE, 
+               control = lmerControl(check.nobs.vs.nlev = "ignore", check.nobs.vs.rankZ = "ignore", 
[…]

### 2015-08-04 R/plots.R

@@ -15,7 +15,7 @@ my_plot_1 <- function(title, ggobj, xlab = expression(paste("")), ylab = "Number
   p
 }
 
-coeff.plot <- function(data, data.complete, data.ideal, LRT, PVAL, title = "",
+coeff.plot.2 <- function(data, data.complete, data.ideal, LRT, PVAL, title = "",
   significativite = "", round.value, limit.x.min, limit.x.max, limit.x.text,
   limit.x.n, limit.y.text.l1, limit.y.text.l2, vjust.value, color1, color2) {
           data.complete["x.coord"] <- limit.x.n
@@ -26,7 +26,7 @@ coeff.plot <- function(data, data.complete, data.ideal, LRT, PVAL, title = "",
             ylab = "Stages") {
             p <- ggobj + labs(title = title) + xlab(xlab) + ylab(ylab) + geom_vline(yintercept = 0,color = "white") + 
               geom_hline(yintercept = 0, size = 0.3, linetype = "dashed") +
-              scale_x_discrete("stage", limit = c("juvenile", "sapling", "adult")) +
+              scale_x_discrete("stage", limit = c("seedling", "juvenile", "sapling", "adult", "mix")) +
               coord_flip() + mytheme + theme(legend.position = "none")
             p }
 
@@ -47,6 +47,63 @@ coeff.plot <- function(data, data.complete, data.ideal, LRT, PVAL, title = "",
             label = paste("p.value =", round(PVAL, round.value), significativite),
             size = 2)
 }
+
+
+coeff.plot <- function(data, data.complete, data.ideal, LRT, PVAL, title = "",
+                       significativite = "", round.value, limit.x.min, limit.x.max, limit.x.text,
+                       limit.x.n, limit.y.text.l1, limit.y.text.l2, vjust.value, color1, color2) {
+  data.complete["x.coord"] <- limit.x.n
+  
+  data.ideal["x.coord"] <- limit.x.n
+  
+  my_size_effect_plot1 <- function(title, ggobj, xlab = "Effect size + CI (95%) ",
+                                   ylab = "Stages") {
+    p <- ggobj + labs(title = title) + xlab(xlab) + ylab(ylab) + geom_vline(yintercept = 0,color = "white") + 
+      geom_hline(yintercept = 0, size = 0.3, linetype = "dashed") +
+      scale_x_discrete("stage", limit = c("juvenile", "sapling", "adult")) +
+      coord_flip() + mytheme + theme(legend.position = "none")
+    p }
+  
[…]

### 2015-08-04 analysis.R

@@ -62,126 +62,126 @@ dir.create("output", showWarnings =FALSE)
 write.csv(RawData, "output/data.csv", row.names=FALSE)
 
 ## Make output
-pdf("output/Fig1.pdf",height=3, width=4)
+pdf("output/FigA1.pdf", height=6) # In the main text, need to be changed
+figure_A1(CompleteData_inter)
+dev.off()
+
+pdf("output/Fig1.pdf",height=3, width=4) # ok
   figure_1(RawData)
 dev.off()
 
-pdf("output/Fig2.pdf",height=6,width=5)
+
+pdf("output/Fig2.pdf",height=6,width=5) # ok
   figure_2(GCi, GIi)
 dev.off()
 
 
-pdf("output/FigA1.pdf", height=6)
-  figure_A1(CompleteData)
+pdf("output/FigA4.pdf",height=6,width=6) # maybe in the main text
+figure_A4(GCi)
 dev.off()
 
 
-pdf("output/FigA2.pdf", height=6, width=6)
+pdf("output/FigA2.pdf", height=6, width=6) # ok , maybe need to put only the line address in the text
   figure_allometry()
 dev.off()
 
-pdf("output/FigA3.pdf", height=3, width=6)
+pdf("output/FigA3.pdf", height=3, width=6)# ok
   figure_map(CoordTable)
 dev.off()
 
-pdf("output/FigA4.pdf",height=6,width=6)
-  figure_A4(GC)
-dev.off()
 
-
-pdf("output/FigA5.pdf",height=6,width=5)
-  figure_A5(GIi)
-dev.off()
-
-pdf("output/FigA5b.pdf",height=6,width=5)
+pdf("output/FigA5.pdf",height=6,width=5) # need to be change, both graph on the same page
+figure_A5(GIi)
 figure_A5b(GIrgr, GIagr)
 dev.off()
 
 
-pdf("output/FigA6.pdf",height=6,width=5)
-  figure_A6(GC)
-dev.off()
+# pdf("output/FigA6.pdf",height=6,width=5)
+#   figure_A6(GCi)
+# dev.off()
 
 
-pdf("output/FigA7.pdf",  height=6, width=5)
[…]

### 2015-08-07 MS.tex
Change in the meta-analysis

@@
 \item
-The literature is inconsistent about empirical correlations between functional traits and plant growth rate (GR), casting doubt on the capacity of traits to predict growth.
+Growth rates have often been seen as central elements of plant ecological strategies, and as linked to species traits.
+Yet, the literature is inconsistent about empirical correlations between functional traits and plant growth rate (GR), casting doubt on the capacity of traits to predict growth.
 
@@
 \section*{Introduction}\label{introduction}
-Plant growth is an important aspect of ecosystem productivity
-Plant species vary considerably in the growth rate they can achieve under favourable growing conditions (Grime and Hunt 1975; Shipley and Keddy 1988; Poorter and Retakes 1990; Lambers and Poorter 1992).
-This variation is important both because potential RGR is an important aspect of ecological performance, and because slow potential RGR is thought to be part of a nexus of adaptations to unfavourable growing conditions (e.g.
-Grime et al.
-1988; Reich et al.
-1992; Chapin et al.
-1993; Aerts and van der Pijl 1993; van der Werf et al.
-1993).
-
 The phrase "plant ecological strategy" refers to how species face the challenge they all share:  to acquire sufficient water, nutrients and light for individual growth and to live long enough to replace themselves with offspring.
 An idea that species strategy differences might involve fast vs slow growth goes back at least to Grime and Hunt \citeyearpar{Grime:1975gr}, who measured a wide spread of relative growth rates for seedlings during early exponential growth under favourable conditions.
-Seedling potential relative growth rate (RGR, the change in a mass/height or diamater per time interval relative to initial size) has continued to be used as a major strategy indicator within the CSR (Competitor - Stress tolerator - Ruderal) scheme and its "Integrated Screening Program" (e.g.
+Seedling potential relative growth rate (RGR, the change in a mass/height or diamater per time interval relative to initial size) has continued to be used as a major strategy indicator within the CSR (Competitor - Stress tolerator - Ruderal) scheme (e.g.
 \citealt{grime1979plant, Grime:1997wm}).
@@
 Currently two main spectra of variation are widely cited as underpinning differences between species in vegetative growth rates.
-The `leaf economic spectrum' \citep{Wright:2004jb} and the 'wood economic spectrum' \citep{Chave:2009iy} reflect tissue construction costs (for specific leaf area and for wood volume respectively) trading off with tissue turnover rates or mortality risks.
+The 'leaf economic spectrum' \citep{Wright:2004jb} and the 'wood economic spectrum' \citep{Chave:2009iy} reflect tissue construction costs (for specific leaf area and for wood volume respectively) trading off with tissue turnover rates or mortality risks.
 It has been widely expected that species with low tissue construction cost will typically have fast growth rates at least in favourable physical environments (e.g.
@@
 
-Meanwhile the possibility has been raised that trait-growth correlations may change systematically with size \citep{Falster:2011ii, Ruger:2012jv, Iida:2014ep, Iida:2014hq}.ADD REF  Recent theory suggests that the absence of a correlation between SLA and growth at larger sizes may be expected, when potential influences of traits on plant function are considered \citep{Falster:2011ii, falster:2013}.
+Meanwhile the possibility has been raised that trait-growth correlations may change systematically with size Inquist et al () \citep{Falster:2011ii, Ruger:2012jv, Iida:2014ep, Iida:2014hq}.
+Recent theory suggests that the absence of a correlation between SLA and growth at larger sizes may be expected, when potential influences of traits on plant function are considered \citep{Falster:2011ii, falster:2013}.
 At larger sizes the low-cost deployment benefits of high SLA may be offset or even outweighed by the high costs of rapid leaf turnover (see Text Box 1\ref{sec:growth}).
@@
 The Web of Science database (Thomson Reuters) was searched between March and June 2014 using a range of Boolean search terms in English.
-Search terms were as follows: (''NAME'' AND (''growth rate'' OR ''relative growth rate'')) AND (''tree*'' OR ''woody*''), ''NAME'' was one of trait names listed in \ref{TableA1}.
+Search terms were as follows: (''NAME'' AND (''growth rate'' OR ''relative growth rate'')) AND (''tree*'' OR ''woody*''), ''NAME'' was one of trait names listed in TableA1.
 According to this snapshot, 62\% of the literature for the 20 traits (or 82\% for the 5 traits for which we have clear predictions) is captured by searching only on SLA and WD.
@@
 Thus, in Google Scholar we displayed papers by relevance and examined the first 750 items.
-
 Each study had to meet some basic criteria to be included in our analysis.
@@
 adult stage).
-Finally, we weighted our data by number of species rather than the sample size for all statistical analyses (see Statistical analyses section).
+We weighted our data by number of species rather than the sample size for all statistical analyses (see Statistical analyses section).
+Finally, to avoid publication bias due to selective reporting of significant results within published articles (e.g.~particular case of a 'failure to publish bias' see \citealt{Jennions:2013ta}), we asked the authors for additional information when they reported a non-significant correlation between growth and trait without reporting an r value.
 
@@
 
-We acknowledge that it would be better to address plant size as a continous variable, but the limited number of correlations available in the literature along plant size steered us to focus on plant stage as an approximation.
+We acknowledge that it would be better to address plant size as a continous variable, but the limited number of correlations available in the literature along plant size constrains us to approximate plant size by plant stage.
 The authors of the 112 articles reported in our meta-analyses, categorized plants into four differents stages (i.e.
@@
 Results using the categories established by the authors are similar than the one using the standardized categories and are available in Fig.
-A8.
+A8 model.1.
 In the main text, we report the results using the standardized categories.
@@
 In the case of multiple comparisons within a study, we used the method proposed by \citet{Borenstein:2009um}: we calculated the mean correlation coefficient by trait and by study, and re-calculated the effect size.
-Finally, we checked the dataset for publication bias with funnel plots (\citealt{Koricheva:2013tz}, Fig.
-A9).
-A publication bias toward significant results creates an asymmetric funnel with small studies with non-significant effects missing from the mouth of the funnel on the side opposite to the true effect.
-In addition, to avoid publication bias due to selective reporting of significant results within published articles (e.g.~particular case of a 'failure to publish bias' see \citealt{Jennions:2013ta}), we asked the authors for additional information when they reported a non-significant correlation between growth and trait without reporting an r value.
-Finally, we explored the temporal change im effect size, by testing the effect of year of publication within stage for each trait.
-In Table 2 in Appendix, we reported how and where (i.e in the main text and/or figures) we addressed the 14 methodological quality criteria for meta-analysis listed by Koricheva and Gurevitch (2014).
+
+Following recent call for the adoption of a checklist of quality criteria for meta-analysis in ecology (Koricheva and Gurevitch, 2014), we conducted several analyses to assess the reliability of our meta-analysis.
+Table A2 in Appendix X reported how and where (i.e in the text and/or figures) we addressed the 14 methodological quality criteria listed by Koricheva and Gurevitch (2014).
+In particular, we checked the dataset for publication bias with funnel plots (\citealt{Koricheva:2013tz}) and the 'trim and fill' method (Appendix), we explored the temporal changes in effect size (Appendix), and we estimated the extend of heterogeneity using the statistic I2 (Appendix X).
 
@@
 We had thought it likely that for some traits correlations would be reported only for one size class, or only mixed across different sizes.
-However these limitations applied only for LAR and NARmass, where studies appeared confined to juvenile stages.
+These limitations applied only for LAR and NARmass, where studies appeared confined to juvenile stages.
+However, among the 20 traits studied we had enough data to test the effect of stage on the trauts value only for the five for which we had predictions.
 
@@
 Number of species used for each correlation ranged from 2 to 300 species with average 31.
-As expected the correlation coefficient varied less widely as sample size increased (funnel plots Fig.
-A9).
-In the analyses described in Figs 2, A5 and A6 coefficients were weighted according to sample size, making the small-sample extremes less influential.
-Funnel plots exhibited a typical funnel shape for all five functional traits analyzed, showing no evidence for publication bias (Fig.
-A9).
+
+Finally, we met all the quality criteria required for meta-analysis in ecology.
+We found no evidence of publication bias, the extend of the heterogenity appares to be low to moderate in our meta-analysis, and there is no temporal change in effect size calculated within a stage.
 

### 2015-08-07 R/figures.R

@@ -959,3 +959,11 @@ figure_A12 <- function(GIi) {
   grid.arrange(funnel_SLA_year,funnel_WD_year,funnel_Hmax_year, funnel_Seedmass_year ,funnel_Aarea_year, nrow=3, ncol=2)
 }
 
+
+figure_9 <- function(GCi){
+  par(mfcol=c(1,2))
+  par(mar=c(5,4,1,2))
+  
+  p1 <- figure_trim.and.fill(GCi) 
+
+}

### 2015-08-07 R/model.R

@@ -603,6 +603,8 @@ fun_model_multiple3.1 <- function(x) {
   
   dat
 } 
+
+
 # Weighted correlation
 table_overall.stage <- function(y) {
   name <- list(1:3, c("stage", "corr.r", "SD", "CI"))
@@ -769,7 +771,7 @@ fun_Onepvalue_year <- function(x) {
 # }
 
 
-fun_HeterogenityI2 <- function(x, plant.stage){ 
+fun_HeterogenityH <- function(x, plant.stage){ 
   data1 <- x
   if (plant.stage=="NA") {data <- data1[!is.na(data1$corr.z) & !is.na(data1$wi.z),]
                         Q <- sum(data$wi.z * (data$corr.z - sum(data$wi.z * data$corr.z)/sum(data$wi.z))^2)
@@ -789,4 +791,29 @@ fun_HeterogenityI2 <- function(x, plant.stage){
                         }
   H 
 }
+
+
+fun_Heterogeneity.CI <- function(x){ 
+  res_null <- rma(corr.z, vr.z, data=x[!is.na(x$corr.z) & !is.na(x$nb.sp),])
+  confint(res_null)
+}
+
+fun_Heterogeneity.H <- function(x, mods){ 
+                      res_null <- rma(corr.z, vr.z, data=x[!is.na(x$corr.z) & !is.na(x$nb.sp),])
+                      res_stage <- rma(corr.z, vr.z, mods= mods, data=x[!is.na(x$corr.z) & !is.na(x$wi.z),])
+                      Hmodel <- (res_null$tau2-res_stage$tau2)/res_null$tau2*100 #% of the total amount of heterogenity can be accounted for by including the moderators of the model
+                      l <- list("Hexplained"=Hmodel,"pvalue"=res_stage$QEp,"Qdf"=res_stage$QE,"effectsize_moderator"=res_stage$zval,"pvalueeffectsize"=res_stage$pval)
+                      l
+}
+
+
+fun_trim.and.fill_number  <- function(x){ 
+                      res <-  rma(corr.z, vr.z, data=x[!is.na(x$corr.z) & !is.na(x$wi.z),])
+                      ### carry out trim-and-fill analysis
+                      taf <- trimfill(res)
+                      taf$k0
+                     
+                  
+}
+
 

### 2015-08-07 R/plots.R

@@ -146,7 +146,6 @@ plot_stage <- function(title, xlab, ggobj, ylab = "ID") {
 }
 
 my_plot_corr.r <- function(data1, title = "", xlab = "Case studies ranked by coefficient of correlation r") {
-
   my_funnelplot2 <- function(title, ggobj, xlab = "", ylab = "") {
     p <- ggobj + labs(title = title) + xlab(xlab) + ylab(ylab) + guides(fill = guide_legend(reverse = TRUE)) +
       mytheme + scale_y_continuous("Correlation coefficient r", limits = c(-1,
@@ -381,174 +380,174 @@ my_plot_overall.b <- function(data1, data2, title = "") {
 #   mtext(title, side = 3, line = 0.5, cex = 0.9, at = 0.5)
 # }
 
-# coeff.plot.multiple3 <- function(data, params, labels = NA, xlab = "Effect size (z) +CI 95%", title = "") {
-#   fun_List_N <- function(data) {c(
-#     length(na.omit(data$coef[data$stageRGR == "seedling"])),
-#     length(na.omit(data$coef[data$stageRGR == "juvenile"])),
-#     length(na.omit(data$coef[data$stageRGR == "sapling"])),
-#     length(na.omit(data$coef[data$stageRGR == "adult"])),
-#     length(na.omit(data$coef[data$stageRGR == "mix"])),
-#     length(na.omit(data$coef[data$RGR == "GR(Di)"])),
-#     length(na.omit(data$coef[data$RGR == "GR(Hi)"])),
-#     length(na.omit(data$coef[data$RGR == "GR(Mi)"])),
-#     length(na.omit(data$coef[data$RGR == "RGR(CSAi)"])),
-#     length(na.omit(data$coef[data$RGR == "RGR(Di)"])),
-#     length(na.omit(data$coef[data$RGR == "RGR(Hi)"])),
-#     length(na.omit(data$coef[data$RGR == "RGR(Mi)"])),
-#     length(na.omit(data$coef[data$RGR == "RGR(Vi)"])),
-#     length(na.omit(data$coef[data$growth.form == "tree"])),
-#     length(na.omit(data$coef[data$growth.form == "woody"])),
-#     length(na.omit(data$coef[data$growth.form == "across growth form"])),
-#     length(na.omit(data$coef[data$experiment == "control"])),
-#     length(na.omit(data$coef[data$experiment == "database"])),
-#     length(na.omit(data$coef[data$experiment == "field"])),
[…]

### 2015-08-07 analysis.R

@@ -19,6 +19,7 @@ library(MAc,quietly=TRUE)
 library(maptools)
 library(maps)
 library(downloader)
+library(metafor)
 
 library(bibtex)
 library(RefManageR)
@@ -101,26 +102,31 @@ dev.off()
 # dev.off()
 
 
-pdf("output/FigA7.pdf",  height=6, width=5) # ok, heterogenity
+pdf("output/FigA7.pdf",  height=6, width=5) # ok, independance of the data (restricted dataset)
   figure_A7(RIi, RCi)
 dev.off()
 
 
-pdf("output/FigA8.pdf")  # ok, test other class
- figure_8(GCi, GIi)
+# pdf("output/FigA8.pdf")  # coefficient plot with only the stage from the authors
+#  figure_8(GCi, GIi)
+# dev.off()
+# # 
+
+pdf("output/FigA8.a.pdf")
+figure_A8(GCi, "SLA","WD", c("a","b"))
 dev.off()
-# 
+
 pdf("output/FigA8.b.pdf")
 figure_A8(GCi, "Aarea","Seedmass", c("c","d"))
 dev.off()
-# 
-# pdf("output/FigA8.c.pdf")
-# figure_A82(GCi, "Hmax", "e")
-# dev.off()
+
+pdf("output/FigA8.c.pdf")
+figure_A82(GCi, "Hmax", "e")
+dev.off()
 
 
 pdf("output/FigA9.pdf") # ok funnel plot
-  figure_A9(GC)
+  # figure_A9(GC)
 dev.off()
 
 
@@ -160,27 +166,40 @@ dev.off()
 # dev.off()
 
 # Heterogeneity
-fun_HeterogenityI2(GIi[["SLA"]], plant.stage="NA") 
-fun_HeterogenityI2(GIi[["SLA"]], plant.stage="juvenile") 
-fun_HeterogenityI2(GIi[["SLA"]], plant.stage="sapling") 
-fun_HeterogenityI2(GIi[["SLA"]], plant.stage="adult") 
+# fun_HeterogenityH(GIi[["SLA"]], plant.stage="NA") 
+# fun_HeterogenityH(GIi[["WD"]], plant.stage="NA") 
+# fun_HeterogenityH(GIi[["Hmax"]], plant.stage="NA") 
+# fun_HeterogenityH(GIi[["Hmax"]], plant.stage="adult")
[…]

### 2015-08-07 MS.tex
Add Script for publication biais

@@
 \item
-Growth rates have often been seen as central elements of plant ecological strategies, and as linked to species traits.
-Yet, the literature is inconsistent about empirical correlations between functional traits and plant growth rate (GR), casting doubt on the capacity of traits to predict growth.
+Growth rates (GR) have often been seen as central elements of plant ecological strategies, and as linked to species traits.
+Yet, the literature is inconsistent about empirical correlations between functional traits and plant growth rate, casting doubt on the capacity of traits to predict growth.
 
@@
 \citealt{grime1979plant, Grime:1997wm}).
-Meanwhile partitioning of seedling RGR into its components (see equation X in Appendix 1) showed that specific leaf area (SLA = 1/leaf mass per area LMA) was typically the strongest source of variation between species \citep{Poorter:1989tx}.
+Meanwhile partitioning of seedling RGR into its components showed that specific leaf area (SLA = 1/leaf mass per area LMA) was typically the strongest source of variation between species \citep{Poorter:1989tx}.
 From the 1990s a new style of "trait ecology" arose whereby measurable traits including SLA were used directly as strategy axes \citep{Westoby:2002ft}.
@@
 
-Meanwhile the possibility has been raised that trait-growth correlations may change systematically with size Inquist et al () \citep{Falster:2011ii, Ruger:2012jv, Iida:2014ep, Iida:2014hq}.
+Meanwhile the possibility has been raised that trait-growth correlations may change systematically with size \citep{Enquist:2007ek,Falster:2011ii, Ruger:2012jv, Iida:2014ep, Iida:2014hq}.
 Recent theory suggests that the absence of a correlation between SLA and growth at larger sizes may be expected, when potential influences of traits on plant function are considered \citep{Falster:2011ii, falster:2013}.
 At larger sizes the low-cost deployment benefits of high SLA may be offset or even outweighed by the high costs of rapid leaf turnover (see Text Box 1\ref{sec:growth}).
+Today, we have no
 
@@
 The main effect of increased seed size is to produce a larger overall seedling.
-Generally relative growth rate decreases with size (REF Enquist et al 1999 Nature, Tilman 1988?), and as such larger seedlings are predicted to have a lower relative growth rate during the earliest phases of growth \citet{Turnbull:2012ew}.
+Generally relative growth rate decreases with size, and as such larger seedlings are predicted to have a lower relative growth rate during the earliest phases of growth \citet{Turnbull:2012ew}.
 However, among larger plants we expect the effect of this initial size to be minimal, and thus the correlation between seed size and growth rate should disappear.
@@
 Relative growth rate (RGR) is commonly used for smaller plants, but is less useful for larger-plants because there is a very rapid decline in RGR with increasing tree size due to accumulation of support tissues (bark, branches etc).
-According to the growth model used here, the correlation between trait and growth is predicted to revert according to the growth measurement used for both SLA and seed mass.
+According to the growth model used here, the correlation between trait and growth is predicted to revert according to the growth measurement used for both SLA and seed mass (see Text Box 1\ref{sec:growth}.
 The predicted relationship between growth and either SLA or seed mass in seedlings differs if absolute growth rate in mass is used instead of $RGR_{mass}$ (i.e.
@@
 
-Following recent call for the adoption of a checklist of quality criteria for meta-analysis in ecology (Koricheva and Gurevitch, 2014), we conducted several analyses to assess the reliability of our meta-analysis.
-Table A2 in Appendix X reported how and where (i.e in the text and/or figures) we addressed the 14 methodological quality criteria listed by Koricheva and Gurevitch (2014).
-In particular, we checked the dataset for publication bias with funnel plots (\citealt{Koricheva:2013tz}) and the 'trim and fill' method (Appendix), we explored the temporal changes in effect size (Appendix), and we estimated the extend of heterogeneity using the statistic I2 (Appendix X).
+Following recent recommendations for the adoption of a checklist of quality criteria for meta-analysis in ecology (\citealt{Koricheva:2014ku}), we conducted several analyses to assess the reliability of our meta-analysis.
+Table A2 in Appendix 1 reported how and where (i.e in the text, appendix and/or figures) we addressed the 14 methodological quality criteria listed by \citet{Koricheva:2014ku}.
 
@@
 Finally, we met all the quality criteria required for meta-analysis in ecology.
-We found no evidence of publication bias, the extend of the heterogenity appares to be low to moderate in our meta-analysis, and there is no temporal change in effect size calculated within a stage.
+We found no evidence of publication bias ().
+The extend of the heterogenity was high in our meta-analysis, and substantially explained by the plant stage for SLA and Seedmass as expected.
+Finally, we showed no temporal change in effect size for all the traits.
 
@@
 \centering
-\caption{\textbf{Checklist of quality criteria for meta-analysis in ecology developed by Koricheva and Gurevitch (2014)} 
+\caption{\textbf{Checklist of quality criteria for meta-analysis in ecology developed by Koricheva and Gurevitch (2014)} }
 \label{TableA2}
@@
 \end{table}
-
-% we conducted two types of analyses to assess the reliability of our meta-analysis.
-First, we estimated heterogeneity using a modified version of the heterogeneity statistic I2 (originally defined by Higgins & Thompson, 2002; see Supporting information for details).
-Heterogeneity estimates the consistency of the results obtained from published stud- ies used in our meta-analysis.
-A low level of heteroge- neity means that discrepancies among the effects reported by the original studies are satisfactorily explained solely by sampling errors and are not the result of different methodologies or species characteris- tics (Higgins & Thompson, 2002; Higgins et al., 2003; Cooper & Hedges, 2009).
-Second, we assessed our data set for signs of publication bias by visually inspecting funnel plots (Sterne et al., 2005) and also by conducting Egger’s regressions (Egger et al., 1997; Peters et al., 2006).
-We applied an Egger’s regression design, modi- fied for lnOR to data points consisting of the residuals of the effect sizes plus their measurement errors
-% a 2012 THE AUTHORS. J. EVOL. BIOL. 25 (2012) 1911–1917
-% JOURNAL OF EVOLUTIONARY BIOLOGY a 2012 EUROPEAN SOCIETY FOR EVOLUTIONARY BIOLOGY
-% Meta-analysis of cost of parental care in birds 1913
-% 1914 E. S. A. SANTOS AND S. NAKAGAWA
-% (Peters et al., 2006; see Supporting information for details). If the intercept of the Egger’s regression is sig- nificantly different from zero, it is evidence of p
 
@@
 \includegraphics{output/FigA9.pdf}
-\caption{\textbf{Funnel plots showing transformed correlation coefficient z between growth and the traits a) Specific leaf area (SLA), b) Wood density (WD), c) Asymptotic height (Hmax), d) Seed mass and e) Assimilation rate of CO2 (Aarea)}.
-Shown here are complete dataset (recorded at both interspecific and intraspecific level and under unstressed and stressed conditions).
-Point colors: red for adult, orange for sapling, grey for juvenile.
-Note that in these plots the x axis is the number of species included in the correlation, not the replication for the correlation.
+\caption{\textbf{Funnel plots with filled in data based on the trim and fill method, showing transformed correlation coefficient z between growth and the traits a) Specific leaf area (SLA), b) Wood density (WD), c) Asymptotic height (Hmax), d) Seed mass and e) Assimilation rate of CO2 (Aarea)}.
+Shown here are ideal dataset (recorded across species and under unstressed conditions).
+Note that in these plots the y axis is the 1/number of species included in the correlation, not the replication for the correlation.
 The number of species is sometimes as low as 1, and these are within-species correlations.
 The number of replicates used for the correlation coefficient was often much greater than the number of species.
-Nevertheless, the characteristic shape of funnel plots is observed, with correlations involving few species showing much wider variation even though within-species replication was sometimes high.}
+Nevertheless, the characteristic shape of funnel plots is observed, with correlations involving few species showing much wider variation even though within-species replication was sometimes high.
+The open points correspond to the estimated missing studies.
+The number of missing values is 9 for SLA,1 for WD, 0 for Hmax, 6 for Seedmass and 0 for Aarea}
 
@@
 \includegraphics{output/FigA10.pdf}
-\caption{\textbf{Growth measurement used by traits and by size.} Shown here are complete dataset (recorded at both across and within species and under unstressed and stressed conditions).
+\caption{\textbf{Growth measurement used by traits and by size.} Shown here are complete dataset (recorded across  species and under both unstressed and stressed conditions).
 The colors correspond to the stage for which the r values have been recorded: red bars corresponds adult stage, orange bars to saplings, and grey bars to juveniles.}

### 2015-08-07 R/data_processing.R

@@ -248,7 +248,7 @@ build_complete_data <- function(RawData) {
     doi, experiment, stress, growth.form, veg.type, bio.scale, nb.sp, RGR,growth, measurement, RGR.min, RGR.max,
     RGR.unit, stageRGR, similarity, stageTrait, stage, trait, trait.min, trait.max,
     measure.size, size.min, size.max, size.mean.range, coef, sample.size, corr.r,
-    corr.z, vr.z, wi.z))
+    corr.z, vr.z, wi.z, se.z))
   CompleteData$id <- as.factor(CompleteData$id)
   CompleteData
 }
@@ -266,7 +266,7 @@ Build_intersp_complete_data <- function(RawData) {
                                                   doi, experiment, stress, growth.form, veg.type, bio.scale, nb.sp, RGR, growth, measurement, RGR.min, RGR.max,
                                                   RGR.unit, stageRGR, similarity, stageTrait, stage, trait, trait.min, trait.max,
                                                   measure.size, size.min, size.max, size.mean.range, coef, sample.size, corr.r,
-                                                  corr.z, vr.z, wi.z))
+                                                  corr.z, vr.z, wi.z, se.z))
   CompleteData$id <- as.factor(CompleteData$id)
   CompleteData
 }

### 2015-08-07 R/figures.R

@@ -694,6 +694,19 @@ figure_A82 <- function(GC, trait1, titles) {
   mtext("mod1", side=2, line=4.2, cex=0.8, at=15.2)
 }
 
+
+figure_A9 <- function(GCi){
+  par(mfrow=c(3,2))
+  par(mar=c(5,4,1,2))
+  
+  p1 <- figure_trim.and.fill(GIi[["SLA"]], title= 'a) SLA') 
+  p2 <- figure_trim.and.fill(GIi[["WD"]], title= 'b) WD')
+  p3 <- figure_trim.and.fill(GIi[["Hmax"]],title= 'c) Hmax') 
+  p4 <- figure_trim.and.fill(GIi[["Seedmass"]],title= 'd) Seedmass') 
+  p5 <- figure_trim.and.fill(GIi[["Aarea"]],title= 'e) Aarea') 
+}
+
+
 # figure_A8b <- function(GC, trait1, trait2, titles) {
 #   par(mfcol=c(1,2))
 #   par(mar=c(2,5,2,0))
@@ -742,42 +755,42 @@ figure_A82 <- function(GC, trait1, titles) {
 #   
 # }
 
-figure_A9 <- function(GC) {
-
-  funnel_SLA_nbsp <- my_funnelplot("a) SLA",
-    ggplot(GC[["SLA"]],aes(x=nb.sp,y=corr.r, colour=factor(stage), size=2, alpha=0.6))) +
-    geom_point() + scale_y_continuous("Correlation coefficient  r",limits=c(-1,1)) +theme( legend.position="none")
-
-
-  funnel_WD_nbsp <- my_funnelplot("b) WD",
-    ggplot(GC[["WD"]],aes(x=nb.sp,y=corr.r,colour=factor(stage), size=2, alpha=0.6))) +
-    geom_point()+
-    scale_y_continuous("",limits=c(-1,1)) +
-    scale_x_continuous("",limits=c(0,150)) +
-    theme( legend.position="none")
-
-  funnel_Hmax_nbsp <- my_funnelplot("c) Hmax",
-    ggplot(GC[["Hmax"]],aes(x=nb.sp,y=corr.r,colour=factor(stage), size=2, alpha=0.6))) +
-    geom_point() + scale_y_continuous("Correlation coefficient r",limits=c(-1,1))+
-    scale_x_continuous("",limits=c(0,150)) +
-    theme( legend.position="none")
-
-
-  funnel_Seedmass_nbsp <- my_funnelplot("d) Seed mass",
[…]

### 2015-08-07 R/model.R

@@ -771,28 +771,6 @@ fun_Onepvalue_year <- function(x) {
 # }
 
 
-fun_HeterogenityH <- function(x, plant.stage){ 
-  data1 <- x
-  if (plant.stage=="NA") {data <- data1[!is.na(data1$corr.z) & !is.na(data1$wi.z),]
-                        Q <- sum(data$wi.z * (data$corr.z - sum(data$wi.z * data$corr.z)/sum(data$wi.z))^2)
-                        df <- length(data$corr.z)-1
-                        # pchisq(Q,df=df, lower=FALSE) 
-                        I2 <- ((Q-df)/Q)*100 
-                        H2 =1-(I2/100)
-                        H=sqrt(H2)
-                } else {data2 <- subset(data1, data1$stage==plant.stage)
-                        data <- data2[!is.na(data2$corr.z) & !is.na(data2$wi.z),]
-                        Q <- sum(data$wi.z * (data$corr.z - sum(data$wi.z * data$corr.z)/sum(data$wi.z))^2)
-                        df <- length(data$corr.z)-1
-                        # pchisq(Q,df=df, lower=FALSE) 
-                        I2 <- ((Q-df)/Q)*100 
-                        H2 =1-(I2/100)
-                        H=sqrt(H2)
-                        }
-  H 
-}
-
-
 fun_Heterogeneity.CI <- function(x){ 
   res_null <- rma(corr.z, vr.z, data=x[!is.na(x$corr.z) & !is.na(x$nb.sp),])
   confint(res_null)
@@ -800,7 +778,7 @@ fun_Heterogeneity.CI <- function(x){
 
 fun_Heterogeneity.H <- function(x, mods){ 
                       res_null <- rma(corr.z, vr.z, data=x[!is.na(x$corr.z) & !is.na(x$nb.sp),])
-                      res_stage <- rma(corr.z, vr.z, mods= mods, data=x[!is.na(x$corr.z) & !is.na(x$wi.z),])
+                      res_stage <- rma(corr.z, vr.z, mods= mods, data=x[!is.na(x$corr.z) & !is.na(x$vr.z),])
                       Hmodel <- (res_null$tau2-res_stage$tau2)/res_null$tau2*100 #% of the total amount of heterogenity can be accounted for by including the moderators of the model
[…]

### 2015-08-07 R/plots.R

@@ -601,10 +601,11 @@ my_funnelplot <- function(title, ggobj, xlab = "", ylab = "") {
 }
 
 
-figure_trim.and.fill <- function(x){
-  res <- rma(corr.z, vr.z,  data=x[!is.na(x$corr.z) & !is.na(x$wi.z),])
+figure_trim.and.fill <- function(x, title){
+  res <- rma(corr.z, vr.z,  data=x[!is.na(x$corr.z) & !is.na(x$vr.z),])
   ### carry out trim-and-fill analysis
   taf <- trimfill(res)
-  funnel(taf) ### draw funnel plot with missing studies filled in
+  funnel(taf,axis="corr.z", main= title)
 }
+
 

### 2015-08-07 analysis.R

@@ -126,7 +126,7 @@ dev.off()
 
 
 pdf("output/FigA9.pdf") # ok funnel plot
-  # figure_A9(GC)
+  figure_A9(GIi)
 dev.off()
 
 
@@ -176,30 +176,43 @@ dev.off()
 fun_Heterogeneity.CI(GIi[["SLA"]])
 fun_Heterogeneity.H(GIi[["SLA"]], mods=~stage +year)
 fun_Heterogeneity.H(GIi[["SLA"]], mods=~stage )
-fun_trim.and.fill_number(GIi[["SLA"]])
+
 
 fun_Heterogeneity.CI(GIi[["WD"]])
 fun_Heterogeneity.H(GIi[["WD"]], mods=~stage +year)
 fun_Heterogeneity.H(GIi[["WD"]], mods=~stage )
-fun_trim.and.fill_number(GIi[["WD"]])
+
 
 fun_Heterogeneity.CI(GIi[["Hmax"]])
 fun_Heterogeneity.H(GIi[["Hmax"]], mods=~stage +year)
 fun_Heterogeneity.H(GIi[["Hmax"]], mods=~stage )
-fun_trim.and.fill_number(GIi[["Hmax"]])
-
-
 
 
 fun_Heterogeneity.CI(GIi[["Seedmass"]])
 fun_Heterogeneity.H(GIi[["Seedmass"]], mods=~stage +year)
 fun_Heterogeneity.H(GIi[["Seedmass"]], mods=~stage )
-fun_trim.and.fill_number(GIi[["Seedmass"]])
+
 
 fun_Heterogeneity.CI(GIi[["Aarea"]])
 fun_Heterogeneity.H(GIi[["Aarea"]], mods=~stage +year)
 fun_Heterogeneity.H(GIi[["Aarea"]], mods=~stage )
+
+
+fun_trim.and.fill_number(GIi[["SLA"]])
+fun_trim.and.fill_number(GIi[["WD"]])
+fun_trim.and.fill_number(GIi[["Hmax"]])
+fun_trim.and.fill_number(GIi[["Seedmass"]])
 fun_trim.and.fill_number(GIi[["Aarea"]])
+
+
+fsn(data=GIi[["SLA"]], corr.z, vi=vr.z, sei= se.z, type="Rosenberg") 
+fsn(data=GIi[["WD"]], corr.z, vi=vr.z, sei= se.z, type="Rosenberg") 
[…]

### 2015-08-10 MS.tex
Add 14 quality criteria for meta-analyses - add table - appendix D - ref

@@
 
-\newpage
+\clearpage
 
@@
 
-\textit{Type of article} Letters
-
-\textit{Number of words in the abstract} 150
-
-\textit{Number of words in the main text} 4583
-
-\textit{Number of words in each text box} 770
-
-\textit{Number of general references} 50
-
-\textit{Number of data source references} 112
-
-\textit{Number of figures} 2
-
-\textit{Number of tables} 1
-
-\textit{Number of text boxes} 1
-
 \textit{corresponding author} Anais Gibert, anais.gibert@gmail.com, Dept of Biological Sciences, Macquarie University, Sydney, NSW 2109, Australia, tel: +61 2 9850 8194
@@
 At larger sizes the low-cost deployment benefits of high SLA may be offset or even outweighed by the high costs of rapid leaf turnover (see Text Box 1\ref{sec:growth}).
-Today, we have no
 
@@
 
-\textbf{Effect on absolute (AbsGR) and relative growth rate (RGR}
-Tree growth is the increase in dimensions (i.e.
-diameter, height or mass) of an individual tree through time.
-While plant functional traits measurements are standardized across plant ontogeny, plant growth is commonly expressed differently according to the plant size/stage considered.
-Thus, mass and height are both used for smaller plants, whereas height and diamater are more convenient measures for larger tree.
-In addition, the growth increment (i.e.
-rate of change of a dimension per unit time) can be expressed in either absolute or relative terms.
-Relative growth rate (RGR) is commonly used for smaller plants, but is less useful for larger-plants because there is a very rapid decline in RGR with increasing tree size due to accumulation of support tissues (bark, branches etc).
-According to the growth model used here, the correlation between trait and growth is predicted to revert according to the growth measurement used for both SLA and seed mass (see Text Box 1\ref{sec:growth}.
-The predicted relationship between growth and either SLA or seed mass in seedlings differs if absolute growth rate in mass is used instead of $RGR_{mass}$ (i.e.
+\textbf{Effect on absolute (AbsGR) and relative growth rate (RGR)}
+
+The correlation between trait and growth is predicted to revert according to the growth measurement used for both SLA and seed mass (see Text Box 1\ref{sec:growth}).
+Tree growth in diameter, height or mass can be expressed in either absolute (AbsGR) or relative terms (RGR).
+Here, the predicted relationship between growth and either SLA or seed mass in seedlings differs if absolute growth rate in mass is used instead of $RGR_{mass}$ (i.e.
 becomes negative for SLA, positive for SM).
@@
 seedling, juvenile, sapling, adult).
-They also reported plant size informations in diameter, height or age; generally the authors give the size of the smallest and the biggest plants species used in their analyses.
+They also reported plant size informations in diameter, height or age (generally the authors give the size of the smallest and the biggest plants species used in their analyses).
+
 While the stage categories have been established according to the expertise and the appreciation of the authors, by compiling data across multiple studies and across different growth form (tree, woody, etc), there is a risk of assigning plants of similar size to different categories.
-Thus, we tested how consistent were the range values in size/age attributed to each stage across the 112 studies, and across the different growth form (tree, woody and across growth form, Fig.
-A1).
+Thus, we tested how consistent were the range values in size/age attributed to each stage across the 112 studies, and across the different growth form (tree, woody and across growth form, (Fig.
+\ref{Fig2}).
 Suprisingly, the threshold in size/age used by the authors to defined a plant stage are quite steady across the 112 studies (Fig.
-A1).
+\ref{Fig2}).
 In particular, there was a clear break between seedlings and saplings in both age (at 1 yr) and height (at 0.5 m); there was also a clear break between saplings and adults in diameter (at 10 cm).
@@
 diameter, height and age, Fig.
-A2).
+\ref{FigA1}).
 For instance, we showed according to BAAD that a sapling with a diameter < 10 cm would have a height < 1 m.
 Thus, according to the size/stage threshold established across 112 studies, the plant will be assigned to the sapling stage whatever we focused on its diameter or height (see Fig.
-A2 c).
+\ref{FigA1} c).
 
@@
 Interestingly, these discrepancies were not due to a differences between growth form; all the ambiguous cases corresponds to studies focusing exclusively on tree species (Fig.
-A1).
+\ref{FigA1}).
 In fact, we identified two main explanations.
@@
 Second, the reproductive state of a plant is not strictly correlated to plant size; some plants with a large stature are not assessed as adult because the authors selected them to be non reproductive (See ID 50, 52 and 105 in Fig.
-A1).
+\ref{FigA1}).
 Thus, we attributed a study to a new stage category when 95\% of the recorded range of sizes for that study lay within a new category.
@@
 The size/stage threshold defined across the 112 articles, allowed us to attribute straightforwardly a stage category to studies for which no stage have been distinctly mentionned by the authors (5\% of the data, noted as 'mix' in Fig.
-A1).
+\ref{Fig2}).
 Finally, we run the analyses with both the old and the standardized categories to ensure that the different stage attribution will not disturb our results.
@@
 Results using the categories established by the authors are similar than the one using the standardized categories and are available in Fig.
-A8 model.1.
+\ref{FigA5} model.1.
 In the main text, we report the results using the standardized categories.
@@
 In the case of multiple comparisons within a study, we used the method proposed by \citet{Borenstein:2009um}: we calculated the mean correlation coefficient by trait and by study, and re-calculated the effect size.
-
 Following recent recommendations for the adoption of a checklist of quality criteria for meta-analysis in ecology (\citealt{Koricheva:2014ku}), we conducted several analyses to assess the reliability of our meta-analysis.
@@
 Model fits improved when stage was incorporated (see log likelihood ratio tests, Fig.
-\ref{Fig2} a and d; average values for the coefficients r ($r_{\textrm{mean}}$) in Fig.
-A5).
+\ref{Fig3} a and d; average values for the coefficients r ($r_{\textrm{mean}}$) in Fig.
+\ref{FigA4}).
 The correlation between growth and SLA shifted from strongly positive at juvenile stage $r_{\textrm{mean}}=0.6 \pm 0.08$, Mean +SD) to not significantly different from zero at adult stage ($r_{\textrm{mean}}= -0.01 \pm 0.07$, CI 95\% overlapping zero in Fig.
-\ref{Fig2} a).
+\ref{Fig3} a).
 The correlation between growth and SM shifted from negative at juvenile stage ($r_{\textrm{mean}}= -0.59 \pm 0.07$) to not significantly different from zero at adult stage ($r_{\textrm{mean}}= -0.09 \pm 0.02$, , CI 95\% overlapping zero in Fig.
-\ref{Fig2} d).
+\ref{Fig3} d).
 For both traits, correlation coefficients recorded at sapling stage were intermediate between juvenile and adult stages.
@@
 At sapling and juvenile stages, the correlation between Hmax and growth was not significantly different from that observed at adult stage (model fit not improved when stage was incorporated, see log likelihood ratio tests in Fig.
-\ref{Fig2}c), but also was consistent with no correlation (Fig \ref{Fig2}c, confidence intervals overlapping zero), due to much smaller numbers of replicate studies.
-Similarly for WD and for Aarea, results were consistent with negative (WD) and positive (Aarea) correlations with growth across all plant sizes (Fig 2 b and e, model fit not improved when stage was incorporated).
+\ref{Fig3} c), but also was consistent with no correlation (Fig \ref{Fig3} c, confidence intervals overlapping zero), due to much smaller numbers of replicate studies.
+Similarly for WD and for Aarea, results were consistent with negative (WD) and positive (Aarea) correlations with growth across all plant sizes (Fig.
+\ref{Fig3} b and e, model fit not improved when stage was incorporated).
 However, at the same time confidence intervals of r often spanned zero especially where there were small numbers of studies for particular growth stages.
@@
 This "complete" dataset generated similar effect sizes to those reported above from the "ideal" dataset, and led to similar conclusions (Fig.
-\ref{Fig2} grey points).
+\ref{Fig3} grey points).
 Differences concerned often the confidence intervals around particular mean effect sizes in Fig.
-\ref{Fig2}.
+\ref{Fig3}.
 These differences in CI were not easily attributed to any single cause.
@@
 Finally, our results were unlikely to be biased by dominance of one or a few studies that measured a large number of responses, since when multiple responses were condensed into a single average within a trait and within a study, outcomes were very similar (Fig.
-A7).
+\ref{FigA5}).
 
@@
 These limitations applied only for LAR and NARmass, where studies appeared confined to juvenile stages.
-However, among the 20 traits studied we had enough data to test the effect of stage on the trauts value only for the five for which we had predictions.
+However, among the 20 traits studied we had enough data to test the effect of stage on the correlation between growth and traits only for the five for which we had predictions.
 
@@
 Climate zones spanned from temperate regions to  tropics (map in Fig.
-A3).
+\ref{FigA2}).
 Different experiment types (laboratory, field, plantation or greenhouse), growth measurements and growth form (tree, woody or across growth form) were included.
+Number of species used for each correlation ranged from 2 to 300 species with average 31.
 Given this variety, it was not surprising to find wide ranges of r reported for all traits.
 For instance, r varied from -0.98 to 0.99 for SLA, and from -0.74 to 0.74 for WD (Fig.
-A4).
+\ref{FigA3}).
 The growth form, the experiment types and the growth measurement were not markedly best predictors of the data (results shown in the Fig.
-A8).
-Number of species used for each correlation ranged from 2 to 300 species with average 31.
+\ref{FigA5}).
 
-Finally, we met all the quality criteria required for meta-analysis in ecology.
-We found no evidence of publication bias ().
-The extend of the heterogenity was high in our meta-analysis, and substantially explained by the plant stage for SLA and Seedmass as expected.
-Finally, we showed no temporal change in effect size for all the traits.
+We met all the quality criteria required for meta-analysis in ecology (Table 2).
+We showed that the impact of publication bias is probably trivial in our meta-analyses (Appendix D, Fig.
+\ref{FigA7}).
+The extend of the heterogenity was high in our meta-analysis, and substantially explained by the plant stage for SLA and Seedmass as expected (Appendix D).
+Finally, temporal change in effect size did not jeopardizing the stability of our conclusions for all the traits (Appendix D, Fig.
+\ref{FigA9}).
 
@@
 This negative relationship arises because seedlings from larger seeds are larger to begin with, as extensively discussed in the literature \citep[reviewed by][]{Turnbull:2012ew}.
-It applies only to RGR not to absolute growth rate, but for seedlings growth is most often reported as RGR (Appendix FigA10 d).
+It applies only to RGR not to absolute growth rate, but for seedlings growth is most often reported as RGR (Appendix Fig.
+\ref{FigA8} d).
 
@@
 
-\newpage
+\clearpage
 \section*{Figures}
 
-\begin{figure}[htbp]
+\begin{figure}[h!]
 \centering
@@
 
-\begin{figure}[htbp]
+\begin{figure}[h!]
 \centering
 \includegraphics{output/Fig2.pdf}
+\caption{Range of plant size in \textbf{a)} age, \textbf{b)} height and \textbf{c)} diameter and the plant stage assigned by the authors of the articles used in the meta-analyses.
+Each segment represents the plant size range (max and min values) of the species used to measure the correlation between growth and traits in each article.
+ID is the reference number of the article in our dataset.
+The colors represents the stage information given by the authors (green: seedling, blue: juvenile, orange: sapling, red: adult, grey: unspecified by the authors), the vertical line represents the most likely limits between stage categories, the horizontal line styles corresponds to the species growth form used in each study (solid line: exclusively tree, dashed line: woody species , dotted line: tree mixed with another growth form).
+Shown here are the "raw dataset" (recorded both across and within species, and under unstressed and stressed conditions).}
+\label{Fig2}
+\end{figure}
+
+\begin{figure}[h!]
+\centering
+\includegraphics{output/Fig3.pdf}
 \caption{The relationship between growth rates and SLA or seed mass changes with plant stage.
@@
 }
-\label{Fig2}
+\label{Fig3}
 \end{figure}
 
-\newpage
-\section*{Table} \label{sec:table}
-
-\begin{table}[ht]
+\clearpage
+\section*{Table}
+\setcounter{table}{0}
+\begin{table}[h!]
 \centering
-\caption{\textbf{ Hypothesised effects of traits on key elements of plant function determining growth rate.} Arrows indicate the effect an increase in trait value would have on the main elements of growth eqs.
+\caption{\textbf{Hypothesised effects of traits on key elements of plant function determining growth rate.} Arrows indicate the effect an increase in trait value would have on the main elements of growth eqs.
 \ref{eq:eq0}-\ref{eq:eq4} in Text box 1:  Leaf deployment per mass ($\frac{\textrm{d}a_\textrm{l}}{\textrm{d}m_\textrm{t}}$), Allocation to vegetative growth ($\frac{\textrm{d}m_\textrm{t}}{\textrm{d}b}$), Net live biomass production ($\frac{\textrm{d}b}{\textrm{d}t}$), Sapwood turnover ($k_s a_s$).
@@
   Aarea &$\_$ &$\_$ & $\nearrow$ &$\_$ \\
-
 \hline
   \end{tabular}
+  \end{table}
 \label{tab:trade-offs}
+
+\clearpage
+\begin{table}[h!]
+\centering
+\caption{\textbf{Checklist of quality criteria for meta-analysis in ecology} developed by Koricheva and Gurevitch (2014) }
+\label{Table 2}
+\vspace{0.5cm}
+\begin{tabular}{p{3cm} p{1cm} p{10cm} p{3cm}}
+  \hline
+  Quality criteria & Check & Explanations & Addressed in \\
+  \hline
+  1.
+Reporting full details of bibliographic searches & yes	& Google Scholar database was searched using the range of Boolean search terms ((''SLA'' OR ''LMA'' OR ''specific leaf area'' OR ''leaf    mass area'' OR ''wood density'' OR ''WD'' OR ''wood specific gravity'' OR ''stem density'' OR ''stem specific density'') AND (''growth rate'' OR ''relative growth rate'')) AND (tree* OR woody*), in english.
+& "Systematic search", Table A1 \\
+  2.
+Reporting inclusion/exclusion criteria & yes & Studies included report i) correlation coefficient between growth and trait, ii) the sample size/ number of species, and iii) the size/stage of plants.
+Studies excluded report correlation within species	& "Systematic search" \\
+  3.
+Weighting effect sizes by study precision & yes & Effects sizes were weighted by number of species.
+The question addressed in our study concerns the correlation between growth and trait across species, thus the number of species is a better proxy of a study quality than sample size.
+&	 "Systematic search" and  "Effect size calculation" \\
+ 4. Specifying meta-analytical model &	yes	& Mixed-effect model with a study ID as a random variation, and stage as a fixed effect, m1 ~lmer (stage + (1|ID)) &	"Statistical analyses", Fig3 \\
+ 5. Quantifying heterogeneity in effect sizes &	yes &	We estimated the extend of the heterogeneity using the statistics $I^{2}$ (Santos and Nakagawa, 2012) for each trait. &	Appendix D \\
+ 6. Exploring causes of heterogeneity &	yes &	We explored two causes of variability: the stage and the year of publication & Appendix D, Fig3 \\
+ 7.
+Multifactorial analysis of explanatory variable	& yes & We focused on the "plant stage" as the main exploratory variable.
+Yet, the stage variable may be confunded with other explanatory moderators (i.e.
+growth measurement, experiment type or growth form).
+Thus, we checked if no one of them would not consistenly be a strongest predictor of the data.
+We did not test the multiple variables in a hierarchical fashion, because of the limited size of our dataset.
+& FigA4, FigA6  \\
+  8.
+Testing for publication bias &	yes	& We used funnel plots for a visual assessement.
+We  used the "trim and fill" method to estimate the number of studies missing (Duval and Tweedie 2000).
+We also estimated the Rosenberg’s fail-safe number (Rosenberg 2005).
+	&  Appendix D, FigA7\\
+  9.
+Sensitivity analysis &	yes &	We tested how robust are our results to the decision made in the analysis.
+We calculated effect size using 3 differents dataset: i) an  "ideal" dataset, focusing on unstressed conditions exclusively, ii) a "complete dataset" reporting all conditions, and iii) a "reduced dataset" where multiple responses were condensed into a single average within a trait and within a study.
+&	Fig3, FigA5 \\
+  10.Exploring temporal changes in effect size &	yes	& There may be a confounding effect between the publication year and the stage.
+Thus, we explored the publication effect on the effect size within each stage for traits where a stage effect had been highlighted (SLA and Seedmass).
+& Appendix D, FigA9 \\
+  11. Controlling for phylogeny &	no &	It was not possible to control by the phylogeny since the number of species used to measured each coeffcient of correlation ranged from 2 to 300 species. &	\\
+  12. Specifying the software used &	yes	& R softward, code available on Github. & "Availability of code and data" \\
+ 13.
+Providing reference list of primary studies included in the analysis &	yes &	Available on Github.
+The Bibtex file "meta-analyses.bib" corresponds to all the articles included in the meta-analyses, "read.bib" corresponds to all the articles (included and excluded) inspected for the meta-analyses.	& "Availability of code and data" \\
+  14. Providing the data set used for meta-analysis  &	yes &	A copy of the complete data set is available on Github.	& "Availability of code and data" \\
+   \hline
+\end{tabular}
 \end{table}
 
-\newpage
+\clearpage
 \section*{Text Box 1} \label{sec:growth}
@@
 
-\newpage
+\clearpage
 \begin{appendices}\label{sec:appendices}
@@
 
-\newpage
+\clearpage
 \section{Supporting tables}\label{app:supp_info_tables}
@@
 
-\begin{table}[ht]
+\begin{table}[h!]
 \centering
@@
 
-\begin{table}[ht]
-\centering
-\caption{\textbf{Checklist of quality criteria for meta-analysis in ecology developed by Koricheva and Gurevitch (2014)} }
-\label{TableA2}
-\vspace{0.5cm}
-\begin{tabular}{p{3cm}p{3cm}p{8cm}}
-  \hline
-Criteria & Addressed & \\
-  \hline
-Aarea & Photosynthetic rate per area & "photosynthetic rate per area" OR "rate of CO2 assimilation per area" OR "Aarea" OR "Amax" OR "photosynthetic capacity per area" \\
-  Amass & Photosynthetic rate per mass & "photosynthetic rate per mass" OR "rate of CO2 assimilation per mass" OR "Amass" OR "Amax" \\
-  Hmax & Maximum height & "potential height" OR "maximum height" OR "Hmax" \\
-  Ks & Stem specific conductance & "Ks" OR "stem specific conductance" OR "stem hydraulic conductance" OR "sapwood conductance" \\
-  LA & Leaf lamina area & "leaf length" OR "leaf lamina area" OR "leaf width" OR "leaf size" \\
-  LAR & Leaf area ratio & "leaf area ratio" \\
-  LMR & Leaf mass ratio & "leaf mass ratio" OR "leaf mass fraction" \\
-  NARarea & Net assimilation rate per area &  "net assimilation rate per area" OR "rate of dry mass increament per area" OR "NARarea" OR "NAR" \\
-  Narea & Leaf nitrogen content per area & "Narea" OR "nitrogen per area" OR "N/area" OR "leaf nitrogen content per area" OR "LNCarea" OR "leaf nitrogen content" \\
-  NARmass & Net assimilation rate per mass &  "net assimilation rate per mass" OR "rate of dry mass increament per mass" OR "NARmass" OR "NAR" \\
-  Nmass & Leaf nitrogen content per mass & "Nmass" OR "nitrogen per mass" OR "N/mass" OR "leaf nitrogen content per mass" OR "LNCmass" OR "leaf nitrogen content" \\
-  Parea & Leaf phosphorus content per area & "Parea" OR "leaf P" OR  "leaf phosphorus content per area"  OR "leaf phosphorus content" \\
-  Pmass & Leaf phosphorus content per mass & "Pmass" OR "leaf P" OR  "leaf phosphorus content per mass" OR "leaf phosphorus content" \\
-  SA/LA & Sapwood area per leaf area & "sapwood area per leaf area" OR "huber value" OR "leaf area per sapwood area" \\
-  Seed mass & Seed mass & "seed mass" OR "seed size" OR "seed volume" \\
-  SLA & Specific Leaf Area & "leaf mass per area" OR "specific leaf area" OR "leaf construction cost" \\
-  Thickness & Leaf thickness & "leaf thickness"  OR "leaf tissue density" \\
-  Vessel density & Vessel density & "vessel density" OR "stem conduit density" \\
-  Vessel size & Vessel area or diameter & "conduit area" OR "stem conduit area" OR "vessel diameter" OR "vessel size" OR "conduit size"   \\
-  WD & Wood density & "wood density" OR"WD" OR "wood specific gravity" OR "stem density" OR "stem specific density" OR "SSD" \\
-   \hline
-\end{tabular}
-\end{table}
-
-\newpage
+\clearpage
 \section{Supporting figures}\label{app:supp_info_figures}
 
-\begin{figure}[htbp]
+\begin{figure}[h!]
 \centering
 \includegraphics{output/FigA1.pdf}
-\caption{Range of plant size in \textbf{a)} age, \textbf{b)} height and \textbf{c)} diameter and the plant stage assigned by the authors of the articles used in the meta-analyses.
-Each segment represents the plant size range (max and min values) of the species used to measure the correlation between growth and traits in each article.
-ID is the reference number of the article in our dataset.
-The colors represents the stage information given by the authors (green: seedling, blue: juvenile, orange: sapling, red: adult, grey: unspecified by the authors), the vertical line represents the most likely limits between stage categories, the horizontal line styles corresponds to the species growth form used in each study (solid line: exclusively tree, dashed line: woody species , dotted line: tree mixed with another growth form).
-Shown here are the "raw dataset" (recorded both across and within species, and under unstressed and stressed conditions).}
+\caption{Allometric relationships between a) age and diameter (m), b) age and height (m), and c) diameter and height in trees according to the BAAD database.
+Green and red lines are the cutoffs between stage categories used in the literature.
+Green lines corresponds to limits between juveniles and saplings, red lines to limits between saplings and adults.}
 \label{FigA1}
@@
 
-\begin{figure}[htbp]
+\begin{figure}[h!]
 \centering
 \includegraphics{output/FigA2.pdf}
-\caption{Allometric relationships between a) age and diameter (m), b) age and height (m), and c) diameter and height in trees according to the BAAD database.
-Green and red lines are the cutoffs between stage categories used in the literature.
-Green lines corresponds to limits between juveniles and saplings, red lines to limits between saplings and adults.}
+\caption{Geographical distribution of site locations from studies performed in the field used in the meta-analysis.
+Shown here are the "raw dataset" (recorded both across and within species, and under unstressed and stressed conditions).}
 \label{FigA2}
@@
 
-\begin{figure}[htbp]
+\begin{figure}[h!]
 \centering
 \includegraphics{output/FigA3.pdf}
-\caption{Geographical distribution of site locations from studies performed in the field used in the meta-analysis.
-Shown here are the "raw dataset" (recorded both across and within species, and under unstressed and stressed conditions).}
-\label{FigA3}
-\end{figure}
-
-\begin{figure}[htbp]
-\centering
-\includegraphics{output/FigA4.pdf}
 \caption{Range of correlations (r) between
@@
 points to juveniles.}
+\label{FigA3}
+\end{figure}
+
+\begin{figure}[h!]
+\centering
+\includegraphics{output/FigA4.pdf}
+\end{figure}
+
+\begin{figure}[h!]
+\centering
+\includegraphics{output/FigA4b.pdf}
+\caption{\textbf{Mean coefficient correlation r (+SD) between growth rate and traits, established from 112 articles.} The mean coefficients are weighted by sample size (i.e number of species used to perform the correlation), and calculated both across all plant stages and for each stage.
+Each panel corresponds to a functional trait: \textbf{a)} Specific leaf area (SLA), \textbf{b)} Wood density (WD), \textbf{c)} Net assimilation rate (NARarea), \textbf{d)} Seed mass, \textbf{e)} Asymptotic height (Hmax) and \textbf{f)} Assimilation rate of CO2 (Aarea).
+Shown here are the "unstressed dataset" (recorded across species and under unstressed conditions).}
 \label{FigA4}
@@
 
-\begin{figure}[htbp]
+\begin{figure}[h!]
 \centering
 \includegraphics{output/FigA5.pdf}
-\caption{\textbf{Mean coefficient correlation r (+SD) between growth rate and traits, established from 112 articles.} The mean coefficients are weighted by sample size (i.e number of species used to perform the correlation), and calculated both across all plant stages and for each stage.
-Each panel corresponds to a functional trait: \textbf{a)} Specific leaf area (SLA), \textbf{b)} Wood density (WD), \textbf{c)} Net assimilation rate (NARarea), \textbf{d)} Seed mass, \textbf{e)} Asymptotic height (Hmax) and \textbf{f)} Assimilation rate of CO2 (Aarea).
-Shown here are the "unstressed dataset" (recorded across species and under unstressed conditions).}
-\label{FigA5}
-\end{figure}
-
-\begin{figure}[htbp]
-\centering
-\includegraphics{output/FigA6.pdf}
-\caption{Effect size (+ 95\%CI) of plant stage on the correlations between growth rate and five functional traits across and between species.
-Effects size are calculated for a) Specific leaf area (SLA), b) Wood density (WD), c) Net assimilation rate (NARarea), d) Seed mass, e) Asymptotic height (Hmax) and f) Assimilation rate of CO2 (Aarea).
-Effect size is a standardized measure of the magnitude of the relationship between a particular stage and the correlation coefficient z (Fisher's z-transformed).
-Effects are significant if confidence intervals (+CI95\%) do not overlap with zero.
-LRT: likelihood Ratio Test compared the fit between null model and stage model, both models are fitted by Maximum Likelihood.
-Shown here are the "raw dataset" (recorded both across and within species and under unstressed and stressed conditions).
-'n' indicate the number of independent comparisons for each effect.
-}
-\label{FigA6}
-\end{figure}
-
-\begin{figure}[htbp]
-\centering
-\includegraphics{output/FigA7.pdf}
 \caption{\textbf{Effect size (+ 95\%CI) of plant stage on the correlations between growth rate and five functional traits across species, with a data set averaging multiple comparisons by trait and by study.} Effects size are calculated from a reduced dataset; in the case of multiple comparisons within a study, we calculated the mean correlation coefficient by trait and by study.
@@
 'n' indicate the number of independent comparisons for each effect.}
-\label{FigA7}
+\label{FigA5}
 \end{figure}
 
-\begin{figure}[htbp]
+\begin{figure}[h!]
 \centering
-\includegraphics{output/FigA8a.pdf}
+\includegraphics{output/FigA6a.pdf}
 \end{figure}
 
-\begin{figure}[htbp]
+\begin{figure}[h!]
 \centering
-\includegraphics{output/FigA8b.pdf}
+\includegraphics{output/FigA6b.pdf}
 \end{figure}
 
-\begin{figure}[htbp]
+\begin{figure}[h!]
 \centering
-\includegraphics{output/FigA8c.pdf}
-\end{figure}
-
-\begin{figure}[htbp]
-\includegraphics{output/FigA8d.pdf}
-\centering
-\end{figure}
-
-\begin{figure}[htbp]
-\centering
-\includegraphics{output/FigA8e.pdf}
+\includegraphics{output/FigA6c.pdf}
 \caption{\textbf{Effects size on the correlation between growth and traits of plant stage (mod1), vegetation type (mod2), growth measurement (mod3) and experiment type (mod4).} The effect size (z + 95\%CI) is reported for each class, and models are fitted by restricted max likelihood (REML).
@@
 Shown here are "ideal dataset" (recorded at interspecific and under unstressed condition) and "raw dataset" (recorded at both interspecific and intraspecific level and under unstressed and stressed conditions).}
-\label{FigA8}
+\label{FigA6}
 \end{figure}
 
-\begin{figure}[htbp]
+\begin{figure}[h!]
 \centering
-\includegraphics{output/FigA9.pdf}
+\includegraphics{output/FigA7.pdf}
 \caption{\textbf{Funnel plots with filled in data based on the trim and fill method, showing transformed correlation coefficient z between growth and the traits a) Specific leaf area (SLA), b) Wood density (WD), c) Asymptotic height (Hmax), d) Seed mass and e) Assimilation rate of CO2 (Aarea)}.
@@
 The number of missing values is 9 for SLA,1 for WD, 0 for Hmax, 6 for Seedmass and 0 for Aarea}
+\label{FigA7}
+\end{figure}
 
+\begin{figure}[h!]
+\centering
+\includegraphics{output/FigA8.pdf}
+\caption{\textbf{Growth measurement used by traits and by size.} Shown here are complete dataset (recorded across species and under both unstressed and stressed conditions).
+The colors correspond to the stage for which the r values have been recorded: red bars corresponds adult stage, orange bars to saplings, and grey bars to juveniles.}
+\label{FigA8}
+\end{figure}
+
+\begin{figure}[h!]
+\centering
+\includegraphics{output/FigA9.pdf}
+\caption{\textbf{Temporal changes in coefficient of correlation between traits and growth.
+a) Specific leaf area (SLA), b) Wood density (WD), c) Asymptotic height (Hmax), d) Seed mass and e) Assimilation rate of CO2 (Aarea)} Shown here are ideal dataset (recorded across species and under  unstressed conditions).
+The colors correspond to the stage for which the r values have been recorded: red points corresponds adult stage, orange points to saplings, and grey points to juveniles.}
 \label{FigA9}
@@
 
-\begin{figure}[htbp]
-\centering
-\includegraphics{output/FigA10.pdf}
-\caption{\textbf{Growth measurement used by traits and by size.} Shown here are complete dataset (recorded across  species and under both unstressed and stressed conditions).
-The colors correspond to the stage for which the r values have been recorded: red bars corresponds adult stage, orange bars to saplings, and grey bars to juveniles.}
-\label{FigA10}
-\end{figure}
+\clearpage
+\section{Supporting Analyses}\label{app:supp_info_analyses}
+\subsection{Quantifying and exploring the cause of heterogeneity in effect sizes}
+
+\textbf{Goal:} In our meta-analysis, studies reported differed in design as well as in vegetation types, biome or species studied.
+Such diversity is commonly referred as methodological heterogeneity, and may or may not be responsible for observed discrepancies in the results of the studies.
+The extent of heterogeneity might influence the results of the meta-analysis, and then induces some difficulty in drawing overall conclusions (See \citealt{Higgins:2002iq}).
+It is therefore important to be able to quantify the extent of heterogeneity among a collection of studies.
+
+\textbf{Methods:} A common way of addressing the extent of heterogeneity is the statistic $I^{2}$ (\citealt{Santos:2012gt}, originally defined by \citealt{Higgins:2002iq}).
+$I^{2}$ estimates the consistency of the results obtained from published studies used in our meta-analysis; it describes the percentage of variability in point estimates that is due to heterogeneity rather than sampling error.
+It can be interpreted as a ratio (0\% < $I^{2}$ < 100\%) not affected by the number of studies or the metric of the effect size in the analysis.
+It also has the advantage of being analogous to indices used for regression (where R2 is the proportion of the total variance that can be explained by the covariates) a common statistics in the trait literature.
+
+An $I^{2}$ near zero indicates that almost all of the dispersion will be attributed to random error, and any attempt to explain the variance is an attempt to explain something that is (by definition) random.
+By contrast, as $I^{2}$ moves away from zero we know that some of the variance is real and can potentially be explained by subgroup analysis or meta-regression.
+No universal rule could cover definition for ‘low, ‘moderate’ or ‘high heterogeneity.
+\citealt{Higgins:2003hz} suggested some benchmarks for $I^{2}$ based on the survey of meta-analyses of clinical trials.
+They suggested that values on the order of 25\%, 50\% and 75\% might be considered as "low", "moderate" and "high", respectively.
+These suggestions are tentative; the interpretation of heterogeneity in a systematic review will depend critically on the size and direction of treatment effects, as well as on considerations of methodological diversity in the studies (see \citealt{Borenstein:2009um}).
+Here, we estimated $I^{2}$ as following equation from \citealt{Higgins:2002iq}., then we calculated how part of the heterogeneity may be due to the influence of moderators (stage and publication year) and finally we asked if the residual heterogeneity is statistically significant.
+In R, we used the package metafor (code available on guithub).
+
+\textbf{Results:} We observed high levels of heterogeneity for all traits (SLA :$I^{2}$ 85.4\% CI: 80.9 to 92.1, WD :$I^{2}$ 61.8\% CI: 42.8 to 84.1, Hmax: $I^{2}$ 81.2\% CI: 69.8 to 93.4, Seedmass: $I^{2}$ 91.2\%, 85.9 to 96.1, Aarea: $I^{2}$ 68.3\% CI: 33.7 to 90.1) which suggests that the correlations coefficient r between growth and traits are not uniform across the range of studies investigated.
+This result suggested that a large part of the variance is not explained by sample error.
+
+For SLA and Seedmass, 50.1\% and 20\% respectively of the total amount of heterogeneity were accounted by including the stage as a moderator.
+For the other traits, the stage explained few or no part of the heterogeneity observed across studies (<5\%).
+These results were consistent with our expectations about a shift in the relationship between growth and traits along plant size for SLA, Seed mass and the absence of effect for WD and Aarea (see Theoretical expectation section).
+The result of Hmax was more ambigus since we expected the relationship between asymptotic maximum height (Hmax) and growth rate to be absent in seedlings but to strengthen with increasing plant size (at adult stage).
+As discussed in the result section of the article, the smaller numbers of replicate studies for sapling and seedling stage limited the generality of our conclusion for this trait.
+
+The test for residual heterogeneity was significant for all traits, possibly indicating that others moderators not considered in the model were influencing the correlation between growth and trait.
+This result is not surprising for the trait literature.
+While the trait and growth measurements are standardized \citep{Cornelissen:2003gw}, studies differed largely in their design as well as in vegetation types, biome or species studied.
+Indeed, a goal in the trait literature is to establish general pattern about correlation between growth and traits and to validate them across a large variation of conditions.
+Here, we did not explore the influence of other moderators, since our goal was to test clear hypotheses about the influence of plant size/stage, not to establish the best predictor of the correlation between growth and trait.
+Finally, since between study variation is significant, as indicated by heterogeneity analyses, using the random effect model was more appropriate in our meta-analysis.
+
+\subsection{Testing for publication bias}
+\textbf{Goal:} Studies with significant results are more likely to be published.
+As a consequence, the studies in a meta-analysis may overestimate the true effect size because they are based on a biased sample of the target population of studies.
+A publication bias occurs when the probability of publication depends on the statistical significance of the effect.
+Here we tested if there is an evidence of any bias, and if the effect size observed for each trait is an artefact of this biais.
+
+\textbf{Method:} We first checked the dataset for publication bias with a visual assessment of funnel plots.
+A publication bias toward significant results creates an asymmetric funnel with small studies with non-significant effects missing from the mouth of the funnel on the side opposite to the true effect.
+While funnel plot are recommended to aid interpretation, there is a high risk failing to detect actual publication bias (see (\citealt{Koricheva:2013tz}) by using exclusively a visual assessment.
+In addition, funnel plots are not effective when the number of studies is small (<30) such as for Aarea and Seed mass.
+We also used the ‘trim and fill’ method to estimate the number of studies missing from our meta-analyse. This method adjusts for funnel plot asymmetry \citep{Duval:2000dg}. 
+Finally, we estimated the number of studies needed to overturn a result, using the Rosenberg’s fail-safe number \citep{Rosenberg:2005hk}.
+The fail-safe N is not based on funnel plot asymmetry.
+The Rosenberg method calculates the number of studies averaging null results that would have to be added to the given set of observed outcomes to reduce significance level (p-value) of the weighted average effect \citep{Rosenberg:2005hk}.
+A significant meta-analytic result is robust if the fail-safe N is greater than 5k+10, where k is the number or studies already in the meta-analysis \citep{Rosenthal:1979do}.
+In R, we used the package metafor (code available on guithub).
+
+\textbf{Result:} As expected the correlation coefficient varied less widely as sample size increased (funnel plots in Fig.
+\ref{FigA9}).
+Funnel plots exhibited a typical funnel shape for all five functional traits analyzed, showing no evidence for publication bias (Fig.
+\ref{FigA9}).
+The ‘trim and fill’ method detected some missing values in our data.
+The estimated number of missing value ranges from 0 to 9 depending on the trait considered (Fig.
+\ref{FigA9}).
+The overall estimates measured with the fill in data changed from 0.5 ±0.07 to 0.4 ±0.07 for SLA and from -0.48±0.11 to -0.32±0.12 for the seed mass, suggesting a lower correlation coefficient for SLA, and Seedmass.
+Even if the estimated correlation were closest from zero with the missing studied filled in, the results still indicate that the effect is statistically significant.
+The Rosenberg’s Fail-safe N are 7086, 1823, 990, 574, 291 for SLA, WD, Hmax, Seedmass and A area, suggesting that there would need to be over a large number of studies with a mean correlation coefficient of 0 added to the analysis before the cumulative correlation would become non significant.
+N is greater than 5k+10 for all traits.
+All together these result suggest that the impact of bias is probably trivial in our meta-analyses.
+
+\subsection{Exploring temporal changes in effect size}
+\textbf{Goal:} Our meta-analysis combines data from studies published between 1983 and 2014.
+It has been shown that the magnitude of the effect size may changes over time due to a publication bias (i.e.
+a lag to publish negative results), a change in the methodology or biological changes in the magnitude of the effect (see \citealt{Koricheva:2013hy}).
+Therefore, detecting such temporal changes may be important to the interpretation of the results of a meta-analysis.
+
+\textbf{Method:} In the trait literature the year of publication may be confounded with a methodological change.
+Indeed, in the early 90’s studies mainly focused on seedlings, whereas today a broader range of plant size/stage are studied (Fig.
+\ref{FigA9}).
+As a consequence, we used publication year as a moderator in our analyses \citep{Zvereva:2008jm}p across and within stages for all traits.
+
+\textbf{Results:} There was a change in the effect size with publication year for SLA (pvalue<0.0001, estimates: -0.04 ±0.009), Seed mass (pvalue =0.011, estimates: 0.041 ±0.016) and Aarea (pvalue=0.0102, estimates: -0.0453± 0.0176).
+The Fig.
+\ref{FigA9} showed that for these 3 traits the publication years may be confounded with plant stage; the correlation coefficients have been reported from 1993, but studies started to report data on adult stage only 10 years later (around 2000-2007).
+
+For SLA and Seed mass, a publication year effect was not observed within seedling and sapling stages, but was identified for the adult stage (SLA pvalue=0.003, Seedmass pvalue=0.06).
+For both SLA and Seedmass, the magnitude of the effect size decreased with publication year (Fig.
+\ref{FigA9} a and d), suggesting we overestimated the magnitude of the effect size for these two traits.
+In reality, the main effect size obtained would be more close to zero or more negative for SLA and more positive for Seedmass.
+These results are consistent with our hypotheses; we expected a negative or non-significant effect of SLA on growth in adult stage, and a non-significant or positive effect of Seed mass on plant growth (see theoretical expectation).
+
+For Aarea, publication year explained a part of the variation across stage but not within stage, and the magnitude of the effect size decreased with publication year.
+This pattern is classic in meta-analyses; \citealt{Koricheva:2013hy} showed that a majority of studies reported a decrease rather than an increase in the magnitude of effect size with publication year.
+Yet, here this effect did not lead to a loss of the statistical significance of the main effect size or to a change of sign.
+While overestimated, the main effect size for the correlation between growth and Aarea stay positive  (Fig.
+\ref{FigA9} e).
+
+The temporal change were confounded with a plant stage effect in our meta-analyse, but they did not jeopardizing the stability of our conclusions.
+The conclusions of a meta-analyses conducted in different year may not differ from the one reported here.
 

### 2015-08-10 R/model.R

@@ -785,6 +785,7 @@ fun_Heterogeneity.H <- function(x, mods){
 }
 
 
+
 fun_trim.and.fill_number  <- function(x){ 
                       res <-  rma(corr.z, vr.z, data=x[!is.na(x$corr.z) & !is.na(x$vr.z),])
                       ### carry out trim-and-fill analysis
@@ -793,4 +794,26 @@ fun_trim.and.fill_number  <- function(x){
                      
 }
 
-x=GIi[["SLA"]]
+
+fun_year <- function(data){
+            table <-  data
+            
+            res <- rma(corr.z, vr.z, mod= ~year ,data=table[!is.na(table$corr.z) & !is.na(table$nb.sp),])
+           
+            x<- subset(table, table$stage=="juvenile")
+            res_juv <- rma(corr.z, vr.z, mod= ~year ,data=x[!is.na(x$corr.z) & !is.na(x$nb.sp),])
+          
+            y <-subset(table, table$stage=="sapling")
+            res_sap <- rma(corr.z, vr.z, mod= ~year ,data=y[!is.na(y$corr.z) & !is.na(y$nb.sp),])
+            
+            z <-subset(table, table$stage=="adult")
+            res_adu <- rma(corr.z, vr.z, mod= ~year ,data=z[!is.na(z$corr.z) & !is.na(z$nb.sp),])
+            
+            l <- list("all"=res, "juvenile"=res_juv, "sapling"=res_sap, "adult"= res_adu)
+            
+            l
+           
+}
+
+# x <- subset(x, x$stage=="juvenile")
+# res_null <- rma(corr.z, vr.z, mod= ~year ,data=x[!is.na(x$corr.z) & !is.na(x$nb.sp),])

### 2015-08-10 analysis.R

@@ -63,46 +63,50 @@ dir.create("output", showWarnings =FALSE)
 write.csv(RawData, "output/data.csv", row.names=FALSE)
 
 ## Make output
-pdf("output/FigA1.pdf", height=6) # In the main text, need to be changed
-figure_A1(CompleteData_inter)
-dev.off()
-
 pdf("output/Fig1.pdf",height=3, width=4) # ok
   figure_1(RawData)
 dev.off()
 
+pdf("output/Fig2.pdf", height=6) # In the main text, need to be changed
+figure_A1(CompleteData_inter)
+dev.off()
 
-pdf("output/Fig2.pdf",height=6,width=5) # ok
+
+pdf("output/Fig3.pdf",height=6,width=5) # ok
   figure_2(GCi, GIi)
 dev.off()
 
 
-pdf("output/FigA4.pdf",height=6,width=6) # maybe in the main text
+
+pdf("output/FigA1.pdf", height=6, width=6) # ok , maybe need to put only the line address in the text
+figure_allometry()
+dev.off()
+
+
+pdf("output/FigA2.pdf", height=3, width=6)# ok
+figure_map(CoordTable)
+dev.off()
+
+
+pdf("output/FigA3.pdf",height=6,width=6) # maybe in the main text
 figure_A4(GCi)
 dev.off()
 
 
-pdf("output/FigA2.pdf", height=6, width=6) # ok , maybe need to put only the line address in the text
-  figure_allometry()
-dev.off()
 
-pdf("output/FigA3.pdf", height=3, width=6)# ok
-  figure_map(CoordTable)
-dev.off()
-
-
-pdf("output/FigA5.pdf",height=6,width=5) # need to be change, both graph on the same page
+pdf("output/FigA4.pdf",height=6,width=5) # need to be change, both graph on the same page
 figure_A5(GIi)
+dev.off()
+
+pdf("output/FigA4b.pdf",height=6,width=5) 
 figure_A5b(GIrgr, GIagr)
 dev.off()
-
-
 # pdf("output/FigA6.pdf",height=6,width=5)
[…]

### 2015-08-31 MS.tex
ms edition

@@
 
-\author[1]{Anais Gibert}
+\author[1]{Anais Gibert*}
 \author[1]{Emma F. Gray}
@@
 
-\textit{Keywords (8/10)} asymptotic maximum height, maximum photosynthetic rate, plant ontogenetic stage, plant functional traits, plant growth strategy, seed mass, specific leaf area, wood density
-
-\textit{corresponding author} Anais Gibert, anais.gibert@gmail.com, Dept of Biological Sciences, Macquarie University, Sydney, NSW 2109, Australia, tel: +61 2 9850 8194
-
-\textit{Statement of authorship} MW, DF, IW, AG designed the study, IW and DF provided their bibliography database, AG and EG searched and collected the data, AG performed the meta-analyses, DF performed modeling work, AG wrote the first draft, MW improved substantially the manuscript, and all authors contributed to revisions.
+\textit{Corresponding author} Anais Gibert, anais.gibert@gmail.com, Dept of Biological Sciences, Macquarie University, Sydney, NSW 2109, Australia, tel: +61 2 9850 8194
 
@@
 
-\section*{Abstract}\label{abstract}
+\section*{Abstract (195/350 words)}\label{abstract}
 
@@
 \item 
-We show that traits-GR correlations change in a predictable way as a function of plant size.
+Synthesis: We show that traits-GR correlations change in a predictable way as a function of plant size.
 Our understanding of plant strategies should shift away from attributing slow vs fast growth to species throughout life, in favour of attributing growth trajectories.
@@
 
+\textit{Keywords (8/10)} asymptotic maximum height, maximum photosynthetic rate, plant ontogenetic stage, plant functional traits, plant growth strategy, seed mass, specific leaf area, wood density
+
 \section*{Introduction}\label{introduction}
-The phrase "plant ecological strategy" refers to how species face the challenge they all share:  to acquire sufficient water, nutrients and light for individual growth and to live long enough to replace themselves with offspring.
+Plant "ecological strategy" refers to how species face the challenge they all share: to acquire sufficient water, nutrients and light for individual growth and to live long enough to replace themselves with offspring.
 An idea that species strategy differences might involve fast vs slow growth goes back at least to Grime and Hunt \citeyearpar{Grime:1975gr}, who measured a wide spread of relative growth rates for seedlings during early exponential growth under favourable conditions.
-Seedling potential relative growth rate (RGR, the change in a mass/height or diamater per time interval relative to initial size) has continued to be used as a major strategy indicator within the CSR (Competitor - Stress tolerator - Ruderal) scheme (e.g.
+Seedling potential relative growth rate (RGR) has continued to be used as a major strategy indicator within the CSR (Competitor - Stress tolerator - Ruderal) classification (e.g.
 \citealt{grime1979plant, Grime:1997wm}).
@@
 From the 1990s a new style of "trait ecology" arose whereby measurable traits including SLA were used directly as strategy axes \citep{Westoby:2002ft}.
-An approach via measurable traits made broad comparisons possible across continents and latitudes and thousands of species.
-Traits have been seen as constructive approaches to understanding plant growth strategies \citep{Grime:1977kc,Chapin:1980gz}, community composition \citep{Lavorel:2002ff,Shipley:2006ie}, global vegetation dynamics \citep{Scheiter:2013ed} and ecosystem processes \citep{Lavorel:2002ff}.
+This approach via measurable traits made broad comparisons possible across continents and latitudes and thousands of species.
+Since then, traits have been seen as constructive approaches to understanding plant growth strategies \citep{Grime:1977kc,Chapin:1980gz}, community composition \citep{Lavorel:2002ff,Shipley:2006ie}, global vegetation dynamics \citep{Scheiter:2013ed} and ecosystem processes \citep{Lavorel:2002ff}.
 
-Currently two main spectra of variation are widely cited as underpinning differences between species in vegetative growth rates.
+Currently, two main spectra of variation are widely cited as underpinning differences between species in vegetative growth rates.
 The 'leaf economic spectrum' \citep{Wright:2004jb} and the 'wood economic spectrum' \citep{Chave:2009iy} reflect tissue construction costs (for specific leaf area and for wood volume respectively) trading off with tissue turnover rates or mortality risks.
@@
 \citealt{MullerLandau:2004dc,Wright:2004jb,Poorter:2008iu,Chave:2009iy,Larjavaara:2010bn,Iida:2012jb,Paine:2015df}).
-Yet a growing number of empirical studies indicate the correlation between traits and growth is not as consistent as that.
+Yet, a growing number of empirical studies indicate the correlation between traits and growth is not as consistent as that.
 Consider SLA as an illustration.
@@
 Recent theory suggests that the absence of a correlation between SLA and growth at larger sizes may be expected, when potential influences of traits on plant function are considered \citep{Falster:2011ii, falster:2013}.
-At larger sizes the low-cost deployment benefits of high SLA may be offset or even outweighed by the high costs of rapid leaf turnover (see Text Box 1\ref{sec:growth}).
+At larger sizes the low-cost deployment benefits of high SLA may be offset or even outweighted by the high costs of rapid leaf turnover \citep{Falster:2011ii, falster:2013}.
+Recently, some empirical studies examined the relationships between functional traits and demographic rates across a wide range of tree sizes in specific experimental site (see \citealt{Iida:2014ep, Iida:2014hq}) and suggested a variation with plant size.
+However, it is still an opening question whether the influence of traits on growth change with plant size in a predictable and consistent way across different environemtal context.
 
-Here, we review published literature reporting on relationships between plant growth and five prominent traits (specific leaf area = SLA, wood or stem tissue density = WD, maximum leaf photosynthetic capacity per unit area = Aarea,  maximum height= Hmax, and seed mass= SM) in tree or woody species in order to assess the following questions.
+In this study, we review published literature reporting on relationships between plant growth and five prominent traits (specific leaf area = SLA, wood or stem tissue density = WD, maximum leaf photosynthetic capacity per unit area = Aarea,  maximum height= Hmax, and seed mass= SM) in tree or woody species in order to assess the following questions.
 
@@
   \item How general is the tendency for correlations between traits and growth rate to vary with plant size?
-  \item Do the observed relationships conform to predictions (outlined below) from a recently developed  mechanistic
-model \citep{Falster:2011ii, falster:2013}?
+  \item Do the observed relationships conform to predictions (outlined below) from a recently developed mechanistic model \citep{Falster:2011ii, falster:2013}?
+  \item
 \end{enumerate}
 
-While most studies on traits have not been concerned with effects of plant stage or size, they have reported trait-growth correlations for identifiable size classes.
-We gathered correlation coefficients between trait and growth from studies that gave explicit information about the size or stage of the plants.
-Meta-analysis allowed us to generalize about trait influences on growth.
+While most studies on traits have not been concerned with effects of plant stage or size, they have reported trait-growth correlations for identifiable size/stage classes.
+Thus, we gathered correlation coefficients between traits and growth from studies that gave explicit information about the size or stage of the plants.
+Meta-analytic approach offers several advantage, in particular it allows us to generalize about the influence of traits on growth across different ecological context.
 
@@
 Recent theoretical work \citep{Falster:2011ii} allows hypotheses to be formulated about relationships between traits and growth, based on a mathematical decomposition of plant growth rate.
-Specific predictions arise from considering the influence of traits on elements of these equations and how these effects may vary with size (see Text Box 1\ref{sec:growth}).
+Specific predictions arise from considering the influence of traits on elements of these equations and how these effects may vary with size (see Appendix\ref{sec:growth} for mathematical explanations).
 
@@
 
-The correlation between trait and growth is predicted to revert according to the growth measurement used for both SLA and seed mass (see Text Box 1\ref{sec:growth}).
+The correlation between trait and growth is predicted to revert according to the growth measurement used for both SLA and seed mass (see Appendix 1\ref{sec:growth}).
 Tree growth in diameter, height or mass can be expressed in either absolute (AbsGR) or relative terms (RGR).
@@
 
-To test how general is the tendency for correlations between traits and growth rate to vary with plant size, we focused on an initial list of 20 traits (Fig.
+We focused on an initial list of 20 traits (Fig.
 \ref{Fig1}).
@@
 Following recent recommendations for the adoption of a checklist of quality criteria for meta-analysis in ecology (\citealt{Koricheva:2014ku}), we conducted several analyses to assess the reliability of our meta-analysis.
-Table A2 in Appendix 1 reported how and where (i.e in the text, appendix and/or figures) we addressed the 14 methodological quality criteria listed by \citet{Koricheva:2014ku}.
+Table 2 reported how and where (i.e in the text, appendix and/or figures) we addressed the 14 methodological quality criteria listed by \citet{Koricheva:2014ku}.
 

### 2015-09-01 MS.tex
MS: change text introduction, and mat and met

@@
 Traits should influence growth in a way that depend on individual plants size.
-We outline mechanisms and hypotheses based on new theory, and test these predictions in tree species for five traits using a meta-analysis of 112 studies (> 500 correlations).
-As an approximation of plants size, we analysed the shift in the correlations between growth and traits across plant stages.
+We outline mechanisms and hypotheses based on new theory, and test these predictions in tree species for five traits using a meta-analysis of 112 studies ( > 500 correlations).
+As a first approximation of plants size, we analysed the shift in the correlations between growth and traits across three plant stages (i.e.
+juvenile, sapling and adult).
 
@@
 Results were consistent with predictions.
-Specific leaf area was correlated with GR in small but not large plants.
-Correlations of GR with wood density and assimilation rate were not affected by size.
-Maximum height and seed mass were correlated with GR only in one plant size category.
+Specific leaf area was correlated with GR in juvenile but not in adult plants.
+Correlations of GR with wood density and assimilation rate were not affected by stage.
+Maximum height and seed mass were correlated with GR only in one plant stage category.
 
@@
 
+\clearpage
+
 \section*{Introduction}\label{introduction}
-Plant "ecological strategy" refers to how species face the challenge they all share: to acquire sufficient water, nutrients and light for individual growth and to live long enough to replace themselves with offspring.
+Plant "ecological strategy" refers to how species face the challenge they all share: to acquire sufficient water, nutrients and light to live long enough to replace themselves with offspring.
+Growth rates have often been seen as central elements of plant ecological strategies.
 An idea that species strategy differences might involve fast vs slow growth goes back at least to Grime and Hunt \citeyearpar{Grime:1975gr}, who measured a wide spread of relative growth rates for seedlings during early exponential growth under favourable conditions.
@@
 From the 1990s a new style of "trait ecology" arose whereby measurable traits including SLA were used directly as strategy axes \citep{Westoby:2002ft}.
-This approach via measurable traits made broad comparisons possible across continents and latitudes and thousands of species.
+An approach via measurable traits made broad comparisons possible across continents and latitudes and thousands of species.
 Since then, traits have been seen as constructive approaches to understanding plant growth strategies \citep{Grime:1977kc,Chapin:1980gz}, community composition \citep{Lavorel:2002ff,Shipley:2006ie}, global vegetation dynamics \citep{Scheiter:2013ed} and ecosystem processes \citep{Lavorel:2002ff}.
@@
 Recent theory suggests that the absence of a correlation between SLA and growth at larger sizes may be expected, when potential influences of traits on plant function are considered \citep{Falster:2011ii, falster:2013}.
-At larger sizes the low-cost deployment benefits of high SLA may be offset or even outweighted by the high costs of rapid leaf turnover \citep{Falster:2011ii, falster:2013}.
-Recently, some empirical studies examined the relationships between functional traits and demographic rates across a wide range of tree sizes in specific experimental site (see \citealt{Iida:2014ep, Iida:2014hq}) and suggested a variation with plant size.
-However, it is still an opening question whether the influence of traits on growth change with plant size in a predictable and consistent way across different environemtal context.
+At larger sizes the low-cost deployment benefits of high SLA may be offset or even outweighted by the high costs of rapid leaf turnover (see section "Theoretical expectations").
+While recent empirical studies supported the idea of a variation in the relationships between traits and growth rates across plant sizes (\citealt{Iida:2014ep, Iida:2014hq}), the trend and mechanisms behind this variation remain unclear.
+It is still an opening question whether the influence of traits on growth change with plant size in a predictable and consistent way.
 
-In this study, we review published literature reporting on relationships between plant growth and five prominent traits (specific leaf area = SLA, wood or stem tissue density = WD, maximum leaf photosynthetic capacity per unit area = Aarea,  maximum height= Hmax, and seed mass= SM) in tree or woody species in order to assess the following questions.
-
+In this paper, we used a meta-analytic approach on five prominent traits (specific leaf area = SLA, wood or stem tissue density = WD, maximum leaf photosynthetic capacity per unit area = Aarea, maximum height= Hmax, and seed mass= SM) to investigate:
 \begin{enumerate}
   \item How general is the tendency for correlations between traits and growth rate to vary with plant size?
-  \item Do the observed relationships conform to predictions (outlined below) from a recently developed mechanistic model \citep{Falster:2011ii, falster:2013}?
-  \item
+  \item  Do the observed relationships conform to predictions (outlined in section "Theoretical expectations") from a recently developed mechanistic model (Falster et al., 2011; Falster, 2013)?
 \end{enumerate}
-
-While most studies on traits have not been concerned with effects of plant stage or size, they have reported trait-growth correlations for identifiable size/stage classes.
-Thus, we gathered correlation coefficients between traits and growth from studies that gave explicit information about the size or stage of the plants.
-Meta-analytic approach offers several advantage, in particular it allows us to generalize about the influence of traits on growth across different ecological context.
+We gathered correlation coefficients between trait and growth from studies that gave explicit information about the size or stage of the plants.
+While most studies on traits have not been concerned with effects of plant size, they have generally reported trait-growth correlations for identifiable stage classes.
+We used plant stage (i.e.
+juvenile, sapling and adult) as a first approximation of plant size.
+We focused mainly on tree and woody species since the mechanistic model used to assess our predictions is most applicable to tree.
 
@@
 
-Recent theoretical work \citep{Falster:2011ii} allows hypotheses to be formulated about relationships between traits and growth, based on a mathematical decomposition of plant growth rate.
+Recent theoretical work \citep{Falster:2011ii} allows us to formulate hypotheses about relationships between traits and growth, based on a mathematical decomposition of plant growth rate.
 Specific predictions arise from considering the influence of traits on elements of these equations and how these effects may vary with size (see Appendix\ref{sec:growth} for mathematical explanations).
@@
 
-We focused on an initial list of 20 traits (Fig.
-\ref{Fig1}).
-These traits have been selected because they capture different aspects of plant species strategies, and are commonly addressed in the functional traits litterature.
-Specific leaf area (SLA), leaf area, leaf nitrogen and phosphorus concentration, net (mass) assimilation rates (NAR), and assimilation rate of CO$_2$ (Aarea) are traits involved in species leaf economic strategy \citep{Wright:2004jb,Wright:2010tp}.
-Seed mass (SM), and maximum plant height (Hmax) capture information about reproductive strategy \citep{Falster:2005bw,Moles:2006ft}.
-Wood density (WD) and sapwood area per leaf area (SA/LA), vessel size and density, and stem specific conductance are all involved in species wood economic strategy \citep{Chave:2009iy}.
-Here WD and SA/LA are also considered as indicators of stem construction cost \citep{Falster:2011ii}, whereas SLA and leaf thickness capture crucial information about leaf construction cost \citep{Wright:2004jb}.
-Finally, the leaf area ratio and leaf mass ratio are indicators of resource allocation to leaf \citep{Lambers:1992bj}.
-
-We aimed to identify studies that measured the correlation between a functional trait and a growth measurement across species.
-We searched for relevant studies using a three step procedure.
-First, we identified traits for which a substantial number of studies would be available using a literature snapshot in Web of Science.
+\subsection*{Literature snapshot}\label{literature-snapshot}
+We aimed to identify studies that measured the correlation between five prominent functional trait (SLA, WD, Aarea, Hmax and Seed mass) and a growth measurement across species.
+A snapshot of the literature on Web of Science database (Thomson Reuters) showed that 82\% of the literature for these 5 traits is captured by searching only on SLA and WD.
+This snapshot was performed between March and June 2014 using a range of Boolean search terms in English.
+Search terms were as follows: (''TRAIT'' AND (''growth rate'' OR ''relative growth rate'')) AND (''tree*'' OR ''woody*''), ''TRAIT'' was all trait names listed in Table A1.
 While Web of Science guarantees a relatively stable and reproducible search environment, with clearly defined lists of indexed journals, its searches are restricted to metadata, such as title, keywords and abstracts \citep{Beckmann:2012hn}.
 This limitation does not apply to Google Scholar, where, theoretically, all text that is electronically available on the Internet will be indexed.
-Thus, our second step was to systematically read documents returned by Google scholar for a restricted set of traits.
-Finally, we identified and recorded other possible data sources using our own knowledge as researchers in the field (this included adding data from an as-yet unpublished study by Gleason et al).
-The complete list of studies where we inspected the full text is given in Appendix \ref{app:supp_info_files} in Supplementary material.
-
-\subsection*{Literature snapshot}\label{literature-snapshot}
-
-The Web of Science database (Thomson Reuters) was searched between March and June 2014 using a range of Boolean search terms in English.
-Search terms were as follows: (''NAME'' AND (''growth rate'' OR ''relative growth rate'')) AND (''tree*'' OR ''woody*''), ''NAME'' was one of trait names listed in TableA1.
-According to this snapshot, 62\% of the literature for the 20 traits (or 82\% for the 5 traits for which we have clear predictions) is captured by searching only on SLA and WD.
+Thus, we used Google Scholar to perform a more systematic search of the literature for SLA and WD.
 
 \subsection*{Systematic search}\label{systematic-search}
-
 Google Scholar database was searched using the range of Boolean search terms for SLA and WD.
@@
 Thus, in Google Scholar we displayed papers by relevance and examined the first 750 items.
+We also identified and recorded other possible data sources using our own knowledge as researchers in the field (this included adding data from an as-yet unpublished study by Gleason et al).
+To avoid publication bias due to selective reporting of significant results within published articles (e.g.~particular case of a 'failure to publish bias' see \citealt{Jennions:2013ta}), we asked the authors for additional information when they reported a non-significant correlation between growth and trait without reporting a correlation coefficient value.
+The complete list of studies where we inspected the full text is given in Appendix \ref{app:supp_info_files} in Supplementary material.
+
 Each study had to meet some basic criteria to be included in our analysis.
 We restricted our meta-analysis to documents reporting: i) the relationship between growth and trait as a correlation coefficient, ii) the sample size and the number of species used to perform the correlation, and iii) the size/stage of plants.
-Where available we also recorded the geographic coordinates, number of sites, experiment type (greenhouse, field experiment, forest, shade-house etc.), growth measure (relative or absolute growth rate measured using plant diameter, height or mass), vegetation type, life form (tree, woody or mixed with herbaceous species etc.), biological scale (interspecific, intraspecific or intragenus), and experimental treatments (e.g.~fertilization, shade, salt stress).
-Ultimately data was included from 112 different studies (starred references in bibliography).
-The articles laid aside because they did not meet our criteria are listed in Appendix \ref{app:supp_info_files} in Supplementary material.
+Ultimately data was included from 112 different articles (starred references in bibliography).
+Where available we also recorded the geographic coordinates, number of sites, experiment type (greenhouse, field experiment, forest, shade-house etc.), growth measure (relative or absolute growth rate measured using plant diameter, height or mass), vegetation type, life form (tree, woody or mixed with herbaceous species etc.), biological scale (interspecific, intraspecific or intragenus), experimental treatments (e.g.~fertilization, shade, salt stress), and data for additional traits.
+We reported coefficient correlations for a list of 20 traits (Fig.
+\ref{Fig1}): the five for which we had prior expectations, plus 15 others which capture different aspects of plant species strategies.
+Specific leaf area (SLA), leaf area, leaf nitrogen and phosphorus concentration, net (mass) assimilation rates (NAR), and assimilation rate of CO2 (Aarea) are traits involved in species leaf economic strategy \citep{Wright:2004jb,Wright:2010tp}.
+Seed mass (SM), and maximum plant height (Hmax) capture information about reproductive strategy \citep{Falster:2005bw,Moles:2006ft}.
+Wood density (WD) and sapwood area per leaf area (SA/LA), vessel size and density, and stem specific conductance are all involved in species wood economic strategy  \citep{Chave:2009iy}.
+Here WD and SA/LA are also considered as indicators of stem construction cost (\citep{Falster:2011ii}, whereas SLA and leaf thickness capture crucial information about leaf construction cost \citep{Wright:2004jb}.
+Finally, the leaf area ratio and leaf mass ratio are indicators of resource allocation to leaf \citep{Lambers:1992bj}.
+According to the snapshot of the literature on Web of Science, 62\% of the literature for these 20 traits were captured by a search on SLA and WD.
 
+\subsection*{Plant stage categories}\label{plant-stage-categories}
+
+The authors of the 112 articles reported in our meta-analyses, categorized plants into four differents stages (i.e.
+seedling, juvenile, sapling, adult).
+While the stage categories have been established according to the expertise and the appreciation of the authors, by compiling data across multiple studies and across different growth form (tree and woody, etc), there is a risk of assigning plants of similar size to different categories.
+We verified the consistency of size/age range attributed to each stage across the 112 studies reported here.
+Fig.
+\ref{Fig2} showed that the threshold in size/age used by the authors to defined a plant stage are quite steady.
+In particular, there was a clear break between seedlings and saplings in both age (at 1 yr) and height (at 0.5 m); there was also a clear break between saplings and adults in diameter (at 10 cm).
+According to simple allometric relationships from the Biomass And Allometry Database (BAAD) \citep{Falster:2015}, these stage cutoffs match across the different size measurements (i.e.
+diameter, height and age, Fig.
+\ref{FigA1}).
+The size/stage threshold defined across the 112 articles, allowed us to attribute straightforwardly a stage category to studies for which no stage have been distinctly mentionned by the authors (5\% of the data, noted as 'mix' in Fig.
+\ref{Fig2}).
+
+Less than 5\% of the studies (i.e.
+five studies on 112) were ambiguous on their plant stage attribution.
+Half of these equivocal cases involved the juvenile category.
+The term "juvenile" is vague enough to cover size range from either seedling or sapling stages.
+according to the authors.
+This redundancy encourages us to focus on a three stage classification (i.e.
+juvenile, sapling, adult).
+In the rest of the mansucript we preferred the term "juvenile" to "seedling", because for a portion of the scientific community "seedling" also refers to a particular experimental condition (a greenhouse experiment).
+We attributed a study to a new stage category only when 95\% of the recorded range of sizes for that study lay within a new stage category.
+The others equivocal cases were caused by an ambiguity in the definition of "adult" used by the authors.
+Some plants with a large stature are not assessed as adult by the authors because they are still non reproductive.
+Here, we attributed a study to the adult stage when the authors identified the plants as reproductive, and to sapling stage when they identified the plants as non-reproductive, regardless the plant size or age.
+Results using the categories established by the authors are similar than the one using the standardized categories and are available in Fig.
+\ref{FigA5} model.1.
+In the main text, we report the results using the standardized categories.
+
+\subsection*{Statistical analyses}\label{statistical-analyses}
 The number of species used to perform the correlation, the experimental conditions, and the concordance between stage used to measure trait and growth are clear criteria for assessing the quality of the data for addressing our hypotheses.
@@
 adult stage).
-We weighted our data by number of species rather than the sample size for all statistical analyses (see Statistical analyses section).
-Finally, to avoid publication bias due to selective reporting of significant results within published articles (e.g.~particular case of a 'failure to publish bias' see \citealt{Jennions:2013ta}), we asked the authors for additional information when they reported a non-significant correlation between growth and trait without reporting an r value.
-
-\subsection*{Plant size categories}\label{plant-size-categories}
-
-We acknowledge that it would be better to address plant size as a continous variable, but the limited number of correlations available in the literature along plant size constrains us to approximate plant size by plant stage.
-The authors of the 112 articles reported in our meta-analyses, categorized plants into four differents stages (i.e.
-seedling, juvenile, sapling, adult).
-They also reported plant size informations in diameter, height or age (generally the authors give the size of the smallest and the biggest plants species used in their analyses).
-
-While the stage categories have been established according to the expertise and the appreciation of the authors, by compiling data across multiple studies and across different growth form (tree, woody, etc), there is a risk of assigning plants of similar size to different categories.
-Thus, we tested how consistent were the range values in size/age attributed to each stage across the 112 studies, and across the different growth form (tree, woody and across growth form, (Fig.
-\ref{Fig2}).
-Suprisingly, the threshold in size/age used by the authors to defined a plant stage are quite steady across the 112 studies (Fig.
-\ref{Fig2}).
-In particular, there was a clear break between seedlings and saplings in both age (at 1 yr) and height (at 0.5 m); there was also a clear break between saplings and adults in diameter (at 10 cm).
-The distinctions between sapling-adult in age (around 5 yrs) and height (around 2 m), and between seedling-sapling in diameter (around 1cm) were less pronounced.
-We used simple allometric relationships from the Biomass And Allometry Database (BAAD) \citep{Falster:2015} to ensure that these size/stage cutoffs match across the different size measurements (i.e.
-diameter, height and age, Fig.
-\ref{FigA1}).
-For instance, we showed according to BAAD that a sapling with a diameter < 10 cm would have a height < 1 m.
-Thus, according to the size/stage threshold established across 112 studies, the plant will be assigned to the sapling stage whatever we focused on its diameter or height (see Fig.
-\ref{FigA1} c).
-
-There were an ambiguity on the plant stage attribution for less than 5\% of the studies (i.e.
-5 studies on 112).
-We re-red carefully each of these studies, looking at any particular reason addressed by authors that could explained these discrepancies.
-Interestingly, these discrepancies were not due to a differences between growth form; all the ambiguous cases corresponds to studies focusing exclusively on tree species (Fig.
-\ref{FigA1}).
-In fact, we identified two main explanations.
-First, the term "juvenile" was vague enough to cover either seedling or sapling stages according to the authors.
-Second, the reproductive state of a plant is not strictly correlated to plant size; some plants with a large stature are not assessed as adult because the authors selected them to be non reproductive (See ID 50, 52 and 105 in Fig.
-\ref{FigA1}).
-Thus, we attributed a study to a new stage category when 95\% of the recorded range of sizes for that study lay within a new category.
-And, we attributed a study to the adult stage when the authors identified the plants as reproductive regardless the plant size or age.
-The size/stage threshold defined across the 112 articles, allowed us to attribute straightforwardly a stage category to studies for which no stage have been distinctly mentionned by the authors (5\% of the data, noted as 'mix' in Fig.
-\ref{Fig2}).
-Finally, we run the analyses with both the old and the standardized categories to ensure that the different stage attribution will not disturb our results.
-
-Results using the categories established by the authors are similar than the one using the standardized categories and are available in Fig.
-\ref{FigA5} model.1.
-In the main text, we report the results using the standardized categories.
-In the rest of the mansucript, we preferred the term "juvenile" to "seedling", because for a portion of the scientific community "seedling" also refers to a particular experimental condition (a greenhouse experiment).
-
-\subsection*{Effect size calculation}\label{effect-size-calculation}
 
@@
 
-\subsection*{Statistical analyses}\label{statistical-analyses}
-
 We tested stage effect on traits for which > 15 correlation coefficients across at least two stages were recorded.
@@
 Following recent recommendations for the adoption of a checklist of quality criteria for meta-analysis in ecology (\citealt{Koricheva:2014ku}), we conducted several analyses to assess the reliability of our meta-analysis.
-Table 2 reported how and where (i.e in the text, appendix and/or figures) we addressed the 14 methodological quality criteria listed by \citet{Koricheva:2014ku}.
+Table 2 detailed how and where (i.e in the text, appendix and/or figures) we addressed the 14 methodological quality criteria listed by \citet{Koricheva:2014ku}.
 

### 2015-09-02 MS.tex
Change in text

@@
 Traits should influence growth in a way that depend on individual plants size.
-We outline mechanisms and hypotheses based on new theory, and test these predictions in tree species for five traits using a meta-analysis of 112 studies ( > 500 correlations).
+We outline mechanisms and hypotheses based on new theory, and test these predictions in tree species for five traits using a meta-analysis of 112 studies (> 500 correlations).
 As a first approximation of plants size, we analysed the shift in the correlations between growth and traits across three plant stages (i.e.
@@
 \citealt{grime1979plant, Grime:1997wm}).
-Meanwhile partitioning of seedling RGR into its components showed that specific leaf area (SLA = 1/leaf mass per area LMA) was typically the strongest source of variation between species \citep{Poorter:1989tx}.
+Meanwhile partitioning of seedling RGR into different components showed that specific leaf area (SLA = 1/leaf mass per area LMA) was typically the strongest source of variation between species \citep{Poorter:1989tx}.
 From the 1990s a new style of "trait ecology" arose whereby measurable traits including SLA were used directly as strategy axes \citep{Westoby:2002ft}.
@@
 
-\textbf{H2: The relationship between wood or stem density (WD) and growth rate is expected to be negative across all plant sizes}
+\textbf{H2: The relationship between wood or stem density (WD) and growth rate is expected to be negative across all plant size}
 
@@
 \textbf{Effect on absolute (AbsGR) and relative growth rate (RGR)}  
-
-The correlation between trait and growth is predicted to revert according to the growth measurement used for both SLA and seed mass (see Appendix 1\ref{sec:growth}).
 Tree growth in diameter, height or mass can be expressed in either absolute (AbsGR) or relative terms (RGR).
-Here, the predicted relationship between growth and either SLA or seed mass in seedlings differs if absolute growth rate in mass is used instead of $RGR_{mass}$ (i.e.
-becomes negative for SLA, positive for SM).
+According to the growth model, the predicted relationship between growth and either SLA or seed mass in seedlings revert if absolute $Abs_{mass}$ is used instead of $RGR_{mass}$ (see Appendix 1\ref{sec:growth}).
+For SLA, the correlation with $RGR_{mass}$ is positive but becomes negative with $AbsGR_{mass}$.
+For SM the correlation with $RGR_{mass}$ is negative but becomes positive with $AbsGR_{mass}$.
+For the others traits (WD, Hmax and Aarea), the predicted relationships are not affected by the growth measurement used.
 
@@
 We aimed to identify studies that measured the correlation between five prominent functional trait (SLA, WD, Aarea, Hmax and Seed mass) and a growth measurement across species.
-A snapshot of the literature on Web of Science database (Thomson Reuters) showed that 82\% of the literature for these 5 traits is captured by searching only on SLA and WD.
+According to a snapshot of the literature on Web of Science database (Thomson Reuters), 82\% of the literature for these 5 traits is captured by searching only on SLA and WD.
 This snapshot was performed between March and June 2014 using a range of Boolean search terms in English.
@@
 Ultimately data was included from 112 different articles (starred references in bibliography).
-Where available we also recorded the geographic coordinates, number of sites, experiment type (greenhouse, field experiment, forest, shade-house etc.), growth measure (relative or absolute growth rate measured using plant diameter, height or mass), vegetation type, life form (tree, woody or mixed with herbaceous species etc.), biological scale (interspecific, intraspecific or intragenus), experimental treatments (e.g.~fertilization, shade, salt stress), and data for additional traits.
+
+Where available we also recorded the geographic coordinates, number of sites, experiment type (greenhouse, field experiment, forest, shade-house etc.), growth measure (relative or absolute growth rate measured using plant diameter, height or mass), vegetation type, life form (tree, woody or mixed with herbaceous species etc.), biological scale (interspecific, intraspecific or intragenus), and experimental treatments (e.g.
+fertilization, shade, salt stress).
 We reported coefficient correlations for a list of 20 traits (Fig.
-\ref{Fig1}): the five for which we had prior expectations, plus 15 others which capture different aspects of plant species strategies.
+\ref{Fig1}): the five for which we had prior expectations, plus 15 others which capture different aspects of plant species strategies and are commonly addressed in the trait literature.
 Specific leaf area (SLA), leaf area, leaf nitrogen and phosphorus concentration, net (mass) assimilation rates (NAR), and assimilation rate of CO2 (Aarea) are traits involved in species leaf economic strategy \citep{Wright:2004jb,Wright:2010tp}.
@@
 Fig.
-\ref{Fig2} showed that the threshold in size/age used by the authors to defined a plant stage are quite steady.
+\ref{Fig2} showed that the thresholds in size/age used by the authors to defined a plant stage are quite steady.
 In particular, there was a clear break between seedlings and saplings in both age (at 1 yr) and height (at 0.5 m); there was also a clear break between saplings and adults in diameter (at 10 cm).
@@
 This redundancy encourages us to focus on a three stage classification (i.e.
-juvenile, sapling, adult).
+juvenile, sapling, adult) instead of a four stage one (i.e.
+seedling, juvenile, sapling, adult).
 In the rest of the mansucript we preferred the term "juvenile" to "seedling", because for a portion of the scientific community "seedling" also refers to a particular experimental condition (a greenhouse experiment).
@@
 The others equivocal cases were caused by an ambiguity in the definition of "adult" used by the authors.
-Some plants with a large stature are not assessed as adult by the authors because they are still non reproductive.
+Some plants with a large stature are not assessed as adult by the authors because they are still non reproductive (see ID 52 and 50).
 Here, we attributed a study to the adult stage when the authors identified the plants as reproductive, and to sapling stage when they identified the plants as non-reproductive, regardless the plant size or age.
@@
 \subsection*{Statistical analyses}\label{statistical-analyses}
-The number of species used to perform the correlation, the experimental conditions, and the concordance between stage used to measure trait and growth are clear criteria for assessing the quality of the data for addressing our hypotheses.
-Therefore, we focused on correlation across species, and we stratified the data set into two subsets: one including exclusively studies under unstressed conditions ('ideal' dataset), and the other set including studies under all conditions ('complete' dataset).
-We excluded from the 'ideal' dataset studies where growth and traits were measured on plants from different stages, unless a particular stage is by definition required to measure a trait such as for seed mass (i.e.
-seed stage), or Hmax (i.e.
-adult stage).
 
+Effect size calculation:
 We used the cross-species Pearson product-moment correlation coefficient r between growth rate and species trait as our measure of effect size, weighted by the number of species contributing.
@@
 n being the number of species.
+We weighted effect size by the study precision using the number of species instead of the sample size because the question addressed in our study concerned the correlation between growth and traits across species and not within species.
 
+Stage effect:
 We tested stage effect on traits for which > 15 correlation coefficients across at least two stages were recorded.
@@
 Estimates of the effect size for each stage were considered significant if the 95\% confidence intervals did not overlap with zero.
+
+Sensitivity analysis:
+We tested how robust are our results to the decision made in the analysis.
+In particular we tested our prediction using two datatset with different inclusion criteria.
+The number of species used to perform the correlation, the experimental conditions, and the concordance between stage used to measure trait and growth are clear criteria for assessing the quality of the data for addressing our hypotheses.
+Therefore, we focused exclusively on correlation across species, and we stratified the data set into two subsets: one including only studies under unstressed conditions ('ideal' dataset), and the other set including studies under all conditions ('complete' dataset).
+We excluded from the 'ideal' dataset studies where growth and traits were measured on plants from different stages, unless a particular stage is by definition required to measure a trait such as for seed mass (i.e.
+seed stage), or Hmax (i.e.
+adult stage).
+We also tested the sentivity of our results to the dominance of one or a few studies that measured a large number of response for the same trait.
 In the case of multiple comparisons within a study, we used the method proposed by \citet{Borenstein:2009um}: we calculated the mean correlation coefficient by trait and by study, and re-calculated the effect size.
-Following recent recommendations for the adoption of a checklist of quality criteria for meta-analysis in ecology (\citealt{Koricheva:2014ku}), we conducted several analyses to assess the reliability of our meta-analysis.
-Table 2 detailed how and where (i.e in the text, appendix and/or figures) we addressed the 14 methodological quality criteria listed by \citet{Koricheva:2014ku}.
+This corresponds to the ”reduced dataset” where multiple responses were condensed into a single average within a trait and within a study.
+
+Quality criteria for meta-analysis:
+We conducted several analyses to assess the reliability of our meta-analysis.
+In particular, we quantified heterogeneity in effects size, we tested for publication bias and we explored temporal change in effect size (see Appendix \ref{app:supp_info_files}).
+We addressed the 14 methodological quality criteria listed by \citet{Koricheva:2014ku} as required to assess the relaibility of a meta-analyses (Table A2 detailed how and where in this article each citeria is addressed).
 
@@
 However, at the same time confidence intervals of r often spanned zero especially where there were small numbers of studies for particular growth stages.
+
+RGR in mass and height are commonly used to measure growth in small size tree, whereas AbsGR in diameter or height are more often used for larger stature tree. A ECRIRE
 

### 2015-09-02 MS.tex
Change in text
clean brackets

@@
 
-\title{Plant species traits and growth rates: meta-analysis shows correlations change with plant size as predicted}
+\title{On the link between functional traits and growth rate: meta-analysis shows effects change with plant size, as predicted}
 
@@
 \author[1]{Daniel S. Falster}
-\affil[1]{Dept of Biological Sciences, Macquarie University, Sydney, NSW 2109, Australia}
+\affil[1]{Biological Sciences, Macquarie University NSW 2109, Australia}
 
@@
 
-\textit{Running title (36/45 characters)} Trait influence on growth along plant size
+\textit{Running title (36/45 characters)}Influence of traits on growth changes with size
 
-\textit{Corresponding author} Anais Gibert, anais.gibert@gmail.com, Dept of Biological Sciences, Macquarie University, Sydney, NSW 2109, Australia, tel: +61 2 9850 8194
+\textit{Corresponding author} Anais Gibert, anais.gibert@gmail.com, Biological Sciences, Macquarie University NSW 2109, Australia, tel: +61 2 9850 8194
 
@@
 \section*{Introduction}\label{introduction}
-Plant "ecological strategy" refers to how species face the challenge they all share: to acquire sufficient water, nutrients and light to live long enough to replace themselves with offspring.
-Growth rates have often been seen as central elements of plant ecological strategies.
-An idea that species strategy differences might involve fast vs slow growth goes back at least to Grime and Hunt \citeyearpar{Grime:1975gr}, who measured a wide spread of relative growth rates for seedlings during early exponential growth under favourable conditions.
+
+The phrase ``plant ecological strategy'' refers to how species face common challenges of acquiring sufficient water, nutrients and light for growth, and then ultimately to replace themselves with offspring.
+An idea that species strategy differences might involve fast versus slow growth goes back at least to \citet{Grime:1975gr}, who measured a wide spread of relative growth rates for seedlings during early exponential growth under favourable conditions.
 Seedling potential relative growth rate (RGR) has continued to be used as a major strategy indicator within the CSR (Competitor - Stress tolerator - Ruderal) classification (e.g.
@@
 Meanwhile partitioning of seedling RGR into different components showed that specific leaf area (SLA = 1/leaf mass per area LMA) was typically the strongest source of variation between species \citep{Poorter:1989tx}.
-From the 1990s a new style of "trait ecology" arose whereby measurable traits including SLA were used directly as strategy axes \citep{Westoby:2002ft}.
+From the 1990s a new style of ``trait ecology'' arose whereby measurable traits including SLA were used directly as strategy axes \citep{Westoby:2002ft}.
 An approach via measurable traits made broad comparisons possible across continents and latitudes and thousands of species.
@@
 Currently, two main spectra of variation are widely cited as underpinning differences between species in vegetative growth rates.
-The 'leaf economic spectrum' \citep{Wright:2004jb} and the 'wood economic spectrum' \citep{Chave:2009iy} reflect tissue construction costs (for specific leaf area and for wood volume respectively) trading off with tissue turnover rates or mortality risks.
-It has been widely expected that species with low tissue construction cost will typically have fast growth rates at least in favourable physical environments (e.g.
-\citealt{MullerLandau:2004dc,Wright:2004jb,Poorter:2008iu,Chave:2009iy,Larjavaara:2010bn,Iida:2012jb,Paine:2015df}).
+The ``leaf economic spectrum'' \citep{Wright:2004jb} and the ``wood economic spectrum'' \citep{Chave:2009iy} reflect tissue construction costs (for leaf area and for wood volume respectively), trading off with rates of tissue turnover or mortality.
+It has been widely expected that species with low tissue construction cost will typically have fast growth rates, at least in favourable physical environments \citep[e.g.][]{MullerLandau:2004dc,Wright:2004jb,Poorter:2008iu,Chave:2009iy,Larjavaara:2010bn,Iida:2012jb,Paine:2015df}.
 Yet, a growing number of empirical studies indicate the correlation between traits and growth is not as consistent as that.
@@
 Recent theory suggests that the absence of a correlation between SLA and growth at larger sizes may be expected, when potential influences of traits on plant function are considered \citep{Falster:2011ii, falster:2013}.
-At larger sizes the low-cost deployment benefits of high SLA may be offset or even outweighted by the high costs of rapid leaf turnover (see section "Theoretical expectations").
+At larger sizes the low-cost deployment benefits of high SLA may be offset or even outweighted by the high costs of rapid leaf turnover (see section ``Theoretical expectations'').
 While recent empirical studies supported the idea of a variation in the relationships between traits and growth rates across plant sizes (\citealt{Iida:2014ep, Iida:2014hq}), the trend and mechanisms behind this variation remain unclear.
@@
   \item How general is the tendency for correlations between traits and growth rate to vary with plant size?
-  \item  Do the observed relationships conform to predictions (outlined in section "Theoretical expectations") from a recently developed mechanistic model (Falster et al., 2011; Falster, 2013)?
+  \item  Do the observed relationships conform to predictions (outlined in section ``Theoretical expectations'') from a recently developed mechanistic model (Falster et al., 2011; Falster, 2013)?
 \end{enumerate}
@@
 This snapshot was performed between March and June 2014 using a range of Boolean search terms in English.
-Search terms were as follows: (''TRAIT'' AND (''growth rate'' OR ''relative growth rate'')) AND (''tree*'' OR ''woody*''), ''TRAIT'' was all trait names listed in Table A1.
+Search terms were as follows: (``TRAIT'' AND (``growth rate'' OR ``relative growth rate'')) AND (``tree*'' OR ``woody*''), ``TRAIT'' was all trait names listed in Table A1.
 While Web of Science guarantees a relatively stable and reproducible search environment, with clearly defined lists of indexed journals, its searches are restricted to metadata, such as title, keywords and abstracts \citep{Beckmann:2012hn}.
@@
 Google Scholar database was searched using the range of Boolean search terms for SLA and WD.
-Search terms were as follows: ((''SLA'' OR ''LMA'' OR ''specific leaf area'' OR ''leaf mass area'' OR ''wood density'' OR ''WD'' OR ''wood specific gravity'' OR ''stem density'' OR ''stem specific density'') AND (''growth rate'' OR ''relative growth rate'')) AND (tree* OR woody*).
+Search terms were as follows: ((``SLA'' OR ``LMA'' OR ``specific leaf area'' OR ``leaf mass area'' OR ``wood density'' OR ``WD'' OR ``wood specific gravity'' OR ``stem density'' OR ``stem specific density'') AND (``growth rate'' OR ``relative growth rate'')) AND (tree* OR woody*).
 The keyword search in Google Scholar returns approx.
@@
 We also identified and recorded other possible data sources using our own knowledge as researchers in the field (this included adding data from an as-yet unpublished study by Gleason et al).
-To avoid publication bias due to selective reporting of significant results within published articles (e.g.~particular case of a 'failure to publish bias' see \citealt{Jennions:2013ta}), we asked the authors for additional information when they reported a non-significant correlation between growth and trait without reporting a correlation coefficient value.
+To avoid publication bias due to selective reporting of significant results within published articles (e.g.~particular case of a ``failure to publish bias'' see \citealt{Jennions:2013ta}), we asked the authors for additional information when they reported a non-significant correlation between growth and trait without reporting a correlation coefficient value.
 The complete list of studies where we inspected the full text is given in Appendix \ref{app:supp_info_files} in Supplementary material.
@@
 \ref{FigA1}).
-The size/stage threshold defined across the 112 articles, allowed us to attribute straightforwardly a stage category to studies for which no stage have been distinctly mentionned by the authors (5\% of the data, noted as 'mix' in Fig.
+The size/stage threshold defined across the 112 articles, allowed us to attribute straightforwardly a stage category to studies for which no stage have been distinctly mentionned by the authors (5\% of the data, noted as ``mix'' in Fig.
 \ref{Fig2}).
@@
 Half of these equivocal cases involved the juvenile category.
-The term "juvenile" is vague enough to cover size range from either seedling or sapling stages.
+The term ``juvenile'' is vague enough to cover size range from either seedling or sapling stages.
 according to the authors.
@@
 seedling, juvenile, sapling, adult).
-In the rest of the mansucript we preferred the term "juvenile" to "seedling", because for a portion of the scientific community "seedling" also refers to a particular experimental condition (a greenhouse experiment).
+In the rest of the mansucript we preferred the term ``juvenile'' to ``seedling'', because for a portion of the scientific community ``seedling'' also refers to a particular experimental condition (a greenhouse experiment).
 We attributed a study to a new stage category only when 95\% of the recorded range of sizes for that study lay within a new stage category.
-The others equivocal cases were caused by an ambiguity in the definition of "adult" used by the authors.
+The others equivocal cases were caused by an ambiguity in the definition of ``adult'' used by the authors.
 Some plants with a large stature are not assessed as adult by the authors because they are still non reproductive (see ID 52 and 50).
@@
 Therefore, we focused exclusively on correlation across species, and we stratified the data set into two subsets: one including only studies under unstressed conditions ('ideal' dataset), and the other set including studies under all conditions ('complete' dataset).
-We excluded from the 'ideal' dataset studies where growth and traits were measured on plants from different stages, unless a particular stage is by definition required to measure a trait such as for seed mass (i.e.
+We excluded from the ``ideal'' dataset studies where growth and traits were measured on plants from different stages, unless a particular stage is by definition required to measure a trait such as for seed mass (i.e.
 seed stage), or Hmax (i.e.
@@
 
-\subsection*{Availability of code and data}\label{code}
-
+Availability of code and data:
 All analyses were conducted with R software \citep{Ralanguageanden:2014wf}.
@@
 The results reported were confined to correlations across species, and under non-stressed conditions (n=176).
-A "complete" dataset (n=216) also included correlations measured under stressed conditions, and spanning different plant stages between the growth and trait measurements.
-This "complete" dataset generated similar effect sizes to those reported above from the "ideal" dataset, and led to similar conclusions (Fig.
+A ``complete'' dataset (n=216) also included correlations measured under stressed conditions, and spanning different plant stages between the growth and trait measurements.
+This ``complete'' dataset generated similar effect sizes to those reported above from the ``ideal'' dataset, and led to similar conclusions (Fig.
 \ref{Fig3} grey points).
@@
 Note that in \citet{Iida:2014hq}, the shift in the correlation between growth and WD occurred for trees larger than 22-26 cm dbh.
-This points to one of the possible limitations in our meta-analysis, where trees with height above 5 m were pooled as "adult".
+This points to one of the possible limitations in our meta-analysis, where trees with height above 5 m were pooled as ``adult''.
 
@@
 \caption{Number of correlations between trait and growth for each plant stage recorded in our dataset.
-Shown here are 'raw dataset' (recorded both across and within species, under unstressed and stressed conditions).
+Shown here are ``raw dataset'' (recorded both across and within species, under unstressed and stressed conditions).
 Bar colors: red for adult, orange for sapling, grey for juvenile.
@@
 The colors represents the stage information given by the authors (green: seedling, blue: juvenile, orange: sapling, red: adult, grey: unspecified by the authors), the vertical line represents the most likely limits between stage categories, the horizontal line styles corresponds to the species growth form used in each study (solid line: exclusively tree, dashed line: woody species , dotted line: tree mixed with another growth form).
-Shown here are the "raw dataset" (recorded both across and within species, and under unstressed and stressed conditions).}
+Shown here are the ``raw dataset'' (recorded both across and within species, and under unstressed and stressed conditions).}
 \label{Fig2}
@@
 Effects are significant if confidence intervals (95\%CI) for a given stage do not overlap with zero.
-Shown here are 'across species dataset' (recorded only across species, and under both unstressed and stressed conditions).
+Shown here are ``across species dataset'' (recorded only across species, and under both unstressed and stressed conditions).
 Black point: unstressed conditions, grey points: all the data.
-'n' indicates number of correlations contributing to each effect.
+``n'' indicates number of correlations contributing to each effect.
 Likelihood Ratio Tests (LRT, for unstressed conditions only) compared maximum-likelihood fits between a pooled model and one separated by stage.
@@
   1.
-Reporting full details of bibliographic searches & yes	& Google Scholar database was searched using the range of Boolean search terms ((''SLA'' OR ''LMA'' OR ''specific leaf area'' OR ''leaf    mass area'' OR ''wood density'' OR ''WD'' OR ''wood specific gravity'' OR ''stem density'' OR ''stem specific density'') AND (''growth rate'' OR ''relative growth rate'')) AND (tree* OR woody*), in english.
-& "Systematic search", Table A1 \\
+Reporting full details of bibliographic searches & yes	& Google Scholar database was searched using the range of Boolean search terms ((``SLA'' OR ``LMA'' OR ``specific leaf area'' OR ``leaf    mass area'' OR ``wood density'' OR ``WD'' OR ``wood specific gravity'' OR ``stem density'' OR ``stem specific density'') AND (``growth rate'' OR ``relative growth rate'')) AND (``tree*'' OR ``woody*''), in english.
+& ``Systematic search'', Table A1 \\
   2.
 Reporting inclusion/exclusion criteria & yes & Studies included report i) correlation coefficient between growth and trait, ii) the sample size/ number of species, and iii) the size/stage of plants.
-Studies excluded report correlation within species	& "Systematic search" \\
+Studies excluded report correlation within species	& ``Systematic search'' \\
   3.
@@
 The question addressed in our study concerns the correlation between growth and trait across species, thus the number of species is a better proxy of a study quality than sample size.
-&	 "Systematic search" and  "Effect size calculation" \\
- 4. Specifying meta-analytical model &	yes	& Mixed-effect model with a study ID as a random variation, and stage as a fixed effect, m1 ~lmer (stage + (1|ID)) &	"Statistical analyses", Fig3 \\
+&	 ``Systematic search'' and  ``Effect size calculation'' \\
+ 4. Specifying meta-analytical model &	yes	& Mixed-effect model with a study ID as a random variation, and stage as a fixed effect, m1 ~lmer (stage + (1|ID)) &	``Statistical analyses'', Fig3 \\
  5. Quantifying heterogeneity in effect sizes &	yes &	We estimated the extend of the heterogeneity using the statistics $I^{2}$ (Santos and Nakagawa, 2012) for each trait. &	Appendix D \\
@@
  7.
-Multifactorial analysis of explanatory variable	& yes & We focused on the "plant stage" as the main exploratory variable.
-Yet, the stage variable may be confunded with other explanatory moderators (i.e.
+Multifactorial analysis of explanatory variable	& yes & We focused on the ``plant stage'' as the main exploratory variable.
+Yet, the stage variable may be confounded with other explanatory moderators (i.e.
 growth measurement, experiment type or growth form).
@@
   8.
-Testing for publication bias &	yes	& We used funnel plots for a visual assessement.
-We used the "trim and fill" method to estimate the number of studies missing (Duval and Tweedie 2000).
+Testing for publication bias &	yes	& We used funnel plots for a visual assessment.
+We used the ``trim and fill'' method to estimate the number of studies missing (Duval and Tweedie 2000).
 We also estimated the Rosenberg’s fail-safe number (Rosenberg 2005).
@@
 Sensitivity analysis &	yes &	We tested how robust are our results to the decision made in the analysis.
-We calculated effect size using 3 differents dataset: i) an  "ideal" dataset, focusing on unstressed conditions exclusively, ii) a "complete dataset" reporting all conditions, and iii) a "reduced dataset" where multiple responses were condensed into a single average within a trait and within a study.
+We calculated effect size using 3 differents dataset: i) an  ``ideal'' dataset, focusing on unstressed conditions exclusively, ii) a ``complete dataset'' reporting all conditions, and iii) a ``reduced dataset'' where multiple responses were condensed into a single average within a trait and within a study.
 &	Fig3, FigA5 \\
@@
   11. Controlling for phylogeny &	no &	It was not possible to control by the phylogeny since the number of species used to measured each coeffcient of correlation ranged from 2 to 300 species. &	\\
-  12. Specifying the software used &	yes	& R softward, code available on Github. & "Availability of code and data" \\
+  12. Specifying the software used &	yes	& R softward, code available on Github. & ``Availability of code and data'' \\
  13.
 Providing reference list of primary studies included in the analysis &	yes &	Available on Github.
-The Bibtex file "meta-analyses.bib" corresponds to all the articles included in the meta-analyses, "read.bib" corresponds to all the articles (included and excluded) inspected for the meta-analyses.	& "Availability of code and data" \\
-  14. Providing the data set used for meta-analysis  &	yes &	A copy of the complete data set is available on Github.	& "Availability of code and data" \\
+The Bibtex file `meta-analyses.bib` corresponds to all the articles included in the meta-analyses, `read.bib` corresponds to all the articles (included and excluded) inspected for the meta-analyses.	& ``Availability of code and data'' \\
+  14. Providing the data set used for meta-analysis  &	yes &	A copy of the complete data set is available on Github.	& ``Availability of code and data'' \\
    \hline
@@
 
-"code.zip": the data and analysis code used to generate the results in this paper. A copy of the complete data set is also available from the Dryad Digital Repository.
+code.zip: the data and analysis code used to generate the results in this paper. A copy of the complete data set is also available from the Dryad Digital Repository.
 
@@
   \hline
-Aarea & Photosynthetic rate per area & "photosynthetic rate per area" OR "rate of CO2 assimilation per area" OR "Aarea" OR "Amax" OR "photosynthetic capacity per area" \\
-  Amass & Photosynthetic rate per mass & "photosynthetic rate per mass" OR "rate of CO2 assimilation per mass" OR "Amass" OR "Amax" \\
-  Hmax & Maximum height & "potential height" OR "maximum height" OR "Hmax" \\
-  Ks & Stem specific conductance & "Ks" OR "stem specific conductance" OR "stem hydraulic conductance" OR "sapwood conductance" \\
-  LA & Leaf lamina area & "leaf length" OR "leaf lamina area" OR "leaf width" OR "leaf size" \\
-  LAR & Leaf area ratio & "leaf area ratio" \\
-  LMR & Leaf mass ratio & "leaf mass ratio" OR "leaf mass fraction" \\
-  NARarea & Net assimilation rate per area &  "net assimilation rate per area" OR "rate of dry mass increament per area" OR "NARarea" OR "NAR" \\
-  Narea & Leaf nitrogen content per area & "Narea" OR "nitrogen per area" OR "N/area" OR "leaf nitrogen content per area" OR "LNCarea" OR "leaf nitrogen content" \\
-  NARmass & Net assimilation rate per mass &  "net assimilation rate per mass" OR "rate of dry mass increament per mass" OR "NARmass" OR "NAR" \\
-  Nmass & Leaf nitrogen content per mass & "Nmass" OR "nitrogen per mass" OR "N/mass" OR "leaf nitrogen content per mass" OR "LNCmass" OR "leaf nitrogen content" \\
-  Parea & Leaf phosphorus content per area & "Parea" OR "leaf P" OR  "leaf phosphorus content per area"  OR "leaf phosphorus content" \\
-  Pmass & Leaf phosphorus content per mass & "Pmass" OR "leaf P" OR  "leaf phosphorus content per mass" OR "leaf phosphorus content" \\
-  SA/LA & Sapwood area per leaf area & "sapwood area per leaf area" OR "huber value" OR "leaf area per sapwood area" \\
-  Seed mass & Seed mass & "seed mass" OR "seed size" OR "seed volume" \\
-  SLA & Specific Leaf Area & "leaf mass per area" OR "specific leaf area" OR "leaf construction cost" \\
-  Thickness & Leaf thickness & "leaf thickness"  OR "leaf tissue density" \\
-  Vessel density & Vessel density & "vessel density" OR "stem conduit density" \\
-  Vessel size & Vessel area or diameter & "conduit area" OR "stem conduit area" OR "vessel diameter" OR "vessel size" OR "conduit size"   \\
-  WD & Wood density & "wood density" OR"WD" OR "wood specific gravity" OR "stem density" OR "stem specific density" OR "SSD" \\
+Aarea & Photosynthetic rate per area & ``photosynthetic rate per area'' OR ``rate of CO2 assimilation per area'' OR ``Aarea'' OR ``Amax'' OR ``photosynthetic capacity per area'' \\
+  Amass & Photosynthetic rate per mass & ``photosynthetic rate per mass'' OR ``rate of CO2 assimilation per mass'' OR ``Amass'' OR ``Amax'' \\
+  Hmax & Maximum height & ``potential height'' OR ``maximum height'' OR ``Hmax'' \\
+  Ks & Stem specific conductance & ``Ks'' OR ``stem specific conductance'' OR ``stem hydraulic conductance'' OR ``sapwood conductance'' \\
+  LA & Leaf lamina area & ``leaf length'' OR ``leaf lamina area'' OR ``leaf width'' OR ``leaf size'' \\
+  LAR & Leaf area ratio & ``leaf area ratio'' \\
+  LMR & Leaf mass ratio & ``leaf mass ratio'' OR ``leaf mass fraction'' \\
+  NARarea & Net assimilation rate per area &  ``net assimilation rate per area'' OR ``rate of dry mass increament per area'' OR ``NARarea'' OR ``NAR'' \\
+  Narea & Leaf nitrogen content per area & ``Narea'' OR ``nitrogen per area'' OR ``N/area'' OR ``leaf nitrogen content per area'' OR ``LNCarea'' OR ``leaf nitrogen content" \\
+  NARmass & Net assimilation rate per mass &  ``net assimilation rate per mass'' OR ``rate of dry mass increament per mass'' OR ``NARmass'' OR ``NAR'' \\
+  Nmass & Leaf nitrogen content per mass & ``Nmass'' OR ``nitrogen per mass'' OR ``N/mass'' OR ``leaf nitrogen content per mass'' OR ``LNCmass'' OR ``leaf nitrogen content" \\
+  Parea & Leaf phosphorus content per area & ``Parea'' OR ``leaf P'' OR  ``leaf phosphorus content per area''  OR ``leaf phosphorus content'' \\
+  Pmass & Leaf phosphorus content per mass & ``Pmass'' OR ``leaf P'' OR  ``leaf phosphorus content per mass'' OR ``leaf phosphorus content'' \\
+  SA/LA & Sapwood area per leaf area & ``sapwood area per leaf area'' OR ``huber value'' OR ``leaf area per sapwood area'' \\
+  Seed mass & Seed mass & ``seed mass'' OR ``seed size'' OR ``seed volume'' \\
+  SLA & Specific Leaf Area & ``leaf mass per area'' OR ``specific leaf area'' OR ``leaf construction cost'' \\
+  Thickness & Leaf thickness & ``leaf thickness''  OR ``leaf tissue density'' \\
+  Vessel density & Vessel density & ``vessel density'' OR ``stem conduit density'' \\
+  Vessel size & Vessel area or diameter & ``conduit area'' OR ``stem conduit area'' OR ``vessel diameter'' OR ``vessel size'' OR ``conduit size''   \\
+  WD & Wood density & ``wood density'' OR``WD'' OR ``wood specific gravity'' OR ``stem density'' OR ``stem specific density'' OR ``SSD'' \\
    \hline
@@
 \caption{Geographical distribution of site locations from studies performed in the field used in the meta-analysis.
-Shown here are the "raw dataset" (recorded both across and within species, and under unstressed and stressed conditions).}
+Shown here are the ``raw dataset'' (recorded both across and within species, and under unstressed and stressed conditions).}
 \label{FigA2}
@@
 articles. The x abcissa represents the articles ID sorted by the average coefficient value r reported.
-Shown here are the "raw dataset" (recorded both across and within species
+Shown here are the ``raw dataset'' (recorded both across and within species
 and under unstressed and stressed conditions). Each bubble represents a r value, the diameter of the bubble
@@
 Each panel corresponds to a functional trait: \textbf{a)} Specific leaf area (SLA), \textbf{b)} Wood density (WD), \textbf{c)} Net assimilation rate (NARarea), \textbf{d)} Seed mass, \textbf{e)} Asymptotic height (Hmax) and \textbf{f)} Assimilation rate of CO2 (Aarea).
-Shown here are the "unstressed dataset" (recorded across species and under unstressed conditions).}
+Shown here are the ``unstressed dataset'' (recorded across species and under unstressed conditions).}
 \label{FigA4}
@@
 Black point: ideal data (under unstressed conditions), grey points: all the data.
-'n' indicate the number of independent comparisons for each effect.}
+``n'' indicate the number of independent comparisons for each effect.}
 \label{FigA5}
@@
 Smallest is the AIC better is the model.
-Shown here are "ideal dataset" (recorded at interspecific and under unstressed condition) and "raw dataset" (recorded at both interspecific and intraspecific level and under unstressed and stressed conditions).}
+Shown here are ``ideal dataset'' (recorded at interspecific and under unstressed condition) and ``raw dataset'' (recorded at both interspecific and intraspecific level and under unstressed and stressed conditions).}
 \label{FigA6}
@@
 \citealt{Higgins:2003hz} suggested some benchmarks for $I^{2}$ based on the survey of meta-analyses of clinical trials.
-They suggested that values on the order of 25\%, 50\% and 75\% might be considered as "low", "moderate" and "high", respectively.
+They suggested that values on the order of 25\%, 50\% and 75\% might be considered as ``low'', ``moderate'' and ``high'', respectively.
 These suggestions are tentative; the interpretation of heterogeneity in a systematic review will depend critically on the size and direction of treatment effects, as well as on considerations of methodological diversity in the studies (see \citealt{Borenstein:2009um}).

### 2015-09-02 MS.tex
Substantial edits throughout

@@
 Traits should influence growth in a way that depend on individual plants size.
-We outline mechanisms and hypotheses based on new theory, and test these predictions in tree species for five traits using a meta-analysis of 112 studies (> 500 correlations).
+We outline mechanisms and hypotheses based on new theory, and test these predictions in tree species for five traits using a meta-analysis of 112 studies ($>$ 500 correlations).
 As a first approximation of plants size, we analysed the shift in the correlations between growth and traits across three plant stages (i.e.
@@
 For seedling relative growth rates under favourable conditions, high SLA has repeatedly been found to be a strong predictor regardless of vegetation type or growth form \citep{Lambers:1992bj,Reich:1992wm,Grime:1997wm,Poorter:1999wd,Wright:1999ds}.
-Yet for adult plants, this correlation appears weaker or absent \citep{coomes_comparison_1998,Poorter:2008iu,Aiba:2009ft,Easdale:2009gv,Wright:2010tp}.
+Yet for adult plants, the correlation is mostly much weaker or absent \citep{coomes_comparison_1998,Poorter:2008iu,Aiba:2009ft,Easdale:2009gv,Wright:2010tp}.
 The growing discrepancy between theoretical expectation and empirical results has led some to question whether traits are even useful for understanding growth \citep{Wright:2010tp, Paine:2015df}.
 
-Meanwhile the possibility has been raised that trait-growth correlations may change systematically with size \citep{Enquist:2007ek,Falster:2011ii, Ruger:2012jv, Iida:2014ep, Iida:2014hq}.
-Recent theory suggests that the absence of a correlation between SLA and growth at larger sizes may be expected, when potential influences of traits on plant function are considered \citep{Falster:2011ii, falster:2013}.
-At larger sizes the low-cost deployment benefits of high SLA may be offset or even outweighted by the high costs of rapid leaf turnover (see section ``Theoretical expectations'').
+Meanwhile the possibility has been raised that trait-growth correlations may change systematically with size \citep{Falster:2011ii, Ruger:2012jv, Iida:2014ep, Iida:2014hq}.
+Recent theory suggests that the absence of a correlation between SLA and growth at larger sizes may be expected, when potential influences of traits on plant function are considered \citep{Falster:2011ii}.
+At larger sizes the low-cost deployment benefits of high SLA may be offset or even outweighed by the high costs of rapid leaf turnover (see section ``Theoretical expectations'').
 While recent empirical studies supported the idea of a variation in the relationships between traits and growth rates across plant sizes (\citealt{Iida:2014ep, Iida:2014hq}), the trend and mechanisms behind this variation remain unclear.
-It is still an opening question whether the influence of traits on growth change with plant size in a predictable and consistent way.
+Moreover, the question whether the influence of traits on growth changes with plant size in a predictable and consistent way is very much open.
 
-In this paper, we used a meta-analytic approach on five prominent traits (specific leaf area = SLA, wood or stem tissue density = WD, maximum leaf photosynthetic capacity per unit area = Aarea, maximum height= Hmax, and seed mass= SM) to investigate:
+In this paper, we used a meta-analytic approach on five prominent traits (specific leaf area = SLA, wood or stem tissue density = WD, maximum leaf photosynthetic capacity per unit area = Aarea, asymptotic or maximum height = Hmax, and seed mass = SM) to investigate:
 \begin{enumerate}
   \item How general is the tendency for correlations between traits and growth rate to vary with plant size?
-  \item  Do the observed relationships conform to predictions (outlined in section ``Theoretical expectations'') from a recently developed mechanistic model (Falster et al., 2011; Falster, 2013)?
+  \item  Do the observed relationships conform to predictions (outlined in section ``Theoretical expectations'') derived from a recently developed mechanistic model \citep{Falster:2011ii}?
 \end{enumerate}
@@
 juvenile, sapling and adult) as a first approximation of plant size.
-We focused mainly on tree and woody species since the mechanistic model used to assess our predictions is most applicable to tree.
+We focused on tree and woody species since the mechanistic model used to assess our predictions is most applicable to these growth forms.
 
@@
 Recent theoretical work \citep{Falster:2011ii} allows us to formulate hypotheses about relationships between traits and growth, based on a mathematical decomposition of plant growth rate.
-Specific predictions arise from considering the influence of traits on elements of these equations and how these effects may vary with size (see Appendix\ref{sec:growth} for mathematical explanations).
+Specific predictions arise from considering the influence of traits on elements of these equations and how these effects may vary with size (see Appendix \ref{sec:growth} for mathematical explanations).
+This model extends earlier efforts to model growth as a function of traits \citep{Lambers:1992bj,cornelissen_seedling_1996,Wright:2000kw,Enquist:2007ek}.
+However, whereas earlier models focused solely on mass-based relative growth rate and did not predict a change in effect of traits with size, the revised equations do allow for these effects, while also making predictions for both absolute and relative growth rates in any of height, diameter or mass.
 
-\textbf{H1: The relationship between specific leaf area (SLA) and growth rate is expected to shift from positive in seedlings to non-significant or negative in adult plants}
+\textbf{H1: The relationship between SLA and growth rate is expected to shift from positive in seedlings to non-significant or negative in adult plants}
 
@@
 However, high-SLA species also have shorter leaf lifespan and faster leaf turnover rate \citep{Wright:2004jb}.
-Whether plant growth increases with SLA depends on the relative magnitude of the leaf construction and leaf turnover effects of SLA (Table 1).
-During early life, while leaf comprises a large part of the plant, decreasing leaf construction cost has a positive effect on growth rate.
+Whether plant growth increases with SLA depends on the relative magnitude of the leaf construction and leaf turnover effects of SLA (Table \ref{tab:trade-offs}).
+During early life, when leaf comprises a large part of the plant, decreasing leaf construction cost has a positive effect on growth rate.
 As plants increase in size and leaf mass fraction decreases, the benefit of cheaper leaf construction diminishes; thus the cost of replacing leaf turnover becomes more important.
 
-\textbf{H2: The relationship between wood or stem density (WD) and growth rate is expected to be negative across all plant size}
+\textbf{H2: The relationship between WD and growth rate is expected to be negative across all plant size}
 
-Low WD decreases the cost of building stem tissue and thus the cost of deploying additional leaf area (Table 1), which should result in faster growth.
+Low WD decreases the cost of building stem tissue and thus the cost of deploying additional leaf area (Table \ref{tab:trade-offs}), which should result in faster growth.
 Although cheaper wood carries a risk of increased mortality, this cost is not reflected in growth outcomes.
@@
 
-\textbf{H3: The relationship between asymptotic maximum height (Hmax) and growth rate is expected to be absent in seedlings but to strengthen with increasing plant size.}
+\textbf{H3: The relationship between Hmax and growth rate is expected to be absent in seedlings but to strengthen with increasing plant size.}
 
-As plants approach maximum height they increasingly divert energy away from growth and into reproduction (see \citealt{Thomas:1996do, Falster:2011ii, Wenk:2014jz}).
+As plants approach maximum height they increasingly divert energy away from growth and into reproduction (see \citealt{Thomas:1996do,Thomas-2011, Wenk:2014jz}).
 For seedlings, where all individuals are investing solely in growth, we expect no influence of Hmax on growth.
-As plants become larger, species with smaller Hmax are expected to be allocating more to reproduction and less to growth, because at any given size they are closer to their Hmax (Table 1).
+As plants become larger, species with smaller Hmax are expected to be allocating more to reproduction and less to growth, because at any given size they are closer to their Hmax (Table \ref{tab:trade-offs}).
 
-\textbf{H4: The relationship between seed mass (SM) and relative growth rate is negative in seedlings, but weakens with increasing size.}
+\textbf{H4: The relationship between SM and relative growth rate is negative in seedlings, but weakens with increasing size.}
 
 The main effect of increased seed size is to produce a larger overall seedling.
-Generally relative growth rate decreases with size, and as such larger seedlings are predicted to have a lower relative growth rate during the earliest phases of growth \citet{Turnbull:2012ew}.
+Generally relative growth rate decreases with size, and as such larger seedlings are predicted to have a lower relative growth rate during the earliest phases of growth \citep{Turnbull:2012ew}.
 However, among larger plants we expect the effect of this initial size to be minimal, and thus the correlation between seed size and growth rate should disappear.
 
-\textbf{H5: The relationship between maximum photosynthetic rate (Aarea) and growth rate is expected to be positive across all plant sizes, at least under high-light conditions}
+\textbf{H5: The relationship between Aarea and growth rate is expected to be positive across all plant sizes, at least under high-light conditions}
 
-We expect greater photosynthetic capacity to translate into faster growth rates by increasing the rate of biomass production (Table 1), at least at high light where Aarea is measured.
+We expect greater photosynthetic capacity to translate into faster growth rates by increasing the rate of biomass production (Table \ref{tab:trade-offs}), at least at high light where Aarea is measured.
 It is uncertain how much this might translate to faster growth in low light.
 
-\textbf{Effect on absolute (AbsGR) and relative growth rate (RGR)}
-Tree growth in diameter, height or mass can be expressed in either absolute (AbsGR) or relative terms (RGR).
-According to the growth model, the predicted relationship between growth and either SLA or seed mass in seedlings revert if absolute $Abs_{mass}$ is used instead of $RGR_{mass}$ (see Appendix 1\ref{sec:growth}).
-For SLA, the correlation with $RGR_{mass}$ is positive but becomes negative with $AbsGR_{mass}$.
-For SM the correlation with $RGR_{mass}$ is negative but becomes positive with $AbsGR_{mass}$.
+\textbf{Effect on absolute and relative growth rates}
+Tree growth in diameter, height or mass can be expressed in either absolute (AGR) or relative terms (RGR).
+According to the growth model, the predicted relationship between growth and either SLA or SM in seedlings revert if absolute AGR$_\textrm{mass}$ is used instead of RGR$_\textrm{mass}$ (see Appendix \ref{sec:growth}).
+For SLA, the correlation with RGR$_\textrm{mass}$ is positive but becomes negative with AGR$_\textrm{mass}$.
+For SM the correlation with RGR$_\textrm{mass}$ is negative but becomes positive with AGR$_\textrm{mass}$.
 For the others traits (WD, Hmax and Aarea), the predicted relationships are not affected by the growth measurement used.
@@
 
-\subsection*{Literature snapshot}\label{literature-snapshot}
-We aimed to identify studies that measured the correlation between five prominent functional trait (SLA, WD, Aarea, Hmax and Seed mass) and a growth measurement across species.
-According to a snapshot of the literature on Web of Science database (Thomson Reuters), 82\% of the literature for these 5 traits is captured by searching only on SLA and WD.
-This snapshot was performed between March and June 2014 using a range of Boolean search terms in English.
-Search terms were as follows: (``TRAIT'' AND (``growth rate'' OR ``relative growth rate'')) AND (``tree*'' OR ``woody*''), ``TRAIT'' was all trait names listed in Table A1.
-While Web of Science guarantees a relatively stable and reproducible search environment, with clearly defined lists of indexed journals, its searches are restricted to metadata, such as title, keywords and abstracts \citep{Beckmann:2012hn}.
+\subsection*{Dataset construction}
+
+We aimed to identify studies that measured the correlation between five prominent functional trait (SLA, WD, Aarea, Hmax and SM) and a growth measurement across species.
+Our literature search was conducted in two phases.
+
+\subsubsection*{Phase 1 - Literature snapshot}\label{literature-snapshot}
+
+We first developed a snapshot of the literature, to assess potential to recover useufl data from the wide corpus of literature available.
+This snapshot was obtained via Web of Science database (Thomson Reuters), between March and June 2014, using a range of Boolean search terms in English.
+Search terms were as follows: (``trait'' AND (``growth rate'' OR ``relative growth rate'')) AND (``tree*'' OR ``woody*''), where ``trait'' was allowed to be any of the trait names listed in Table \ref{tab:lit_search}.
+This snapshot indicated that 82\% of the reported correlations linking growth to any of our five core traits would be recovered by searching only on SLA and WD, allowing us to narrow our search considerably.
+
+\subsubsection*{Phase 2 - Systematic search}\label{systematic-search}
+
+While Web of Science guarantees a relatively stable and reproducible search environment, with clearly defined lists of indexed journals, its searches are restricted to meta-data, such as title, keywords and abstracts \citep{Beckmann:2012hn}.
 This limitation does not apply to Google Scholar, where, theoretically, all text that is electronically available on the Internet will be indexed.
@@
 
-\subsection*{Systematic search}\label{systematic-search}
-Google Scholar database was searched using the range of Boolean search terms for SLA and WD.
-Search terms were as follows: ((``SLA'' OR ``LMA'' OR ``specific leaf area'' OR ``leaf mass area'' OR ``wood density'' OR ``WD'' OR ``wood specific gravity'' OR ``stem density'' OR ``stem specific density'') AND (``growth rate'' OR ``relative growth rate'')) AND (tree* OR woody*).
-The keyword search in Google Scholar returns approx.
-18900 papers.
-For comparison, with the same keyword search Web of Science returns 541 papers.
-Thus, in Google Scholar we displayed papers by relevance and examined the first 750 items.
-We also identified and recorded other possible data sources using our own knowledge as researchers in the field (this included adding data from an as-yet unpublished study by Gleason et al).
-To avoid publication bias due to selective reporting of significant results within published articles (e.g.~particular case of a ``failure to publish bias'' see \citealt{Jennions:2013ta}), we asked the authors for additional information when they reported a non-significant correlation between growth and trait without reporting a correlation coefficient value.
+The Google Scholar database was searched using a range of Boolean search terms for SLA and WD: ((``SLA'' OR ``LMA'' OR ``specific leaf area'' OR ``leaf mass area'' OR ``wood density'' OR ``WD'' OR ``wood specific gravity'' OR ``stem density'' OR ``stem specific density'') AND (``growth rate'' OR ``relative growth rate'')) AND (``tree*'' OR ``woody*'').
+This keyword search in Google Scholar returned approx.
+18900 papers, from which we took the first 750 items when ranked by ``relevance''.
+These papers were examined in addition to those discovered in Phase 1.
+In addition, we gleaned data from other sources, using our own knowledge as researchers in the field (this included adding data from an as-yet unpublished study by Gleason et al).
 The complete list of studies where we inspected the full text is given in Appendix \ref{app:supp_info_files} in Supplementary material.
@@
 Ultimately data was included from 112 different articles (starred references in bibliography).
+Where available, we also recorded the geographic coordinates, number of sites, experiment type (greenhouse, field experiment, forest, shade-house etc.), growth measure (relative or absolute growth rate measured using plant diameter, height or mass), vegetation type, life form (tree, woody or mixed with herbaceous species etc.), biological scale (interspecific, intraspecific or intragenus), and experimental treatments (e.g.
+fertilization, shade, salt stress).
+To minimise publication bias via selective reporting of significant results within the published articles (e.g.
+a particular case of a ``failure to publish bias'' see \citealt{Jennions:2013ta}), we asked those authors reporting a non-significant correlation for additional information about the specific correlation coefficient when these were not provided.
 
-Where available we also recorded the geographic coordinates, number of sites, experiment type (greenhouse, field experiment, forest, shade-house etc.), growth measure (relative or absolute growth rate measured using plant diameter, height or mass), vegetation type, life form (tree, woody or mixed with herbaceous species etc.), biological scale (interspecific, intraspecific or intragenus), and experimental treatments (e.g.
-fertilization, shade, salt stress).
-We reported coefficient correlations for a list of 20 traits (Fig.
-\ref{Fig1}): the five for which we had prior expectations, plus 15 others which capture different aspects of plant species strategies and are commonly addressed in the trait literature.
-Specific leaf area (SLA), leaf area, leaf nitrogen and phosphorus concentration, net (mass) assimilation rates (NAR), and assimilation rate of CO2 (Aarea) are traits involved in species leaf economic strategy \citep{Wright:2004jb,Wright:2010tp}.
-Seed mass (SM), and maximum plant height (Hmax) capture information about reproductive strategy \citep{Falster:2005bw,Moles:2006ft}.
-Wood density (WD) and sapwood area per leaf area (SA/LA), vessel size and density, and stem specific conductance are all involved in species wood economic strategy  \citep{Chave:2009iy}.
+Overall, we recorded coefficient correlations for a list of 20 traits (Fig.
+\ref{fig:fig1}): the five for which we had prior expectations, plus 15 others commonly used in the trait literature.
+SLA, leaf area, leaf nitrogen and phosphorus concentration, net (mass) assimilation rates (NAR), and Aarea are traits involved in species leaf economic strategy \citep{Wright:2004jb,Wright:2010tp}.
+SM and Hmax capture information about reproductive strategy \citep{Falster:2005bw,Moles:2006ft}.
+WD and sapwood area per leaf area (SA/LA), vessel size and density, and stem specific conductance are all involved in species wood economic strategy  \citep{Chave:2009iy}.
 Here WD and SA/LA are also considered as indicators of stem construction cost (\citep{Falster:2011ii}, whereas SLA and leaf thickness capture crucial information about leaf construction cost \citep{Wright:2004jb}.
@@
 
-\subsection*{Plant stage categories}\label{plant-stage-categories}
+\subsubsection*{Plant stage categories}\label{plant-stage-categories}
 
-The authors of the 112 articles reported in our meta-analyses, categorized plants into four differents stages (i.e.
-seedling, juvenile, sapling, adult).
-While the stage categories have been established according to the expertise and the appreciation of the authors, by compiling data across multiple studies and across different growth form (tree and woody, etc), there is a risk of assigning plants of similar size to different categories.
-We verified the consistency of size/age range attributed to each stage across the 112 studies reported here.
-Fig.
-\ref{Fig2} showed that the thresholds in size/age used by the authors to defined a plant stage are quite steady.
+We were unable to obtain a consistent and continuous measure of plant size across all studies, thus we relied on categorical groupings by ``stage'' to test our hypotheses.
+The authors of the 112 articles used in the meta-analyses, reported their plants as belonging to any of fix different stages: ``seedling'', ``juvenile'', ``sapling'', ``adult'', ``mixed''.
+While these categories have been established according to the expertise of the authors, by compiling data across multiple studies and vegetation types, we were concerned about the risk of assigning plants of similar size to different categories.
+This risk turned out to be negligible: overall, we found that the original thresholds in size/age used by the authors to distinguish different stages was relatively compatible (Fig.
+\ref{fig:fig2}).
 In particular, there was a clear break between seedlings and saplings in both age (at 1 yr) and height (at 0.5 m); there was also a clear break between saplings and adults in diameter (at 10 cm).
-According to simple allometric relationships from the Biomass And Allometry Database (BAAD) \citep{Falster:2015}, these stage cutoffs match across the different size measurements (i.e.
-diameter, height and age, Fig.
-\ref{FigA1}).
-The size/stage threshold defined across the 112 articles, allowed us to attribute straightforwardly a stage category to studies for which no stage have been distinctly mentionned by the authors (5\% of the data, noted as ``mix'' in Fig.
-\ref{Fig2}).
+According to simple allometric relationships between size variables plotted using data from the Biomass And Allometry Database \citep{Falster:2015}, these thresholds also align relatively well with one another (Fig.
+\ref{fig:figA1}).
+Thus we adopted the above values as cut-offs for defining stage boundaries.
+However, the groups ``juvenile'' and ``sapling'' were largely overlapping, causing us to merge these two.
 
-Less than 5\% of the studies (i.e.
-five studies on 112) were ambiguous on their plant stage attribution.
+Using the identified boundaries among stages we were able to assign all studies into one of three classes: ``juvenile'', ``sapling'', or ``adult''.
+We preferred the term ``juvenile'' to ``seedling'', because for a portion of the scientific community ``seedling'' also refers to a particular experimental condition.
+Using the above cut-offs we were also able to assign a stage category to studies for which no stage have been distinctly mentioned by the authors (5\% of the data, noted as ``mix'' in Fig.
+\ref{fig:fig2}).
+Only 5 of 112 studies were ambiguous on their plant stage attribution.
 Half of these equivocal cases involved the juvenile category.
-The term ``juvenile'' is vague enough to cover size range from either seedling or sapling stages.
-according to the authors.
-This redundancy encourages us to focus on a three stage classification (i.e.
-juvenile, sapling, adult) instead of a four stage one (i.e.
-seedling, juvenile, sapling, adult).
-In the rest of the mansucript we preferred the term ``juvenile'' to ``seedling'', because for a portion of the scientific community ``seedling'' also refers to a particular experimental condition (a greenhouse experiment).
 We attributed a study to a new stage category only when 95\% of the recorded range of sizes for that study lay within a new stage category.
@@
 Results using the categories established by the authors are similar than the one using the standardized categories and are available in Fig.
-\ref{FigA5} model.1.
-In the main text, we report the results using the standardized categories.
+\ref{fig:figA5} model.1.
+In the main text, we report only results using the standardized categories.
 
@@
 
-Effect size calculation:
-We used the cross-species Pearson product-moment correlation coefficient r between growth rate and species trait as our measure of effect size, weighted by the number of species contributing.
-When studies did not report r values but another coefficient such as coefficient of determination (R2), Spearman's rho rank correlation or Kendall's tau rank correlation, we converted these to correlation coefficients  \citep{Lajeunesse:2013tm} (see code in Appendix \ref{app:supp_info_files} for details).
-When the magnitude of Pearson's correlation coefficient approaches +/- 1, its distribution becomes skewed.
-Accordingly we transformed the correlation r into a metric with desirable statistical properties using Fisher's z-transformation,
+\subsubsection*{Effect size calculation}
 
-\[ z = \frac{1}{2} \ln \frac{1+r}{1-r} \]
+As a measure of effect size, we used the cross-species Pearson product-moment correlation coefficient $r$ between growth rate and trait, weighted by the number of species contributing to the relationship.
+For studies that reported another coefficient -- such as coefficient of determination, Spearman's rho rank correlation, or Kendall's tau rank correlation -- we converted these to correlation coefficients following \citet{Lajeunesse:2013tm}.
+As the magnitude of Pearson's correlation coefficient approaches $\pm$ 1.0, its distribution becomes skewed.
+Accordingly we transformed the correlation $r$ into a metric $z$ with more-desirable statistical properties.
+The transformation was achieved via Fisher's z-transformation,
+\[ z = \frac{1}{2} \ln \frac{1+r}{1-r}, \]
+which has a variance estimate of
+\[ v_z= \frac{1}{n-3}, \]
+where $n$ is the number of species.
+We weighted effect size by the number of species used to calculation the correlation, instead of the raw number of individuals, because our questions primarily concerned the correlation between growth and traits across species and not within species.
 
-which has a variance estimate
+\subsubsection*{Stage effect}
 
-\[ v_z= \frac{1}{n-3} \]
-
-n being the number of species.
-We weighted effect size by the study precision using the number of species instead of the sample size because the question addressed in our study concerned the correlation between growth and traits across species and not within species.
-
-Stage effect:
-We tested stage effect on traits for which > 15 correlation coefficients across at least two stages were recorded.
+We tested stage effect on traits for which $>$ 15 correlation coefficients across at least two stages were recorded.
 We used a mixed-effect model of meta-analysis, in which it is assumed that studies within a stage share a common mean effect but that there is also random variation among studies in a stage, in addition to sampling variation.
-This random effect allows us to account for the heterogeneity among studies (e.g.~experimental type, vegetation type, error, etc.).
-For each trait, we established if stage could explain variance in the coefficient correlation by comparing models with the stage variable to the null model using log-likelihood ratios \citep{Zuur:2009cfa}.
+This random effect allows us to account for the heterogeneity among studies (e.g.
+experimental type, vegetation type, error, etc.).
+For each trait, we established if stage could explain variance in $z$ by comparing models with the stage variable to the null model using log-likelihood ratios \citep{Zuur:2009cfa}.
 If the log-likelihood test returned a significant p-value, the stage model fitted the data better than the null model.
@@
 
-Sensitivity analysis:
-We tested how robust are our results to the decision made in the analysis.
-In particular we tested our prediction using two datatset with different inclusion criteria.
+\subsubsection*{Sensitivity analysis}
+
+We tested how robust are our results were to the particular decisions made in the analysis, in the criteria used for including a study in the analysis.
 The number of species used to perform the correlation, the experimental conditions, and the concordance between stage used to measure trait and growth are clear criteria for assessing the quality of the data for addressing our hypotheses.
-Therefore, we focused exclusively on correlation across species, and we stratified the data set into two subsets: one including only studies under unstressed conditions ('ideal' dataset), and the other set including studies under all conditions ('complete' dataset).
-We excluded from the ``ideal'' dataset studies where growth and traits were measured on plants from different stages, unless a particular stage is by definition required to measure a trait such as for seed mass (i.e.
+Thus we stratified the data set into two subsets: one including only studies under unstressed conditions ('ideal' dataset), and the other set including studies under all conditions ('complete' dataset).
+We excluded from the ``ideal'' dataset studies where growth and traits were measured on plants from different stages, unless a particular stage is by definition required to measure a trait such as for SM (i.e.
 seed stage), or Hmax (i.e.
 adult stage).
-We also tested the sentivity of our results to the dominance of one or a few studies that measured a large number of response for the same trait.
-In the case of multiple comparisons within a study, we used the method proposed by \citet{Borenstein:2009um}: we calculated the mean correlation coefficient by trait and by study, and re-calculated the effect size.
-This corresponds to the ”reduced dataset” where multiple responses were condensed into a single average within a trait and within a study.
+We also tested the sensitivity of our results to inclusion of the few studies that measured a large number of responses for the same trait.
+In the case of multiple comparisons within a study, we used the method proposed by \citet{Borenstein:2009um}: we calculated the mean correlation coefficient by trait and by study, and then re-calculated the effect size.
+This produced a reduced dataset, where multiple responses for any given trait were condensed into a study-level average.
 
-Quality criteria for meta-analysis:
-We conducted several analyses to assess the reliability of our meta-analysis.
-In particular, we quantified heterogeneity in effects size, we tested for publication bias and we explored temporal change in effect size (see Appendix \ref{app:supp_info_files}).
-We addressed the 14 methodological quality criteria listed by \citet{Koricheva:2014ku} as required to assess the relaibility of a meta-analyses (Table A2 detailed how and where in this article each citeria is addressed).
+\subsubsection*{Quality criteria for meta-analysis}
 
-Availability of code and data:
+\cite{Koricheva:2014ku} outlined 14 methodological quality criteria to ensure robust results from meta-analyses.
+Table \ref{tab:meta} outlines how we address each of these.
+In particular, we quantified heterogeneity in effects size, we tested for publication bias and we explored temporal change in effect size (see Appendix \ref{app:supp_info_analyses}).
+
+\subsection*{Availability of code and data}\label{code}
+
 All analyses were conducted with R software \citep{Ralanguageanden:2014wf}.
-The code and data underpinning this paper is available at github.com/AnaisGibert/Growth\_trait\_metaanalysis.
-Archival copies are also included in Appendix \ref{app:supp_info_files} in Supplementary material.
+The code and data for producing all figures and results in this paper is available at github.com/AnaisGibert/Growth\_trait\_metaanalysis.
 
@@
 Model fits improved when stage was incorporated (see log likelihood ratio tests, Fig.
-\ref{Fig3} a and d; average values for the coefficients r ($r_{\textrm{mean}}$) in Fig.
-\ref{FigA4}).
-The correlation between growth and SLA shifted from strongly positive at juvenile stage $r_{\textrm{mean}}=0.6 \pm 0.08$, Mean +SD) to not significantly different from zero at adult stage ($r_{\textrm{mean}}= -0.01 \pm 0.07$, CI 95\% overlapping zero in Fig.
-\ref{Fig3} a).
-The correlation between growth and SM shifted from negative at juvenile stage ($r_{\textrm{mean}}= -0.59 \pm 0.07$) to not significantly different from zero at adult stage ($r_{\textrm{mean}}= -0.09 \pm 0.02$, , CI 95\% overlapping zero in Fig.
-\ref{Fig3} d).
+\ref{fig:fig3} a and d; average values for the coefficients ($\bar{r}$) in Fig.
+\ref{fig:figA4}).
+The correlation between growth and SLA shifted from strongly positive at juvenile stage $\bar{r}=0.6 \pm 0.08$, Mean $\pm$ SD) to not significantly different from zero at adult stage ($\bar{r}= -0.01 \pm 0.07$, CI 95\% overlapping zero in Fig.
+\ref{fig:fig3} a).
+The correlation between growth and SM shifted from negative at juvenile stage ($\bar{r}= -0.59 \pm 0.07$) to not significantly different from zero at adult stage ($\bar{r}= -0.09 \pm 0.02$, , CI 95\% overlapping zero in Fig.
+\ref{fig:fig3} d).
 For both traits, correlation coefficients recorded at sapling stage were intermediate between juvenile and adult stages.
 
-For WD, Hmax and Aarea, correlations with growth were also reasonably consistent with expectations, though with limitations arising from very unequal numbers of observations between growth stages.
+For WD, Hmax and Aarea, correlations with growth were also consistent with expectations, although with limitations arising from very unequal numbers of observations between growth stages for some traits.
 For Hmax, the expectation was for a correlation with growth to be absent for small plants but present at intermediate and larger sizes, the mechanism being increased relative allocation to reproduction as Hmax is approached.
-Indeed Hmax was positively correlated with growth at adult stage ($r_{\textrm{mean}}= 0.38 \pm 0.05$, n=18).
+Indeed Hmax was positively correlated with growth at adult stage ($\bar{r}= 0.38 \pm 0.05$, $n=18$).
 At sapling and juvenile stages, the correlation between Hmax and growth was not significantly different from that observed at adult stage (model fit not improved when stage was incorporated, see log likelihood ratio tests in Fig.
-\ref{Fig3} c), but also was consistent with no correlation (Fig \ref{Fig3} c, confidence intervals overlapping zero), due to much smaller numbers of replicate studies.
+\ref{fig:fig3} c), but also was consistent with no correlation (Fig \ref{fig:fig3} c, confidence intervals overlapping zero), due to much smaller numbers of replicate studies.
 Similarly for WD and for Aarea, results were consistent with negative (WD) and positive (Aarea) correlations with growth across all plant sizes (Fig.
-\ref{Fig3} b and e, model fit not improved when stage was incorporated).
+\ref{fig:fig3} b and e, model fit not improved when stage was incorporated).
 However, at the same time confidence intervals of r often spanned zero especially where there were small numbers of studies for particular growth stages.
-
-RGR in mass and height are commonly used to measure growth in small size tree, whereas AbsGR in diameter or height are more often used for larger stature tree. A ECRIRE
 
@@
 Given our basic conclusion that reported correlations responded to plant size in a manner consistent with expectations from theory, we assess now the coverage of the available data, to determine if biased sampling could have erroneously generated the above results.
-The results reported were confined to correlations across species, and under non-stressed conditions (n=176).
-A ``complete'' dataset (n=216) also included correlations measured under stressed conditions, and spanning different plant stages between the growth and trait measurements.
+
+In total, we found 112 studies published between between 1983 and 2014 that met our requirements.
+Climate zones spanned from temperate regions to  tropics (map in Fig.
+\ref{fig:figA2}).
+Different experiment types (laboratory, field, plantation or greenhouse), growth measurements and growth form (tree, woody or across growth form) were included.
+Number of species used for each correlation ranged from 2 to 300 species with average 31.
+Given this variety, it was not surprising to find wide ranges of $r$ reported for all traits.
+For instance, $r$ varied from -0.98 to 0.99 for SLA, and from -0.74 to 0.74 for WD (Fig.
+\ref{fig:figA3}).
+The growth form, the experiment types and the growth measurement were not markedly best predictors of the data (results shown in the Fig.
+\ref{fig:figA5}).
+
+The results reported above were confined to correlations across species, and under non-stressed conditions ($n = 176$).
+A ``complete'' dataset ($n = 216$) also included correlations measured under stressed conditions, and spanning different plant stages between the growth and trait measurements.
 This ``complete'' dataset generated similar effect sizes to those reported above from the ``ideal'' dataset, and led to similar conclusions (Fig.
-\ref{Fig3} grey points).
-Differences concerned often the confidence intervals around particular mean effect sizes in Fig.
-\ref{Fig3}.
+\ref{fig:fig3} grey points).
+Differences primarily concerned the confidence intervals around particular mean effect sizes in Fig.
+\ref{fig:fig3}.
 These differences in CI were not easily attributed to any single cause.
-For instance, the correlation between growth and WD at juvenile stage shifted from negative to non significant (i.e CI95\% included zero) due to 2 positive correlation coefficients from \citet{Augspurger:1984ct};  these correlations unlike others used wood density values from adult plants together with growth from juveniles.
+For instance, the correlation between growth and WD at juvenile stage shifted from negative to non significant (i.e CI 95\% included zero) due to 2 positive correlation coefficients from \citet{Augspurger:1984ct};  these correlations unlike others used values of WD from adult plants together with growth from juveniles.
 For Aarea, the comparison between complete and ideal data showed no signal of an effect of stress (here mainly low light) on the correlation with growth at seedling stage; the correlation was still positive between Aarea and growth even when 7 correlations measured under low light conditions were added.
 Finally, our results were unlikely to be biased by dominance of one or a few studies that measured a large number of responses, since when multiple responses were condensed into a single average within a trait and within a study, outcomes were very similar (Fig.
-\ref{FigA5}).
+\ref{fig:figA5}).
 
-We were pleasantly surprised to find that correlations had been reported for at least two different stages across 18 traits out of the 20 targeted (Fig.
-\ref{Fig1}).
-We had thought it likely that for some traits correlations would be reported only for one size class, or only mixed across different sizes.
-These limitations applied only for LAR and NARmass, where studies appeared confined to juvenile stages.
-However, among the 20 traits studied we had enough data to test the effect of stage on the correlation between growth and traits only for the five for which we had predictions.
-
-We found 112 studies published between between 1983 and 2014 that met our requirements.
-Climate zones spanned from temperate regions to  tropics (map in Fig.
-\ref{FigA2}).
-Different experiment types (laboratory, field, plantation or greenhouse), growth measurements and growth form (tree, woody or across growth form) were included.
-Number of species used for each correlation ranged from 2 to 300 species with average 31.
-Given this variety, it was not surprising to find wide ranges of r reported for all traits.
-For instance, r varied from -0.98 to 0.99 for SLA, and from -0.74 to 0.74 for WD (Fig.
-\ref{FigA3}).
-The growth form, the experiment types and the growth measurement were not markedly best predictors of the data (results shown in the Fig.
-\ref{FigA5}).
-
-We met all the quality criteria required for meta-analysis in ecology (Table 2).
+Overall our study met all the quality criteria required for meta-analysis in ecology (Table \ref{tab:meta}).
 We showed that the impact of publication bias is probably trivial in our meta-analyses (Appendix D, Fig.
-\ref{FigA7}).
-The extend of the heterogenity was high in our meta-analysis, and substantially explained by the plant stage for SLA and Seedmass as expected (Appendix D).
-Finally, temporal change in effect size did not jeopardizing the stability of our conclusions for all the traits (Appendix D, Fig.
-\ref{FigA9}).
+\ref{fig:figA7}).
+The extent of the heterogeneity was high in our meta-analysis,  but substantially explained by the plant stage effect for SLA and SM, as expected (Appendix D).
+Finally, there was no indication of a temporal change in the effect size being reported within stages (Appendix D, Fig.
+\ref{fig:figA9}).
 
@@
 
-The meta-analysis reported here demonstrates that the influence of traits on growth rates changes as plants grow from small to large, for several key traits.
-While this point has been made recently in smaller scale studies, it is the first time that mechanistic hypotheses are confirmed across a large number of studies already available.
-Meta-analysis allowed us to generalize and help to reach a concensus about trait influences on growth.
-Thus, plant growth rates change with size through ontogeny \citep{Condit:1993hd, Clark:1999ed, Herault:2011dd} - \textit{they follow a trajectory of growth} - and species traits should be understood as influencing this trajectory and consequently rearranging the ranking of growth rates with size, rather than as rendering species fast-growing or slow-growing throughout life.
+%TODO please insert refs below
+The meta-analysis reported here demonstrates that for several key traits the influence of traits on growth rates changes as plants grow from small to large.
+While this point has been made recently in smaller scale studies (refs??), it is the first time that mechanistic hypotheses are confirmed across a large number of studies already available.
+Meta-analysis allowed us to generalize and thus to reach a consensus about the effect of traits on growth.
+Growth rates are known to change with size through ontogeny \citep{Condit:1993hd, Clark:1999ed, Herault:2011dd}, \textit{i.e.
+plants follow a growth trajectory}; species traits should be understood as influencing this trajectory and potentially re-ranking growth rates with size.
+This is a shift in view from the current approach in plant strategy schemes, whereby traits are thought to render species fast-growing or slow-growing throughout life.
 
-\subsection*{Traits influence on growth along plant size}
+\subsection*{Why does the effect of traits on growth vary with size?}
 
@@
 This indicates provisionally that the mechanisms through which traits affect growth are correctly understood in the model.
-For specific leaf area (SLA) and for seed mass (SM) the meta-analysis confirms quite strongly the predicted influence of plant size on the trait-growth correlation.
-For wood density (WD), assimilation rate of CO2 (Aarea) and maximum height (Hmax) results were consistent with predictions, but coverage was limited and additional studies would be helpful for some trait-growth-stage relationships.
+For SLA and for SM the meta-analysis confirms quite strongly the predicted influence of plant size on the trait-growth correlation.
+For WD, Aarea and Hmax results were consistent with predictions, but coverage was limited and additional studies would be helpful for some trait-growth-stage relationships.
 
 It has previously been noted that the correlation of SLA with growth disappears among saplings and larger trees (\citealt{Wright:2010tp} for Barro Colorado Island forest, Panama), and this meta-analysis generalises that result.
-Several authors have suggested that the disappearance of SLA's influence on growth might be due to a disproportionate accumulation of leaf area by low SLA species \citep{Reich:1992wm,Poorter:2008iu,Wright:2010tp}, yet it remain uncear whether such a mechanism works as intended.
-More importantly, the assumed empirical relationship between SLA and total leaf area does not hold true across large number of species (Duursma and Falster, in review).In the model described here, the mechanism is slightly different: high-SLA species incur faster leaf and other tissues turnovers, the cost of which outweighs the benefits of cheap leaf construction at larger sizes.
+Several authors have suggested that the disappearance of SLA's influence on growth might be due to a disproportionate accumulation of leaf area by low SLA species \citep{Reich:1992wm,Poorter:2008iu,Wright:2010tp}, yet it remains unclear whether such a mechanism works as intended.
+More importantly, the assumed empirical relationship between SLA and total leaf area does not hold true across large number of species (Duursma and Falster, in review).
+In the model described here, the mechanism is slightly different: high-SLA species incur faster leaf turnover, the cost of which outweighs the benefits of cheap leaf construction at larger sizes.
 
-For seedlings our meta-analyses showed as expected a negative relationship between seed mass and relative growth rate (in mass or height or volume) that disappeared across plant stage.
-This negative relationship arises because seedlings from larger seeds are larger to begin with, as extensively discussed in the literature \citep[reviewed by][]{Turnbull:2012ew}.
-It applies only to RGR not to absolute growth rate, but for seedlings growth is most often reported as RGR (Appendix Fig.
-\ref{FigA8} d).
+For seedlings our meta-analyses showed, as expected, a negative relationship between SM and relative growth rate (in mass or height or volume) for small plants, that dissipated as plants grew larger.
+This negative relationship arises because seedlings from larger seeds are begin life larger themselves, as has been extensively discussed in the literature \citep[reviewed by][]{Turnbull:2012ew}.
+moreover, the prediction applies only to RGR not to AGR (Appendix Fig.
+\ref{fig:figA8} d).
 
@@
 It should be noted however that there are few tests of this proposition at seedling stage.
-In our model (Text Box 1 \ref{sec:growth}) cheaper stem construction is responsible for the predicted negative correlation.
+In our model (Appendix \ref{sec:growth}) cheaper stem construction is responsible for the predicted negative correlation.
 Lower xylem conductance and associated lower photosynthetic potential have also been suggested \citep[reviewed by][]{Chave:2009iy}.
 
-For the correlation between Aarea and growth, to our knowledge no study has previously assessed this in relation to plant size.
-In the growth model (Text Box 1 \ref{sec:growth}), a consistent correlation irrespective of size arises from a direct effect of Aarea on plant growth rate.
+As far as we are aware, our study is the first to compared correlations between Aarea and growth among small and large plants.
+In the growth model (Appendix \ref{sec:growth}), a consistent correlation irrespective of size arises from a direct effect of Aarea on plant growth rate.
 In juvenile stage, where most of the data were, we noted no signal of an effect of low light on the positive correlation between Aarea and growth rate.
@@
 
-Light and water micro-environments can affect growth values, and might modify correlations with traits in relation to plant size.
+Light and water micro-environments can affect growth rates, and might modify correlations with traits in relation to plant size.
 For example, instead of a positive relationship that disappeared with plant size, \citet{Iida:2014ep} found SLA was negatively correlated with RGR at small size and positively correlated with RGR at larger sizes.
@@
 \includegraphics{output/Fig1.pdf}
-\caption{Number of correlations between trait and growth for each plant stage recorded in our dataset.
-Shown here are ``raw dataset'' (recorded both across and within species, under unstressed and stressed conditions).
-Bar colors: red for adult, orange for sapling, grey for juvenile.
-Aarea (or Amass) = rate of $CO_{2}$ assimilation per unit leaf area (or leaf mass) = maximum photosynthetic rate, Hmax= asymptotic maximum height,  Ks =stem hydraulic conductance, LA = leaf area, LMR = leaf mass ratio, NARarea (or NARmass) = net mass assimilation rate per unit of leaf area (or leaf mass), Nmass (or Narea) = nitrogen content per unit of leaf mass (or leaf area), Pmass = phosphorus content per unit of leaf mass, SA/LA = sapwood area per leaf area, SLA = specific leaf area, thickness = leaf thickness, Vessel size = stem conduit size, vessel density = stem conduit density, WD = wood density}
-\label{Fig1}
+\caption{Number of recorded correlations between trait and growth rate in our dataset, byt size and trait.
+Results shown here are for the ``complete'' dataset (recorded both across and within species, under unstressed and stressed conditions).
+Traits are: Aarea (or Amass) = rate of CO$_{2}$ assimilation per unit leaf area (or leaf mass) = maximum photosynthetic rate, Hmax = asymptotic maximum height,  Ks = stem hydraulic conductance, LA = leaf area, LMR = leaf mass ratio, NARarea (or NARmass) = net mass assimilation rate per unit of leaf area (or leaf mass), Nmass (or Narea) = nitrogen content per unit of leaf mass (or leaf area), Pmass = phosphorus content per unit of leaf mass, SA/LA = sapwood area per leaf area, SLA = specific leaf area, thickness = leaf thickness, Vessel size = stem conduit size, vessel density = stem conduit density, WD = wood density.}
+\label{fig:fig1}
 \end{figure}
@@
 \includegraphics{output/Fig2.pdf}
-\caption{Range of plant size in \textbf{a)} age, \textbf{b)} height and \textbf{c)} diameter and the plant stage assigned by the authors of the articles used in the meta-analyses.
-Each segment represents the plant size range (max and min values) of the species used to measure the correlation between growth and traits in each article.
-ID is the reference number of the article in our dataset.
-The colors represents the stage information given by the authors (green: seedling, blue: juvenile, orange: sapling, red: adult, grey: unspecified by the authors), the vertical line represents the most likely limits between stage categories, the horizontal line styles corresponds to the species growth form used in each study (solid line: exclusively tree, dashed line: woody species , dotted line: tree mixed with another growth form).
-Shown here are the ``raw dataset'' (recorded both across and within species, and under unstressed and stressed conditions).}
-\label{Fig2}
+\caption{The range of plant sizes and stage recoded in original publications, compared to standardised thresholds used in the analysis. Panels are for
+\textbf{a)} age, \textbf{b)} height and \textbf{c)} diameter.
+Line segments indicate the size range (max., min.) for the plants used to measure growth.
+Article IDs correspond to the reference number in our dataset.
+Colours denote stage information given by the authors, while line styles denote growth form.
+The vertical lines indicate the thresholds used in our analysis.
+Results shown here are the ``complete'' dataset (see methods for details).}
+\label{fig:fig2}
 \end{figure}
@@
 \includegraphics{output/Fig3.pdf}
-\caption{The relationship between growth rates and SLA or seed mass changes with plant stage.
-Plots show the effect size (+ 95\%CI) of the correlation across species between growth rate and five functional traits for plant stage comparisons.
-\textbf{a)} Specific leaf area (SLA), \textbf{b)} Wood density (WD), \textbf{c)} Asymptotic height (Hmax) \textbf{d)} Seed mass and \textbf{e)} Assimilation rate of CO2 (Aarea).
+\caption{The relationship between growth rates and traits changes with plant stage and trait.
+Plots show the effect size (+ 95\%CI) for the average correlation across species, by plant stage.
 Effect size is a standardized measure of the deviation of correlation coefficient from zero (Fisher's z-transformed).
 Effects are significant if confidence intervals (95\%CI) for a given stage do not overlap with zero.
-Shown here are ``across species dataset'' (recorded only across species, and under both unstressed and stressed conditions).
-Black point: unstressed conditions, grey points: all the data.
-``n'' indicates number of correlations contributing to each effect.
-Likelihood Ratio Tests (LRT, for unstressed conditions only) compared maximum-likelihood fits between a pooled model and one separated by stage.
-A significant p-value means the stage model fitted the data better than the null model.
+Results shown are from both the ``complete'' (black)  and ``ideal'' (grey) datasets.
+Trait names as in Fig.
+\ref{fig:fig1}.
+$n$ indicates number of correlations contributing to each effect.
+Likelihood Ratio Tests (LRT, for ``ideal'' dataset only) compared maximum-likelihood fits between a pooled model and one separated by stage.
+A significant p-value means the model including stage effect fitted the data better than the null model.
 }
-\label{Fig3}
+\label{fig:fig3}
 \end{figure}
@@
 \caption{\textbf{Hypothesised effects of traits on key elements of plant function determining growth rate.} Arrows indicate the effect an increase in trait value would have on the main elements of growth eqs.
-\ref{eq:eq0}-\ref{eq:eq4} in Text box 1:  Leaf deployment per mass ($\frac{\textrm{d}a_\textrm{l}}{\textrm{d}m_\textrm{t}}$), Allocation to vegetative growth ($\frac{\textrm{d}m_\textrm{t}}{\textrm{d}b}$), Net live biomass production ($\frac{\textrm{d}b}{\textrm{d}t}$), Sapwood turnover ($k_s a_s$).
-SLA: Specific leaf area, WD: Wood density, Hmax: Asymptotic maximum height, SM: seed mass, Aarea: Maximum photosynthetic rate.
-For further details, see Text Box 1.}
+\ref{eq:eq0}-\ref{eq:eq4} in Appendix \ref{sec:growth}.
+Traits are SLA: Specific leaf area, WD: Wood density, Hmax: Asymptotic maximum height, SM: seed mass, Aarea: Maximum photosynthetic rate.
+For further details, see  Appendix \ref{sec:growth}.}
 \vspace{1cm}
-  \begin{tabular}{l p{3cm} p{2cm}p{4cm} p{2cm}}
-  & Leaf deployment \newline per mass
-  & Allocation to vegetative growth
-  & Net live biomass \newline production
-  & Sapwood turnover\\
-  & & & &\\\hline
-  & & & & \\
-Increase in : & & & & \\
-  SLA &$\nearrow$ &$\_$ & $\searrow$ \newline (via $\nearrow$ of tissue turnover) &$\_$ \\
-  WD & $\searrow$ &$\_$  &$\_$ &$\_$ \\
-  Hmax &$\_$ &$\nearrow$ &$\_$ &$\_$ \\
-  SM &$\_$&$\_$&$\_$& $\_$\\
-  Aarea &$\_$ &$\_$ & $\nearrow$ &$\_$ \\
+  \begin{tabular}{cccc}
+   & Leaf deployment per mass & Allocation to vegetative growth & Net live biomass production \\
+   Trait
+    & ($\frac{\textrm{d}a_\textrm{l}}{\textrm{d}m_\textrm{t}}$)
+    & ($\frac{\textrm{d}m_\textrm{t}}{\textrm{d}b}$)
+    & ($\frac{\textrm{d}b}{\textrm{d}t}$) \\ \hline
+  SLA &$\nearrow$ &$\_$ & $\searrow$  \\
+  WD & $\searrow$ &$\_$  &$\_$ \\
+  Hmax &$\_$ &$\nearrow$ &$\_$ \\
+  SM &$\_$&$\_$&$\_$ \\
+  Aarea &$\_$ &$\_$ & $\nearrow$ \\
 \hline
   \end{tabular}
+\label{tab:trade-offs}
   \end{table}
-\label{tab:trade-offs}
 
+%TODO: I suggest keeping this table, but merging the two right hand columns.
+The text in the explanation column mostly just repeats material that is presented elsewhere, so best to just say briefly where to find it.
 \clearpage
@@
 \centering
-\caption{\textbf{Checklist of quality criteria for meta-analysis in ecology} developed by Koricheva and Gurevitch (2014) }
-\label{Table 2}
+\caption{\textbf{Check-list of quality criteria for meta-analysis in ecology} developed by Koricheva and Gurevitch (2014) }
 \vspace{0.5cm}
@@
   1.
-Reporting full details of bibliographic searches & yes	& Google Scholar database was searched using the range of Boolean search terms ((``SLA'' OR ``LMA'' OR ``specific leaf area'' OR ``leaf    mass area'' OR ``wood density'' OR ``WD'' OR ``wood specific gravity'' OR ``stem density'' OR ``stem specific density'') AND (``growth rate'' OR ``relative growth rate'')) AND (``tree*'' OR ``woody*''), in english.
-& ``Systematic search'', Table A1 \\
+Reporting full details of bibliographic searches & yes	& Google Scholar database was searched using the range of Boolean search terms ((``SLA'' OR ``LMA'' OR ``specific leaf area'' OR ``leaf    mass area'' OR ``wood density'' OR ``WD'' OR ``wood specific gravity'' OR ``stem density'' OR ``stem specific density'') AND (``growth rate'' OR ``relative growth rate'')) AND (``tree*'' OR ``woody*''), in English.
+& ``Systematic search'', Table \ref{tab:lit_search} \\
   2.
@@
 Sensitivity analysis &	yes &	We tested how robust are our results to the decision made in the analysis.
-We calculated effect size using 3 differents dataset: i) an  ``ideal'' dataset, focusing on unstressed conditions exclusively, ii) a ``complete dataset'' reporting all conditions, and iii) a ``reduced dataset'' where multiple responses were condensed into a single average within a trait and within a study.
+We calculated effect size using 3 differents dataset: i) an  ``ideal'' dataset, focusing on unstressed conditions exclusively, ii) a ``complete'' dataset reporting all conditions, and iii) a ``reduced dataset'' where multiple responses were condensed into a single average within a trait and within a study.
 &	Fig3, FigA5 \\
   10.Exploring temporal changes in effect size &	yes	& There may be a confounding effect between the publication year and the stage.
-Thus, we explored the publication effect on the effect size within each stage for traits where a stage effect had been highlighted (SLA and Seedmass).
+Thus, we explored the publication effect on the effect size within each stage for traits where a stage effect had been highlighted (SLA and SM).
 & Appendix D, FigA9 \\
-  11. Controlling for phylogeny &	no &	It was not possible to control by the phylogeny since the number of species used to measured each coeffcient of correlation ranged from 2 to 300 species. &	\\
-  12. Specifying the software used &	yes	& R softward, code available on Github. & ``Availability of code and data'' \\
+  11. Controlling for phylogeny &	no &	It was not possible to control by the phylogeny since the number of species used to measured each coefficient of correlation ranged from 2 to 300 species. &	\\
+  12. Specifying the software used &	yes	& R software, code available on Github. & ``Availability of code and data'' \\
  13.
@@
 \end{tabular}
+\label{tab:meta}
 \end{table}
@@
 \clearpage
-\section*{Text Box 1} \label{sec:growth}
+\begin{appendices}\label{sec:appendices}
+\renewcommand{\thefigure}{S\arabic{figure}}
+\renewcommand{\thetable}{S\arabic{table}}
 
-\subsection*{Derivation of hypotheses from growth equations}
+\setcounter{figure}{0}
+\setcounter{table}{0}
 
-We adapted growth equations from \cite{Falster:2011ii} and \cite{falster:2013} to generate hypotheses on both absolute and relative growth rates in mass (eqn \ref{eq:eq1}), height (eqn \ref{eq:eq2}) and diameter (eqn \ref{eq:eq4}).
+\section{Derivation of hypotheses from growth equations}\label{sec:growth}
+
+We adapted growth equations from \cite{Falster:2011ii} to generate hypotheses on both absolute and relative growth rates in mass (eqn \ref{eq:eq1}), height (eqn \ref{eq:eq2}) and diameter (eqn \ref{eq:eq4}).
 
@@
 \begin{equation}\label{eq:eq0}
-\underbrace{\color{green}\frac{db}{dt}}_{\text{net live biomass production}} = \underbrace{y}_{\text{yield}}  \big(\underbrace{a_{l} A_{\textrm{area}}}_{\text{photosynthesis}} - \underbrace{\sum_{i=l,s,r,f} m_{i} r_{i}}_{\text{respiration}}\big) - \underbrace{ \sum_{i=l,s,r,f} m_{i} k_{i}}_{\text{turnover}},
+\underbrace{\frac{db}{dt}}_{\text{net live biomass production}} = \underbrace{y}_{\text{yield}}  \big(\underbrace{a_{l} A_{\textrm{area}}}_{\text{photosynthesis}} - \underbrace{\sum_{i = l,s,r,f} m_{i} r_{i}}_{\text{respiration}}\big) - \underbrace{ \sum_{i = l,s,r,f} m_{i} k_{i}}_{\text{turnover}},
 \end{equation}
@@
 
-Here, and in the following equations, $m_i$ denotes the \textbf{live mass on the plant}, $r_i$ the mass-specific \textbf{respiration rate}, and $k_i$ the \textbf{turnover rate} of different plant tissues; the subscripts $i=l,s,r,t,f$ referring to leaves, sapwood and bark, roots, total of these vegetative tissues, and to the reproductive tissues (fruits, flowers etc.) (note that the live biomass $b= m_t +m_f$).
-Similarly $a_i$ denotes \textbf{areas}, of leaves ($i=l$) and of cross-sections of total stem and sapwood ($i= st,ss$) respectively.
+Here, and in the following equations, $m_i$ denotes the \textbf{live mass on the plant}, $r_i$ the mass-specific \textbf{respiration rate}, and $k_i$ the \textbf{turnover rate} of different plant tissues; the subscripts $i = l,s,r,t,f$ referring to leaves, sapwood and bark, roots, total of these vegetative tissues, and to the reproductive tissues (fruits, flowers etc.) (note that the live biomass $b = m_t +m_f$).
+Similarly $a_i$ denotes \textbf{areas}, of leaves ($i = l$) and of cross-sections of total stem and sapwood ($i = st,ss$) respectively.
 
@@
 \begin{equation}\label{eq:eq1}
-\underbrace{{\color{magenta}\frac{dm_t}{dt}}}_{\text{growth rate in mass}} = \underbrace{\color{blue}\frac{dm_t}{db}}_{\text{allocation to vegetative growth}}  \times \underbrace{\color{green}\frac{db}{dt}}_{\text{net live biomass production}},
+\underbrace{{\frac{dm_t}{dt}}}_{\text{growth rate in mass}} = \underbrace{\frac{dm_t}{db}}_{\text{allocation to vegetative growth}}  \times \underbrace{\frac{db}{dt}}_{\text{net live biomass production}},
 \end{equation}
@@
 \begin{equation}\label{eq:eq2}
-\underbrace{\frac{dH}{dt}}_{\text{growth rate in height}} = \underbrace{\frac{dH}{da_{l}}}_{\text{architecture layout}} \times \underbrace{{\color{orange}\frac{da_{l}}{dm_{t}}}}_{\text{leaf deployment per mass}} \times {\color{blue}\frac{dm_t}{db}} \times {\color{green}\frac{db}{dt}}.
+\underbrace{\frac{dH}{dt}}_{\text{growth rate in height}} = \underbrace{\frac{dH}{da_{l}}}_{\text{architecture layout}} \times \underbrace{{\frac{da_{l}}{dm_{t}}}}_{\text{leaf deployment per mass}} \times {\frac{dm_t}{db}} \times {\frac{db}{dt}}.
 \end{equation}
@@
 \begin{equation}\label{eq:eq3}
-\underbrace{{\color{cyan}\frac{da_{st}}{dt}}}_{\text{basal area growth rate}} = \underbrace{\frac{da_{ss}}{da_{l}}}_{\text{sapwood area per leaf area}} \times {\color{orange}\frac{da_{l}}{dm_{t}}} \times  {\color{blue}\frac{dm_t}{db}} \times {\color{green}\frac{db}{dt}} +  \underbrace{ k_{s} a_s }_{\text{sapwood turnover}}.
+\underbrace{{\frac{da_{st}}{dt}}}_{\text{basal area growth rate}} = \underbrace{\frac{da_{ss}}{da_{l}}}_{\text{sapwood area per leaf area}} \times {\frac{da_{l}}{dm_{t}}} \times  {\frac{dm_t}{db}} \times {\frac{db}{dt}} +  \underbrace{ \frac{da_{st}}{dt}}_{\text{sapwood turnover}}.
 \end{equation}
@@
 \begin{equation}\label{eq:eq4}
-\underbrace{\frac{dD}{dt}}_{\text{growth rate in diameter}} = \sqrt[]{\frac{\Pi}{a_{st}}} \times {\color{cyan}\frac{da_{st}}{dt}}.
+\underbrace{\frac{dD}{dt}}_{\text{growth rate in diameter}} = \sqrt[]{\frac{\Pi}{a_{st}}} \times {\frac{da_{st}}{dt}}.
 \end{equation}
@@
 \begin{equation}\label{eq:eq1_seedlings}
-{\color{magenta}\frac{dm_t}{dt}}  \approx  a_{l} \, y \, (A_{\textrm{area}} - r_{l}).
+{\frac{dm_t}{dt}}  \approx  a_{l} \, y \, (A_{\textrm{area}} - r_{l}).
 \end{equation}
@@
 \end{equation}
- where net assimilation rate NAR=$y \, (A_{\textrm{area}} - r)$, SLA = $a_{l}/ m_{l}$ and leaf mass fraction LMF = $m_{l}/ m_{t}$.
+ where net assimilation rate NAR = $y \, (A_{\textrm{area}} - r)$, SLA = $a_{l}/ m_{l}$ and leaf mass fraction LMF = $m_{l}/ m_{t}$.
 
@@
 
-\textbf{Seed mass:} The $\textrm{RGR}_{\textrm{mass}}$ slows as plants grow larger, and large-seeded species begin larger as seedlings.
-For larger plants, seed mass is not expected to have any distinct influence on growth rates  (Table \ref{tab:trade-offs}).
+\textbf{Seed mass (SM):} The $\textrm{RGR}_{\textrm{mass}}$ slows as plants grow larger, and large-seeded species begin larger as seedlings.
+For larger plants, SM is not expected to have any distinct influence on growth rates  (Table \ref{tab:trade-offs}).
 
-\textbf{Aarea:} The effects of benefits (higher assimilation) and costs (higher respiration) of increased Area occur within the same element of eq.
+\textbf{Potential photosynthesis rate (Aarea):} The effects of benefits (higher assimilation) and costs (higher respiration) of increased Area occur within the same element of eq.
 \ref{eq:eq0}, and assimilation must outweigh respiration for there to be growth, so the net effect will be positive (Table \ref{tab:trade-offs}).
 
-Note that the predicted relationship between growth and either SLA or seed mass in seedlings differs if absolute growth rate in mass is used instead of $RGR_{mass}$ (i.e.
+Note that the predicted relationship between growth and either SLA or SM in seedlings differs if absolute growth rate in mass is used instead of RGR$_\textrm{mass}$ (i.e.
 becomes negative for SLA, positive for SM).
@@
 \clearpage
-\begin{appendices}\label{sec:appendices}
-\renewcommand{\thefigure}{S\arabic{figure}}
-\renewcommand{\thetable}{S\arabic{table}}
-
-\setcounter{figure}{0}
-\setcounter{table}{0}
 
@@
 
-The following files are provided:
+The code and data for producing all figures and results in this paper is available at github.com/AnaisGibert/Growth\_trait\_metaanalysis.
+Upon publication, a copy of the complete data set is also available from the Dryad Digital Repository.
 
-code.zip: the data and analysis code used to generate the results in this paper. A copy of the complete data set is also available from the Dryad Digital Repository.
-
-\clearpage
 \section{Supporting tables}\label{app:supp_info_tables}
@@
 definition and search term used in the meta-analysis}
-\label{TableA1}
+\label{tab:lit_search}
 \vspace{0.5cm}
@@
 Green lines corresponds to limits between juveniles and saplings, red lines to limits between saplings and adults.}
-\label{FigA1}
+\label{fig:figA1}
 \end{figure}
@@
 \includegraphics{output/FigA2.pdf}
-\caption{Geographical distribution of site locations from studies performed in the field used in the meta-analysis.
-Shown here are the ``raw dataset'' (recorded both across and within species, and under unstressed and stressed conditions).}
-\label{FigA2}
+\caption{Geographical distribution of site locations from studies performed in the field used in the meta-analysis. Results shown here are from the ``complete'' dataset (see methods for details).}
+\label{fig:figA2}
 \end{figure}
@@
 growth and trait reported in the literature (112 articles). Plots shown the coefficients of correlation (r)
-between the plant growth and \textbf{a)} Specific leaf area (SLA, n=
-111), \textbf{b)} Wood density (WD, n=64), \textbf{c)} Asymptotic
-maximum height (Hmax, n=23), \textbf{d)} Seed mass (Seedmass, n=36 and
-\textbf{e)} Rate of CO2 assimilation (Aarea, n=24) reported from 112
+between the plant growth and \textbf{a)} Specific leaf area (SLA, n =
+111), \textbf{b)} Wood density (WD, n = 64), \textbf{c)} Asymptotic
+maximum height (Hmax, n = 23), \textbf{d)} Seed mass (Seedmass, n = 36 and
+\textbf{e)} Rate of CO2 assimilation (Aarea, n = 24) reported from 112
 articles. The x abcissa represents the articles ID sorted by the average coefficient value r reported.
-Shown here are the ``raw dataset'' (recorded both across and within species
+Results shown here are from the ``complete'' dataset (recorded both across and within species
 and under unstressed and stressed conditions). Each bubble represents a r value, the diameter of the bubble
@@
 points to juveniles.}
-\label{FigA3}
+\label{fig:figA3}
 \end{figure}
@@
 Each panel corresponds to a functional trait: \textbf{a)} Specific leaf area (SLA), \textbf{b)} Wood density (WD), \textbf{c)} Net assimilation rate (NARarea), \textbf{d)} Seed mass, \textbf{e)} Asymptotic height (Hmax) and \textbf{f)} Assimilation rate of CO2 (Aarea).
-Shown here are the ``unstressed dataset'' (recorded across species and under unstressed conditions).}
-\label{FigA4}
+Results shown here are from the ``unstressed dataset'' (recorded across species and under unstressed conditions).}
+\label{fig:figA4}
 \end{figure}
@@
 ``n'' indicate the number of independent comparisons for each effect.}
-\label{FigA5}
+\label{fig:figA5}
 \end{figure}
@@
 \caption{\textbf{Effects size on the correlation between growth and traits of plant stage (mod1), vegetation type (mod2), growth measurement (mod3) and experiment type (mod4).} The effect size (z + 95\%CI) is reported for each class, and models are fitted by restricted max likelihood (REML).
-n= number of correlation r reported.
-Abbreviation: across veg= more than 2 vegetation types, boreal\&temp= boreal and temperate deciduous forest, med= Mediterranean,  temp\&med = temperate deciduous and Mediterranean forests, temp= temperate deciduous, temp rain= temperate rain, trop rain= tropical rain, trop seas= tropical seasonal forests, GR= growth rate and RGR= relative growth rate, measured in diameter (D), height (H), mass(M), cross section area (CSA).
+n = number of correlation r reported.
+Abbreviation: across veg = more than 2 vegetation types, boreal\&temp = boreal and temperate deciduous forest, med = Mediterranean,  temp\&med = temperate deciduous and Mediterranean forests, temp = temperate deciduous, temp rain = temperate rain, trop rain = tropical rain, trop seas = tropical seasonal forests, GR = growth rate and RGR = relative growth rate, measured in diameter (D), height (H), mass(M), cross section area (CSA).
 AIC: Akaike information criterion corresponds to the quality of each model, and allow a comparison between models.
 Smallest is the AIC better is the model.
-Shown here are ``ideal dataset'' (recorded at interspecific and under unstressed condition) and ``raw dataset'' (recorded at both interspecific and intraspecific level and under unstressed and stressed conditions).}
-\label{FigA6}
+Results shown here are from ``ideal'' dataset (recorded at interspecific and under unstressed condition) and ``complete'' dataset (recorded at both interspecific and intraspecific level and under unstressed and stressed conditions).}
+\label{fig:figA6}
 \end{figure}
@@
 \includegraphics{output/FigA7.pdf}
-\caption{\textbf{Funnel plots with filled in data based on the trim and fill method, showing transformed correlation coefficient z between growth and the traits a) Specific leaf area (SLA), b) Wood density (WD), c) Asymptotic height (Hmax), d) Seed mass and e) Assimilation rate of CO2 (Aarea)}.
-Shown here are ideal dataset (recorded across species and under unstressed conditions).
+\caption{\textbf{Funnel plots with filled in data based on the trim and fill method, showing transformed correlation coefficient z between growth and the traits a) Specific leaf area (SLA), b) Wood density (WD), c) Asymptotic height (Hmax), d) Seed mass (SM) and e) Assimilation rate of CO2 (Aarea)}.
+Results shown here are from the ``ideal'' dataset (recorded across species and under unstressed conditions).
 Note that in these plots the y axis is the 1/number of species included in the correlation, not the replication for the correlation.
@@
 The open points correspond to the estimated missing studies.
-The number of missing values is 9 for SLA,1 for WD, 0 for Hmax, 6 for Seedmass and 0 for Aarea}
-\label{FigA7}
+The number of missing values is 9 for SLA,1 for WD, 0 for Hmax, 6 for SM and 0 for Aarea}
+\label{fig:figA7}
 \end{figure}
@@
 \includegraphics{output/FigA8.pdf}
-\caption{\textbf{Growth measurement used by traits and by size.} Shown here are complete dataset (recorded across species and under both unstressed and stressed conditions).
-The colors correspond to the stage for which the r values have been recorded: red bars corresponds adult stage, orange bars to saplings, and grey bars to juveniles.}
-\label{FigA8}
+\caption{\textbf{Growth measurement used by traits and by size.} Results shown here are from the ``complete'' dataset (recorded across species and under both unstressed and stressed conditions).
+The colours correspond to the stage for which the r values have been recorded: red bars corresponds adult stage, orange bars to saplings, and grey bars to juveniles.}
+\label{fig:figA8}
 \end{figure}
@@
 \caption{\textbf{Temporal changes in coefficient of correlation between traits and growth.
-a) Specific leaf area (SLA), b) Wood density (WD), c) Asymptotic height (Hmax), d) Seed mass and e) Assimilation rate of CO2 (Aarea)} Shown here are ideal dataset (recorded across species and under  unstressed conditions).
-The colors correspond to the stage for which the r values have been recorded: red points corresponds adult stage, orange points to saplings, and grey points to juveniles.}
-\label{FigA9}
+a) Specific leaf area (SLA), b) Wood density (WD), c) Asymptotic height (Hmax), d) Seed mass (SM) and e) Assimilation rate of CO2 (Aarea)} Results shown here are from the ``ideal'' dataset (recorded across species and under  unstressed conditions).
+The colours correspond to the stage for which the r values have been recorded: red points corresponds adult stage, orange points to saplings, and grey points to juveniles.}
+\label{fig:figA9}
 \end{figure}
@@
 $I^{2}$ estimates the consistency of the results obtained from published studies used in our meta-analysis; it describes the percentage of variability in point estimates that is due to heterogeneity rather than sampling error.
-It can be interpreted as a ratio (0\% < $I^{2}$ < 100\%) not affected by the number of studies or the metric of the effect size in the analysis.
+It can be interpreted as a ratio (0\% $<$ $I^{2}$ $<$ 100\%) not affected by the number of studies or the metric of the effect size in the analysis.
 It also has the advantage of being analogous to indices used for regression (where R2 is the proportion of the total variance that can be explained by the covariates) a common statistics in the trait literature.
@@
 
-\textbf{Results:} We observed high levels of heterogeneity for all traits (SLA :$I^{2}$ 85.4\% CI: 80.9 to 92.1, WD :$I^{2}$ 61.8\% CI: 42.8 to 84.1, Hmax: $I^{2}$ 81.2\% CI: 69.8 to 93.4, Seedmass: $I^{2}$ 91.2\%, 85.9 to 96.1, Aarea: $I^{2}$ 68.3\% CI: 33.7 to 90.1) which suggests that the correlations coefficient r between growth and traits are not uniform across the range of studies investigated.
+\textbf{Results:} We observed high levels of heterogeneity for all traits (SLA :$I^{2}$ 85.4\% CI: 80.9 to 92.1, WD :$I^{2}$ 61.8\% CI: 42.8 to 84.1, Hmax: $I^{2}$ 81.2\% CI: 69.8 to 93.4, SM: $I^{2}$ 91.2\%, 85.9 to 96.1, Aarea: $I^{2}$ 68.3\% CI: 33.7 to 90.1) which suggests that the correlations coefficient r between growth and traits are not uniform across the range of studies investigated.
 This result suggested that a large part of the variance is not explained by sample error.
 
-For SLA and Seedmass, 50.1\% and 20\% respectively of the total amount of heterogeneity were accounted by including the stage as a moderator.
-For the other traits, the stage explained few or no part of the heterogeneity observed across studies (<5\%).
-These results were consistent with our expectations about a shift in the relationship between growth and traits along plant size for SLA, Seed mass and the absence of effect for WD and Aarea (see Theoretical expectation section).
-The result of Hmax was more ambigus since we expected the relationship between asymptotic maximum height (Hmax) and growth rate to be absent in seedlings but to strengthen with increasing plant size (at adult stage).
+For SLA and SM, 50.1\% and 20\% respectively of the total amount of heterogeneity were accounted by including the stage as a moderator.
+For the other traits, the stage explained few or no part of the heterogeneity observed across studies ($<$5\%).
+These results were consistent with our expectations about a shift in the relationship between growth and traits along plant size for SLA, SM and the absence of effect for WD and Aarea (see Theoretical expectation section).
+The result of Hmax was more ambiguous since we expected the relationship between Hmax and growth rate to be absent in seedlings but to strengthen with increasing plant size (at adult stage).
 As discussed in the result section of the article, the smaller numbers of replicate studies for sapling and seedling stage limited the generality of our conclusion for this trait.
@@
 A publication bias occurs when the probability of publication depends on the statistical significance of the effect.
-Here we tested if there is an evidence of any bias, and if the effect size observed for each trait is an artefact of this biais.
+Here we tested if there is an evidence of any bias, and if the effect size observed for each trait is an artefact of this bias.
 
@@
 While funnel plot are recommended to aid interpretation, there is a high risk failing to detect actual publication bias (see (\citealt{Koricheva:2013tz}) by using exclusively a visual assessment.
-In addition, funnel plots are not effective when the number of studies is small (<30) such as for Aarea and Seed mass.
-We also used the ‘trim and fill’ method to estimate the number of studies missing from our meta-analyse. This method adjusts for funnel plot asymmetry \citep{Duval:2000dg}.
+In addition, funnel plots are not effective when the number of studies is small ($<30$) such as for Aarea and SM.
+We also used the ``trim and fill'' method to estimate the number of studies missing from our meta-analyse. This method adjusts for funnel plot asymmetry \citep{Duval:2000dg}.
 Finally, we estimated the number of studies needed to overturn a result, using the Rosenberg’s fail-safe number \citep{Rosenberg:2005hk}.
@@
 A significant meta-analytic result is robust if the fail-safe N is greater than 5k+10, where k is the number or studies already in the meta-analysis \citep{Rosenthal:1979do}.
-In R, we used the package metafor (code available on guithub).
+In R, we used the package `metafor` (code available on guithub).
 
 \textbf{Result:} As expected the correlation coefficient varied less widely as sample size increased (funnel plots in Fig.
-\ref{FigA9}).
+\ref{fig:figA9}).
 Funnel plots exhibited a typical funnel shape for all five functional traits analyzed, showing no evidence for publication bias (Fig.
-\ref{FigA9}).
+\ref{fig:figA9}).
 The ‘trim and fill’ method detected some missing values in our data.
 The estimated number of missing value ranges from 0 to 9 depending on the trait considered (Fig.
-\ref{FigA9}).
-The overall estimates measured with the fill in data changed from 0.5 ±0.07 to 0.4 ±0.07 for SLA and from -0.48±0.11 to -0.32±0.12 for the seed mass, suggesting a lower correlation coefficient for SLA, and Seedmass.
+\ref{fig:figA9}).
+The overall estimates measured with the fill in data changed from $0.5 \pm 0.07$  to $0.4 \pm 0.07$  for SLA and from $-0.48 \pm 0.11$  to $-0.32 \pm 0.12$  for the seed mass, suggesting a lower correlation coefficient for SLA, and SM.
 Even if the estimated correlation were closest from zero with the missing studied filled in, the results still indicate that the effect is statistically significant.
@@
 Indeed, in the early 90’s studies mainly focused on seedlings, whereas today a broader range of plant size/stage are studied (Fig.
-\ref{FigA9}).
+\ref{fig:figA9}).
 As a consequence, we used publication year as a moderator in our analyses \citep{Zvereva:2008jm}p across and within stages for all traits.
 
-\textbf{Results:} There was a change in the effect size with publication year for SLA (pvalue<0.0001, estimates: -0.04 ±0.009), Seed mass (pvalue =0.011, estimates: 0.041 ±0.016) and Aarea (pvalue=0.0102, estimates: -0.0453± 0.0176).
+\textbf{Results:} There was a change in the effect size with publication year for SLA ($p<0.0001$, estimates: $-0.04 \pm 0.009$ ), SM ($p = 0.011$, estimates: $0.041 \pm 0.016$ ) and Aarea ($p = 0.0102$, estimates: $-0.0453 \pm 0.0176$ ).
 The Fig.
-\ref{FigA9} showed that for these 3 traits the publication years may be confounded with plant stage; the correlation coefficients have been reported from 1993, but studies started to report data on adult stage only 10 years later (around 2000-2007).
+\ref{fig:figA9} showed that for these 3 traits the publication years may be confounded with plant stage; the correlation coefficients have been reported from 1993, but studies started to report data on adult stage only 10 years later (around 2000-2007).
 
-For SLA and Seed mass, a publication year effect was not observed within seedling and sapling stages, but was identified for the adult stage (SLA pvalue=0.003, Seedmass pvalue=0.06).
-For both SLA and Seedmass, the magnitude of the effect size decreased with publication year (Fig.
-\ref{FigA9} a and d), suggesting we overestimated the magnitude of the effect size for these two traits.
-In reality, the main effect size obtained would be more close to zero or more negative for SLA and more positive for Seedmass.
-These results are consistent with our hypotheses; we expected a negative or non-significant effect of SLA on growth in adult stage, and a non-significant or positive effect of Seed mass on plant growth (see theoretical expectation).
+For SLA and SM, a publication year effect was not observed within seedling and sapling stages, but was identified for the adult stage (SLA $p = 0.003$, SM $p = 0.06$).
+For both SLA and SM, the magnitude of the effect size decreased with publication year (Fig.
+\ref{fig:figA9} a and d), suggesting we overestimated the magnitude of the effect size for these two traits.
+In reality, the main effect size obtained would be more close to zero or more negative for SLA and more positive for SM.
+These results are consistent with our hypotheses; we expected a negative or non-significant effect of SLA on growth in adult stage, and a non-significant or positive effect of SM on plant growth (see theoretical expectation).
 
@@
 While overestimated, the main effect size for the correlation between growth and Aarea stay positive  (Fig.
-\ref{FigA9} e).
+\ref{fig:figA9} e).
 

### 2015-09-02 build.R
Script to build pdf

@@ -1,0 +1,69 @@
+#!/usr/bin/env Rscript
+
+latex_build <- function(filename, bibliography=NULL,
+                        chdir=TRUE, interaction="nonstopmode",
+                        max_attempts=5L, clean=FALSE, engine="pdflatex") {
+  if (chdir && dirname(filename) != "") {
+    owd <- setwd(dirname(filename))
+    on.exit(setwd(owd))
+    filename <- basename(filename)
+  }
+
+  res <- run_latex(filename, interaction, engine)
+  if(engine=="xelatex") {
+      res <- run_latex(filename, interaction, engine)
+  }
+  if (!is.null(bibliography)) {
+    run_bibtex(filename)
+    res <- run_latex(filename, interaction, engine)
+  }
+
+  pat <- c("Rerun to get cross-references right", # labels
+           "Rerun to get citations correct",      # bibtex
+           "Rerun to get outlines right")         # tikz
+  isin <- function(p, x) {
+    any(grepl(p, x))
+  }
+  for (i in seq_len(max_attempts)) {
+    if (any(vapply(pat, isin, logical(1), res))) {
+      res <- run_latex(filename, interaction, engine)
+    } else {
+      break
+    }
+  }
+
+  if (clean) {
+    latex_clean(filename)
+  }
+
+  invisible(NULL)
+}
+
+latex_clean <- function(filename) {
+  filebase <- sub(".tex$", "", filename)
+  exts <- c(".log", ".aux", ".bbl", ".blg", ".fls", ".out", ".snm",
+            ".nav", ".tdo", ".toc")
+  aux <- paste0(filebase, exts)
+  file.remove(aux[file.exists(aux)])
+}
+
+run_latex <- function(filename, interaction="nonstopmode", engine="pdflatex") {
+  args <- c(paste0("-interaction=", interaction),
+            "-halt-on-error",
+            filename)
+  callr::call_system(Sys_which(engine), args)
+}
+
+run_bibtex <- function(filename) {
+  callr::call_system(Sys_which("bibtex"), sub(".tex$", "", filename))
+}
+
+Sys_which <- function(x) {
+  ret <- Sys.which(x)
+  if (ret == "") {
+    stop(sprintf("%s not found in $PATH", x))
+  }
+  ret
+}
+
+latex_build("MS.tex", bibliography="references/paper.bib", clean=TRUE)

### 2015-09-02 MS.tex
Format for BES journals
Formatting files kindly provided by Rich FitzJohn

@@
-\documentclass[a4paper]{article}\usepackage[]{graphicx}\usepackage[]{color}
-\usepackage{alltt}
-\usepackage{amssymb,amsmath}
-\usepackage{palatino}
-\usepackage{framed}
-\usepackage{parskip}
+\documentclass[a4paper,11pt]{article}
+\usepackage[osf]{mathpazo}
+\usepackage{ms}
+\usepackage[]{natbib}
+\raggedright
+
+\newcommand{\smurl}[1]{{\footnotesize\url{#1}}}
 \usepackage{graphicx}
-\usepackage{fixltx2e}
-\usepackage[default,osfigures,scale=0.95]{opensans}
-\usepackage{geometry}
-\usepackage{longtable}
-\usepackage{authblk}
-\usepackage[colorinlistoftodos]{todonotes}
-\geometry{verbose,tmargin=2cm,bmargin=2cm,lmargin=2cm,rmargin=2.5cm}
-\linespread{2}
-\usepackage{color}
-
 \usepackage[title,titletoc,toc]{appendix}
 
-\usepackage{etoolbox}
-\newbool{MyRefNumbers}
-\booltrue{MyRefNumbers}
+\title{On the link between functional traits and growth rate: meta-analysis shows effects change with plant size, as predicted}
+\author{Anais Gibert\textasteriskcentered, Emma F. Gray, Mark Westoby, Ian J. Wright, Daniel S. Falster}
+\affiliation{Biological Sciences, Macquarie University NSW 2109, Australia\\
+\textasteriskcentered Email for correspondence: \texttt{ anais.gibert@gmail.com}\\
+Word count: ~XXXX words}
+\date{}
 
-\usepackage{natbib}
-
-\bibliographystyle{ecol_let}
-\setcitestyle{authoryear,open={(},close={)}}
+\bibliographystyle{mee}
 \newcommand{\bibstar}{* }
 
+\mstype{Research Article}
+\runninghead{Influence of traits on growth changes with size}
+\keywords{maximum height, photosynthetic rate, ontogenetic stage, functional trait, growth strategy, seed mass, specific leaf area, wood density}
+
 \begin{document}
-
-\clearpage
-
-\title{On the link between functional traits and growth rate: meta-analysis shows effects change with plant size, as predicted}
-
-\author[1]{Anais Gibert*}
-\author[1]{Emma F. Gray}
-\author[1]{Mark Westoby}
-\author[1]{Ian J. Wright}
-\author[1]{Daniel S. Falster}
-\affil[1]{Biological Sciences, Macquarie University NSW 2109, Australia}
-
-\maketitle
-
-\textit{Running title (36/45 characters)}Influence of traits on growth changes with size
-
-\textit{Corresponding author} Anais Gibert, anais.gibert@gmail.com, Biological Sciences, Macquarie University NSW 2109, Australia, tel: +61 2 9850 8194
-
-\clearpage
-
-\section*{Abstract (195/350 words)}\label{abstract}
-
+\mstitlepage
+\noindent
+\parindent=1.5em
+\addtolength{\parskip}{.3em}
+\doublespacing
+\linenumbers
+\section{Summary}\label{abstract}
 \begin{enumerate}
-
-\item
-Growth rates (GR) have often been seen as central elements of plant ecological strategies, and as linked to species traits.
+\def\labelenumi{\arabic{enumi}.}
+\itemsep1pt\parskip0pt\parsep0pt
+\item Growth rates (GR) have often been seen as central elements of plant ecological strategies, and as linked to species traits.
 Yet, the literature is inconsistent about empirical correlations between functional traits and plant growth rate, casting doubt on the capacity of traits to predict growth.
 
-\item
-Traits should influence growth in a way that depend on individual plants size.
+\item Traits should influence growth in a way that depend on individual plants size.
 We outline mechanisms and hypotheses based on new theory, and test these predictions in tree species for five traits using a meta-analysis of 112 studies ($>$ 500 correlations).
@@
 
-\item
-Results were consistent with predictions.
+\item Results were consistent with predictions.
 Specific leaf area was correlated with GR in juvenile but not in adult plants.
@@
 
-\item
-Synthesis: We show that traits-GR correlations change in a predictable way as a function of plant size.
+\item Synthesis: We show that traits-GR correlations change in a predictable way as a function of plant size.
 Our understanding of plant strategies should shift away from attributing slow vs fast growth to species throughout life, in favour of attributing growth trajectories.
@@
 \end{enumerate}
-
-\textit{Keywords (8/10)} asymptotic maximum height, maximum photosynthetic rate, plant ontogenetic stage, plant functional traits, plant growth strategy, seed mass, specific leaf area, wood density
 
@@
 All analyses were conducted with R software \citep{Ralanguageanden:2014wf}.
-The code and data for producing all figures and results in this paper is available at github.com/AnaisGibert/Growth\_trait\_metaanalysis.
+The code and data for producing all figures and results in this paper is available at \smurl{github.com/AnaisGibert/Growth\_trait\_metaanalysis}.
 
@@
 \centering
-\includegraphics{output/Fig1.pdf}
+\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/Fig1.pdf}
 \caption{Number of recorded correlations between trait and growth rate in our dataset, byt size and trait.
@@
 \centering
-\includegraphics{output/Fig2.pdf}
+\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/Fig2.pdf}
 \caption{The range of plant sizes and stage recoded in original publications, compared to standardised thresholds used in the analysis. Panels are for
@@
 \centering
-\includegraphics{output/Fig3.pdf}
+\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/Fig3.pdf}
 \caption{The relationship between growth rates and traits changes with plant stage and trait.
@@
 For further details, see  Appendix \ref{sec:growth}.}
+{\footnotesize
 \vspace{1cm}
@@
   \end{tabular}
+  }
 \label{tab:trade-offs}
@@
 \caption{\textbf{Check-list of quality criteria for meta-analysis in ecology} developed by Koricheva and Gurevitch (2014) }
+{\footnotesize
 \vspace{0.5cm}
@@
 \end{tabular}
+}
 \label{tab:meta}
@@
 \clearpage
+\setcounter{secnumdepth}{1}
 \begin{appendices}\label{sec:appendices}
@@
 \vspace{0.5cm}
+{\footnotesize
 \begin{tabular}{p{3cm}p{3cm}p{8cm}}
@@
 \end{tabular}
+}
 \end{table}
@@
 \centering
-\includegraphics{output/FigA1.pdf}
+\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA1.pdf}
 \caption{Allometric relationships between a) age and diameter (m), b) age and height (m), and c) diameter and height in trees according to the BAAD database.
@@
 \centering
-\includegraphics{output/FigA2.pdf}
+\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA2.pdf}
 \caption{Geographical distribution of site locations from studies performed in the field used in the meta-analysis. Results shown here are from the ``complete'' dataset (see methods for details).}
@@
 \centering
-\includegraphics{output/FigA3.pdf}
+\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA3.pdf}
 \caption{Range of correlations (r) between
@@
 \centering
-\includegraphics{output/FigA4.pdf}
+\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA4.pdf}
 \end{figure}
@@
 \centering
-\includegraphics{output/FigA4b.pdf}
+\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA4b.pdf}
 \caption{\textbf{Mean coefficient correlation r (+SD) between growth rate and traits, established from 112 articles.} The mean coefficients are weighted by sample size (i.e number of species used to perform the correlation), and calculated both across all plant stages and for each stage.
@@
 \centering
-\includegraphics{output/FigA5.pdf}
+\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA5.pdf}
 \caption{\textbf{Effect size (+ 95\%CI) of plant stage on the correlations between growth rate and five functional traits across species, with a data set averaging multiple comparisons by trait and by study.} Effects size are calculated from a reduced dataset; in the case of multiple comparisons within a study, we calculated the mean correlation coefficient by trait and by study.
@@
 \centering
-\includegraphics{output/FigA6a.pdf}
+\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA6a.pdf}
 \end{figure}
@@
 \centering
-\includegraphics{output/FigA6b.pdf}
+\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA6b.pdf}
 \end{figure}
@@
 \centering
-\includegraphics{output/FigA6c.pdf}
+\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA6c.pdf}
 \caption{\textbf{Effects size on the correlation between growth and traits of plant stage (mod1), vegetation type (mod2), growth measurement (mod3) and experiment type (mod4).} The effect size (z + 95\%CI) is reported for each class, and models are fitted by restricted max likelihood (REML).
@@
 \centering
-\includegraphics{output/FigA7.pdf}
+\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA7.pdf}
 \caption{\textbf{Funnel plots with filled in data based on the trim and fill method, showing transformed correlation coefficient z between growth and the traits a) Specific leaf area (SLA), b) Wood density (WD), c) Asymptotic height (Hmax), d) Seed mass (SM) and e) Assimilation rate of CO2 (Aarea)}.
@@
 \centering
-\includegraphics{output/FigA8.pdf}
+\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA8.pdf}
 \caption{\textbf{Growth measurement used by traits and by size.} Results shown here are from the ``complete'' dataset (recorded across species and under both unstressed and stressed conditions).
@@
 \centering
-\includegraphics{output/FigA9.pdf}
+\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA9.pdf}
 \caption{\textbf{Temporal changes in coefficient of correlation between traits and growth.

### 2015-09-03 MS.tex
Change Fig and table

@@
 \usepackage[]{natbib}
-\raggedright
+%\raggedright
 
-\newcommand{\smurl}[1]{{\footnotesize\url{#1}}}
+\newcommand{\smurl}[1]{\url{#1}}
 \usepackage{graphicx}
@@
 
-\subsection*{Dataset construction}
+\subsection*{Dataset construction}\label{data-construction}
 
@@
 The others equivocal cases were caused by an ambiguity in the definition of ``adult'' used by the authors.
-Some plants with a large stature are not assessed as adult by the authors because they are still non reproductive (see ID 52 and 50).
+Some plants with a large stature are not assessed as adult by the authors because they are still non reproductive (see ID 150).
 Here, we attributed a study to the adult stage when the authors identified the plants as reproductive, and to sapling stage when they identified the plants as non-reproductive, regardless the plant size or age.
@@
 
-\subsubsection*{Effect size calculation}
+\subsubsection*{Effect size calculation}\label{effect-size}
 
@@
 
-\subsubsection*{Stage effect}
+\subsubsection*{Stage effect}\label{stage-effect}
 
@@
 
-\subsubsection*{Sensitivity analysis}
+\subsubsection*{Sensitivity analysis}\label{sensitivity-analysis}
 
@@
 \vspace{0.5cm}
-\begin{tabular}{p{3cm} p{1cm} p{10cm} p{3cm}}
+\begin{tabular}{p{0.2cm}p{5cm}p{0.8cm}p{9cm}}
   \hline
-  Quality criteria & Check & Explanations & Addressed in \\
+  & Quality criteria & Check & How and where is it addressed? \\
   \hline
-  1.
-Reporting full details of bibliographic searches & yes	& Google Scholar database was searched using the range of Boolean search terms ((``SLA'' OR ``LMA'' OR ``specific leaf area'' OR ``leaf    mass area'' OR ``wood density'' OR ``WD'' OR ``wood specific gravity'' OR ``stem density'' OR ``stem specific density'') AND (``growth rate'' OR ``relative growth rate'')) AND (``tree*'' OR ``woody*''), in English.
-& ``Systematic search'', Table \ref{tab:lit_search} \\
-  2.
-Reporting inclusion/exclusion criteria & yes & Studies included report i) correlation coefficient between growth and trait, ii) the sample size/ number of species, and iii) the size/stage of plants.
-Studies excluded report correlation within species	& ``Systematic search'' \\
-  3.
-Weighting effect sizes by study precision & yes & Effects sizes were weighted by number of species.
-The question addressed in our study concerns the correlation between growth and trait across species, thus the number of species is a better proxy of a study quality than sample size.
-&	 ``Systematic search'' and  ``Effect size calculation'' \\
- 4. Specifying meta-analytical model &	yes	& Mixed-effect model with a study ID as a random variation, and stage as a fixed effect, m1 ~lmer (stage + (1|ID)) &	``Statistical analyses'', Fig3 \\
- 5. Quantifying heterogeneity in effect sizes &	yes &	We estimated the extend of the heterogeneity using the statistics $I^{2}$ (Santos and Nakagawa, 2012) for each trait. &	Appendix D \\
- 6. Exploring causes of heterogeneity &	yes &	We explored two causes of variability: the stage and the year of publication & Appendix D, Fig3 \\
- 7.
-Multifactorial analysis of explanatory variable	& yes & We focused on the ``plant stage'' as the main exploratory variable.
-Yet, the stage variable may be confounded with other explanatory moderators (i.e.
-growth measurement, experiment type or growth form).
-Thus, we checked if no one of them would not consistenly be a strongest predictor of the data.
+  1.& Reporting full details of bibliographic searches & yes	& We provided complete details of bibliographic searches (i.e.
+electronic reference data bases that were searched, keywords, language and search dates) in sub-section "Phase 2 - Systematic search" in material and method.\\
+  2.& Reporting inclusion/exclusion criteria & yes & We specified several inclusion criteria in the sub-section "Phase 2 - Systematic search" in material and method.
+The Bibtex file `read.bib` on Guithub reports all the articles red but laid out because they failed to met our criteria.\\
+  3.& Weighting effect sizes by study precision & yes & Effects sizes were weighted by number of species. See	 details in sub-section ``Effect size calculation'' in material and method.\\
+ 4.& Specifying meta-analytical model &	yes	& We used a mixed-effect model with a study ID as a random variation, and stage as a fixed effect.
+See details in sub-section "Stage effect" in material and methods.
+Results are shown in Fig3.\\
+ 5.& Quantifying heterogeneity in effect sizes &	yes &	We estimated the extend of the heterogeneity using the statistics $I^{2}$ for each trait. See details of methods and results in Appendix D.\\
+ 6.& Exploring causes of heterogeneity & yes &	We explored the effect of stage, and the year of publication (see points 4 and 10 in this list). \\
+ 7.& Multifactorial analysis of explanatory variable	& yes & We checked if no one of several other explanatory moderators (i.e.
+growth measurement, experiment type or growth form) would not consistenly be a strongest predictor of the data.
 We did not test the multiple variables in a hierarchical fashion, because of the limited size of our dataset.
-& FigA4, FigA6  \\
-  8.
-Testing for publication bias &	yes	& We used funnel plots for a visual assessment.
-We used the ``trim and fill'' method to estimate the number of studies missing (Duval and Tweedie 2000).
-We also estimated the Rosenberg’s fail-safe number (Rosenberg 2005).
-	&  Appendix D, FigA7\\
-  9.
-Sensitivity analysis &	yes &	We tested how robust are our results to the decision made in the analysis.
-We calculated effect size using 3 differents dataset: i) an  ``ideal'' dataset, focusing on unstressed conditions exclusively, ii) a ``complete'' dataset reporting all conditions, and iii) a ``reduced dataset'' where multiple responses were condensed into a single average within a trait and within a study.
-&	Fig3, FigA5 \\
-  10.Exploring temporal changes in effect size &	yes	& There may be a confounding effect between the publication year and the stage.
-Thus, we explored the publication effect on the effect size within each stage for traits where a stage effect had been highlighted (SLA and SM).
-& Appendix D, FigA9 \\
-  11. Controlling for phylogeny &	no &	It was not possible to control by the phylogeny since the number of species used to measured each coefficient of correlation ranged from 2 to 300 species. &	\\
-  12. Specifying the software used &	yes	& R software, code available on Github. & ``Availability of code and data'' \\
- 13.
-Providing reference list of primary studies included in the analysis &	yes &	Available on Github.
-The Bibtex file `meta-analyses.bib` corresponds to all the articles included in the meta-analyses, `read.bib` corresponds to all the articles (included and excluded) inspected for the meta-analyses.	& ``Availability of code and data'' \\
-  14. Providing the data set used for meta-analysis  &	yes &	A copy of the complete data set is available on Github.	& ``Availability of code and data'' \\
+See FigA4b and FigA6.\\
+  8.& Testing for publication bias &	yes	& We used several methods (i.e.
+funnel plots, the ``trim and fill'' method and the Rosenberg’s fail-safe number).
+See details of methods and results in Appendix D and FigA7\\
+  9.& Sensitivity analysis &	yes &	See details in sub-section "Sensitivity analysis" in material and method. See results in Fig3 and FigA5 \\
+  10.& Exploring temporal changes in effect size &	yes	& See details of methods and results in Appendix D and FigA9.\\
+  11.& Controlling for phylogeny &	no &	It was not possible to control by the phylogeny since the number of species used to measured each coefficient of correlation ranged from 2 to 300 species.\\
+  12.& Specifying the software used &	yes	& See sub-section ``Availability of code and data'' in material and methods\\
+ 13.& Providing reference list of primary studies included in the analysis &	yes &	See sub-section ``Availability of code and data'' in material and methods.
+The Bibtex file `meta-analyses.bib` corresponds to all the articles included in the meta-analyses.
+\\
+  14.& Providing the data set used for meta-analysis  &	yes &	A copy of the complete data set is available on Github.
+See ``Availability of code and data'', section "Statistical analysis" in material and methods.
+\\
    \hline

### 2015-09-03 R/figures.R

@@ -286,38 +286,93 @@ figure_8 <- function(GCi, GIi) {
   grid.arrange(p1,p2,p3,p4,p5,ncol=2, nrow=3,widths=c(1.2,1))
 }
 
-figure_A1 <- function(CompleteData) {
-  s <- CompleteData[order(CompleteData$stage, CompleteData$trait,CompleteData$size.mean.range),] # sort by trait et stage
+figure_A1 <- function(CompleteData_inter) {
+    s <- unique(CompleteData_inter[c("ref","id", "stageRGR","measure.size","size.mean.range","size.min","size.max","growth.form")])
+    s <- s[order(s$measure.size,s$size.max,s$size.min,s$stageRGR),] 
+    s <- na.omit(s)
+  
+  # sort by trait et stage
   s$stageRGR <- factor(s$stageRGR, levels=c("seedling","juvenile","sapling","adult","mix"))
+  s$id <- as.factor(s$id)
   sh <- subset(s,s$measure.size=="height")
   sa <- subset(s,s$measure.size=="age")
   sd <- subset(s,s$measure.size=="diameter")
+  sd <- sd[order(sd$size.min,sd$size.max),] 
+  
+  # p_diam <- 
+  # par(mfcol=c(3,1))
+  layout(matrix(c(1,2,3),3,1,byrow=TRUE), widths=c(3,3,3),heights=c(4.8,2,4.3))
+  # layout.show(3)
+  
+  par(mar=c(4,4,1,1)+0.1)
+  plotCI(x=sort(sa$size.mean.rang), y= 1:length(sa$size.mean.rang), 
+         xlim=c(0,45),ylim=rev(range(1:length(sa$size.mean.rang))),yaxt="n",
+         err="x" ,li=sa$size.min, ui=sa$size.max, 
+         xlab="age (yrs)",ylab="",
+         col=c("green", "blue", "orange",
+               "red", "grey")[sa$stageRGR], pch=".", 
+         cex.axis=0.75, bty="n", gap=0, sfrac=0)
+  axis(2, at=1:length(sa$size.mean.rang), labels=sa$id, las=1, cex.axis=0.4)
+  abline(v = 1, col = "green", lty=2, lwd=2)
+  abline(v = 5, col = "grey", lty=2, lwd=1)
+  # text(x=0, y =(length(sa$size.mean.rang), labels ="(a)")
+  # abline(v = 5, col = "orange", lty=3)
 
-  p_diam <-  plot_stage("c)", xlab= "basal diameter (cm)",ylab="",
[…]

### 2015-09-03 analysis.R

@@ -20,6 +20,7 @@ library(maptools)
 library(maps)
 library(downloader)
 library(metafor)
+library(gplots)
 
 library(bibtex)
 library(RefManageR)

### 2015-09-04 MS.tex
Change in ms
Change in Fig S8 and Fig2 legende in ms

@@
 
-We first developed a snapshot of the literature, to assess potential to recover useufl data from the wide corpus of literature available.
+We first developed a snapshot of the literature, to assess potential to recover useful data from the wide corpus of literature available.
 This snapshot was obtained via Web of Science database (Thomson Reuters), between March and June 2014, using a range of Boolean search terms in English.
@@
 Article IDs correspond to the reference number in our dataset.
-Colours denote stage information given by the authors, while line styles denote growth form.
+Colours denote stage information given by the authors.
 The vertical lines indicate the thresholds used in our analysis.
-Results shown here are the ``complete'' dataset (see methods for details).}
+"*" indicated when a stage reassignment is needed.
+Dots on right side of the graph indicate cases where plants had different growth form.
+Results shown here are the ''complete'' dataset (see methods for details).}
 \label{fig:fig2}
@@
 
-%TODO: I suggest keeping this table, but merging the two right hand columns.
-The text in the explanation column mostly just repeats material that is presented elsewhere, so best to just say briefly where to find it.
 \clearpage
@@
 \vspace{0.5cm}
-\begin{tabular}{p{0.2cm}p{5cm}p{0.8cm}p{9cm}}
+\begin{tabular}{p{0.2cm}p{4cm}p{0.8cm}p{7cm}}
   \hline
@@
 electronic reference data bases that were searched, keywords, language and search dates) in sub-section "Phase 2 - Systematic search" in material and method.\\
-  2.& Reporting inclusion/exclusion criteria & yes & We specified several inclusion criteria in the sub-section "Phase 2 - Systematic search" in material and method.
+  2.& Reporting inclusion or exclusion criteria & yes & We specified several inclusion criteria in the sub-section "Phase 2 - Systematic search" in material and method.
 The Bibtex file `read.bib` on Guithub reports all the articles red but laid out because they failed to met our criteria.\\
@@
 correspond to the stage for which the r values have been recorded: red
-points corresponds adult stage, orange points to saplings, and grey
+points corresponds adult stage, orange points to saplings, and green
 points to juveniles.}

### 2015-09-04 R/figures.R

@@ -25,10 +25,10 @@ figure_allometry <- function() {
     plot(data[[px$var]], data[[py$var]], log="xy",
       xlim = px$lim, ylim = py$lim,
       xlab = px$lab, ylab = py$lab, col=adjustcolor("#00000033", alpha=0.5))
-    abline(v=px$sap, col="green", lty=5)
-    abline(h=py$sap, col="green", lty=5)
-    abline(v=px$adult, col="red", lty=5)
-    abline(h=py$adult, col="red", lty=5)
+    abline(v=px$sap, col="#93EA6D", lty=5)
+    abline(h=py$sap, col="#93EA6D", lty=5)
+    abline(v=px$adult, col="#E6224C", lty=5)
+    abline(h=py$adult, col="#E6224C", lty=5)
   }
 
   filename <- "downloads/baad.rds"
@@ -288,12 +288,15 @@ figure_8 <- function(GCi, GIi) {
 
 figure_A1 <- function(CompleteData_inter) {
 
-    s <- unique(CompleteData_inter[c("ref","id", "stageRGR","measure.size","size.mean.range","size.min","size.max","growth.form")])
-    s <- s[order(s$measure.size,s$size.max,s$size.min,s$stageRGR),]
+    s <- unique(CompleteData_inter[c("ref","id", "stageRGR","measure.size","size.min","size.max","growth.form","stage")])
+    s <- s[order(s$size.max,s$size.min,s$stageRGR),]
     s <- na.omit(s)
 
   # sort by trait et stage
   s$stageRGR <- factor(s$stageRGR, levels=c("seedling","juvenile","sapling","adult","mix"))
+  s$stage <- factor(s$stage, levels=c("seedling","juvenile","sapling","adult","mix"))
+  s$stage <- replace(s$stage, s$stage=="juvenile", "seedling")
+  
   s$id <- as.factor(s$id)
   sh <- subset(s,s$measure.size=="height")
   sa <- subset(s,s$measure.size=="age")
@@ -325,36 +328,50 @@ figure_A1 <- function(CompleteData_inter) {
     data$size.max <- rescale( data$size.max, cuts)
 
     data <- data[order(data$size.max, data$size.min),]
+    data["growthf"] <- -0.02
 
     n <- nrow(data)
     y <- rev(seq_len(n))
-    cols <- c("green", "blue", "orange",
-               "red", "grey")[data$stageRGR]
-
[…]

### 2015-09-04 R/plots.R

@@ -6,550 +6,555 @@ mytheme <- theme_bw() + theme(text = element_text(size = 9, colour = "black"),
   panel.background = element_blank(), legend.justification = c(1, 0), legend.position = c(1,0))
 
 my_plot_1 <- function(title, ggobj, xlab = expression(paste("")), ylab = "Number of correlations extracted") {
-  p <- ggobj + geom_bar() + coord_cartesian(ylim = ylim) + coord_flip() + labs(title = title) +
+  p <- ggobj + geom_bar(alpha = 0.9) + coord_cartesian(ylim = ylim) + coord_flip() + labs(title = title) +
     xlab(xlab) + ylab(ylab) + scale_x_discrete() + theme(text = element_text(size = 9),
     axis.text.x = element_text(size = 9, angle = 0, vjust = 1)) + mytheme +
-    theme(axis.title = element_text(size = 10, hjust = 0.5)) + scale_fill_manual(values = c(juvenile = "grey",
-    sapling = "orange", adult = "red"), breaks = c("juvenile", "sapling", "adult"),
+    theme(axis.title = element_text(size = 10, hjust = 0.5)) + scale_fill_manual(values = c(juvenile = "#93EA6D",
+    sapling = "#F57C34", adult = "#E6224C"), breaks = c("juvenile", "sapling", "adult"),
     labels = c("juvenile", "sapling", "adult"))
   p
+ 
 }
-
-coeff.plot.2 <- function(data, data.complete, data.ideal, LRT, PVAL, title = "",
-  significativite = "", round.value, limit.x.min, limit.x.max, limit.x.text,
-  limit.x.n, limit.y.text.l1, limit.y.text.l2, vjust.value, color1, color2) {
-          data.complete["x.coord"] <- limit.x.n
-          
-          data.ideal["x.coord"] <- limit.x.n
-          
-          my_size_effect_plot1 <- function(title, ggobj, xlab = "Effect size + CI (95%) ",
-            ylab = "Stages") {
-            p <- ggobj + labs(title = title) + xlab(xlab) + ylab(ylab) + geom_vline(yintercept = 0,color = "white") + 
-              geom_hline(yintercept = 0, size = 0.3, linetype = "dashed") +
-              scale_x_discrete("stage", limit = c("seedling", "juvenile", "sapling", "adult", "mix")) +
-              coord_flip() + mytheme + theme(legend.position = "none")
-            p }
-
-          dodge <- position_dodge(width = 0.4)
[…]

### 2015-09-04 analysis.R

@@ -30,11 +30,16 @@ for( f in list.files("R", full.names=TRUE)) {
 }
 
 CompileTable <- clean_raw_data()
+
 RawData <- standardise_data(CompileTable)
+
 CompleteData <- build_complete_data(RawData)
 CompleteData_inter <- Build_intersp_complete_data (RawData)
+
 IdealData_inter  <- build_ideal_data(CompleteData)
+
 CoordTable <- build_map_data(RawData)
+
 IdealData_rgr <- subset(IdealData_inter,IdealData_inter$growth=="RGR")
 IdealData_agr <- subset(IdealData_inter,IdealData_inter$growth=="AbGR")
 ## split datasets by trait - makes a list with named elements

### 2015-09-07 MS.tex
FigS9 updated FigS4 Graph with and without distinction of relative and absolute growth rate are merged

@@
 \includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA4.pdf}
-\end{figure}
-
-\begin{figure}[h!]
-\centering
-\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA4b.pdf}
-\caption{\textbf{Mean coefficient correlation r (+SD) between growth rate and traits, established from 112 articles.} The mean coefficients are weighted by sample size (i.e number of species used to perform the correlation), and calculated both across all plant stages and for each stage.
-Each panel corresponds to a functional trait: \textbf{a)} Specific leaf area (SLA), \textbf{b)} Wood density (WD), \textbf{c)} Net assimilation rate (NARarea), \textbf{d)} Seed mass, \textbf{e)} Asymptotic height (Hmax) and \textbf{f)} Assimilation rate of CO2 (Aarea).
-Results shown here are from the ``unstressed dataset'' (recorded across species and under unstressed conditions).}
+\caption{Mean coefficient correlation r (+SD) between growth and \textbf{a)} Specific leaf area (SLA), \textbf{b)} Wood density (WD), \textbf{c)} Net assimilation rate (NARarea), \textbf{d)} Seed mass, \textbf{e)} Asymptotic height (Hmax) and \textbf{f)} Assimilation rate of CO2 (Aarea).
+On panels B, relative (RGR) and absolute (AbsGR) growth rates are set appart.
+The mean coefficients are weighted by sample size and established from 112 articles and.
+Results shown here are from the ''ideal dataset''.
+''n'' indicate the number of correlation.}
 \label{fig:figA4}
@@
 \includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA8.pdf}
-\caption{\textbf{Growth measurement used by traits and by size.} Results shown here are from the ``complete'' dataset (recorded across species and under both unstressed and stressed conditions).
-The colours correspond to the stage for which the r values have been recorded: red bars corresponds adult stage, orange bars to saplings, and grey bars to juveniles.}
+\caption{\textbf{Growth (absolute vs relative, and measurement) used by traits and by stage.} Results shown here are from the ``complete'' dataset (recorded under both unstressed and stressed conditions).
+On the right side of each graph are the Absolute growth rates (AbsGR), on the left side the relative growth rate (RGR).}
 \label{fig:figA8}

### 2015-09-07 R/figures.R

@@ -6,13 +6,202 @@ to.pdf <- function(expr, filename, ..., verbose=TRUE) {
   eval.parent(substitute(expr))
 }
 
-figure_1 <- function(RawData) {
+figure1 <- function(RawData) {
   p2 <- my_plot_1("",
           ggplot(RawData, aes(x=reorder(factor(trait), factor(trait), function(x) length(x)*1), fill=stage, order=stage)))
   p2
 }
 
-figure_allometry <- function() {
+figure2 <- function(CompleteData_inter) {
+  
+  s <- unique(CompleteData_inter[c("ref","id", "stageRGR","measure.size","size.min","size.max","growth.form","stage")])
+  s <- s[order(s$size.max,s$size.min,s$stageRGR),]
+  s <- na.omit(s)
+  
+  # sort by trait et stage
+  s$stageRGR <- factor(s$stageRGR, levels=c("seedling","juvenile","sapling","adult","mix"))
+  s$stage <- factor(s$stage, levels=c("seedling","juvenile","sapling","adult","mix"))
+  s$stage <- replace(s$stage, s$stage=="juvenile", "seedling")
+  
+  s$id <- as.factor(s$id)
+  sh <- subset(s,s$measure.size=="height")
+  sa <- subset(s,s$measure.size=="age")
+  sd <- subset(s,s$measure.size=="diameter")
+  sd <- sd[order(sd$size.min,sd$size.max),]
+  
+  heights <- c(nrow(sa), nrow(sh), nrow(sd))
+  heights <- heights/sum(heights) +0.1
+  
+  layout(matrix(c(1,2,3),3,1,byrow=TRUE), widths=c(3,3,3),heights= heights)
+  # layout.show(3)
+  par(mar=c(4,4,0,0.5), oma = c(1,2,1,1))
+  
+  plotCI2 <- function(data,  cuts, xlab) {
+    
+    rescale <- function(x, cuts) {
+      x[x > max(cuts)] <- max(cuts)
+      x2 <- x
+      for( i in seq_along(cuts)[-1]) {
+        low <- cuts[i-1]
+        high <- cuts[i]
+        ii <- (low < x & x <= high)
+        x2[ii] <- i-2 + (x[ii] - low)/(high-low)
+      }
+      x2
+    }
+    
[…]

### 2015-09-07 R/model.R

@@ -605,7 +605,7 @@ fun_model_multiple3.1 <- function(x) {
 } 
 
 
-# Weighted correlation
+# Weighted correlation for FigA4
 table_overall.stage <- function(y) {
   name <- list(1:3, c("stage", "corr.r", "SD", "CI"))
   MeanTab <- as.data.frame(matrix(nrow = length(name[[1]]), ncol = length(name[[2]]), 
@@ -619,19 +619,31 @@ table_overall.stage <- function(y) {
   MeanTab$CI <- sapply(split(y, na.omit(y$stage)), function(x) {
     1.96 * (sqrt(wtd.var(x$corr.r, x$nb.sp))/sqrt(length(x)))
   })
+  
+  n <- count(y,"stage")
+
+  MeanTab <-  merge(MeanTab, n, by = "stage")
+  MeanTab$freq <- as.character(MeanTab$freq)
+  
   as.data.frame(MeanTab)
+
 }
 
 table_overall <- function(y) {
-  name <- list(1:1, c("stage", "corr.r", "CI", "SD"))
+  name <- list(1:1, c("stage", "corr.r", "CI", "SD","freq"))
+  y <- y[!is.na(y[, "corr.r"]), ]
   MeanTab <- as.data.frame(matrix(nrow = length(name[[1]]), ncol = length(name[[2]]), 
     dimnames = name))
   MeanTab[, 1] <- "total"
   MeanTab$corr.r <- wtd.mean(y$corr.r, y$nb.sp)
   MeanTab$SD <- sqrt(wtd.var(y$corr.r, y$nb.sp))
   MeanTab$CI <- 1.96 * (sqrt(wtd.var(y$corr.r, y$nb.sp))/sqrt(length(y)))
+  n <- count(y,"stage")
+  MeanTab$freq <- sum(n$freq)
+  MeanTab$freq <- as.character(MeanTab$freq)
   as.data.frame(MeanTab)
-}
+
+  }
 
 
 # Summarise results of the model

### 2015-09-07 R/plots.R

@@ -52,24 +52,24 @@ my_plot_1 <- function(title, ggobj, xlab = expression(paste("")), ylab = "Number
       }
       
       
-      coeff.plot <- function(data, data.complete, data.ideal, LRT, PVAL, title = "",
-                             significativite = "", round.value, limit.x.min, limit.x.max, limit.x.text,
-                             limit.x.n, limit.y.text.l1, limit.y.text.l2, vjust.value, color1, color2) {
-        data.complete["x.coord"] <- limit.x.n
+coeff.plot <- function(data, data.complete, data.ideal, LRT, PVAL, title = "",
+                       significativite = "", round.value, limit.x.min, limit.x.max, limit.x.text,
+                       limit.x.n, limit.y.text.l1, limit.y.text.l2, vjust.value, color1, color2) {
         
+        data.complete["x.coord"] <- limit.x.n
         data.ideal["x.coord"] <- limit.x.n
         
-        my_size_effect_plot1 <- function(title, ggobj, xlab = "Effect size + CI (95%) ",
-                                         ylab = "Stages") {
-          p <- ggobj + labs(title = title) + xlab(xlab) + ylab(ylab) + geom_vline(yintercept = 0,color = "white") + 
-            geom_hline(yintercept = 0, size = 0.3, linetype = "dashed") +
-            scale_x_discrete("stage", limit = c("juvenile", "sapling", "adult")) +
-            coord_flip() + mytheme + theme(legend.position = "none")
-          p }
+        plot1 <- function(title, ggobj, xlab = "Effect size + CI (95%) ", ylab = "Stages") {
+          
+                          p <- ggobj + labs(title = title) + xlab(xlab) + ylab(ylab) + geom_vline(yintercept = 0,color = "white") + 
+                            geom_hline(yintercept = 0, size = 0.3, linetype = "dashed") +
+                            scale_x_discrete("stage", limit = c("juvenile", "sapling", "adult")) +
+                            coord_flip() + mytheme + theme(legend.position = "none")
+                          p }
         
         dodge <- position_dodge(width = 0.4)
         
-        my_size_effect_plot1(title, ggplot(data, aes(stage, Inte, ymin = Inte - 1.96 *SE, ymax = Inte + 1.96 * SE, color = factor(stress)))) +
+        plot1(title, ggplot(data, aes(stage, Inte, ymin = Inte - 1.96 *SE, ymax = Inte + 1.96 * SE, color = factor(stress)))) +
[…]

### 2015-09-07 analysis.R

@@ -69,44 +69,44 @@ dir.create("output", showWarnings =FALSE)
 write.csv(RawData, "output/data.csv", row.names=FALSE)
 
 ## Make output
-pdf("output/Fig1.pdf",height=3, width=4) # ok
-  figure_1(RawData)
+pdf("output/Fig1.pdf",height=3, width=4) 
+  figure1(RawData)
 dev.off()
 
-pdf("output/Fig2.pdf", height=8, width=4) # In the main text, need to be changed
-figure_A1(CompleteData_inter)
-dev.off()
-
-
-pdf("output/Fig3.pdf",height=6,width=5) # ok
-  figure_2(GCi, GIi)
+pdf("output/Fig2.pdf", height=8, width=4) 
+  figure2(CompleteData_inter)
 dev.off()
 
 
-
-pdf("output/FigA1.pdf", height=6, width=6) # ok , maybe need to put only the line address in the text
-figure_allometry()
+pdf("output/Fig3.pdf",height=6,width=5) 
+  figure3(GCi, GIi)
 dev.off()
 
 
-pdf("output/FigA2.pdf", height=3, width=6)# ok
-figure_map(CoordTable)
+## Figure appendix
+pdf("output/FigA1.pdf", height=6, width=6) # allometry
+figureA1()
 dev.off()
 
 
-pdf("output/FigA3.pdf",height=6,width=6) # maybe in the main text
-figure_A4(GCi)
+pdf("output/FigA2.pdf", height=3, width=6) #map
+figureA2(CoordTable)
 dev.off()
 
 
-
-pdf("output/FigA4.pdf",height=6,width=5) # need to be change, both graph on the same page
-figure_A5(GIi)
+pdf("output/FigA3.pdf",height=6,width=6) 
+figureA3(GCi)
 dev.off()
 
-pdf("output/FigA4b.pdf",height=6,width=5) 
-figure_A5b(GIrgr, GIagr)
+pdf("output/FigA4.pdf",height=7,width=5) # need to be change, both graph on the same page
+figureA4(GIi, GIrgr,GIagr)
 dev.off()
+
+# pdf("output/FigA4b.pdf",height=6,width=5) 
[…]

### 2015-09-07 R/appendix4.R
new file: appendix4, corresponds to analyses done in appendix4. Not run with the analysis.R file

@@ -1,0 +1,44 @@
+# 
+# fun_Heterogeneity.CI(GIi[["SLA"]])
+# fun_Heterogeneity.H(GIi[["SLA"]], mods=~stage +year)
+# fun_Heterogeneity.H(GIi[["SLA"]], mods=~stage )
+# 
+# 
+# fun_Heterogeneity.CI(GIi[["WD"]])
+# fun_Heterogeneity.H(GIi[["WD"]], mods=~stage +year)
+# fun_Heterogeneity.H(GIi[["WD"]], mods=~stage )
+# 
+# 
+# fun_Heterogeneity.CI(GIi[["Hmax"]])
+# fun_Heterogeneity.H(GIi[["Hmax"]], mods=~stage +year)
+# fun_Heterogeneity.H(GIi[["Hmax"]], mods=~stage )
+# 
+# 
+# fun_Heterogeneity.CI(GIi[["Seedmass"]])
+# fun_Heterogeneity.H(GIi[["Seedmass"]], mods=~stage +year)
+# fun_Heterogeneity.H(GIi[["Seedmass"]], mods=~stage )
+# 
+# 
+# fun_Heterogeneity.CI(GIi[["Aarea"]])
+# fun_Heterogeneity.H(GIi[["Aarea"]], mods=~stage +year)
+# fun_Heterogeneity.H(GIi[["Aarea"]], mods=~stage )
+# 
+# 
+# fun_trim.and.fill_number(GIi[["SLA"]])
+# fun_trim.and.fill_number(GIi[["WD"]])
+# fun_trim.and.fill_number(GIi[["Hmax"]])
+# fun_trim.and.fill_number(GIi[["Seedmass"]])
+# fun_trim.and.fill_number(GIi[["Aarea"]])
+# 
+# 
+# fsn(data=GIi[["SLA"]], corr.z, vi=vr.z, sei= se.z, type="Rosenberg") 
+# fsn(data=GIi[["WD"]], corr.z, vi=vr.z, sei= se.z, type="Rosenberg") 
+# fsn(data=GIi[["Hmax"]], corr.z,vi=vr.z, sei= se.z, type="Rosenberg") 
+# fsn(data=GIi[["Seedmass"]], corr.z, vi=vr.z, sei= se.z, type="Rosenberg") 
+# fsn(data=GIi[["Aarea"]], corr.z, vi=vr.z, sei= se.z, type="Rosenberg") 
+# 
[…]

### 2015-09-07 MS.tex
Clean code: change name fig

@@
 \includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA1.pdf}
-\caption{Allometric relationships between a) age and diameter (m), b) age and height (m), and c) diameter and height in trees according to the BAAD database.
-Green and red lines are the cutoffs between stage categories used in the literature.
+\caption{\textbf{Allometric relationships between a) age and diameter (m), b) age and height (m), and c) diameter and height in trees according to the BAAD database.} Green and red lines are the cutoffs between stage categories used in the literature.
 Green lines corresponds to limits between juveniles and saplings, red lines to limits between saplings and adults.}
@@
 \includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA2.pdf}
-\caption{Geographical distribution of site locations from studies performed in the field used in the meta-analysis. Results shown here are from the ``complete'' dataset (see methods for details).}
+\caption{\textbf{Geographical distribution of site locations from studies performed in the field used in the meta-analysis}.
+Results shown here are from the ``complete'' dataset (see methods for details).}
 \label{fig:figA2}
@@
 \includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA3.pdf}
-\caption{Range of correlations (r) between
-growth and trait reported in the literature (112 articles). Plots shown the coefficients of correlation (r)
+\caption{\textbf{Range of correlations (r) between
+growth and trait reported in the literature (112 articles)}. Plots shown the coefficients of correlation (r)
 between the plant growth and \textbf{a)} Specific leaf area (SLA, n =
@@
 articles. The x abcissa represents the articles ID sorted by the average coefficient value r reported.
-Results shown here are from the ``complete'' dataset (recorded both across and within species
-and under unstressed and stressed conditions). Each bubble represents a r value, the diameter of the bubble
-is proportional to its weights in the meta-analysis (i.e. number of species used). The colors
-correspond to the stage for which the r values have been recorded: red
+Results shown here are from the ``complete'' dataset (see methods for details).
+Each bubble represents a r value, the diameter of the bubble is proportional to its weights in the meta-analysis (i.e.
+number of species used).
+The colors correspond to the stage for which the r values have been recorded: red
 points corresponds adult stage, orange points to saplings, and green
@@
 \includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA4.pdf}
-\caption{Mean coefficient correlation r (+SD) between growth and \textbf{a)} Specific leaf area (SLA), \textbf{b)} Wood density (WD), \textbf{c)} Net assimilation rate (NARarea), \textbf{d)} Seed mass, \textbf{e)} Asymptotic height (Hmax) and \textbf{f)} Assimilation rate of CO2 (Aarea).
+\caption{\textbf{Mean coefficient correlation r (+SD) between growth and traits.} \textbf{a)} Specific leaf area (SLA), \textbf{b)} Wood density (WD), \textbf{c)} Net assimilation rate (NARarea), \textbf{d)} Seed mass, \textbf{e)} Asymptotic height (Hmax) and \textbf{f)} Assimilation rate of CO2 (Aarea).
 On panels B, relative (RGR) and absolute (AbsGR) growth rates are set appart.
 The mean coefficients are weighted by sample size and established from 112 articles and.
-Results shown here are from the ''ideal dataset''.
+Results shown here are from the ''ideal dataset'' (see methods for details).
 ''n'' indicate the number of correlation.}
@@
 \includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA5.pdf}
-\caption{\textbf{Effect size (+ 95\%CI) of plant stage on the correlations between growth rate and five functional traits across species, with a data set averaging multiple comparisons by trait and by study.} Effects size are calculated from a reduced dataset; in the case of multiple comparisons within a study, we calculated the mean correlation coefficient by trait and by study.
-a) Specific leaf area (SLA), b) Wood density (WD), c) Net assimilation rate (NARarea), d) Seed mass, e) Asymptotic height (Hmax) and f) Assimilation rate of CO2 (Aarea).
+\caption{\textbf{Effect size (+ 95\%CI) of plant stage on the correlations between growth rate and five functional traits across species, with a data set averaging multiple comparisons by trait and by study}.
+Effects size are calculated from a reduced dataset; in the case of multiple comparisons within a study, we calculated the mean correlation coefficient by trait and by study.
+\textbf{a)} Specific leaf area (SLA), \textbf{b)} Wood density (WD), \textbf{c)} Net assimilation rate (NARarea), \textbf{d)} Seed mass, \textbf{e)} Asymptotic height (Hmax) and \textbf{f)} Assimilation rate of CO2 (Aarea).
 Effect size is a standardized measure of the magnitude of the relationship between a particular stage and the correlation coefficient z (Fisher's z-transformed).
@@
 LRT: likelihood Ratio Test compared the fit between null model and stage model, both models are fitted by Maximum Likelihood.
-Black point: ideal data (under unstressed conditions), grey points: all the data.
-``n'' indicate the number of independent comparisons for each effect.}
+Black point: ideal data , grey points: all the data (see methods for details).
+''n'' indicate the number of independent comparisons for each effect.}
 \label{fig:figA5}
@@
 Smallest is the AIC better is the model.
-Results shown here are from ``ideal'' dataset (recorded at interspecific and under unstressed condition) and ``complete'' dataset (recorded at both interspecific and intraspecific level and under unstressed and stressed conditions).}
+Results shown here are from ``ideal'' dataset (see methods for details).}
 \label{fig:figA6}
@@
 \includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA7.pdf}
-\caption{\textbf{Funnel plots with filled in data based on the trim and fill method, showing transformed correlation coefficient z between growth and the traits a) Specific leaf area (SLA), b) Wood density (WD), c) Asymptotic height (Hmax), d) Seed mass (SM) and e) Assimilation rate of CO2 (Aarea)}.
-Results shown here are from the ``ideal'' dataset (recorded across species and under unstressed conditions).
+\caption{\textbf{Funnel plots with filled in data based on the trim and fill method}, showing transformed correlation coefficient z between growth and \textbf{a)} Specific leaf area (SLA), \textbf{b)} Wood density (WD), \textbf{c)} Net assimilation rate (NARarea), \textbf{d)} Seed mass, \textbf{e)} Asymptotic height (Hmax) and \textbf{f)} Assimilation rate of CO2 (Aarea).
+Results shown here are from the ''ideal'' dataset (see material and methode for details).
 Note that in these plots the y axis is the 1/number of species included in the correlation, not the replication for the correlation.
@@
 The open points correspond to the estimated missing studies.
-The number of missing values is 9 for SLA,1 for WD, 0 for Hmax, 6 for SM and 0 for Aarea}
+The number of missing values is 9 for SLA,1 for WD, 0 for Hmax, 6 for SM and 0 for Aarea.}
 \label{fig:figA7}
@@
 \includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA8.pdf}
-\caption{\textbf{Growth (absolute vs relative, and measurement) used by traits and by stage.} Results shown here are from the ``complete'' dataset (recorded under both unstressed and stressed conditions).
-On the right side of each graph are the Absolute growth rates (AbsGR), on the left side the relative growth rate (RGR).}
+\caption{\textbf{Growth (absolute vs relative, and measurement) used by traits and by stage.} \textbf{a)} Specific leaf area (SLA), \textbf{b)} Wood density (WD), \textbf{c)} Net assimilation rate (NARarea), \textbf{d)} Seed mass, \textbf{e)} Asymptotic height (Hmax) and \textbf{f)} Assimilation rate of CO2 (Aarea).
+On the right side of each graph are the absolute growth rates (AbsGR), on the left side the relative growth rate (RGR).
+Results shown here are from the ``complete'' dataset (see methods for details).
+}
 \label{fig:figA8}
@@
 \includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA9.pdf}
-\caption{\textbf{Temporal changes in coefficient of correlation between traits and growth.
-a) Specific leaf area (SLA), b) Wood density (WD), c) Asymptotic height (Hmax), d) Seed mass (SM) and e) Assimilation rate of CO2 (Aarea)} Results shown here are from the ``ideal'' dataset (recorded across species and under  unstressed conditions).
+\caption{\textbf{Temporal changes in coefficient of correlation between growth and traits}.
+\textbf{a)} Specific leaf area (SLA), \textbf{b)} Wood density (WD), \textbf{c)} Net assimilation rate (NARarea), \textbf{d)} Seed mass, \textbf{e)} Asymptotic height (Hmax) and \textbf{f)} Assimilation rate of CO2 (Aarea).
+Results shown here are from the ``ideal'' dataset (see methods for details).
 The colours correspond to the stage for which the r values have been recorded: red points corresponds adult stage, orange points to saplings, and grey points to juveniles.}

### 2015-09-07 R/figures.R

@@ -6,13 +6,14 @@ to.pdf <- function(expr, filename, ..., verbose=TRUE) {
   eval.parent(substitute(expr))
 }
 
-figure1 <- function(RawData) {
+## Figure main text
+figure_1 <- function(RawData) {
   p2 <- my_plot_1("",
           ggplot(RawData, aes(x=reorder(factor(trait), factor(trait), function(x) length(x)*1), fill=stage, order=stage)))
   p2
 }
 
-figure2 <- function(CompleteData_inter) {
+figure_2 <- function(CompleteData_inter) {
   
   s <- unique(CompleteData_inter[c("ref","id", "stageRGR","measure.size","size.min","size.max","growth.form","stage")])
   s <- s[order(s$size.max,s$size.min,s$stageRGR),]
@@ -99,7 +100,7 @@ figure2 <- function(CompleteData_inter) {
   
 }
 
-figure3 <- function(GC, GI) {
+figure_3 <- function(GC, GI) {
   CoefModel.SLA<-fun_model(GI[["SLA"]],GC[["SLA"]])
   CoefModel.SLA["trait"] <- "SLA"
   CoefModel.SLA.s <- subset(CoefModel.SLA,stress=='complete')
@@ -199,9 +200,9 @@ figure3 <- function(GC, GI) {
   grid.arrange(p1,p2,p3,p4,p5,ncol=2, nrow=3,widths=c(1.2,1))
 }
 
-##Figure appendix
 
-figureA1 <- function() {
+##Figure appendix
+figure_A1 <- function() {
 
   download_baad <- function(destination_filename) {
     url <-
@@ -257,7 +258,7 @@ figureA1 <- function() {
   single_plot(pars[["dia"]], pars[["ht"]], data)
 }
 
-figureA2 <- function(CoordTable) {
+figure_A2 <- function(CoordTable) {
   mapWorld <- borders("world", colour="#FFCC33", fill="#FFCC33",lty=0) # create a layer of borders
   mp <- ggplot() + mapWorld + theme(text=element_text(size = 9, colour = "black"),
                                       title=element_text(size=9),
@@ -270,7 +271,7 @@ figureA2 <- function(CoordTable) {
   coordinate.map
 }
 
[…]

### 2015-09-07 analysis.R

@@ -70,82 +70,61 @@ write.csv(RawData, "output/data.csv", row.names=FALSE)
 
 ## Make output
 pdf("output/Fig1.pdf",height=3, width=4) 
-  figure1(RawData)
+  figure_1(RawData)
 dev.off()
 
 pdf("output/Fig2.pdf", height=8, width=4) 
-  figure2(CompleteData_inter)
+  figure_2(CompleteData_inter)
 dev.off()
 
-
 pdf("output/Fig3.pdf",height=6,width=5) 
-  figure3(GCi, GIi)
+  figure_3(GCi, GIi)
 dev.off()
 
 
 ## Figure appendix
 pdf("output/FigA1.pdf", height=6, width=6) # allometry
-figureA1()
+  figure_A1()
 dev.off()
-
 
 pdf("output/FigA2.pdf", height=3, width=6) #map
-figureA2(CoordTable)
+  figure_A2(CoordTable)
 dev.off()
-
 
 pdf("output/FigA3.pdf",height=6,width=6) 
-figureA3(GCi)
+  figure_A3(GCi)
 dev.off()
 
-pdf("output/FigA4.pdf",height=7,width=5) # need to be change, both graph on the same page
-figureA4(GIi, GIrgr,GIagr)
+pdf("output/FigA4.pdf",height=7,width=5) 
+  figure_A4(GIi, GIrgr,GIagr)
 dev.off()
 
-# pdf("output/FigA4b.pdf",height=6,width=5) 
-# figure_A5b(GIrgr, GIagr)
-# dev.off()
-
-
-# pdf("output/FigA6.pdf",height=6,width=5)
-#   figure_A6(GCi)
-# dev.off()
-
-
-pdf("output/FigA5.pdf",  height=6, width=5) # ok, independance of the data (restricted dataset)
-  figure_A7(RIi, RCi)
+pdf("output/FigA5.pdf",  height=6, width=5) 
+  figure_A5(RIi, RCi)
 dev.off()
-
-
-# pdf("output/FigA8.pdf")  # coefficient plot with only the stage from the authors
-#  figure_8(GCi, GIi)
-# dev.off()
-# # 
 
 pdf("output/FigA6a.pdf")
-figure_A8(GCi, "SLA","WD", c("a","b"))
+  figure_A6(GCi, "SLA","WD", c("a","b"))
 dev.off()
 
[…]

### 2015-09-11 MS.tex
Editing changes

@@
 \affiliation{Biological Sciences, Macquarie University NSW 2109, Australia\\
-\textasteriskcentered Email for correspondence: \texttt{ anais.gibert@gmail.com}\\
+\textasteriskcentered Email for correspondence: \texttt{anais.gibert@gmail.com}\\
 Word count: ~XXXX words}
@@
 \item Traits should influence growth in a way that depend on individual plants size.
-We outline mechanisms and hypotheses based on new theory, and test these predictions in tree species for five traits using a meta-analysis of 112 studies ($>$ 500 correlations).
+We outline mechanisms and hypotheses based on new theory, and test these predictions in tree species for five traits (specific leaf area, wood density, maximum height, seed mass and assimilation rate) using a meta-analysis of 112 studies ($>$ 500 correlations).
 As a first approximation of plants size, we analysed the shift in the correlations between growth and traits across three plant stages (i.e.
@@
 It has been widely expected that species with low tissue construction cost will typically have fast growth rates, at least in favourable physical environments \citep[e.g.][]{MullerLandau:2004dc,Wright:2004jb,Poorter:2008iu,Chave:2009iy,Larjavaara:2010bn,Iida:2012jb,Paine:2015df}.
-Yet, a growing number of empirical studies indicate the correlation between traits and growth is not as consistent as that.
+Yet, a growing number of empirical studies indicates the correlation between traits and growth is not as consistent as that.
 Consider SLA as an illustration.
@@
 \end{enumerate}
-We gathered correlation coefficients between trait and growth from studies that gave explicit information about the size or stage of the plants.
+We gathered correlation coefficients between traits and growth from studies that gave explicit information about the size or stage of the plants.
 While most studies on traits have not been concerned with effects of plant size, they have generally reported trait-growth correlations for identifiable stage classes.
@@
 
-Low WD decreases the cost of building stem tissue and thus the cost of deploying additional leaf area (Table \ref{tab:trade-offs}), which should result in faster growth.
-Although cheaper wood carries a risk of increased mortality, this cost is not reflected in growth outcomes.
-Thus decreasing WD is predicted to increase growth across the entire size range.
+High WD increases the cost of building stem tissue and thus the cost of deploying additional leaf area (Table \ref{tab:trade-offs}), which should result in slower growth.
+Although expensive wood decreases the risk of mortality, this benefit is not reflected in growth outcomes.
+Thus increasing WD is predicted to decrease growth across the entire size range.
 
@@
 Tree growth in diameter, height or mass can be expressed in either absolute (AGR) or relative terms (RGR).
-According to the growth model, the predicted relationship between growth and either SLA or SM in seedlings revert if absolute AGR$_\textrm{mass}$ is used instead of RGR$_\textrm{mass}$ (see Appendix \ref{sec:growth}).
+According to the growth model, the predicted relationship between growth and either SLA or SM in seedlings reverts if absolute AGR$_\textrm{mass}$ is used instead of RGR$_\textrm{mass}$ (see Appendix \ref{sec:growth}).
 For SLA, the correlation with RGR$_\textrm{mass}$ is positive but becomes negative with AGR$_\textrm{mass}$.
@@
 
-We aimed to identify studies that measured the correlation between five prominent functional trait (SLA, WD, Aarea, Hmax and SM) and a growth measurement across species.
+We aimed to identify studies that measured the correlation between five prominent functional traits (SLA, WD, Aarea, Hmax and SM) and a growth measurement across species.
 Our literature search was conducted in two phases.
@@
 
-While Web of Science guarantees a relatively stable and reproducible search environment, with clearly defined lists of indexed journals, its searches are restricted to meta-data, such as title, keywords and abstracts \citep{Beckmann:2012hn}.
-This limitation does not apply to Google Scholar, where, theoretically, all text that is electronically available on the Internet will be indexed.
+While Web of Science guarantees a relatively stable and reproducible search environment, with clearly defined lists of indexed journals, its searches are limited to meta-data (i.e.
+title, keywords and abstracts, \citealt{Beckmann:2012hn}).
+This limitation does not apply to Google Scholar, where all text that is electronically available on the Internet will be indexed.
 Thus, we used Google Scholar to perform a more systematic search of the literature for SLA and WD.
@@
 
-Overall, we recorded coefficient correlations for a list of 20 traits (Fig.
-\ref{fig:fig1}): the five for which we had prior expectations, plus 15 others commonly used in the trait literature.
+Overall, we recorded coefficient correlations for a list of 19 traits (Fig.
+\ref{fig:fig1}): the five for which we had prior expectations, plus 14 others commonly used in the trait literature.
 SLA, leaf area, leaf nitrogen and phosphorus concentration, net (mass) assimilation rates (NAR), and Aarea are traits involved in species leaf economic strategy \citep{Wright:2004jb,Wright:2010tp}.
@@
 WD and sapwood area per leaf area (SA/LA), vessel size and density, and stem specific conductance are all involved in species wood economic strategy  \citep{Chave:2009iy}.
-Here WD and SA/LA are also considered as indicators of stem construction cost (\citep{Falster:2011ii}, whereas SLA and leaf thickness capture crucial information about leaf construction cost \citep{Wright:2004jb}.
+Here WD and SA/LA are also considered as indicators of stem construction cost \citep{Falster:2011ii}, whereas SLA and leaf thickness capture crucial information about leaf construction cost \citep{Wright:2004jb}.
 Finally, the leaf area ratio and leaf mass ratio are indicators of resource allocation to leaf \citep{Lambers:1992bj}.
-According to the snapshot of the literature on Web of Science, 62\% of the literature for these 20 traits were captured by a search on SLA and WD.
+According to the snapshot of the literature on Web of Science, 62\% of the literature for these 19 traits were captured by a search on SLA and WD.
 
@@
 Thus we adopted the above values as cut-offs for defining stage boundaries.
-However, the groups ``juvenile'' and ``sapling'' were largely overlapping, causing us to merge these two.
+However, the group ``juvenile'' was largely overlapping with the three others, causing us to merge this category with one of the other on a case by case basis for each study.
 
@@
 We preferred the term ``juvenile'' to ``seedling'', because for a portion of the scientific community ``seedling'' also refers to a particular experimental condition.
-Using the above cut-offs we were also able to assign a stage category to studies for which no stage have been distinctly mentioned by the authors (5\% of the data, noted as ``mix'' in Fig.
+Using the above cut-offs we were also able to assign a stage category to studies for which no stage have been distinctly mentioned by the authors (5\% of the articles, noted as ``mix'' in Fig.
 \ref{fig:fig2}).
-Only 5 of 112 studies were ambiguous on their plant stage attribution.
+Only 7 of 112 articles were ambiguous on their plant stage attribution.
 Half of these equivocal cases involved the juvenile category.
 We attributed a study to a new stage category only when 95\% of the recorded range of sizes for that study lay within a new stage category.
-The others equivocal cases were caused by an ambiguity in the definition of ``adult'' used by the authors.
-Some plants with a large stature are not assessed as adult by the authors because they are still non reproductive (see ID 150).
+Others equivocal cases were caused by an ambiguity in the definition of ``adult'' used by the authors.
+Some plants with a large stature are not assessed as adult by the authors because they are still non reproductive \citep{King:2006dg,King:2006he}.
+Whereas plants with a small stature -because stunnded by frequent wind for example \citep{Stratton:2001ck}- are assessed as adult because they are reproductive.
 Here, we attributed a study to the adult stage when the authors identified the plants as reproductive, and to sapling stage when they identified the plants as non-reproductive, regardless the plant size or age.
 Results using the categories established by the authors are similar than the one using the standardized categories and are available in Fig.
-\ref{fig:figA5} model.1.
+\ref{fig:figA6} model.1.
 In the main text, we report only results using the standardized categories.
@@
 
-We tested how robust are our results were to the particular decisions made in the analysis, in the criteria used for including a study in the analysis.
-The number of species used to perform the correlation, the experimental conditions, and the concordance between stage used to measure trait and growth are clear criteria for assessing the quality of the data for addressing our hypotheses.
+We tested how robust our results were to the particular decisions made in the analysis.
+In partiuclar, we tested the sensitivity of our results to inclusion of studies that measured a large number of responses for the same trait.
+The idea is to check that our results are not generated by the dominance of one or few studies reporting several values for the same trait.
+In the case of multiple comparisons within a study, we used the method proposed by \citet{Borenstein:2009um}: we calculated the mean correlation coefficient by trait and by study, and then re-calculated the effect size.
+This produced a reduced dataset, where multiple responses for any given trait were condensed into a study-level average.
+We also tested if the criteria used for including a study in the analysis affect our results.
+In addition of the chosen criteria, the experimental conditions (stress vs unstressed), and the concordance between stage used to measure trait and growth are clear criteria for assessing the quality of the data for addressing our hypotheses.
 Thus we stratified the data set into two subsets: one including only studies under unstressed conditions ('ideal' dataset), and the other set including studies under all conditions ('complete' dataset).
-We excluded from the ``ideal'' dataset studies where growth and traits were measured on plants from different stages, unless a particular stage is by definition required to measure a trait such as for SM (i.e.
+We excluded from the ''ideal'' dataset studies where growth and traits were measured on plants from different stages, unless a particular stage is by definition required to measure a trait such as for SM (i.e.
 seed stage), or Hmax (i.e.
 adult stage).
-We also tested the sensitivity of our results to inclusion of the few studies that measured a large number of responses for the same trait.
-In the case of multiple comparisons within a study, we used the method proposed by \citet{Borenstein:2009um}: we calculated the mean correlation coefficient by trait and by study, and then re-calculated the effect size.
-This produced a reduced dataset, where multiple responses for any given trait were condensed into a study-level average.
 
@@
 \ref{fig:fig3} a and d; average values for the coefficients ($\bar{r}$) in Fig.
-\ref{fig:figA4}).
+\ref{fig:figA4} a-e).
 The correlation between growth and SLA shifted from strongly positive at juvenile stage $\bar{r}=0.6 \pm 0.08$, Mean $\pm$ SD) to not significantly different from zero at adult stage ($\bar{r}= -0.01 \pm 0.07$, CI 95\% overlapping zero in Fig.
 \ref{fig:fig3} a).
-The correlation between growth and SM shifted from negative at juvenile stage ($\bar{r}= -0.59 \pm 0.07$) to not significantly different from zero at adult stage ($\bar{r}= -0.09 \pm 0.02$, , CI 95\% overlapping zero in Fig.
+The correlation between growth and SM shifted from negative at juvenile stage ($\bar{r}= -0.5 \pm 0.07$) to not significantly different from zero at adult stage ($\bar{r}= -0.09 \pm 0.02$, , CI 95\% overlapping zero in Fig.
 \ref{fig:fig3} d).
 For both traits, correlation coefficients recorded at sapling stage were intermediate between juvenile and adult stages.
+The relationship between growth and either SLA or SM in seedlings is expected to differ if absolute GR in mass is used instead of RGR mass.
+Here, for both traits growth in mass was exclusively expressed in relative terms for seedlings(results shown in the Fig.
+\ref{fig:figA8} and Fig \ref{fig:figA4} f-j)
 
@@
 For Hmax, the expectation was for a correlation with growth to be absent for small plants but present at intermediate and larger sizes, the mechanism being increased relative allocation to reproduction as Hmax is approached.
-Indeed Hmax was positively correlated with growth at adult stage ($\bar{r}= 0.38 \pm 0.05$, $n=18$).
+Indeed Hmax was positively correlated with growth at adult stage ($\bar{r}= 0.38 \pm 0.05$).
 At sapling and juvenile stages, the correlation between Hmax and growth was not significantly different from that observed at adult stage (model fit not improved when stage was incorporated, see log likelihood ratio tests in Fig.
@@
 The growth form, the experiment types and the growth measurement were not markedly best predictors of the data (results shown in the Fig.
-\ref{fig:figA5}).
+\ref{fig:figA6}).
 
@@
 For instance, the correlation between growth and WD at juvenile stage shifted from negative to non significant (i.e CI 95\% included zero) due to 2 positive correlation coefficients from \citet{Augspurger:1984ct};  these correlations unlike others used values of WD from adult plants together with growth from juveniles.
-For Aarea, the comparison between complete and ideal data showed no signal of an effect of stress (here mainly low light) on the correlation with growth at seedling stage; the correlation was still positive between Aarea and growth even when 7 correlations measured under low light conditions were added.
+For Aarea, the comparison between complete and ideal data showed no signal of an effect of stress (here mainly low light) on the correlation with growth at seedling stage; the correlation was still positive between Aarea and growth even when 8 correlations measured under low light conditions were added.
 Finally, our results were unlikely to be biased by dominance of one or a few studies that measured a large number of responses, since when multiple responses were condensed into a single average within a trait and within a study, outcomes were very similar (Fig.
@@
 Overall our study met all the quality criteria required for meta-analysis in ecology (Table \ref{tab:meta}).
-We showed that the impact of publication bias is probably trivial in our meta-analyses (Appendix D, Fig.
+We showed that the impact of publication bias is probably trivial in our meta-analyses (Appendix E, Fig.
 \ref{fig:figA7}).
-The extent of the heterogeneity was high in our meta-analysis,  but substantially explained by the plant stage effect for SLA and SM, as expected (Appendix D).
-Finally, there was no indication of a temporal change in the effect size being reported within stages (Appendix D, Fig.
+The extent of the heterogeneity was high in our meta-analysis,  but substantially explained by the plant stage effect for SLA and SM, as expected (Appendix E).
+Finally, there was no indication of a temporal change in the effect size being reported within stages (Appendix E, Fig.
 \ref{fig:figA9}).
@@
 
-%TODO please insert refs below
 The meta-analysis reported here demonstrates that for several key traits the influence of traits on growth rates changes as plants grow from small to large.
-While this point has been made recently in smaller scale studies (refs??), it is the first time that mechanistic hypotheses are confirmed across a large number of studies already available.
+While the possibility has been raised recently that trait-growth correlations may change systematically with size \citep{Falster:2011ii, Ruger:2012jv, Iida:2014ep, Iida:2014hq}, it is the first time that mechanistic hypotheses are corroborated across a large number of studies already available.
 Meta-analysis allowed us to generalize and thus to reach a consensus about the effect of traits on growth.
@@
 This negative relationship arises because seedlings from larger seeds are begin life larger themselves, as has been extensively discussed in the literature \citep[reviewed by][]{Turnbull:2012ew}.
-moreover, the prediction applies only to RGR not to AGR (Appendix Fig.
-\ref{fig:figA8} d).
 
 For WD the meta-analysis showed negative correlation with growth across all plant stages, as previously reported from individual studies \citep{Wright:2010tp,Ruger:2012jv}.
-It should be noted however that there are few tests of this proposition at seedling stage.
+It should be noted however that there are few data available to test this proposition at seedling stage (n=2-5).
 In our model (Appendix \ref{sec:growth}) cheaper stem construction is responsible for the predicted negative correlation.
@@
 In the growth model (Appendix \ref{sec:growth}), a consistent correlation irrespective of size arises from a direct effect of Aarea on plant growth rate.
-In juvenile stage, where most of the data were, we noted no signal of an effect of low light on the positive correlation between Aarea and growth rate.
+Meta-analyses showed a positive correlation for adult and juvenile but not for saplings (n=2) In juvenile stage, where most of the data were, we noted no signal of an effect of low light on the positive correlation between Aarea and growth rate.
 
@@
 Note that in \citet{Iida:2014hq}, the shift in the correlation between growth and WD occurred for trees larger than 22-26 cm dbh.
-This points to one of the possible limitations in our meta-analysis, where trees with height above 5 m were pooled as ``adult''.
+This points to one of the possible limitations in our meta-analysis, where trees with diameter above 10 cm were pooled as ``adult''.
 
@@
 Charles Warren and Jordi Martìnez-Vilalta kindly provided additional information about their published results.
-This work was funded by the Australian Research Council through a fellowship to Westoby and a discovery grant to Falster.
+This work was funded by the Australian Research Council through a fellowship to MW and a discovery grant to DF.
 
@@
 \includegraphics[width=15cm,height=20cm,keepaspectratio]{output/Fig1.pdf}
-\caption{Number of recorded correlations between trait and growth rate in our dataset, byt size and trait.
-Results shown here are for the ``complete'' dataset (recorded both across and within species, under unstressed and stressed conditions).
-Traits are: Aarea (or Amass) = rate of CO$_{2}$ assimilation per unit leaf area (or leaf mass) = maximum photosynthetic rate, Hmax = asymptotic maximum height,  Ks = stem hydraulic conductance, LA = leaf area, LMR = leaf mass ratio, NARarea (or NARmass) = net mass assimilation rate per unit of leaf area (or leaf mass), Nmass (or Narea) = nitrogen content per unit of leaf mass (or leaf area), Pmass = phosphorus content per unit of leaf mass, SA/LA = sapwood area per leaf area, SLA = specific leaf area, thickness = leaf thickness, Vessel size = stem conduit size, vessel density = stem conduit density, WD = wood density.}
+\caption{Number of recorded correlations between trait and growth rate in our dataset, by size and trait.
+Traits are: Aarea (or Amass) = rate of CO$_{2}$ assimilation per unit leaf area (or leaf mass) = maximum photosynthetic rate, Hmax = asymptotic maximum height,  Ks = stem hydraulic conductance, LA = leaf area, LMR = leaf mass ratio, NARarea = net mass assimilation rate per unit of leaf area, Nmass (or Narea) = nitrogen content per unit of leaf mass (or leaf area), Pmass = phosphorus content per unit of leaf mass, SA/LA = sapwood area per leaf area, SLA = specific leaf area, thickness = leaf thickness, Vessel size = stem conduit size, vessel density = stem conduit density, WD = wood density.
+Results shown here are the ``complete'' dataset (see methods for details).}
 \label{fig:fig1}
@@
 \textbf{a)} age, \textbf{b)} height and \textbf{c)} diameter.
-Line segments indicate the size range (max., min.) for the plants used to measure growth.
-Article IDs correspond to the reference number in our dataset.
+Horizontal line segments indicate the size range (max., min.) for the plants used to measure growth.
+Study IDs correspond to the reference number in our dataset.
 Colours denote stage information given by the authors.
-The vertical lines indicate the thresholds used in our analysis.
+The solid vertical lines indicate the thresholds used in our analysis.
 "*" indicated when a stage reassignment is needed.
-Dots on right side of the graph indicate cases where plants had different growth form.
+Dots on left side of the graph indicate cases where plants had different growth form.
 Results shown here are the ''complete'' dataset (see methods for details).}
@@
 Effects are significant if confidence intervals (95\%CI) for a given stage do not overlap with zero.
-Results shown are from both the ``complete'' (black)  and ``ideal'' (grey) datasets.
 Trait names as in Fig.
@@
 A significant p-value means the model including stage effect fitted the data better than the null model.
-}
+Results shown are from both the ``complete'' (black)  and ``ideal'' (grey) datasets (see methods for details).}
 \label{fig:fig3}
@@
 \vspace{1cm}
-  \begin{tabular}{cccc}
-   & Leaf deployment per mass & Allocation to vegetative growth & Net live biomass production \\
-   Trait
-    & ($\frac{\textrm{d}a_\textrm{l}}{\textrm{d}m_\textrm{t}}$)
-    & ($\frac{\textrm{d}m_\textrm{t}}{\textrm{d}b}$)
-    & ($\frac{\textrm{d}b}{\textrm{d}t}$) \\ \hline
-  SLA &$\nearrow$ &$\_$ & $\searrow$  \\
-  WD & $\searrow$ &$\_$  &$\_$ \\
-  Hmax &$\_$ &$\nearrow$ &$\_$ \\
-  SM &$\_$&$\_$&$\_$ \\
-  Aarea &$\_$ &$\_$ & $\nearrow$ \\
+  \begin{tabular}{llccccccc}
+  & & & & SLA & WD & Hmax & SM & Aarea \\ \hline
+  \multicolumn{3}{ l } {Main element of growth} & & & & & \\ 
+  & \multicolumn{2}{ l } {Leaf deployment per mass}  & $\frac{\textrm{d}a_\textrm{l}}{\textrm{d}m_\textrm{t}}$ & $\uparrow$ & $\downarrow$ & - & - & - \\
+  & \multicolumn{2}{ l } {Net live biomass production} & $\frac{\textrm{d}b}{\textrm{d}t}$ & & & & & \\
+  & &    photosynthesis & & - & - & - & - & $\uparrow$  \\
+  & &     respiration   & & - & - & - & - & -  \\
+  & &     leaf turnover & & $\uparrow$ & - & - & - & - \\
+  & \multicolumn{2}{ c } {Allocation to vegetative growth} & $\frac{\textrm{d}m_\textrm{t}}{\textrm{d}b}$ & - & - & $\uparrow$ & - & - \\ 
+  & & & & & & \\
+    \multicolumn{3}{ l } {Relative growth rate in mass} & & $\uparrow$ or $\downarrow$ & $\downarrow$ & - or $\uparrow$ & $\downarrow$ or - & $\uparrow$\\
 \hline
@@
 See details in sub-section "Stage effect" in material and methods.
-Results are shown in Fig3.\\
- 5.& Quantifying heterogeneity in effect sizes &	yes &	We estimated the extend of the heterogeneity using the statistics $I^{2}$ for each trait. See details of methods and results in Appendix D.\\
+Results are shown in Fig.
+\ref{fig:fig3}.\\
+ 5.& Quantifying heterogeneity in effect sizes &	yes &	We estimated the extend of the heterogeneity using the statistics $I^{2}$ for each trait. See details of methods and results in Appendix E.\\
  6.& Exploring causes of heterogeneity & yes &	We explored the effect of stage, and the year of publication (see points 4 and 10 in this list). \\
@@
 We did not test the multiple variables in a hierarchical fashion, because of the limited size of our dataset.
-See FigA4b and FigA6.\\
+See in Fig.
+\ref{fig:figA4} f-j and in Fig.
+\ref{fig:figA6}.\\
   8.& Testing for publication bias &	yes	& We used several methods (i.e.
 funnel plots, the ``trim and fill'' method and the Rosenberg’s fail-safe number).
-See details of methods and results in Appendix D and FigA7\\
-  9.& Sensitivity analysis &	yes &	See details in sub-section "Sensitivity analysis" in material and method. See results in Fig3 and FigA5 \\
-  10.& Exploring temporal changes in effect size &	yes	& See details of methods and results in Appendix D and FigA9.\\
+See details of methods and results in Appendix E and in Fig.
+\ref{fig:figA7}.\\
+  9.& Sensitivity analysis &	yes &	See details in sub-section "Sensitivity analysis" in material and method. See results in Fig. \ref{fig:fig3} and Fig. \ref{fig:figA5}  \\
+  10.& Exploring temporal changes in effect size &	yes	& See details of methods and results in Appendix E and Fig. \ref{fig:figA9}. \\
   11.& Controlling for phylogeny &	no &	It was not possible to control by the phylogeny since the number of species used to measured each coefficient of correlation ranged from 2 to 300 species.\\
@@
 \centering
-\caption{\textbf{List of the twenty traits targeted}. Abbreviation,
+\caption{\textbf{List of the nineteen traits targeted}. Abbreviation,
 definition and search term used in the meta-analysis}
@@
   Narea & Leaf nitrogen content per area & ``Narea'' OR ``nitrogen per area'' OR ``N/area'' OR ``leaf nitrogen content per area'' OR ``LNCarea'' OR ``leaf nitrogen content" \\
-  NARmass & Net assimilation rate per mass &  ``net assimilation rate per mass'' OR ``rate of dry mass increament per mass'' OR ``NARmass'' OR ``NAR'' \\
   Nmass & Leaf nitrogen content per mass & ``Nmass'' OR ``nitrogen per mass'' OR ``N/mass'' OR ``leaf nitrogen content per mass'' OR ``LNCmass'' OR ``leaf nitrogen content" \\
@@
 \textbf{e)} Rate of CO2 assimilation (Aarea, n = 24) reported from 112
-articles. The x abcissa represents the articles ID sorted by the average coefficient value r reported.
-Results shown here are from the ``complete'' dataset (see methods for details).
+articles.
+The x abcissa represents the articles ID sorted by the average coefficient value r reported.
 Each bubble represents a r value, the diameter of the bubble is proportional to its weights in the meta-analysis (i.e.
 number of species used).
-The colors correspond to the stage for which the r values have been recorded: red
-points corresponds adult stage, orange points to saplings, and green
-points to juveniles.}
+The colors correspond to the stage for which the r values have been recorded: red points corresponds adult stage, orange points to saplings, and green points to juveniles.
+Results shown here are from the ``complete'' dataset (see methods for details).
+}
 \label{fig:figA3}
@@
 \includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA4.pdf}
-\caption{\textbf{Mean coefficient correlation r (+SD) between growth and traits.} \textbf{a)} Specific leaf area (SLA), \textbf{b)} Wood density (WD), \textbf{c)} Net assimilation rate (NARarea), \textbf{d)} Seed mass, \textbf{e)} Asymptotic height (Hmax) and \textbf{f)} Assimilation rate of CO2 (Aarea).
-On panels B, relative (RGR) and absolute (AbsGR) growth rates are set appart.
+\caption{\textbf{Mean coefficient correlation r (+SD) between growth and traits, measured by stage and by stage and growth type.} \textbf{a and f)} Specific leaf area (SLA), \textbf{b snd g)} Wood density (WD), \textbf{c and h)} Asymptotic maximum height (Hmax), \textbf{d and i)} Seed mass (Seedmass) and \textbf{e and j)} Rate of CO2 assimilation (Aarea).
+On graphs e to j, relative (RGR) and absolute (AGR) growth rates are set appart.
 The mean coefficients are weighted by sample size and established from 112 articles and.
 Results shown here are from the ''ideal dataset'' (see methods for details).
-''n'' indicate the number of correlation.}
+''n'' indicates the number of correlation.}
 \label{fig:figA4}
@@
 Effects size are calculated from a reduced dataset; in the case of multiple comparisons within a study, we calculated the mean correlation coefficient by trait and by study.
-\textbf{a)} Specific leaf area (SLA), \textbf{b)} Wood density (WD), \textbf{c)} Net assimilation rate (NARarea), \textbf{d)} Seed mass, \textbf{e)} Asymptotic height (Hmax) and \textbf{f)} Assimilation rate of CO2 (Aarea).
+\textbf{a)} Specific leaf area (SLA), \textbf{b)} Wood density (WD), \textbf{c)} Net assimilation rate (NARarea), \textbf{d)} Seed mass, \textbf{e)} Asymptotic maximum height (Hmax) and \textbf{f)} Assimilation rate of CO2 (Aarea).
 Effect size is a standardized measure of the magnitude of the relationship between a particular stage and the correlation coefficient z (Fisher's z-transformed).
@@
 Black point: ideal data , grey points: all the data (see methods for details).
-''n'' indicate the number of independent comparisons for each effect.}
+''n'' indicates the number of independent comparisons for each effect.}
 \label{fig:figA5}
@@
 \includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA6c.pdf}
-\caption{\textbf{Effects size on the correlation between growth and traits of plant stage (mod1), vegetation type (mod2), growth measurement (mod3) and experiment type (mod4).} The effect size (z + 95\%CI) is reported for each class, and models are fitted by restricted max likelihood (REML).
-n = number of correlation r reported.
-Abbreviation: across veg = more than 2 vegetation types, boreal\&temp = boreal and temperate deciduous forest, med = Mediterranean,  temp\&med = temperate deciduous and Mediterranean forests, temp = temperate deciduous, temp rain = temperate rain, trop rain = tropical rain, trop seas = tropical seasonal forests, GR = growth rate and RGR = relative growth rate, measured in diameter (D), height (H), mass(M), cross section area (CSA).
+\caption{\textbf{Effects size on the correlation between growth and traits of plant stage (mod1), vegetation type (mod2), growth measurement (mod3) and experiment type (mod4).} \textbf{a)} Specific leaf area (SLA), \textbf{b)} Wood density (WD), \textbf{c)} Net assimilation rate (NARarea), \textbf{d)} Seed mass, \textbf{e)} Asymptotic maximum height (Hmax) and \textbf{f)} Assimilation rate of CO2 (Aarea).
+The effect size (z + 95\%CI) is reported for each class, and models are fitted by restricted max likelihood (REML).
+Abbreviation: across veg = more than 2 vegetation types, boreal\&temp = boreal and temperate deciduous forest, med = Mediterranean,  temp\&med = temperate deciduous and Mediterranean forests, temp = temperate deciduous, temp rain = temperate rain, trop rain = tropical rain, trop seas = tropical seasonal forests, GR = growth rate and RGR = relative growth rate, measured in diameter (D), height (H), mass(M), volume (V) and cross section area (CSA).
 AIC: Akaike information criterion corresponds to the quality of each model, and allow a comparison between models.
 Smallest is the AIC better is the model.
-Results shown here are from ``ideal'' dataset (see methods for details).}
+Results shown here are from ``ideal'' dataset (see methods for details).
+''n'' indicates number of correlation r reported.}
 \label{fig:figA6}
@@
 \includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA7.pdf}
-\caption{\textbf{Funnel plots with filled in data based on the trim and fill method}, showing transformed correlation coefficient z between growth and \textbf{a)} Specific leaf area (SLA), \textbf{b)} Wood density (WD), \textbf{c)} Net assimilation rate (NARarea), \textbf{d)} Seed mass, \textbf{e)} Asymptotic height (Hmax) and \textbf{f)} Assimilation rate of CO2 (Aarea).
-Results shown here are from the ''ideal'' dataset (see material and methode for details).
+\caption{\textbf{Funnel plots with filled in data based on the trim and fill method}, showing transformed correlation coefficient z between growth and \textbf{a)} Specific leaf area (SLA), \textbf{b)} Wood density (WD), \textbf{c)} Net assimilation rate (NARarea), \textbf{d)} Seed mass, \textbf{e)} Asymptotic maximum height (Hmax) and \textbf{f)} Assimilation rate of CO2 (Aarea).
 Note that in these plots the y axis is the 1/number of species included in the correlation, not the replication for the correlation.
-The number of species is sometimes as low as 1, and these are within-species correlations.
-The number of replicates used for the correlation coefficient was often much greater than the number of species.
-Nevertheless, the characteristic shape of funnel plots is observed, with correlations involving few species showing much wider variation even though within-species replication was sometimes high.
 The open points correspond to the estimated missing studies.
-The number of missing values is 9 for SLA,1 for WD, 0 for Hmax, 6 for SM and 0 for Aarea.}
+The number of missing values is 7 for SLA,1 for WD, 0 for Hmax, 6 for SM and 0 for Aarea.
+Results shown here are from the ''ideal'' dataset (see method for details).}
 \label{fig:figA7}
@@
 \includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA8.pdf}
-\caption{\textbf{Growth (absolute vs relative, and measurement) used by traits and by stage.} \textbf{a)} Specific leaf area (SLA), \textbf{b)} Wood density (WD), \textbf{c)} Net assimilation rate (NARarea), \textbf{d)} Seed mass, \textbf{e)} Asymptotic height (Hmax) and \textbf{f)} Assimilation rate of CO2 (Aarea).
-On the right side of each graph are the absolute growth rates (AbsGR), on the left side the relative growth rate (RGR).
+\caption{\textbf{Number of correlation extracted by traits, stage and growth type (absolute vs relative, and measurement).} \textbf{a)} Specific leaf area (SLA), \textbf{b)} Wood density (WD), \textbf{c)} Net assimilation rate (NARarea), \textbf{d)} Seed mass, \textbf{e)} Asymptotic maximum height (Hmax) and \textbf{f)} Assimilation rate of CO2 (Aarea).
+On the right side of each graph are the absolute growth rates (AGR), on the left side the relative growth rate (RGR).
 Results shown here are from the ``complete'' dataset (see methods for details).
@@
 \caption{\textbf{Temporal changes in coefficient of correlation between growth and traits}.
-\textbf{a)} Specific leaf area (SLA), \textbf{b)} Wood density (WD), \textbf{c)} Net assimilation rate (NARarea), \textbf{d)} Seed mass, \textbf{e)} Asymptotic height (Hmax) and \textbf{f)} Assimilation rate of CO2 (Aarea).
-Results shown here are from the ``ideal'' dataset (see methods for details).
-The colours correspond to the stage for which the r values have been recorded: red points corresponds adult stage, orange points to saplings, and grey points to juveniles.}
+\textbf{a)} Specific leaf area (SLA), \textbf{b)} Wood density (WD), \textbf{c)} Net assimilation rate (NARarea), \textbf{d)} Seed mass, \textbf{e)} Asymptotic maximum height (Hmax) and \textbf{f)} Assimilation rate of CO2 (Aarea).
+The colours correspond to the stage for which the r values have been recorded: red points corresponds adult stage, orange points to saplings, and grey points to juveniles.
+Results shown here are from the ``ideal'' dataset (see methods for details).}
 \label{fig:figA9}
@@
 It can be interpreted as a ratio (0\% $<$ $I^{2}$ $<$ 100\%) not affected by the number of studies or the metric of the effect size in the analysis.
-It also has the advantage of being analogous to indices used for regression (where R2 is the proportion of the total variance that can be explained by the covariates) a common statistics in the trait literature.
 
@@
 By contrast, as $I^{2}$ moves away from zero we know that some of the variance is real and can potentially be explained by subgroup analysis or meta-regression.
-No universal rule could cover definition for ‘low, ‘moderate’ or ‘high heterogeneity.
+There is no universal rule to cover definition for ‘low, ‘moderate’ or ‘high heterogeneity.
 \citealt{Higgins:2003hz} suggested some benchmarks for $I^{2}$ based on the survey of meta-analyses of clinical trials.
-They suggested that values on the order of 25\%, 50\% and 75\% might be considered as ``low'', ``moderate'' and ``high'', respectively.
+They suggested that values on the order of 25\%, 50\% and 75\% might be considered as ''low'', ''moderate'' and ''high'', respectively.
 These suggestions are tentative; the interpretation of heterogeneity in a systematic review will depend critically on the size and direction of treatment effects, as well as on considerations of methodological diversity in the studies (see \citealt{Borenstein:2009um}).
-Here, we estimated $I^{2}$ as following equation from \citealt{Higgins:2002iq}., then we calculated how part of the heterogeneity may be due to the influence of moderators (stage and publication year) and finally we asked if the residual heterogeneity is statistically significant.
+Here, we estimated $I^{2}$ as following equation from \citealt{Higgins:2002iq}, then we calculated how part of the heterogeneity may be due to the influence of moderators (stage and publication year) and finally we asked if the residual heterogeneity is statistically significant.
 In R, we used the package metafor (code available on guithub).
@@
 Here, we did not explore the influence of other moderators, since our goal was to test clear hypotheses about the influence of plant size/stage, not to establish the best predictor of the correlation between growth and trait.
-Finally, since between study variation is significant, as indicated by heterogeneity analyses, using the random effect model was more appropriate in our meta-analysis.
+Finally, since between study variation is significant, as indicated by heterogeneity analyses, the use of the random effect model was appropriate in our meta-analysis.
 
@@
 A publication bias toward significant results creates an asymmetric funnel with small studies with non-significant effects missing from the mouth of the funnel on the side opposite to the true effect.
-While funnel plot are recommended to aid interpretation, there is a high risk failing to detect actual publication bias (see (\citealt{Koricheva:2013tz}) by using exclusively a visual assessment.
+While funnel plot are recommended to aid interpretation, there is a high risk failing to detect actual publication bias (see \citealt{Koricheva:2013tz}) by using exclusively a visual assessment.
 In addition, funnel plots are not effective when the number of studies is small ($<30$) such as for Aarea and SM.
-We also used the ``trim and fill'' method to estimate the number of studies missing from our meta-analyse. This method adjusts for funnel plot asymmetry \citep{Duval:2000dg}.
+We also used the ''trim and fill'' method to estimate the number of studies missing from our meta-analyse. This method adjusts for funnel plot asymmetry \citep{Duval:2000dg}.
 Finally, we estimated the number of studies needed to overturn a result, using the Rosenberg’s fail-safe number \citep{Rosenberg:2005hk}.
@@
 The ‘trim and fill’ method detected some missing values in our data.
-The estimated number of missing value ranges from 0 to 9 depending on the trait considered (Fig.
+The estimated number of missing value ranges from 0 to 7 depending on the trait considered (Fig.
 \ref{fig:figA9}).
@@
 \ref{fig:figA9}).
-As a consequence, we used publication year as a moderator in our analyses \citep{Zvereva:2008jm}p across and within stages for all traits.
+As a consequence, we used publication year as a moderator in our analyses \citep{Zvereva:2008jm} across but also within stages for all traits.
 
-\textbf{Results:} There was a change in the effect size with publication year for SLA ($p<0.0001$, estimates: $-0.04 \pm 0.009$ ), SM ($p = 0.011$, estimates: $0.041 \pm 0.016$ ) and Aarea ($p = 0.0102$, estimates: $-0.0453 \pm 0.0176$ ).
+\textbf{Result:} There was a change in the effect size with publication year for SLA ($p<0.0001$, estimates: $-0.04 \pm 0.009$ ), SM ($p = 0.011$, estimates: $0.041 \pm 0.016$ ) and Aarea ($p = 0.0102$, estimates: $-0.0453 \pm 0.0176$ ).
 The Fig.
@@
 The temporal change were confounded with a plant stage effect in our meta-analyse, but they did not jeopardizing the stability of our conclusions.
-The conclusions of a meta-analyses conducted in different year may not differ from the one reported here.
+The conclusions of a meta-analyses conducted in different years may not differ from the one reported here.
 

### 2015-09-11 R/figures.R

@@ -329,22 +329,23 @@ figure_A4 <- function(GIi,GIrgr, GIagr) {
   Seedmass_gr <- table_trait_gr(GIrgr, GIagr,"Seedmass")
   Aarea_gr <- table_trait_gr(GIrgr, GIagr,"Aarea")
   
-  grobA <- grobTree(textGrob("A",x=0.1,  y=0.95, hjust=0,just = "left",gp = gpar(fontsize = 10, col = "black")))
-  grobB<- grobTree(textGrob("B",x=0.1,  y=0.95, hjust=0,just = "left",gp = gpar(fontsize = 10, col = "black")))
+#   grobA <- grobTree(textGrob("A",x=0.1,  y=0.95, hjust=0,just = "left",gp = gpar(fontsize = 10, col = "black")))
+#   grobB<- grobTree(textGrob("B",x=0.1,  y=0.95, hjust=0,just = "left",gp = gpar(fontsize = 10, col = "black")))
+  # + annotation_custom(grobA)
   
-  p1 <- my_plot_overall(SLA, title='a) SLA') + theme(plot.margin=unit(c(0,0,1,0),"mm"),axis.title.x=element_blank())+ annotation_custom(grobA)
-  p2 <- my_plot_overall(WD, title='b) WD') + theme(plot.margin=unit(c(0,0,1,0),"mm"),axis.title.x=element_blank())+ annotation_custom(grobA)
-  p3 <- my_plot_overall(Hmax, title='c) Hmax') + theme(plot.margin=unit(c(0,0,1,0),"mm"),axis.title.x=element_blank())+ annotation_custom(grobA)
-  p4 <- my_plot_overall(Seedmass, title='d) Seed mass') + theme(plot.margin=unit(c(0,0,1,0),"mm"),axis.title.x=element_blank())+ annotation_custom(grobA)
-  p5 <- my_plot_overall(Aarea, title='e) Aarea') + theme (plot.margin=unit(c(0,0,1,0),"mm"))+ annotation_custom(grobA)
+  p1 <- my_plot_overall(SLA, title='a) SLA') + theme(plot.margin=unit(c(0,0,1,0),"mm"),axis.title.x=element_blank())
+  p2 <- my_plot_overall(WD, title='b) WD') + theme(plot.margin=unit(c(0,0,1,0),"mm"),axis.title.x=element_blank())
[…]

### 2015-09-11 R/plots.R

@@ -223,8 +223,8 @@ my_plot_overall_gr <- function(data, title = "") {
                                 geom_errorbar(aes(x = stage, y = corr.r), position = dodge, size = 0.4, width = 0.2) +
                                 scale_y_continuous("Coefficient of correlation r (+SD) ", limits = c(-1, 1)) +
                                 coord_flip()+
-                                geom_text(aes(stage, 0.8, label = paste("(n=",freq, ")"), color = factor(growth), group = "RGR"), size = 2, data = data1,parse = F, position = "identity", vjust = -0.48, hjust = 0) +
-                                geom_text(aes(stage, 0.8, label = paste("(n=", freq, ")"), color = factor(growth), group = "AbsGR"), size = 2, data = data2, parse = F, position = "identity", vjust = +0.48,hjust = 0) +      
+                                geom_text(aes(stage, 0.8, label = paste("(n=",freq, ")"), color = factor(growth), group = "RGR"), size = 2, data = data1,parse = F, position = "identity", vjust = -0.5, hjust = 0) +
+                                geom_text(aes(stage, 0.8, label = paste("(n=", freq, ")"), color = factor(growth), group = "AbsGR"), size = 2, data = data2, parse = F, position = "identity", vjust = +0.5,hjust = 0) +      
                                 scale_colour_manual(values=c("RGR" = "#9E5F3A", "AbsGR"="#F4395B"), breaks=c("RGR", "AbsGR"))+
                                 theme(legend.position = "none")
                               

### 2015-09-11 analysis.R

@@ -95,11 +95,11 @@ pdf("output/FigA3.pdf",height=6,width=6)
   figure_A3(GCi)
 dev.off()
 
-pdf("output/FigA4.pdf",height=7,width=5) 
+pdf("output/FigA4.pdf", height=7,width=5) 
   figure_A4(GIi, GIrgr,GIagr)
 dev.off()
 
-pdf("output/FigA5.pdf",  height=6, width=5) 
+pdf("output/FigA5.pdf", height=6, width=5) 
   figure_A5(RIi, RCi)
 dev.off()
 
@@ -120,7 +120,7 @@ pdf("output/FigA7.pdf")
 dev.off()
 
 pdf("output/FigA8.pdf")
-  figure_A8(GC)
+  figure_A8(GCi)
 dev.off()
 
 pdf("output/FigA9.pdf")

### 2015-09-17 R/figures.R
use filled symbol in figure

@@ -214,7 +214,7 @@ figure_A1 <- function() {
 
     plot(data[[px$var]], data[[py$var]], log="xy",
       xlim = px$lim, ylim = py$lim,
-      xlab = px$lab, ylab = py$lab, col=adjustcolor("#00000033", alpha=0.5))
+      xlab = px$lab, ylab = py$lab, col=adjustcolor("#00000033", alpha=0.5), pch=16)
     abline(v=px$sap, col="#93EA6D", lty=5)
     abline(h=py$sap, col="#93EA6D", lty=5)
     abline(v=px$adult, col="#E6224C", lty=5)

### 2015-09-17 MS.tex
Suggested edits on abstract

@@
 \itemsep1pt\parskip0pt\parsep0pt
-\item Growth rates (GR) have often been seen as central elements of plant ecological strategies, and as linked to species traits.
-Yet, the literature is inconsistent about empirical correlations between functional traits and plant growth rate, casting doubt on the capacity of traits to predict growth.
+\item A plant's growth rate (GR) has often been seen as a central element of it's ecological strategy, and as ultimately linked to its traits.
+Yet, the literature is inconsistent about the empirical correlation between functional traits and GR, casting doubt on the capacity of traits to predict growth.
 
-\item Traits should influence growth in a way that depend on individual plants size.
-We outline mechanisms and hypotheses based on new theory, and test these predictions in tree species for five traits (specific leaf area, wood density, maximum height, seed mass and assimilation rate) using a meta-analysis of 112 studies ($>$ 500 correlations).
-As a first approximation of plants size, we analysed the shift in the correlations between growth and traits across three plant stages (i.e.
-juvenile, sapling and adult).
+\item We propose that traits should influence growth in a way that depends on the plant's size.
+We outline mechanisms and hypotheses based on new theory, and test these predictions in tree species for five traits (specific leaf area, wood density, maximum height, seed mass and maximum assimilation rate) using a meta-analysis of 112 studies ($>$ 500 correlations).
+To cpature the effects of size, we tested for a shift in the direction of correlation between GR and traits across three plant stages: juvenile, sapling and adult.
 
@@
 Correlations of GR with wood density and assimilation rate were not affected by stage.
-Maximum height and seed mass were correlated with GR only in one plant stage category.
+Seed mass and maximum height were correlated with GR only in one plant stage category: juveniles and adults, respectively.
 
-\item Synthesis: We show that traits-GR correlations change in a predictable way as a function of plant size.
-Our understanding of plant strategies should shift away from attributing slow vs fast growth to species throughout life, in favour of attributing growth trajectories.
+\item Synthesis: We show how trait-GR correlations change in a predictable way with plant size.
+These  Our understanding of plant strategies should shift away from attributing species as having slow or fast GR throughout their life, in favour of attributing growth trajectories.
 

### 2015-09-17 MS.tex
Change in Fig code

@@
 \linenumbers
-\section{Summary}\label{abstract}
+\section{Summary 274/350}\label{abstract}
 \begin{enumerate}
@@
 For example, instead of a positive relationship that disappeared with plant size, \citet{Iida:2014ep} found SLA was negatively correlated with RGR at small size and positively correlated with RGR at larger sizes.
-Similarly, instead of a negative correlation between WD and growth across all plant stages, \citep{Iida:2014ep,Iida:2014hq} found a negative correlation at small size that disappeared when trees were larger.
-\citet{Iida:2014hq} explained the switch in directionality by changes in light and water condition up the vertical profile within a forest: larger trees reached a position in the canopy where they were released from light limitations, other resources such as water may have become limiting, and the performance of trees may then have been regulated by different traits.
+Similarly, instead of a negative correlation between WD and growth across all plant stages,  some studies found a negative correlation at small size that disappeared when trees were larger \citep{Iida:2014ep,Iida:2014hq}.
+The authors explained the switch in directionality by changes in light and water condition up the vertical profile within a forest: larger trees reached a position in the canopy where they were released from light limitations, other resources such as water may have become limiting, and the performance of trees may then have been regulated by different traits.
 Note that in \citet{Iida:2014hq}, the shift in the correlation between growth and WD occurred for trees larger than 22-26 cm dbh.

### 2015-09-17 R/figures.R

@@ -59,7 +59,7 @@ figure_2 <- function(CompleteData_inter) {
     
     n <- nrow(data)
     y <- rev(seq_len(n))
-    cols <- c("#93EA6D", "#73005C", "#F57C34","#E6224C",
+    cols <- c("#538936", "#73005C", "#F57C34","#E6224C",
               "grey")[data$stageRGR]
     # 98F98C
     plot(NA, xlim=c(0,3), ylim= c(0,n), yaxt="n",xaxt="n",
@@ -82,15 +82,15 @@ figure_2 <- function(CompleteData_inter) {
   }
   
   plotCI2(sa, c(0,1,5,10), "age (yrs)")
-  abline(v = 1, col = "#93EA6D")
+  abline(v = 1, col = "#538936")
   legend(2.008,40, c("seedling","juvenile","sapling","adult","mix","across growth form","reassignment"), 
          lwd=c(1,1,1,1,1, NA, NA),
-         col=c("#93EA6D", "#73005C", "#F57C34","#E6224C",
+         col=c("#538936", "#73005C", "#F57C34","#E6224C",
                "grey", "black","black"),pch = c(NA, NA,NA,NA,NA,".","*"), 
          bty = "n", x.intersp = 0.3, y.intersp = 1,seg.len = 0.5, cex=0.8)
   
   plotCI2(sh, c(0,0.5,2,20), "height (m)")
-  abline(v = 1, col = "#93EA6D")
+  abline(v = 1, col = "#538936")
   
   plotCI2(sd, c(0,1,10,80), "diameter (cm)")
   abline(v = 2, col = "#E6224C")
@@ -214,9 +214,15 @@ figure_A1 <- function() {
 
     plot(data[[px$var]], data[[py$var]], log="xy",
       xlim = px$lim, ylim = py$lim,
+<<<<<<< Updated upstream
       xlab = px$lab, ylab = py$lab, col=adjustcolor("#00000033", alpha=0.5), pch=16)
     abline(v=px$sap, col="#93EA6D", lty=5)
     abline(h=py$sap, col="#93EA6D", lty=5)
+=======
+      xlab = px$lab, ylab = py$lab, col=adjustcolor("#00000033", alpha=0.5))
+    abline(v=px$sap, col="#538936", lty=5)
+    abline(h=py$sap, col="#538936", lty=5)
+>>>>>>> Stashed changes
     abline(v=px$adult, col="#E6224C", lty=5)
     abline(h=py$adult, col="#E6224C", lty=5)
   }

### 2015-09-17 R/plots.R

@@ -6,17 +6,17 @@ mytheme <- theme_bw() + theme(text = element_text(size = 9, colour = "black"),
   panel.background = element_blank(), legend.justification = c(1, 0), legend.position = c(1,0))
 
 my_plot_1 <- function(title, ggobj, xlab = expression(paste("")), ylab = "Number of correlations extracted") {
-  p <- ggobj + geom_bar(alpha = 0.9) + coord_cartesian(ylim = ylim) + coord_flip() + labs(title = title) +
+  p <- ggobj + geom_bar(alpha = 0.95) + coord_cartesian(ylim = ylim) + coord_flip() + labs(title = title) +
     xlab(xlab) + ylab(ylab) + scale_x_discrete() + theme(text = element_text(size = 9),
     axis.text.x = element_text(size = 9, angle = 0, vjust = 1)) + mytheme +
-    theme(axis.title = element_text(size = 10, hjust = 0.5)) + scale_fill_manual(values = c(juvenile = "#93EA6D",
+    theme(axis.title = element_text(size = 10, hjust = 0.5)) + scale_fill_manual(values = c(juvenile = "#538936",
     sapling = "#F57C34", adult = "#E6224C"), breaks = c("juvenile", "sapling", "adult"),
     labels = c("juvenile", "sapling", "adult"))
   p
  
 }
       
-      
+# "#93EA6D" "#538936"    
       
       coeff.plot.2 <- function(data, data.complete, data.ideal, LRT, PVAL, title = "",
         significativite = "", round.value, limit.x.min, limit.x.max, limit.x.text,
@@ -155,7 +155,7 @@ my_plot_corr.r <- function(data1, title = "", xlab = "Case studies ranked by coe
                   p <- ggobj + labs(title = title) + xlab(xlab) + ylab(ylab) + guides(fill = guide_legend(reverse = TRUE)) +
                     mytheme + scale_y_continuous("Correlation coefficient r", limits = c(-1,
                     1)) + scale_colour_manual(limits = c("juvenile", "sapling", "adult"),
-                    values = c(juvenile = "#93EA6D", sapling = "#F57C34", adult = "#E6224C"), breaks = c("juvenile",
+                    values = c(juvenile = "#538936", sapling = "#F57C34", adult = "#E6224C"), breaks = c("juvenile",
                       "sapling", "adult")) + geom_hline(yintercept = 0, size = 0.3, linetype = "dashed") +
[…]

### 2015-09-25 MS.tex
New version with comments from Ian, Mark and Daniel added

@@
 \item A plant's growth rate (GR) has often been seen as a central element of it's ecological strategy, and as ultimately linked to its traits.
-Yet, the literature is inconsistent about the empirical correlation between functional traits and GR, casting doubt on the capacity of traits to predict growth.
+Yet the literature is inconsistent about the empirical correlation between functional traits and GR, casting doubt on the capacity of traits to predict growth.
 
-\item We propose that traits should influence growth in a way that depends on the plant's size.
+\item We propose that traits should influence growth in a way that depends on the size of individual plants.
 We outline mechanisms and hypotheses based on new theory, and test these predictions in tree species for five traits (specific leaf area, wood density, maximum height, seed mass and maximum assimilation rate) using a meta-analysis of 112 studies ($>$ 500 correlations).
-To cpature the effects of size, we tested for a shift in the direction of correlation between GR and traits across three plant stages: juvenile, sapling and adult.
+To capture the effects of size, we tested for a shift in the direction of correlation between GR and traits across three plant stages: juvenile, sapling and adult.
 
@@
 
-The phrase ``plant ecological strategy'' refers to how species face common challenges of acquiring sufficient water, nutrients and light for growth, and then ultimately to replace themselves with offspring.
+The phrase ``plant ecological strategy'' refers to how species face common challenges of acquiring sufficient water, nutrients and light for growth, and then ultimately replacing themselves with offspring.
 An idea that species strategy differences might involve fast versus slow growth goes back at least to \citet{Grime:1975gr}, who measured a wide spread of relative growth rates for seedlings during early exponential growth under favourable conditions.
@@
 The ``leaf economic spectrum'' \citep{Wright:2004jb} and the ``wood economic spectrum'' \citep{Chave:2009iy} reflect tissue construction costs (for leaf area and for wood volume respectively), trading off with rates of tissue turnover or mortality.
-It has been widely expected that species with low tissue construction cost will typically have fast growth rates, at least in favourable physical environments \citep[e.g.][]{MullerLandau:2004dc,Wright:2004jb,Poorter:2008iu,Chave:2009iy,Larjavaara:2010bn,Iida:2012jb,Paine:2015df}.
-Yet, a growing number of empirical studies indicates the correlation between traits and growth is not as consistent as that.
+It has been widely expected that species with low tissue construction cost will typically have fast growth rates, at least in favourable physical environments \citep[e.g.][]{MullerLandau:2004dc,Poorter:2008iu,Chave:2009iy,Larjavaara:2010bn,Iida:2012jb,Paine:2015df}.
+Yet, a growing number of empirical studies indicate the correlation between traits and growth is not as consistent as that.
 Consider SLA as an illustration.
@@
 For seedling relative growth rates under favourable conditions, high SLA has repeatedly been found to be a strong predictor regardless of vegetation type or growth form \citep{Lambers:1992bj,Reich:1992wm,Grime:1997wm,Poorter:1999wd,Wright:1999ds}.
-Yet for adult plants, the correlation is mostly much weaker or absent \citep{coomes_comparison_1998,Poorter:2008iu,Aiba:2009ft,Easdale:2009gv,Wright:2010tp}.
+Yet for adult plants, the correlation has mostly been much weaker or absent \citep{coomes_comparison_1998,Poorter:2008iu,Aiba:2009ft,Easdale:2009gv,Wright:2010tp}.
 The growing discrepancy between theoretical expectation and empirical results has led some to question whether traits are even useful for understanding growth \citep{Wright:2010tp, Paine:2015df}.
@@
 We used plant stage (i.e.
-juvenile, sapling and adult) as a first approximation of plant size.
+juvenile, sapling and adult) as a surrogate for the effects of plant size.
 We focused on tree and woody species since the mechanistic model used to assess our predictions is most applicable to these growth forms.
@@
 
-\textbf{H2: The relationship between WD and growth rate is expected to be negative across all plant size}
+\textbf{H2: The relationship between WD and growth rate is expected to be negative across all plant sizes}
 
@@
 Tree growth in diameter, height or mass can be expressed in either absolute (AGR) or relative terms (RGR).
-According to the growth model, the predicted relationship between growth and either SLA or SM in seedlings reverts if absolute AGR$_\textrm{mass}$ is used instead of RGR$_\textrm{mass}$ (see Appendix \ref{sec:growth}).
-For SLA, the correlation with RGR$_\textrm{mass}$ is positive but becomes negative with AGR$_\textrm{mass}$.
-For SM the correlation with RGR$_\textrm{mass}$ is negative but becomes positive with AGR$_\textrm{mass}$.
-For the others traits (WD, Hmax and Aarea), the predicted relationships are not affected by the growth measurement used.
+According to the growth model, the predicted relationship between growth and SM in seedlings reverts if absolute AGR$_\textrm{mass}$ is used instead of RGR$_\textrm{mass}$ (see Appendix \ref{sec:growth}).
+The correlation with RGR$_\textrm{mass}$ is negative but becomes positive with AGR$_\textrm{mass}$.
+For SLA, WD, Hmax and Aarea the predicted relationships are not affected by the growth measurement used.
+
+All the above hypotheses arise from direct mechanistic causation between traits and growth rate.
+It is possible that other correlations may arise indirectly.
+For example, seed size is somewhat correlated with height at maturity \citep{Westoby:2009ch}, and so an indirect correlation might arise between seed size and GR in large plants, even though no direct influence is expected.
+Nevertheless, for purposes of this paper we adopt working hypotheses arising only from direct mechanistic causation.
 
@@
 To minimise publication bias via selective reporting of significant results within the published articles (e.g.
-a particular case of a ``failure to publish bias'' see \citealt{Jennions:2013ta}), we asked those authors reporting a non-significant correlation for additional information about the specific correlation coefficient when these were not provided.
+a particular case of a ``failure to publish bias'' see \citealt{Jennions:2013ta}), we asked those authors reporting a non-significant correlation for additional information about the specific correlation coefficient when this was not provided.
 
@@
 Finally, the leaf area ratio and leaf mass ratio are indicators of resource allocation to leaf \citep{Lambers:1992bj}.
-According to the snapshot of the literature on Web of Science, 62\% of the literature for these 19 traits were captured by a search on SLA and WD.
+According to the snapshot of the literature on Web of Science, 62\% of the literature for these 19 traits was captured by a search on SLA and WD.
 
@@
 We were unable to obtain a consistent and continuous measure of plant size across all studies, thus we relied on categorical groupings by ``stage'' to test our hypotheses.
-The authors of the 112 articles used in the meta-analyses, reported their plants as belonging to any of fix different stages: ``seedling'', ``juvenile'', ``sapling'', ``adult'', ``mixed''.
+The authors of the 112 articles used in this analysis reported their plants as belonging to any of five different stages: ``seedling'', ``juvenile'', ``sapling'', ``adult'', ``mixed''.
 While these categories have been established according to the expertise of the authors, by compiling data across multiple studies and vegetation types, we were concerned about the risk of assigning plants of similar size to different categories.
-This risk turned out to be negligible: overall, we found that the original thresholds in size/age used by the authors to distinguish different stages was relatively compatible (Fig.
+This risk turned out to be negligible: overall, we found that the original thresholds in size/age used by the authors to distinguish different stages were relatively compatible (Fig.
 \ref{fig:fig2}).
-In particular, there was a clear break between seedlings and saplings in both age (at 1 yr) and height (at 0.5 m); there was also a clear break between saplings and adults in diameter (at 10 cm).
-According to simple allometric relationships between size variables plotted using data from the Biomass And Allometry Database \citep{Falster:2015}, these thresholds also align relatively well with one another (Fig.
+In particular, there was a clear break between seedlings and saplings in both age (at 1 yr) and height (at 0.5 m).
+There was also a clear break between saplings and adults in diameter (at 10 cm).
+According to simple allometric relationships between size variables plotted using data from the Biomass And Allometry Database \citep{Falster:2015}, the thresholds used for each stage transition align relatively well with one another across the different size measurements (age, height and diameter, Fig.
 \ref{fig:figA1}).
 Thus we adopted the above values as cut-offs for defining stage boundaries.
-However, the group ``juvenile'' was largely overlapping with the three others, causing us to merge this category with one of the other on a case by case basis for each study.
+However, the group ``juvenile'' was largely overlapping with the three others, and so we merged this category with one or the other on a case by case basis.
 
@@
 We preferred the term ``juvenile'' to ``seedling'', because for a portion of the scientific community ``seedling'' also refers to a particular experimental condition.
-Using the above cut-offs we were also able to assign a stage category to studies for which no stage have been distinctly mentioned by the authors (5\% of the articles, noted as ``mix'' in Fig.
+Using the above cut-offs we were also able to assign a stage category to studies for which no stage was distinctly mentioned by the authors (5\% of the articles, noted as ``mix'' in Fig.
 \ref{fig:fig2}).
@@
 Half of these equivocal cases involved the juvenile category.
-We attributed a study to a new stage category only when 95\% of the recorded range of sizes for that study lay within a new stage category.
-Others equivocal cases were caused by an ambiguity in the definition of ``adult'' used by the authors.
-Some plants with a large stature are not assessed as adult by the authors because they are still non reproductive \citep{King:2006dg,King:2006he}.
-Whereas plants with a small stature -because stunnded by frequent wind for example \citep{Stratton:2001ck}- are assessed as adult because they are reproductive.
-Here, we attributed a study to the adult stage when the authors identified the plants as reproductive, and to sapling stage when they identified the plants as non-reproductive, regardless the plant size or age.
-Results using the categories established by the authors are similar than the one using the standardized categories and are available in Fig.
-\ref{fig:figA6} model.1.
+We attributed a study to a new stage category only when 95\% of the recorded range of sizes for that study lay within a particular stage category.
+Other equivocal cases were caused by ambiguity in the usage of ``adult'' by the authors.
+Some plants with a large stature were not described as adult by authors because they were still non reproductive \citep{King:2006dg,King:2006he}.
+Conversely plants with small stature -- because stunted by wind for example \citep{Stratton:2001ck}-- were sometimes assessed as adult when reproductive.
+For purposed of the present paper we attributed a study to the adult stage when the authors identified the plants as reproductive, and to sapling stage when they identified the plants as non-reproductive, regardless of the plant's size or age.
+Results using the categories established by the authors are similar to those using the standardized categories (see Fig.
+\ref{fig:figA6} model.1).
 In the main text, we report only results using the standardized categories.
@@
 
-As a measure of effect size, we used the cross-species Pearson product-moment correlation coefficient $r$ between growth rate and trait, weighted by the number of species contributing to the relationship.
+To measure of effect size, we used the cross-species Pearson product-moment correlation coefficient $r$ between growth rate and trait, weighted by the number of species contributing to the relationship.
 For studies that reported another coefficient -- such as coefficient of determination, Spearman's rho rank correlation, or Kendall's tau rank correlation -- we converted these to correlation coefficients following \citet{Lajeunesse:2013tm}.
 As the magnitude of Pearson's correlation coefficient approaches $\pm$ 1.0, its distribution becomes skewed.
-Accordingly we transformed the correlation $r$ into a metric $z$ with more-desirable statistical properties.
+Accordingly, we transformed the correlation $r$ into a metric $z$ with more-desirable statistical properties.
 The transformation was achieved via Fisher's z-transformation,
@@
 where $n$ is the number of species.
-We weighted effect size by the number of species used to calculation the correlation, instead of the raw number of individuals, because our questions primarily concerned the correlation between growth and traits across species and not within species.
+We weighted effect size by the number of species used to calculate the correlation, instead of the raw number of individuals, because our questions primarily concerned the correlation between growth and traits across species and not within species.
 
@@
 We tested stage effect on traits for which $>$ 15 correlation coefficients across at least two stages were recorded.
-We used a mixed-effect model of meta-analysis, in which it is assumed that studies within a stage share a common mean effect but that there is also random variation among studies in a stage, in addition to sampling variation.
+We used a mixed-effect model of meta-analysis, in which it is assumed that studies within a stage share a common mean effect but that there is also random variation among studies in a stage, in addition to sampling variation \citep{Zuur:2009cfa}.
 This random effect allows us to account for the heterogeneity among studies (e.g.
 experimental type, vegetation type, error, etc.).
-For each trait, we established if stage could explain variance in $z$ by comparing models with the stage variable to the null model using log-likelihood ratios \citep{Zuur:2009cfa}.
+For each trait, we established whether stage could explain variance in $z$ by comparing models with the stage variable to the null model using log-likelihood ratios \citep{Zuur:2009cfa}.
 If the log-likelihood test returned a significant p-value, the stage model fitted the data better than the null model.
@@
 We tested how robust our results were to the particular decisions made in the analysis.
-In partiuclar, we tested the sensitivity of our results to inclusion of studies that measured a large number of responses for the same trait.
-The idea is to check that our results are not generated by the dominance of one or few studies reporting several values for the same trait.
+In particular, we tested the sensitivity of our results to inclusion of studies that measured a large number of responses for the same trait.
+The idea is to check that our results were not generated by the dominance of one or few studies reporting several values for the same trait.
 In the case of multiple comparisons within a study, we used the method proposed by \citet{Borenstein:2009um}: we calculated the mean correlation coefficient by trait and by study, and then re-calculated the effect size.
 This produced a reduced dataset, where multiple responses for any given trait were condensed into a study-level average.
-We also tested if the criteria used for including a study in the analysis affect our results.
-In addition of the chosen criteria, the experimental conditions (stress vs unstressed), and the concordance between stage used to measure trait and growth are clear criteria for assessing the quality of the data for addressing our hypotheses.
+We also tested whether the criteria used for including a study in the analysis influenced our results.
+In addition to the chosen criteria, the experimental conditions (stressed vs unstressed), and the concordance between stage used to measure trait and growth are clear criteria for assessing the quality of the data for addressing our hypotheses.
 Thus we stratified the data set into two subsets: one including only studies under unstressed conditions ('ideal' dataset), and the other set including studies under all conditions ('complete' dataset).
-We excluded from the ''ideal'' dataset studies where growth and traits were measured on plants from different stages, unless a particular stage is by definition required to measure a trait such as for SM (i.e.
+We excluded from the ''ideal'' dataset studies where growth and traits were measured on plants from different stages, unless a particular stage was by definition required to measure the trait, such as for SM (i.e.
 seed stage), or Hmax (i.e.
@@
 \cite{Koricheva:2014ku} outlined 14 methodological quality criteria to ensure robust results from meta-analyses.
-Table \ref{tab:meta} outlines how we address each of these.
-In particular, we quantified heterogeneity in effects size, we tested for publication bias and we explored temporal change in effect size (see Appendix \ref{app:supp_info_analyses}).
+Table \ref{tab:meta} outlines how we addressed each of these.
+In particular, we quantified heterogeneity in effect size, we tested for publication bias and we explored temporal change in effect size (see Appendix \ref{app:supp_info_analyses}).
 
@@
 For both traits, correlation coefficients recorded at sapling stage were intermediate between juvenile and adult stages.
-The relationship between growth and either SLA or SM in seedlings is expected to differ if absolute GR in mass is used instead of RGR mass.
-Here, for both traits growth in mass was exclusively expressed in relative terms for seedlings(results shown in the Fig.
+The relationship between growth and SM in seedlings is expected to differ if absolute GR in mass is used instead of RGR mass.
+Here, for SM growth in mass was exclusively expressed in relative terms for seedlings (results shown in the Fig.
 \ref{fig:figA8} and Fig \ref{fig:figA4} f-j)
@@
 \ref{fig:fig3} c), but also was consistent with no correlation (Fig \ref{fig:fig3} c, confidence intervals overlapping zero), due to much smaller numbers of replicate studies.
+We could not distinguish between these alternatives.
 Similarly for WD and for Aarea, results were consistent with negative (WD) and positive (Aarea) correlations with growth across all plant sizes (Fig.
@@
 \ref{fig:figA3}).
-The growth form, the experiment types and the growth measurement were not markedly best predictors of the data (results shown in the Fig.
-\ref{fig:figA6}).
+Growth form, experiment type and growth measurement type were not strong predictors in general (Fig.
+\ref{fig:figA6}), and confounding with these factors is not a likely explanation fo the major results reported.
 
-The results reported above were confined to correlations across species, and under non-stressed conditions ($n = 176$).
-A ``complete'' dataset ($n = 216$) also included correlations measured under stressed conditions, and spanning different plant stages between the growth and trait measurements.
+The results reported above were obtained using the "ideal" dataset, and were thereby confined to correlations across species, and under non-stressed conditions ($n = 176$).
+The ``complete'' dataset ($n = 216$) also included correlations measured under stressed conditions, and spanning different plant stages between the growth and trait measurements.
 This ``complete'' dataset generated similar effect sizes to those reported above from the ``ideal'' dataset, and led to similar conclusions (Fig.
@@
 \ref{fig:fig3}.
-These differences in CI were not easily attributed to any single cause.
+These differences in CI may have arisen from a variety of causes.
 For instance, the correlation between growth and WD at juvenile stage shifted from negative to non significant (i.e CI 95\% included zero) due to 2 positive correlation coefficients from \citet{Augspurger:1984ct}; these correlations unlike others used values of WD from adult plants together with growth from juveniles.
@@
 
-Overall our study met all the quality criteria required for meta-analysis in ecology (Table \ref{tab:meta}).
-We showed that the impact of publication bias is probably trivial in our meta-analyses (Appendix E, Fig.
+Overall our study met quality criteria expected for meta-analysis in ecology (Table \ref{tab:meta}).
+The impact of publication bias was probably trivial (Appendix E, Fig.
 \ref{fig:figA7}).
-The extent of the heterogeneity was high in our meta-analysis,  but substantially explained by the plant stage effect for SLA and SM, as expected (Appendix E).
+The extent of heterogeneity was high, but was substantially explained by the plant stage effect for SLA and SM, as expected (Appendix E).
 Finally, there was no indication of a temporal change in the effect size being reported within stages (Appendix E, Fig.
@@
 
-The meta-analysis reported here demonstrates that for several key traits the influence of traits on growth rates changes as plants grow from small to large.
-While the possibility has been raised recently that trait-growth correlations may change systematically with size \citep{Falster:2011ii, Ruger:2012jv, Iida:2014ep, Iida:2014hq}, it is the first time that mechanistic hypotheses are corroborated across a large number of studies already available.
+The meta-analysis reported here demonstrates that for several key traits, the influence of the trait on growth rate changes as plants grow from small to large.
+While the possibility has been raised recently that trait-growth correlations may change systematically with size \citep{Falster:2011ii, Ruger:2012jv, Iida:2014ep, Iida:2014hq}, this is the first time that specific mechanistic hypotheses have been corroborated by meta-analysis of existing literature.
 Meta-analysis allowed us to generalize and thus to reach a consensus about the effect of traits on growth.
-Growth rates are known to change with size through ontogeny \citep{Condit:1993hd, Clark:1999ed, Herault:2011dd}, \textit{i.e.
-plants follow a growth trajectory}; species traits should be understood as influencing this trajectory and potentially re-ranking growth rates with size.
-This is a shift in view from the current approach in plant strategy schemes, whereby traits are thought to render species fast-growing or slow-growing throughout life.
+Growth rates are known to change with size through ontogeny \citep{Condit:1993hd, Clark:1999ed, Herault:2011dd}, in other words plants follow a growth trajectory.
+Species traits should be understood as influencing this trajectory and potentially re-ranking growth rates between species as size increases.
+This is a shift in outlook compared to much present thinking whereby traits are seen as rendering species fast-growing or slow-growing throughout life.
 
@@
 
-Further, for five prominent traits, the patterns observed are consistent with specific predictions from a mechanistic growth model.
-This indicates provisionally that the mechanisms through which traits affect growth are correctly understood in the model.
-For SLA and for SM the meta-analysis confirms quite strongly the predicted influence of plant size on the trait-growth correlation.
+For five prominent traits, the patterns observed were consistent with specific predictions from a mechanistic growth model.
+This is coherent with the mechanisms through which traits affect growth being correctly understood in the model.
+For SLA and for SM the meta-analysis confirmed quite strongly the predicted influence of plant size on the trait-growth correlation.
 For WD, Aarea and Hmax results were consistent with predictions, but coverage was limited and additional studies would be helpful for some trait-growth-stage relationships.
@@
 Several authors have suggested that the disappearance of SLA's influence on growth might be due to a disproportionate accumulation of leaf area by low SLA species \citep{Reich:1992wm,Poorter:2008iu,Wright:2010tp}, yet it remains unclear whether such a mechanism works as intended.
-More importantly, the assumed empirical relationship between SLA and total leaf area does not hold true across large number of species (Duursma and Falster, in review).
+Further, the assumed empirical relationship between SLA and total leaf area does not hold true as a generalisation across large number of species (Duursma and Falster, in review).
 In the model described here, the mechanism is slightly different: high-SLA species incur faster leaf turnover, the cost of which outweighs the benefits of cheap leaf construction at larger sizes.
 
-For seedlings our meta-analyses showed, as expected, a negative relationship between SM and relative growth rate (in mass or height or volume) for small plants, that dissipated as plants grew larger.
-This negative relationship arises because seedlings from larger seeds are begin life larger themselves, as has been extensively discussed in the literature \citep[reviewed by][]{Turnbull:2012ew}.
+For seedlings our meta-analyses showed, as expected, a negative relationship between SM and RGR (in mass or height or volume) for small plants, that dissipated as plants grew larger.
+This negative relationship arises because seedlings from larger seeds begin life larger themselves, as has been extensively discussed in the literature \citep[reviewed by][]{Turnbull:2012ew}.
 
@@
 
-As far as we are aware, our study is the first to compared correlations between Aarea and growth among small and large plants.
+As far as we are aware, our study is the first to compare Aarea and growth correlations between small and large plants.
 In the growth model (Appendix \ref{sec:growth}), a consistent correlation irrespective of size arises from a direct effect of Aarea on plant growth rate.
-Meta-analyses showed a positive correlation for adult and juvenile but not for saplings (n=2) In juvenile stage, where most of the data were, we noted no signal of an effect of low light on the positive correlation between Aarea and growth rate.
+Meta-analyses showed a positive correlation for adult and juvenile but not for saplings (n=2).
+In the juvenile stage, where most of data were available, we noted no signal of an effect of low light on the positive correlation between Aarea and growth rate.
 
@@
 \citealt{Poorter:2008iu,Wright:2010tp,Herault:2011dd,Ruger:2012jv,Iida:2014ep}).
-In \citet{Wright:2010tp}, Hmax was considered as the weakest predictor of growth rates of saplings; however it was the strongest predictor of growth rates of large trees.
+In \citet{Wright:2010tp}, Hmax was considered a weak predictor of growth rates of saplings; however it was the strongest predictor of growth rates of large trees.
 \citet{Poorter:2008iu} speculated that the Hmax-RGR relationship among large trees might arise from including small tree species with maximum size not much larger than the  10cm dbh lower threshold used to define large trees.
@@
 Charles Warren and Jordi Martìnez-Vilalta kindly provided additional information about their published results.
-This work was funded by the Australian Research Council through a fellowship to MW and a discovery grant to DF.
+This work was funded by the Australian Research Council through a fellowship to MW, a discovery grant to DF and a Macquarie University Research Fellowships to EG.
 
@@
 \caption{The range of plant sizes and stage recoded in original publications, compared to standardised thresholds used in the analysis. Panels are for
-\textbf{a)} age, \textbf{b)} height and \textbf{c)} diameter.
+a) age, b) height and c) diameter.
 Horizontal line segments indicate the size range (max., min.) for the plants used to measure growth.
@@
 "*" indicated when a stage reassignment is needed.
-Dots on left side of the graph indicate cases where plants had different growth form.
+"+" on left side of the graph indicate cases where plants had different growth form.
 Results shown here are the ''complete'' dataset (see methods for details).}
@@
 \centering
-\caption{\textbf{Hypothesised effects of traits on key elements of plant function determining growth rate.} Arrows indicate the effect an increase in trait value would have on the main elements of growth eqs.
+\caption{Hypothesised effects of traits on key elements of plant function determining growth rate.
+Arrows indicate the effect an increase in trait value would have on the main elements of growth eqs.
 \ref{eq:eq0}-\ref{eq:eq4} in Appendix \ref{sec:growth}.
-Traits are SLA: Specific leaf area, WD: Wood density, Hmax: Asymptotic maximum height, SM: seed mass, Aarea: Maximum photosynthetic rate.
+Traits names as in Figure 1.
 For further details, see Appendix \ref{sec:growth}.}
@@
 \centering
-\caption{\textbf{Check-list of quality criteria for meta-analysis in ecology} developed by Koricheva and Gurevitch (2014) }
+\caption{Check-list of quality criteria for meta-analysis in ecology developed by Koricheva and Gurevitch (2014) }
 {\footnotesize

### 2015-09-25 R/figures.R

@@ -38,7 +38,7 @@ figure_2 <- function(CompleteData_inter) {
 
   layout(matrix(c(1, 2, 3), 3, 1, byrow = TRUE), widths = c(3, 3, 3), heights = heights)
   # layout.show(3)
-  par(mar = c(4, 4, 0, 0.5), oma = c(1, 2, 1, 1))
+  par(mar = c(4, 4, 0.1, 0.5), oma = c(1, 2, 1, 1))
 
   plotCI2 <- function(data, cuts, xlab) {
 
@@ -71,24 +71,24 @@ figure_2 <- function(CompleteData_inter) {
     points(data$size.min[i], y[i], col = cols[i], pch = "-")
 
     j <- data$stageRGR != data$stage
-    points(data$size.max[j] + 0.05, y[j], col = "black", pch = "*")
+    points(data$size.max[j] + 0.05, y[j], col = "black", pch = "*", cex=2)
 
     t <- (data$growth.form == "across growth form")
-    points(data$growthf[t], y[t], pch = ".")
+    points(data$growthf[t], y[t], pch = "+", cex=1, col="grey")
 
     axis(1, at = 0:3, labels = cuts, las = 1)
-    axis(2, at = y, labels = data$id, las = 1, cex.axis = 0.5)
+    axis(2, at = y, labels = data$id, las = 1, cex.axis = 0.55)
     abline(v = 1, col = "grey", lty = 2, lwd = 0.5)
     abline(v = 2, col = "grey", lty = 2, lwd = 0.5)
   }
 
   plotCI2(sa, c(0, 1, 5, 10), "age (yrs)")
   abline(v = 1, col = "#538936")
-  legend(2.008, 40, c("seedling", "juvenile", "sapling", "adult", "mix", "across growth form",
+  legend(2.38, 40, c("seedling", "juvenile", "sapling", "adult", "mix", "across growth form",
     "reassignment"), lwd = c(1, 1, 1, 1, 1, NA, NA), col = c("#538936", "#73005C",
-    "#F57C34", "#E6224C", "grey", "black", "black"), pch = c(NA, NA, NA, NA,
-    NA, ".", "*"), bty = "n", x.intersp = 0.3, y.intersp = 1, seg.len = 0.5,
-    cex = 0.8)
[…]

### 2015-09-25 analysis.R

@@ -52,7 +52,7 @@ pdf("output/Fig1.pdf", height = 3, width = 4)
 figure_1(RawData)
 dev.off()
 
-pdf("output/Fig2.pdf", height = 8, width = 4)
+pdf("output/Fig2.pdf", height = 8, width = 6)
 figure_2(CompleteData_inter)
 dev.off()
 

### 2015-09-28 MS.tex
Comments of Emma and Mark added: - change terminology: juvenile ->seedling - check spelling Appendix E and D - change color: from green to blue for color-blind person

@@
 \itemsep1pt\parskip0pt\parsep0pt
-\item A plant's growth rate (GR) has often been seen as a central element of it's ecological strategy, and as ultimately linked to its traits.
+\item A plant's growth rate (GR) has often been seen as a central element of its ecological strategy, and as ultimately linked to its traits.
 Yet the literature is inconsistent about the empirical correlation between functional traits and GR, casting doubt on the capacity of traits to predict growth.
@@
 We outline mechanisms and hypotheses based on new theory, and test these predictions in tree species for five traits (specific leaf area, wood density, maximum height, seed mass and maximum assimilation rate) using a meta-analysis of 112 studies ($>$ 500 correlations).
-To capture the effects of size, we tested for a shift in the direction of correlation between GR and traits across three plant stages: juvenile, sapling and adult.
+To capture the effects of size, we tested for a shift in the direction of correlation between GR and traits across three plant stages: seedling, sapling and adult.
 
 \item Results were consistent with predictions.
-Specific leaf area was correlated with GR in juvenile but not in adult plants.
+Specific leaf area was correlated with GR in seedling but not in adult plants.
 Correlations of GR with wood density and assimilation rate were not affected by stage.
-Seed mass and maximum height were correlated with GR only in one plant stage category: juveniles and adults, respectively.
+Seed mass and maximum height were correlated with GR only in one plant stage category: seedlings and adults, respectively.
 
@@
 We used plant stage (i.e.
-juvenile, sapling and adult) as a surrogate for the effects of plant size.
+seedling, sapling and adult) as a surrogate for the effects of plant size.
 We focused on tree and woody species since the mechanistic model used to assess our predictions is most applicable to these growth forms.
@@
 
-Using the identified boundaries among stages we were able to assign all studies into one of three classes: ``juvenile'', ``sapling'', or ``adult''.
-We preferred the term ``juvenile'' to ``seedling'', because for a portion of the scientific community ``seedling'' also refers to a particular experimental condition.
+Using the identified boundaries among stages we were able to assign all studies into one of three classes: ``seedling'', ``sapling'', or ``adult''.
 Using the above cut-offs we were also able to assign a stage category to studies for which no stage was distinctly mentioned by the authors (5\% of the articles, noted as ``mix'' in Fig.
@@
 \ref{fig:figA4} a-e).
-The correlation between growth and SLA shifted from strongly positive at juvenile stage $\bar{r}=0.6 \pm 0.08$, Mean $\pm$ SD) to not significantly different from zero at adult stage ($\bar{r}= -0.01 \pm 0.07$, CI 95\% overlapping zero in Fig.
+The correlation between growth and SLA shifted from strongly positive at seedling stage $\bar{r}=0.6 \pm 0.08$, Mean $\pm$ SD) to not significantly different from zero at adult stage ($\bar{r}= -0.01 \pm 0.07$, CI 95\% overlapping zero in Fig.
 \ref{fig:fig3} a).
-The correlation between growth and SM shifted from negative at juvenile stage ($\bar{r}= -0.5 \pm 0.07$) to not significantly different from zero at adult stage ($\bar{r}= -0.09 \pm 0.02$, , CI 95\% overlapping zero in Fig.
+The correlation between growth and SM shifted from negative at seedling stage ($\bar{r}= -0.5 \pm 0.07$) to not significantly different from zero at adult stage ($\bar{r}= -0.09 \pm 0.02$, , CI 95\% overlapping zero in Fig.
 \ref{fig:fig3} d).
-For both traits, correlation coefficients recorded at sapling stage were intermediate between juvenile and adult stages.
+For both traits, correlation coefficients recorded at sapling stage were intermediate between seedling and adult stages.
 The relationship between growth and SM in seedlings is expected to differ if absolute GR in mass is used instead of RGR mass.
@@
 Indeed Hmax was positively correlated with growth at adult stage ($\bar{r}= 0.38 \pm 0.05$).
-At sapling and juvenile stages, the correlation between Hmax and growth was not significantly different from that observed at adult stage (model fit not improved when stage was incorporated, see log likelihood ratio tests in Fig.
+At sapling and seedling stages, the correlation between Hmax and growth was not significantly different from that observed at adult stage (model fit not improved when stage was incorporated, see log likelihood ratio tests in Fig.
 \ref{fig:fig3} c), but also was consistent with no correlation (Fig \ref{fig:fig3} c, confidence intervals overlapping zero), due to much smaller numbers of replicate studies.
@@
 Growth form, experiment type and growth measurement type were not strong predictors in general (Fig.
-\ref{fig:figA6}), and confounding with these factors is not a likely explanation fo the major results reported.
+\ref{fig:figA6}), and confounding with these factors is not a likely explanation of the major results reported.
 
@@
 These differences in CI may have arisen from a variety of causes.
-For instance, the correlation between growth and WD at juvenile stage shifted from negative to non significant (i.e CI 95\% included zero) due to 2 positive correlation coefficients from \citet{Augspurger:1984ct}; these correlations unlike others used values of WD from adult plants together with growth from juveniles.
+For instance, the correlation between growth and WD at seedling stage shifted from negative to non significant (i.e CI 95\% included zero) due to 2 positive correlation coefficients from \citet{Augspurger:1984ct}; these correlations unlike others used values of WD from adult plants together with growth from seedlings.
 For Aarea, the comparison between complete and ideal data showed no signal of an effect of stress (here mainly low light) on the correlation with growth at seedling stage; the correlation was still positive between Aarea and growth even when 8 correlations measured under low light conditions were added.
@@
 In the growth model (Appendix \ref{sec:growth}), a consistent correlation irrespective of size arises from a direct effect of Aarea on plant growth rate.
-Meta-analyses showed a positive correlation for adult and juvenile but not for saplings (n=2).
-In the juvenile stage, where most of data were available, we noted no signal of an effect of low light on the positive correlation between Aarea and growth rate.
+Meta-analyses showed a positive correlation for adult and seedling but not for saplings (n=2).
+In the seedling stage, where most of data were available, we noted no signal of an effect of low light on the positive correlation between Aarea and growth rate.
 
-Meta-analysis showed a positive correlation between Hmax and growth for adult stage, but not for saplings and juveniles.
+Meta-analysis showed a positive correlation between Hmax and growth for adult stage, but not for saplings and seedlings.
 The trend for tall stature species to grow faster at a given tree size than small stature species has been noted across several tree size classes and forest types (e.g.
-\citealt{Poorter:2008iu,Wright:2010tp,Herault:2011dd,Ruger:2012jv,Iida:2014ep}).
+\citealt{Thomas:1996do,Poorter:2008iu,Wright:2010tp,Herault:2011dd,Ruger:2012jv,Iida:2014ep}).
 In \citet{Wright:2010tp}, Hmax was considered a weak predictor of growth rates of saplings; however it was the strongest predictor of growth rates of large trees.
@@
 At a given tree size, species closer to their Hmax are expected to be allocating relatively less to vegetative growth.
-However this applies only at sizes where some of the species have begun to reproduce, and should not affect sapling and juvenile growth rates.
+However this applies only at sizes where some of the species have begun to reproduce, and should not affect sapling and seedling growth rates.
 
@@
 Clearly there is much scope for strengthening our understanding of correlations between traits and growth through (1) adding further empirical studies for traits and size-classes with weaker representation, (2) accounting more satisfactorily for variables such as light, and (3) expressing plant sizes on continuous scales of mass or height rather than through the approximate and partly subjective categories unavoidably adopted here.
-Additional data are specifically required in small plants (juvenile and sapling) for WD and Hmax, and in large plants (adult and sapling) for Aarea and more broadly for all traits requiring a measure of whole plant biomass (e.g.
+Additional data are specifically required in small plants (seedling and sapling) for WD and Hmax, and in large plants (adult and sapling) for Aarea and more broadly for all traits requiring a measure of whole plant biomass (e.g.
 LMR, LAR, NAR).
@@
   2.& Reporting inclusion or exclusion criteria & yes & We specified several inclusion criteria in the sub-section "Phase 2 - Systematic search" in material and method.
-The Bibtex file `read.bib` on Guithub reports all the articles red but laid out because they failed to met our criteria.\\
+The Bibtex file `read.bib` on Github reports all the articles red but laid out because they failed to met our criteria.\\
   3.& Weighting effect sizes by study precision & yes & Effects sizes were weighted by number of species. See	 details in sub-section ``Effect size calculation'' in material and method.\\
@@
 \ref{eq:eq1}; Table \ref{tab:trade-offs}).
-For juveniles and seedlings this fraction is 1 for all species and so no effect is expected.
+For seedlings and seedlings this fraction is 1 for all species and so no effect is expected.
 But once some species begin to produce seed, then species closer to their Hmax value are expected to be allocating more to seed production and less to vegetative growth.
@@
 \centering
-\caption{\textbf{List of the nineteen traits targeted}. Abbreviation,
+\caption{List of the nineteen traits targeted. Abbreviation,
 definition and search term used in the meta-analysis}
@@
 \includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA1.pdf}
-\caption{\textbf{Allometric relationships between a) age and diameter (m), b) age and height (m), and c) diameter and height in trees according to the BAAD database.} Green and red lines are the cutoffs between stage categories used in the literature.
-Green lines corresponds to limits between juveniles and saplings, red lines to limits between saplings and adults.}
+\caption{Allometric relationships between a) age and diameter (m), b) age and height (m), and c) diameter and height in trees according to the BAAD database.
+Blue and red lines are the cut-offs between stage categories used in the literature.
+Blue lines corresponds to limits between seedlings and saplings, red lines to limits between saplings and adults.}
 \label{fig:figA1}
@@
 \includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA2.pdf}
-\caption{\textbf{Geographical distribution of site locations from studies performed in the field used in the meta-analysis}.
-Results shown here are from the ``complete'' dataset (see methods for details).}
+\caption{Geographical distribution of site locations from studies performed in the field used in the meta-analysis. Results shown here are from the ``complete'' dataset (see methods for details).}
 \label{fig:figA2}
@@
 \includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA3.pdf}
-\caption{\textbf{Range of correlations (r) between
-growth and trait reported in the literature (112 articles)}. Plots shown the coefficients of correlation (r)
-between the plant growth and \textbf{a)} Specific leaf area (SLA, n =
-111), \textbf{b)} Wood density (WD, n = 64), \textbf{c)} Asymptotic
-maximum height (Hmax, n = 23), \textbf{d)} Seed mass (Seedmass, n = 36 and
-\textbf{e)} Rate of CO2 assimilation (Aarea, n = 24) reported from 112
+\caption{Range of correlations (r) between
+growth and traits reported in the literature. Plots show the coefficients of correlation (r)
+between plant growth and a) Specific leaf area (SLA, n =
+111), b) Wood density (WD, n = 64), c) Asymptotic
+maximum height (Hmax, n = 23), d) Seed mass (Seedmass, n = 36 and
+e) Rate of CO2 assimilation (Aarea, n = 24) reported from 112
 articles.
-The x abcissa represents the articles ID sorted by the average coefficient value r reported.
-Each bubble represents a r value, the diameter of the bubble is proportional to its weights in the meta-analysis (i.e.
-number of species used).
-The colors correspond to the stage for which the r values have been recorded: red points corresponds adult stage, orange points to saplings, and green points to juveniles.
+The x axis represents the article ID sorted by the average reported coefficient value r.
+Each bubble represents an r value, the diameter of the bubble is proportional to its weight in the meta-analysis (i.e.
+number of species).
+The colours correspond to the stage for which the r values have been recorded: red points correspond to adult stage, orange points to saplings, and blue points to seedlings.
 Results shown here are from the ``complete'' dataset (see methods for details).
@@
 \includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA4.pdf}
-\caption{\textbf{Mean coefficient correlation r (+SD) between growth and traits, measured by stage and by stage and growth type.} \textbf{a and f)} Specific leaf area (SLA), \textbf{b snd g)} Wood density (WD), \textbf{c and h)} Asymptotic maximum height (Hmax), \textbf{d and i)} Seed mass (Seedmass) and \textbf{e and j)} Rate of CO2 assimilation (Aarea).
-On graphs e to j, relative (RGR) and absolute (AGR) growth rates are set appart.
-The mean coefficients are weighted by sample size and established from 112 articles and.
-Results shown here are from the ''ideal dataset'' (see methods for details).
-''n'' indicates the number of correlation.}
+\caption{Mean coefficient correlation r (+SD) between growth and traits, measured by stage (a-e
+) and by stage and growth type (f-j).
+a and f) Specific leaf area (SLA), b and g) Wood density (WD), c and h) Asymptotic maximum height (Hmax), d and i) Seed mass (Seedmass) and e and j) Rate of CO2 assimilation (Aarea).
+On figures f to j, relative (RGR) and absolute (AGR) growth rates are set apart.
+The mean coefficients are weighted by sample size and established from 112 articles.
+Results shown here are from the ''ideal dataset'' (see methods for details), ''n'' indicates the number of correlations.}
 \label{fig:figA4}
@@
 \includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA5.pdf}
-\caption{\textbf{Effect size (+ 95\%CI) of plant stage on the correlations between growth rate and five functional traits across species, with a data set averaging multiple comparisons by trait and by study}.
-Effects size are calculated from a reduced dataset; in the case of multiple comparisons within a study, we calculated the mean correlation coefficient by trait and by study.
-\textbf{a)} Specific leaf area (SLA), \textbf{b)} Wood density (WD), \textbf{c)} Net assimilation rate (NARarea), \textbf{d)} Seed mass, \textbf{e)} Asymptotic maximum height (Hmax) and \textbf{f)} Assimilation rate of CO2 (Aarea).
+\caption{Effect size (+ 95\%CI) of plant stage on the correlations between growth rate and five functional traits across species, with a data set averaging multiple comparisons by trait and by study.
+In the case of multiple comparisons within a study, effect sizes were calculated using the mean correlation coefficient by trait and by study.
+a) Specific leaf area (SLA), b) Wood density (WD), c) Asymptotic maximum height (Hmax) , d) Seed mass and e) Assimilation rate of CO2 (Aarea).
 Effect size is a standardized measure of the magnitude of the relationship between a particular stage and the correlation coefficient z (Fisher's z-transformed).
@@
 \includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA6c.pdf}
-\caption{\textbf{Effects size on the correlation between growth and traits of plant stage (mod1), vegetation type (mod2), growth measurement (mod3) and experiment type (mod4).} \textbf{a)} Specific leaf area (SLA), \textbf{b)} Wood density (WD), \textbf{c)} Net assimilation rate (NARarea), \textbf{d)} Seed mass, \textbf{e)} Asymptotic maximum height (Hmax) and \textbf{f)} Assimilation rate of CO2 (Aarea).
+\caption{Effects size on the correlation between growth and traits of plant stage (mod1), growth measurement (mod2), vegetation type (mod3),  and experiment type (mod4).
+a) Specific leaf area (SLA), b) Wood density (WD),c) Assimilation rate of CO2 (Aarea), d) Seed mass, and e) Asymptotic maximum height (Hmax).
 The effect size (z + 95\%CI) is reported for each class, and models are fitted by restricted max likelihood (REML).
-Abbreviation: across veg = more than 2 vegetation types, boreal\&temp = boreal and temperate deciduous forest, med = Mediterranean,  temp\&med = temperate deciduous and Mediterranean forests, temp = temperate deciduous, temp rain = temperate rain, trop rain = tropical rain, trop seas = tropical seasonal forests, GR = growth rate and RGR = relative growth rate, measured in diameter (D), height (H), mass(M), volume (V) and cross section area (CSA).
+Abbreviation: GR = growth rate and RGR = relative growth rate, measured in diameter (D), height (H), mass(M), cross section area (CSA) and volume (V), across GF: coefficient of correlation measured on tree in mixture with other growth form.
 AIC: Akaike information criterion corresponds to the quality of each model, and allow a comparison between models.
@@
 \includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA7.pdf}
-\caption{\textbf{Funnel plots with filled in data based on the trim and fill method}, showing transformed correlation coefficient z between growth and \textbf{a)} Specific leaf area (SLA), \textbf{b)} Wood density (WD), \textbf{c)} Net assimilation rate (NARarea), \textbf{d)} Seed mass, \textbf{e)} Asymptotic maximum height (Hmax) and \textbf{f)} Assimilation rate of CO2 (Aarea).
-Note that in these plots the y axis is the 1/number of species included in the correlation, not the replication for the correlation.
+\caption{Funnel plots with filled in data based on the trim and fill method, showing transformed correlation coefficient z between growth and a) Specific leaf area (SLA), b) Wood density (WD), c) Asymptotic maximum height (Hmax), d) Seed mass and e) Assimilation rate of CO2 (Aarea).
+Note that in these plots the y axis is 1/number of species included in the correlation, not the replication for the correlation.
 The open points correspond to the estimated missing studies.
 The number of missing values is 7 for SLA,1 for WD, 0 for Hmax, 6 for SM and 0 for Aarea.
-Results shown here are from the ''ideal'' dataset (see method for details).}
+Results shown here are from the ''ideal'' dataset (see methods for details).}
 \label{fig:figA7}
@@
 \includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA8.pdf}
-\caption{\textbf{Number of correlation extracted by traits, stage and growth type (absolute vs relative, and measurement).} \textbf{a)} Specific leaf area (SLA), \textbf{b)} Wood density (WD), \textbf{c)} Net assimilation rate (NARarea), \textbf{d)} Seed mass, \textbf{e)} Asymptotic maximum height (Hmax) and \textbf{f)} Assimilation rate of CO2 (Aarea).
-On the right side of each graph are the absolute growth rates (AGR), on the left side the relative growth rate (RGR).
+\caption{Number of correlation extracted by traits, stage and growth type (absolute vs relative, and measurement).
+a) Specific leaf area (SLA), b) Wood density (WD), c) Asymptotic maximum height (Hmax), d) Seed mass and e) Assimilation rate of CO2 (Aarea).
+Absolute growth rate (AGR) is on the left and relative growth rate (RGR) on the right of each plot.
 Results shown here are from the ``complete'' dataset (see methods for details).
@@
 \includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA9.pdf}
-\caption{\textbf{Temporal changes in coefficient of correlation between growth and traits}.
-\textbf{a)} Specific leaf area (SLA), \textbf{b)} Wood density (WD), \textbf{c)} Net assimilation rate (NARarea), \textbf{d)} Seed mass, \textbf{e)} Asymptotic maximum height (Hmax) and \textbf{f)} Assimilation rate of CO2 (Aarea).
-The colours correspond to the stage for which the r values have been recorded: red points corresponds adult stage, orange points to saplings, and grey points to juveniles.
+\caption{Temporal changes in coefficient of correlation between growth and traits.
+a) Specific leaf area (SLA), b) Wood density (WD), c) Asymptotic maximum height (Hmax), d) Seed mass, and e) Assimilation rate of CO2 (Aarea).
+The colours correspond to the stage for which the r values have been recorded: red points corresponds to adult stage, orange points to saplings, and grey points to seedlings.
 Results shown here are from the ``ideal'' dataset (see methods for details).}
@@
 
-\textbf{Goal:} In our meta-analysis, studies reported differed in design as well as in vegetation types, biome or species studied.
-Such diversity is commonly referred as methodological heterogeneity, and may or may not be responsible for observed discrepancies in the results of the studies.
-The extent of heterogeneity might influence the results of the meta-analysis, and then induces some difficulty in drawing overall conclusions (See \citealt{Higgins:2002iq}).
+\textbf{Goal:} In our meta-analysis, reported studies differed in design as well as in vegetation type, biome or species studied.
+Such diversity is commonly referred to as methodological heterogeneity, and may or may not be responsible for observed discrepancies in the results of the studies.
+The extent of heterogeneity might influence the results of the meta-analysis, and thus induce some difficulty in drawing overall conclusions (See \citealt{Higgins:2002iq}).
 It is therefore important to be able to quantify the extent of heterogeneity among a collection of studies.
@@
 These suggestions are tentative; the interpretation of heterogeneity in a systematic review will depend critically on the size and direction of treatment effects, as well as on considerations of methodological diversity in the studies (see \citealt{Borenstein:2009um}).
-Here, we estimated $I^{2}$ as following equation from \citealt{Higgins:2002iq}, then we calculated how part of the heterogeneity may be due to the influence of moderators (stage and publication year) and finally we asked if the residual heterogeneity is statistically significant.
-In R, we used the package metafor (code available on guithub).
+Here, we estimated $I^{2}$ as following equation from \citealt{Higgins:2002iq}, then we calculated how part of the heterogeneity may be due to the influence of moderators (stage and publication year) and finally we asked if the residual heterogeneity was statistically significant.
+In R, we used the package metafor (code available on github).
 
@@
 
-For SLA and SM, 50.1\% and 20\% respectively of the total amount of heterogeneity were accounted by including the stage as a moderator.
-For the other traits, the stage explained few or no part of the heterogeneity observed across studies ($<$5\%).
-These results were consistent with our expectations about a shift in the relationship between growth and traits along plant size for SLA, SM and the absence of effect for WD and Aarea (see Theoretical expectation section).
-The result of Hmax was more ambiguous since we expected the relationship between Hmax and growth rate to be absent in seedlings but to strengthen with increasing plant size (at adult stage).
-As discussed in the result section of the article, the smaller numbers of replicate studies for sapling and seedling stage limited the generality of our conclusion for this trait.
+For SLA and SM, 50.1\% and 20\% respectively of the total amount of heterogeneity were accounted for by including the stage as a moderator.
+For the other traits, the stage explained little or no part of the heterogeneity observed across studies ($<$5\%).
+These results were consistent with our expectations about a shift in the relationship between growth and traits across plant size for SLA and SM, and the absence of an effect for WD and Aarea (see Theoretical expectation section).
+The result for Hmax was more ambiguous since we expected the relationship between Hmax and growth rate to be absent in seedlings but to strengthen with increasing plant size (at adult stage).
+As discussed in the results section of the article, the smaller number of replicate studies for sapling and seedling stage limited the generality of our conclusion for this trait.
 
-The test for residual heterogeneity was significant for all traits, possibly indicating that others moderators not considered in the model were influencing the correlation between growth and trait.
-This result is not surprising for the trait literature.
-While the trait and growth measurements are standardized \citep{Cornelissen:2003gw}, studies differed largely in their design as well as in vegetation types, biome or species studied.
-Indeed, a goal in the trait literature is to establish general pattern about correlation between growth and traits and to validate them across a large variation of conditions.
-Here, we did not explore the influence of other moderators, since our goal was to test clear hypotheses about the influence of plant size/stage, not to establish the best predictor of the correlation between growth and trait.
+The test for residual heterogeneity was significant for all traits, possibly indicating that other moderators not considered in the model were influencing the correlation between growth and traits.
+This is not surprising because although the trait and growth measurements are standardized \citep{Cornelissen:2003gw}, studies differed in their design as well as in vegetation type, biome and species studied.
+Indeed, a goal in the trait literature is to establish general patterns of correlation between growth and traits and to validate them across a large variety of conditions.
+Here, we did not explore the influence of other moderators, since our goal was to test clear hypotheses about the influence of plant size/stage, not to establish the best predictor of the correlation between growth and traits.
 Finally, since between study variation is significant, as indicated by heterogeneity analyses, the use of the random effect model was appropriate in our meta-analysis.
@@
 A publication bias occurs when the probability of publication depends on the statistical significance of the effect.
-Here we tested if there is an evidence of any bias, and if the effect size observed for each trait is an artefact of this bias.
+Here we tested if there is evidence of any bias, and if the effect size observed for each trait is an artefact of this bias.
 
-\textbf{Method:} We first checked the dataset for publication bias with a visual assessment of funnel plots.
+\textbf{Method:} Initially, we checked the dataset for publication bias with a visual assessment of funnel plots.
 A publication bias toward significant results creates an asymmetric funnel with small studies with non-significant effects missing from the mouth of the funnel on the side opposite to the true effect.
-While funnel plot are recommended to aid interpretation, there is a high risk failing to detect actual publication bias (see \citealt{Koricheva:2013tz}) by using exclusively a visual assessment.
+While funnel plot are recommended to aid interpretation, there is a high risk of failing to detect actual publication bias (see \citealt{Koricheva:2013tz}) by using an exclusively visual assessment.
 In addition, funnel plots are not effective when the number of studies is small ($<30$) such as for Aarea and SM.
-We also used the ''trim and fill'' method to estimate the number of studies missing from our meta-analyse. This method adjusts for funnel plot asymmetry \citep{Duval:2000dg}.
-Finally, we estimated the number of studies needed to overturn a result, using the Rosenberg’s fail-safe number \citep{Rosenberg:2005hk}.
+Next, we used the ''trim and fill'' method to estimate the number of studies missing from our meta-analysis. This method adjusts for funnel plot asymmetry \citep{Duval:2000dg}.
+Finally, we estimated the number of studies needed to overturn a result, using Rosenberg’s fail-safe number \citep{Rosenberg:2005hk}.
 The fail-safe N is not based on funnel plot asymmetry.
-The Rosenberg method calculates the number of studies averaging null results that would have to be added to the given set of observed outcomes to reduce significance level (p-value) of the weighted average effect \citep{Rosenberg:2005hk}.
-A significant meta-analytic result is robust if the fail-safe N is greater than 5k+10, where k is the number or studies already in the meta-analysis \citep{Rosenthal:1979do}.
-In R, we used the package `metafor` (code available on guithub).
+The Rosenberg method calculates the number of studies averaging null results that would have to be added to the given set of observed outcomes to reduce the significance level (p-value) of the weighted average effect \citep{Rosenberg:2005hk}.
+A significant meta-analytic result is robust if the fail-safe N is greater than 5k+10, where k is the number of studies already in the meta-analysis \citep{Rosenthal:1979do}.
+In R, we used the package `metafor` (code available on github).
 
-\textbf{Result:} As expected the correlation coefficient varied less widely as sample size increased (funnel plots in Fig.
+\textbf{Result:} As expected the correlation coefficient varied less as sample size increased (funnel plots in Fig.
 \ref{fig:figA9}).
-Funnel plots exhibited a typical funnel shape for all five functional traits analyzed, showing no evidence for publication bias (Fig.
+Funnel plots exhibited a typical funnel shape for all five functional traits analysed, showing no evidence for publication bias (Fig.
 \ref{fig:figA9}).
@@
 The overall estimates measured with the fill in data changed from $0.5 \pm 0.07$  to $0.4 \pm 0.07$ for SLA and from $-0.48 \pm 0.11$ to $-0.32 \pm 0.12$ for the seed mass, suggesting a lower correlation coefficient for SLA, and SM.
-Even if the estimated correlation were closest from zero with the missing studied filled in, the results still indicate that the effect is statistically significant.
-The Rosenberg’s Fail-safe N are 7086, 1823, 990, 574, 291 for SLA, WD, Hmax, Seedmass and A area, suggesting that there would need to be over a large number of studies with a mean correlation coefficient of 0 added to the analysis before the cumulative correlation would become non significant.
-N is greater than 5k+10 for all traits.
-All together these result suggest that the impact of bias is probably trivial in our meta-analyses.
+Even although the estimated correlations were closer to zero with the missing studies filled in, the results still indicate that the effect is statistically significant.
+The Rosenberg’s Fail-safe (N) were 7086, 1823, 990, 574, 291 for SLA, WD, Hmax, Seedmass and Aarea, suggesting that a large number of studies with a mean correlation coefficient of 0 need to be added to the analysis before the cumulative correlation would become non-significant.
+N was greater than 5k+10 for all traits.
+These results suggest that the impact of publication bias is probably trivial in our meta-analyses.
 
@@
 \textbf{Goal:} Our meta-analysis combines data from studies published between 1983 and 2014.
-It has been shown that the magnitude of the effect size may changes over time due to a publication bias (i.e.
+It has been shown that the magnitude of the effect size may change over time due to a publication bias (i.e.
 a lag to publish negative results), a change in the methodology or biological changes in the magnitude of the effect (see \citealt{Koricheva:2013hy}).
@@
 \textbf{Method:} In the trait literature the year of publication may be confounded with a methodological change.
-Indeed, in the early 90’s studies mainly focused on seedlings, whereas today a broader range of plant size/stage are studied (Fig.
+Indeed, in the early 90’s studies mainly focused on seedlings, whereas today a broader range of plant sizes/stages are studied (Fig.
 \ref{fig:figA9}).
@@
 The Fig.
-\ref{fig:figA9} showed that for these 3 traits the publication years may be confounded with plant stage; the correlation coefficients have been reported from 1993, but studies started to report data on adult stage only 10 years later (around 2000-2007).
+\ref{fig:figA9} shows that for these three traits the publication years may be confounded with plant stage; correlation coefficients have been reported since 1993, but studies started to report data on adult stage only ten years later (around 2000-2007).
 
@@
 This pattern is classic in meta-analyses; \citealt{Koricheva:2013hy} showed that a majority of studies reported a decrease rather than an increase in the magnitude of effect size with publication year.
-Yet, here this effect did not lead to a loss of the statistical significance of the main effect size or to a change of sign.
-While overestimated, the main effect size for the correlation between growth and Aarea stay positive (Fig.
+Yet, here this effect did not lead to a reduction in statistical significance of the main effect size or to a change of sign.
+While overestimated, the main effect size for the correlation between growth and Aarea stays positive (Fig.
 \ref{fig:figA9} e).
 
-The temporal change were confounded with a plant stage effect in our meta-analyse, but they did not jeopardizing the stability of our conclusions.
-The conclusions of a meta-analyses conducted in different years may not differ from the one reported here.
+The temporal changes were confounded with a plant stage effect in our meta-analysis, but they did not jeopardize the stability of our conclusions.
+The conclusions of a meta-analysis conducted in different years should not differ from those reported here.
 

### 2015-09-28 R/data_processing.R

@@ -90,8 +90,11 @@ clean_raw_data <- function(filename = "data/CompileData.csv") {
   Table$stageRGR[Table$RGR.stage == "juveniladult"] <- "mix"
 
 
-  Table$stage <- factor(Table$stage, levels = c("juvenile", "sapling", "adult"))
+  # Table$stage[Table$stageRGR == "juvenile" & Table$ ] <- "seedling"
   Table$stage <- as.factor(Table$stage)
+  Table$stage <- factor(Table$stage, levels = c("seedling", "juvenile", "sapling", "adult","mix"))
+  Table$stage <- replace(Table$stage, Table$stage == "juvenile", "seedling")
+  Table$stage <- factor(Table$stage, levels = c("seedling", "sapling", "adult"))
 
 
   ##### less restrictive, all experiments using data from database in parallel of
@@ -272,7 +275,7 @@ build_ideal_data <- function(CompleteData) {
 
   IdealData <- subset(CompleteData, CompleteData$stress == "unstressed" & CompleteData$bio.scale ==
     "intersp" & CompleteData$similarity == "Sim")
-  IdealData$stage <- factor(IdealData$stage, levels = c("juvenile", "sapling",
+  IdealData$stage <- factor(IdealData$stage, levels = c("seedling", "sapling",
     "adult"))
   IdealData$stageTrait <- factor(IdealData$stageTrait, levels = c("seedling",
     "juvenile", "sapling", "adult", "mix"))

### 2015-09-28 R/figures.R

@@ -62,7 +62,7 @@ figure_2 <- function(CompleteData_inter) {
 
     n <- nrow(data)
     y <- rev(seq_len(n))
-    cols <- c("#538936", "#73005C", "#F57C34", "#E6224C", "grey")[data$stageRGR]
+    cols <- c("#13519E", "#73005C", "#F57C34", "#E6224C", "grey")[data$stageRGR]
     plot(NA, xlim = c(0, 3), ylim = c(0, n), yaxt = "n", xaxt = "n", xlab = "",
       ylab = "")
     mtext(xlab, 1, line = 2, cex = 0.75)
@@ -83,15 +83,15 @@ figure_2 <- function(CompleteData_inter) {
   }
 
   plotCI2(sa, c(0, 1, 5, 10), "age (yrs)")
-  abline(v = 1, col = "#538936")
+  abline(v = 1, col = "#13519E")
   legend(2.38, 40, c("seedling", "juvenile", "sapling", "adult", "mix", "across growth form",
-    "reassignment"), lwd = c(1, 1, 1, 1, 1, NA, NA), col = c("#538936", "#73005C",
+    "reassignment"), lwd = c(1, 1, 1, 1, 1, NA, NA), col = c("#13519E", "#73005C",
     "#F57C34", "#E6224C", "grey", "grey", "black"), pch = c(NA, NA, NA, NA,
     NA,"+", "*"), bty = "n", x.intersp = 0.3, y.intersp = 1, seg.len = 0.5,
     cex = 1)
 
   plotCI2(sh, c(0, 0.5, 2, 20), "height (m)")
-  abline(v = 1, col = "#538936")
+  abline(v = 1, col = "#13519E")
 
   plotCI2(sd, c(0, 1, 10, 80), "diameter (cm)")
   abline(v = 2, col = "#E6224C")
@@ -205,8 +205,8 @@ figure_A1 <- function() {
     plot(data[[px$var]], data[[py$var]], log = "xy", xlim = px$lim, ylim = py$lim,
       xlab = px$lab, ylab = py$lab, col = adjustcolor("#00000033", alpha = 0.5),
       pch = 16)
-    abline(v = px$sap, col = "#93EA6D", lty = 5)
-    abline(h = py$sap, col = "#93EA6D", lty = 5)
+    abline(v = px$sap, col = "#13519E", lty = 5)
+    abline(h = py$sap, col = "#13519E", lty = 5)
[…]

### 2015-09-28 R/model.R

@@ -72,13 +72,13 @@ fun_model <- function(x, y) {
     CoefModel[j, 6] <- CoefModel[j, 4] * 1.96 - CoefModel[j, 3]
   }
 
-  CoefModel$stage[CoefModel$stage == "stagejuvenile"] <- "juvenile"
+  CoefModel$stage[CoefModel$stage == "stageseedling"] <- "seedling"
   CoefModel$stage[CoefModel$stage == "stagesapling"] <- "sapling"
   CoefModel$stage[CoefModel$stage == "stageadult"] <- "adult"
 
 
   fun1 <- function(z) length(na.omit(z$corr.z))
-  fun2 <- function(z) length(na.omit(z$corr.z[z$stage == "juvenile"]))
+  fun2 <- function(z) length(na.omit(z$corr.z[z$stage == "seedling"]))
   fun5 <- function(z) length(na.omit(z$corr.z[z$stage == "sapling"]))
   fun3 <- function(z) length(na.omit(z$corr.z[z$stage == "adult"]))
 
@@ -87,8 +87,8 @@ fun_model <- function(x, y) {
 
   CoefModel["N"] <- "NA"
   # CoefModel['N'] <- N[!(apply(N, 1, function(s) any(s == 0))),]
-  CoefModel$N[CoefModel$stage == "juvenile" & CoefModel$stress == "ideal"] <- fun2(x)
-  CoefModel$N[CoefModel$stage == "juvenile" & CoefModel$stress == "complete"] <- fun2(y)
+  CoefModel$N[CoefModel$stage == "seedling" & CoefModel$stress == "ideal"] <- fun2(x)
+  CoefModel$N[CoefModel$stage == "seedling" & CoefModel$stress == "complete"] <- fun2(y)
 
   CoefModel$N[CoefModel$stage == "sapling" & CoefModel$stress == "ideal"] <- fun5(x)
   CoefModel$N[CoefModel$stage == "sapling" & CoefModel$stress == "complete"] <- fun5(y)
@@ -144,13 +144,13 @@ fun_model2 <- function(x) {
     CoefModel[i, 6] <- CoefModel[i, 4] * 1.96 - CoefModel[i, 3]
   }
 
-  CoefModel$stage[CoefModel$stage == "stagejuvenile"] <- "juvenile"
+  CoefModel$stage[CoefModel$stage == "stageseedling"] <- "seedling"
   CoefModel$stage[CoefModel$stage == "stagesapling"] <- "sapling"
[…]

### 2015-09-28 R/plots.R

@@ -10,9 +10,9 @@ my_plot_1 <- function(title, ggobj, xlab = expression(paste("")), ylab = "Number
   p <- ggobj + geom_bar(alpha = 0.95) + coord_cartesian(ylim = ylim) + coord_flip() +
     labs(title = title) + xlab(xlab) + ylab(ylab) + scale_x_discrete() + theme(text = element_text(size = 9),
     axis.text.x = element_text(size = 9, angle = 0, vjust = 1)) + mytheme +
-    theme(axis.title = element_text(size = 10, hjust = 0.5)) + scale_fill_manual(values = c(juvenile = "#538936",
-    sapling = "#F57C34", adult = "#E6224C"), breaks = c("juvenile", "sapling",
-    "adult"), labels = c("juvenile", "sapling", "adult"))
+    theme(axis.title = element_text(size = 10, hjust = 0.5)) + scale_fill_manual(values = c(seedling = "#13519E",
+    sapling = "#F57C34", adult = "#E6224C"), breaks = c("seedling", "sapling",
+    "adult"), labels = c("seedling", "sapling", "adult"))
   p
 
 }
@@ -29,7 +29,7 @@ coeff.plot.2 <- function(data, data.complete, data.ideal, LRT, PVAL, title = "",
     ylab = "Stages") {
     p <- ggobj + labs(title = title) + xlab(xlab) + ylab(ylab) + geom_vline(yintercept = 0,
       color = "white") + geom_hline(yintercept = 0, size = 0.3, linetype = "dashed") +
-      scale_x_discrete("stage", limit = c("seedling", "juvenile", "sapling",
+      scale_x_discrete("stage", limit = c("seedling", "seedling", "sapling",
         "adult", "mix")) + coord_flip() + mytheme + theme(legend.position = "none")
     p
   }
@@ -65,7 +65,7 @@ coeff.plot <- function(data, data.complete, data.ideal, LRT, PVAL, title = "",
 
     p <- ggobj + labs(title = title) + xlab(xlab) + ylab(ylab) + geom_vline(yintercept = 0,
       color = "white") + geom_hline(yintercept = 0, size = 0.3, linetype = "dashed") +
-      scale_x_discrete("stage", limit = c("juvenile", "sapling", "adult")) +
+      scale_x_discrete("stage", limit = c("seedling", "sapling", "adult")) +
       coord_flip() + mytheme + theme(legend.position = "none")
     p
   }
[…]

### 2015-09-28 CL.tex
Cover letter + changes in the starred literature

\documentclass{letter}
\usepackage{hyperref}
\signature{Anais Gibert on behalf of all authors}
\address{Biological Sciences\\ Macquarie University \\ NSW 2109, Australia}
\begin{document}

\begin{letter}{Editor-in-Chief Journal of Ecology}
\opening{Dear Dr David J. Gibson,}

May we please submit for Journal of Ecology a manuscript titled ``On the link between functional traits and growth rate: meta-analysis shows effects change with plant size, as predicted``. We would be grateful if you would consider it for publication.

May we please drawn your attention on the literature cited? We strongly believe that authors whose data publications enter into meta-analyses deserve to get credit via citation. In the current draft, these citations are in the main list of Literature Cited --as starred references-- increasing substantially it length. We hope it may no affect the review process. Maybe do you have another solution to situations of this kind?

\textbf{Novelty statement:}
In a nutshell, this paper sorts out the differences across plant species in potential growth rates. We believe it's a very substantial advance. Growth rates are obviously really important for ecology. They have been seen as a core element of plant ecological strategies going back to Grime and Hunt 1975. Over the past 20 years much ecological strategy research has shifted into "trait ecology", using traits such as SLA and wood density and seed mass as indicators of ecological strategy. Yet empirical reports of the correlations between traits and growth rates have been inconsistent. Our manuscript first spells out reasons why traits should influence growth differently depending what size the individual plant has achieved -- in other words, traits should influence growth trajectories rather than simply making species fast-growing versus slow-growing throughout life. Then second, we provide meta-analysis of correlations that have been reported between traits and growth rate. To the extent data are available, these correlations are shown to shift depending on plant size consistently with the reasons explained and the predictions made in the first part of the paper.

We are excited by this work and look forward to your evaluation of the paper.

\closing{Sincerely}

\end{letter}
\end{document}

### 2015-09-28 MS.tex
Cover letter + changes in the starred literature

@@
 \textasteriskcentered Email for correspondence: \texttt{anais.gibert@gmail.com}\\
-Word count: ~XXXX words}
+Word count: ~5538 words (without supplementary material, Fig and ref)}
 \date{}
@@
 \linenumbers
-\section{Summary 274/350}\label{abstract}
+\section{Summary 232/350}\label{abstract}
 \begin{enumerate}
@@
 \item Synthesis: We show how trait-GR correlations change in a predictable way with plant size.
-These  Our understanding of plant strategies should shift away from attributing species as having slow or fast GR throughout their life, in favour of attributing growth trajectories.
+Our understanding of plant strategies should shift away from attributing species as having slow or fast GR throughout their life, in favour of attributing growth trajectories.
 
@@
 Several authors have suggested that the disappearance of SLA's influence on growth might be due to a disproportionate accumulation of leaf area by low SLA species \citep{Reich:1992wm,Poorter:2008iu,Wright:2010tp}, yet it remains unclear whether such a mechanism works as intended.
-Further, the assumed empirical relationship between SLA and total leaf area does not hold true as a generalisation across large number of species (Duursma and Falster, in review).
+Further, the assumed empirical relationship between SLA and total leaf area does not hold true as a generalisation across large number of species (\citeauthor{Duursma-2015}, in review).
 In the model described here, the mechanism is slightly different: high-SLA species incur faster leaf turnover, the cost of which outweighs the benefits of cheap leaf construction at larger sizes.
@@
 Charles Warren and Jordi Martìnez-Vilalta kindly provided additional information about their published results.
-This work was funded by the Australian Research Council through a fellowship to MW, a discovery grant to DF and a Macquarie University Research Fellowships to EG.
+This work was funded by the Australian Research Council through a fellowship to M.W, a discovery grant to D.S.F and a Macquarie University Research Fellowships to E.F.G.
 
@@
 "*" indicated when a stage reassignment is needed.
-"+" on left side of the graph indicate cases where plants had different growth form.
+"+" on left side of the graph indicate cases where plants came from different growth form.
 Results shown here are the ''complete'' dataset (see methods for details).}

### 2015-11-23 MS.tex
Change main result to RGR exclusively analyses: Fig 3RGR, Fig4 all growth ms: rewrite the result part

@@
 \linenumbers
-\section{Summary 232/350}\label{abstract}
+\section{Summary 235/350}\label{abstract}
 \begin{enumerate}
@@
 \itemsep1pt\parskip0pt\parsep0pt
-\item A plant's growth rate (GR) has often been seen as a central element of its ecological strategy, and as ultimately linked to its traits.
-Yet the literature is inconsistent about the empirical correlation between functional traits and GR, casting doubt on the capacity of traits to predict growth.
+\item A plant's growth rate has often been seen as a central element of its ecological strategy, and as ultimately linked to its traits.
+Yet the literature is inconsistent about the empirical correlation between functional traits and growth, casting doubt on the capacity of traits to predict growth.
 
@@
 \item Results were consistent with predictions.
-Specific leaf area was correlated with GR in seedling but not in adult plants.
-Correlations of GR with wood density and assimilation rate were not affected by stage.
-Seed mass and maximum height were correlated with GR only in one plant stage category: seedlings and adults, respectively.
+Specific leaf area was correlated with relative growth rate (RGR) in seedling but not in adult plants.
+Correlations of RGR with wood density and assimilation rate were not affected by stage.
+Seed mass and maximum height were correlated with RGR only in one plant stage category: seedlings and adults, respectively.
 
-\item Synthesis: We show how trait-GR correlations change in a predictable way with plant size.
+\item Synthesis: We show how trait-growth correlations change in a predictable way with plant size.
 Our understanding of plant strategies should shift away from attributing species as having slow or fast GR throughout their life, in favour of attributing growth trajectories.
@@
 While recent empirical studies supported the idea of a variation in the relationships between traits and growth rates across plant sizes (\citealt{Iida:2014ep, Iida:2014hq}), the trend and mechanisms behind this variation remain unclear.
-Moreover, the question whether the influence of traits on growth changes with plant size in a predictable and consistent way is very much open.
 
@@
 
-For both SLA and SM, the correlation between growth rate and the trait changed significantly with plant size in the manner expected.
-Model fits improved when stage was incorporated (see log likelihood ratio tests, Fig.
-\ref{fig:fig3} a and d; average values for the coefficients ($\bar{r}$) in Fig.
+For SLA the correlation between RGR and the trait changed significantly with plant size in the manner expected.
+Model fit improved when stage was incorporated (see log likelihood ratio tests, Fig.
+\ref{fig:fig3} a; average values for the coefficients ($\bar{r}$) in Fig.
 \ref{fig:figA4} a-e).
-The correlation between growth and SLA shifted from strongly positive at seedling stage $\bar{r}=0.6 \pm 0.08$, Mean $\pm$ SD) to not significantly different from zero at adult stage ($\bar{r}= -0.01 \pm 0.07$, CI 95\% overlapping zero in Fig.
+The correlation between RGR and SLA shifted from strongly positive at seedling stage $\bar{r}=0.6 \pm 0.08$, Mean $\pm$ SD) to not significantly different from zero at adult stage ($\bar{r}= -0.01 \pm 0.07$, CI 95\% overlapping zero in Fig.
 \ref{fig:fig3} a).
-The correlation between growth and SM shifted from negative at seedling stage ($\bar{r}= -0.5 \pm 0.07$) to not significantly different from zero at adult stage ($\bar{r}= -0.09 \pm 0.02$, , CI 95\% overlapping zero in Fig.
-\ref{fig:fig3} d).
-For both traits, correlation coefficients recorded at sapling stage were intermediate between seedling and adult stages.
-The relationship between growth and SM in seedlings is expected to differ if absolute GR in mass is used instead of RGR mass.
-Here, for SM growth in mass was exclusively expressed in relative terms for seedlings (results shown in the Fig.
-\ref{fig:figA8} and Fig \ref{fig:figA4} f-j)
+The correlation coefficients recorded at sapling stage were intermediate between seedling and adult stages.
 
-For WD, Hmax and Aarea, correlations with growth were also consistent with expectations, although with limitations arising from very unequal numbers of observations between growth stages for some traits.
-For Hmax, the expectation was for a correlation with growth to be absent for small plants but present at intermediate and larger sizes, the mechanism being increased relative allocation to reproduction as Hmax is approached.
+For WD, results were consistent with negative correlations with RGR across all plant sizes (Fig.
+\ref{fig:fig3} b, model fit not improved when stage was incorporated).
+Note that the confident intervals were not crossing zero for sapling and seedling stage despite small sample sizes (n= 4 and 2 respectively), meaning a good consistency in the coefficient reported for each stage across studies.
+
+For both Hmax and seed mass, correlations with RGR were also consistent with expectations, although with limitations arising from very unequal numbers of observations between growth stages for some traits.
+Indeed, confidence intervals of r often spanned zero especially where there were small numbers of studies for particular growth stages, precluding strong conclusions.
+For Hmax, the expectation was for a correlation with growth to be absent for small plants but present at larger sizes, the mechanism being increased relative allocation to reproduction as Hmax is approached.
 Indeed Hmax was positively correlated with growth at adult stage ($\bar{r}= 0.38 \pm 0.05$).
-At sapling and seedling stages, the correlation between Hmax and growth was not significantly different from that observed at adult stage (model fit not improved when stage was incorporated, see log likelihood ratio tests in Fig.
-\ref{fig:fig3} c), but also was consistent with no correlation (Fig \ref{fig:fig3} c, confidence intervals overlapping zero), due to much smaller numbers of replicate studies.
+At sapling stages, the correlation between Hmax and growth was not significantly different from that observed at adult stage (model fit not improved when stage was incorporated, see log likelihood ratio tests in Fig.
+\ref{fig:fig3} c, and confident intervals overlapping), but also was consistent with no correlation (Fig \ref{fig:fig3} c, confidence intervals overlapping zero), due to much smaller numbers of replicate studies.
 We could not distinguish between these alternatives.
-Similarly for WD and for Aarea, results were consistent with negative (WD) and positive (Aarea) correlations with growth across all plant sizes (Fig.
-\ref{fig:fig3} b and e, model fit not improved when stage was incorporated).
-However, at the same time confidence intervals of r often spanned zero especially where there were small numbers of studies for particular growth stages.
+As expected for seed mass, the correlation with RGR shifted from negative at seedling stage ($\bar{r}= -0.5 \pm 0.07$) to not significantly different from zero at adult and sapling stages (Fig \ref{fig:fig3} c, confidence intervals overlapping zero).
+Hovever, the correlation between seed mass and RGR at adult and saling stages were also not significantly different from that observed at seedling stage (see log likelihood ratio tests and confident intervals overlapping in Fig.
+\ref{fig:fig3} c).
+Again we could not distinguish between these alternatives.
+But unlike Hmax, the number of coefficent reported for seed mass was almost similar between adult (n= 7) and seedling (n= 10) stages, suggesting that confident interval overalapping zero at adult stage were due to variation in coefficients of correlation reported rather than to a much smaller numbers of replicate.
+
+For Aarea, results were consistent with a positive correlation with RGR at seedling stage.
+However, no conclusion can be drawn about a change along plant stages; only four correlation coefficients were reported for this trait, and three of them were measured at the seedling stage.
 
@@
 
-Given our basic conclusion that reported correlations responded to plant size in a manner consistent with expectations from theory, we assess now the coverage of the available data, to determine if biased sampling could have erroneously generated the above results.
+Given our basic conclusion that reported correlations responded to plant size in a manner consistent with expectations from theory, we assess now the coverage of the available data, to determine if biased sampling could have erroneously generated the above results, or if additional data could reinforce some of our conclusions.
 
-In total, we found 112 studies published between between 1983 and 2014 that met our requirements.
+In total, we found only 112 studies published between between 1983 and 2014 that met our requirements.
 Climate zones spanned from temperate regions to tropics (map in Fig.
@@
 
-The results reported above were obtained using the "ideal" dataset, and were thereby confined to correlations across species, and under non-stressed conditions ($n = 176$).
-The ``complete'' dataset ($n = 216$) also included correlations measured under stressed conditions, and spanning different plant stages between the growth and trait measurements.
-This ``complete'' dataset generated similar effect sizes to those reported above from the ``ideal'' dataset, and led to similar conclusions (Fig.
-\ref{fig:fig3} grey points).
-Differences primarily concerned the confidence intervals around particular mean effect sizes in Fig.
-\ref{fig:fig3}.
-These differences in CI may have arisen from a variety of causes.
-For instance, the correlation between growth and WD at seedling stage shifted from negative to non significant (i.e CI 95\% included zero) due to 2 positive correlation coefficients from \citet{Augspurger:1984ct}; these correlations unlike others used values of WD from adult plants together with growth from seedlings.
-For Aarea, the comparison between complete and ideal data showed no signal of an effect of stress (here mainly low light) on the correlation with growth at seedling stage; the correlation was still positive between Aarea and growth even when 8 correlations measured under low light conditions were added.
+The results reported above were obtained using an even more conservative dataset ($n = 98$), and were thereby confined to correlations with RGR, across at least 10 species, under non-stressed conditions, and controlling for the source of trait and growth (i.e.
+both had to be measured on the same stage).
+The ''complete'' dataset ($n = 216$) also included correlations measured with absolute growth rate, across two to 10 species, under stressed conditions, and spanning different plant stages between the growth and trait measurements.
+The release of criteria enlarged in a considerable extent the number of replicates.
+While some trait-stage combinations were particularly well studied with 59 correlation coefficient reported for SLA at seedling stage, other still showed weak support.
+Indeed, on the 13 traits-stage combinations studied here, six were supported by five or less correlations coefficient (i.e.
+WD-seedling, Hmax-sapling, Hmax-seedling, Seed mass-sapling, Aarea-adult and Aarea-sapling).
+
+This ''complete'' dataset generated similar effect sizes to those reported above for SLA, WD and Hmax, and led to similar conclusions (Fig.
+\ref{fig:fig4}).
+While the correlation between growth and WD at seedling stage was still negative, the upper CI 95\% was very closed from zero (lower CI: -0.065) due to 2 positive correlation coefficients from \citet{Augspurger:1984ct}; these correlations unlike others used values of WD from adult plants together with growth from seedlings.
+
+For seed mass and Aarea, results from the ''complete'' dataset were even more consistent with expectations from the model.
+For seed mass, the correlation with RGR was undoubtly not significantly different from zero at adult stage (Fig \ref{fig:fig4}; CI for seedling and adult stages were not overlapping anymore, and model fit improved when stage was incorporated (see log likelihood ratio tests, Fig.
+\ref{fig:fig4 d}.
+For Aarea, results were consistent with expectation of positive correlations with RGR across adult and seedling stages (Fig \ref{fig:fig4} e; CI not overlapping zero).
+The comparison of effect size between conservative dataset (Fig.
+\ref{fig:fig3 d}) and complete (Fig.
+\ref{fig:fig4 d} showed no signal of an effect of stress (here mainly low light) on the correlation with growth at seedling stage; the correlation was still positive between Aarea and growth even when 8 correlations measured under low light conditions were added.
+
 Finally, our results were unlikely to be biased by dominance of one or a few studies that measured a large number of responses, since when multiple responses were condensed into a single average within a trait and within a study, outcomes were very similar (Fig.
@@
 In the growth model (Appendix \ref{sec:growth}), a consistent correlation irrespective of size arises from a direct effect of Aarea on plant growth rate.
-Meta-analyses showed a positive correlation for adult and seedling but not for saplings (n=2).
+Meta-analyses showed a positive correlation for adult and seedling but not for saplings (n=3).
 In the seedling stage, where most of data were available, we noted no signal of an effect of low light on the positive correlation between Aarea and growth rate.
@@
 Traits are: Aarea (or Amass) = rate of CO$_{2}$ assimilation per unit leaf area (or leaf mass) = maximum photosynthetic rate, Hmax = asymptotic maximum height,  Ks = stem hydraulic conductance, LA = leaf area, LMR = leaf mass ratio, NARarea = net mass assimilation rate per unit of leaf area, Nmass (or Narea) = nitrogen content per unit of leaf mass (or leaf area), Pmass = phosphorus content per unit of leaf mass, SA/LA = sapwood area per leaf area, SLA = specific leaf area, thickness = leaf thickness, Vessel size = stem conduit size, vessel density = stem conduit density, WD = wood density.
-Results shown here are the ``complete'' dataset (see methods for details).}
+Results shown here are the ''complete'' dataset (see methods for details).}
 \label{fig:fig1}
@@
 \includegraphics[width=15cm,height=20cm,keepaspectratio]{output/Fig3.pdf}
-\caption{The relationship between growth rates and traits changes with plant stage and trait.
+\caption{The relationship between relative growth rates (RGR) and traits changes with plant stage and trait.
 Plots show the effect size (+ 95\%CI) for the average correlation across species, by plant stage.
@@
 $n$ indicates number of correlations contributing to each effect.
-Likelihood Ratio Tests (LRT, for ``ideal'' dataset only) compared maximum-likelihood fits between a pooled model and one separated by stage.
+Likelihood Ratio Tests (LRT) compared maximum-likelihood fits between a pooled model and one separated by stage.
 A significant p-value means the model including stage effect fitted the data better than the null model.
-Results shown are from both the ``complete'' (black)  and ``ideal'' (grey) datasets (see methods for details).}
+Results shown are from correlation coefficients measured for RGR exclusively, with > 10 species, under unstressed conditions and for a controled trait source (see methods for details).}
+\label{fig:fig3}
+\end{figure}
+
+\begin{figure}[h!]
+\centering
+\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/Fig4.pdf}
+\caption{The relationships between growth rates and traits along plant stage are not overcasted by experimental conditions (i.e.
+growth measurement used, environemental conditions, trait source or number of species used to draw the correlation).
+Plots show the effect size (+ 95\%CI) for the average correlation across species, by plant stage.
+Effect size is a standardized measure of the deviation of correlation coefficient from zero (Fisher's z-transformed).
+Effects are significant if confidence intervals (95\%CI) for a given stage do not overlap with zero.
+Trait names as in Fig.
+\ref{fig:fig1}.
+$n$ indicates number of correlations contributing to each effect.
+Likelihood Ratio Tests (LRT) compared maximum-likelihood fits between a pooled model and one separated by stage.
+A significant p-value means the model including stage effect fitted the data better than the null model.
+Results shown are from the ''complete dataset'' (see methods for details).}
 \label{fig:fig3}

### 2015-11-23 R/data_processing.R

@@ -273,8 +273,8 @@ Build_intersp_complete_data <- function(RawData) {
 # perfomed at the same plant stage
 build_ideal_data <- function(CompleteData) {
 
-  IdealData <- subset(CompleteData, CompleteData$stress == "unstressed" & CompleteData$bio.scale ==
-    "intersp" & CompleteData$similarity == "Sim")
+  IdealData <- subset(CompleteData, CompleteData$stress == "unstressed" & CompleteData$nb.sp > 10
+     & CompleteData$similarity == "Sim")
   IdealData$stage <- factor(IdealData$stage, levels = c("seedling", "sapling",
     "adult"))
   IdealData$stageTrait <- factor(IdealData$stageTrait, levels = c("seedling",
@@ -294,10 +294,12 @@ EffectSizeSum <- function(data) {
     var <- (1/n)^2 * (sum(y)) + 2 * 1 * sqrt(z)
     var
   }
+  
+  data2 <- data[, c("corr.z", "id", "stage","trait", "vr.z", "nb.sp")]
 
-  res <- aggregate(corr.z ~ id + stage + trait, mean, data = na.omit(data))
-  res2 <- aggregate(vr.z ~ id + stage + trait, Fun_var, data = na.omit(data))
-  res3 <- aggregate(nb.sp ~ id + stage + trait, mean, data = na.omit(data))
+  res <- aggregate(corr.z ~ id + stage + trait, mean, data = na.omit(data2))
+  res2 <- aggregate(vr.z ~ id + stage + trait, Fun_var, data = na.omit(data2))
+  res3 <- aggregate(nb.sp ~ id + stage + trait, mean, data = na.omit(data2))
   table <- cbind(res, res2[, "vr.z"], res3[, "nb.sp"])
   colnames(table) <- c("id", "stage", "trait", "corr.z", "vr.z", "nb.sp")
   table

### 2015-11-23 R/figures.R

@@ -103,7 +103,7 @@ figure_2 <- function(CompleteData_inter) {
 }
 
 
-figure_3 <- function(GC, GI) {
+figure_3.3 <- function(GC, GI) {
   CoefModel.SLA <- fun_model(GI[["SLA"]], GC[["SLA"]])
   CoefModel.SLA["trait"] <- "SLA"
   CoefModel.SLA.s <- subset(CoefModel.SLA, stress == "complete")
@@ -264,6 +264,161 @@ figure_3.2 <- function(GCrgr , GCagr) {
   
   grid.arrange(p1, p2, p3, p4, p5, ncol = 2, nrow = 3, widths = c(1.2, 1))
 }
+
+
+figure_3 <- function(GIrgr) {
+  CoefModel.SLA <- fun_model2(GIrgr[["SLA"]])
+  CoefModel.SLA["trait"] <- "SLA"
+  LRT.sla <- fun_OneLR(GIrgr[["SLA"]])
+  PVAL.sla <- fun_Onepvalue(GIrgr[["SLA"]])
+
+  CoefModel.WD <- fun_model2( GIrgr[["WD"]])
+  CoefModel.WD["trait"] <- "WD"
+  LRT.wd <- fun_OneLR(GIrgr[["WD"]])
+  PVAL.wd <- fun_Onepvalue(GIrgr[["WD"]])
+  
+  
+  CoefModel.Hmax <- fun_model2(GIrgr[["Hmax"]])
+  CoefModel.Hmax["trait"] <- "Hmax"
+  LRT.hmax <- fun_OneLR(GIrgr[["Hmax"]])
+  PVAL.hmax <- fun_Onepvalue(GIrgr[["Hmax"]])
+  
+  
+  CoefModel.Seedmass <- fun_model2(GIrgr[["Seedmass"]])
+  CoefModel.Seedmass["trait"] <- "Seedmass"
+  LRT.sm <- fun_OneLR(GIrgr[["Seedmass"]])
+  PVAL.sm <- fun_Onepvalue(GIrgr[["Seedmass"]])
+  
+  CoefModel.Aarea <- fun_model2(GIrgr[["Aarea"]])
+  CoefModel.Aarea["trait"] <- "Aarea"
+  LRT.aarea<- fun_OneLR(GIrgr[["Aarea"]])
+  PVAL.aarea <- fun_Onepvalue(GIrgr[["Aarea"]])
+  
[…]

### 2015-11-23 R/plots.R

@@ -90,11 +90,41 @@ coeff.plot <- function(data, data.complete, data.ideal, LRT, PVAL, title = "",
 }
 
 
-coeff.plot.gr <- function(data, data.RGR, data.AGR, title = "",limit.x.min, limit.x.max, limit.x.text,
+coeff.plot.gr <- function(data, data.RGR, data.AGR, title = "",LRT, PVAL,round.value,significativite = "", limit.x.min, limit.x.max, limit.x.text,
                        limit.x.n, limit.y.text.l1, limit.y.text.l2, vjust.value, color1="#9E5F3A", color2="black") {
   
   data.RGR["x.coord"] <- limit.x.n
   data.AGR["x.coord"] <- limit.x.n
+  
+  plot1 <- function(title, ggobj, xlab = "Effect size + CI (95%) ", ylab = "Stages") {
+    
+    p <- ggobj + labs(title = title) + xlab(xlab) + ylab(ylab) +
+      geom_vline(yintercept = 0,color = "white") + geom_hline(yintercept = 0, size = 0.3, linetype = "dashed") +
+      scale_x_discrete("stage", limit = c("seedling", "sapling", "adult")) +
+      coord_flip() + mytheme + theme(legend.position = "none") 
+    p
+  }
+  
+  dodge <- position_dodge(width = 0.4)
+  
+  
+  
+  plot1(title, ggplot(data, aes(stage, Inte, ymin = Inte - 1.96 * SE, ymax = Inte +1.96 * SE, color = factor(growth)))) +
+    geom_point(aes(x = stage, y = Inte),position = dodge) + geom_errorbar(aes(x = stage, y = Inte), size = 0.4,width = 0.2, position = dodge) +
+    scale_y_continuous("Effect size (z) + CI 95%",limits = c(limit.x.min, limit.x.max)) +
+    geom_text(aes(stage,x.coord, label = paste("n=", N), color = factor(growth), group = "AGR"),size = 2, data = data.AGR, parse = F, position = "identity", vjust = +vjust.value, hjust = 0) + 
+    geom_text(aes(stage, x.coord, label = paste("n=",N), color = factor(growth), group = "RGR"), size = 2, data = data.RGR, parse = F, position = "identity", vjust = -vjust.value, hjust = 0) +
+    scale_color_manual(name = "", values=c(color1, color2), breaks = c("RGR", "AGR"), labels = c("RGR", "AGR"))+
[…]

### 2015-11-23 R/utils.R

@@ -78,3 +78,78 @@ rename <- function(data, replace, warn_missing = TRUE, warn_duplicated = TRUE) {
   }
   data
 }
+
+
+list_by_sym <- function(df) {
+  split(df, df$SymArd)
+}
+
+list_by_fert <- function(df) {
+  split(df, df$Fertilization)
+}
+
+
+
+
+
+simplefreq <- function (x,y=NULL,margin=1,html=NULL) {
+  if (is.null(y)) {simplefreq.tab<-cbind(data.frame(addmargins(
+    prop.table(table(x)))), 
+    data.frame(addmargins(table(x)))[2]) 
+  colnames(simplefreq.tab)<-c(deparse(substitute(x)),"Percentage","Count") 
+  RESTABLE<-simplefreq.tab 
+  
+  MINCHI2=NULL 
+  MINOR=NULL 
+  CHI2=NULL 
+  } 
+  if (!is.null(y)) { 
+    simplefreq.tab0<-table(x,y) 
+    simplefreq.chi<-chisq.test(simplefreq.tab0,
+                               correct=FALSE) 
+    if (margin==1) 
+    { 
+      simplefreq.tab<-cbind(addmargins(prop.table(
+        addmargins(simplefreq.tab0,1),1),2), 
+        rowSums(addmargins(simplefreq.tab0,1))) 
+      colnames(simplefreq.tab)<-c(colnames(simplefreq.tab0),"Total","Count") 
+      rownames(simplefreq.tab)<-c(rownames(simplefreq.tab0),"All") 
+    } 
+    if (margin==2) 
+    { 
+      simplefreq.tab<-rbind(addmargins(prop.table(
+        addmargins(simplefreq.tab0,2),2),1), 
+        t(colSums(addmargins(simplefreq.tab0,2)))) 
+      rownames(simplefreq.tab)<-c(rownames(simplefreq.tab0),"Total","Count") 
+      colnames(simplefreq.tab)<-c(colnames(simplefreq.tab0),"All") 
+    } 
+    RESTABLE<-simplefreq.tab 
+    CHI2<-simplefreq.chi 
+    
+    WARNING1 <- "Mining chi-square : what would be the chi-square if we were analyzing a 2*2 table. " 
+    WARNING2 <- "Sign is used for over (+) or under(-) representation." 
+    
+    MINCHI2<-sign(simplefreq.chi$observed-simplefreq.chi$expected)* 
[…]

### 2015-11-23 analysis.R

@@ -10,6 +10,9 @@ for (f in list.files("R", full.names = TRUE)) {
   source(f)
 }
 
+x <- readLines("data/CompileData.csv")
+writeLines(x, "data/CompileData.csv")
+
 CompileTable <- clean_raw_data()
 RawData <- standardise_data(CompileTable)
 
@@ -43,7 +46,7 @@ GCagr <- list_by_trait(CompleteData_agr)
 ## Create restricted Dataset: coefficient of correlation are averaged by study
 ## and by trait
 RCi <- list_by_trait(EffectSizeSum(CompleteData_inter))
-RIi <- list_by_trait(EffectSizeSum(IdealData_inter))
+RIi <- list_by_trait(EffectSizeSum(IdealData_rgr))
 
 ## output directory
 
@@ -61,13 +64,14 @@ pdf("output/Fig2.pdf", height = 8, width = 6)
 figure_2(CompleteData_inter)
 dev.off()
 
+
 pdf("output/Fig3.pdf", height = 6, width = 5)
-figure_3(GCi, GIi)
+figure_3(GIrgr)
 dev.off()
 
 
-pdf("output/Fig3.2.pdf", height = 6, width = 5)
-figure_3.2(GCrgr, GCagr)
+pdf("output/Fig4.pdf", height = 6, width = 5)
+figure_4(GCi)
 dev.off()
 
 
@@ -86,6 +90,10 @@ dev.off()
 
 pdf("output/FigA4.pdf", height = 7, width = 5)
 figure_A4(GIi, GIrgr, GIagr)
+dev.off()
+
+pdf("output/FigA4.1.pdf", height = 6, width = 5)
+figure_3.3(GCi, GIi)
 dev.off()
 
 pdf("output/FigA5.pdf", height = 6, width = 5)

### 2015-11-25 MS.tex
Response to reviwer: change done in results part and discussion

@@
 \citealt{grime1979plant, Grime:1997wm}).
-Meanwhile partitioning of seedling RGR into different components showed that specific leaf area (SLA = 1/leaf mass per area LMA) was typically the strongest source of variation between species \citep{Poorter:1989tx}.
+Meanwhile partitioning of seedling RGR into different components showed that specific leaf area (SLA = 1/leaf mass per area LMA) was typically the strongest source of variation between species \citep{Poorter:1989tx, Rees:2010gk}.
 From the 1990s a new style of ``trait ecology'' arose whereby measurable traits including SLA were used directly as strategy axes \citep{Westoby:2002ft}.
@@
 Tree growth in diameter, height or mass can be expressed in either absolute (AGR) or relative terms (RGR).
-According to the growth model, the predicted relationship between growth and SM in seedlings reverts if absolute AGR$_\textrm{mass}$ is used instead of RGR$_\textrm{mass}$ (see Appendix \ref{sec:growth}).
+According to the growth model, the predicted relationship between growth and SM in seedlings reverses if absolute AGR$_\textrm{mass}$ is used instead of RGR$_\textrm{mass}$ (see Appendix \ref{sec:growth}).
 The correlation with RGR$_\textrm{mass}$ is negative but becomes positive with AGR$_\textrm{mass}$.
@@
 
-We first developed a snapshot of the literature, to assess potential to recover useful data from the wide corpus of literature available.
+We first developed a snapshot of the literature, to assess the potential to recover useful data from the wide corpus of literature available.
 This snapshot was obtained via Web of Science database (Thomson Reuters), between March and June 2014, using a range of Boolean search terms in English.
@@
 fertilization, shade, salt stress).
-To minimise publication bias via selective reporting of significant results within the published articles (e.g.
-a particular case of a ``failure to publish bias'' see \citealt{Jennions:2013ta}), we asked those authors reporting a non-significant correlation for additional information about the specific correlation coefficient when this was not provided.
+We asked the authors reporting a non-significant correlation for additional information about the specific correlation coefficient value when this was not provide.
+This allowed us to minimise publication bias via selective reporting of significant results within the published articles (e.g.
+a particular case of a ``failure to publish bias'' see \citealt{Jennions:2013ta}).
 
@@
 The transformation was achieved via Fisher's z-transformation,
-\[ z = \frac{1}{2} \ln \frac{1+r}{1-r}, \]
+\[ z = \frac{1}{2} \ln \frac{1+r}{1-r}\]
 which has a variance estimate of
-\[ v_z= \frac{1}{n-3}, \]
+\[ v_z= \frac{1}{n-3}\]
 where $n$ is the number of species.
@@
 
-\subsubsection*{Sensitivity analysis}\label{sensitivity-analysis}
+\subsubsection*{"Ideal" vs "complete" dataset}\label{ideal-vs-complete-dataset}
 
-We tested how robust our results were to the particular decisions made in the analysis.
-In particular, we tested the sensitivity of our results to inclusion of studies that measured a large number of responses for the same trait.
-The idea is to check that our results were not generated by the dominance of one or few studies reporting several values for the same trait.
-In the case of multiple comparisons within a study, we used the method proposed by \citet{Borenstein:2009um}: we calculated the mean correlation coefficient by trait and by study, and then re-calculated the effect size.
-This produced a reduced dataset, where multiple responses for any given trait were condensed into a study-level average.
-We also tested whether the criteria used for including a study in the analysis influenced our results.
-In addition to the chosen criteria, the experimental conditions (stressed vs unstressed), and the concordance between stage used to measure trait and growth are clear criteria for assessing the quality of the data for addressing our hypotheses.
-Thus we stratified the data set into two subsets: one including only studies under unstressed conditions ('ideal' dataset), and the other set including studies under all conditions ('complete' dataset).
-We excluded from the ''ideal'' dataset studies where growth and traits were measured on plants from different stages, unless a particular stage was by definition required to measure the trait, such as for SM (i.e.
+In addition to the chosen criteria for the meta-analyses, the growth measurement used (relative growth rate-RGR or absolute growth rate-AGR), the number of species, the experimental conditions (stressed vs unstressed), and the concordance between stage used to measure trait and growth are clear criteria for assessing the quality of the data for addressing our hypotheses.
+Thus we stratified the data set into two subsets: one including only studies on RGR, under unstressed conditions and measuring a correlation coefficient at least across 10 species (’ideal’ dataset), and the other set including studies under all conditions (’complete’ dataset).
+We excluded from the ”ideal” dataset studies where growth and traits were measured on plants from different stages, unless a particular stage was by definition required to measure the trait, such as for SM (i.e.
 seed stage), or Hmax (i.e.
@@
 In particular, we quantified heterogeneity in effect size, we tested for publication bias and we explored temporal change in effect size (see Appendix \ref{app:supp_info_analyses}).
+We also tested how robust our results were to the decisions made in the analysis.
+In particular, we tested the sensitivity of our results to inclusion of studies that measured a same trait-growth correlation across different conditions (e.g.
+vegetation type, sites, environemental conditions).
+The idea is to check that our results were not generated by the dominance of one or few studies reporting several values for the same trait.
+In the case of multiple comparisons within a study, we used the method proposed by \citet{Borenstein:2009um}: we calculated the mean correlation coefficient by trait and by study, and then re-calculated the effect size.
+This produced a reduced dataset, where multiple responses for any given trait were condensed into a study-level average.
 
@@
 
+A few number of study reported a trait-growth correlation and meet our basic criteria (112 articles, $n = 216$).
+The main results reported here were obtained with a conservative approach ($n = 98$), and were thereby confined to correlations with RGR, across at least 10 species, under non-stressed conditions, and for which the source of trait and growth was controlled (i.e.
+"ideal" dataset).
+
 For SLA the correlation between RGR and the trait changed significantly with plant size in the manner expected.
@@
 
+For WD, Hmax and seed mass, correlations with RGR were also consistent with expectations, although with limitations arising from very unequal numbers of observations between growth stages for some traits.
+Indeed, confidence intervals of r often spanned zero especially where there were small numbers of studies for particular growth stages, precluding strong conclusions.
 For WD, results were consistent with negative correlations with RGR across all plant sizes (Fig.
@@
 
-For both Hmax and seed mass, correlations with RGR were also consistent with expectations, although with limitations arising from very unequal numbers of observations between growth stages for some traits.
-Indeed, confidence intervals of r often spanned zero especially where there were small numbers of studies for particular growth stages, precluding strong conclusions.
 For Hmax, the expectation was for a correlation with growth to be absent for small plants but present at larger sizes, the mechanism being increased relative allocation to reproduction as Hmax is approached.
@@
 We could not distinguish between these alternatives.
+
 As expected for seed mass, the correlation with RGR shifted from negative at seedling stage ($\bar{r}= -0.5 \pm 0.07$) to not significantly different from zero at adult and sapling stages (Fig \ref{fig:fig3} c, confidence intervals overlapping zero).
@@
 Again we could not distinguish between these alternatives.
-But unlike Hmax, the number of coefficent reported for seed mass was almost similar between adult (n= 7) and seedling (n= 10) stages, suggesting that confident interval overalapping zero at adult stage were due to variation in coefficients of correlation reported rather than to a much smaller numbers of replicate.
+But unlike Hmax, the number of coefficent reported for seed mass was almost similar between adult (n= 7) and seedling (n= 10) stages, suggesting that confident interval overalapping zero at adult stage were due to variation in correlation coefficient reported rather than to a much smaller numbers of replicate.
 
 For Aarea, results were consistent with a positive correlation with RGR at seedling stage.
-However, no conclusion can be drawn about a change along plant stages; only four correlation coefficients were reported for this trait, and three of them were measured at the seedling stage.
+However, no conclusion can be drawn about a change along plant stages; only four correlation coefficients were reported for this trait, and three of them were measured at the seedling stage (Fig.
+\ref{fig:fig3} e).
+
+\subsection*{Results from a more complete dataset}
+
+We also reported results from a more complete dataset to determine if additional data could reinforce some of our conclusions.
+This ''complete'' dataset included correlations measured with both absolute and relative growth rate (Fig.
+\ref{fig:fig4}), across at least two species, and did not required any control for the source of trait or growth (i.e.
+both could be measured on different stages) and for the environemental conditions.
+This release of criteria enlarged in a considerable extent the number of replicates ($n = 216$).
+
+The ''complete'' dataset generated similar effect sizes to those reported above for SLA, WD, Hmax and seed mass, and led to similar conclusions (Fig.
+\ref{fig:fig4}).
+For Aarea, additional replicates from the ''complete'' dataset allowed to compare the effect size across plant stage.
+The results were consistent with a positive correlations with RGR across adult and seedling stages (Fig \ref{fig:fig4} e; CI not overlapping zero).
+
+The comparison of Aarea effect size between "ideal" (Fig.
+\ref{fig:fig3} d) and "complete" (Fig.
+\ref{fig:fig4} d) dataset, showed no signal of an effect of stress (here mainly low light) on the correlation with RGR at seedling stage; the correlation was still positive between Aarea and RGR even when 8 correlations measured under low light conditions were added.
+
+The comparison between RGR and AGR was possible for some trait-stage combinations.
+For seed mass, effects size differed significantly between RGR and AGR at seedling stage; as expected the correlation with RGR was positive and shifted to non significant with AGR (Fig \ref{fig:fig4} d; CI not overlapping).
+For both WD and Hmax, effects size measured with RGR or AGR were no differents at adult stage; CI were overlapping despite equal sample size (Fig \ref{fig:fig4} b and c).
+
+New replicates from the complete dataset were not equally distributed across all trait-stage combinations.
+Some trait-stage combinations already well studied got even more support (e.g.
+from 25 to 59 correlation coefficients reported for SLA at seedling stage), but other still had few replicates.
+Thus, on the 13 traits-stage combinations studied in total, six were only supported by five or less correlations coefficient (i.e.
+WD-seedling, Hmax-sapling, Hmax-seedling, Seed mass-sapling, Aarea-adult and Aarea-sapling).
 
@@
 
-Given our basic conclusion that reported correlations responded to plant size in a manner consistent with expectations from theory, we assess now the coverage of the available data, to determine if biased sampling could have erroneously generated the above results, or if additional data could reinforce some of our conclusions.
+Given our basic conclusion that reported correlations responded to plant size in a manner consistent with expectations from theory, we assess now the coverage of the available data, to determine if biased sampling could have erroneously generated the above results.
 
@@
 
-The results reported above were obtained using an even more conservative dataset ($n = 98$), and were thereby confined to correlations with RGR, across at least 10 species, under non-stressed conditions, and controlling for the source of trait and growth (i.e.
-both had to be measured on the same stage).
-The ''complete'' dataset ($n = 216$) also included correlations measured with absolute growth rate, across two to 10 species, under stressed conditions, and spanning different plant stages between the growth and trait measurements.
-The release of criteria enlarged in a considerable extent the number of replicates.
-While some trait-stage combinations were particularly well studied with 59 correlation coefficient reported for SLA at seedling stage, other still showed weak support.
-Indeed, on the 13 traits-stage combinations studied here, six were supported by five or less correlations coefficient (i.e.
-WD-seedling, Hmax-sapling, Hmax-seedling, Seed mass-sapling, Aarea-adult and Aarea-sapling).
-
-This ''complete'' dataset generated similar effect sizes to those reported above for SLA, WD and Hmax, and led to similar conclusions (Fig.
-\ref{fig:fig4}).
-While the correlation between growth and WD at seedling stage was still negative, the upper CI 95\% was very closed from zero (lower CI: -0.065) due to 2 positive correlation coefficients from \citet{Augspurger:1984ct}; these correlations unlike others used values of WD from adult plants together with growth from seedlings.
-
-For seed mass and Aarea, results from the ''complete'' dataset were even more consistent with expectations from the model.
-For seed mass, the correlation with RGR was undoubtly not significantly different from zero at adult stage (Fig \ref{fig:fig4}; CI for seedling and adult stages were not overlapping anymore, and model fit improved when stage was incorporated (see log likelihood ratio tests, Fig.
-\ref{fig:fig4 d}.
-For Aarea, results were consistent with expectation of positive correlations with RGR across adult and seedling stages (Fig \ref{fig:fig4} e; CI not overlapping zero).
-The comparison of effect size between conservative dataset (Fig.
-\ref{fig:fig3 d}) and complete (Fig.
-\ref{fig:fig4 d} showed no signal of an effect of stress (here mainly low light) on the correlation with growth at seedling stage; the correlation was still positive between Aarea and growth even when 8 correlations measured under low light conditions were added.
-
-Finally, our results were unlikely to be biased by dominance of one or a few studies that measured a large number of responses, since when multiple responses were condensed into a single average within a trait and within a study, outcomes were very similar (Fig.
-\ref{fig:figA5}).
-
 Overall our study met quality criteria expected for meta-analysis in ecology (Table \ref{tab:meta}).
@@
 \ref{fig:figA9}).
+
+Finally, our results were unlikely to be biased by dominance of one or a few studies that measured a large number of responses, since when multiple responses were condensed into a single average within a trait and within a study, outcomes were very similar (Fig.
+\ref{fig:figA5}).
 
@@
 
-For WD the meta-analysis showed negative correlation with growth across all plant stages, as previously reported from individual studies \citep{Wright:2010tp,Ruger:2012jv}.
+For WD the meta-analysis showed negative correlation with RGR across all plant stages, as previously reported from individual studies \citep{Wright:2010tp,Ruger:2012jv}.
 It should be noted however that there are few data available to test this proposition at seedling stage (n=2-5).
@@
 
-Meta-analysis showed a positive correlation between Hmax and growth for adult stage, but not for saplings and seedlings.
+Meta-analysis showed a positive correlation between Hmax and RGR for adult stage, but not for saplings and seedlings.
 The trend for tall stature species to grow faster at a given tree size than small stature species has been noted across several tree size classes and forest types (e.g.
@@
 However this applies only at sizes where some of the species have begun to reproduce, and should not affect sapling and seedling growth rates.
+While our results are consistent with this pattern, a doubt arise about the absence of correlation between growth and Hmax for small plant stature, due to the limited number of replicates for both saplings (n=4) and seedling stages (n=1).
 
@@
 "*" indicated when a stage reassignment is needed.
-"+" on left side of the graph indicate cases where plants came from different growth form.
-Results shown here are the ''complete'' dataset (see methods for details).}
+"+" on left side of the graph indicate cases where plants came from different growth form.}
 \label{fig:fig2}
@@
 A significant p-value means the model including stage effect fitted the data better than the null model.
-Results shown are from correlation coefficients measured for RGR exclusively, with > 10 species, under unstressed conditions and for a controled trait source (see methods for details).}
+Results shown are from the ideal dataset (see methods for details).}
 \label{fig:fig3}
@@
 \includegraphics[width=15cm,height=20cm,keepaspectratio]{output/Fig4.pdf}
-\caption{The relationships between growth rates and traits along plant stage are not overcasted by experimental conditions (i.e.
-growth measurement used, environemental conditions, trait source or number of species used to draw the correlation).
-Plots show the effect size (+ 95\%CI) for the average correlation across species, by plant stage.
-Effect size is a standardized measure of the deviation of correlation coefficient from zero (Fisher's z-transformed).
-Effects are significant if confidence intervals (95\%CI) for a given stage do not overlap with zero.
-Trait names as in Fig.
-\ref{fig:fig1}.
-$n$ indicates number of correlations contributing to each effect.
-Likelihood Ratio Tests (LRT) compared maximum-likelihood fits between a pooled model and one separated by stage.
-A significant p-value means the model including stage effect fitted the data better than the null model.
-Results shown are from the ''complete dataset'' (see methods for details).}
-\label{fig:fig3}
+\caption{Relationships between relative (RGR) and/or absolute (AGR) growth rates and traits along plant stage.
+The legend is identical to Fig 3, with two exceptions.
+i) Results shown are from the "complete" dataset (see methods for details).
+ii) Likelihodd Ratio Tests were calculated on effect size combining RGR and AGR exclusively.}
+\label{fig:fig4}
 \end{figure}

### 2015-11-25 R/figures.R

@@ -223,12 +223,12 @@ figure_3.2 <- function(GCrgr , GCagr) {
   CoefModel.Aarea.opt <- subset(CoefModel.Aarea, growth == "AGR")
   
   
-  p1 <- coeff.plot.gr(data = CoefModel.SLA, data.RGR = CoefModel.SLA.s, data.AGR = CoefModel.SLA.opt, title = "a) SLA",
+  p1 <- coeff.plot.gr2(data = CoefModel.SLA, data.RGR = CoefModel.SLA.s, data.AGR = CoefModel.SLA.opt, title = "a) SLA",
                       limit.x.min = -1, limit.x.max = 1.5, limit.x.n = 1.3,
                    vjust.value = 1, limit.x.text = -0.1, limit.y.text.l1 = 0.25, limit.y.text.l2 = 0.25)
   
-  p2 <- coeff.plot.gr(data = CoefModel.WD, data.RGR = CoefModel.WD.s, data.AGR = CoefModel.WD.opt,title = "b) WD",
-                      limit.x.min = -1, limit.x.max = 1, limit.x.n = 0.85,
+  p2 <- coeff.plot.gr2(data = CoefModel.WD, data.RGR = CoefModel.WD.s, data.AGR = CoefModel.WD.opt,title = "b) WD",
+                      limit.x.min = -1.5, limit.x.max = 1, limit.x.n = 0.85,
                    vjust.value = 1, limit.x.text = -1, limit.y.text.l1 = 0.5, limit.y.text.l2 = 0.25)
   
 #   p3 <- coef.plot.gr.AGR(data.AGR = CoefModel.Hmax.opt, LRT = LRT.h, PVAL = PVAL.h,
@@ -236,23 +236,131 @@ figure_3.2 <- function(GCrgr , GCagr) {
 #                          limit.x.max = 1.5, limit.x.text = -0.1, limit.y.text.l1 = 0.5, limit.y.text.l2 = 0.25,
 #                          limit.x.n = 1.2, vjust.value = 0, color1 = "black")
   
-  p3 <- coeff.plot.gr(data = CoefModel.Hmax, data.RGR = CoefModel.Hmax.s,
+  p3 <- coeff.plot.gr2(data = CoefModel.Hmax, data.RGR = CoefModel.Hmax.s,
[…]

### 2015-11-25 R/model.R

@@ -230,11 +230,11 @@ fun_model2 <- function(x) {
 
   a <- (l1 + 1)
 
-  name <- list(1:l, c("stage", "stress", "Inte", "SE", "CIupper", "CIlower"))
+  name <- list(1:l, c("stage", "growth", "Inte", "SE", "CIupper", "CIlower"))
   CoefModel <- as.data.frame(matrix(nrow = length(name[[1]]), ncol = length(name[[2]]),
     dimnames = name))
   CoefModel[1:l1, 1] <- c((FP$stage))
-  CoefModel[1:l1, 2] <- "raw"
+  CoefModel[1:l1, 2] <- "all"
 
 
   for (i in 1:l1) {
@@ -259,11 +259,11 @@ fun_model2 <- function(x) {
 
   CoefModel["N"] <- "NA"
   # CoefModel['N'] <- N[!(apply(N, 1, function(s) any(s == 0))),]
-  CoefModel$N[CoefModel$stage == "seedling" & CoefModel$stress == "raw"] <- fun2(x)
+  CoefModel$N[CoefModel$stage == "seedling" & CoefModel$growth == "all"] <- fun2(x)
 
-  CoefModel$N[CoefModel$stage == "sapling" & CoefModel$stress == "raw"] <- fun5(x)
+  CoefModel$N[CoefModel$stage == "sapling" & CoefModel$growth == "all"] <- fun5(x)
 
-  CoefModel$N[CoefModel$stage == "adult" & CoefModel$stress == "raw"] <- fun3(x)
+  CoefModel$N[CoefModel$stage == "adult" & CoefModel$growth == "all"] <- fun3(x)
 
   CoefModel
 }

### 2015-11-25 R/plots.R

@@ -119,6 +119,64 @@ coeff.plot.gr <- function(data, data.RGR, data.AGR, title = "",LRT, PVAL,round.v
     annotate("text", x = limit.y.text.l2, y = limit.x.text, label = paste("p.value =", round(PVAL, round.value), significativite), size = 2)
 }
 
+
+coeff.plot.gr3 <- function(data, data1, data.RGR, data.AGR, title = "",LRT, PVAL,round.value,significativite = "", limit.x.min, limit.x.max, limit.x.text,
+                          limit.x.n, limit.y.text.l1, limit.y.text.l2, vjust.value, color1="gray", color2="#9E5F3A", color3="black") {
+  data.RGR["x.coord"] <- limit.x.n
+  data.AGR["x.coord"] <- limit.x.n
+  data1["x.coord"] <- limit.x.n
+  
+    plot1 <- function(title, ggobj, xlab = "Effect size + CI (95%) ", ylab = "Stages") {
+    
+    p <- ggobj + labs(title = title) + xlab(xlab) + ylab(ylab) +
+      geom_vline(yintercept = 0,color = "white") + geom_hline(yintercept = 0, size = 0.3, linetype = "dashed") +
+      scale_x_discrete("stage", limit = c("seedling", "sapling", "adult")) +
+      coord_flip() + mytheme + theme(legend.position = "none") 
+    p
+  }
+  
+  dodge <- position_dodge(width = 0.5)
+  
+  plot1(title, ggplot(data, aes(stage, Inte, ymin = Inte - 1.96 * SE, ymax = Inte +1.96 * SE, color = factor(growth), linetype = factor(growth)))) +
+    geom_point(aes(x = stage, y = Inte), position = dodge ) + geom_errorbar(aes(x = stage, y = Inte), size = 0.4, width = 0.2, position = dodge) +
+    scale_y_continuous("Effect size (z) + CI 95%",limits = c(limit.x.min, limit.x.max)) +
+    geom_text(aes(stage,x.coord, label = paste("n =", N), color = factor(growth), group = "AGR"),size = 2, data = data.AGR, parse = F, position = "identity", vjust = +vjust.value, hjust = 0) + 
+    geom_text(aes(stage, x.coord, label = paste("n =",N), color = factor(growth), group = "RGR"), size = 2, data = data.RGR, parse = F, position = "identity", vjust = 0, hjust = 0) +
[…]

### 2015-11-25 analysis.R

@@ -64,14 +64,14 @@ pdf("output/Fig2.pdf", height = 8, width = 6)
 figure_2(CompleteData_inter)
 dev.off()
 
-
 pdf("output/Fig3.pdf", height = 6, width = 5)
 figure_3(GIrgr)
 dev.off()
 
 
 pdf("output/Fig4.pdf", height = 6, width = 5)
-figure_4(GCi)
+# figure_4(GCi)
+figure_3.4(GCi, GCrgr , GCagr)
 dev.off()
 
 

### 2015-11-27 MS.tex
Dataset change for Herault et al 1995 Reviewer comments added

@@
 \runninghead{Influence of traits on growth changes with size}
-\keywords{maximum height, photosynthetic rate, ontogenetic stage, functional trait, growth strategy, seed mass, specific leaf area, wood density}
+\keywords{absolute growth rate, maximum height, photosynthetic rate, ontogenetic stage, functional trait, growth strategy, relative growth rate, seed mass, specific leaf area, wood density}
 
@@
 \linenumbers
-\section{Summary 235/350}\label{abstract}
+\section{Summary 268/350}\label{abstract}
 \begin{enumerate}
@@
 We outline mechanisms and hypotheses based on new theory, and test these predictions in tree species for five traits (specific leaf area, wood density, maximum height, seed mass and maximum assimilation rate) using a meta-analysis of 112 studies ($>$ 500 correlations).
-To capture the effects of size, we tested for a shift in the direction of correlation between GR and traits across three plant stages: seedling, sapling and adult.
+To capture the effects of size, we tested for a shift in the direction of correlation between growth rates and traits across three plant stages: seedling, sapling and adult.
 
@@
 Seed mass and maximum height were correlated with RGR only in one plant stage category: seedlings and adults, respectively.
+Despite the vast litterature on trait and growth, coverage was limited for wood density, seed mass, maximum height and assimilation rate, and additional studies would be helpful for some trait-growth-stage relationships.
 
 \item Synthesis: We show how trait-growth correlations change in a predictable way with plant size.
-Our understanding of plant strategies should shift away from attributing species as having slow or fast GR throughout their life, in favour of attributing growth trajectories.
+Our understanding of plant strategies should shift away from attributing species as having slow or fast growth throughout their life, in favour of attributing growth trajectories.
 
@@
 The phrase ``plant ecological strategy'' refers to how species face common challenges of acquiring sufficient water, nutrients and light for growth, and then ultimately replacing themselves with offspring.
-An idea that species strategy differences might involve fast versus slow growth goes back at least to \citet{Grime:1975gr}, who measured a wide spread of relative growth rates for seedlings during early exponential growth under favourable conditions.
+An idea that species strategy differences might involve fast versus slow growth goes back at least to \citet{Grime:1975gr}, who measured a wide spread of relative growth rates of seedlings during early exponential growth under favourable conditions.
 Seedling potential relative growth rate (RGR) has continued to be used as a major strategy indicator within the CSR (Competitor - Stress tolerator - Ruderal) classification (e.g.
@@
 It has been widely expected that species with low tissue construction cost will typically have fast growth rates, at least in favourable physical environments \citep[e.g.][]{MullerLandau:2004dc,Poorter:2008iu,Chave:2009iy,Larjavaara:2010bn,Iida:2012jb,Paine:2015df}.
-Yet, a growing number of empirical studies indicate the correlation between traits and growth is not as consistent as that.
+Yet, recently a number of empirical studies indicate the correlation between traits and growth is not as consistent as that.
 Consider SLA as an illustration.
 Species with high SLA can deploy more canopy area for a given dry mass investment in leaves \citep{Poorter:1999wd, Reich:1992wm}.
-In addition, SLA is correlated with high photosynthetic rates and high nitrogen (N) or phosphorus concentrations in the leaf \citep{Wright:2004jb}.
+In addition, SLA is correlated with specific photosynthetic capacity per unit of leaf mass and high nitrogen (N) or phosphorus concentrations in the leaf \citep{Wright:2004jb}.
 For seedling relative growth rates under favourable conditions, high SLA has repeatedly been found to be a strong predictor regardless of vegetation type or growth form \citep{Lambers:1992bj,Reich:1992wm,Grime:1997wm,Poorter:1999wd,Wright:1999ds}.
 Yet for adult plants, the correlation has mostly been much weaker or absent \citep{coomes_comparison_1998,Poorter:2008iu,Aiba:2009ft,Easdale:2009gv,Wright:2010tp}.
-The growing discrepancy between theoretical expectation and empirical results has led some to question whether traits are even useful for understanding growth \citep{Wright:2010tp, Paine:2015df}.
+The discrepancy between theoretical expectation and empirical results has led some to question whether traits are even useful for understanding growth \citep{Wright:2010tp, Paine:2015df}.
 
 Meanwhile the possibility has been raised that trait-growth correlations may change systematically with size \citep{Falster:2011ii, Ruger:2012jv, Iida:2014ep, Iida:2014hq}.
+Size has long been known to play a central role in organismal design and function \citep{Vogel:1988ux, Vogel:2003wb}, including that of trees \citep{Farnsworth:1995im, Givnish:1995ta}.
 Recent theory suggests that the absence of a correlation between SLA and growth at larger sizes may be expected, when potential influences of traits on plant function are considered \citep{Falster:2011ii}.
@@
 
-In this paper, we used a meta-analytic approach on five prominent traits (specific leaf area = SLA, wood or stem tissue density = WD, maximum leaf photosynthetic capacity per unit area = Aarea, asymptotic or maximum height = Hmax, and seed mass = SM) to investigate:
+In this paper, we used a meta-analytic approach on five prominent traits (specific leaf area = SLA, wood or stem tissue density = WD, maximum leaf photosynthetic capacity per unit area = Aarea, asymptotic or maximum height = Hmax, and seed mass) to investigate:
 \begin{enumerate}
@@
 We focused on tree and woody species since the mechanistic model used to assess our predictions is most applicable to these growth forms.
+
+Meta-analytic approach allows generalization by summarizing and integrating research results across studies, just like large data compilation commonly used in trait ecology.
+Yet, a specific interest of meta-analytic approach is also to identify key knowledge gaps.
+Here, we expected a vast literature on trait and growth to be available, but we were uncertain about the representation of all trait-stages combinations.
+Thus, a goal of our study was also to identify areas of research needed to improve our understanding of the link between trait and growth.
 
@@
 
-\textbf{H4: The relationship between SM and relative growth rate is negative in seedlings, but weakens with increasing size.}
+\textbf{H4: The relationship between seed mass and relative growth rate is negative in seedlings, but weakens with increasing size.}
 
@@
 It is uncertain how much this might translate to faster growth in low light.
+It might greatly depend on the level of light available.
 
@@
 Tree growth in diameter, height or mass can be expressed in either absolute (AGR) or relative terms (RGR).
-According to the growth model, the predicted relationship between growth and SM in seedlings reverses if absolute AGR$_\textrm{mass}$ is used instead of RGR$_\textrm{mass}$ (see Appendix \ref{sec:growth}).
+The choice of the growth measurement is generally confunded with the size of the plant; RGR in mass is mainly used for seedling, and AGR in diameter or height are mainly used for adult.
+According to the growth model, the predicted relationship between growth and seed mass in seedlings reverses if absolute AGR$_\textrm{mass}$ is used instead of RGR$_\textrm{mass}$ (see Appendix \ref{sec:growth}).
 The correlation with RGR$_\textrm{mass}$ is negative but becomes positive with AGR$_\textrm{mass}$.
 For SLA, WD, Hmax and Aarea the predicted relationships are not affected by the growth measurement used.
+However RGR and AGR are fundamentaly different for a lot of ecologists.
+So we adopted a two step approach, first we were conservative by focusing exclusively on RGR, then we compared results with those of a more inclusive dataset with both RGR and AGR.
 
@@
 
-We aimed to identify studies that measured the correlation between five prominent functional traits (SLA, WD, Aarea, Hmax and SM) and a growth measurement across species.
+We aimed to identify studies that measured the correlation between five prominent functional traits (SLA, WD, Aarea, Hmax and seed mass) and a growth measurement across species.
 Our literature search was conducted in two phases.
@@
 These papers were examined in addition to those discovered in Phase 1.
-In addition, we gleaned data from other sources, using our own knowledge as researchers in the field (this included adding data from an as-yet unpublished study by Gleason et al).
+In addition, we gleaned data from other sources, using our own knowledge as researchers in the field (this included adding data from an in-review study by \citeauthor{Gleason:2016}).
 The complete list of studies where we inspected the full text is given in Appendix \ref{app:supp_info_files} in Supplementary material.
@@
 SLA, leaf area, leaf nitrogen and phosphorus concentration, net (mass) assimilation rates (NAR), and Aarea are traits involved in species leaf economic strategy \citep{Wright:2004jb,Wright:2010tp}.
-SM and Hmax capture information about reproductive strategy \citep{Falster:2005bw,Moles:2006ft}.
+Seed mass and Hmax capture information about reproductive strategy \citep{Falster:2005bw,Moles:2006ft}.
 WD and sapwood area per leaf area (SA/LA), vessel size and density, and stem specific conductance are all involved in species wood economic strategy  \citep{Chave:2009iy}.
 Here WD and SA/LA are also considered as indicators of stem construction cost \citep{Falster:2011ii}, whereas SLA and leaf thickness capture crucial information about leaf construction cost \citep{Wright:2004jb}.
-Finally, the leaf area ratio and leaf mass ratio are indicators of resource allocation to leaf \citep{Lambers:1992bj}.
+Finally, the leaf area ratio and leaf mass ratio are indicators of resource distribution to leaf \citep{Lambers:1992bj}.
 According to the snapshot of the literature on Web of Science, 62\% of the literature for these 19 traits was captured by a search on SLA and WD.
@@
 Thus we stratified the data set into two subsets: one including only studies on RGR, under unstressed conditions and measuring a correlation coefficient at least across 10 species (’ideal’ dataset), and the other set including studies under all conditions (’complete’ dataset).
-We excluded from the ”ideal” dataset studies where growth and traits were measured on plants from different stages, unless a particular stage was by definition required to measure the trait, such as for SM (i.e.
+We excluded from the ”ideal” dataset studies where growth and traits were measured on plants from different stages, unless a particular stage was by definition required to measure the trait, such as for seed mass (i.e.
 seed stage), or Hmax (i.e.
@@
 
-A few number of study reported a trait-growth correlation and meet our basic criteria (112 articles, $n = 216$).
-The main results reported here were obtained with a conservative approach ($n = 98$), and were thereby confined to correlations with RGR, across at least 10 species, under non-stressed conditions, and for which the source of trait and growth was controlled (i.e.
+Contrary to our expert expectation, a few number of study reported a trait-growth correlation and meet our basic criteria (112 articles, $n = 216$).
+The main results reported here were obtained with an even more conservative approach ($n = 98$), and were thereby confined to correlations with RGR, across at least 10 species, under non-stressed conditions, and for which the source of trait and growth was controlled (i.e.
 "ideal" dataset).
@@
 \ref{fig:fig3} b, model fit not improved when stage was incorporated).
-Note that the confident intervals were not crossing zero for sapling and seedling stage despite small sample sizes (n= 4 and 2 respectively), meaning a good consistency in the coefficient reported for each stage across studies.
+Note that the confident intervals were not crossing zero for sapling and seedling stage despite small sample sizes (n= 4 and 1 respectively), meaning a strong correlation and /or a good consistency in the coefficient reported for each stage across studies.
 
@@
 As expected for seed mass, the correlation with RGR shifted from negative at seedling stage ($\bar{r}= -0.5 \pm 0.07$) to not significantly different from zero at adult and sapling stages (Fig \ref{fig:fig3} c, confidence intervals overlapping zero).
-Hovever, the correlation between seed mass and RGR at adult and saling stages were also not significantly different from that observed at seedling stage (see log likelihood ratio tests and confident intervals overlapping in Fig.
+Hovever, the correlation between seed mass and RGR at adult and sapling stages were also not significantly different from that observed at seedling stage (see log likelihood ratio tests and confident intervals overlapping in Fig.
 \ref{fig:fig3} c).
 Again we could not distinguish between these alternatives.
-But unlike Hmax, the number of coefficent reported for seed mass was almost similar between adult (n= 7) and seedling (n= 10) stages, suggesting that confident interval overalapping zero at adult stage were due to variation in correlation coefficient reported rather than to a much smaller numbers of replicate.
+But unlike Hmax, the number of coefficent reported for seed mass was almost similar between adult (n= 7) and seedling (n= 10) stages, suggesting that confident interval overalapping zero at adult stage were due to variation in correlation coefficient reported rather than to a much smaller numbers of replicates.
 
@@
 
-\subsection*{Results from a more complete dataset}
+\subsection*{Results with an inclusive approach}
 
-We also reported results from a more complete dataset to determine if additional data could reinforce some of our conclusions.
+We also reported results from a more complete dataset, to determine if additional data could reinforce or in contrast overcast some of our conclusions.
 This ''complete'' dataset included correlations measured with both absolute and relative growth rate (Fig.
@@
 \ref{fig:fig4}).
+This supports the robustness of the analysis using the conservative approach ('ideal dataset').
 For Aarea, additional replicates from the ''complete'' dataset allowed to compare the effect size across plant stage.
@@
 \ref{fig:figA7}).
-The extent of heterogeneity was high, but was substantially explained by the plant stage effect for SLA and SM, as expected (Appendix E).
+The extent of heterogeneity was high, but was substantially explained by the plant stage effect for SLA and seed mass, as expected (Appendix E).
 Finally, there was no indication of a temporal change in the effect size being reported within stages (Appendix E, Fig.
@@
 This is coherent with the mechanisms through which traits affect growth being correctly understood in the model.
-For SLA and for SM the meta-analysis confirmed quite strongly the predicted influence of plant size on the trait-growth correlation.
-For WD, Aarea and Hmax results were consistent with predictions, but coverage was limited and additional studies would be helpful for some trait-growth-stage relationships.
+Other mechanisms could also generated these patterns and we discussed them in the discussion.
+For SLA the meta-analysis confirmed quite strongly the predicted influence of plant size on the trait-growth correlation.
+For WD, Aarea, seed mass and Hmax results were consistent with predictions, but coverage was limited and additional studies would be helpful for some trait-growth-stage relationships.
 
@@
 
-For seedlings our meta-analyses showed, as expected, a negative relationship between SM and RGR (in mass or height or volume) for small plants, that dissipated as plants grew larger.
+For seedlings our study showed, as expected, a negative relationship between seed mass and RGR (in mass or height or volume) for small plants, that dissipated as plants grew larger.
 This negative relationship arises because seedlings from larger seeds begin life larger themselves, as has been extensively discussed in the literature \citep[reviewed by][]{Turnbull:2012ew}.
@@
 For WD the meta-analysis showed negative correlation with RGR across all plant stages, as previously reported from individual studies \citep{Wright:2010tp,Ruger:2012jv}.
-It should be noted however that there are few data available to test this proposition at seedling stage (n=2-5).
+It should be noted however that there are few data available to test this proposition at seedling stage (n=1-5).
 In our model (Appendix \ref{sec:growth}) cheaper stem construction is responsible for the predicted negative correlation.
 Lower xylem conductance and associated lower photosynthetic potential have also been suggested \citep[reviewed by][]{Chave:2009iy}.
+For seedlings a negative correlation arose regardless wood density was measured on adult plants, or calculated as seedling stem segment dry weight over its volume (i.e.
+stem density in  \citealt{CastroDiez:1998gz}), suggesting that both measurements could be used.
 
@@
 However this applies only at sizes where some of the species have begun to reproduce, and should not affect sapling and seedling growth rates.
-While our results are consistent with this pattern, a doubt arise about the absence of correlation between growth and Hmax for small plant stature, due to the limited number of replicates for both saplings (n=4) and seedling stages (n=1).
+While the results of the meta-analysis were consistent with the expected pattern for Hmax, we noted that a limited number of replicates were available for both saplings (n=4) and seedling stages (n=1).
+Consequently, subsequent research are welcomed to validate this result.
 
@@
 For example, several papers have suggested that correlations between Hmax and growth rate may arise via cross-correlation with other traits such as WD \citep{Thomas:1996do, Poorter:2006vb, Wright:2010tp}.
-Similarly, effects of SM on growth have been suspected to be mediated via other traits \citep{Shipley:1990js,Westoby:2002ft,Poorter:2006vb}.
+Similarly, effects of seed mass on growth have been suspected to be mediated via other traits \citep{Shipley:1990js,Westoby:2002ft,Poorter:2006vb}.
 Secondary cross-correlation might also potentially have the effect of suppressing a correlation that would otherwise be present.
@@
 
-Light and water micro-environments can affect growth rates, and might modify correlations with traits in relation to plant size.
+A lot of biotic and abiotic conditions such as light and water micro-environments can affect growth rates, and might modify correlations with traits in relation to plant size.
 For example, instead of a positive relationship that disappeared with plant size, \citet{Iida:2014ep} found SLA was negatively correlated with RGR at small size and positively correlated with RGR at larger sizes.
@@
 LMR, LAR, NAR).
-Nevertheless the existing published evidence, even with all its limitations, is consistent with predictions from a simple growth model, and this suggests that species traits can shed light on their growth trajectories, and hence on the changing growth rate rankings across species as individuals become larger.
+However, the existing published evidence is consistent with qualitative predictions of a simple model that assesses the effects of plant size on growth.
+Thus, the linkage of growth to the mechanisms outlined here can shed light on tree growth trajectories and the size-dependent effects of functional traits on the changing species growth rate rankings as individuals grow larger.
 
@@
 Arrows indicate the effect an increase in trait value would have on the main elements of growth eqs.
-\ref{eq:eq0}-\ref{eq:eq4} in Appendix \ref{sec:growth}.
+\ref{eq:eq0}-\ref{eq:eq4} in Appendix \ref{sec:growth}, dashes indicate no significant effect.
 Traits names as in Figure 1.
@@
   \begin{tabular}{llccccccc}
-  & & & & SLA & WD & Hmax & SM & Aarea \\ \hline
+  & & & & SLA & WD & Hmax & seed mass & Aarea \\ \hline
   \multicolumn{3}{ l } {Main element of growth} & & & & & \\ 
@@
 
-\textbf{Seed mass (SM):} The $\textrm{RGR}_{\textrm{mass}}$ slows as plants grow larger, and large-seeded species begin larger as seedlings.
-For larger plants, SM is not expected to have any distinct influence on growth rates  (Table \ref{tab:trade-offs}).
+\textbf{Seed mass:} The $\textrm{RGR}_{\textrm{mass}}$ slows as plants grow larger, and large-seeded species begin larger as seedlings.
+For larger plants, seed mass is not expected to have any distinct influence on growth rates  (Table \ref{tab:trade-offs}).
 
@@
 
-Note that the predicted relationship between growth and either SLA or SM in seedlings differs if absolute growth rate in mass is used instead of RGR$_\textrm{mass}$ (i.e.
-becomes negative for SLA, positive for SM).
+Note that the predicted relationship between growth and either SLA or seed mass in seedlings differs if absolute growth rate in mass is used instead of RGR$_\textrm{mass}$ (i.e.
+becomes negative for SLA, positive for seed mass).
 In our study, all data recorded for these trait-stage combinations have been measured on a RGR base for mass (see Fig S9).
@@
 The open points correspond to the estimated missing studies.
-The number of missing values is 7 for SLA,1 for WD, 0 for Hmax, 6 for SM and 0 for Aarea.
+The number of missing values is 7 for SLA,1 for WD, 0 for Hmax, 6 for seed mass and 0 for Aarea.
 Results shown here are from the ''ideal'' dataset (see methods for details).}
@@
 
-\textbf{Results:} We observed high levels of heterogeneity for all traits (SLA :$I^{2}$ 85.4\% CI: 80.9 to 92.1, WD :$I^{2}$ 61.8\% CI: 42.8 to 84.1, Hmax: $I^{2}$ 81.2\% CI: 69.8 to 93.4, SM: $I^{2}$ 91.2\%, 85.9 to 96.1, Aarea: $I^{2}$ 68.3\% CI: 33.7 to 90.1) which suggests that the correlations coefficient r between growth and traits are not uniform across the range of studies investigated.
+\textbf{Results:} We observed high levels of heterogeneity for all traits (SLA :$I^{2}$ 85.4\% CI: 80.9 to 92.1, WD :$I^{2}$ 61.8\% CI: 42.8 to 84.1, Hmax: $I^{2}$ 81.2\% CI: 69.8 to 93.4, seed mass: $I^{2}$ 91.2\%, 85.9 to 96.1, Aarea: $I^{2}$ 68.3\% CI: 33.7 to 90.1) which suggests that the correlations coefficient r between growth and traits are not uniform across the range of studies investigated.
 This result suggested that a large part of the variance is not explained by sample error.
 
-For SLA and SM, 50.1\% and 20\% respectively of the total amount of heterogeneity were accounted for by including the stage as a moderator.
+For SLA and seed mass, 50.1\% and 20\% respectively of the total amount of heterogeneity were accounted for by including the stage as a moderator.
 For the other traits, the stage explained little or no part of the heterogeneity observed across studies ($<$5\%).
-These results were consistent with our expectations about a shift in the relationship between growth and traits across plant size for SLA and SM, and the absence of an effect for WD and Aarea (see Theoretical expectation section).
+These results were consistent with our expectations about a shift in the relationship between growth and traits across plant size for SLA and seed mass, and the absence of an effect for WD and Aarea (see Theoretical expectation section).
 The result for Hmax was more ambiguous since we expected the relationship between Hmax and growth rate to be absent in seedlings but to strengthen with increasing plant size (at adult stage).
@@
 While funnel plot are recommended to aid interpretation, there is a high risk of failing to detect actual publication bias (see \citealt{Koricheva:2013tz}) by using an exclusively visual assessment.
-In addition, funnel plots are not effective when the number of studies is small ($<30$) such as for Aarea and SM.
+In addition, funnel plots are not effective when the number of studies is small ($<30$) such as for Aarea and seed mass.
 Next, we used the ''trim and fill'' method to estimate the number of studies missing from our meta-analysis. This method adjusts for funnel plot asymmetry \citep{Duval:2000dg}.
@@
 \ref{fig:figA9}).
-The overall estimates measured with the fill in data changed from $0.5 \pm 0.07$  to $0.4 \pm 0.07$ for SLA and from $-0.48 \pm 0.11$ to $-0.32 \pm 0.12$ for the seed mass, suggesting a lower correlation coefficient for SLA, and SM.
+The overall estimates measured with the fill in data changed from $0.5 \pm 0.07$  to $0.4 \pm 0.07$ for SLA and from $-0.48 \pm 0.11$ to $-0.32 \pm 0.12$ for the seed mass, suggesting a lower correlation coefficient for SLA, and seed mass.
 Even although the estimated correlations were closer to zero with the missing studies filled in, the results still indicate that the effect is statistically significant.
@@
 
-\textbf{Result:} There was a change in the effect size with publication year for SLA ($p<0.0001$, estimates: $-0.04 \pm 0.009$ ), SM ($p = 0.011$, estimates: $0.041 \pm 0.016$ ) and Aarea ($p = 0.0102$, estimates: $-0.0453 \pm 0.0176$ ).
+\textbf{Result:} There was a change in the effect size with publication year for SLA ($p<0.0001$, estimates: $-0.04 \pm 0.009$ ), seed mass ($p = 0.011$, estimates: $0.041 \pm 0.016$ ) and Aarea ($p = 0.0102$, estimates: $-0.0453 \pm 0.0176$ ).
 The Fig.
@@
 
-For SLA and SM, a publication year effect was not observed within seedling and sapling stages, but was identified for the adult stage (SLA $p = 0.003$, SM $p = 0.06$).
-For both SLA and SM, the magnitude of the effect size decreased with publication year (Fig.
+For SLA and seed mass, a publication year effect was not observed within seedling and sapling stages, but was identified for the adult stage (SLA $p = 0.003$, seed mass $p = 0.06$).
+For both SLA and seed mass, the magnitude of the effect size decreased with publication year (Fig.
 \ref{fig:figA9} a and d), suggesting we overestimated the magnitude of the effect size for these two traits.
-In reality, the main effect size obtained would be more close to zero or more negative for SLA and more positive for SM.
-These results are consistent with our hypotheses; we expected a negative or non-significant effect of SLA on growth in adult stage, and a non-significant or positive effect of SM on plant growth (see theoretical expectation).
+In reality, the main effect size obtained would be more close to zero or more negative for SLA and more positive for seed mass.
+These results are consistent with our hypotheses; we expected a negative or non-significant effect of SLA on growth in adult stage, and a non-significant or positive effect of seed mass on plant growth (see theoretical expectation).
 

### 2015-11-27 R/figures.R

@@ -77,7 +77,7 @@ figure_2 <- function(CompleteData_inter) {
     points(data$growthf[t], y[t], pch = "+", cex=1, col="grey")
 
     axis(1, at = 0:3, labels = cuts, las = 1)
-    axis(2, at = y, labels = data$id, las = 1, cex.axis = 0.55)
+    axis(2, at = y, labels = data$id, las = 1, cex.axis = 0.6)
     abline(v = 1, col = "grey", lty = 2, lwd = 0.5)
     abline(v = 2, col = "grey", lty = 2, lwd = 0.5)
   }

### 2015-11-29 MS.tex
Reviwer3 suggestions added

@@
 \newcommand{\smurl}[1]{\url{#1}}
+\newcommand{\tabitem}{~~\llap{\textbullet}~~}
 \usepackage{graphicx}
@@
 The main effect of increased seed size is to produce a larger overall seedling.
-Generally relative growth rate decreases with size, and as such larger seedlings are predicted to have a lower relative growth rate during the earliest phases of growth \citep{Turnbull:2012ew}.
+Under similar light conditions, relative growth rate decreases with size because the ratio of leaf area to total biomass decreases with increasing plant size.
+Thus, larger seedlings are predicted to have a lower relative growth rate during the earliest phases of growth \citep{Turnbull:2012ew}.
 However, among larger plants we expect the effect of this initial size to be minimal, and thus the correlation between seed size and growth rate should disappear.
@@
 However RGR and AGR are fundamentaly different for a lot of ecologists.
-So we adopted a two step approach, first we were conservative by focusing exclusively on RGR, then we compared results with those of a more inclusive dataset with both RGR and AGR.
+So we adopted a two steps approach, first we were conservative by focusing exclusively on RGR, then we compared results with those of a more inclusive dataset with both RGR and AGR.
 
@@
 Traits names as in Figure 1.
+$a_\textrm{l}$ : leaves area, $m_\textrm{t}$: vegetative live mass, $b$: live biomass.
 For further details, see Appendix \ref{sec:growth}.}
@@
 \vspace{1cm}
-  \begin{tabular}{llccccccc}
+  \begin{tabular}{lllcccccc}
   & & & & SLA & WD & Hmax & seed mass & Aarea \\ \hline
@@
   & \multicolumn{2}{ l } {Net live biomass production} & $\frac{\textrm{d}b}{\textrm{d}t}$ & & & & & \\
-  & &    photosynthesis & & - & - & - & - & $\uparrow$  \\
-  & &     respiration   & & - & - & - & - & -  \\
-  & &     leaf turnover & & $\uparrow$ & - & - & - & - \\
+  & &     \tabitem photosynthesis & & - & - & - & - & $\uparrow$  \\
+  & &     \tabitem respiration   & & - & - & - & - & -  \\
+  & &     \tabitem leaf turnover & & $\uparrow$ & - & - & - & - \\
   & \multicolumn{2}{ c } {Allocation to vegetative growth} & $\frac{\textrm{d}m_\textrm{t}}{\textrm{d}b}$ & - & - & $\uparrow$ & - & - \\ 
@@
   2.& Reporting inclusion or exclusion criteria & yes & We specified several inclusion criteria in the sub-section "Phase 2 - Systematic search" in material and method.
-The Bibtex file `read.bib` on Github reports all the articles red but laid out because they failed to met our criteria.\\
+The Bibtex file `read.bib` on Github reports all the articles consulted but not used.\\
   3.& Weighting effect sizes by study precision & yes & Effects sizes were weighted by number of species. See	 details in sub-section ``Effect size calculation'' in material and method.\\
- 4.& Specifying meta-analytical model &	yes	& We used a mixed-effect model with a study ID as a random variation, and stage as a fixed effect.
+ 4.& Specifying meta-analytical model &	yes	& We used a mixed-effect model with a study ID as a random variable, and stage as a fixed effect.
 See details in sub-section "Stage effect" in material and methods.

### 2016-01-13 analysis.R
Use remake to generate analysis.R
For anlyone who doesn't want to use remake

@@ -12,31 +12,33 @@ source("R/model.R")
 source("R/plots.R")
 source("R/utils.R")
 dir.create("output", FALSE, TRUE)
-pdf("output/FigA1.pdf", height = 6L, width = 6L)
-figure_A1()
-dev.off()
+dir.create("downloads", FALSE, TRUE)
+library("remake")
+make_script(file = "analysis.R")
+library("downloader")
+download_baad("downloads/baad.rds")
 paper_bib <- read.bib("references/paper.bib")
 meta_bib <- read.bib("references/metaanalyses.bib")
 combined_bib <- merge_bib_files(meta_bib, paper_bib)
 write.bib(combined_bib, file = "output/refs.bib")
-CompileTable <- clean_raw_data("data/CompileData.csv")
-RawData <- standardise_data(CompileTable)
-CompleteData <- build_complete_data(RawData)
-CompleteData_inter <- Build_intersp_complete_data(RawData)
-IdealData_inter <- build_ideal_data(CompleteData)
-CoordTable <- build_map_data(RawData)
-IdealData_rgr <- subset_growth(IdealData_inter, "RGR")
-IdealData_agr <- subset_growth(IdealData_inter, "AbGR")
+AllData <- clean_raw_data("data/CompileData.csv")
+CleanData <- standardise_data(AllData)
+CompleteData <- build_complete_data(CleanData)
+CompleteData_inter <- Build_intersp_complete_data(CleanData)
+IdealData <- build_ideal_data(CompleteData)
+CoordTable <- build_map_data(CleanData)
+IdealData_rgr <- subset_growth(IdealData, "RGR")
+IdealData_agr <- subset_growth(IdealData, "AbGR")
 CompleteData_rgr <- subset_growth(CompleteData_inter, "RGR")
 CompleteData_agr <- subset_growth(CompleteData_inter, "AbGR")
 GCi <- list_by_trait(CompleteData_inter)
-GIi <- list_by_trait(IdealData_inter)
+GIi <- list_by_trait(IdealData)
 GIrgr <- list_by_trait(IdealData_rgr)
 GIagr <- list_by_trait(IdealData_agr)
 GCrgr <- list_by_trait(CompleteData_rgr)
 GCagr <- list_by_trait(CompleteData_agr)
 pdf("output/Fig1.pdf", height = 3L, width = 4L)
[…]

### 2016-01-13 MS.tex
Substantial edits to text
- still work to do merging theoretical section with hypotheses

@@
 \title{On the link between functional traits and growth rate: meta-analysis shows effects change with plant size, as predicted}
-\author{Anais Gibert\textasteriskcentered, Emma F. Gray, Mark Westoby, Ian J. Wright, Daniel S. Falster}
+\author{Ana{\"i}s Gibert\textasteriskcentered, Emma F. Gray, Mark Westoby, Ian J. Wright, Daniel S. Falster}
 \affiliation{Biological Sciences, Macquarie University NSW 2109, Australia\\
@@
 \date{}
+
+% Todo:
+% Ditch abbrvos for SLA, wood density, Hmax?
+% Fix plots
+%   -- labels causing plot size to change, e.g. Fig 3d
+%   -- only one y label for multi-panel plots
+%   -- sample sizes skewiff relative to plots if Figure 4
+%   -- major revision of code -- > lots of repetition, hard to follow
+%   -- Figure 2: add * against traits used in meta-analysis
 
@@
 \runninghead{Influence of traits on growth changes with size}
-\keywords{absolute growth rate, maximum height, photosynthetic rate, ontogenetic stage, functional trait, growth strategy, relative growth rate, seed mass, specific leaf area, wood density}
+\keywords{maximum height, photosynthetic rate, ontogenetic stage, functional trait, growth strategy, seed mass, specific leaf area, wood density}
 
@@
 \itemsep1pt\parskip0pt\parsep0pt
-\item A plant's growth rate has often been seen as a central element of its ecological strategy, and as ultimately linked to its traits.
-Yet the literature is inconsistent about the empirical correlation between functional traits and growth, casting doubt on the capacity of traits to predict growth.
+\item A plant's growth rate is seen as a central element of its ecological strategy, and as determined by its traits.
+Yet the literature is inconsistent about the empirical correlation between functional traits and growth, casting doubt on the capacity of some prominent traits to influence growth rate.
 
 \item We propose that traits should influence growth in a way that depends on the size of individual plants.
-We outline mechanisms and hypotheses based on new theory, and test these predictions in tree species for five traits (specific leaf area, wood density, maximum height, seed mass and maximum assimilation rate) using a meta-analysis of 112 studies ($>$ 500 correlations).
+We outline mechanisms and hypotheses based on new theory, and test these predictions in tree species using a meta-analysis of 103 studies ($>$ 500 correlations) for five traits (specific leaf area, wood density, maximum height, seed mass and maximum assimilation rate).
 To capture the effects of size, we tested for a shift in the direction of correlation between growth rates and traits across three plant stages: seedling, sapling and adult.
@@
 \item Results were consistent with predictions.
-Specific leaf area was correlated with relative growth rate (RGR) in seedling but not in adult plants.
+Specific leaf area was correlated with relative growth rate (RGR) in seedlings but not in adult plants.
 Correlations of RGR with wood density and assimilation rate were not affected by stage.
 Seed mass and maximum height were correlated with RGR only in one plant stage category: seedlings and adults, respectively.
-Despite the vast litterature on trait and growth, coverage was limited for wood density, seed mass, maximum height and assimilation rate, and additional studies would be helpful for some trait-growth-stage relationships.
+Yet, despite a sizeable literature on traits and growth, coverage was still limited for wood density, seed mass, maximum height and assimilation rate.
+Additional studies are needed for some trait-growth-stage relationships.
 
@@
 
-The phrase ``plant ecological strategy'' refers to how species face common challenges of acquiring sufficient water, nutrients and light for growth, and then ultimately replacing themselves with offspring.
-An idea that species strategy differences might involve fast versus slow growth goes back at least to \citet{Grime:1975gr}, who measured a wide spread of relative growth rates of seedlings during early exponential growth under favourable conditions.
-Seedling potential relative growth rate (RGR) has continued to be used as a major strategy indicator within the CSR (Competitor - Stress tolerator - Ruderal) classification (e.g.
+The phrase ``plant ecological strategy'' refers to how species face common challenges of acquiring sufficient water, nutrients, and light for growth; and then ultimately replacing themselves with offspring.
+The idea that a strategy differences among species might involve fast versus slow growth goes back at least to \citet{Grime:1975gr}, who observed a wide spread of relative growth rate (RGR) among seedlings growing under favourable conditions.
+Seedling potential RGR has continued to be used as a major strategy indicator within Grime's CSR (Competitor -- Stress tolerator -- Ruderal) classification (e.g.
 \citealt{grime1979plant, Grime:1997wm}).
-Meanwhile partitioning of seedling RGR into different components showed that specific leaf area (SLA = 1/leaf mass per area LMA) was typically the strongest source of variation between species \citep{Poorter:1989tx, Rees:2010gk}.
-From the 1990s a new style of ``trait ecology'' arose whereby measurable traits including SLA were used directly as strategy axes \citep{Westoby:2002ft}.
-An approach via measurable traits made broad comparisons possible across continents and latitudes and thousands of species.
-Since then, traits have been seen as constructive approaches to understanding plant growth strategies \citep{Grime:1977kc,Chapin:1980gz}, community composition \citep{Lavorel:2002ff,Shipley:2006ie}, global vegetation dynamics \citep{Scheiter:2013ed} and ecosystem processes \citep{Lavorel:2002ff}.
+Meanwhile partitioning of seedling RGR into different components showed that specific leaf area (SLA) was typically the strongest source of variation between species \citep{Poorter:1989tx, Rees:2010gk}.
+From the 1990s a new style of ``trait ecology'' arose whereby measurable traits, including SLA, were used directly as strategy axes \citep{Westoby:2002ft}.
+An approach via measurable traits made broad comparisons possible across continents, latitudes, and thousands of species.
+Since then, traits have been seen as constructive approaches to understanding plant growth strategies \citep{Westoby:2002ft}, community composition \citep{Lavorel:2002ff,Shipley:2006ie}, global vegetation dynamics \citep{Scheiter:2013ed} and ecosystem processes \citep{Lavorel:2002ff}.
 
-Currently, two main spectra of variation are widely cited as underpinning differences between species in vegetative growth rates.
+Currently, two main spectra of trait variation are widely cited as underpinning differences between species in vegetative growth rates.
 The ``leaf economic spectrum'' \citep{Wright:2004jb} and the ``wood economic spectrum'' \citep{Chave:2009iy} reflect tissue construction costs (for leaf area and for wood volume respectively), trading off with rates of tissue turnover or mortality.
@@
 Consider SLA as an illustration.
-Species with high SLA can deploy more canopy area for a given dry mass investment in leaves \citep{Poorter:1999wd, Reich:1992wm}.
-In addition, SLA is correlated with specific photosynthetic capacity per unit of leaf mass and high nitrogen (N) or phosphorus concentrations in the leaf \citep{Wright:2004jb}.
-For seedling relative growth rates under favourable conditions, high SLA has repeatedly been found to be a strong predictor regardless of vegetation type or growth form \citep{Lambers:1992bj,Reich:1992wm,Grime:1997wm,Poorter:1999wd,Wright:1999ds}.
+By definition, species with high SLA can deploy more leaf area for a given dry mass investment in leaves \citep{Poorter:1999wd, Reich:1992wm}.
+In addition, SLA is correlated with specific photosynthetic capacity per unit of leaf mass and high nitrogen or phosphorus concentrations in the leaf \citep{Wright:2004jb}.
+For seedling RGR under favourable conditions, SLA has repeatedly been found to be a strong predictor regardless of vegetation type or growth form \citep{Lambers:1992bj,Reich:1992wm,Grime:1997wm,Poorter:1999wd,Wright:1999ds}.
 Yet for adult plants, the correlation has mostly been much weaker or absent \citep{coomes_comparison_1998,Poorter:2008iu,Aiba:2009ft,Easdale:2009gv,Wright:2010tp}.
@@
 Size has long been known to play a central role in organismal design and function \citep{Vogel:1988ux, Vogel:2003wb}, including that of trees \citep{Farnsworth:1995im, Givnish:1995ta}.
-Recent theory suggests that the absence of a correlation between SLA and growth at larger sizes may be expected, when potential influences of traits on plant function are considered \citep{Falster:2011ii}.
-At larger sizes the low-cost deployment benefits of high SLA may be offset or even outweighed by the high costs of rapid leaf turnover (see section ``Theoretical expectations'').
-While recent empirical studies supported the idea of a variation in the relationships between traits and growth rates across plant sizes (\citealt{Iida:2014ep, Iida:2014hq}), the trend and mechanisms behind this variation remain unclear.
+Recent theory suggests that the absence of a correlation between SLA and growth at larger sizes may in fact be expected, when potential influences of traits on plant function are considered \citep{Falster:2011ii}.
+As plants grow larger, a greater amount of the energy is devoted towards building and maintaining non-photosynthetic tissues \citep{Givnish:1995ta}.
+A model by \citet{Falster:2011ii} suggests this change shifts the benefits and costs of some trait-based trade-offs, such that the net effect on the trait on growth changes with size.
+While recent empirical studies support the idea that the relationship between traits and growth rates may change with size (\citealt{Iida:2014ep, Iida:2014hq}), the trend and mechanisms behind this variation remain unclear.
 
-In this paper, we used a meta-analytic approach on five prominent traits (specific leaf area = SLA, wood or stem tissue density = WD, maximum leaf photosynthetic capacity per unit area = Aarea, asymptotic or maximum height = Hmax, and seed mass) to investigate:
+In this paper, we investigate for five prominent traits (specific leaf area = SLA, wood or stem tissue density = WD, maximum leaf photosynthetic capacity per unit area = Aarea, asymptotic or maximum height = Hmax, and seed mass):
 \begin{enumerate}
   \item How general is the tendency for correlations between traits and growth rate to vary with plant size?
-  \item  Do the observed relationships conform to predictions (outlined in section ``Theoretical expectations'') derived from a recently developed mechanistic model \citep{Falster:2011ii}?
+  \item Do the observed relationships conform to predictions derived from a recently developed mechanistic model \citep{Falster:2011ii} (see ``Theoretical expectations'')?
 \end{enumerate}
-We gathered correlation coefficients between traits and growth from studies that gave explicit information about the size or stage of the plants.
-While most studies on traits have not been concerned with effects of plant size, they have generally reported trait-growth correlations for identifiable stage classes.
-We used plant stage (i.e.
-seedling, sapling and adult) as a surrogate for the effects of plant size.
+To address these questions we used a meta-analytic approach, compiling data from diverse studies reporting correlation coefficients between traits and growth.
+While most studies investigating the link between traits and growth have not primarily been concerned with effects of plant size, they have generally reported trait-growth correlations for identifiable stage classes (i.e.
+seedling, sapling, and adult).
+We therefore used plant stage as a surrogate for the effects of plant size.
 We focused on tree and woody species since the mechanistic model used to assess our predictions is most applicable to these growth forms.
-
-Meta-analytic approach allows generalization by summarizing and integrating research results across studies, just like large data compilation commonly used in trait ecology.
-Yet, a specific interest of meta-analytic approach is also to identify key knowledge gaps.
-Here, we expected a vast literature on trait and growth to be available, but we were uncertain about the representation of all trait-stages combinations.
-Thus, a goal of our study was also to identify areas of research needed to improve our understanding of the link between trait and growth.
+We chose to assess hypotheses via meta-analysis because there already exist a considerable number of studies with salient information, allowing us to assess our hypotheses across a much broader number of species and vegetation types than would have been possible in an experiential study.
+While, we anticipated a reasonably-sizeable literature on trait and growth to be available, we were uncertain about the representation of all trait-stages combinations.
+An additional goal of our study was therefore to identify any gaps in knowledge needed to improve our understanding of the link between trait and growth.
 
@@
 Specific predictions arise from considering the influence of traits on elements of these equations and how these effects may vary with size (see Appendix \ref{sec:growth} for mathematical explanations).
-This model extends earlier efforts to model growth as a function of traits \citep{Lambers:1992bj,cornelissen_seedling_1996,Wright:2000kw,Enquist:2007ek}.
-However, whereas earlier models focused solely on mass-based relative growth rate and did not predict a change in effect of traits with size, the revised equations do allow for these effects, while also making predictions for both absolute and relative growth rates in any of height, diameter or mass.
+This model extends earlier efforts to model growth as a function of traits \citep{Lambers:1992bj,Cornelissen:1996hf,Wright:2000kw,Enquist:2007ek}.
+However, whereas earlier models focused solely on mass-based RGR and did not predict a change in effect of traits with size, the revised equations do allow for these effects, while also making predictions for both AGR and RGR in any of height, diameter or mass.
+
+\section{Derivation of hypotheses from growth equations}\label{sec:growth}
+
+We adapted growth equations from \cite{Falster:2011ii} to generate hypotheses on both absolute and relative growth rate in mass (eqn \ref{eq:eq1}), height (eqn \ref{eq:eq2}) and diameter (eqn \ref{eq:eq4}).
+
+The rate at which \textbf{live biomass} $b$ is produced by a plant is given by:
+
+\begin{equation}\label{eq:eq0}
+\underbrace{\frac{db}{dt}}_{\text{net live biomass production}} = \underbrace{y}_{\text{yield}}  \big(\underbrace{a_{l} A_{\textrm{area}}}_{\text{photosynthesis}} - \underbrace{\sum_{i = l,s,r,f} m_{i} r_{i}}_{\text{respiration}}\big) - \underbrace{ \sum_{i = l,s,r,f} m_{i} k_{i}}_{\text{turnover}},
+\end{equation}
+where $y$ is the ratio of carbon fixed in mass per carbon assimilated, and $A_{\textrm{area}}$ is the assimilation rate of CO$_{2}$ per leaf area.
+
+Here, and in the following equations, $m_i$ denotes the \textbf{live mass on the plant}, $r_i$ the mass-specific \textbf{respiration rate}, and $k_i$ the \textbf{turnover rate} of different plant tissues; the subscripts $i = l,s,r,t,f$ referring to leaves, sapwood and bark, roots, total of these vegetative tissues, and to the reproductive tissues (fruits, flowers etc.) (note that the live biomass $b = m_t +m_f$).
+Similarly $a_i$ denotes \textbf{areas}, of leaves ($i = l$) and of cross-sections of total stem and sapwood ($i = st,ss$) respectively.
+
+The \textbf{growth rate in mass}, being the increment in vegetative live mass ($m_t$), is then:
+
+\begin{equation}\label{eq:eq1}
+\underbrace{{\frac{dm_t}{dt}}}_{\text{growth rate in mass}} = \underbrace{\frac{dm_t}{db}}_{\text{allocation to vegetative growth}}  \times \underbrace{\frac{db}{dt}}_{\text{net live biomass production}},
+\end{equation}
+where allocation to growth is the fraction of net live biomass increase that goes to vegetative growth rather than to reproductive tissue production.
+
+The \textbf{growth rate in height} can then be expressed as:
+\begin{equation}\label{eq:eq2}
+\underbrace{\frac{dH}{dt}}_{\text{growth rate in height}} = \underbrace{\frac{dH}{da_{l}}}_{\text{architecture layout}} \times \underbrace{{\frac{da_{l}}{dm_{t}}}}_{\text{leaf deployment per mass}} \times {\frac{dm_t}{db}} \times {\frac{db}{dt}}.
+\end{equation}
+Similarly \textbf{growth rate in basal area} can be expressed as:
+\begin{equation}\label{eq:eq3}
+\underbrace{{\frac{da_{st}}{dt}}}_{\text{basal area growth rate}} = \underbrace{\frac{da_{ss}}{da_{l}}}_{\text{sapwood area per leaf area}} \times {\frac{da_{l}}{dm_{t}}} \times  {\frac{dm_t}{db}} \times {\frac{db}{dt}} +  \underbrace{ \frac{da_{st}}{dt}}_{\text{sapwood turnover}}.
+\end{equation}
+
+The \textbf{growth rate in diameter} is then given by the geometric relationship between diameter and area applied to stem:
+\begin{equation}\label{eq:eq4}
+\underbrace{\frac{dD}{dt}}_{\text{growth rate in diameter}} = \sqrt[]{\frac{\Pi}{a_{st}}} \times {\frac{da_{st}}{dt}}.
+\end{equation}
+
+For the case of seedlings, eqs.
+\ref{eq:eq0}-\ref{eq:eq1} can be simplified considerably.
+Turnover of all tissues and allocation to reproduction have not yet begun.
+It is also common to assume all respiration rates are proportional to leaf area.
+Biomass growth rate in seedling then becomes a linear function of leaf area:
+\begin{equation}\label{eq:eq1_seedlings}
+{\frac{dm_t}{dt}}  \approx  a_{l} \, y \, (A_{\textrm{area}} - r_{l}).
+\end{equation}
+
+The \textbf{relative growth rate in mass} $(\textrm{RGR}_{\textrm{mass}})$ in seedlings can be obtained by dividing both sides of this simplified eq \ref{eq:eq1_seedlings} by the total mass of living tissues $m_{t}$.
+The outcome is equivalent to the classical partitioning of RGR \citep{Lambers:1992bj, Cornelissen:1998ta}:
+\begin{equation}\label{eq:eq1_seedlings_RGR}
+\textrm{RGR}_{\textrm{mass}}  \approx \textrm{NAR} \times  \textrm{SLA} \times  \textrm{LMF},
+\end{equation}
+where net assimilation rate NAR = $y \, (A_{\textrm{area}} - r)$, SLA = $a_{l}/ m_{l}$ and leaf mass fraction LMF = $m_{l}/ m_{t}$.
+
+The predicted effects of different traits on growth can then be understood by considering the influence of trait variation on elements of equations  \ref{eq:eq0}-\ref{eq:eq1_seedlings_RGR} (see Table \ref{tab:trade-offs}) and how these may interact with plant size.
 
@@
 Plants with high SLA can deploy more leaf area per unit of mass invested.
-However, high-SLA species also have shorter leaf lifespan and faster leaf turnover rate \citep{Wright:2004jb}.
-Whether plant growth increases with SLA depends on the relative magnitude of the leaf construction and leaf turnover effects of SLA (Table \ref{tab:trade-offs}).
-During early life, when leaf comprises a large part of the plant, decreasing leaf construction cost has a positive effect on growth rate.
+However, high-SLA species also have shorter leaf lifespan, and must use more energy replacing leaves lost via turnover \citep{Wright:2004jb}.
+Whether plant growth rate increases with SLA depends on the how the relative magnitude of the benefit (cheap leaf construction) and cost (higher leaf turnover) of increased SLA also change with size (Table \ref{tab:trade-offs}).
+During early life, when leaf comprises a large part of the plant, decreasing SLA has an overwhelmingly positive effect on growth rate.
 As plants increase in size and leaf mass fraction decreases, the benefit of cheaper leaf construction diminishes; thus the cost of replacing leaf turnover becomes more important.
+
+For seedlings (eq.
+\ref{eq:eq1_seedlings_RGR}), cheaper leaf construction (high SLA) should translate directly into faster relative growth rate in mass.
+For larger plants (eq.
+\ref{eq:eq1}-\ref{eq:eq4}), SLA is expected to affect growth rate positively through more cost-efficient deployment of leaf area (via $da_l/dm_t$; the same effect as in seedlings), but also negatively via increased leaf turnover (eqn 1; Table \ref{tab:trade-offs}).
+The effect of SLA on $da_l/dm_t$ decreases as plant size increases and increasing amounts of the plant are wood.
+Consequently the effect of turnover costs in slowing growth comes to dominate at larger sizes.
 
@@
 
-High WD increases the cost of building stem tissue and thus the cost of deploying additional leaf area (Table \ref{tab:trade-offs}), which should result in slower growth.
+High WD increases the cost of building stem tissue and thus the cost of deploying additional leaf area (Table \ref{tab:trade-offs}), which should slow growth.
 Although expensive wood decreases the risk of mortality, this benefit is not reflected in growth outcomes.
@@
 
-\textbf{H3: The relationship between Hmax and growth rate is expected to be absent in seedlings but to strengthen with increasing plant size.}
+Cheaper stem construction (low WD or stem density) increases the marginal rate of leaf deployment per total mass increment ($da_l/dm_t$), and consequently increases growth rate in leaf area, height, and diameter (eqs.
+\ref{eq:eq2}-\ref{eq:eq4}; Table \ref{tab:trade-offs}).
+Disadvantages associated with cheap stem construction take the form of higher mortality and so are not reflected in growth equations.
+Under this scenario, wood density is negatively correlated to growth rate across all plant stages.
+Because the relative expenditure on stem compared to leaf is increases as plants grow larger, the relationship between WD and growth may also strengthen in larger plants.
 
-As plants approach maximum height they increasingly divert energy away from growth and into reproduction (see \citealt{Thomas:1996do,Thomas-2011, Wenk:2014jz}).
+\textbf{H3: The relationship between Hmax and growth rate is expected to be absent in seedlings but to strengthen with increasing plant size}
+
+As plants approach maximum height they increasingly divert energy away from growth and into reproduction (see \citealt{Thomas:1996do,Thomas-2011, Wenk:2015jz}).
 For seedlings, where all individuals are investing solely in growth, we expect no influence of Hmax on growth.
@@
 
-\textbf{H4: The relationship between seed mass and relative growth rate is negative in seedlings, but weakens with increasing size.}
+Hmax affects growth via the fraction of energy allocated to vegetative growth versus to seed production ($dm_t/db$ in eq.
+\ref{eq:eq1}; Table \ref{tab:trade-offs}).
+For seedlings and seedlings this fraction is 1 for all species and so no effect is expected.
+But once some species begin to produce seed, then species closer to their Hmax value are expected to be allocating more to seed production and less to vegetative growth.
+Hence when comparing across plants at a given size, species with smaller Hmax are expected to show slower vegetative growth rates.
+
+\textbf{H4: The relationship between seed mass and RGR is negative in seedlings, but weakens with increasing size}
 
 The main effect of increased seed size is to produce a larger overall seedling.
-Under similar light conditions, relative growth rate decreases with size because the ratio of leaf area to total biomass decreases with increasing plant size.
-Thus, larger seedlings are predicted to have a lower relative growth rate during the earliest phases of growth \citep{Turnbull:2012ew}.
+Under similar light conditions, RGR decreases with size because the ratio of leaf area to total biomass decreases with increasing plant size.
+Thus, larger seedlings are predicted to have a lower RGR during the earliest phases of growth \citep{Turnbull:2012ew}.
 However, among larger plants we expect the effect of this initial size to be minimal, and thus the correlation between seed size and growth rate should disappear.
 
+The $\textrm{RGR}_{\textrm{mass}}$ slows as plants grow larger, and large-seeded species begin larger as seedlings.
+For larger plants, seed mass is not expected to have any distinct influence on growth rates  (Table \ref{tab:trade-offs}).
 \textbf{H5: The relationship between Aarea and growth rate is expected to be positive across all plant sizes, at least under high-light conditions}
@@
 
+The effects of benefits (higher assimilation) and costs (higher respiration) of increased Area occur within the same element of eq.
+\ref{eq:eq0}, and assimilation must outweigh respiration for there to be growth, so the net effect will be positive (Table \ref{tab:trade-offs}).
+
+Note that the predicted relationship between growth and either SLA or seed mass in seedlings differs if AGR in mass is used instead of RGR$_\textrm{mass}$ (i.e.
+becomes negative for SLA, positive for seed mass).
+In our study, all data recorded for these trait-stage combinations have been measured on a RGR base for mass (see Fig S9).
+
 \textbf{Effect on absolute and relative growth rates}
-Tree growth in diameter, height or mass can be expressed in either absolute (AGR) or relative terms (RGR).
-The choice of the growth measurement is generally confunded with the size of the plant; RGR in mass is mainly used for seedling, and AGR in diameter or height are mainly used for adult.
-According to the growth model, the predicted relationship between growth and seed mass in seedlings reverses if absolute AGR$_\textrm{mass}$ is used instead of RGR$_\textrm{mass}$ (see Appendix \ref{sec:growth}).
+Tree growth in diameter, height or mass can be expressed as either absolute growth rate (AGR) or relative growth rate (RGR).
+The choice of the growth measurement is generally confounded with the size of the plant; RGR in mass is mainly used for seedling, and AGR in diameter or height are mainly used for adult.
+According to the growth model, the predicted relationship between growth and seed mass in seedlings reverses if AGR$_\textrm{mass}$ is used instead of RGR$_\textrm{mass}$ (see Appendix \ref{sec:growth}).
 The correlation with RGR$_\textrm{mass}$ is negative but becomes positive with AGR$_\textrm{mass}$.
-For SLA, WD, Hmax and Aarea the predicted relationships are not affected by the growth measurement used.
-However RGR and AGR are fundamentaly different for a lot of ecologists.
+For SLA, WD, Hmax, and Aarea, the direction of the predicted relationship is not affected by the growth measurement used.
+However RGR and AGR are fundamentally different for a lot of ecologists.
 So we adopted a two steps approach, first we were conservative by focusing exclusively on RGR, then we compared results with those of a more inclusive dataset with both RGR and AGR.
@@
 
-We aimed to identify studies that measured the correlation between five prominent functional traits (SLA, WD, Aarea, Hmax and seed mass) and a growth measurement across species.
-Our literature search was conducted in two phases.
+We aimed to identify studies reporting the correlations, measured across species, between functional traits and one of several measures of growth  rate (Table \ref{tab:trade-offs}) .
+We supplemented records from our own bibliographic libraries with results from searching online databases and suggestions from other researchers.
+Systematic searches were conducted across the two most comprehensive bibliographic platforms: Google scholar and Web of Science (Thomson Reuters).
+While Web of Science guarantees a relatively stable and reproducible search environment, with clearly defined lists of indexed journals, its searches are limited to meta-data (i.e.
+title, keywords, and abstracts, \citealt{Beckmann:2012hn}).
+This limitation does not apply to Google Scholar, where all text that is electronically available on the internet is indexed.
 
-\subsubsection*{Phase 1 - Literature snapshot}\label{literature-snapshot}
+The biggest challenge when searching literature databases is to identify suitable studies from the vast corpus available.
+Initially we were interested to know whether data existed for a variety of traits; however the number of potential search terms made systemic searching for all these terms in Google Scholar impractical.
+A preliminary investigation of search results for a variety of traits on the Web of Science platform suggested that searching only on SLA and WD -- two of the most widely measured traits -- would capture  $\sim$80\% of search records that would be returned by searching for a wider range of traits (see Appendix \ref{app:literature-snapshot}).
+We therefore narrowed our searching to only cover these two main traits.
 
-We first developed a snapshot of the literature, to assess the potential to recover useful data from the wide corpus of literature available.
-This snapshot was obtained via Web of Science database (Thomson Reuters), between March and June 2014, using a range of Boolean search terms in English.
-Search terms were as follows: (``trait'' AND (``growth rate'' OR ``relative growth rate'')) AND (``tree*'' OR ``woody*''), where ``trait'' was allowed to be any of the trait names listed in Table \ref{tab:lit_search}.
-This snapshot indicated that 82\% of the reported correlations linking growth to any of our five core traits would be recovered by searching only on SLA and WD, allowing us to narrow our search considerably.
+Both Web of Science and Google Scholar databases were searched for records linking SLA and WD to growth rate.
+On Web of Science, we searched using  search terms: (``trait'' AND (``growth rate'' OR ``relative growth rate'')) AND (``tree*'' OR ``woody*''), where ``trait'' was either (``leaf mass per area'' OR ``specific leaf area'' OR ``leaf construction cost'') or (``wood density'' OR``WD'' OR ``wood specific gravity'' OR ``stem density'' OR ``stem specific density'' OR ``SSD'' ).
+On Google scholar we searched using terms: ((``SLA'' OR ``LMA'' OR ``specific leaf area'' OR ``leaf mass area'' OR ``wood density'' OR ``WD'' OR ``wood specific gravity'' OR ``stem density'' OR ``stem specific density'') AND (``growth rate'' OR ``relative growth rate'')) AND (``tree*'' OR ``woody*'').
+This keyword search in Google Scholar returned approximately 18900 papers.
+We examined all records returned from the Web of Science search (XXX) and the first 750 items from Google Scholar when ranked by ``relevance''.
+All searches were conducted between March and December 2014.
 
-\subsubsection*{Phase 2 - Systematic search}\label{systematic-search}
+In total we inspected the full text of 583 articles (see Appendix XXXX in Supplementary material for list).
+Individual studies had to report the following information to be included in our dataset: i) the relationship between growth and trait as a correlation coefficient, ii) the sample size and the number of species used to perform the correlation, and iii) the size or stage of plants.
+Despite searching only on SLA and WD, we recorded coefficient correlations for a list of 19 traits in total: the five for which we had prior expectations, plus any of 14 others commonly used in the trait literature.
+Where available, we also recorded the geographic coordinates, number of sites, experiment type (greenhouse, field experiment, forest, shade-house etc.), growth measure (relative or AGR measured using plant diameter, height or mass), vegetation type, life form (tree, woody or mixed with herbaceous species etc.), biological scale (interspecific, intraspecific or intragenus), and experimental treatments (e.g.
+fertilization, shade, salt stress).
+In some cases, we asked the authors for additional information about the specific correlation coefficient value when this was not already provided.
 
-While Web of Science guarantees a relatively stable and reproducible search environment, with clearly defined lists of indexed journals, its searches are limited to meta-data (i.e.
-title, keywords and abstracts, \citealt{Beckmann:2012hn}).
-This limitation does not apply to Google Scholar, where all text that is electronically available on the Internet will be indexed.
-Thus, we used Google Scholar to perform a more systematic search of the literature for SLA and WD.
-
-The Google Scholar database was searched using a range of Boolean search terms for SLA and WD: ((``SLA'' OR ``LMA'' OR ``specific leaf area'' OR ``leaf mass area'' OR ``wood density'' OR ``WD'' OR ``wood specific gravity'' OR ``stem density'' OR ``stem specific density'') AND (``growth rate'' OR ``relative growth rate'')) AND (``tree*'' OR ``woody*'').
-This keyword search in Google Scholar returned approx.
-18900 papers, from which we took the first 750 items when ranked by ``relevance''.
-These papers were examined in addition to those discovered in Phase 1.
-In addition, we gleaned data from other sources, using our own knowledge as researchers in the field (this included adding data from an in-review study by \citeauthor{Gleason:2016}).
-The complete list of studies where we inspected the full text is given in Appendix \ref{app:supp_info_files} in Supplementary material.
-
-Each study had to meet some basic criteria to be included in our analysis.
-We restricted our meta-analysis to documents reporting: i) the relationship between growth and trait as a correlation coefficient, ii) the sample size and the number of species used to perform the correlation, and iii) the size/stage of plants.
-Ultimately data was included from 112 different articles (starred references in bibliography).
-Where available, we also recorded the geographic coordinates, number of sites, experiment type (greenhouse, field experiment, forest, shade-house etc.), growth measure (relative or absolute growth rate measured using plant diameter, height or mass), vegetation type, life form (tree, woody or mixed with herbaceous species etc.), biological scale (interspecific, intraspecific or intragenus), and experimental treatments (e.g.
-fertilization, shade, salt stress).
-We asked the authors reporting a non-significant correlation for additional information about the specific correlation coefficient value when this was not provide.
-This allowed us to minimise publication bias via selective reporting of significant results within the published articles (e.g.
-a particular case of a ``failure to publish bias'' see \citealt{Jennions:2013ta}).
-
-Overall, we recorded coefficient correlations for a list of 19 traits (Fig.
+We recorded coefficient correlations for a list of 19 traits (Fig.
 \ref{fig:fig1}): the five for which we had prior expectations, plus 14 others commonly used in the trait literature.
@@
 Finally, the leaf area ratio and leaf mass ratio are indicators of resource distribution to leaf \citep{Lambers:1992bj}.
-According to the snapshot of the literature on Web of Science, 62\% of the literature for these 19 traits was captured by a search on SLA and WD.
+
+Ultimately, data was recorded from from 103 different articles \citep{Aiba:1997ho, Aiba:2009ft, Antunez:2001gk, Atkin:1998in, augspurger_light_1984, baltzer_physiological_2007, baraloto_differential_2006, baraloto_seed_2005, Bloor:2003fa,  Broncano:1998ck, Brown:1996ks, Bruhn:2000jz, Cai:2007ie, CamaraZapata:2003df, CastroDiez:1998gz, CastroDiez:2003jd, Cernusak:2008ds, Chao:2008hg, Chaturvedi:2011jx, Chaturvedi:2014ie, Chave:2009iy,  coomes_comparison_1998, coomes_greater_2009, Cornelissen:1996hf, Cornelissen:1997fd, Cornelissen:1998ta, Dalling:2004gs, DeBell:1994ix, Easdale:2009gv, fan_hydraulic_2012, Fayolle:2012bx, Fujimoto:2006fg, Galmes:2005fa, Gleason:2016, gleeson_plant_1994, grotkopp_toward_2002, Grubb:1996kr, Herault:2011dd, Hoffmann:2003ga, Huante:1995fd, Huante:1995tl, Huante:1998bk, HUNT:1997ge, Iida:2014ep, Iida:2014hq, king_influence_1994, king_tree_2005,  King:2006he, Kitajima:1994ez, Kohyama:2003dk, Kruger:2006fq, Lamers:2006dl, LopezIglesias:2014dk, Loveys:2002hj, Lusk:1997ga, Lusk:2002fma, Lusk:2013bq, Lusk:2013hz, MartinezVilalta:2010iq, McCormack:2012ch, Moya:2008ep, Muller-landau_interspecific_2004, Nascimento:2005kl, Osone:2008dr, Osunkoya:1994ip, Osunkoya:2010ef, Paz:2005kx, Poorter:1999fp, Poorter:2006vb, Poorter:2008iu, Poorter:2010co, Popma:1988tv, Prior:2004cv, Quero:2008jg, Read:2011du, Reich:1998ir, Reich:1998ja, Rossatto:2009gq, RuizRobleto:2005hc, Sack:2004hm, saldana-acosta_seedling_2009, SalgadoLuarte:2012ci, Saverimuttu:1996ih, Shen:2014fw, Shipley:2002fs, Stratton:2001ck, Thomas:1996do, Tomlinson:2014im, Veneklaas:2002dt, Villagra:2013do, Villar:2006cf, walters_are_1996, Walters:1993eu, Walters:1993hf, Wang:1998cs, Warren:2005bc, Westbrook:2011ja, Wright:1999ds, Wright:2000kw, Wright:2001gb, Wright:2003kb, Wright:2010tp, Zhang:1995bh}.
+
+% bib <- bibtex::read.bib("references/metaanalyses.bib")
+% paste(sort(names(x$keys)), collapse = ', ')
+% These studies dropped because not in list of top traits:
+% Bohlman:2006eo, Cochard:2007bn, Coley:1983hk,  Comas:2002wt, Comas:2004jza, King:2006dg, Poorter:2001fj, Schulze:2006ww,  Tjoelker:1999gp, Tobner:2013cv,
 
@@
 
-We were unable to obtain a consistent and continuous measure of plant size across all studies, thus we relied on categorical groupings by ``stage'' to test our hypotheses.
-The authors of the 112 articles used in this analysis reported their plants as belonging to any of five different stages: ``seedling'', ``juvenile'', ``sapling'', ``adult'', ``mixed''.
-While these categories have been established according to the expertise of the authors, by compiling data across multiple studies and vegetation types, we were concerned about the risk of assigning plants of similar size to different categories.
-This risk turned out to be negligible: overall, we found that the original thresholds in size/age used by the authors to distinguish different stages were relatively compatible (Fig.
+We used categorical groupings by plant ``stage'' to test our hypotheses regarding the effects of traits on growth rates.
+The authors of the 103 articles used in this analysis reported their plants as belonging to any of five different stages: ``seedling'', ``juvenile'', ``sapling'', ``adult'', ``mixed''.
+While these categories have been established according to the expertise of the authors, we were concerned about the risk of assigning plants of similar size to different categories when compiling data across multiple studies and vegetation types.
+This risk turned out to be small: overall, we found that the original thresholds in size/age used by the authors to distinguish different stages were relatively compatible (Fig.
 \ref{fig:fig2}).
@@
 There was also a clear break between saplings and adults in diameter (at 10 cm).
-According to simple allometric relationships between size variables plotted using data from the Biomass And Allometry Database \citep{Falster:2015}, the thresholds used for each stage transition align relatively well with one another across the different size measurements (age, height and diameter, Fig.
+Comparing these values to the bivariate relationships observed between variables (age, height, diameter) in the ``Biomass And Allometry Database'' \citep{Falster:2015}, demonstrated that the thresholds identified above for each stage transition also aligned relatively well with one another (Fig.
 \ref{fig:figA1}).
 Thus we adopted the above values as cut-offs for defining stage boundaries.
-However, the group ``juvenile'' was largely overlapping with the three others, and so we merged this category with one or the other on a case by case basis.
 
 Using the identified boundaries among stages we were able to assign all studies into one of three classes: ``seedling'', ``sapling'', or ``adult''.
-Using the above cut-offs we were also able to assign a stage category to studies for which no stage was distinctly mentioned by the authors (5\% of the articles, noted as ``mix'' in Fig.
+The group ``juvenile'' was largely overlapping with the three others, and so we merged this category with one or the other on a case by case basis.
+Using the above cut-offs, we were also able to assign a stage category to studies for which no stage was distinctly mentioned by the authors (5\% of the articles, noted as ``mix'' in Fig.
 \ref{fig:fig2}).
-Only 7 of 112 articles were ambiguous on their plant stage attribution.
+Only 7 of 103 articles were ambiguous on their plant stage attribution.
 Half of these equivocal cases involved the juvenile category.
@@
 Other equivocal cases were caused by ambiguity in the usage of ``adult'' by the authors.
-Some plants with a large stature were not described as adult by authors because they were still non reproductive \citep{King:2006dg,King:2006he}.
-Conversely plants with small stature -- because stunted by wind for example \citep{Stratton:2001ck}-- were sometimes assessed as adult when reproductive.
-For purposed of the present paper we attributed a study to the adult stage when the authors identified the plants as reproductive, and to sapling stage when they identified the plants as non-reproductive, regardless of the plant's size or age.
-Results using the categories established by the authors are similar to those using the standardized categories (see Fig.
-\ref{fig:figA6} model.1).
-In the main text, we report only results using the standardized categories.
+Some plants with a large stature were not described as adult by authors because they were still non reproductive \citep{King:2006he}.
+Conversely plants with small stature -- because stunted by wind for example \citep{Stratton:2001ck} -- were sometimes assessed as adult when reproductive.
+For purposes of the present paper, we attributed a study to the adult stage when the authors identified the plants as reproductive, and to sapling stage when they identified the plants as non-reproductive, regardless of the plant's size or age.
+We found that results using the original categories established by the authors were similar to those using the standardized categories (see Fig.
+\ref{fig:figA6}).
+Thus in the main text, we report only results using the standardized categories.
 
-\subsection*{Statistical analyses}\label{statistical-analyses}
+\subsubsection*{Measurements under ideal conditions}\label{ideal-vs-entire-dataset}
+
+Compiled data included studies differing in the growth measurement used (RGR or AGR), the number of species, the experimental conditions (stressed vs unstressed), and the concordance between stage used to measure trait and growth rate.
+To assess whether such factors influenced our results, we investigated whether results changed between the entire dataset and a more conservative subset.
+The entire dataset includes all noted correlations.
+A second ``ideal'' subset, included only studies recording RGR across \underline{\textgreater} 10 species, under unstressed conditions, and where growth rates and traits were measured on plants from the same stage (expect for Hmax and seed mass, where a particular stage is by definition required to measure the trait).
+
+\subsection*{Statistical analysis}\label{statistical-analyses}
 
@@
 
-To measure of effect size, we used the cross-species Pearson product-moment correlation coefficient $r$ between growth rate and trait, weighted by the number of species contributing to the relationship.
-For studies that reported another coefficient -- such as coefficient of determination, Spearman's rho rank correlation, or Kendall's tau rank correlation -- we converted these to correlation coefficients following \citet{Lajeunesse:2013tm}.
+To measure effect size, we used the cross-species Pearson product-moment correlation coefficient $r$ between growth rate and trait, weighted by the number of species contributing to the relationship.
+Results from studies that reported another coefficient -- such as coefficient of determination, Spearman's rho rank correlation, or Kendall's tau rank correlation -- were converted to correlation coefficients following \citet{Lajeunesse:2013tm}.
 As the magnitude of Pearson's correlation coefficient approaches $\pm$ 1.0, its distribution becomes skewed.
@@
 The transformation was achieved via Fisher's z-transformation,
-\[ z = \frac{1}{2} \ln \frac{1+r}{1-r}\]
+\[ z = \frac{1}{2} \ln \frac{1+r}{1-r},\]
 which has a variance estimate of
-\[ v_z= \frac{1}{n-3}\]
+\[ v_z= \frac{1}{n-3},\]
 where $n$ is the number of species.
 We weighted effect size by the number of species used to calculate the correlation, instead of the raw number of individuals, because our questions primarily concerned the correlation between growth and traits across species and not within species.
+Throughout we report means and 95\% confidence intervals (CI) on effect size.
 
@@
 
-We tested stage effect on traits for which $>$ 15 correlation coefficients across at least two stages were recorded.
-We used a mixed-effect model of meta-analysis, in which it is assumed that studies within a stage share a common mean effect but that there is also random variation among studies in a stage, in addition to sampling variation \citep{Zuur:2009cfa}.
-This random effect allows us to account for the heterogeneity among studies (e.g.
-experimental type, vegetation type, error, etc.).
-For each trait, we established whether stage could explain variance in $z$ by comparing models with the stage variable to the null model using log-likelihood ratios \citep{Zuur:2009cfa}.
-If the log-likelihood test returned a significant p-value, the stage model fitted the data better than the null model.
-Estimates of the effect size for each stage were considered significant if the 95\% confidence intervals did not overlap with zero.
+We tested an effect of plant stage on the relationship between growth rate and traits using a mixed-effect model, in which it was assumed that studies within a stage shared a common mean effect, but that there was also random variation among studies, in addition to sampling variation \citep{Zuur:2009cfa}.
+Inclusion of this random effect allowed us to account for heterogeneity among studies, for example in experimental type, and vegetation type.
+For each trait, we established whether stage could additional explain variance in $z$ by comparing models with a without a stage effect  using log-likelihood ratios \citep{Zuur:2009cfa}.
+If the log-likelihood test returned a significant p-value, the stage model fitted the data better than the model without.
+Estimates of the effect size for each stage were considered significant if the CIs did not overlap with zero.
 
-\subsubsection*{"Ideal" vs "complete" dataset}\label{ideal-vs-complete-dataset}
+\subsubsection*{Quality criteria for meta-analyses}
 
-In addition to the chosen criteria for the meta-analyses, the growth measurement used (relative growth rate-RGR or absolute growth rate-AGR), the number of species, the experimental conditions (stressed vs unstressed), and the concordance between stage used to measure trait and growth are clear criteria for assessing the quality of the data for addressing our hypotheses.
-Thus we stratified the data set into two subsets: one including only studies on RGR, under unstressed conditions and measuring a correlation coefficient at least across 10 species (’ideal’ dataset), and the other set including studies under all conditions (’complete’ dataset).
-We excluded from the ”ideal” dataset studies where growth and traits were measured on plants from different stages, unless a particular stage was by definition required to measure the trait, such as for seed mass (i.e.
-seed stage), or Hmax (i.e.
-adult stage).
-
-\subsubsection*{Quality criteria for meta-analysis}
-
-\cite{Koricheva:2014ku} outlined 14 methodological quality criteria to ensure robust results from meta-analyses.
-Table \ref{tab:meta} outlines how we addressed each of these.
-In particular, we quantified heterogeneity in effect size, we tested for publication bias and we explored temporal change in effect size (see Appendix \ref{app:supp_info_analyses}).
+\citet{Koricheva:2014ku} outlined 14 methodological criteria to ensure robust results from meta-analyses.
+Table \ref{tab:meta} summarises how we addressed each of these.
+In particular, we i) quantified heterogeneity in effect size, ii) tested for publication bias, and iii) explored temporal change in effect size (see Appendix \ref{app:supp_info_analyses}).
 We also tested how robust our results were to the decisions made in the analysis.
-In particular, we tested the sensitivity of our results to inclusion of studies that measured a same trait-growth correlation across different conditions (e.g.
-vegetation type, sites, environemental conditions).
-The idea is to check that our results were not generated by the dominance of one or few studies reporting several values for the same trait.
+Specifically, we assessed the sensitivity of our results to inclusion of studies reporting multiple trait-growth correlation across different conditions (e.g.
+vegetation type, sites, environmental treatment).
 In the case of multiple comparisons within a study, we used the method proposed by \citet{Borenstein:2009um}: we calculated the mean correlation coefficient by trait and by study, and then re-calculated the effect size.
@@
 
-\subsection*{Availability of code and data}\label{code}
+\subsubsection*{Software}
 
-All analyses were conducted with R software \citep{Ralanguageanden:2014wf}.
-The code and data for producing all figures and results in this paper is available at \smurl{github.com/AnaisGibert/Growth\_trait\_metaanalysis}.
+All analyses were conducted with \texttt{R} software \citep{Ralanguageanden:2014wf} using packages \texttt{lme4} \citep{Bates-2014}.
+\texttt{metafor} \citep{Viechtbauer-2010}, and \texttt{gpplot2} \citep{Wickham:2009}.
 
@@
 
+\subsection*{Trait coverage}
+In total, 103 articles containing 551 correlations linking growth rate to any of the 19 traits  across a range of plant stages were identified (Fig.
+\ref{fig:fig1}).
+Considering only our top five traits of interest, the number reduced to 93 articles and 267 correlations.
+For measurements under ideal conditions, we identified only 55 studies with 137 correlations.
+The main results reported here were obtained with this ``ideal'' subset of data.
+These were then compare against results obtained with the entire dataset.
+
+% x <- remake::make("CleanData")
+% unqiue(x$ref)
+% nrow(x)
+% x <- remake::make("CompleteData")
+% unique(x$ref)
+% nrow(x)
+% x <- remake::make("IdealData")
+% unique(x$ref)
+% nrow(x)
+
 \subsection*{Main effects}
 
-Contrary to our expert expectation, a few number of study reported a trait-growth correlation and meet our basic criteria (112 articles, $n = 216$).
-The main results reported here were obtained with an even more conservative approach ($n = 98$), and were thereby confined to correlations with RGR, across at least 10 species, under non-stressed conditions, and for which the source of trait and growth was controlled (i.e.
-"ideal" dataset).
+Overall, results were consistent with predictions, although with limitations arising for some traits due to very unequal numbers of observations between growth stages.
 
-For SLA the correlation between RGR and the trait changed significantly with plant size in the manner expected.
-Model fit improved when stage was incorporated (see log likelihood ratio tests, Fig.
-\ref{fig:fig3} a; average values for the coefficients ($\bar{r}$) in Fig.
-\ref{fig:figA4} a-e).
-The correlation between RGR and SLA shifted from strongly positive at seedling stage $\bar{r}=0.6 \pm 0.08$, Mean $\pm$ SD) to not significantly different from zero at adult stage ($\bar{r}= -0.01 \pm 0.07$, CI 95\% overlapping zero in Fig.
-\ref{fig:fig3} a).
+For SLA, the correlation between RGR and the trait changed significantly with plant size in the manner expected (Fig.
+\ref{fig:fig3}a).
+The correlation between RGR and SLA shifted from strongly positive at seedling stage ($\bar{r}=0.6 \pm 0.08$, Mean $\pm$ SD) to not significantly different from zero at adult stage ($\bar{r}= -0.01 \pm 0.07$, CI 95\% overlapping zero).
 The correlation coefficients recorded at sapling stage were intermediate between seedling and adult stages.
+Model fit improved significantly when stage was incorporated (see log likelihood ratio tests, Fig.
+\ref{fig:fig3}a; average values for the coefficients ($\bar{r}$) in Fig.
+\ref{fig:figA4}a-e).
 
-For WD, Hmax and seed mass, correlations with RGR were also consistent with expectations, although with limitations arising from very unequal numbers of observations between growth stages for some traits.
-Indeed, confidence intervals of r often spanned zero especially where there were small numbers of studies for particular growth stages, precluding strong conclusions.
-For WD, results were consistent with negative correlations with RGR across all plant sizes (Fig.
-\ref{fig:fig3} b, model fit not improved when stage was incorporated).
-Note that the confident intervals were not crossing zero for sapling and seedling stage despite small sample sizes (n= 4 and 1 respectively), meaning a strong correlation and /or a good consistency in the coefficient reported for each stage across studies.
+For WD, Hmax, and seed mass, correlations with RGR were also consistent with expectations, although our ability to test all hypotheses was at times limited due to low sample size.
+Indeed, CIs of $r$ often spanned zero especially where there were small numbers of studies for particular growth stages, precluding strong conclusions.
+For WD, results were consistent with the prediction for negative correlations with RGR across all plant sizes (Fig.
+\ref{fig:fig3}b).
+Accordingly, model fits were not improved when stage was incorporated.
+Note that the CIs were not crossing zero for sapling and seedling stage despite the small sample sizes (n= 4 and 1 respectively), meaning a strong correlation and /or a good consistency in the coefficient reported for each stage across studies.
 
@@
 At sapling stages, the correlation between Hmax and growth was not significantly different from that observed at adult stage (model fit not improved when stage was incorporated, see log likelihood ratio tests in Fig.
-\ref{fig:fig3} c, and confident intervals overlapping), but also was consistent with no correlation (Fig \ref{fig:fig3} c, confidence intervals overlapping zero), due to much smaller numbers of replicate studies.
+\ref{fig:fig3}c, and CIs overlapping), but also was consistent with no correlation (Fig \ref{fig:fig3}c, CIs overlapping zero), due to much smaller numbers of replicate studies.
 We could not distinguish between these alternatives.
 
-As expected for seed mass, the correlation with RGR shifted from negative at seedling stage ($\bar{r}= -0.5 \pm 0.07$) to not significantly different from zero at adult and sapling stages (Fig \ref{fig:fig3} c, confidence intervals overlapping zero).
-Hovever, the correlation between seed mass and RGR at adult and sapling stages were also not significantly different from that observed at seedling stage (see log likelihood ratio tests and confident intervals overlapping in Fig.
-\ref{fig:fig3} c).
+As expected for seed mass, the correlation with RGR shifted from negative at seedling stage ($\bar{r}= -0.5 \pm 0.07$) to not significantly different from zero at adult and sapling stages (Fig \ref{fig:fig3}c, CIs overlapping zero).
+However, the correlation between seed mass and RGR at adult and sapling stages were also not significantly different from that observed at seedling stage (see log likelihood ratio tests and CIs overlapping in Fig.
+\ref{fig:fig3}c).
 Again we could not distinguish between these alternatives.
-But unlike Hmax, the number of coefficent reported for seed mass was almost similar between adult (n= 7) and seedling (n= 10) stages, suggesting that confident interval overalapping zero at adult stage were due to variation in correlation coefficient reported rather than to a much smaller numbers of replicates.
+But unlike Hmax, the number of coefficient reported for seed mass was almost similar between adult (n= 7) and seedling (n= 10) stages, suggesting that CIs overlapping zero at adult stage were due to variation in correlation coefficient reported rather than to a much smaller numbers of replicates.
 
 For Aarea, results were consistent with a positive correlation with RGR at seedling stage.
-However, no conclusion can be drawn about a change along plant stages; only four correlation coefficients were reported for this trait, and three of them were measured at the seedling stage (Fig.
-\ref{fig:fig3} e).
+However, no conclusion can be drawn about a change along plant stages; as only four correlation coefficients were reported for this trait, and three of these were measured at the seedling stage (Fig.
+\ref{fig:fig3}e).
 
-\subsection*{Results with an inclusive approach}
+\subsection*{Sensitivity of results to analysis decisions}
 
-We also reported results from a more complete dataset, to determine if additional data could reinforce or in contrast overcast some of our conclusions.
-This ''complete'' dataset included correlations measured with both absolute and relative growth rate (Fig.
-\ref{fig:fig4}), across at least two species, and did not required any control for the source of trait or growth (i.e.
-both could be measured on different stages) and for the environemental conditions.
-This release of criteria enlarged in a considerable extent the number of replicates ($n = 216$).
+The above results were generated using data measured under ``ideal'' conditions: unstressed growth, growth measured as RGR, traits and growth recorded in same stage, \underline{\textgreater} 10 species.
+We now report results from the entire dataset, to determine if additional data would alter our conclusions.
+This entire dataset included correlations measured with both AGR and RGR (Fig.
+\ref{fig:fig4}), across at least two species, and did not control for the source of trait or growth (i.e.
+both could be measured on different stages) or environmental conditions.
+These relaxed criteria considerably increased the number of replicates, from $n = 137$ to $n = 267$ correlations.
+These additional replicates were unequally distributed across trait-stage combinations.
+Some trait-stage combinations already with a lot of data got even more support (e.g.
+from 25 to 59 correlation coefficients reported for SLA at seedling stage), while others still had few replicates.
+On the 13 traits-stage combinations studied in total, six had \textless five correlation coefficients: (i.e.
+WD-seedling, Hmax-sapling, Hmax-seedling, Seed mass-sapling, Aarea-adult and Aarea-sapling.
 
-The ''complete'' dataset generated similar effect sizes to those reported above for SLA, WD, Hmax and seed mass, and led to similar conclusions (Fig.
+% x <- remake::make("CompleteData")
+% nrow(x)
+
+Effect sizes and overall results using the entire dataset were similar to those reported above using the ``ideal'' subset (Fig.
 \ref{fig:fig4}).
-This supports the robustness of the analysis using the conservative approach ('ideal dataset').
-For Aarea, additional replicates from the ''complete'' dataset allowed to compare the effect size across plant stage.
-The results were consistent with a positive correlations with RGR across adult and seedling stages (Fig \ref{fig:fig4} e; CI not overlapping zero).
+For Aarea, the additional replicates in the entire dataset allowed us to compare the effect size across plant stage.
+The results were consistent with the prediction for a positive correlation with RGR across adult and seedling stages (Fig \ref{fig:fig4}e; CI not overlapping zero).
+Comparison of Aarea effect  between the ``ideal'' subset (Fig.
+\ref{fig:fig3}d) and entire dataset (Fig.
+\ref{fig:fig4}d), indicated little effect of stress (here mainly low light) on the correlation with RGR at seedling stage; as the correlation was still positive  when 8 correlations measured under low light conditions were added.
 
-The comparison of Aarea effect size between "ideal" (Fig.
-\ref{fig:fig3} d) and "complete" (Fig.
-\ref{fig:fig4} d) dataset, showed no signal of an effect of stress (here mainly low light) on the correlation with RGR at seedling stage; the correlation was still positive between Aarea and RGR even when 8 correlations measured under low light conditions were added.
+For some trait-stage combinations, it was possible to compare results between RGR and AGR.
+For both WD and Hmax, effects size measured with RGR or AGR were no different at adult stage; CIs were overlapping despite equal sample size (Fig \ref{fig:fig4}b-c).
+For seed mass, effects size differed significantly between RGR and AGR at seedling stage; as expected the correlation with RGR was positive and shifted to non significant with AGR (Fig \ref{fig:fig4}d; CI not overlapping).
 
-The comparison between RGR and AGR was possible for some trait-stage combinations.
-For seed mass, effects size differed significantly between RGR and AGR at seedling stage; as expected the correlation with RGR was positive and shifted to non significant with AGR (Fig \ref{fig:fig4} d; CI not overlapping).
-For both WD and Hmax, effects size measured with RGR or AGR were no differents at adult stage; CI were overlapping despite equal sample size (Fig \ref{fig:fig4} b and c).
+\subsection*{Tests for bias in sampling}
 
-New replicates from the complete dataset were not equally distributed across all trait-stage combinations.
-Some trait-stage combinations already well studied got even more support (e.g.
-from 25 to 59 correlation coefficients reported for SLA at seedling stage), but other still had few replicates.
-Thus, on the 13 traits-stage combinations studied in total, six were only supported by five or less correlations coefficient (i.e.
-WD-seedling, Hmax-sapling, Hmax-seedling, Seed mass-sapling, Aarea-adult and Aarea-sapling).
+Given our basic conclusion that reported correlations responded to plant size in a manner consistent with expectations from theory, we assessed the coverage of the available data, to determine if biased sampling could have erroneously generated the above results.
 
-\subsection*{Coverage of dataset}
-
-Given our basic conclusion that reported correlations responded to plant size in a manner consistent with expectations from theory, we assess now the coverage of the available data, to determine if biased sampling could have erroneously generated the above results.
-
-In total, we found only 112 studies published between between 1983 and 2014 that met our requirements.
+In total, we found only 103 studies published between between 1983 and 2014 that met our requirements.
 Climate zones spanned from temperate regions to tropics (map in Fig.
@@
 Different experiment types (laboratory, field, plantation or greenhouse), growth measurements and growth form (tree, woody or across growth form) were included.
-Number of species used for each correlation ranged from 2 to 300 species with average 31.
-Given this variety, it was not surprising to find wide ranges of $r$ reported for all traits.
+The number of species used for each correlation ranged from 2 to 300 species, with an average of 31.
+Given this variety, it was not surprising to find a wide range of $r$ reported for each trait.
 For instance, $r$ varied from -0.98 to 0.99 for SLA, and from -0.74 to 0.74 for WD (Fig.
@@
 Growth form, experiment type and growth measurement type were not strong predictors in general (Fig.
-\ref{fig:figA6}), and confounding with these factors is not a likely explanation of the major results reported.
+\ref{fig:figA6}); suggesting confounding with these factors is not a likely explanation of the major results reported.
 
 Overall our study met quality criteria expected for meta-analysis in ecology (Table \ref{tab:meta}).
-The impact of publication bias was probably trivial (Appendix E, Fig.
+The impact of publication bias was seemingly trivial (Appendix E, Fig.
 \ref{fig:figA7}).
-The extent of heterogeneity was high, but was substantially explained by the plant stage effect for SLA and seed mass, as expected (Appendix E).
-Finally, there was no indication of a temporal change in the effect size being reported within stages (Appendix E, Fig.
+The extent of heterogeneity was high, but was substantially explained by our core hypothesis of a plant stage effect for SLA and seed mass (Appendix E).
+There was no indication of a temporal change in the effect size being reported within stages (Appendix E, Fig.
 \ref{fig:figA9}).
-
 Finally, our results were unlikely to be biased by dominance of one or a few studies that measured a large number of responses, since when multiple responses were condensed into a single average within a trait and within a study, outcomes were very similar (Fig.
@@
 The meta-analysis reported here demonstrates that for several key traits, the influence of the trait on growth rate changes as plants grow from small to large.
-While the possibility has been raised recently that trait-growth correlations may change systematically with size \citep{Falster:2011ii, Ruger:2012jv, Iida:2014ep, Iida:2014hq}, this is the first time that specific mechanistic hypotheses have been corroborated by meta-analysis of existing literature.
+While the possibility has been raised recently that trait-growth correlations may change systematically with size \citep{Falster:2011ii, Ruger:2012jv, Iida:2014ep, Iida:2014hq}, this is the first time that specific mechanistic hypotheses have been corroborated against a wide array of existing studies.
 Meta-analysis allowed us to generalize and thus to reach a consensus about the effect of traits on growth.
-Growth rates are known to change with size through ontogeny \citep{Condit:1993hd, Clark:1999ed, Herault:2011dd}, in other words plants follow a growth trajectory.
-Species traits should be understood as influencing this trajectory and potentially re-ranking growth rates between species as size increases.
-This is a shift in outlook compared to much present thinking whereby traits are seen as rendering species fast-growing or slow-growing throughout life.
+Growth rates were already known to change with size through ontogeny \citep{Condit:1993hd, Clark:1999ed, Herault:2011dd}, in other words individual plants follow a growth trajectory.
+Our results suggest species traits should be understood as influencing this trajectory and potentially re-ranking growth rates between individuals from different species as their size increases.
+This is a shift in outlook compared to much present thinking, whereby traits are seen as rendering species fast-growing or slow-growing throughout life.
+
+TODO: XXXX Something about limited amount of data
 
@@
 For five prominent traits, the patterns observed were consistent with specific predictions from a mechanistic growth model.
-This is coherent with the mechanisms through which traits affect growth being correctly understood in the model.
-Other mechanisms could also generated these patterns and we discussed them in the discussion.
+This suggests the mechanisms through which traits affect growth may be correctly understood in the model.
 For SLA the meta-analysis confirmed quite strongly the predicted influence of plant size on the trait-growth correlation.
@@
 Several authors have suggested that the disappearance of SLA's influence on growth might be due to a disproportionate accumulation of leaf area by low SLA species \citep{Reich:1992wm,Poorter:2008iu,Wright:2010tp}, yet it remains unclear whether such a mechanism works as intended.
-Further, the assumed empirical relationship between SLA and total leaf area does not hold true as a generalisation across large number of species (\citeauthor{Duursma-2015}, in review).
+Further, the assumed empirical relationship between SLA and total leaf area does not hold true as a generalisation across large number of species \citep{Duursma-2015}.
 In the model described here, the mechanism is slightly different: high-SLA species incur faster leaf turnover, the cost of which outweighs the benefits of cheap leaf construction at larger sizes.
@@
 It should be noted however that there are few data available to test this proposition at seedling stage (n=1-5).
-In our model (Appendix \ref{sec:growth}) cheaper stem construction is responsible for the predicted negative correlation.
+In our model, cheaper stem construction is responsible for the predicted negative correlation.
 Lower xylem conductance and associated lower photosynthetic potential have also been suggested \citep[reviewed by][]{Chave:2009iy}.
-For seedlings a negative correlation arose regardless wood density was measured on adult plants, or calculated as seedling stem segment dry weight over its volume (i.e.
+For seedlings a negative correlation arose regardless WD was measured on adult plants, or calculated as seedling stem segment dry weight over its volume (i.e.
 stem density in  \citealt{CastroDiez:1998gz}), suggesting that both measurements could be used.
@@
 As far as we are aware, our study is the first to compare Aarea and growth correlations between small and large plants.
-In the growth model (Appendix \ref{sec:growth}), a consistent correlation irrespective of size arises from a direct effect of Aarea on plant growth rate.
+In the growth model, a consistent correlation irrespective of size arises from a direct effect of Aarea on plant growth rate.
 Meta-analyses showed a positive correlation for adult and seedling but not for saplings (n=3).
@@
 
-\section*{Acknowledgments}\label{Acknowledgment}
+\section*{Acknowledgements}\label{Acknowledgment}
 
 We thank Andrea Stephens for helpful comments on the meta-analyses, and Sean Gleason et al for pre-publication access to their data.
-Charles Warren and Jordi Martìnez-Vilalta kindly provided additional information about their published results.
+Charles Warren and Jordi Mart{\'i}nez-Vilalta kindly provided additional information about their published results.
 This work was funded by the Australian Research Council through a fellowship to M.W, a discovery grant to D.S.F and a Macquarie University Research Fellowships to E.F.G.
+
+\subsection*{Availability of code and data}\label{code}
+
+The code and data for producing all figures and results in this paper is available at \smurl{github.com/AnaisGibert/Growth\_trait\_metaanalysis}.
+Upon publication, a copy of the data set will also be made available in the Dryad Digital Repository.
 
@@
 \linespread{1}
-
-\nocite{*}
 
@@
 \centering
-\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/Fig1.pdf}
-\caption{Number of recorded correlations between trait and growth rate in our dataset, by size and trait.
-Traits are: Aarea (or Amass) = rate of CO$_{2}$ assimilation per unit leaf area (or leaf mass) = maximum photosynthetic rate, Hmax = asymptotic maximum height,  Ks = stem hydraulic conductance, LA = leaf area, LMR = leaf mass ratio, NARarea = net mass assimilation rate per unit of leaf area, Nmass (or Narea) = nitrogen content per unit of leaf mass (or leaf area), Pmass = phosphorus content per unit of leaf mass, SA/LA = sapwood area per leaf area, SLA = specific leaf area, thickness = leaf thickness, Vessel size = stem conduit size, vessel density = stem conduit density, WD = wood density.
-Results shown here are the ''complete'' dataset (see methods for details).}
-\label{fig:fig1}
+\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/Fig2.pdf}
+\caption{The range of plant sizes and stage recoded in original publications (coloured lines), compared to standardised thresholds used in the analysis (black lines).
+Horizontal line segments indicate the size range (max., min.) for the plants used to measure growth.
+The solid vertical lines indicate the thresholds used to classify plants in one of three stages.
+Studies mark with a ``*'' were those where stage was changed, compared to the original publication.
+Studies marked with ``+'' are those where plants came from different growth form.}
+% TODO: Anais -- what does different growth form mean?
+\label{fig:fig2}
 \end{figure}
@@
 \centering
-\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/Fig2.pdf}
-\caption{The range of plant sizes and stage recoded in original publications, compared to standardised thresholds used in the analysis. Panels are for
-a) age, b) height and c) diameter.
-Horizontal line segments indicate the size range (max., min.) for the plants used to measure growth.
-Study IDs correspond to the reference number in our dataset.
-Colours denote stage information given by the authors.
-The solid vertical lines indicate the thresholds used in our analysis.
-"*" indicated when a stage reassignment is needed.
-"+" on left side of the graph indicate cases where plants came from different growth form.}
-\label{fig:fig2}
+\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/Fig1.pdf}
+\caption{Number of recorded correlations between trait and growth rate in our dataset, by size and trait.
+Traits are: Aarea (or Amass) = rate of CO$_{2}$ assimilation per unit leaf area (or leaf mass) = maximum photosynthetic rate, Hmax = asymptotic or maximum height,  Ks = stem hydraulic conductance, LA = leaf area, LMR = leaf mass ratio, NARarea = net mass assimilation rate per unit of leaf area, Nmass (or Narea) = nitrogen content per unit of leaf mass (or leaf area), Pmass = phosphorus content per unit of leaf mass, SA/LA = sapwood area per leaf area, SLA = specific leaf area, Thickness = leaf thickness, Vessel size = stem conduit size, Vessel density = stem conduit density, WD = wood density.
+Results shown are from the entire dataset (see methods for details).}
+\label{fig:fig1}
 \end{figure}
@@
 \caption{The relationship between relative growth rates (RGR) and traits changes with plant stage and trait.
-Plots show the effect size (+ 95\%CI) for the average correlation across species, by plant stage.
+Plots show the effect size (+ 95\% confidence intervals; CI) for the average correlation across species, by plant stage.
 Effect size is a standardized measure of the deviation of correlation coefficient from zero (Fisher's z-transformed).
-Effects are significant if confidence intervals (95\%CI) for a given stage do not overlap with zero.
+Effects are significant if CIs for a given stage do not overlap with zero.
 Trait names as in Fig.
@@
 Likelihood Ratio Tests (LRT) compared maximum-likelihood fits between a pooled model and one separated by stage.
-A significant p-value means the model including stage effect fitted the data better than the null model.
+A significant p-value means adding a stage effect to the model significantly improved model fit.
 Results shown are from the ideal dataset (see methods for details).}
@@
 The legend is identical to Fig 3, with two exceptions.
-i) Results shown are from the "complete" dataset (see methods for details).
-ii) Likelihodd Ratio Tests were calculated on effect size combining RGR and AGR exclusively.}
+i) Results shown are from the entire dataset (see methods for details).
+ii) Likelihood Ratio Tests were calculated on effect size combining RGR and AGR exclusively.}
 \label{fig:fig4}
@@
 \centering
-\caption{Check-list of quality criteria for meta-analysis in ecology developed by Koricheva and Gurevitch (2014) }
+\caption{Check-list of criteria for meta-analysis in ecology developed by \citet{Koricheva:2014ku}.}
 {\footnotesize
@@
   \hline
-  & Quality criteria & Check & How and where is it addressed? \\
+  & Quality criteria & Check & How and where is it addressed?\\
   \hline
-  1.& Reporting full details of bibliographic searches & yes	& We provided complete details of bibliographic searches (i.e.
-electronic reference data bases that were searched, keywords, language and search dates) in sub-section "Phase 2 - Systematic search" in material and method.\\
-  2.& Reporting inclusion or exclusion criteria & yes & We specified several inclusion criteria in the sub-section "Phase 2 - Systematic search" in material and method.
-The Bibtex file `read.bib` on Github reports all the articles consulted but not used.\\
-  3.& Weighting effect sizes by study precision & yes & Effects sizes were weighted by number of species. See	 details in sub-section ``Effect size calculation'' in material and method.\\
- 4.& Specifying meta-analytical model &	yes	& We used a mixed-effect model with a study ID as a random variable, and stage as a fixed effect.
-See details in sub-section "Stage effect" in material and methods.
+  1.& Reporting full details of bibliographic searches & yes	& Complete details of bibliographic searches (i.e.
+electronic reference data bases that were searched, keywords, language, and search dates) are available in the ``Material and Methods''.\\
+  2.& Reporting inclusion or exclusion criteria & yes & Inclusion criteria are specified in the ``Material and Methods''.
+A full list of all articles evaluated is available in the Appendix \ref{app:literature-snapshot}.\\
+  3.& Weighting effect sizes by study precision & yes & Effects sizes were weighted by number of species. See	``Material and Methods'' for details.\\
+ 4.& Specifying meta-analytical model &	yes	& We use a mixed-effect model with a study ID as a random variable, and stage as a fixed effect.
+See ``Material and Methods'' for details.
 Results are shown in Fig.
 \ref{fig:fig3}.\\
- 5.& Quantifying heterogeneity in effect sizes &	yes &	We estimated the extend of the heterogeneity using the statistics $I^{2}$ for each trait. See details of methods and results in Appendix E.\\
- 6.& Exploring causes of heterogeneity & yes &	We explored the effect of stage, and the year of publication (see points 4 and 10 in this list). \\
- 7.& Multifactorial analysis of explanatory variable	& yes & We checked if no one of several other explanatory moderators (i.e.
-growth measurement, experiment type or growth form) would not consistenly be a strongest predictor of the data.
-We did not test the multiple variables in a hierarchical fashion, because of the limited size of our dataset.
-See in Fig.
-\ref{fig:figA4} f-j and in Fig.
-\ref{fig:figA6}.\\
+ 5.& Quantifying heterogeneity in effect sizes &	yes &	We estimate the extent of heterogeneity for each trait using the $I^{2}$ statistic. See Appendix \ref{app:supp_info_analyses} for details.\\
+ 6.& Exploring causes of heterogeneity & yes &	We explore the effect of stage, and the year of publication (see points 4 and 10 in this list).\\
+ 7.& Multifactorial analysis of explanatory variable	& yes & We check whether several other explanatory moderators (i.e.
+growth measurement, experiment type or growth form) are consistently the strongest predictors of the data.
+We do not test the multiple variables in a hierarchical fashion, because of the limited size of our dataset.
+See in Figs \ref{fig:figA4}f-j \& \ref{fig:figA6}.\\
   8.& Testing for publication bias &	yes	& We used several methods (i.e.
-funnel plots, the ``trim and fill'' method and the Rosenberg’s fail-safe number).
-See details of methods and results in Appendix E and in Fig.
-\ref{fig:figA7}.\\
-  9.& Sensitivity analysis &	yes &	See details in sub-section "Sensitivity analysis" in material and method. See results in Fig. \ref{fig:fig3} and Fig. \ref{fig:figA5}  \\
-  10.& Exploring temporal changes in effect size &	yes	& See details of methods and results in Appendix E and Fig. \ref{fig:figA9}. \\
-  11.& Controlling for phylogeny &	no &	It was not possible to control by the phylogeny since the number of species used to measured each coefficient of correlation ranged from 2 to 300 species.\\
-  12.& Specifying the software used &	yes	& See sub-section ``Availability of code and data'' in material and methods\\
- 13.& Providing reference list of primary studies included in the analysis &	yes &	See sub-section ``Availability of code and data'' in material and methods.
-The Bibtex file `meta-analyses.bib` corresponds to all the articles included in the meta-analyses.
-\\
-  14.& Providing the data set used for meta-analysis  &	yes &	A copy of the complete data set is available on Github.
-See ``Availability of code and data'', section "Statistical analysis" in material and methods.
-\\
+funnel plots, the ``trim and fill'' method, and Rosenberg's fail-safe number).
+See Appendix \ref{app:supp_info_analyses} for details.\\
+  9.& Sensitivity analysis &	yes &See ``Material and Methods'' for details, results in Figs \ref{fig:fig3} \& \ref{fig:figA5}.\\
+  10.& Exploring temporal changes in effect size &	yes	& See Appendix \ref{app:supp_info_analyses} for details.\\
+  11.& Controlling for phylogeny &	no &	It was not possible to control by the phylogeny, since the number of species used to measured each coefficient of correlation ranged from 2 to 300 species.\\
+  12.& Specifying the software used &	yes	& See sections in ``Material and Methods'' and ``Availability of code and data''.\\
+ 13.& Providing reference list of primary studies included in the analysis &	yes &	All articles from which data were extracted are cited in the paper.\\
+  14.& Providing the data set used for meta-analysis  &	yes &	A copy of the data set is available. See ``Availability of code and data'' for details.\\
    \hline
@@
 
-\section{Derivation of hypotheses from growth equations}\label{sec:growth}
-
-We adapted growth equations from \cite{Falster:2011ii} to generate hypotheses on both absolute and relative growth rates in mass (eqn \ref{eq:eq1}), height (eqn \ref{eq:eq2}) and diameter (eqn \ref{eq:eq4}).
-
-The rate at which \textbf{live biomass} $b$ is produced by a plant is given by:
-
-\begin{equation}\label{eq:eq0}
-\underbrace{\frac{db}{dt}}_{\text{net live biomass production}} = \underbrace{y}_{\text{yield}}  \big(\underbrace{a_{l} A_{\textrm{area}}}_{\text{photosynthesis}} - \underbrace{\sum_{i = l,s,r,f} m_{i} r_{i}}_{\text{respiration}}\big) - \underbrace{ \sum_{i = l,s,r,f} m_{i} k_{i}}_{\text{turnover}},
-\end{equation}
-
-where $y$ is the ratio of carbon fixed in mass per carbon assimilated,  and  $A_{\textrm{area}}$ is the assimilation rate of CO$_{2}$ per leaf area.
-
-Here, and in the following equations, $m_i$ denotes the \textbf{live mass on the plant}, $r_i$ the mass-specific \textbf{respiration rate}, and $k_i$ the \textbf{turnover rate} of different plant tissues; the subscripts $i = l,s,r,t,f$ referring to leaves, sapwood and bark, roots, total of these vegetative tissues, and to the reproductive tissues (fruits, flowers etc.) (note that the live biomass $b = m_t +m_f$).
-Similarly $a_i$ denotes \textbf{areas}, of leaves ($i = l$) and of cross-sections of total stem and sapwood ($i = st,ss$) respectively.
-
-The \textbf{growth rate in mass}, being the increment in vegetative live mass ($m_t$), is then:
-
-\begin{equation}\label{eq:eq1}
-\underbrace{{\frac{dm_t}{dt}}}_{\text{growth rate in mass}} = \underbrace{\frac{dm_t}{db}}_{\text{allocation to vegetative growth}}  \times \underbrace{\frac{db}{dt}}_{\text{net live biomass production}},
-\end{equation}
-
-where allocation to growth is the fraction of net live biomass increase that goes to vegetative growth rather than to reproductive tissue production.
-
-The \textbf{growth rate in height} can then be expressed as:
-
-\begin{equation}\label{eq:eq2}
-\underbrace{\frac{dH}{dt}}_{\text{growth rate in height}} = \underbrace{\frac{dH}{da_{l}}}_{\text{architecture layout}} \times \underbrace{{\frac{da_{l}}{dm_{t}}}}_{\text{leaf deployment per mass}} \times {\frac{dm_t}{db}} \times {\frac{db}{dt}}.
-\end{equation}
-
-Similarly \textbf{growth rate in basal area} can be expressed as:
-
-\begin{equation}\label{eq:eq3}
-\underbrace{{\frac{da_{st}}{dt}}}_{\text{basal area growth rate}} = \underbrace{\frac{da_{ss}}{da_{l}}}_{\text{sapwood area per leaf area}} \times {\frac{da_{l}}{dm_{t}}} \times  {\frac{dm_t}{db}} \times {\frac{db}{dt}} +  \underbrace{ \frac{da_{st}}{dt}}_{\text{sapwood turnover}}.
-\end{equation}
-
-The \textbf{growth rate in diameter} is then given by the geometric relationship between diameter and area applied to stem:
-\begin{equation}\label{eq:eq4}
-\underbrace{\frac{dD}{dt}}_{\text{growth rate in diameter}} = \sqrt[]{\frac{\Pi}{a_{st}}} \times {\frac{da_{st}}{dt}}.
-\end{equation}
-
-For the case of seedlings, eqs.
-\ref{eq:eq0}-\ref{eq:eq1} can be simplified considerably.
-Turnover of all tissues and allocation to reproduction have not yet begun.
-It is also common to assume all respiration rates are proportional to leaf area.
-Biomass growth rate in seedling then becomes a linear function of leaf area:
-
-\begin{equation}\label{eq:eq1_seedlings}
-{\frac{dm_t}{dt}}  \approx  a_{l} \, y \, (A_{\textrm{area}} - r_{l}).
-\end{equation}
-
-The \textbf{relative growth rate in mass} $(\textrm{RGR}_{\textrm{mass}})$ in seedlings can be obtained by dividing both sides of this simplified eq \ref{eq:eq1_seedlings} by the total mass of living tissues $m_{t}$.
-The outcome is equivalent to the classical partitioning of RGR \citep{Lambers:1992bj, Cornelissen:1998ta}:
-\begin{equation}\label{eq:eq1_seedlings_RGR}
-\textrm{RGR}_{\textrm{mass}}  \approx \textrm{NAR} \times  \textrm{SLA} \times  \textrm{LMF},
-\end{equation}
- where net assimilation rate NAR = $y \, (A_{\textrm{area}} - r)$, SLA = $a_{l}/ m_{l}$ and leaf mass fraction LMF = $m_{l}/ m_{t}$.
-
-The predicted effects of different traits on growth can then be understood by considering the influence of trait variation on elements of equations  \ref{eq:eq0}-\ref{eq:eq1_seedlings_RGR} (see Table \ref{tab:trade-offs}) and how these may interact with plant size.
-
-\textbf{Specific leaf area (SLA):} For seedlings (eq.
-\ref{eq:eq1_seedlings_RGR}), cheaper leaf construction (high SLA) should translate directly into faster relative growth rate in mass.
-For larger plants (eq.
-\ref{eq:eq1}-\ref{eq:eq4}), SLA is expected to affect growth rate positively through more cost-efficient deployment of leaf area (via $da_l/dm_t$; the same effect as in seedlings), but also negatively via increased leaf turnover (eqn 1; Table \ref{tab:trade-offs}).
-The effect of SLA on $da_l/dm_t$ decreases as plant size increases and increasing amounts of the plant are wood.
-Consequently the effect of turnover costs in slowing growth comes to dominate at larger sizes.
-
-\textbf{Wood density (WD):} Cheaper stem construction (low WD or stem density) increases the marginal rate of leaf deployment per total mass increment ($da_l/dm_t$), and consequently increases growth rate in leaf area, height and diameter (eqs.
-\ref{eq:eq2}-\ref{eq:eq4}; Table \ref{tab:trade-offs}).
-Disadvantages associated with cheap stem construction take the form of higher mortality and so are not reflected in growth equations.
-Under this scenario, wood density is negatively correlated to growth rate across all plant stages.
-Because the relative expenditure on stem compared to leaf is increases as plants grow larger, the relationship between WD and growth may also strengthen in larger plants.
-
-\textbf{Maximum height (Hmax):} Hmax affects growth via the fraction of energy allocated to vegetative growth versus to seed production ($dm_t/db$ in eq.
-\ref{eq:eq1}; Table \ref{tab:trade-offs}).
-For seedlings and seedlings this fraction is 1 for all species and so no effect is expected.
-But once some species begin to produce seed, then species closer to their Hmax value are expected to be allocating more to seed production and less to vegetative growth.
-Hence when comparing across plants at a given size, species with smaller Hmax are expected to show slower vegetative growth rates.
-
-\textbf{Seed mass:} The $\textrm{RGR}_{\textrm{mass}}$ slows as plants grow larger, and large-seeded species begin larger as seedlings.
-For larger plants, seed mass is not expected to have any distinct influence on growth rates  (Table \ref{tab:trade-offs}).
-
-\textbf{Potential photosynthesis rate (Aarea):} The effects of benefits (higher assimilation) and costs (higher respiration) of increased Area occur within the same element of eq.
-\ref{eq:eq0}, and assimilation must outweigh respiration for there to be growth, so the net effect will be positive (Table \ref{tab:trade-offs}).
-
-Note that the predicted relationship between growth and either SLA or seed mass in seedlings differs if absolute growth rate in mass is used instead of RGR$_\textrm{mass}$ (i.e.
-becomes negative for SLA, positive for seed mass).
-In our study, all data recorded for these trait-stage combinations have been measured on a RGR base for mass (see Fig S9).
+\clearpage
 
 \clearpage
+\section{Supporting figures}\label{app:supp_info_figures}
 
-\section{Supporting files}\label{app:supp_info_files}
+\begin{figure}[h!]
+\centering
+\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA1.pdf}
+\caption{Relationships between a) age and diameter (m), b) age and height (m), and c) diameter and height among plants in the Biomass and Allometry Database.
+Lines indicate the cut-offs between stage categories used in this study: blue lines indicate limit between seedlings and saplings, red lines indicate limits between saplings and adults.}
+\label{fig:figA1}
+\end{figure}
 
-The code and data for producing all figures and results in this paper is available at github.com/AnaisGibert/Growth\_trait\_metaanalysis.
-Upon publication, a copy of the complete data set is also available from the Dryad Digital Repository.
+\begin{figure}[h!]
+\centering
+\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA2.pdf}
+\caption{Geographical distribution of site locations from studies performed in the field used in the meta-analysis.
+Results shown here are from the entire dataset (for details see ``Material and Methods'').}
+\label{fig:figA2}
+\end{figure}
 
-\section{Supporting tables}\label{app:supp_info_tables}
+\begin{figure}[h!]
+\centering
+\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA3.pdf}
+\caption{Range of correlations (r) between
+growth and traits reported in the literature. Plots show the coefficients of correlation (r)
+between plant growth and a) Specific leaf area (SLA, n =
+111), b) Wood density (WD, n = 64), c) Asymptotic
+maximum height (Hmax, n = 23), d) Seed mass (Seedmass, n = 36 and
+e) Rate of CO2 assimilation (Aarea, n = 24) reported from 103
+articles.
+The x axis represents the article ID sorted by the average reported coefficient value r.
+Each bubble represents an r value, the diameter of the bubble is proportional to its weight in the meta-analysis (i.e.
+number of species).
+The colours correspond to the stage for which the r values have been recorded: red points correspond to adult stage, orange points to saplings, and blue points to seedlings.
+Results shown here are from the entire dataset (for details see ``Material and Methods'').
+}
+\label{fig:figA3}
+\end{figure}
+
+\begin{figure}[h!]
+\centering
+\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA4.pdf}
+\caption{Mean coefficient correlation r (+SD) between growth and traits, measured by stage (a-e
+) and by stage and growth type (f-j).
+a and f) Specific leaf area (SLA), b and g) Wood density (WD), c and h) Asymptotic maximum height (Hmax), d and i) Seed mass (Seedmass) and e and j) Rate of CO2 assimilation (Aarea).
+On figures f to j, relative (RGR) and absolute (AGR) growth rates are set apart.
+The mean coefficients are weighted by sample size and established from 103 articles.
+Results shown here are from the ``ideal'' subset of data (for details see ``Material and Methods''), ``n'' indicates the number of correlations.}
+\label{fig:figA4}
+\end{figure}
+
+\begin{figure}[h!]
+\centering
+\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA5.pdf}
+\caption{Effect size ($\pm$95\% confidence intervals, CI) of plant stage on the correlations between growth rate and five functional traits across species, with a data set averaging multiple comparisons by trait and by study.
+In the case of multiple comparisons within a study, effect sizes were calculated using the mean correlation coefficient by trait and by study.
+a) Specific leaf area (SLA), b) Wood density (WD), c) Asymptotic maximum height (Hmax) , d) Seed mass and e) Assimilation rate of CO2 (Aarea).
+Effect size is a standardized measure of the magnitude of the relationship between a particular stage and the correlation coefficient z (Fisher's z-transformed).
+Effects are significant if CIs do not overlap with zero.
+LRT: likelihood Ratio Test compared the fit between null model and stage model, both models are fitted by Maximum Likelihood.
+Black point: ideal data , grey points: all the data (for details see ``Material and Methods'').
+``n'' indicates the number of independent comparisons for each effect.}
+\label{fig:figA5}
+\end{figure}
+
+\begin{figure}[h!]
+\centering
+\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA6a.pdf}
+\end{figure}
+
+\begin{figure}[h!]
+\centering
+\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA6b.pdf}
+\end{figure}
+
+\begin{figure}[h!]
+\centering
+\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA6c.pdf}
+\caption{Effects size on the correlation between growth and traits of plant stage (mod1), growth measurement (mod2), vegetation type (mod3), and experiment type (mod4).
+a) Specific leaf area (SLA), b) Wood density (WD),c) Assimilation rate of CO2 (Aarea), d) Seed mass, and e) Asymptotic maximum height (Hmax).
+The effect size (z + 95\%CI) is reported for each class, and models are fitted by restricted max likelihood (REML).
+Abbreviation: GR = growth rate and RGR = relative growth rate, measured in diameter (D), height (H), mass(M), cross section area (CSA) and volume (V), across GF: coefficient of correlation measured on tree in mixture with other growth form.
+AIC: Akaike information criterion corresponds to the quality of each model, and allow a comparison between models.
+Smallest is the AIC better is the model.
+Results shown here are from ``ideal'' subset of data (for details see ``Material and Methods'').
+``n'' indicates number of correlation r reported.}
+\label{fig:figA6}
+\end{figure}
+
+\begin{figure}[h!]
+\centering
+\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA7.pdf}
+\caption{Funnel plots with filled in data based on the trim and fill method, showing transformed correlation coefficient z between growth and a) Specific leaf area (SLA), b) Wood density (WD), c) Asymptotic maximum height (Hmax), d) Seed mass and e) Assimilation rate of CO2 (Aarea).
+Note that in these plots the y axis is 1/number of species included in the correlation, not the replication for the correlation.
+The open points correspond to the estimated missing studies.
+The number of missing values is 7 for SLA,1 for WD, 0 for Hmax, 6 for seed mass and 0 for Aarea.
+Results shown here are from the ``ideal'' subset of data (for details see ``Material and Methods'').}
+\label{fig:figA7}
+\end{figure}
+
+\begin{figure}[h!]
+\centering
+\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA8.pdf}
+\caption{Number of correlation extracted by traits, stage, and growth type (absolute vs relative, and measurement).
+a) Specific leaf area (SLA), b) Wood density (WD), c) Asymptotic maximum height (Hmax), d) Seed mass and e) Assimilation rate of CO2 (Aarea).
+Absolute growth rate (AGR) is on the left and relative growth rate (RGR) on the right of each plot.
+Results shown here are from the entire dataset (for details see ``Material and Methods'').
+}
+\label{fig:figA8}
+\end{figure}
+
+\begin{figure}[h!]
+\centering
+\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA9.pdf}
+\caption{Temporal changes in coefficient of correlation between growth and traits.
+a) Specific leaf area (SLA), b) Wood density (WD), c) Asymptotic maximum height (Hmax), d) Seed mass, and e) Assimilation rate of CO2 (Aarea).
+The colours correspond to the stage for which the r values have been recorded: red points corresponds to adult stage, orange points to saplings, and grey points to seedlings.
+Results shown here are from the ``ideal'' subset of data (for details see ``Material and Methods'').}
+\label{fig:figA9}
+\end{figure}
+
+\clearpage
+\section{Supporting Analyses}\label{app:supp_info_analyses}
+
+\subsection{Literature coverage by trait}\label{app:literature-snapshot}
+
+TODO: XXXX
+
+We first developed a snapshot of the literature, to assess the potential to recover useful data from the wide corpus of literature available.
+This snapshot was obtained via Web of Science database (Thomson Reuters), between March and June 2014, using a range of Boolean search terms in English.
+Search terms were as follows: (``trait'' AND (``growth rate'' OR ``relative growth rate'')) AND (``tree*'' OR ``woody*''), where ``trait'' was allowed to be any of the trait names listed in Table \ref{tab:lit_search}.
+This snapshot indicated that 82\% of the reported correlations linking growth to any of our five core traits would be recovered by searching only on SLA and WD, allowing us to narrow our search considerably.
 
@@
 
-\clearpage
-\section{Supporting figures}\label{app:supp_info_figures}
-
-\begin{figure}[h!]
-\centering
-\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA1.pdf}
-\caption{Allometric relationships between a) age and diameter (m), b) age and height (m), and c) diameter and height in trees according to the BAAD database.
-Blue and red lines are the cut-offs between stage categories used in the literature.
-Blue lines corresponds to limits between seedlings and saplings, red lines to limits between saplings and adults.}
-\label{fig:figA1}
-\end{figure}
-
-\begin{figure}[h!]
-\centering
-\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA2.pdf}
-\caption{Geographical distribution of site locations from studies performed in the field used in the meta-analysis. Results shown here are from the ``complete'' dataset (see methods for details).}
-\label{fig:figA2}
-\end{figure}
-
-\begin{figure}[h!]
-\centering
-\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA3.pdf}
-\caption{Range of correlations (r) between
-growth and traits reported in the literature. Plots show the coefficients of correlation (r)
-between plant growth and a) Specific leaf area (SLA, n =
-111), b) Wood density (WD, n = 64), c) Asymptotic
-maximum height (Hmax, n = 23), d) Seed mass (Seedmass, n = 36 and
-e) Rate of CO2 assimilation (Aarea, n = 24) reported from 112
-articles.
-The x axis represents the article ID sorted by the average reported coefficient value r.
-Each bubble represents an r value, the diameter of the bubble is proportional to its weight in the meta-analysis (i.e.
-number of species).
-The colours correspond to the stage for which the r values have been recorded: red points correspond to adult stage, orange points to saplings, and blue points to seedlings.
-Results shown here are from the ``complete'' dataset (see methods for details).
-}
-\label{fig:figA3}
-\end{figure}
-
-\begin{figure}[h!]
-\centering
-\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA4.pdf}
-\caption{Mean coefficient correlation r (+SD) between growth and traits, measured by stage (a-e
-) and by stage and growth type (f-j).
-a and f) Specific leaf area (SLA), b and g) Wood density (WD), c and h) Asymptotic maximum height (Hmax), d and i) Seed mass (Seedmass) and e and j) Rate of CO2 assimilation (Aarea).
-On figures f to j, relative (RGR) and absolute (AGR) growth rates are set apart.
-The mean coefficients are weighted by sample size and established from 112 articles.
-Results shown here are from the ''ideal dataset'' (see methods for details), ''n'' indicates the number of correlations.}
-\label{fig:figA4}
-\end{figure}
-
-\begin{figure}[h!]
-\centering
-\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA5.pdf}
-\caption{Effect size (+ 95\%CI) of plant stage on the correlations between growth rate and five functional traits across species, with a data set averaging multiple comparisons by trait and by study.
-In the case of multiple comparisons within a study, effect sizes were calculated using the mean correlation coefficient by trait and by study.
-a) Specific leaf area (SLA), b) Wood density (WD), c) Asymptotic maximum height (Hmax) , d) Seed mass and e) Assimilation rate of CO2 (Aarea).
-Effect size is a standardized measure of the magnitude of the relationship between a particular stage and the correlation coefficient z (Fisher's z-transformed).
-Effects are significant if confidence intervals (+CI95\%) do not overlap with zero.
-LRT: likelihood Ratio Test compared the fit between null model and stage model, both models are fitted by Maximum Likelihood.
-Black point: ideal data , grey points: all the data (see methods for details).
-''n'' indicates the number of independent comparisons for each effect.}
-\label{fig:figA5}
-\end{figure}
-
-\begin{figure}[h!]
-\centering
-\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA6a.pdf}
-\end{figure}
-
-\begin{figure}[h!]
-\centering
-\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA6b.pdf}
-\end{figure}
-
-\begin{figure}[h!]
-\centering
-\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA6c.pdf}
-\caption{Effects size on the correlation between growth and traits of plant stage (mod1), growth measurement (mod2), vegetation type (mod3),  and experiment type (mod4).
-a) Specific leaf area (SLA), b) Wood density (WD),c) Assimilation rate of CO2 (Aarea), d) Seed mass, and e) Asymptotic maximum height (Hmax).
-The effect size (z + 95\%CI) is reported for each class, and models are fitted by restricted max likelihood (REML).
-Abbreviation: GR = growth rate and RGR = relative growth rate, measured in diameter (D), height (H), mass(M), cross section area (CSA) and volume (V), across GF: coefficient of correlation measured on tree in mixture with other growth form.
-AIC: Akaike information criterion corresponds to the quality of each model, and allow a comparison between models.
-Smallest is the AIC better is the model.
-Results shown here are from ``ideal'' dataset (see methods for details).
-''n'' indicates number of correlation r reported.}
-\label{fig:figA6}
-\end{figure}
-
-\begin{figure}[h!]
-\centering
-\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA7.pdf}
-\caption{Funnel plots with filled in data based on the trim and fill method, showing transformed correlation coefficient z between growth and a) Specific leaf area (SLA), b) Wood density (WD), c) Asymptotic maximum height (Hmax), d) Seed mass and e) Assimilation rate of CO2 (Aarea).
-Note that in these plots the y axis is 1/number of species included in the correlation, not the replication for the correlation.
-The open points correspond to the estimated missing studies.
-The number of missing values is 7 for SLA,1 for WD, 0 for Hmax, 6 for seed mass and 0 for Aarea.
-Results shown here are from the ''ideal'' dataset (see methods for details).}
-\label{fig:figA7}
-\end{figure}
-
-\begin{figure}[h!]
-\centering
-\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA8.pdf}
-\caption{Number of correlation extracted by traits, stage and growth type (absolute vs relative, and measurement).
-a) Specific leaf area (SLA), b) Wood density (WD), c) Asymptotic maximum height (Hmax), d) Seed mass and e) Assimilation rate of CO2 (Aarea).
-Absolute growth rate (AGR) is on the left and relative growth rate (RGR) on the right of each plot.
-Results shown here are from the ``complete'' dataset (see methods for details).
-}
-\label{fig:figA8}
-\end{figure}
-
-\begin{figure}[h!]
-\centering
-\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA9.pdf}
-\caption{Temporal changes in coefficient of correlation between growth and traits.
-a) Specific leaf area (SLA), b) Wood density (WD), c) Asymptotic maximum height (Hmax), d) Seed mass, and e) Assimilation rate of CO2 (Aarea).
-The colours correspond to the stage for which the r values have been recorded: red points corresponds to adult stage, orange points to saplings, and grey points to seedlings.
-Results shown here are from the ``ideal'' dataset (see methods for details).}
-\label{fig:figA9}
-\end{figure}
-
-\clearpage
-\section{Supporting Analyses}\label{app:supp_info_analyses}
 \subsection{Quantifying and exploring the cause of heterogeneity in effect sizes}
 
-\textbf{Goal:} In our meta-analysis, reported studies differed in design as well as in vegetation type, biome or species studied.
+\noindent\textbf{Goal:} In our meta-analysis, reported studies differed in design as well as in vegetation type, biome or species studied.
 Such diversity is commonly referred to as methodological heterogeneity, and may or may not be responsible for observed discrepancies in the results of the studies.
@@
 
-\textbf{Methods:} A common way of addressing the extent of heterogeneity is the statistic $I^{2}$ (\citealt{Santos:2012gt}, originally defined by \citealt{Higgins:2002iq}).
+\noindent\textbf{Methods:} A common way of addressing the extent of heterogeneity is the statistic $I^{2}$ (\citealt{Santos:2012gt}, originally defined by \citealt{Higgins:2002iq}).
 $I^{2}$ estimates the consistency of the results obtained from published studies used in our meta-analysis; it describes the percentage of variability in point estimates that is due to heterogeneity rather than sampling error.
@@
 By contrast, as $I^{2}$ moves away from zero we know that some of the variance is real and can potentially be explained by subgroup analysis or meta-regression.
-There is no universal rule to cover definition for ‘low, ‘moderate’ or ‘high heterogeneity.
+There is no universal rule to cover definition for ``low'', ``moderate'' or ``high'' heterogeneity.
 \citealt{Higgins:2003hz} suggested some benchmarks for $I^{2}$ based on the survey of meta-analyses of clinical trials.
-They suggested that values on the order of 25\%, 50\% and 75\% might be considered as ''low'', ''moderate'' and ''high'', respectively.
+They suggested that values on the order of 25\%, 50\% and 75\% might be considered as ``low'', ``moderate'' and ``high'', respectively.
 These suggestions are tentative; the interpretation of heterogeneity in a systematic review will depend critically on the size and direction of treatment effects, as well as on considerations of methodological diversity in the studies (see \citealt{Borenstein:2009um}).
 Here, we estimated $I^{2}$ as following equation from \citealt{Higgins:2002iq}, then we calculated how part of the heterogeneity may be due to the influence of moderators (stage and publication year) and finally we asked if the residual heterogeneity was statistically significant.
-In R, we used the package metafor (code available on github).
+In R, we used the package metafor  \citep{Viechtbauer-2010}.
 
-\textbf{Results:} We observed high levels of heterogeneity for all traits (SLA :$I^{2}$ 85.4\% CI: 80.9 to 92.1, WD :$I^{2}$ 61.8\% CI: 42.8 to 84.1, Hmax: $I^{2}$ 81.2\% CI: 69.8 to 93.4, seed mass: $I^{2}$ 91.2\%, 85.9 to 96.1, Aarea: $I^{2}$ 68.3\% CI: 33.7 to 90.1) which suggests that the correlations coefficient r between growth and traits are not uniform across the range of studies investigated.
-This result suggested that a large part of the variance is not explained by sample error.
+\noindent\textbf{Results:} We observed high levels of heterogeneity for all traits (SLA :$I^{2}$ 85.4\% CI: 80.9 to 92.1, WD :$I^{2}$ 61.8\% CI: 42.8 to 84.1, Hmax: $I^{2}$ 81.2\% CI: 69.8 to 93.4, seed mass: $I^{2}$ 91.2\%, 85.9 to 96.1, Aarea: $I^{2}$ 68.3\% CI: 33.7 to 90.1) which suggests that the correlations coefficient r between growth and traits are not uniform across the range of studies investigated.
+This result suggested that a large part of the variance is not explained by sampling error.
 
-For SLA and seed mass, 50.1\% and 20\% respectively of the total amount of heterogeneity were accounted for by including the stage as a moderator.
-For the other traits, the stage explained little or no part of the heterogeneity observed across studies ($<$5\%).
+For SLA and seed mass, 50.1\% and 20\% respectively of the total amount of heterogeneity were accounted for by including the plant stage as a moderator.
+For the other traits, the plant stage explained little or no part of the heterogeneity observed across studies ($<$5\%).
 These results were consistent with our expectations about a shift in the relationship between growth and traits across plant size for SLA and seed mass, and the absence of an effect for WD and Aarea (see Theoretical expectation section).
@@
 The test for residual heterogeneity was significant for all traits, possibly indicating that other moderators not considered in the model were influencing the correlation between growth and traits.
-This is not surprising because although the trait and growth measurements are standardized \citep{Cornelissen:2003gw}, studies differed in their design as well as in vegetation type, biome and species studied.
+This is not surprising because although the trait and growth measurements are standardized \citep{Cornelissen:2003gw}, studies differed in their design as well as in vegetation type, biome, and species studied.
 Indeed, a goal in the trait literature is to establish general patterns of correlation between growth and traits and to validate them across a large variety of conditions.
@@
 \subsection{Testing for publication bias}
-\textbf{Goal:} Studies with significant results are more likely to be published.
+\noindent\textbf{Goal:} Studies with significant results are more likely to be published.
 As a consequence, the studies in a meta-analysis may overestimate the true effect size because they are based on a biased sample of the target population of studies.
@@
 
-\textbf{Method:} Initially, we checked the dataset for publication bias with a visual assessment of funnel plots.
+\noindent\textbf{Methods:} Initially, we checked the dataset for publication bias with a visual assessment of funnel plots.
 A publication bias toward significant results creates an asymmetric funnel with small studies with non-significant effects missing from the mouth of the funnel on the side opposite to the true effect.
@@
 In addition, funnel plots are not effective when the number of studies is small ($<30$) such as for Aarea and seed mass.
-Next, we used the ''trim and fill'' method to estimate the number of studies missing from our meta-analysis. This method adjusts for funnel plot asymmetry \citep{Duval:2000dg}.
-Finally, we estimated the number of studies needed to overturn a result, using Rosenberg’s fail-safe number \citep{Rosenberg:2005hk}.
+Next, we used the ``trim and fill'' method to estimate the number of studies missing from our meta-analysis. This method adjusts for funnel-plot asymmetry \citep{Duval:2000dg}.
+Finally, we estimated the number of studies needed to overturn a result, using Rosenberg's fail-safe number \citep{Rosenberg:2005hk}.
 The fail-safe N is not based on funnel plot asymmetry.
-The Rosenberg method calculates the number of studies averaging null results that would have to be added to the given set of observed outcomes to reduce the significance level (p-value) of the weighted average effect \citep{Rosenberg:2005hk}.
+Rather, the Rosenberg method calculates the number of studies on-average null results that would need to be added to the given set of observed outcomes to reduce the significance level (p-value) of the weighted average effect \citep{Rosenberg:2005hk}.
 A significant meta-analytic result is robust if the fail-safe N is greater than 5k+10, where k is the number of studies already in the meta-analysis \citep{Rosenthal:1979do}.
-In R, we used the package `metafor` (code available on github).
+In R, we used the package ``metafor''  \citep{Viechtbauer-2010}.
 
-\textbf{Result:} As expected the correlation coefficient varied less as sample size increased (funnel plots in Fig.
+\noindent\textbf{Results:} As expected the correlation coefficient varied less as sample size increased (funnel plots in Fig.
 \ref{fig:figA9}).
@@
 \ref{fig:figA9}).
-The ‘trim and fill’ method detected some missing values in our data.
+The ``trim and fill'' method detected some missing values in our data.
 The estimated number of missing value ranges from 0 to 7 depending on the trait considered (Fig.
@@
 The overall estimates measured with the fill in data changed from $0.5 \pm 0.07$  to $0.4 \pm 0.07$ for SLA and from $-0.48 \pm 0.11$ to $-0.32 \pm 0.12$ for the seed mass, suggesting a lower correlation coefficient for SLA, and seed mass.
-Even although the estimated correlations were closer to zero with the missing studies filled in, the results still indicate that the effect is statistically significant.
-The Rosenberg’s Fail-safe (N) were 7086, 1823, 990, 574, 291 for SLA, WD, Hmax, Seedmass and Aarea, suggesting that a large number of studies with a mean correlation coefficient of 0 need to be added to the analysis before the cumulative correlation would become non-significant.
+Although the correlations estimated with the missing studies filled in were closer to zero than without, the trait effect is still statistically significant.
+The Rosenberg's Fail-safe (N) were 7086, 1823, 990, 574, 291 for SLA, WD, Hmax, Seedmass, and Aarea, suggesting that a large number of studies with a mean correlation coefficient of 0 need to be added to the analysis before the cumulative correlation would become non-significant.
 N was greater than 5k+10 for all traits.
@@
 \subsection{Exploring temporal changes in effect size}
-\textbf{Goal:} Our meta-analysis combines data from studies published between 1983 and 2014.
+\noindent\textbf{Goal:} Our meta-analysis combines data from studies published between 1983 and 2014.
 It has been shown that the magnitude of the effect size may change over time due to a publication bias (i.e.
@@
 
-\textbf{Method:} In the trait literature the year of publication may be confounded with a methodological change.
-Indeed, in the early 90’s studies mainly focused on seedlings, whereas today a broader range of plant sizes/stages are studied (Fig.
+\noindent\textbf{Methods:} In the trait literature the year of publication may be confounded with a methodological change.
+Indeed, in the early 90's studies mainly focused on seedlings, whereas today a broader range of plant sizes/stages are studied (Fig.
 \ref{fig:figA9}).
@@
 
-\textbf{Result:} There was a change in the effect size with publication year for SLA ($p<0.0001$, estimates: $-0.04 \pm 0.009$ ), seed mass ($p = 0.011$, estimates: $0.041 \pm 0.016$ ) and Aarea ($p = 0.0102$, estimates: $-0.0453 \pm 0.0176$ ).
-The Fig.
+\noindent\textbf{Results:} There was a change in the effect size with publication year for SLA ($p<0.0001$, estimates: $-0.04 \pm 0.009$ ), seed mass ($p = 0.011$, estimates: $0.041 \pm 0.016$ ) and Aarea ($p = 0.0102$, estimates: $-0.0453 \pm 0.0176$ ).
+Fig.
 \ref{fig:figA9} shows that for these three traits the publication years may be confounded with plant stage; correlation coefficients have been reported since 1993, but studies started to report data on adult stage only ten years later (around 2000-2007).
@@
 For Aarea, publication year explained a part of the variation across stage but not within stage, and the magnitude of the effect size decreased with publication year.
-This pattern is classic in meta-analyses; \citealt{Koricheva:2013hy} showed that a majority of studies reported a decrease rather than an increase in the magnitude of effect size with publication year.
+This pattern is classic feature in meta-analyses: \citealt{Koricheva:2013hy} showed that a majority of studies reported a decrease rather than an increase in the magnitude of effect size with publication year.
 Yet, here this effect did not lead to a reduction in statistical significance of the main effect size or to a change of sign.

### 2016-01-14 MS.tex
fix fig labl and map some editing on ms

@@
 
-We aimed to identify studies reporting the correlations, measured across species, between functional traits and one of several measures of growth  rate (Table \ref{tab:trade-offs}) .
+We aimed to identify studies reporting the correlations, measured across species, between functional traits and one of several measures of growth rate (Table \ref{tab:trade-offs}).
 We supplemented records from our own bibliographic libraries with results from searching online databases and suggestions from other researchers.
@@
 title, keywords, and abstracts, \citealt{Beckmann:2012hn}).
-This limitation does not apply to Google Scholar, where all text that is electronically available on the internet is indexed.
+This limitation does not apply to Google Scholar.
 
@@
 Both Web of Science and Google Scholar databases were searched for records linking SLA and WD to growth rate.
-On Web of Science, we searched using  search terms: (``trait'' AND (``growth rate'' OR ``relative growth rate'')) AND (``tree*'' OR ``woody*''), where ``trait'' was either (``leaf mass per area'' OR ``specific leaf area'' OR ``leaf construction cost'') or (``wood density'' OR``WD'' OR ``wood specific gravity'' OR ``stem density'' OR ``stem specific density'' OR ``SSD'' ).
-On Google scholar we searched using terms: ((``SLA'' OR ``LMA'' OR ``specific leaf area'' OR ``leaf mass area'' OR ``wood density'' OR ``WD'' OR ``wood specific gravity'' OR ``stem density'' OR ``stem specific density'') AND (``growth rate'' OR ``relative growth rate'')) AND (``tree*'' OR ``woody*'').
+On Web of Science, we searched using  search terms: (``trait'' AND (``growth rate'' OR ``relative growth rate'')) AND (``tree*'' OR ``woody*''), where ``trait'' was either (``leaf mass per area'' OR ``specific leaf area'' OR ``leaf construction cost'') or (``wood density'' OR``WD'' OR ``wood specific gravity'' OR ``stem density'' OR ``stem specific density'' OR ``SSD'' ).On Google scholar we searched using terms: ((``SLA'' OR ``LMA'' OR ``specific leaf area'' OR ``leaf mass area'' OR ``wood density'' OR ``WD'' OR ``wood specific gravity'' OR ``stem density'' OR ``stem specific density'') AND (``growth rate'' OR ``relative growth rate'')) AND (``tree*'' OR ``woody*'').
 This keyword search in Google Scholar returned approximately 18900 papers.
@@
 
+% TO DO : maybe explain in one sentence that mixing RGR and AGR is not a heresy here because we are not expecting different pattern with RGR vs AGR except for seedmass in seedling
+
 Effect sizes and overall results using the entire dataset were similar to those reported above using the ``ideal'' subset (Fig.
@@
 The solid vertical lines indicate the thresholds used to classify plants in one of three stages.
-Studies mark with a ``*'' were those where stage was changed, compared to the original publication.
-Studies marked with ``+'' are those where plants came from different growth form.}
-% TODO: Anais -- what does different growth form mean?
+Studies mark with a ``*'' were those where stage was changed or assigned, compared to the original publication.
+}
 \label{fig:fig2}
@@
 
+\clearpage
 \subsection{Quantifying and exploring the cause of heterogeneity in effect sizes}

### 2016-01-14 R/figures.R

@@ -67,8 +67,8 @@ figure_2 <- function(CompleteData_inter) {
     j <- data$stageRGR != data$stage
     points(data$size.max[j] + 0.05, y[j], col = "black", pch = "*", cex=1.5)
 
-    t <- (data$growth.form == "across growth form")
-    points(data$growthf[t], y[t], pch = "+", cex= 1, col="black")
+#     t <- (data$growth.form == "across growth form")
+#     points(data$growthf[t], y[t], pch = "+", cex= 1, col="black")
 
     axis(1, at = 0:3, labels = cuts, las = 1)
     axis(2, at = y, labels = data$ref, las = 1, cex.axis = 0.6)
@@ -82,8 +82,8 @@ figure_2 <- function(CompleteData_inter) {
   legend(2.3, 42, c("seedling", "juvenile", "sapling", "adult", "mix"), lwd = 1,  title = "Original stage:",
     col = c("#13519E", "#73005C", "#F57C34", "#E6224C", "grey"), pch = NA, bty = "n", cex = 0.75,
    x.intersp = 0.3, y.intersp = 1, seg.len = 0.5,  title.adj = 0)
-  legend(2.3, 32, c("reassigned", "multiple",  " growth forms"), lwd = NA, col = "black",
-    pch = c("+", "*", NA), title = "Flag:", bty = "n", cex = 0.75,
+  legend(2.3, 32, c("reassigned"), lwd = NA, col = "black",
+    pch = c( "*"), title = "Flag:", bty = "n", cex = 0.75,
     x.intersp = 0.3, y.intersp = 1, seg.len = 0.5,  title.adj = 0)
 
   text(0.5, 45, "Seedlings", xpd=NA, col = "black")
@@ -334,7 +334,7 @@ figure_3.4 <- function(GCi, GCrgr , GCagr) {
   
   p2 <- coeff.plot.gr3(data = CoefModel.WD, data1=CoefModel.WD2, data.RGR = CoefModel.WD.s, data.AGR = CoefModel.WD.opt, 
                        LRT=LRT.wd, PVAL=PVAL.wd, round.value = 2, significativite = "ns", title = "b) WD",
-                       limit.x.min = -1, limit.x.max = 1, limit.x.n = 0.85,
+                       limit.x.min = -1, limit.x.max = 1, limit.x.n = 0.84,
[…]

### 2016-01-14 R/plots.R

@@ -61,7 +61,8 @@ coeff.plot <- function(data, data.complete, data.ideal, LRT, PVAL, title = "",
 
   data.complete["x.coord"] <- limit.x.n
   data.ideal["x.coord"] <- limit.x.n
-
+  data["x.coord"] <- limit.x.n
+  
   plot1 <- function(title, ggobj, xlab = "Effect size", ylab = "Stage") {
 
     p <- ggobj + labs(title = title) + xlab(xlab) + ylab(ylab) + geom_vline(yintercept = 0,
@@ -71,18 +72,19 @@ coeff.plot <- function(data, data.complete, data.ideal, LRT, PVAL, title = "",
     p
   }
 
-  dodge <- position_dodge(width = 0.4)
+  dodge <- position_dodge(width = 0.6)
 
   plot1(title, ggplot(data, aes(stage, Inte, ymin = Inte - 1.96 * SE, ymax = Inte +
     1.96 * SE, color = factor(stress)))) + geom_point(aes(x = stage, y = Inte),
     position = dodge) + geom_errorbar(aes(x = stage, y = Inte), size = 0.4,
     width = 0.2, position = dodge) + scale_y_continuous("Effect size",
     limits = c(limit.x.min, limit.x.max)) + geom_text(aes(stage, x.coord, label = paste("n=",
-    N), color = factor(stress), group = "all"), size = 2, data = data.complete,
-    parse = F, position = "identity", vjust = +vjust.value, hjust = 0) + geom_text(aes(stage,
-    x.coord, label = paste("n=", N), color = factor(stress), group = "ideal"),
-    size = 2, data = data.ideal, parse = F, position = "identity", vjust = -vjust.value,
-    hjust = 0) + 
+    N), color = factor(stress)), size = 2, data = data,
+    parse = F, position = dodge, nudge_y =0  , hjust = 0) + 
+#     geom_text(aes(stage,
+#     x.coord, label = paste("n=", N), color = factor(stress), group = "ideal"),
+#     size = 2, data = data.ideal, parse = F, position = "identity", vjust = -vjust.value,
+#     hjust = 0) + 
     scale_color_manual(name = "", values=c(color1, color2), breaks = c("ideal", "complete"), labels = c(ideal = "ideal", complete = "complete")) +
        annotate("text", x = limit.y.text.l1, y = limit.x.text, label = paste("LRT:", round(LRT,
[…]

### 2016-01-15 MS.tex
Figure3,4, A3, A4, A5 : fix label, alignment etc Figure A4: delete pannel 2 (was redundant with Fig3) remake.yml: shut off figureA4.1 MS: modification caption of Fig 1, 2, 3 and A4.

@@
 %   -- only one y label for multi-panel plots
-%   -- sample sizes skewiff relative to plots if Figure 4
 %   -- major revision of code -- > lots of repetition, hard to follow
@@
 \includegraphics[width=15cm,height=20cm,keepaspectratio]{output/Fig2.pdf}
-\caption{The range of plant sizes and stage recoded in original publications (coloured lines), compared to standardised thresholds used in the analysis (black lines).
+\caption{The range of plant sizes and stage recoded in original publications (horizontal coloured lines), compared to standardised thresholds used in the analysis (vertical black lines).
 Horizontal line segments indicate the size range (max., min.) for the plants used to measure growth.
-The solid vertical lines indicate the thresholds used to classify plants in one of three stages.
-Studies mark with a ``*'' were those where stage was changed or assigned, compared to the original publication.
+The solid vertical lines indicate the thresholds used to classify plants in one of three stages in our meta-anlyses.
+Studies mark with a ''*'' were those where stage was changed or assigned, compared to the original publication.
 }
@@
 \includegraphics[width=15cm,height=20cm,keepaspectratio]{output/Fig1.pdf}
-\caption{Number of recorded correlations between trait and growth rate in our dataset, by size and trait.
+\caption{Number of recorded correlations between trait and growth rate in our dataset, by stage and trait.
 Traits are: Aarea (or Amass) = rate of CO$_{2}$ assimilation per unit leaf area (or leaf mass) = maximum photosynthetic rate, Hmax = asymptotic or maximum height,  Ks = stem hydraulic conductance, LA = leaf area, LMR = leaf mass ratio, NARarea = net mass assimilation rate per unit of leaf area, Nmass (or Narea) = nitrogen content per unit of leaf mass (or leaf area), Pmass = phosphorus content per unit of leaf mass, SA/LA = sapwood area per leaf area, SLA = specific leaf area, Thickness = leaf thickness, Vessel size = stem conduit size, Vessel density = stem conduit density, WD = wood density.
@@
 \caption{The relationship between relative growth rates (RGR) and traits changes with plant stage and trait.
-Plots show the effect size (+ 95\% confidence intervals; CI) for the average correlation across species, by plant stage.
+Plots show the effect size (+ 95\% confidence intervals; CI) for the average correlation across >10 species, by plant stage.
 Effect size is a standardized measure of the deviation of correlation coefficient from zero (Fisher's z-transformed).
@@
 \includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA4.pdf}
-\caption{Mean coefficient correlation r (+SD) between growth and traits, measured by stage (a-e
-) and by stage and growth type (f-j).
-a and f) Specific leaf area (SLA), b and g) Wood density (WD), c and h) Asymptotic maximum height (Hmax), d and i) Seed mass (Seedmass) and e and j) Rate of CO2 assimilation (Aarea).
-On figures f to j, relative (RGR) and absolute (AGR) growth rates are set apart.
+\caption{Mean coefficient correlation r (+SD) between growth and traits measured by stage.
+a) Specific leaf area (SLA), b) Wood density (WD), c) Asymptotic maximum height (Hmax), d) Seed mass (Seedmass) and e) Rate of CO2 assimilation (Aarea).
 The mean coefficients are weighted by sample size and established from 103 articles.
-Results shown here are from the ``ideal'' subset of data (for details see ``Material and Methods''), ``n'' indicates the number of correlations.}
+Results shown here are from the ''ideal'' subset of data (for details see ``Material and Methods''), ``n'' indicates the number of correlations.}
 \label{fig:figA4}

### 2016-01-15 R/figures.R

@@ -96,7 +96,6 @@ figure_2 <- function(CompleteData_inter) {
 
 }
 
-
 figure_3.3 <- function(GC, GI) {
   CoefModel.SLA <- fun_model(GI[["SLA"]], GC[["SLA"]])
   CoefModel.SLA["trait"] <- "SLA"
@@ -174,92 +173,92 @@ figure_3.3 <- function(GC, GI) {
     theme(legend.title = element_blank(), legend.justification = c(0, 0), legend.position = c(1.2,
       0.5), legend.key = element_blank())
 
-  p1 <- p1 + theme(plot.margin = unit(c(0, 0, 0, 0), "mm"), axis.title.x = element_blank())
+  p1 <- p1 + theme(plot.margin = unit(c(0, 0, 0, 0), "mm"), axis.title.x = element_blank(),axis.title.y = element_text(colour = "white"))
   p2 <- p2 + theme(axis.text.y = element_blank(), axis.title.y = element_blank(),
     plot.margin = unit(c(0, 0, 0, 0), "mm"), axis.title.x = element_blank())
   p3 <- p3 + theme(plot.margin = unit(c(0, 0, 1.5, 0), "mm"), axis.title.x = element_blank())
   p4 <- p4 + theme(axis.text.y = element_blank(), axis.title.y = element_blank(),
-    plot.margin = unit(c(0, 0, 0, 0), "mm"))
-  p5 <- p5 + theme(plot.margin = unit(c(0, 0, 0, 0), "mm"))
+    plot.margin = unit(c(0, 0, -1, 0), "mm"))
+  p5 <- p5 + theme(plot.margin = unit(c(0, 0, 0, 0), "mm"), axis.title.y = element_text(colour = "white"))
 
   grid.arrange(p1, p2, p3, p4, p5, ncol = 2, nrow = 3, widths = c(1.2, 1))
 }
 
 
-figure_3.2 <- function(GCrgr , GCagr) {
-  CoefModel.SLA <- fun_model1(GCrgr[["SLA"]],GCagr[["SLA"]])
-  CoefModel.SLA["trait"] <- "SLA"
-  CoefModel.SLA.s <- subset(CoefModel.SLA, growth == "RGR")
-  CoefModel.SLA.opt <- subset(CoefModel.SLA, growth == "AGR")
-
-  
-  CoefModel.WD <- fun_model1( GCrgr[["WD"]], GCagr[["WD"]])
-  CoefModel.WD["trait"] <- "WD"
[…]

### 2016-01-15 R/plots.R

@@ -85,7 +85,7 @@ coeff.plot <- function(data, data.complete, data.ideal, LRT, PVAL, title = "",
 #     x.coord, label = paste("n=", N), color = factor(stress), group = "ideal"),
 #     size = 2, data = data.ideal, parse = F, position = "identity", vjust = -vjust.value,
 #     hjust = 0) + 
-    scale_color_manual(name = "", values=c(color1, color2), breaks = c("ideal", "complete"), labels = c(ideal = "ideal", complete = "complete")) +
+    scale_color_manual(name = "", values=c(color1, color2), breaks = c("ideal", "complete"), labels = c(ideal = "ideal", complete = "entire")) +
        annotate("text", x = limit.y.text.l1, y = limit.x.text, label = paste("LRT:", round(LRT,
       2)), size = 2) + annotate("text", x = limit.y.text.l2, y = limit.x.text,
     label = paste("p.value =", round(PVAL, round.value), significativite),

### 2016-01-15 analysis.R

@@ -59,11 +59,8 @@ dev.off()
 pdf("output/FigA3.pdf", height = 6L, width = 6L)
 figure_A3(GCi)
 dev.off()
-pdf("output/FigA4.pdf", height = 7L, width = 5L)
+pdf("output/FigA4.pdf", height = 6L, width = 5L)
 figure_A4(GIi, GIrgr, GIagr)
-dev.off()
-pdf("output/FigA4.1.pdf", height = 6L, width = 5L)
-figure_3.3(GCi, GIi)
 dev.off()
 pdf("output/FigA6a.pdf")
 figure_A6(GCi, "SLA", "WD", c("a", "b"))

### 2016-01-15 MS.tex
Change fig number in Table2 Fixed error in caption Fig3

@@
 \caption{The relationship between relative growth rates (RGR) and traits changes with plant stage and trait.
-Plots show the effect size (+ 95\% confidence intervals; CI) for the average correlation across >10 species, by plant stage.
+Plots show the effect size (+ 95\% confidence intervals; CI) for the average correlation across $>$10 species, by plant stage.
 Effect size is a standardized measure of the deviation of correlation coefficient from zero (Fisher's z-transformed).
@@
 Results are shown in Fig.
-\ref{fig:fig3}.\\
+\ref{fig:fig3} \& \ref{fig:fig4}.\\
  5.& Quantifying heterogeneity in effect sizes &	yes &	We estimate the extent of heterogeneity for each trait using the $I^{2}$ statistic. See Appendix \ref{app:supp_info_analyses} for details.\\
@@
 We do not test the multiple variables in a hierarchical fashion, because of the limited size of our dataset.
-See in Figs \ref{fig:figA4}f-j \& \ref{fig:figA6}.\\
+See in Figs \ref{fig:figA6}.\\
   8.& Testing for publication bias &	yes	& We used several methods (i.e.
@@
 See Appendix \ref{app:supp_info_analyses} for details.\\
-  9.& Sensitivity analysis &	yes &See ``Material and Methods'' for details, results in Figs \ref{fig:fig3} \& \ref{fig:figA5}.\\
+  9.& Sensitivity analysis &	yes &See ``Material and Methods'' for details, results in Figs \ref{fig:fig4} \& \ref{fig:figA5}.\\
   10.& Exploring temporal changes in effect size &	yes	& See Appendix \ref{app:supp_info_analyses} for details.\\

### 2016-01-18 MS.tex
Add new task to do on ms.tex
some changed in Material and methods and results

@@
 % Fix plots
-%   -- labels causing plot size to change, e.g. Fig 3d
-%   -- only one y label for multi-panel plots
 %   -- major revision of code -- > lots of repetition, hard to follow
 %   -- Figure 2: add * against traits used in meta-analysis
+%   -- check the appendix: in particular test of heterogeneity etc. need to re-run the analysis
+%   -- check the results and adequation with text of ms
 
@@
 
-Compiled data included studies differing in the growth measurement used (RGR or AGR), the number of species, the experimental conditions (stressed vs unstressed), and the concordance between stage used to measure trait and growth rate.
-To assess whether such factors influenced our results, we investigated whether results changed between the entire dataset and a more conservative subset.
-The entire dataset includes all noted correlations.
-A second ``ideal'' subset, included only studies recording RGR across \underline{\textgreater} 10 species, under unstressed conditions, and where growth rates and traits were measured on plants from the same stage (expect for Hmax and seed mass, where a particular stage is by definition required to measure the trait).
+The entire dataset included studies differing in the growth measurement used (RGR or AGR), the number of species, the experimental conditions (stressed vs unstressed), and the concordance between stage used to measure trait and growth rate.
+The main results reported here were obtained with an ``ideal'' subset of data.
+This ``ideal'' subset, included only studies recording RGR across \underline{\textgreater} 10 species, under unstressed conditions, and where growth rates and traits were measured on plants from the same stage (expect for Hmax and seed mass, where a particular stage is by definition required to measure the trait).
+These were then compare against results obtained with the entire dataset, including all noted correlations.
 
@@
 
-\subsection*{Trait coverage}
-In total, 103 articles containing 551 correlations linking growth rate to any of the 19 traits  across a range of plant stages were identified (Fig.
-\ref{fig:fig1}).
-Considering only our top five traits of interest, the number reduced to 93 articles and 267 correlations.
-For measurements under ideal conditions, we identified only 55 studies with 137 correlations.
-The main results reported here were obtained with this ``ideal'' subset of data.
-These were then compare against results obtained with the entire dataset.
-
 % x <- remake::make("CleanData")
@@
 
-Overall, results were consistent with predictions, although with limitations arising for some traits due to very unequal numbers of observations between growth stages.
+Overall, results were consistent with predictions, although with limitations arising for some traits due to very unequal (and limited) numbers of observations between growth stages.
+We identified only 55 studies with 137 correlations reporting data measured under ``ideal'' conditions: unstressed growth, growth measured as RGR, traits and growth recorded in same stage, and correlation coefficient calculated across \underline{\textgreater} 10 species.
 
@@
 
-For WD, Hmax, and seed mass, correlations with RGR were also consistent with expectations, although our ability to test all hypotheses was at times limited due to low sample size.
-Indeed, CIs of $r$ often spanned zero especially where there were small numbers of studies for particular growth stages, precluding strong conclusions.
+For WD, Hmax, and seed mass, correlations with RGR were also consistent with expectations but our ability to test all hypotheses was at times limited due to low sample size.
+Indeed, while meta-analysis are possible even with few observations, strong conclusions are generally precluded by very large CIs of the effect size (i.e CI often spanned zero).
 For WD, results were consistent with the prediction for negative correlations with RGR across all plant sizes (Fig.
 \ref{fig:fig3}b).
-Accordingly, model fits were not improved when stage was incorporated.
-Note that the CIs were not crossing zero for sapling and seedling stage despite the small sample sizes (n= 4 and 1 respectively), meaning a strong correlation and /or a good consistency in the coefficient reported for each stage across studies.
+Accordingly, model fits were marginaly improved when stage was incorporated (p.value = 0.049).
+Note that the CIs were not crossing zero for seedling and sapling stage despite the small sample sizes (n= 1 and 4 respectively), meaning a strong correlation and/or a good consistency in the coefficient reported for each stage across studies.
 
-For Hmax, the expectation was for a correlation with growth to be absent for small plants but present at larger sizes, the mechanism being increased relative allocation to reproduction as Hmax is approached.
-Indeed Hmax was positively correlated with growth at adult stage ($\bar{r}= 0.38 \pm 0.05$).
-At sapling stages, the correlation between Hmax and growth was not significantly different from that observed at adult stage (model fit not improved when stage was incorporated, see log likelihood ratio tests in Fig.
-\ref{fig:fig3}c, and CIs overlapping), but also was consistent with no correlation (Fig \ref{fig:fig3}c, CIs overlapping zero), due to much smaller numbers of replicate studies.
-We could not distinguish between these alternatives.
+For Hmax, the expectation was for a correlation with growth to be present for large plants but absent for smaller sizes, the mechanism being increased relative allocation to reproduction as Hmax is approached.
+Here, Hmax was positively correlated with growth at adult stage ($\bar{r}= 0.38 \pm 0.05$), not correlated at sapling stages (Fig \ref{fig:fig3}c, CIs overlapping zero) and no data were recorded for seedling stages.
+While these results were consistent with expectation, we could not distinguish with another alternative: Hmax was correlated to growth for adult stage, but the correlation between Hmax and growth at sapling stage was not significantly different from that observed at adult stage (model fit not improved when stage was incorporated, see log likelihood ratio tests in Fig.
+\ref{fig:fig3}c, and CIs overlapping between sapling and adult stages).
+Due to small numbers of replicate studies for sapling stage and no replicates for seedling stage, we could not conclude on the absence of correlation between Hmax and growth at small plant size.
 
@@
 
-\subsection*{Sensitivity of results to analysis decisions}
+\subsection*{Main effects under relaxed criteria}
 
-The above results were generated using data measured under ``ideal'' conditions: unstressed growth, growth measured as RGR, traits and growth recorded in same stage, \underline{\textgreater} 10 species.
-We now report results from the entire dataset, to determine if additional data would alter our conclusions.
+We now report results from the entire dataset, to determine if additional data would alter or reinforce our conclusions, drawn sometimes with limited replicates.
 This entire dataset included correlations measured with both AGR and RGR (Fig.
-\ref{fig:fig4}), across at least two species, and did not control for the source of trait or growth (i.e.
-both could be measured on different stages) or environmental conditions.
-These relaxed criteria considerably increased the number of replicates, from $n = 137$ to $n = 267$ correlations.
-These additional replicates were unequally distributed across trait-stage combinations.
+\ref{fig:fig4}), across at least two species (but measured using several individuals), and did not control for the source of trait or growth (i.e.
+trait could be measured on a different stage) or environmental conditions.
+The relaxed criteria considerably increased the number of replicates, from $n = 137$ to $n = 267$ correlations across 93 articles.
+However, the additional replicates were unequally distributed across trait-stage combinations.
 Some trait-stage combinations already with a lot of data got even more support (e.g.
 from 25 to 59 correlation coefficients reported for SLA at seedling stage), while others still had few replicates.
-On the 13 traits-stage combinations studied in total, six had \textless five correlation coefficients: (i.e.
+On the 13 traits-stage combinations studied in total, six had $\le$ five correlation coefficients: (i.e.
 WD-seedling, Hmax-sapling, Hmax-seedling, Seed mass-sapling, Aarea-adult and Aarea-sapling.
@@
 
-% TO DO : maybe explain in one sentence that mixing RGR and AGR is not a heresy here because we are not expecting different pattern with RGR vs AGR except for seedmass in seedling
-
-Effect sizes and overall results using the entire dataset were similar to those reported above using the ``ideal'' subset (Fig.
-\ref{fig:fig4}).
+Results from the entire dataset reinforced our conclusions for both SLA and WD, set appart alternative explanations for seed mass, and allowed to compare correlations with growth along plant stages for Aarea.
+For SLA and WD, the number of replicates doubled by using the entire dataset, and effect sizes and overall results were similar to those reported above using the ''ideal'' subset (Fig.
+\ref{fig:fig4})).
+As expected for seed mass, the correlation with growth at adult stage was significantly different from that observed at seedling stage (see CIs in Fig.
+\ref{fig:fig4}c, and model fit improved when stage was incorporated).
 For Aarea, the additional replicates in the entire dataset allowed us to compare the effect size across plant stage.
@@
 \ref{fig:fig4}d), indicated little effect of stress (here mainly low light) on the correlation with RGR at seedling stage; as the correlation was still positive when 8 correlations measured under low light conditions were added.
+For Hmax, there were still too few replicates to conclude undoubtely on the correlation to be absent for smaller sizes.
 
-For some trait-stage combinations, it was possible to compare results between RGR and AGR.
-For both WD and Hmax, effects size measured with RGR or AGR were no different at adult stage; CIs were overlapping despite equal sample size (Fig \ref{fig:fig4}b-c).
+We had no hypotheses about a change in the correlation between trait and growth as AGR was used instead of RGR, except for seed mass.
 For seed mass, effects size differed significantly between RGR and AGR at seedling stage; as expected the correlation with RGR was positive and shifted to non significant with AGR (Fig \ref{fig:fig4}d; CI not overlapping).
+For other traits, effect size were generally consistent between RGR and AGR when both measurement were available.
+Some differences occured but they were not easily attributed to any single cause.
+For instance for WD, the correlation at juvenile stage shifted from negative with RGR to non significant with AGR (i.e CI included zero, Fig.
+\ref{fig:fig4}b).
+The correlation coefficients recorded for AGR came from Augspurger & Kelly (1984) and unlike others they used wood density values from adult plants together with growth from juveniles.
 
@@
 
-In total, we found only 103 studies published between between 1983 and 2014 that met our requirements.
+In total, 103 articles published between 1983 and 2014, and containing 551 correlations linking growth rate to any of the 19 traits across a range of plant stages were identified (Fig.
+\ref{fig:fig1}).
 Climate zones spanned from temperate regions to tropics (map in Fig.

### 2016-01-18 MS.tex
Update theoretical mdoel and table 1

@@
 \usepackage[]{natbib}
+\definecolor{grey}{rgb}{0.5, 0.5, 0.5}
+
 %\raggedright
@@
 \newcommand{\smurl}[1]{\url{#1}}
+\newcommand{\ud}{\ensuremath{\rm{d}}}
 \newcommand{\tabitem}{~~\llap{\textbullet}~~}
@@
 %   -- check the results and adequation with text of ms
+% - seach on XXX, footnote
+% - check refs to appendices in main text
 
 \bibliographystyle{mee}
-\newcommand{\bibstar}{* }
 
@@
 \citealt{grime1979plant, Grime:1997wm}).
-Meanwhile partitioning of seedling RGR into different components showed that specific leaf area (SLA) was typically the strongest source of variation between species \citep{Poorter:1989tx, Rees:2010gk}.
+Meanwhile partitioning of seedling RGR into different components showed that the trait specific leaf area (SLA) was typically the strongest source of variation between species \citep{Poorter:1989tx, Rees:2010gk}.
 From the 1990s a new style of ``trait ecology'' arose whereby measurable traits, including SLA, were used directly as strategy axes \citep{Westoby:2002ft}.
@@
 Yet, recently a number of empirical studies indicate the correlation between traits and growth is not as consistent as that.
-Consider SLA as an illustration.
+Consider SLA as an example.
 By definition, species with high SLA can deploy more leaf area for a given dry mass investment in leaves \citep{Poorter:1999wd, Reich:1992wm}.
-In addition, SLA is correlated with specific photosynthetic capacity per unit of leaf mass and high nitrogen or phosphorus concentrations in the leaf \citep{Wright:2004jb}.
-For seedling RGR under favourable conditions, SLA has repeatedly been found to be a strong predictor regardless of vegetation type or growth form \citep{Lambers:1992bj,Reich:1992wm,Grime:1997wm,Poorter:1999wd,Wright:1999ds}.
+In seedlings growing under favourable conditions, SLA has repeatedly been found to be a strong predictor of relative growth rate, regardless of vegetation type or growth form \citep{Lambers:1992bj,Reich:1992wm,Grime:1997wm,Poorter:1999wd,Wright:1999ds}.
 Yet for adult plants, the correlation has mostly been much weaker or absent \citep{coomes_comparison_1998,Poorter:2008iu,Aiba:2009ft,Easdale:2009gv,Wright:2010tp}.
@@
 
-Meanwhile the possibility has been raised that trait-growth correlations may change systematically with size \citep{Falster:2011ii, Ruger:2012jv, Iida:2014ep, Iida:2014hq}.
+Meanwhile the possibility has been raised that trait-growth correlations may change systematically with size \citep{King-1999,Falster:2011ii, Ruger:2012jv, Iida:2014ep, Iida:2014hq}.
 Size has long been known to play a central role in organismal design and function \citep{Vogel:1988ux, Vogel:2003wb}, including that of trees \citep{Farnsworth:1995im, Givnish:1995ta}.
@@
 To address these questions we used a meta-analytic approach, compiling data from diverse studies reporting correlation coefficients between traits and growth.
-While most studies investigating the link between traits and growth have not primarily been concerned with effects of plant size, they have generally reported trait-growth correlations for identifiable stage classes (i.e.
+While most studies investigating the link between traits and growth have not primarily been concerned with the effects of plant size, they have generally reported trait-growth correlations for identifiable stage classes (i.e.
 seedling, sapling, and adult).
-We therefore used plant stage as a surrogate for the effects of plant size.
+We therefore used plant stage as a surrogate for plant size.
 We focused on tree and woody species since the mechanistic model used to assess our predictions is most applicable to these growth forms.
@@
 While, we anticipated a reasonably-sizeable literature on trait and growth to be available, we were uncertain about the representation of all trait-stages combinations.
-An additional goal of our study was therefore to identify any gaps in knowledge needed to improve our understanding of the link between trait and growth.
+An additional goal of our study was therefore to identify gaps in knowledge, needed to improve our understanding of the link between trait and growth.
 
@@
 
-Recent theoretical work \citep{Falster:2011ii} allows us to formulate hypotheses about relationships between traits and growth, based on a mathematical decomposition of plant growth rate.
-Specific predictions arise from considering the influence of traits on elements of these equations and how these effects may vary with size (see Appendix \ref{sec:growth} for mathematical explanations).
+Recent theoretical work \citep{Falster:2011ii} allows us to formulate hypotheses about the expected relationship between traits and growth, based on a mathematical decomposition of plant growth rate.
+Specific predictions arise from considering the influence of traits on elements of these equations and how these effects may vary with size.
 This model extends earlier efforts to model growth as a function of traits \citep{Lambers:1992bj,Cornelissen:1996hf,Wright:2000kw,Enquist:2007ek}.
-However, whereas earlier models focused solely on mass-based RGR and did not predict a change in effect of traits with size, the revised equations do allow for these effects, while also making predictions for both AGR and RGR in any of height, diameter or mass.
+However, whereas earlier models focused solely on mass-based RGR and did not predict a change in effect of traits with size, the revised equations do allow for these effects, while also making predictions for both absolute and relative growth in any of mass (eq.
+\ref{eq:eq1}), height (eq.
+\ref{eq:eq2}), or diameter (eq.
+\ref{eq:eq4}).
 
-\section{Derivation of hypotheses from growth equations}\label{sec:growth}
+Below we first outline equations for the new growth model, adapted \citet{Falster:2011ii}.
+We then use this model to generate qualitative predictions on how the effect of traits on growth rate changes with plant size.
+These hypotheses are summarised in Table \ref{tab:trade-offs}.
 
-We adapted growth equations from \cite{Falster:2011ii} to generate hypotheses on both absolute and relative growth rate in mass (eqn \ref{eq:eq1}), height (eqn \ref{eq:eq2}) and diameter (eqn \ref{eq:eq4}).
+\subsection*{A generic model for growth rate in plant mass, height and stem diameter}\label{sec:growth}
 
-The rate at which \textbf{live biomass} $b$ is produced by a plant is given by:
+The rate at which \textbf{live biomass} $B$ is produced by a plant is given by:
+\begin{equation}\label{eq:eq0}
+\underbrace{\frac{\ud B}{\ud t}}_{\text{net live biomass production}} = \underbrace{\alpha_{\rm y}}_{\text{yield}}  \big(\underbrace{A_{\rm l} p}_{\text{photosynthesis}} - \underbrace{\sum_{i = {\rm l,s,r}} M_{i} r_{i}}_{\text{respiration}}\big) - \underbrace{ \sum_{i = \rm{l,s,r}} M_{i} k_{i}}_{\text{turnover}},
+\end{equation}
+where $\alpha_{\rm y}$ is the ratio of carbon fixed in mass per carbon assimilated, and $p$ is the assimilation rate of CO$_{2}$ per leaf area.
+Here, and in the following equations, $M_i$ denotes the \textbf{live mass on the plant}, $r_i$ the mass-specific \textbf{respiration rate}, and $k_i$ the \textbf{turnover rate} of different plant tissues; the subscripts $i = \rm{l,s,r,t,f}$ referring to leaves, sapwood and bark, roots, total of these vegetative tissues, and to the reproductive tissues (fruits, flowers etc.)  Similarly $A_i$ denotes \textbf{areas}, of leaves ($i = l$) and of cross-sections of total stem and sapwood ($i =\rm{st,ss}$) respectively.
+Note that the live biomass $B = M_{\rm t} + M_{\rm f}$.
+Applying the product rule of differential calculus, the \textbf{growth rate in plant mass}, ($M_{\rm t}$), can be decomposed as
+\begin{equation}\label{eq:eq1}
+\underbrace{{\frac{\ud M_{\rm t}}{\ud t}}}_{\text{growth rate in mass}} = \underbrace{\frac{\ud M_{\rm t}}{\ud B}}_{\text{allocation to vegetative growth}}  \times \underbrace{\frac{\ud B}{\ud t}}_{\text{net live biomass production}},
+\end{equation}
+where $\frac{\ud M_{\rm t}}{\ud B}$ is the fraction of net live biomass increase that goes to vegetative growth rather than to production of reproductive tissues.
 
-\begin{equation}\label{eq:eq0}
-\underbrace{\frac{db}{dt}}_{\text{net live biomass production}} = \underbrace{y}_{\text{yield}}  \big(\underbrace{a_{l} A_{\textrm{area}}}_{\text{photosynthesis}} - \underbrace{\sum_{i = l,s,r,f} m_{i} r_{i}}_{\text{respiration}}\big) - \underbrace{ \sum_{i = l,s,r,f} m_{i} k_{i}}_{\text{turnover}},
+The \textbf{growth rate in height} can likewise be decomposed as the product of several meaningful terms:
+\begin{equation}\label{eq:eq2}
+\underbrace{\frac{\ud H}{\ud t}}_{\text{growth rate in height}} = \underbrace{\frac{\ud H}{\ud A_{\rm l}}}_{\text{architecture layout}} \times \underbrace{{\frac{\ud A_{\rm l}}{\ud M_{\rm t}}}}_{\text{leaf deployment per mass}} \times {\frac{\ud M_{\rm t}}{\ud B}} \times {\frac{\ud B}{\ud t}}.
 \end{equation}
-where $y$ is the ratio of carbon fixed in mass per carbon assimilated, and $A_{\textrm{area}}$ is the assimilation rate of CO$_{2}$ per leaf area.
-
-Here, and in the following equations, $m_i$ denotes the \textbf{live mass on the plant}, $r_i$ the mass-specific \textbf{respiration rate}, and $k_i$ the \textbf{turnover rate} of different plant tissues; the subscripts $i = l,s,r,t,f$ referring to leaves, sapwood and bark, roots, total of these vegetative tissues, and to the reproductive tissues (fruits, flowers etc.) (note that the live biomass $b = m_t +m_f$).
-Similarly $a_i$ denotes \textbf{areas}, of leaves ($i = l$) and of cross-sections of total stem and sapwood ($i = st,ss$) respectively.
-
-The \textbf{growth rate in mass}, being the increment in vegetative live mass ($m_t$), is then:
-
-\begin{equation}\label{eq:eq1}
-\underbrace{{\frac{dm_t}{dt}}}_{\text{growth rate in mass}} = \underbrace{\frac{dm_t}{db}}_{\text{allocation to vegetative growth}}  \times \underbrace{\frac{db}{dt}}_{\text{net live biomass production}},
-\end{equation}
-where allocation to growth is the fraction of net live biomass increase that goes to vegetative growth rather than to reproductive tissue production.
-
-The \textbf{growth rate in height} can then be expressed as:
-\begin{equation}\label{eq:eq2}
-\underbrace{\frac{dH}{dt}}_{\text{growth rate in height}} = \underbrace{\frac{dH}{da_{l}}}_{\text{architecture layout}} \times \underbrace{{\frac{da_{l}}{dm_{t}}}}_{\text{leaf deployment per mass}} \times {\frac{dm_t}{db}} \times {\frac{db}{dt}}.
-\end{equation}
-Similarly \textbf{growth rate in basal area} can be expressed as:
-\begin{equation}\label{eq:eq3}
-\underbrace{{\frac{da_{st}}{dt}}}_{\text{basal area growth rate}} = \underbrace{\frac{da_{ss}}{da_{l}}}_{\text{sapwood area per leaf area}} \times {\frac{da_{l}}{dm_{t}}} \times  {\frac{dm_t}{db}} \times {\frac{db}{dt}} +  \underbrace{ \frac{da_{st}}{dt}}_{\text{sapwood turnover}}.
+The first term on the right of eq \ref{eq:eq2},
+$\ud H / \ud A_{\rm l}$, is the growth in plant height
+per unit growth in total leaf area -- accounting for the architectural
+strategy of the plant. We assume this function is unrelated to the traits considered in the current paper. The second term, $\ud A_{\rm l} / \ud M_{\rm t}$,
+accounts for the marginal cost of deploying an additional unit of leaf
+area, including construction of the leaf itself and various support
+structures. As such, $\ud A_{\rm l} / \ud M_{\rm t}$
+can itself be expressed as a sum of construction costs per unit leaf
+area,
+\begin{equation}\label{eq:daldmt}
+\frac{\ud A_{\rm l}}{\ud M_{\rm t}}
+= \left(\frac{\ud M_{\rm l}}{\ud A_{\rm l}}
+ +  \frac{\ud M_{\rm s}}{\ud A_{\rm l}} + \frac{\ud M_{\rm r}}{\ud A_{\rm l}}\right)^{-1}.
 \end{equation}
 
-The \textbf{growth rate in diameter} is then given by the geometric relationship between diameter and area applied to stem:
+Similarly \textbf{growth rate in basal area} can be expressed as the sum of growth in sapwood and heartwood, with the former term again decomposed as a product:
+\begin{equation}\label{eq:eq3}
+\begin{array}{ccccc}
+\underbrace{{\frac{\ud A_{\rm st}}{\ud t}}}_{\text{basal area growth rate}} &=& \frac{\ud A_{\rm ss}}{\ud t} &+& \frac{\ud A_{\rm sh}}{\ud t} \\
+&=& \underbrace{\frac{\ud A_{\rm ss}}{\ud A_{\rm l}}  \times {\frac{\ud A_{\rm l}}{\ud M_{\rm t}}} \times  {\frac{\ud M_{\rm t}}{\ud B}} \times {\frac{\ud B}{\ud t}}}_{\text{increase in total sapwood}} &+&  \underbrace{k_{\rm ss} \times \frac{\ud A_{\rm ss}}{\ud t}}_{\text{sapwood turnover}},\\
+\end{array}
+\end{equation}
+where $\frac{\ud A_{\rm ss}}{\ud A_{\rm l}} $ is the  sapwood area per leaf area.
+The \textbf{growth rate in diameter} is then obtained via the geometric relationship between stem diameter and stem area,
 \begin{equation}\label{eq:eq4}
-\underbrace{\frac{dD}{dt}}_{\text{growth rate in diameter}} = \sqrt[]{\frac{\Pi}{a_{st}}} \times {\frac{da_{st}}{dt}}.
+\underbrace{\frac{\ud D}{\ud t}}_{\text{growth rate in diameter}} = \sqrt[]{\frac{\Pi}{A_{\rm st}}} \times {\frac{\ud A_{\rm st}}{\ud t}}.
 \end{equation}
 
-For the case of seedlings, eqs.
-\ref{eq:eq0}-\ref{eq:eq1} can be simplified considerably.
-Turnover of all tissues and allocation to reproduction have not yet begun.
-It is also common to assume all respiration rates are proportional to leaf area.
-Biomass growth rate in seedling then becomes a linear function of leaf area:
-\begin{equation}\label{eq:eq1_seedlings}
-{\frac{dm_t}{dt}}  \approx  a_{l} \, y \, (A_{\textrm{area}} - r_{l}).
-\end{equation}
+\subsection*{Predicted effects of traits on growth}
 
-The \textbf{relative growth rate in mass} $(\textrm{RGR}_{\textrm{mass}})$ in seedlings can be obtained by dividing both sides of this simplified eq \ref{eq:eq1_seedlings} by the total mass of living tissues $m_{t}$.
-The outcome is equivalent to the classical partitioning of RGR \citep{Lambers:1992bj, Cornelissen:1998ta}:
-\begin{equation}\label{eq:eq1_seedlings_RGR}
-\textrm{RGR}_{\textrm{mass}}  \approx \textrm{NAR} \times  \textrm{SLA} \times  \textrm{LMF},
-\end{equation}
-where net assimilation rate NAR = $y \, (A_{\textrm{area}} - r)$, SLA = $a_{l}/ m_{l}$ and leaf mass fraction LMF = $m_{l}/ m_{t}$.
+The above equations are general, i.e.
+they do not depend on detailed assumptions about plant construction.
+To make qualitative predictions with respect to traits such as specific leaf area and wood density, however, we require one additional assumption: that the mass of sapwood tissue ($M_{\rm ss}$) increases disproportionately with respect to the plants leaf area ($A_{\rm l}$).
+This assumption, which is included in nearly every model of plant growth that has been developed, has the effect of changing the relative importance of different components within equations for $\frac{\ud B}{\ud t}$ and $\frac{\ud A_{\rm l}}{\ud M_{\rm t}}$ above as a plant increases in size.
+Specifically, in eq.
+\ref{eq:eq0}, the costs of stem respiration and turnover increase faster than leaf photosynthesis, respiration or turnover, as the plant grows.
+Similarly, in eq.
+\ref{eq:daldmt}, the costs of constructing sapwood support to support a given unit of leaf area, $\frac{\ud M_{\rm s}}{\ud A_{\rm l}}$, increases faster the cost of producing a unit of leaf area, $\frac{\ud M_{\rm l}}{\ud A_{\rm l}}$ which is simply the inverse of specific leaf area.
+Whether plant growth rate increases with a specific trait, therefore depends on how the trait effects the different elements of \ref{eq:eq0}-\ref{eq:eq4} and how those effects change with size (Table \ref{tab:trade-offs}).
 
-The predicted effects of different traits on growth can then be understood by considering the influence of trait variation on elements of equations  \ref{eq:eq0}-\ref{eq:eq1_seedlings_RGR} (see Table \ref{tab:trade-offs}) and how these may interact with plant size.
+Based on the above model and this single assumption about growth, we outline five hypotheses, which arise by considering the influence of trait variation on elements of equations  \ref{eq:eq0}-\ref{eq:eq4} (see Table \ref{tab:trade-offs}) and how these may interact with plant size.
+These hypotheses reflect a direct mechanistic causation between traits and growth rate.
+It is possible that other correlations may arise indirectly.
+Nevertheless, for purposes of this paper we adopt working hypotheses arising only from direct mechanistic causation.
+With only XXX exception, the predicted effects of the trait are also similar when growth is expressed on relative of absolute terms, and as diameter, height or mass growth (Table \ref{tab:trade-offs} (TRUE XXXX?).
+\footnote{The correlation with RGR$_{\rm mass}$ is negative but becomes positive with AGR$_{\rm mass}$.
+For SLA, WD, Hmax, and Aarea, the direction of the predicted relationship is not affected by the growth measurement used.
+However RGR and AGR are fundamentally different for a lot of ecologists.
+So we adopted a two steps approach, first we were conservative by focusing exclusively on RGR, then we compared results with those of a more inclusive dataset with both RGR and AGR.}
 
-\textbf{H1: The relationship between SLA and growth rate is expected to shift from positive in seedlings to non-significant or negative in adult plants}
+\subsubsection*{H1: The relationship between SLA and growth rate is expected to shift from positive in seedlings to non-significant or negative in adult plants}
 
-Plants with high SLA can deploy more leaf area per unit of mass invested.
+Plants with high SLA can deploy a unit of leaf area more cheaply.
 However, high-SLA species also have shorter leaf lifespan, and must use more energy replacing leaves lost via turnover \citep{Wright:2004jb}.
-Whether plant growth rate increases with SLA depends on the how the relative magnitude of the benefit (cheap leaf construction) and cost (higher leaf turnover) of increased SLA also change with size (Table \ref{tab:trade-offs}).
-During early life, when leaf comprises a large part of the plant, decreasing SLA has an overwhelmingly positive effect on growth rate.
-As plants increase in size and leaf mass fraction decreases, the benefit of cheaper leaf construction diminishes; thus the cost of replacing leaf turnover becomes more important.
+These two effects occur within the terms  $\frac{\ud B}{\ud t}$ and $\frac{\ud A_{\rm l}}{\ud M_{\rm t}}$ in the above model.
+Whether plant growth rate increases with SLA depends on the how the relative magnitude of the benefit (cheap leaf construction, via $\frac{\ud A_{\rm l}}{\ud M_{\rm t}}$ ) and cost (higher leaf turnover, via $\frac{\ud B}{\ud t}$) of increased SLA also change with size (Table \ref{tab:trade-offs}).
+During early life, when leaf comprises a large part of the plant, decreasing SLA has an overwhelmingly positive effect on height and diameter growth rate, because the effect of reducing $\frac{\ud M_{\rm l}}{\ud A_{\rm l}}$ has a large effect compared to the other terms in eq.
+\ref{eq:daldmt}.
+As plants increase in size, however, the cost of building sapwood ($\frac{\ud M_{\rm s}}{\ud A_{\rm l}}$) increases disproportionately, decreasing the benefit of cheaper leaf construction in eq.
+\ref{eq:daldmt}.
+Consequently, the relative effect of leaf turnover comes to dominate at larger sizes, and as such, the effect of SLA on height and diameter growth shifts from positive to negative as plants increase in size.
 
-For seedlings (eq.
-\ref{eq:eq1_seedlings_RGR}), cheaper leaf construction (high SLA) should translate directly into faster relative growth rate in mass.
-For larger plants (eq.
-\ref{eq:eq1}-\ref{eq:eq4}), SLA is expected to affect growth rate positively through more cost-efficient deployment of leaf area (via $da_l/dm_t$; the same effect as in seedlings), but also negatively via increased leaf turnover (eqn 1; Table \ref{tab:trade-offs}).
-The effect of SLA on $da_l/dm_t$ decreases as plant size increases and increasing amounts of the plant are wood.
-Consequently the effect of turnover costs in slowing growth comes to dominate at larger sizes.
+Among seedlings, growth is often measured in units of plant mass, rather than stem or diameter.
+For mass growth in seedlings, cheaper leaf construction (high SLA)  translates directly into faster relative growth rate (See Appendix XXX eq.
+\ref{eq:eq1_seedlings_RGR}).
 
-\textbf{H2: The relationship between WD and growth rate is expected to be negative across all plant sizes}
+\subsection*{H2: The relationship between WD and growth rate is expected to be negative across all plant sizes}
 
 High WD increases the cost of building stem tissue and thus the cost of deploying additional leaf area (Table \ref{tab:trade-offs}), which should slow growth.
+This effects occur within the term $\frac{\ud A_{\rm l}}{\ud M_{\rm t}}$ in the above model.
 Although expensive wood decreases the risk of mortality, this benefit is not reflected in growth outcomes.
@@
 
-Cheaper stem construction (low WD or stem density) increases the marginal rate of leaf deployment per total mass increment ($da_l/dm_t$), and consequently increases growth rate in leaf area, height, and diameter (eqs.
+Cheaper stem construction (low WD or stem density) increases the marginal rate of leaf deployment per total mass increment ($\frac{\ud A_{\rm l}}{\ud M_{\rm t}}$), and consequently increases growth rate in leaf area, height, and diameter (eqs.
 \ref{eq:eq2}-\ref{eq:eq4}; Table \ref{tab:trade-offs}).
@@
 
-\textbf{H3: The relationship between Hmax and growth rate is expected to be absent in seedlings but to strengthen with increasing plant size}
+\subsection*{H3: The relationship between Hmax and growth rate is expected to be absent in seedlings but to strengthen with increasing plant size}
 
 As plants approach maximum height they increasingly divert energy away from growth and into reproduction (see \citealt{Thomas:1996do,Thomas-2011, Wenk:2015jz}).
-For seedlings, where all individuals are investing solely in growth, we expect no influence of Hmax on growth.
-As plants become larger, species with smaller Hmax are expected to be allocating more to reproduction and less to growth, because at any given size they are closer to their Hmax (Table \ref{tab:trade-offs}).
+This effect occurs in the term $\frac{\ud M_{\rm t}}{\ud B}$ in the above model.
+For seedlings, where all individuals are investing solely in growth, we expect no influence of Hmax on growth (i.e.
+$\frac{\ud M_{\rm t}}{\ud B} =1$).
+But once some species begin to produce seed, then species closer to their Hmax value are expected to be allocating more to seed production and less to vegetative growth.
+Hence when comparing across plants at a given size, species with smaller Hmax are expected to show slower vegetative growth rates (Table \ref{tab:trade-offs}).
 
-Hmax affects growth via the fraction of energy allocated to vegetative growth versus to seed production ($dm_t/db$ in eq.
-\ref{eq:eq1}; Table \ref{tab:trade-offs}).
-For seedlings and seedlings this fraction is 1 for all species and so no effect is expected.
-But once some species begin to produce seed, then species closer to their Hmax value are expected to be allocating more to seed production and less to vegetative growth.
-Hence when comparing across plants at a given size, species with smaller Hmax are expected to show slower vegetative growth rates.
-
-\textbf{H4: The relationship between seed mass and RGR is negative in seedlings, but weakens with increasing size}
+\subsection*{H4: The relationship between seed mass and RGR is negative in seedlings, but weakens with increasing size}
 
@@
 However, among larger plants we expect the effect of this initial size to be minimal, and thus the correlation between seed size and growth rate should disappear.
+The ${\rm RGR}_{{\rm mass}}$ slows as plants grow larger, and large-seeded species begin larger as seedlings.
+For larger plants, seed mass is not expected to have any distinct influence on growth rates  (Table \ref{tab:trade-offs}).
+However, the predicted relationship between growth and seed mass in seedlings reverses if AGR$_{\rm mass}$ is used instead of RGR$_{\rm mass}$.
 
-The $\textrm{RGR}_{\textrm{mass}}$ slows as plants grow larger, and large-seeded species begin larger as seedlings.
-For larger plants, seed mass is not expected to have any distinct influence on growth rates  (Table \ref{tab:trade-offs}).
-\textbf{H5: The relationship between Aarea and growth rate is expected to be positive across all plant sizes, at least under high-light conditions}
+\subsection*{H5: The relationship between Aarea and growth rate is expected to be positive across all plant sizes, at least under high-light conditions}
 
 We expect greater photosynthetic capacity to translate into faster growth rates by increasing the rate of biomass production (Table \ref{tab:trade-offs}), at least at high light where Aarea is measured.
-It is uncertain how much this might translate to faster growth in low light.
+This effects occurs within the term  $\frac{\ud B}{\ud t} $ in the above model.
+The effects of benefits (higher assimilation) and costs (higher respiration) of increased Area occur within the same element of eq.
+\ref{eq:eq0}, and because assimilation is typically higher than respiration in high light, the net effect will be positive (Table \ref{tab:trade-offs}).
+It is uncertain how much this effect might translate to faster growth in low light.
 It might greatly depend on the level of light available.
-
-The effects of benefits (higher assimilation) and costs (higher respiration) of increased Area occur within the same element of eq.
-\ref{eq:eq0}, and assimilation must outweigh respiration for there to be growth, so the net effect will be positive (Table \ref{tab:trade-offs}).
-
-Note that the predicted relationship between growth and either SLA or seed mass in seedlings differs if AGR in mass is used instead of RGR$_\textrm{mass}$ (i.e.
-becomes negative for SLA, positive for seed mass).
-In our study, all data recorded for these trait-stage combinations have been measured on a RGR base for mass (see Fig S9).
-
-\textbf{Effect on absolute and relative growth rates}
-Tree growth in diameter, height or mass can be expressed as either absolute growth rate (AGR) or relative growth rate (RGR).
-The choice of the growth measurement is generally confounded with the size of the plant; RGR in mass is mainly used for seedling, and AGR in diameter or height are mainly used for adult.
-According to the growth model, the predicted relationship between growth and seed mass in seedlings reverses if AGR$_\textrm{mass}$ is used instead of RGR$_\textrm{mass}$ (see Appendix \ref{sec:growth}).
-The correlation with RGR$_\textrm{mass}$ is negative but becomes positive with AGR$_\textrm{mass}$.
-For SLA, WD, Hmax, and Aarea, the direction of the predicted relationship is not affected by the growth measurement used.
-However RGR and AGR are fundamentally different for a lot of ecologists.
-So we adopted a two steps approach, first we were conservative by focusing exclusively on RGR, then we compared results with those of a more inclusive dataset with both RGR and AGR.
-
-All the above hypotheses arise from direct mechanistic causation between traits and growth rate.
-It is possible that other correlations may arise indirectly.
-For example, seed size is somewhat correlated with height at maturity \citep{Westoby:2009ch}, and so an indirect correlation might arise between seed size and GR in large plants, even though no direct influence is expected.
-Nevertheless, for purposes of this paper we adopt working hypotheses arising only from direct mechanistic causation.
 
@@
 TODO: XXXX Something about limited amount of data
+TODO: XXX some thing about qualitative predictions \ref{Falster-2016}
 
@@
 Several authors have suggested that the disappearance of SLA's influence on growth might be due to a disproportionate accumulation of leaf area by low SLA species \citep{Reich:1992wm,Poorter:2008iu,Wright:2010tp}, yet it remains unclear whether such a mechanism works as intended.
-Further, the assumed empirical relationship between SLA and total leaf area does not hold true as a generalisation across large number of species \citep{Duursma-2015}.
+\footnote{R3:  It is difficult to figure out what this statement is referring to.
+Were these publications referring to an increase in LAI and hence self-shading in large plants with high SLA as compared to large plants with low SLA?} Further, the assumed empirical relationship between SLA and total leaf area does not hold true as a generalisation across large number of species \citep{Duursma-2015}.
 In the model described here, the mechanism is slightly different: high-SLA species incur faster leaf turnover, the cost of which outweighs the benefits of cheap leaf construction at larger sizes.
+\footnote{TODO XXX R3:That field-grown seedlings generally have higher SLAs than do trees of the same species under similar high-light environments (King 1999) is consistent with both our observed and predicted growth benefits of high SLA for seedlings.}
 
@@
 The code and data for producing all figures and results in this paper is available at \smurl{github.com/AnaisGibert/Growth\_trait\_metaanalysis}.
-Upon publication, a copy of the data set will also be made available in the Dryad Digital Repository.
+Prior to publication, the data set will also be made available in the Dryad Digital Repository.
 
@@
 \setcounter{table}{0}
+
+\newcommand{\sepp}{{\color{grey}/}}
+
 \begin{table}[h!]
 \centering
-\caption{Hypothesised effects of traits on key elements of plant function determining growth rate.
-Arrows indicate the effect an increase in trait value would have on the main elements of growth eqs.
-\ref{eq:eq0}-\ref{eq:eq4} in Appendix \ref{sec:growth}, dashes indicate no significant effect.
-Traits names as in Figure 1.
-$a_\textrm{l}$ : leaves area, $m_\textrm{t}$: vegetative live mass, $b$: live biomass.
-For further details, see Appendix \ref{sec:growth}.}
+\caption{Hypothesised effects of traits on key elements of plant function determining growth rate, as described in eq.
+\ref{eq:eq0}-\ref{eq:eq4}.
+Arrows indicate the effect an increase in trait value would have on each element of the equations, with dashes indicating no effect.
+For further details, see main text.}
 {\footnotesize
@@
   \begin{tabular}{lllcccccc}
-  & & & & SLA & WD & Hmax & seed mass & Aarea \\ \hline
-  \multicolumn{3}{ l } {Main element of growth} & & & & & \\ 
-  & \multicolumn{2}{ l } {Leaf deployment per mass}  & $\frac{\textrm{d}a_\textrm{l}}{\textrm{d}m_\textrm{t}}$ & $\uparrow$ & $\downarrow$ & - & - & - \\
-  & \multicolumn{2}{ l } {Net live biomass production} & $\frac{\textrm{d}b}{\textrm{d}t}$ & & & & & \\
+  & & & & SLA & WD & Hmax & Seed mass & Aarea \\ \hline
+  \\
+  \multicolumn{9}{ l } {\textbf{Elements of equations \ref{eq:eq0}-\ref{eq:eq4}}}  \\
+  & \multicolumn{2}{ l } {Leaf deployment per mass}  & $\frac{\ud A_{\rm l}}{\ud M_{\rm t}}$ & \\
+    & &     \tabitem leaf  &  & $\uparrow$ & - & - & - & - \\
+    & &     \tabitem sapwood & & - & $\downarrow$ & - & - & - \\
+    & &     \tabitem root & & - & - & - & - & - \\
+  & \multicolumn{2}{ c } {Allocation to vegetative growth} & $\frac{\ud M_{\rm t}}{\ud B}$ & - & - & $\uparrow$ & - & - \\
+  & & & & & & \\
+  & \multicolumn{2}{ l } {Net live biomass production} & $\frac{\ud B}{\ud t}$ & & & & & \\
   & &     \tabitem photosynthesis & & - & - & - & - & $\uparrow$  \\
-  & &     \tabitem respiration   & & - & - & - & - & -  \\
-  & &     \tabitem leaf turnover & & $\uparrow$ & - & - & - & - \\
-  & \multicolumn{2}{ c } {Allocation to vegetative growth} & $\frac{\textrm{d}m_\textrm{t}}{\textrm{d}b}$ & - & - & $\uparrow$ & - & - \\ 
-  & & & & & & \\
-    \multicolumn{3}{ l } {Relative growth rate in mass} & & $\uparrow$ or $\downarrow$ & $\downarrow$ & - or $\uparrow$ & $\downarrow$ or - & $\uparrow$\\
+  & &     \tabitem respiration   & & - & - & - & - & $\uparrow$  \\
+  & &     \tabitem leaf turnover & & $\downarrow$ & - & - & - & - \\
+  & \multicolumn{2}{ l } {Architecture} & $\frac{\ud H}{\ud A_{\rm l}}$ & - & - & - & - & - \\
+  & \multicolumn{2}{ l } {Sapwood area per leaf} & $\frac{\ud A_{\rm ss}}{\ud A_{\rm l}}$ & - & - & - & - & - \\
+  & \multicolumn{2}{ l } {Sapwood turnover} & $k_{\rm ss}$ & - & - & - & - & - \\ \hline
+  \\
+  \multicolumn{9}{ l } {\textbf{Predicted effect on plant growth rate} (small plant {\sepp} large plant)} \\
+  & \multicolumn{2}{ l } {in mass, $M_{\rm t}$} \\
+  & & \tabitem{Absolute} & & $-$\sepp$\downarrow$ & $-$\sepp$-$ &  $-${\sepp}$\uparrow$ & $\uparrow${\sepp}$-$ & $\uparrow${\sepp}$\uparrow$ \\
+  & & \tabitem{Relative} & & $\uparrow${\sepp}$\downarrow$ & $-${\sepp}$-$ &  $-${\sepp}$\uparrow$ & $\downarrow${\sepp}$-$ & $\uparrow${\sepp}$\uparrow$ \\
+  & \multicolumn{2}{ l } {in height, $H$} \\
+  & & \tabitem{Absolute} & & $\uparrow${\sepp}$\downarrow$ & $\downarrow${\sepp}$\downarrow$ & $-${\sepp}$\uparrow$ & $\uparrow${\sepp}$-$ & $\uparrow${\sepp}$\uparrow$ \\
+  & & \tabitem{Relative} & & $\uparrow${\sepp}$\downarrow$ & $\downarrow${\sepp}$\downarrow$ & $-${\sepp}$\uparrow$ & $\downarrow${\sepp}$-$ & $\uparrow${\sepp}$\uparrow$ \\
+  & \multicolumn{2}{ l } {in diameter, $D$} \\
+  & & \tabitem{Absolute} & & $\uparrow${\sepp}$\downarrow$ & $\downarrow${\sepp}$\downarrow$ & $-${\sepp}$\uparrow$ & $\uparrow${\sepp}$-$ & $\uparrow${\sepp}$\uparrow$ \\
+  & & \tabitem{Relative} & & $\uparrow${\sepp}$\downarrow$ & $\downarrow${\sepp}$\downarrow$ & $-${\sepp}$\uparrow$ & $\downarrow${\sepp}$-$ & $\uparrow${\sepp}$\uparrow$ \\
 \hline
@@
 \clearpage
+
+\subsection{Simplified growth equations for seedlings of similar size}
+
+For the case of seedlings, eqs.
+\ref{eq:eq0}-\ref{eq:eq1} can be simplified considerably.
+Turnover of all tissues and allocation to reproduction have not yet begun.
+It is also common to assume all respiration rates are proportional to leaf area.
+Biomass growth rate in seedling then becomes a linear function of leaf area:
+\begin{equation}\label{eq:eq1_seedlings}
+{\frac{\ud M_{\rm t}}{\ud t}}  \approx  A_{\rm l} \, y \, (p - r_{\rm l}).
+\end{equation}
+
+The \textbf{relative growth rate in mass} $({\rm RGR}_{{\rm mass}})$ in seedlings can be obtained by dividing both sides of this simplified eq \ref{eq:eq1_seedlings} by the total mass of living tissues $M_{\rm t}$.
+The outcome is equivalent to the classical partitioning of RGR \citep{Lambers:1992bj, Cornelissen:1998ta}:
+\begin{equation}\label{eq:eq1_seedlings_RGR}
+{\rm RGR}_{{\rm mass}}  \approx {\rm NAR} \times  {\rm SLA} \times  {\rm LMF},
+\end{equation}
+where net assimilation rate NAR = $y \, (p - r)$, SLA = $A_{\rm l}/ M_{\rm l}$ and leaf mass fraction LMF = $M_{\rm l}/ M_{\rm t}$.
+
 \subsection{Quantifying and exploring the cause of heterogeneity in effect sizes}

### 2016-01-18 MS.tex
Small corection

@@
 \ref{fig:fig4}b).
-The correlation coefficients recorded for AGR came from Augspurger & Kelly (1984) and unlike others they used wood density values from adult plants together with growth from juveniles.
+The correlation coefficients recorded for AGR came from \citet{Augspurger:1984ct} and unlike others they used wood density values from adult plants together with growth from juveniles.
 

### 2016-01-19 MS.tex
Functions incorporated in Appendix Fig A8 moved as Fig A7 Fig A8 and A9 performed with entire dataset captions of these figures modified accordingly

@@
 For Hmax, the expectation was for a correlation with growth to be present for large plants but absent for smaller sizes, the mechanism being increased relative allocation to reproduction as Hmax is approached.
-Here, Hmax was positively correlated with growth at adult stage ($\bar{r}= 0.38 \pm 0.05$), not correlated at sapling stages (Fig \ref{fig:fig3}c, CIs overlapping zero) and no data were recorded for seedling stages.
+Here, Hmax was positively correlated with growth at adult stage ($\bar{r}= 0.38 \pm 0.05$), not correlated at sapling stage (Fig \ref{fig:fig3}c, CIs overlapping zero) and no data were recorded for seedling stage.
 While these results were consistent with expectation, we could not distinguish with another alternative: Hmax was correlated to growth for adult stage, but the correlation between Hmax and growth at sapling stage was not significantly different from that observed at adult stage (model fit not improved when stage was incorporated, see log likelihood ratio tests in Fig.
@@
 \centering
+\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/Fig1.pdf}
+\caption{Number of recorded correlations between trait and growth rate in our dataset, by stage and trait.
+Traits are: Aarea (or Amass) = rate of CO$_{2}$ assimilation per unit leaf area (or leaf mass) = maximum photosynthetic rate, Hmax = asymptotic or maximum height,  Ks = stem hydraulic conductance, LA = leaf area, LMR = leaf mass ratio, NARarea = net mass assimilation rate per unit of leaf area, Nmass (or Narea) = nitrogen content per unit of leaf mass (or leaf area), Pmass = phosphorus content per unit of leaf mass, SA/LA = sapwood area per leaf area, SLA = specific leaf area, Thickness = leaf thickness, Vessel size = stem conduit size, Vessel density = stem conduit density, WD = wood density.
+Results shown are from the entire dataset (see methods for details).}
+\label{fig:fig1}
+\end{figure}
+
+\begin{figure}[h!]
+\centering
 \includegraphics[width=15cm,height=20cm,keepaspectratio]{output/Fig2.pdf}
@@
 \label{fig:fig2}
-\end{figure}
-
-\begin{figure}[h!]
-\centering
-\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/Fig1.pdf}
-\caption{Number of recorded correlations between trait and growth rate in our dataset, by stage and trait.
-Traits are: Aarea (or Amass) = rate of CO$_{2}$ assimilation per unit leaf area (or leaf mass) = maximum photosynthetic rate, Hmax = asymptotic or maximum height,  Ks = stem hydraulic conductance, LA = leaf area, LMR = leaf mass ratio, NARarea = net mass assimilation rate per unit of leaf area, Nmass (or Narea) = nitrogen content per unit of leaf mass (or leaf area), Pmass = phosphorus content per unit of leaf mass, SA/LA = sapwood area per leaf area, SLA = specific leaf area, Thickness = leaf thickness, Vessel size = stem conduit size, Vessel density = stem conduit density, WD = wood density.
-Results shown are from the entire dataset (see methods for details).}
-\label{fig:fig1}
 \end{figure}
@@
 \centering
+\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA8.pdf}
+\caption{Number of correlation extracted by traits, stage, and growth type (absolute vs relative, and measurement).
+a) Specific leaf area (SLA), b) Wood density (WD), c) Asymptotic maximum height (Hmax), d) Seed mass and e) Assimilation rate of CO2 (Aarea).
+Absolute growth rate (AGR) is on the left and relative growth rate (RGR) on the right of each plot.
+Results shown here are from the "ideal" subset of the data (for details see ``Material and Methods'').
+}
+\label{fig:figA8}
+\end{figure}
+
+\begin{figure}[h!]
+\centering
 \includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA7.pdf}
@@
 The open points correspond to the estimated missing studies.
-The number of missing values is 7 for SLA,1 for WD, 0 for Hmax, 6 for seed mass and 0 for Aarea.
-Results shown here are from the ``ideal'' subset of data (for details see ``Material and Methods'').}
+The number of missing values is 4 for SLA,0 for WD, 0 for Hmax, 11 for seed mass and 0 for Aarea.
+Results shown here are from the entire dataset.
+Results with the "ideal" subset of data (for details see ``Material and Methods''), shown no missing values for all traits.}
 \label{fig:figA7}
-\end{figure}
-
-\begin{figure}[h!]
-\centering
-\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA8.pdf}
-\caption{Number of correlation extracted by traits, stage, and growth type (absolute vs relative, and measurement).
-a) Specific leaf area (SLA), b) Wood density (WD), c) Asymptotic maximum height (Hmax), d) Seed mass and e) Assimilation rate of CO2 (Aarea).
-Absolute growth rate (AGR) is on the left and relative growth rate (RGR) on the right of each plot.
-Results shown here are from the entire dataset (for details see ``Material and Methods'').
-}
-\label{fig:figA8}
 \end{figure}
@@
 The colours correspond to the stage for which the r values have been recorded: red points corresponds to adult stage, orange points to saplings, and grey points to seedlings.
-Results shown here are from the ``ideal'' subset of data (for details see ``Material and Methods'').}
+Results shown here are from the entire dataset.}
 \label{fig:figA9}
@@
 
-\noindent\textbf{Goal:} In our meta-analysis, reported studies differed in design as well as in vegetation type, biome or species studied.
-Such diversity is commonly referred to as methodological heterogeneity, and may or may not be responsible for observed discrepancies in the results of the studies.
-The extent of heterogeneity might influence the results of the meta-analysis, and thus induce some difficulty in drawing overall conclusions (See \citealt{Higgins:2002iq}).
-It is therefore important to be able to quantify the extent of heterogeneity among a collection of studies.
-
-\noindent\textbf{Methods:} A common way of addressing the extent of heterogeneity is the statistic $I^{2}$ (\citealt{Santos:2012gt}, originally defined by \citealt{Higgins:2002iq}).
-$I^{2}$ estimates the consistency of the results obtained from published studies used in our meta-analysis; it describes the percentage of variability in point estimates that is due to heterogeneity rather than sampling error.
-It can be interpreted as a ratio (0\% $<$ $I^{2}$ $<$ 100\%) not affected by the number of studies or the metric of the effect size in the analysis.
-
-An $I^{2}$ near zero indicates that almost all of the dispersion will be attributed to random error, and any attempt to explain the variance is an attempt to explain something that is (by definition) random.
-By contrast, as $I^{2}$ moves away from zero we know that some of the variance is real and can potentially be explained by subgroup analysis or meta-regression.
-There is no universal rule to cover definition for ``low'', ``moderate'' or ``high'' heterogeneity.
-\citealt{Higgins:2003hz} suggested some benchmarks for $I^{2}$ based on the survey of meta-analyses of clinical trials.
-They suggested that values on the order of 25\%, 50\% and 75\% might be considered as ``low'', ``moderate'' and ``high'', respectively.
-These suggestions are tentative; the interpretation of heterogeneity in a systematic review will depend critically on the size and direction of treatment effects, as well as on considerations of methodological diversity in the studies (see \citealt{Borenstein:2009um}).
-Here, we estimated $I^{2}$ as following equation from \citealt{Higgins:2002iq}, then we calculated how part of the heterogeneity may be due to the influence of moderators (stage and publication year) and finally we asked if the residual heterogeneity was statistically significant.
-In R, we used the package metafor  \citep{Viechtbauer-2010}.
-
-\noindent\textbf{Results:} We observed high levels of heterogeneity for all traits (SLA :$I^{2}$ 85.4\% CI: 80.9 to 92.1, WD :$I^{2}$ 61.8\% CI: 42.8 to 84.1, Hmax: $I^{2}$ 81.2\% CI: 69.8 to 93.4, seed mass: $I^{2}$ 91.2\%, 85.9 to 96.1, Aarea: $I^{2}$ 68.3\% CI: 33.7 to 90.1) which suggests that the correlations coefficient r between growth and traits are not uniform across the range of studies investigated.
-This result suggested that a large part of the variance is not explained by sampling error.
-
-For SLA and seed mass, 50.1\% and 20\% respectively of the total amount of heterogeneity were accounted for by including the plant stage as a moderator.
-For the other traits, the plant stage explained little or no part of the heterogeneity observed across studies ($<$5\%).
-These results were consistent with our expectations about a shift in the relationship between growth and traits across plant size for SLA and seed mass, and the absence of an effect for WD and Aarea (see Theoretical expectation section).
-The result for Hmax was more ambiguous since we expected the relationship between Hmax and growth rate to be absent in seedlings but to strengthen with increasing plant size (at adult stage).
-As discussed in the results section of the article, the smaller number of replicate studies for sapling and seedling stage limited the generality of our conclusion for this trait.
-
-The test for residual heterogeneity was significant for all traits, possibly indicating that other moderators not considered in the model were influencing the correlation between growth and traits.
-This is not surprising because although the trait and growth measurements are standardized \citep{Cornelissen:2003gw}, studies differed in their design as well as in vegetation type, biome, and species studied.
-Indeed, a goal in the trait literature is to establish general patterns of correlation between growth and traits and to validate them across a large variety of conditions.
-Here, we did not explore the influence of other moderators, since our goal was to test clear hypotheses about the influence of plant size/stage, not to establish the best predictor of the correlation between growth and traits.
-Finally, since between study variation is significant, as indicated by heterogeneity analyses, the use of the random effect model was appropriate in our meta-analysis.
-
-\subsection{Testing for publication bias}
-\noindent\textbf{Goal:} Studies with significant results are more likely to be published.
-As a consequence, the studies in a meta-analysis may overestimate the true effect size because they are based on a biased sample of the target population of studies.
-A publication bias occurs when the probability of publication depends on the statistical significance of the effect.
-Here we tested if there is evidence of any bias, and if the effect size observed for each trait is an artefact of this bias.
-
-\noindent\textbf{Methods:} Initially, we checked the dataset for publication bias with a visual assessment of funnel plots.
-A publication bias toward significant results creates an asymmetric funnel with small studies with non-significant effects missing from the mouth of the funnel on the side opposite to the true effect.
-While funnel plot are recommended to aid interpretation, there is a high risk of failing to detect actual publication bias (see \citealt{Koricheva:2013tz}) by using an exclusively visual assessment.
-In addition, funnel plots are not effective when the number of studies is small ($<30$) such as for Aarea and seed mass.
-Next, we used the ``trim and fill'' method to estimate the number of studies missing from our meta-analysis. This method adjusts for funnel-plot asymmetry \citep{Duval:2000dg}.
-Finally, we estimated the number of studies needed to overturn a result, using Rosenberg's fail-safe number \citep{Rosenberg:2005hk}.
-The fail-safe N is not based on funnel plot asymmetry.
-Rather, the Rosenberg method calculates the number of studies on-average null results that would need to be added to the given set of observed outcomes to reduce the significance level (p-value) of the weighted average effect \citep{Rosenberg:2005hk}.
-A significant meta-analytic result is robust if the fail-safe N is greater than 5k+10, where k is the number of studies already in the meta-analysis \citep{Rosenthal:1979do}.
-In R, we used the package ``metafor''  \citep{Viechtbauer-2010}.
-
-\noindent\textbf{Results:} As expected the correlation coefficient varied less as sample size increased (funnel plots in Fig.
-\ref{fig:figA9}).
-Funnel plots exhibited a typical funnel shape for all five functional traits analysed, showing no evidence for publication bias (Fig.
-\ref{fig:figA9}).
-The ``trim and fill'' method detected some missing values in our data.
-The estimated number of missing value ranges from 0 to 7 depending on the trait considered (Fig.
-\ref{fig:figA9}).
-The overall estimates measured with the fill in data changed from $0.5 \pm 0.07$  to $0.4 \pm 0.07$ for SLA and from $-0.48 \pm 0.11$ to $-0.32 \pm 0.12$ for the seed mass, suggesting a lower correlation coefficient for SLA, and seed mass.
-Although the correlations estimated with the missing studies filled in were closer to zero than without, the trait effect is still statistically significant.
-The Rosenberg's Fail-safe (N) were 7086, 1823, 990, 574, 291 for SLA, WD, Hmax, Seedmass, and Aarea, suggesting that a large number of studies with a mean correlation coefficient of 0 need to be added to the analysis before the cumulative correlation would become non-significant.
-N was greater than 5k+10 for all traits.
-These results suggest that the impact of publication bias is probably trivial in our meta-analyses.
-
-\subsection{Exploring temporal changes in effect size}
-\noindent\textbf{Goal:} Our meta-analysis combines data from studies published between 1983 and 2014.
-It has been shown that the magnitude of the effect size may change over time due to a publication bias (i.e.
-a lag to publish negative results), a change in the methodology or biological changes in the magnitude of the effect (see \citealt{Koricheva:2013hy}).
-Therefore, detecting such temporal changes may be important to the interpretation of the results of a meta-analysis.
-
-\noindent\textbf{Methods:} In the trait literature the year of publication may be confounded with a methodological change.
-Indeed, in the early 90's studies mainly focused on seedlings, whereas today a broader range of plant sizes/stages are studied (Fig.
-\ref{fig:figA9}).
-As a consequence, we used publication year as a moderator in our analyses \citep{Zvereva:2008jm} across but also within stages for all traits.
-
-\noindent\textbf{Results:} There was a change in the effect size with publication year for SLA ($p<0.0001$, estimates: $-0.04 \pm 0.009$ ), seed mass ($p = 0.011$, estimates: $0.041 \pm 0.016$ ) and Aarea ($p = 0.0102$, estimates: $-0.0453 \pm 0.0176$ ).
-Fig.
-\ref{fig:figA9} shows that for these three traits the publication years may be confounded with plant stage; correlation coefficients have been reported since 1993, but studies started to report data on adult stage only ten years later (around 2000-2007).
-
-For SLA and seed mass, a publication year effect was not observed within seedling and sapling stages, but was identified for the adult stage (SLA $p = 0.003$, seed mass $p = 0.06$).
-For both SLA and seed mass, the magnitude of the effect size decreased with publication year (Fig.
-\ref{fig:figA9} a and d), suggesting we overestimated the magnitude of the effect size for these two traits.
-In reality, the main effect size obtained would be more close to zero or more negative for SLA and more positive for seed mass.
-These results are consistent with our hypotheses; we expected a negative or non-significant effect of SLA on growth in adult stage, and a non-significant or positive effect of seed mass on plant growth (see theoretical expectation).
-
-For Aarea, publication year explained a part of the variation across stage but not within stage, and the magnitude of the effect size decreased with publication year.
-This pattern is classic feature in meta-analyses: \citealt{Koricheva:2013hy} showed that a majority of studies reported a decrease rather than an increase in the magnitude of effect size with publication year.
-Yet, here this effect did not lead to a reduction in statistical significance of the main effect size or to a change of sign.
-While overestimated, the main effect size for the correlation between growth and Aarea stays positive (Fig.
-\ref{fig:figA9} e).
-
-The temporal changes were confounded with a plant stage effect in our meta-analysis, but they did not jeopardize the stability of our conclusions.
-The conclusions of a meta-analysis conducted in different years should not differ from those reported here.
+\input{ms_suppinfo}
 

### 2016-01-19 ms_suppinfo.Rnw
Functions incorporated in Appendix Fig A8 moved as Fig A7 Fig A8 and A9 performed with entire dataset captions of these figures modified accordingly

<<preload, echo=FALSE>>=
library(knitr)
opts_chunk$set(echo=FALSE)
@

\noindent\textbf{Goal:} In our meta-analysis, reported studies differed in design as well as in vegetation type, biome or species studied. Such diversity is commonly referred to as methodological heterogeneity, and may or may not be responsible for observed discrepancies in the results of the studies. The extent of heterogeneity might influence the results of the meta-analysis, and thus induce some difficulty in drawing overall conclusions (See \citealt{Higgins:2002iq}). It is therefore important to be able to quantify the extent of heterogeneity among a collection of studies.

\noindent\textbf{Methods:} A common way of addressing the extent of heterogeneity is the statistic $I^{2}$ (\citealt{Santos:2012gt}, originally defined by \citealt{Higgins:2002iq}). $I^{2}$ estimates the consistency of the results obtained from published studies used in our meta-analysis; it describes the percentage of variability in point estimates that is due to heterogeneity rather than sampling error. It can be interpreted as a ratio (0\% $<$ $I^{2}$ $<$ 100\%) not affected by the number of studies or the metric of the effect size in the analysis.

An $I^{2}$ near zero indicates that almost all of the dispersion will be attributed to random error, and any attempt to explain the variance is an attempt to explain something that is (by definition) random. By contrast, as $I^{2}$ moves away from zero we know that some of the variance is real and can potentially be explained by subgroup analysis or meta-regression.
There is no clear rule to cover definition for ``low'', ``moderate'' or ``high'' heterogeneity. \citealt{Higgins:2003hz} suggested some benchmarks for $I^{2}$ based on the survey of meta-analyses of clinical trials. They suggested that values on the order of 25\%, 50\% and 75\% might be considered as ``low'', ``moderate'' and ``high'', respectively. These suggestions are tentative; the interpretation of heterogeneity in a systematic review will depend critically on the size and direction of treatment effects, as well as on considerations of methodological diversity in the studies (see \citealt{Borenstein:2009um}).
Here, we estimated $I^{2}$ as following equation from \citealt{Higgins:2002iq} using the entire dataset, then we calculated how part of the heterogeneity may be due to the influence of moderators (stage and publication year) and finally we asked if the residual heterogeneity was statistically significant. In R, we used the package metafor  \citep{Viechtbauer-2010}.

\noindent\textbf{Results:} We observed high levels of heterogeneity for all traits (SLA :$I^{2}$ \Sexpr{round(fun_Heterogeneity.H(GCi[["SLA"]], ~stageRGR)$Hlevel,0)}\% CI: \Sexpr{round(fun_Heterogeneity.CI(GCi[["SLA"]])$random[7], 0)}-\Sexpr{round(fun_Heterogeneity.CI(GCi[["SLA"]])$random[11],0)}\%, WD :$I^{2}$ \Sexpr{round(fun_Heterogeneity.H(GCi[["WD"]], ~stage)$Hlevel,0)}\% CI: \Sexpr{round(fun_Heterogeneity.CI(GCi[["WD"]])$random[7], 0)}-\Sexpr{round(fun_Heterogeneity.CI(GCi[["WD"]])$random[11],0)}, Hmax: $I^{2}$ \Sexpr{round(fun_Heterogeneity.H(GCi[["Hmax"]], ~stageRGR)$Hlevel,0)}\% CI: \Sexpr{round(fun_Heterogeneity.CI(GCi[["Hmax"]])$random[7], 0)}-\Sexpr{round(fun_Heterogeneity.CI(GCi[["Hmax"]])$random[11],0)}, seed mass: $I^{2}$ \Sexpr{round(fun_Heterogeneity.H(GCi[["Seedmass"]], ~stage)$Hlevel,0)}\%, CI \Sexpr{round(fun_Heterogeneity.CI(GCi[["Seedmass"]])$random[7], 1)}-\Sexpr{round(fun_Heterogeneity.CI(GCi[["Seedmass"]])$random[11],1)}, Aarea: $I^{2}$ \Sexpr{round(fun_Heterogeneity.H(GCi[["Aarea"]], ~stage)$Hlevel,1)}\% CI: \Sexpr{round(fun_Heterogeneity.CI(GCi[["Aarea"]])$random[7], 0)}-\Sexpr{round(fun_Heterogeneity.CI(GCi[["Aarea"]])$random[11],0)}) which suggests that the correlations coefficient r between growth and traits are not uniform across the range of studies investigated. This result suggested that a large part of the variance is not explained by sampling error.

For SLA, seed mass and Hmax, \Sexpr{round(fun_Heterogeneity.H(GCi[["SLA"]], ~stageRGR)$Hexplained,1)}\%, \Sexpr{round(fun_Heterogeneity.H(GCi[["Seedmass"]], ~stage)$Hexplained,1)}\% and \Sexpr{round(fun_Heterogeneity.H(GCi[["Hmax"]], ~stageRGR)$Hexplained, 0)}\% respectively of the total amount of heterogeneity were accounted for by including the plant stage as a moderator. For the other traits, the plant stage explained little or no part of the heterogeneity observed across studies ( WD: \Sexpr{round(fun_Heterogeneity.H(GCi[["WD"]], ~stage)$Hexplained, 0)}\% and Aarea: \Sexpr{round(fun_Heterogeneity.H(GCi[["Aarea"]], ~stage)$Hexplained, 1)}\% ). These results were consistent with our expectations about a shift in the relationship between growth and traits across plant size for SLA, seed mass and Hmax, and the absence of an effect for WD and Aarea (see Theoretical expectation section).

The test for residual heterogeneity was significant for all traits, possibly indicating that other moderators not considered in the model were influencing the correlation between growth and traits. This is not surprising because although the trait and growth measurements are standardized \citep{Cornelissen:2003gw}, studies differed in their design as well as in vegetation type, biome, and species studied. Indeed, a goal in the trait literature is to establish general patterns of correlation between growth and traits and to validate them across a large variety of conditions. Here, we did not explore the influence of other moderators, since our goal was to test clear hypotheses about the influence of plant size/stage, not to establish the best predictor of the correlation between growth and traits. Finally, since between study variation is significant, as indicated by heterogeneity analyses, the use of the random effect model was appropriate in our meta-analysis.

\subsection{Testing for publication bias}
\noindent\textbf{Goal:} Studies with significant results are more likely to be published. As a consequence, the studies in a meta-analysis may overestimate the true effect size because they are based on a biased sample of the target population of studies. A publication bias occurs when the probability of publication depends on the statistical significance of the effect. Here we tested if there is evidence of any bias, and if the effect size observed for each trait is an artefact of this bias.

\noindent\textbf{Methods:} Initially, we checked the dataset for publication bias with a visual assessment of funnel plots. A publication bias toward significant results creates an asymmetric funnel with small studies with non-significant effects missing from the mouth of the funnel on the side opposite to the true effect. While funnel plot are recommended to aid interpretation, there is a high risk of failing to detect actual publication bias (see \citealt{Koricheva:2013tz}) by using an exclusively visual assessment. In addition, funnel plots are not effective when the number of studies is small ($<30$) such as for Aarea and seed mass.
Next, we used the ``trim and fill'' method to estimate the number of studies missing from our meta-analysis. This method adjusts for funnel-plot asymmetry \citep{Duval:2000dg}.
Finally, we estimated the number of studies needed to overturn a result, using Rosenberg's fail-safe number \citep{Rosenberg:2005hk}. The fail-safe N is not based on funnel plot asymmetry. Rather, the Rosenberg method calculates the number of studies on-average null results that would need to be added to the given set of observed outcomes to reduce the significance level (p-value) of the weighted average effect \citep{Rosenberg:2005hk}. A significant meta-analytic result is robust if the fail-safe N is greater than 5k+10, where k is the number of studies already in the meta-analysis \citep{Rosenthal:1979do}.
In R, we used the package ``metafor''  \citep{Viechtbauer-2010}.

\noindent\textbf{Results:} As expected the correlation coefficient varied less as sample size increased (funnel plots in Fig. \ref{fig:figA7}). Funnel plots exhibited a typical funnel shape for all five functional traits analysed, showing no evidence for publication bias (Fig. \ref{fig:figA7}).
The ``trim and fill'' method detected some missing values in the entire dataset (but no missing values in the "ideal" dataset). In the entire dataset, the estimated number of missing value ranges from 0 to \Sexpr{fun_trim.and.fill_number(GCi[["Seedmass"]])$N} depending on the trait considered (Fig. \ref{fig:figA7}). The overall estimates measured with the fill in data changed from $0.5 \pm 0.07$ to \Sexpr{round(fun_trim.and.fill_number(GCi[["SLA"]])$estimate, 2)} $\pm$ \Sexpr{round(fun_trim.and.fill_number(GCi[["SLA"]])$se, 2)} for SLA and from $-0.48 \pm 0.11$ to \Sexpr{round(fun_trim.and.fill_number(GCi[["Seedmass"]])$estimate, 2)}$\pm$ \Sexpr{round(fun_trim.and.fill_number(GCi[["Seedmass"]])$se, 2)} for the seed mass, suggesting a lower correlation coefficient for SLA, and a higher for seed mass. Although the correlations estimated with the missing studies filled in were closer to zero than without, the trait effect is still statistically significant (CIs not overlapping zero; SLA CI \Sexpr{round(fun_trim.and.fill_number(GCi[["SLA"]])$CImin, 2)} to \Sexpr{round(fun_trim.and.fill_number(GCi[["SLA"]])$CImax, 2)}, Seed mass CI \Sexpr{round(fun_trim.and.fill_number(GCi[["Seedmass"]])$CImin, 2)} to \Sexpr{round(fun_trim.and.fill_number(GCi[["Seedmass"]])$CImax, 2)}).

The Rosenberg's Fail-safe (N) were \Sexpr{fun_fsn(GCi[["SLA"]])[2]}, \Sexpr{fun_fsn(GCi[["WD"]])[2]}, \Sexpr{fun_fsn(GCi[["Hmax"]])[2]}, \Sexpr{fun_fsn(GCi[["Seedmass"]])[2]}, \Sexpr{fun_fsn(GCi[["Aarea"]])[2]} for SLA, WD, Hmax, Seedmass, and Aarea, suggesting that a large number of studies with a mean correlation coefficient of 0 need to be added to the analysis before the cumulative correlation would become non-significant. N was greater than 5k+10 for all traits (120 $< N <$ 455).
These results suggest that the impact of publication bias is probably trivial in our meta-analyses.

\subsection{Exploring temporal changes in effect size}
\noindent\textbf{Goal:} Our meta-analysis combines data from studies published between 1983 and 2014. It has been shown that the magnitude of the effect size may change over time due to a publication bias (i.e. a lag to publish negative results), a change in the methodology or biological changes in the magnitude of the effect (see \citealt{Koricheva:2013hy}). Therefore, detecting such temporal changes may be important to the interpretation of the results of a meta-analysis.

\noindent\textbf{Methods:} In the trait literature the year of publication may be confounded with a methodological change. Indeed, in the early 90's studies mainly focused on seedlings, whereas today a broader range of plant sizes/stages are studied (Fig. \ref{fig:figA9}). As a consequence, we used publication year as a moderator in our analyses \citep{Zvereva:2008jm} across but also within stages for all traits.

\noindent\textbf{Results:} There was a change in the effect size with publication year for SLA ($p<0.0001$, estimates: $-0.04 \pm 0.009$ ), seed mass ($p = 0.011$, estimates: $0.041 \pm 0.016$ ) and Aarea ($p = 0.0102$, estimates: $-0.0453 \pm 0.0176$ ). Fig. \ref{fig:figA9} shows that for these three traits the publication years may be confounded with plant stage; correlation coefficients have been reported since 1993, but studies started to report data on adult stage only ten years later (around 2000-2007).

For SLA and seed mass, a publication year effect was not observed within seedling and sapling stages, but was identified for the adult stage (SLA $p = 0.003$, seed mass $p = 0.06$). For both SLA and seed mass, the magnitude of the effect size decreased with publication year (Fig. \ref{fig:figA9} a and d), suggesting we overestimated the magnitude of the effect size for these two traits. In reality, the main effect size obtained would be more close to zero or more negative for SLA and more positive for seed mass. These results are consistent with our hypotheses; we expected a negative or non-significant effect of SLA on growth in adult stage, and a non-significant or positive effect of seed mass on plant growth (see theoretical expectation).

For Aarea, publication year explained a part of the variation across stage but not within stage, and the magnitude of the effect size decreased with publication year. This pattern is classic feature in meta-analyses: \citealt{Koricheva:2013hy} showed that a majority of studies reported a decrease rather than an increase in the magnitude of effect size with publication year. Yet, here this effect did not lead to a reduction in statistical significance of the main effect size or to a change of sign. While overestimated, the main effect size for the correlation between growth and Aarea stays positive (Fig. \ref{fig:figA9} e).

The temporal changes were confounded with a plant stage effect in our meta-analysis, but they did not jeopardize the stability of our conclusions. The conclusions of a meta-analysis conducted in different years should not differ from those reported here.

### 2016-01-19 ms_suppinfo.tex
Functions incorporated in Appendix Fig A8 moved as Fig A7 Fig A8 and A9 performed with entire dataset captions of these figures modified accordingly

--- 2016-01-19 ms_suppinfo.Rnw
@@
-<<preload, echo=FALSE>>=
-library(knitr)
-opts_chunk$set(echo=FALSE)
-@
-
 \noindent\textbf{Goal:} In our meta-analysis, reported studies differed in design as well as in vegetation type, biome or species studied.
@@
 
-\noindent\textbf{Results:} We observed high levels of heterogeneity for all traits (SLA :$I^{2}$ \Sexpr{round(fun_Heterogeneity.H(GCi[["SLA"]], ~stageRGR)$Hlevel,0)}\% CI: \Sexpr{round(fun_Heterogeneity.CI(GCi[["SLA"]])$random[7], 0)}-\Sexpr{round(fun_Heterogeneity.CI(GCi[["SLA"]])$random[11],0)}\%, WD :$I^{2}$ \Sexpr{round(fun_Heterogeneity.H(GCi[["WD"]], ~stage)$Hlevel,0)}\% CI: \Sexpr{round(fun_Heterogeneity.CI(GCi[["WD"]])$random[7], 0)}-\Sexpr{round(fun_Heterogeneity.CI(GCi[["WD"]])$random[11],0)}, Hmax: $I^{2}$ \Sexpr{round(fun_Heterogeneity.H(GCi[["Hmax"]], ~stageRGR)$Hlevel,0)}\% CI: \Sexpr{round(fun_Heterogeneity.CI(GCi[["Hmax"]])$random[7], 0)}-\Sexpr{round(fun_Heterogeneity.CI(GCi[["Hmax"]])$random[11],0)}, seed mass: $I^{2}$ \Sexpr{round(fun_Heterogeneity.H(GCi[["Seedmass"]], ~stage)$Hlevel,0)}\%, CI \Sexpr{round(fun_Heterogeneity.CI(GCi[["Seedmass"]])$random[7], 1)}-\Sexpr{round(fun_Heterogeneity.CI(GCi[["Seedmass"]])$random[11],1)}, Aarea: $I^{2}$ \Sexpr{round(fun_Heterogeneity.H(GCi[["Aarea"]], ~stage)$Hlevel,1)}\% CI: \Sexpr{round(fun_Heterogeneity.CI(GCi[["Aarea"]])$random[7], 0)}-\Sexpr{round(fun_Heterogeneity.CI(GCi[["Aarea"]])$random[11],0)}) which suggests that the correlations coefficient r between growth and traits are not uniform across the range of studies investigated.
+\noindent\textbf{Results:} We observed high levels of heterogeneity for all traits (SLA :$I^{2}$ 84\% CI: 80-91\%, WD :$I^{2}$ 63\% CI: 48-85, Hmax: $I^{2}$ 81\% CI: 70-93, seed mass: $I^{2}$ 90\%, CI 84.9-94.9, Aarea: $I^{2}$ 71.5\% CI: 42-86) which suggests that the correlations coefficient r between growth and traits are not uniform across the range of studies investigated.
 This result suggested that a large part of the variance is not explained by sampling error.
 
-For SLA, seed mass and Hmax, \Sexpr{round(fun_Heterogeneity.H(GCi[["SLA"]], ~stageRGR)$Hexplained,1)}\%, \Sexpr{round(fun_Heterogeneity.H(GCi[["Seedmass"]], ~stage)$Hexplained,1)}\% and \Sexpr{round(fun_Heterogeneity.H(GCi[["Hmax"]], ~stageRGR)$Hexplained, 0)}\% respectively of the total amount of heterogeneity were accounted for by including the plant stage as a moderator.
-For the other traits, the plant stage explained little or no part of the heterogeneity observed across studies ( WD: \Sexpr{round(fun_Heterogeneity.H(GCi[["WD"]], ~stage)$Hexplained, 0)}\% and Aarea: \Sexpr{round(fun_Heterogeneity.H(GCi[["Aarea"]], ~stage)$Hexplained, 1)}\% ).
+For SLA, seed mass and Hmax, 41\%, 20.2\% and 17\% respectively of the total amount of heterogeneity were accounted for by including the plant stage as a moderator.
+For the other traits, the plant stage explained little or no part of the heterogeneity observed across studies ( WD: 9\% and Aarea: 0.1\% ).
 These results were consistent with our expectations about a shift in the relationship between growth and traits across plant size for SLA, seed mass and Hmax, and the absence of an effect for WD and Aarea (see Theoretical expectation section).
@@
 The ``trim and fill'' method detected some missing values in the entire dataset (but no missing values in the "ideal" dataset).
-In the entire dataset, the estimated number of missing value ranges from 0 to \Sexpr{fun_trim.and.fill_number(GCi[["Seedmass"]])$N} depending on the trait considered (Fig.
+In the entire dataset, the estimated number of missing value ranges from 0 to 11 depending on the trait considered (Fig.
 \ref{fig:figA7}).
-The overall estimates measured with the fill in data changed from $0.5 \pm 0.07$ to \Sexpr{round(fun_trim.and.fill_number(GCi[["SLA"]])$estimate, 2)} $\pm$ \Sexpr{round(fun_trim.and.fill_number(GCi[["SLA"]])$se, 2)} for SLA and from $-0.48 \pm 0.11$ to \Sexpr{round(fun_trim.and.fill_number(GCi[["Seedmass"]])$estimate, 2)}$\pm$ \Sexpr{round(fun_trim.and.fill_number(GCi[["Seedmass"]])$se, 2)} for the seed mass, suggesting a lower correlation coefficient for SLA, and a higher for seed mass.
-Although the correlations estimated with the missing studies filled in were closer to zero than without, the trait effect is still statistically significant (CIs not overlapping zero; SLA CI \Sexpr{round(fun_trim.and.fill_number(GCi[["SLA"]])$CImin, 2)} to \Sexpr{round(fun_trim.and.fill_number(GCi[["SLA"]])$CImax, 2)}, Seed mass CI \Sexpr{round(fun_trim.and.fill_number(GCi[["Seedmass"]])$CImin, 2)} to \Sexpr{round(fun_trim.and.fill_number(GCi[["Seedmass"]])$CImax, 2)}).
+The overall estimates measured with the fill in data changed from $0.5 \pm 0.07$ to 0.48 $\pm$ 0.07 for SLA and from $-0.48 \pm 0.11$ to \ensuremath{-0.29}$\pm$ 0.12 for the seed mass, suggesting a lower correlation coefficient for SLA, and a higher for seed mass.
+Although the correlations estimated with the missing studies filled in were closer to zero than without, the trait effect is still statistically significant (CIs not overlapping zero; SLA CI 0.35 to 0.62, Seed mass CI \ensuremath{-0.51} to \ensuremath{-0.06}).
 
-The Rosenberg's Fail-safe (N) were \Sexpr{fun_fsn(GCi[["SLA"]])[2]}, \Sexpr{fun_fsn(GCi[["WD"]])[2]}, \Sexpr{fun_fsn(GCi[["Hmax"]])[2]}, \Sexpr{fun_fsn(GCi[["Seedmass"]])[2]}, \Sexpr{fun_fsn(GCi[["Aarea"]])[2]} for SLA, WD, Hmax, Seedmass, and Aarea, suggesting that a large number of studies with a mean correlation coefficient of 0 need to be added to the analysis before the cumulative correlation would become non-significant.
+The Rosenberg's Fail-safe (N) were 10617, 3344, 1138, 2261, 643 for SLA, WD, Hmax, Seedmass, and Aarea, suggesting that a large number of studies with a mean correlation coefficient of 0 need to be added to the analysis before the cumulative correlation would become non-significant.
 N was greater than 5k+10 for all traits (120 $< N <$ 455).

### 2016-01-19 R/model.R

@@ -630,35 +630,47 @@ fun_Onepvalue_year <- function(x) {
 
 
 fun_Heterogeneity.CI <- function(x) {
+  x <- droplevels(x)
+  
   res_null <- rma(corr.z, vr.z, 
                   data = x[!is.na(x$corr.z) & !is.na(x$nb.sp),])
   confint(res_null)
 }
 
 fun_Heterogeneity.H <- function(x, mods) {
+  
+  x <- droplevels(x)
   res_null <- rma(corr.z, vr.z, 
                   data = x[!is.na(x$corr.z) & !is.na(x$nb.sp),])
   res_stage <- rma(corr.z, vr.z, mods = mods, 
                   data = x[!is.na(x$corr.z) & !is.na(x$vr.z),])
   Hmodel <- (res_null$tau2 - res_stage$tau2)/res_null$tau2 * 100  #% of the total amount of heterogeneity can be accounted for by including the moderators of the model
-  l <- list(Hexplained = Hmodel, pvalue = res_stage$QEp, Qdf = res_stage$QE,
+  H <- res_null$I2 
+  l <- list(Hlevel=H, Hexplained = Hmodel, pvalue = res_stage$QEp, Qdf = res_stage$QE,
     effectsize_moderator = res_stage$zval, pvalueeffectsize = res_stage$pval)
   l
 }
 
 
-
 fun_trim.and.fill_number <- function(x) {
+  x <- droplevels(x)
+  
   res <- rma(corr.z, vr.z, data = x[!is.na(x$corr.z) & !is.na(x$vr.z), ])
   ### carry out trim-and-fill analysis
   taf <- trimfill(res)
-  taf$k0
-
+  l <- list(N= taf$k0, estimate= taf$b, se =taf$se, CImax= taf$ci.ub, CImin=taf$ci.lb)
+  l
 }
 
 
-fun_year <- function(data) {
-  table <- data
+fun_fsn <- function(x){
+  a <- fsn(corr.z, vr.z, data = x[!is.na(x$corr.z) & !is.na(x$vr.z), ], type = "Rosenthal", alpha = 0.05, digits = 4)
+  a
+}
+
+
+fun_year <- function(a) {
+  table <- a
 
   res <- rma(corr.z, vr.z, mod = ~year, 
                   data = table[!is.na(table$corr.z) & !is.na(table$nb.sp),])
@@ -672,8 +684,11 @@ fun_year <- function(data) {
[…]

### 2016-01-19 R/utils.R

@@ -79,76 +79,3 @@ rename <- function(data, replace, warn_missing = TRUE, warn_duplicated = TRUE) {
 }
 
 
-list_by_sym <- function(df) {
-  split(df, df$SymArd)
-}
-
-list_by_fert <- function(df) {
-  split(df, df$Fertilization)
-}
-
-
-
-
-
-simplefreq <- function (x,y=NULL,margin=1,html=NULL) {
-  if (is.null(y)) {simplefreq.tab<-cbind(data.frame(addmargins(
-    prop.table(table(x)))), 
-    data.frame(addmargins(table(x)))[2]) 
-  colnames(simplefreq.tab)<-c(deparse(substitute(x)),"Percentage","Count") 
-  RESTABLE<-simplefreq.tab 
-  
-  MINCHI2=NULL 
-  MINOR=NULL 
-  CHI2=NULL 
-  } 
-  if (!is.null(y)) { 
-    simplefreq.tab0<-table(x,y) 
-    simplefreq.chi<-chisq.test(simplefreq.tab0,
-                               correct=FALSE) 
-    if (margin==1) 
-    { 
-      simplefreq.tab<-cbind(addmargins(prop.table(
-        addmargins(simplefreq.tab0,1),1),2), 
-        rowSums(addmargins(simplefreq.tab0,1))) 
-      colnames(simplefreq.tab)<-c(colnames(simplefreq.tab0),"Total","Count") 
-      rownames(simplefreq.tab)<-c(rownames(simplefreq.tab0),"All") 
-    } 
-    if (margin==2) 
-    { 
-      simplefreq.tab<-rbind(addmargins(prop.table(
-        addmargins(simplefreq.tab0,2),2),1), 
-        t(colSums(addmargins(simplefreq.tab0,2)))) 
-      rownames(simplefreq.tab)<-c(rownames(simplefreq.tab0),"Total","Count") 
-      colnames(simplefreq.tab)<-c(colnames(simplefreq.tab0),"All") 
-    } 
-    RESTABLE<-simplefreq.tab 
-    CHI2<-simplefreq.chi 
-    
-    WARNING1 <- "Mining chi-square : what would be the chi-square if we were analyzing a 2*2 table. " 
-    WARNING2 <- "Sign is used for over (+) or under(-) representation." 
-    
-    MINCHI2<-sign(simplefreq.chi$observed-simplefreq.chi$expected)* 
[…]

### 2016-01-19 analysis.R

@@ -33,6 +33,7 @@ CompleteData_rgr <- subset_growth(CompleteData_inter, "RGR")
 CompleteData_agr <- subset_growth(CompleteData_inter, "AbGR")
 GCi <- list_by_trait(CompleteData_inter)
 GIi <- list_by_trait(IdealData)
+knitr::knit("ms_suppinfo.Rnw", "ms_suppinfo.tex")
 GIrgr <- list_by_trait(IdealData_rgr)
 GIagr <- list_by_trait(IdealData_agr)
 GCrgr <- list_by_trait(CompleteData_rgr)
@@ -72,13 +73,13 @@ pdf("output/FigA6c.pdf")
 figure_A6.2(GCi, "Hmax", "e")
 dev.off()
 pdf("output/FigA7.pdf")
-figure_A7(GIi)
+figure_A7(GCi)
 dev.off()
 pdf("output/FigA8.pdf")
 figure_A8(GCi)
 dev.off()
 pdf("output/FigA9.pdf")
-figure_A9(GIi)
+figure_A9(GCi)
 dev.off()
 `RCi{1}` <- EffectSizeSum(CompleteData_inter)
 RCi <- list_by_trait(`RCi{1}`)

### 2016-01-19 MS.tex
Abstract modification to hilight the need of further empirical studies for underrepresented trait size classes combinations

@@
 Seed mass and maximum height were correlated with RGR only in one plant stage category: seedlings and adults, respectively.
-Yet, despite a sizeable literature on traits and growth, coverage was still limited for wood density, seed mass, maximum height and assimilation rate.
-Additional studies are needed for some trait-growth-stage relationships.
+Despite a sizeable literature on traits and growth, coverage was still limited for wood density, seed mass, maximum height and assimilation rate.
+There is still scope for strengthening our understanding of correlations between traits and growth through adding further empirical studies for  traits and size-classes underrepresented in the literature.
 

### 2016-01-19 MS.tex
editing MS

@@
 
-We aimed to identify studies reporting the correlations, measured across species, between functional traits and one of several measures of growth rate (Table \ref{tab:trade-offs}).
-We supplemented records from our own bibliographic libraries with results from searching online databases and suggestions from other researchers.
+We aimed to identify studies reporting a correlation across species, between functional traits and growth rate (e.g.
+relative or absolute growth, in diameter, height or mass, see Table \ref{tab:trade-offs}.
 Systematic searches were conducted across the two most comprehensive bibliographic platforms: Google scholar and Web of Science (Thomson Reuters).
@@
 This limitation does not apply to Google Scholar.
+We supplemented these records with results from our own bibliographic libraries and suggestions from other researchers.
 
-The biggest challenge when searching literature databases is to identify suitable studies from the vast corpus available.
+A big challenge when searching literature databases is to identify suitable studies from the vast corpus available.
 Initially we were interested to know whether data existed for a variety of traits; however the number of potential search terms made systemic searching for all these terms in Google Scholar impractical.
@@
 Both Web of Science and Google Scholar databases were searched for records linking SLA and WD to growth rate.
-On Web of Science, we searched using  search terms: (``trait'' AND (``growth rate'' OR ``relative growth rate'')) AND (``tree*'' OR ``woody*''), where ``trait'' was either (``leaf mass per area'' OR ``specific leaf area'' OR ``leaf construction cost'') or (``wood density'' OR``WD'' OR ``wood specific gravity'' OR ``stem density'' OR ``stem specific density'' OR ``SSD'' ).On Google scholar we searched using terms: ((``SLA'' OR ``LMA'' OR ``specific leaf area'' OR ``leaf mass area'' OR ``wood density'' OR ``WD'' OR ``wood specific gravity'' OR ``stem density'' OR ``stem specific density'') AND (``growth rate'' OR ``relative growth rate'')) AND (``tree*'' OR ``woody*'').
+On Web of Science, we searched using  search terms: (``trait'' AND (``growth rate'' OR ``relative growth rate'')) AND (``tree*'' OR ``woody*''), where ``trait'' was either (``leaf mass per area'' OR ``specific leaf area'' OR ``leaf construction cost'') or (``wood density'' OR``WD'' OR ``wood specific gravity'' OR ``stem density'' OR ``stem specific density'' OR ``SSD'' ).
+On Google scholar we searched using terms: ((``SLA'' OR ``LMA'' OR ``specific leaf area'' OR ``leaf mass area'' OR ``wood density'' OR ``WD'' OR ``wood specific gravity'' OR ``stem density'' OR ``stem specific density'') AND (``growth rate'' OR ``relative growth rate'')) AND (``tree*'' OR ``woody*'').
 This keyword search in Google Scholar returned approximately 18900 papers.
@@
 
-We recorded coefficient correlations for a list of 19 traits (Fig.
-\ref{fig:fig1}): the five for which we had prior expectations, plus 14 others commonly used in the trait literature.
+The 19 traits recorded (Fig.
+\ref{fig:fig1}) capture different components of plant ecological strategies.
 SLA, leaf area, leaf nitrogen and phosphorus concentration, net (mass) assimilation rates (NAR), and Aarea are traits involved in species leaf economic strategy \citep{Wright:2004jb,Wright:2010tp}.
@@
 
-Ultimately, data was recorded from from 103 different articles \citep{Aiba:1997ho, Aiba:2009ft, Antunez:2001gk, Atkin:1998in, augspurger_light_1984, baltzer_physiological_2007, baraloto_differential_2006, baraloto_seed_2005, Bloor:2003fa,  Broncano:1998ck, Brown:1996ks, Bruhn:2000jz, Cai:2007ie, CamaraZapata:2003df, CastroDiez:1998gz, CastroDiez:2003jd, Cernusak:2008ds, Chao:2008hg, Chaturvedi:2011jx, Chaturvedi:2014ie, Chave:2009iy,  coomes_comparison_1998, coomes_greater_2009, Cornelissen:1996hf, Cornelissen:1997fd, Cornelissen:1998ta, Dalling:2004gs, DeBell:1994ix, Easdale:2009gv, fan_hydraulic_2012, Fayolle:2012bx, Fujimoto:2006fg, Galmes:2005fa, Gleason:2016, gleeson_plant_1994, grotkopp_toward_2002, Grubb:1996kr, Herault:2011dd, Hoffmann:2003ga, Huante:1995fd, Huante:1995tl, Huante:1998bk, HUNT:1997ge, Iida:2014ep, Iida:2014hq, king_influence_1994, king_tree_2005,  King:2006he, Kitajima:1994ez, Kohyama:2003dk, Kruger:2006fq, Lamers:2006dl, LopezIglesias:2014dk, Loveys:2002hj, Lusk:1997ga, Lusk:2002fma, Lusk:2013bq, Lusk:2013hz, MartinezVilalta:2010iq, McCormack:2012ch, Moya:2008ep, Muller-landau_interspecific_2004, Nascimento:2005kl, Osone:2008dr, Osunkoya:1994ip, Osunkoya:2010ef, Paz:2005kx, Poorter:1999fp, Poorter:2006vb, Poorter:2008iu, Poorter:2010co, Popma:1988tv, Prior:2004cv, Quero:2008jg, Read:2011du, Reich:1998ir, Reich:1998ja, Rossatto:2009gq, RuizRobleto:2005hc, Sack:2004hm, saldana-acosta_seedling_2009, SalgadoLuarte:2012ci, Saverimuttu:1996ih, Shen:2014fw, Shipley:2002fs, Stratton:2001ck, Thomas:1996do, Tomlinson:2014im, Veneklaas:2002dt, Villagra:2013do, Villar:2006cf, walters_are_1996, Walters:1993eu, Walters:1993hf, Wang:1998cs, Warren:2005bc, Westbrook:2011ja, Wright:1999ds, Wright:2000kw, Wright:2001gb, Wright:2003kb, Wright:2010tp, Zhang:1995bh}.
+Ultimately, data was recorded from 103 different articles \citep{Aiba:1997ho, Aiba:2009ft, Antunez:2001gk, Atkin:1998in, augspurger_light_1984, baltzer_physiological_2007, baraloto_differential_2006, baraloto_seed_2005, Bloor:2003fa,  Broncano:1998ck, Brown:1996ks, Bruhn:2000jz, Cai:2007ie, CamaraZapata:2003df, CastroDiez:1998gz, CastroDiez:2003jd, Cernusak:2008ds, Chao:2008hg, Chaturvedi:2011jx, Chaturvedi:2014ie, Chave:2009iy,  coomes_comparison_1998, coomes_greater_2009, Cornelissen:1996hf, Cornelissen:1997fd, Cornelissen:1998ta, Dalling:2004gs, DeBell:1994ix, Easdale:2009gv, fan_hydraulic_2012, Fayolle:2012bx, Fujimoto:2006fg, Galmes:2005fa, Gleason:2016, gleeson_plant_1994, grotkopp_toward_2002, Grubb:1996kr, Herault:2011dd, Hoffmann:2003ga, Huante:1995fd, Huante:1995tl, Huante:1998bk, HUNT:1997ge, Iida:2014ep, Iida:2014hq, king_influence_1994, king_tree_2005,  King:2006he, Kitajima:1994ez, Kohyama:2003dk, Kruger:2006fq, Lamers:2006dl, LopezIglesias:2014dk, Loveys:2002hj, Lusk:1997ga, Lusk:2002fma, Lusk:2013bq, Lusk:2013hz, MartinezVilalta:2010iq, McCormack:2012ch, Moya:2008ep, Muller-landau_interspecific_2004, Nascimento:2005kl, Osone:2008dr, Osunkoya:1994ip, Osunkoya:2010ef, Paz:2005kx, Poorter:1999fp, Poorter:2006vb, Poorter:2008iu, Poorter:2010co, Popma:1988tv, Prior:2004cv, Quero:2008jg, Read:2011du, Reich:1998ir, Reich:1998ja, Rossatto:2009gq, RuizRobleto:2005hc, Sack:2004hm, saldana-acosta_seedling_2009, SalgadoLuarte:2012ci, Saverimuttu:1996ih, Shen:2014fw, Shipley:2002fs, Stratton:2001ck, Thomas:1996do, Tomlinson:2014im, Veneklaas:2002dt, Villagra:2013do, Villar:2006cf, walters_are_1996, Walters:1993eu, Walters:1993hf, Wang:1998cs, Warren:2005bc, Westbrook:2011ja, Wright:1999ds, Wright:2000kw, Wright:2001gb, Wright:2003kb, Wright:2010tp, Zhang:1995bh}.
 
@@
 This ``ideal'' subset, included only studies recording RGR across \underline{\textgreater} 10 species, under unstressed conditions, and where growth rates and traits were measured on plants from the same stage (expect for Hmax and seed mass, where a particular stage is by definition required to measure the trait).
-These were then compare against results obtained with the entire dataset, including all noted correlations.
+These were then compare against results obtained with the entire dataset (including all noted correlations).
 
@@
 
-TODO: XXXX
-
-We first developed a snapshot of the literature, to assess the potential to recover useful data from the wide corpus of literature available.
+We developed a snapshot of the literature, to assess the potential to recover useful data from the wide corpus of literature available.
 This snapshot was obtained via Web of Science database (Thomson Reuters), between March and June 2014, using a range of Boolean search terms in English.

### 2016-01-19 MS.tex
Done snapshot of the literature in appendix.

@@
 This keyword search in Google Scholar returned approximately 18900 papers.
-We examined all records returned from the Web of Science search (XXX) and the first 750 items from Google Scholar when ranked by ``relevance''.
+We examined all records returned from the Web of Science search (701 articles) and the first 750 items from Google Scholar when ranked by ``relevance''.
 All searches were conducted between March and December 2014.
@@
 
-We developed a snapshot of the literature, to assess the potential to recover useful data from the wide corpus of literature available.
-This snapshot was obtained via Web of Science database (Thomson Reuters), between March and June 2014, using a range of Boolean search terms in English.
-Search terms were as follows: (``trait'' AND (``growth rate'' OR ``relative growth rate'')) AND (``tree*'' OR ``woody*''), where ``trait'' was allowed to be any of the trait names listed in Table \ref{tab:lit_search}.
-This snapshot indicated that 82\% of the reported correlations linking growth to any of our five core traits would be recovered by searching only on SLA and WD, allowing us to narrow our search considerably.
-
-\linespread{1}
-
-\begin{table}[h!]
-\centering
-\caption{List of the nineteen traits targeted. Abbreviation,
-definition and search term used in the meta-analysis}
-\label{tab:lit_search}
-\vspace{0.5cm}
-{\footnotesize
-\begin{tabular}{p{3cm}p{3cm}p{8cm}}
-  \hline
-Trait & Definition & Search terms \\
-  \hline
-Aarea & Photosynthetic rate per area & ``photosynthetic rate per area'' OR ``rate of CO2 assimilation per area'' OR ``Aarea'' OR ``Amax'' OR ``photosynthetic capacity per area'' \\
-  Amass & Photosynthetic rate per mass & ``photosynthetic rate per mass'' OR ``rate of CO2 assimilation per mass'' OR ``Amass'' OR ``Amax'' \\
-  Hmax & Maximum height & ``potential height'' OR ``maximum height'' OR ``Hmax'' \\
-  Ks & Stem specific conductance & ``Ks'' OR ``stem specific conductance'' OR ``stem hydraulic conductance'' OR ``sapwood conductance'' \\
-  LA & Leaf lamina area & ``leaf length'' OR ``leaf lamina area'' OR ``leaf width'' OR ``leaf size'' \\
-  LAR & Leaf area ratio & ``leaf area ratio'' \\
-  LMR & Leaf mass ratio & ``leaf mass ratio'' OR ``leaf mass fraction'' \\
-  NARarea & Net assimilation rate per area &  ``net assimilation rate per area'' OR ``rate of dry mass increament per area'' OR ``NARarea'' OR ``NAR'' \\
-  Narea & Leaf nitrogen content per area & ``Narea'' OR ``nitrogen per area'' OR ``N/area'' OR ``leaf nitrogen content per area'' OR ``LNCarea'' OR ``leaf nitrogen content" \\
-  Nmass & Leaf nitrogen content per mass & ``Nmass'' OR ``nitrogen per mass'' OR ``N/mass'' OR ``leaf nitrogen content per mass'' OR ``LNCmass'' OR ``leaf nitrogen content" \\
-  Parea & Leaf phosphorus content per area & ``Parea'' OR ``leaf P'' OR  ``leaf phosphorus content per area''  OR ``leaf phosphorus content'' \\
-  Pmass & Leaf phosphorus content per mass & ``Pmass'' OR ``leaf P'' OR  ``leaf phosphorus content per mass'' OR ``leaf phosphorus content'' \\
-  SA/LA & Sapwood area per leaf area & ``sapwood area per leaf area'' OR ``huber value'' OR ``leaf area per sapwood area'' \\
-  Seed mass & Seed mass & ``seed mass'' OR ``seed size'' OR ``seed volume'' \\
-  SLA & Specific Leaf Area & ``leaf mass per area'' OR ``specific leaf area'' OR ``leaf construction cost'' \\
-  Thickness & Leaf thickness & ``leaf thickness''  OR ``leaf tissue density'' \\
-  Vessel density & Vessel density & ``vessel density'' OR ``stem conduit density'' \\
-  Vessel size & Vessel area or diameter & ``conduit area'' OR ``stem conduit area'' OR ``vessel diameter'' OR ``vessel size'' OR ``conduit size''   \\
-  WD & Wood density & ``wood density'' OR``WD'' OR ``wood specific gravity'' OR ``stem density'' OR ``stem specific density'' OR ``SSD'' \\
-   \hline
-\end{tabular}
-}
-\end{table}
+\input{ms_snapshotinfo}
 

### 2016-01-19 ms_snapshotinfo.Rnw
Done snapshot of the literature in appendix.

<<preload, echo=FALSE>>=
library(knitr)
opts_chunk$set(echo=FALSE)
@

We developed a snapshot of the literature, to assess the potential to recover useful data from the wide corpus of literature available by searching exclusively on SLA and WD. This snapshot was obtained via Web of Science database (Thomson Reuters), between March and June 2014, using a range of Boolean search terms in English. Search terms were as follows: (``trait'' AND (``growth rate'' OR ``relative growth rate'')) AND (``tree*'' OR ``woody*''), where ``trait'' was allowed to be any of the trait names listed in Table \ref{tab:lit_search}. This snapshot indicated that \Sexpr{round(fun_snapshot(Snapshot)$main.traits ,0)}\% of the reported correlations linking growth to any of our five core traits would be recovered by searching only on SLA and WD. And it was \Sexpr{round(fun_snapshot(Snapshot)$all.traits ,0)}\% of the literature that would be captured by SLA and WD for the total 19 traits. These results allow us to narrow our search considerably.

\linespread{1}

\begin{table}[h!]
\centering
\caption{List of the nineteen traits targeted. Abbreviation,
definition and search term used in the meta-analysis}
\label{tab:lit_search}
\vspace{0.5cm}
{\footnotesize
\begin{tabular}{p{3cm}p{3cm}p{8cm}}
  \hline
Trait & Definition & Search terms \\
  \hline
Aarea & Photosynthetic rate per area & ``photosynthetic rate per area'' OR ``rate of CO2 assimilation per area'' OR ``Aarea'' OR ``Amax'' OR ``photosynthetic capacity per area'' \\
  Amass & Photosynthetic rate per mass & ``photosynthetic rate per mass'' OR ``rate of CO2 assimilation per mass'' OR ``Amass'' OR ``Amax'' \\
  Hmax & Maximum height & ``potential height'' OR ``maximum height'' OR ``Hmax'' \\
  Ks & Stem specific conductance & ``Ks'' OR ``stem specific conductance'' OR ``stem hydraulic conductance'' OR ``sapwood conductance'' \\
  LA & Leaf lamina area & ``leaf length'' OR ``leaf lamina area'' OR ``leaf width'' OR ``leaf size'' \\
  LAR & Leaf area ratio & ``leaf area ratio'' \\
  LMR & Leaf mass ratio & ``leaf mass ratio'' OR ``leaf mass fraction'' \\
  NARarea & Net assimilation rate per area &  ``net assimilation rate per area'' OR ``rate of dry mass increament per area'' OR ``NARarea'' OR ``NAR'' \\
  Narea & Leaf nitrogen content per area & ``Narea'' OR ``nitrogen per area'' OR ``N/area'' OR ``leaf nitrogen content per area'' OR ``LNCarea'' OR ``leaf nitrogen content" \\
  Nmass & Leaf nitrogen content per mass & ``Nmass'' OR ``nitrogen per mass'' OR ``N/mass'' OR ``leaf nitrogen content per mass'' OR ``LNCmass'' OR ``leaf nitrogen content" \\
  Parea & Leaf phosphorus content per area & ``Parea'' OR ``leaf P'' OR  ``leaf phosphorus content per area''  OR ``leaf phosphorus content'' \\
  Pmass & Leaf phosphorus content per mass & ``Pmass'' OR ``leaf P'' OR  ``leaf phosphorus content per mass'' OR ``leaf phosphorus content'' \\
  SA/LA & Sapwood area per leaf area & ``sapwood area per leaf area'' OR ``huber value'' OR ``leaf area per sapwood area'' \\
  Seed mass & Seed mass & ``seed mass'' OR ``seed size'' OR ``seed volume'' \\
  SLA & Specific Leaf Area & ``leaf mass per area'' OR ``specific leaf area'' OR ``leaf construction cost'' \\
  Thickness & Leaf thickness & ``leaf thickness''  OR ``leaf tissue density'' \\
  Vessel density & Vessel density & ``vessel density'' OR ``stem conduit density'' \\
  Vessel size & Vessel area or diameter & ``conduit area'' OR ``stem conduit area'' OR ``vessel diameter'' OR ``vessel size'' OR ``conduit size''   \\
  WD & Wood density & ``wood density'' OR``WD'' OR ``wood specific gravity'' OR ``stem density'' OR ``stem specific density'' OR ``SSD'' \\
   \hline
\end{tabular}
}
\end{table}

### 2016-01-19 ms_snapshotinfo.tex
Done snapshot of the literature in appendix.

--- 2016-01-19 ms_snapshotinfo.Rnw
@@
-<<preload, echo=FALSE>>=
-library(knitr)
-opts_chunk$set(echo=FALSE)
-@
-
 We developed a snapshot of the literature, to assess the potential to recover useful data from the wide corpus of literature available by searching exclusively on SLA and WD.
@@
 Search terms were as follows: (``trait'' AND (``growth rate'' OR ``relative growth rate'')) AND (``tree*'' OR ``woody*''), where ``trait'' was allowed to be any of the trait names listed in Table \ref{tab:lit_search}.
-This snapshot indicated that \Sexpr{round(fun_snapshot(Snapshot)$main.traits ,0)}\% of the reported correlations linking growth to any of our five core traits would be recovered by searching only on SLA and WD.
-And it was \Sexpr{round(fun_snapshot(Snapshot)$all.traits ,0)}\% of the literature that would be captured by SLA and WD for the total 19 traits.
+This snapshot indicated that 84\% of the reported correlations linking growth to any of our five core traits would be recovered by searching only on SLA and WD.
+And it was 70\% of the literature that would be captured by SLA and WD for the total 19 traits.
 These results allow us to narrow our search considerably.

### 2016-01-19 R/data_processing.R

@@ -397,6 +397,6 @@ merge_bib_files <- function(meta, paper) {
   combined[[sort(names(combined))]]
 }
 
-snapshot_websci <- function(filename1 = "data/ref.traits/WebSci_all.csv"){
+snapshot_websci <- function(filename = "data/ref.traits/WebSci_all.csv"){
     Table <- read.csv(filename, sep = ";", dec = ",")
 }

### 2016-01-19 R/model.R

@@ -692,3 +692,19 @@ fun_year <- function(a) {
 }
 
 
+fun_snapshot <- function(Snapshot){
+  
+  Snapshot$ref <- with(Snapshot, paste(AU, TI,PY, sep = "_"))
+    nb_ref <- length(unique(Snapshot$ref))
+  
+  x_2 <- subset(Snapshot, Snapshot$trait %in% c("SLA", "WD"))
+   nb_ref_uniq_2  <- length(unique(x_2$ref))
+  
+  x_5 <- subset(Snapshot, Snapshot$trait %in% c("SLA", "WD", "Aarea", "Hmax", "Seedmass"))
+   nb_ref_uniq_5 <- length(unique(x_5$ref))
+ 
+  perc_19traits = (nb_ref_uniq_2/nb_ref) *100
+  perc_5traits = (nb_ref_uniq_2/nb_ref_uniq_5) *100
+  
+  list(main.traits =perc_5traits, all.traits =perc_19traits)
+  }

### 2016-01-19 analysis.R

@@ -38,6 +38,8 @@ GIrgr <- list_by_trait(IdealData_rgr)
 GIagr <- list_by_trait(IdealData_agr)
 GCrgr <- list_by_trait(CompleteData_rgr)
 GCagr <- list_by_trait(CompleteData_agr)
+Snapshot <- snapshot_websci("data/ref.traits/WebSci_all.csv")
+knitr::knit("ms_snapshotinfo.Rnw", "ms_snapshotinfo.tex")
 pdf("output/Fig1.pdf", height = 3L, width = 4L)
 figure_1(CleanData)
 dev.off()

### 2016-01-19 MS.tex
Minor edits for the abstract Update word count of abstract

@@
 \linenumbers
-\section{Summary 268/350}\label{abstract}
+\section{Summary 288/350}\label{abstract}
 \begin{enumerate}
@@
 We outline mechanisms and hypotheses based on new theory, and test these predictions in tree species using a meta-analysis of 103 studies ($>$ 500 correlations) for five traits (specific leaf area, wood density, maximum height, seed mass and maximum assimilation rate).
-To capture the effects of size, we tested for a shift in the direction of correlation between growth rates and traits across three plant stages: seedling, sapling and adult.
+To capture the effects of plant size, we tested for a shift in the direction of correlation between growth rates and traits across three ontogenic stages: seedling, sapling and adult.
 
-\item Results were consistent with predictions.
+\item Results were consistent with predictions, despite some limitations arising from unequal number of observations across stages.
 Specific leaf area was correlated with relative growth rate (RGR) in seedlings but not in adult plants.
-Correlations of RGR with wood density and assimilation rate were not affected by stage.
+Correlations of growth with wood density and assimilation rate were not affected by stage.
 Seed mass and maximum height were correlated with RGR only in one plant stage category: seedlings and adults, respectively.
-Despite a sizeable literature on traits and growth, coverage was still limited for wood density, seed mass, maximum height and assimilation rate.
-There is still scope for strengthening our understanding of correlations between traits and growth through adding further empirical studies for traits and size-classes underrepresented in the literature.
+Despite a sizeable literature on traits and growth, coverage was still limited for 4 of the 5 traits.
+Clearly, there is scope for strengthening our understanding on the link between traits and growth through adding further empirical studies for traits and size-classes underrepresented in the literature.
 

### 2016-01-20 MS.tex
Add paragraph on the extend of the knowledge gap (unbalanced observations across stages) in abstract, results and discussion

@@
 \textasteriskcentered Email for correspondence: \texttt{anais.gibert@gmail.com}\\
-Word count: ~5538 words (without supplementary material, Fig and ref)}
+Word count: ~8211 words /9600 (without supplementary material, Fig and ref)}
 \date{}
@@
 %   -- Figure 2: add * against traits used in meta-analysis
-%   -- check the appendix: in particular test of heterogeneity etc. need to re-run the analysis
-%   -- check the results and adequation with text of ms
 % - seach on XXX, footnote
@@
 \linenumbers
-\section{Summary 288/350}\label{abstract}
+\section{Summary 327/350}\label{abstract}
 \begin{enumerate}
@@
 \item We propose that traits should influence growth in a way that depends on the size of individual plants.
-We outline mechanisms and hypotheses based on new theory, and test these predictions in tree species using a meta-analysis of 103 studies ($>$ 500 correlations) for five traits (specific leaf area, wood density, maximum height, seed mass and maximum assimilation rate).
+We outline mechanisms and hypotheses based on new theoritical work, and test these predictions in tree species using a meta-analysis of 103 studies ($>$ 500 correlations) for five traits (specific leaf area, wood density, maximum height, seed mass and maximum assimilation rate).
+We also recorded data for a list of 14 others traits commonly used in the trait literature.
 To capture the effects of plant size, we tested for a shift in the direction of correlation between growth rates and traits across three ontogenic stages: seedling, sapling and adult.
 
-\item Results were consistent with predictions, despite some limitations arising from unequal number of observations across stages.
+% Recent theoretical work ? instead of new theory?
+
+\item Results were consistent with predictions, even with some limitations arising from unequal numbers of observation across stages.
 Specific leaf area was correlated with relative growth rate (RGR) in seedlings but not in adult plants.
@@
 Seed mass and maximum height were correlated with RGR only in one plant stage category: seedlings and adults, respectively.
-Despite a sizeable literature on traits and growth, coverage was still limited for 4 of the 5 traits.
+\item Despite a sizeable literature on traits and growth, major knowledge gaps across size-classes still exist; for one-third of traits a majority of correlations with growth reported in the literature ($>$ 75\%) come from a single and unique size-classe.
 Clearly, there is scope for strengthening our understanding on the link between traits and growth through adding further empirical studies for traits and size-classes underrepresented in the literature.
+
+% not sure to keep the end of this sentence
 
@@
 Our understanding of plant strategies should shift away from attributing species as having slow or fast growth throughout their life, in favour of attributing growth trajectories.
+
+%Clearly, there is scope for strengthening our understanding on the link between traits and growth through adding further empirical studies for traits and size-classes underrepresented in the literature.
 
@@
 Size has long been known to play a central role in organismal design and function \citep{Vogel:1988ux, Vogel:2003wb}, including that of trees \citep{Farnsworth:1995im, Givnish:1995ta}.
-Recent theory suggests that the absence of a correlation between SLA and growth at larger sizes may in fact be expected, when potential influences of traits on plant function are considered \citep{Falster:2011ii}.
 As plants grow larger, a greater amount of the energy is devoted towards building and maintaining non-photosynthetic tissues \citep{Givnish:1995ta}.
-A model by \citet{Falster:2011ii} suggests this change shifts the benefits and costs of some trait-based trade-offs, such that the net effect on the trait on growth changes with size.
+A recent model by \citet{Falster:2011ii} suggests this change shifts the benefits and costs of some trait-based trade-offs, such that the net effect of the trait on growth changes with size.
+Thus the absence of a correlation between SLA and growth at larger sizes may in fact be expected, when potential influences of traits on plant function are considered \citep{Falster:2011ii}.
 While recent empirical studies support the idea that the relationship between traits and growth rates may change with size (\citealt{Iida:2014ep, Iida:2014hq}), the trend and mechanisms behind this variation remain unclear.
@@
 We focused on tree and woody species since the mechanistic model used to assess our predictions is most applicable to these growth forms.
-We chose to assess hypotheses via meta-analysis because there already exist a considerable number of studies with salient information, allowing us to assess our hypotheses across a much broader number of species and vegetation types than would have been possible in an experiential study.
+We chose to assess our hypotheses via a meta-analysis because there already exist a considerable number of studies with salient information, allowing us to assess our hypotheses across a much broader number of species and vegetation types than would have been possible in an experiential study.
 While, we anticipated a reasonably-sizeable literature on trait and growth to be available, we were uncertain about the representation of all trait-stages combinations.
-An additional goal of our study was therefore to identify gaps in knowledge, needed to improve our understanding of the link between trait and growth.
+An additional goal of our study was therefore to identify gaps in the knowledge needed to improve our understanding of the link between trait and growth.
 
@@
 
-Below we first outline equations for the new growth model, adapted \citet{Falster:2011ii}.
+Below we first outline equations for the new growth model, adapted from \citet{Falster:2011ii}.
 We then use this model to generate qualitative predictions on how the effect of traits on growth rate changes with plant size.
@@
 
-\subsection*{Tests for bias in sampling}
+In total, correlations had been reported for at least two different stages across 18 traits out of the 19 targeted (Fig.
+\ref{fig:fig1}).
+We had thought it likely that for some traits correlations would be reported only for one size class.
+But this limitation applied only for LAR and NARmass, where studies appeared confined to seedling stages.
+However, for a majority of traits the number of observations across stage was higthly unbalanced; for one-third of the 19 traits $>$ 75\% of correlations with growth reported come from a single and unique plant stage (Fig.
+\ref{fig:fig1}).
+
+\subsection*{Coverage of the data and assessment of publication bias}
 
@@
 
-In total, 103 articles published between 1983 and 2014, and containing 551 correlations linking growth rate to any of the 19 traits across a range of plant stages were identified (Fig.
-\ref{fig:fig1}).
+In total, 103 articles published between 1983 and 2014, and containing 551 correlations linking growth rate to any of the 19 traits across a range of plant stages were identified.
+Data reported here were variable in multiple ways.
 Climate zones spanned from temperate regions to tropics (map in Fig.
@@
 TODO: XXXX Something about limited amount of data
+Despite a sizeable literature on traits and growth, there are major knowledge gaps on the link between trait and growth.
+The number of correlations reported for each 19 traits is generally unbalanced in favor of a particular stage, for historical or practical reasons.
+This means that the knowledge we have on this trait is often biased toward a particular size-classe.
+Additional data are specifically required in small plants (seedling and sapling) for WD and Hmax, and in large plants (adult and sapling) for Aarea and more broadly for all traits requiring a measure of whole plant biomass (e.g.
+LMR, LAR).
+
 TODO: XXX some thing about qualitative predictions \ref{Falster-2016}
@@
 Clearly there is much scope for strengthening our understanding of correlations between traits and growth through (1) adding further empirical studies for traits and size-classes with weaker representation, (2) accounting more satisfactorily for variables such as light, and (3) expressing plant sizes on continuous scales of mass or height rather than through the approximate and partly subjective categories unavoidably adopted here.
-Additional data are specifically required in small plants (seedling and sapling) for WD and Hmax, and in large plants (adult and sapling) for Aarea and more broadly for all traits requiring a measure of whole plant biomass (e.g.
-LMR, LAR, NAR).
 However, the existing published evidence is consistent with qualitative predictions of a simple model that assesses the effects of plant size on growth.

### 2016-01-20 R/model.R

@@ -707,4 +707,15 @@ fun_snapshot <- function(Snapshot){
   perc_5traits = (nb_ref_uniq_2/nb_ref_uniq_5) *100
   
   list(main.traits =perc_5traits, all.traits =perc_19traits)
-  }
+}
+
+
+fun_gap <- function(CleanData){
+  library(plyr)
+  
+  table <- ddply(CleanData, c("trait", "stage"), function(x) length(x$corr.r))
+  table2 <- ddply(table, c("trait"), function(x) max(x$V1)/ sum(x$V1))
+  
+  table3 <- subset(table2, table2$V1 > 0.75)
+  length(table3$V1)
+} 

### 2016-01-20 MS.tex
Small editing in abstract Add comments in footnotes for theoritical expectation Small rewriting of results (add results for SLA RGR vs AGR in mass) Rewriting of "measurements under 'ideal' conditions Move paragraph about stage representativity among traits as a new subsection in results

@@
 %   -- major revision of code -- > lots of repetition, hard to follow
-%   -- Figure 2: add * against traits used in meta-analysis
+%   -- Figure 2: add * against traits used in meta-analysis: no
 % - seach on XXX, footnote
@@
 We outline mechanisms and hypotheses based on new theoritical work, and test these predictions in tree species using a meta-analysis of 103 studies ($>$ 500 correlations) for five traits (specific leaf area, wood density, maximum height, seed mass and maximum assimilation rate).
-We also recorded data for a list of 14 others traits commonly used in the trait literature.
+We also recorded data for 14 others traits commonly used in the trait literature.
 To capture the effects of plant size, we tested for a shift in the direction of correlation between growth rates and traits across three ontogenic stages: seedling, sapling and adult.
@@
 Seed mass and maximum height were correlated with RGR only in one plant stage category: seedlings and adults, respectively.
-\item Despite a sizeable literature on traits and growth, major knowledge gaps across size-classes still exist; for one-third of traits a majority of correlations with growth reported in the literature ($>$ 75\%) come from a single and unique size-classe.
+\item Despite a sizeable literature on traits and growth, major knowledge gaps across size-classes still exist; for one-third of traits the majority of correlations with growth ($>$ 75\%) come from a single and unique size-classe.
 Clearly, there is scope for strengthening our understanding on the link between traits and growth through adding further empirical studies for traits and size-classes underrepresented in the literature.
@@
 With only XXX exception, the predicted effects of the trait are also similar when growth is expressed on relative of absolute terms, and as diameter, height or mass growth (Table \ref{tab:trade-offs} (TRUE XXXX?).
+
 \footnote{The correlation with RGR$_{\rm mass}$ is negative but becomes positive with AGR$_{\rm mass}$.
@@
 So we adopted a two steps approach, first we were conservative by focusing exclusively on RGR, then we compared results with those of a more inclusive dataset with both RGR and AGR.}
+\footnote{We have different expectation for SLA in AGRmass for seedling: but none of our data are in AGRmass, they are mainly in RGRmass (Fig.
+\ref{fig:figA8}).
+Why a change with WD when it is measured in mass?
+All WD seedling are measured in RGRmass, and there are some mass data for both other stages too.
+}
 
@@
 
-We aimed to identify studies reporting a correlation across species, between functional traits and growth rate (e.g.
-relative or absolute growth, in diameter, height or mass, see Table \ref{tab:trade-offs}.
+We aimed to identify studies reporting a correlation across species, between traits and growth rate (e.g.
+relative or absolute growth, in diameter, height or mass, see Table \ref{tab:trade-offs}).
 Systematic searches were conducted across the two most comprehensive bibliographic platforms: Google scholar and Web of Science (Thomson Reuters).
@@
 
-\subsubsection*{Measurements under ideal conditions}\label{ideal-vs-entire-dataset}
+\subsubsection*{Measurements under 'ideal' conditions}\label{ideal-vs-entire-dataset}
 
-The entire dataset included studies differing in the growth measurement used (RGR or AGR), the number of species, the experimental conditions (stressed vs unstressed), and the concordance between stage used to measure trait and growth rate.
-The main results reported here were obtained with an ``ideal'' subset of data.
-This ``ideal'' subset, included only studies recording RGR across \underline{\textgreater} 10 species, under unstressed conditions, and where growth rates and traits were measured on plants from the same stage (expect for Hmax and seed mass, where a particular stage is by definition required to measure the trait).
-These were then compare against results obtained with the entire dataset (including all noted correlations).
+The entire dataset included studies differing in the growth measurement used (RGR or AGR), the number of species, the experimental conditions (stressed vs unstressed), and the concordance between stages used to measure trait and growth rate.
+However RGR and AGR are fundamentally different for a lot of ecologists.
+And the number of species used to perform the correlation, the experimental conditions, and the concordance between stages used to measure trait and growth are clear criteria for assessing the quality of the data for addressing our hypotheses.
+So we adopted a two steps approach, first we were conservative by focusing exclusively on RGR, across \underline{\textgreater} 10 species, under unstressed conditions, and where the source of the trait and growth is the same (expect for Hmax and seed mass, where a particular stage is by definition required to measure the trait).
+This dataset is called the "ideal" dataset.
+Then we compared results with those of a more inclusive dataset - the entire dataset- with both RGR and AGR, and all others criteria relaxed.
 
@@
 
-\subsection*{Main effects}
+\subsection*{Main effects under 'ideal' conditions}
 
@@
 
-We now report results from the entire dataset, to determine if additional data would alter or reinforce our conclusions, drawn sometimes with limited replicates.
+We now report results from the entire dataset to determine if additional data would alter or reinforce our conclusions, drawn sometimes with limited replicates.
 This entire dataset included correlations measured with both AGR and RGR (Fig.
@@
 from 25 to 59 correlation coefficients reported for SLA at seedling stage), while others still had few replicates.
-On the 13 traits-stage combinations studied in total, six had $\le$ five correlation coefficients: (i.e.
-WD-seedling, Hmax-sapling, Hmax-seedling, Seed mass-sapling, Aarea-adult and Aarea-sapling.
+On the 13 traits-stage combinations studied in total, six had $\le$ five correlation coefficients: WD-seedling, Hmax-sapling, Hmax-seedling, Seed mass-sapling, Aarea-adult and Aarea-sapling.
 
@@
 
-We had no hypotheses about a change in the correlation between trait and growth as AGR was used instead of RGR, except for seed mass.
+We had hypotheses for seed mass and SLA, about a change in the correlation between trait and growth as AGR was used instead of RGR, or as mass was used instead of dimater and height.
 For seed mass, effects size differed significantly between RGR and AGR at seedling stage; as expected the correlation with RGR was positive and shifted to non significant with AGR (Fig \ref{fig:fig4}d; CI not overlapping).
+For SLA, the correlation was expected to shift from positive to non significant if AGRmass was used instead of RGRmass for seedling stage; here none of the data have been measured with AGRmass at seedling stage (Fig.
+\ref{fig:figA8}).
+% Why a change with WD when it is measured in mass? All WD seedling are measured in RGRmass, and there are some mass data for both other stages too.  
 For other traits, effect size were generally consistent between RGR and AGR when both measurement were available.
@@
 The correlation coefficients recorded for AGR came from \citet{Augspurger:1984ct} and unlike others they used wood density values from adult plants together with growth from juveniles.
-
-In total, correlations had been reported for at least two different stages across 18 traits out of the 19 targeted (Fig.
-\ref{fig:fig1}).
-We had thought it likely that for some traits correlations would be reported only for one size class.
-But this limitation applied only for LAR and NARmass, where studies appeared confined to seedling stages.
-However, for a majority of traits the number of observations across stage was higthly unbalanced; for one-third of the 19 traits $>$ 75\% of correlations with growth reported come from a single and unique plant stage (Fig.
-\ref{fig:fig1}).
 
@@
 
+\subsection*{Size-classes representativity among 19 traits recorded}
+In total, correlations had been reported for at least two different stages across 18 traits out of the 19 targeted (Fig.
+\ref{fig:fig1}).
+We had thought it likely that for some traits correlations would be reported only for one size class.
+But this limitation applied only for LAR and NARmass, where studies appeared confined to seedling stages.
+However, for a majority of traits the number of observations across stage was higthly unbalanced; for one-third of the 19 traits $>$ 75\% of correlations with growth reported come from a single and unique plant stage (Fig.
+\ref{fig:fig1}).
+
 \section*{Discussion}\label{discussion}
@@
 
-TODO: XXXX Something about limited amount of data
+TODO: XXXX Something about limited amount of data (add the following arguments:)
 Despite a sizeable literature on traits and growth, there are major knowledge gaps on the link between trait and growth.
-The number of correlations reported for each 19 traits is generally unbalanced in favor of a particular stage, for historical or practical reasons.
-This means that the knowledge we have on this trait is often biased toward a particular size-classe.
+The number of correlations reported for each 19 traits is generally unbalanced in favor of a particular stage, either for historical or practical reasons.
+This means that the knowledge we have on each trait is often biased toward a particular size-classe.
 Additional data are specifically required in small plants (seedling and sapling) for WD and Hmax, and in large plants (adult and sapling) for Aarea and more broadly for all traits requiring a measure of whole plant biomass (e.g.

### 2016-01-21 MS.tex
Small editing in ms

@@
 Seed mass and maximum height were correlated with RGR only in one plant stage category: seedlings and adults, respectively.
-\item Despite a sizeable literature on traits and growth, major knowledge gaps across size-classes still exist; for one-third of traits the majority of correlations with growth ($>$ 75\%) come from a single and unique size-classe.
-Clearly, there is scope for strengthening our understanding on the link between traits and growth through adding further empirical studies for traits and size-classes underrepresented in the literature.
+\item Despite a sizeable literature on traits and growth, major knowledge gaps across size still exist; for one-third of traits the majority ($>$ 75\%) of correlations with growth come from a single stage.
+Clearly, there is scope for strengthening our understanding on the link between traits and growth through adding further empirical studies for traits and size classes underrepresented in the literature.
 
@@
 We focused on tree and woody species since the mechanistic model used to assess our predictions is most applicable to these growth forms.
-We chose to assess our hypotheses via a meta-analysis because there already exist a considerable number of studies with salient information, allowing us to assess our hypotheses across a much broader number of species and vegetation types than would have been possible in an experiential study.
+We chose to assess our hypotheses via a meta-analysis because there already exist a considerable number of studies with salient information.
+Using these studies, we were able to assess our hypotheses across a much broader number of species and vegetation types than would have been possible in an experiential study.
 While, we anticipated a reasonably-sizeable literature on trait and growth to be available, we were uncertain about the representation of all trait-stages combinations.
@@
 
-The rate at which \textbf{live biomass} $B$ is produced by a plant is given by:
+The rate at which \textbf{live biomass} $B$ is produced by a plant is given by
 \begin{equation}\label{eq:eq0}
-\underbrace{\frac{\ud B}{\ud t}}_{\text{net live biomass production}} = \underbrace{\alpha_{\rm y}}_{\text{yield}}  \big(\underbrace{A_{\rm l} p}_{\text{photosynthesis}} - \underbrace{\sum_{i = {\rm l,s,r}} M_{i} r_{i}}_{\text{respiration}}\big) - \underbrace{ \sum_{i = \rm{l,s,r}} M_{i} k_{i}}_{\text{turnover}},
+\underbrace{\frac{\ud B}{\ud t}}_{\text{net live biomass production}} = \underbrace{\alpha_{\rm y}}_{\text{yield}}  \big(\underbrace{A_{\rm l} p}_{\text{photosynthesis}} - \underbrace{\sum_{i = {\rm l,s,r}} M_{i} r_{i}}_{\text{respiration}}\big) - \underbrace{ \sum_{i = \rm{l,s,r}} M_{i} k_{i}}_{\text{turnover}} \, ,
 \end{equation}
@@
 \end{equation}
-The first term on the right of eq \ref{eq:eq2},
-$\ud H / \ud A_{\rm l}$, is the growth in plant height
+where $\ud H / \ud A_{\rm l}$, is the growth in plant height
 per unit growth in total leaf area -- accounting for the architectural
@@
 These two effects occur within the terms  $\frac{\ud B}{\ud t}$ and $\frac{\ud A_{\rm l}}{\ud M_{\rm t}}$ in the above model.
-Whether plant growth rate increases with SLA depends on the how the relative magnitude of the benefit (cheap leaf construction, via $\frac{\ud A_{\rm l}}{\ud M_{\rm t}}$ ) and cost (higher leaf turnover, via $\frac{\ud B}{\ud t}$) of increased SLA also change with size (Table \ref{tab:trade-offs}).
+Whether plant growth rate increases with SLA depends on how the relative magnitude of the benefit (cheap leaf construction, via $\frac{\ud A_{\rm l}}{\ud M_{\rm t}}$ ) and cost (higher leaf turnover, via $\frac{\ud B}{\ud t}$) of increased SLA change with size (Table \ref{tab:trade-offs}).
 During early life, when leaf comprises a large part of the plant, decreasing SLA has an overwhelmingly positive effect on height and diameter growth rate, because the effect of reducing $\frac{\ud M_{\rm l}}{\ud A_{\rm l}}$ has a large effect compared to the other terms in eq.
 \ref{eq:daldmt}.
+For mass growth, cheaper leaf construction (high SLA) translates directly into faster relative growth rate in seedlings (See Appendix XXX eq.
+\ref{eq:eq1_seedlings_RGR}).
 As plants increase in size, however, the cost of building sapwood ($\frac{\ud M_{\rm s}}{\ud A_{\rm l}}$) increases disproportionately, decreasing the benefit of cheaper leaf construction in eq.
@@
 
-Among seedlings, growth is often measured in units of plant mass, rather than stem or diameter.
-For mass growth in seedlings, cheaper leaf construction (high SLA)  translates directly into faster relative growth rate (See Appendix XXX eq.
-\ref{eq:eq1_seedlings_RGR}).
-
 \subsection*{H2: The relationship between WD and growth rate is expected to be negative across all plant sizes}
-
-High WD increases the cost of building stem tissue and thus the cost of deploying additional leaf area (Table \ref{tab:trade-offs}), which should slow growth.
-This effects occur within the term $\frac{\ud A_{\rm l}}{\ud M_{\rm t}}$ in the above model.
-Although expensive wood decreases the risk of mortality, this benefit is not reflected in growth outcomes.
-Thus increasing WD is predicted to decrease growth across the entire size range.
 
@@
 Under this scenario, wood density is negatively correlated to growth rate across all plant stages.
-Because the relative expenditure on stem compared to leaf is increases as plants grow larger, the relationship between WD and growth may also strengthen in larger plants.
+Because the relative expenditure on stem compared to leaf increases as plants grow larger, the relationship between WD and growth may also strengthen in larger plants.
 
@@
 As plants approach maximum height they increasingly divert energy away from growth and into reproduction (see \citealt{Thomas:1996do,Thomas-2011, Wenk:2015jz}).
-This effect occurs in the term $\frac{\ud M_{\rm t}}{\ud B}$ in the above model.
+This effect occurs in the term $\frac{\ud M_{\rm t}}{\ud B}$ in the above model eqs.
+(\ref{eq:eq2}-\ref{eq:eq5}).
 For seedlings, where all individuals are investing solely in growth, we expect no influence of Hmax on growth (i.e.
@@
 The main effect of increased seed size is to produce a larger overall seedling.
-Under similar light conditions, RGR decreases with size because the ratio of leaf area to total biomass decreases with increasing plant size.
+Under similar light conditions, RGR decreases with size because the ratio of leaf area to total biomass decreases along plant size.
 Thus, larger seedlings are predicted to have a lower RGR during the earliest phases of growth \citep{Turnbull:2012ew}.
-However, among larger plants we expect the effect of this initial size to be minimal, and thus the correlation between seed size and growth rate should disappear.
-The ${\rm RGR}_{{\rm mass}}$ slows as plants grow larger, and large-seeded species begin larger as seedlings.
-For larger plants, seed mass is not expected to have any distinct influence on growth rates  (Table \ref{tab:trade-offs}).
+However, as plants are growing we expect the effect of this initial size to be minimal, and the correlation between seed size and growth rate should disappear.
+Thus for larger plants, seed mass is not expected to have any distinct influence on growth rates  (Table \ref{tab:trade-offs}).
 However, the predicted relationship between growth and seed mass in seedlings reverses if AGR$_{\rm mass}$ is used instead of RGR$_{\rm mass}$.
@@
 
-\subsection*{Size-classes representativity among 19 traits recorded}
+\subsection*{Representation of stages among 19 traits}
 In total, correlations had been reported for at least two different stages across 18 traits out of the 19 targeted (Fig.
@@
 But this limitation applied only for LAR and NARmass, where studies appeared confined to seedling stages.
-However, for a majority of traits the number of observations across stage was higthly unbalanced; for one-third of the 19 traits $>$ 75\% of correlations with growth reported come from a single and unique plant stage (Fig.
+However, for a majority of traits the number of observations across stage was higthly unbalanced; for one-third of the 19 traits $>$ 75\% of correlations with growth reported come from a single stage (Fig.
 \ref{fig:fig1}).
@@
 This means that the knowledge we have on each trait is often biased toward a particular size-classe.
-Additional data are specifically required in small plants (seedling and sapling) for WD and Hmax, and in large plants (adult and sapling) for Aarea and more broadly for all traits requiring a measure of whole plant biomass (e.g.
-LMR, LAR).
 
@@
 Clearly there is much scope for strengthening our understanding of correlations between traits and growth through (1) adding further empirical studies for traits and size-classes with weaker representation, (2) accounting more satisfactorily for variables such as light, and (3) expressing plant sizes on continuous scales of mass or height rather than through the approximate and partly subjective categories unavoidably adopted here.
+Additional data are specifically required in small plants (seedling and sapling) for WD and Hmax, and in large plants (adult and sapling) for Aarea and more broadly for all traits requiring a measure of whole plant biomass (e.g.
+LMR, LAR).
 However, the existing published evidence is consistent with qualitative predictions of a simple model that assesses the effects of plant size on growth.

### 2016-01-22 MS.tex
Add section for table in Appendix Reorder Fig Appendix to match the ms Add section in Appendix with direction to "read.bib" file in github

@@
 However RGR and AGR are fundamentally different for a lot of ecologists.
-So we adopted a two steps approach, first we were conservative by focusing exclusively on RGR, then we compared results with those of a more inclusive dataset with both RGR and AGR.}
-\footnote{We have different expectation for SLA in AGRmass for seedling: but none of our data are in AGRmass, they are mainly in RGRmass (Fig.
+So we adopted a two steps approach, first we were conservative by focusing exclusively on RGR, then we compared results with those of a more inclusive dataset with both RGR and AGR.
+=> We have different expectation for SLA in AGRmass for seedling: but none of our data are in AGRmass, they are mainly in RGRmass (Fig.
 \ref{fig:figA8}).
@@
 \ref{eq:daldmt}.
-For mass growth, cheaper leaf construction (high SLA) translates directly into faster relative growth rate in seedlings (See Appendix XXX eq.
+For mass growth, cheaper leaf construction (high SLA) translates directly into faster relative growth rate in seedlings (See Appendix \ref{app:growth-equation} eq.
 \ref{eq:eq1_seedlings_RGR}).
@@
 This effect occurs in the term $\frac{\ud M_{\rm t}}{\ud B}$ in the above model eqs.
-(\ref{eq:eq2}-\ref{eq:eq5}).
+(\ref{eq:eq2}-\ref{eq:eq4}).
 For seedlings, where all individuals are investing solely in growth, we expect no influence of Hmax on growth (i.e.
@@
 It might greatly depend on the level of light available.
+
+\clearpage
 
@@
 
-In total we inspected the full text of 583 articles (see Appendix XXXX in Supplementary material for list).
+In total we inspected the full text of 583 articles (see Appendix \ref{app:literature-list} for list).
 Individual studies had to report the following information to be included in our dataset: i) the relationship between growth and trait as a correlation coefficient, ii) the sample size and the number of species used to perform the correlation, and iii) the size or stage of plants.
@@
 
+\clearpage
+
 \section*{Results}\label{results}
@@
 % nrow(x)
+\subsection*{Representation of stages among 19 traits}
+In total, correlations had been reported for at least two different stages across 18 traits out of the 19 targeted (Fig.
+\ref{fig:fig1}).
+We had thought it likely that for some traits correlations would be reported only for one size class.
+But this limitation applied only for LAR and NARmass, where studies appeared confined to seedling stages.
+However, for a majority of traits the number of observations across stage was higthly unbalanced; for one-third of the 19 traits $>$ 75\% of correlations with growth reported come from a single stage (Fig.
+\ref{fig:fig1}).
 
@@
 \ref{fig:fig3}a; average values for the coefficients ($\bar{r}$) in Fig.
-\ref{fig:figA4}a-e).
+\ref{fig:figA4}).
 
@@
 Overall our study met quality criteria expected for meta-analysis in ecology (Table \ref{tab:meta}).
-The impact of publication bias was seemingly trivial (Appendix E, Fig.
+The impact of publication bias was seemingly trivial (See Appendix \ref{app:growth-equation}, Fig.
 \ref{fig:figA7}).
-The extent of heterogeneity was high, but was substantially explained by our core hypothesis of a plant stage effect for SLA and seed mass (Appendix E).
-There was no indication of a temporal change in the effect size being reported within stages (Appendix E, Fig.
+The extent of heterogeneity was high, but was substantially explained by our core hypothesis of a plant stage effect for SLA and seed mass (Appendix \ref{app:supp_info_analyses}).
+There was no indication of a temporal change in the effect size being reported within stages (Appendix \ref{app:supp_info_analyses}, Fig.
 \ref{fig:figA9}).
@@
 \ref{fig:figA5}).
-
-\subsection*{Representation of stages among 19 traits}
-In total, correlations had been reported for at least two different stages across 18 traits out of the 19 targeted (Fig.
-\ref{fig:fig1}).
-We had thought it likely that for some traits correlations would be reported only for one size class.
-But this limitation applied only for LAR and NARmass, where studies appeared confined to seedling stages.
-However, for a majority of traits the number of observations across stage was higthly unbalanced; for one-third of the 19 traits $>$ 75\% of correlations with growth reported come from a single stage (Fig.
-\ref{fig:fig1}).
 
@@
   2.& Reporting inclusion or exclusion criteria & yes & Inclusion criteria are specified in the ``Material and Methods''.
-A full list of all articles evaluated is available in the Appendix \ref{app:literature-snapshot}.\\
+A full list of all articles evaluated is available in the Appendix \ref{app:literature-list}.\\
   3.& Weighting effect sizes by study precision & yes & Effects sizes were weighted by number of species. See	``Material and Methods'' for details.\\
@@
 \clearpage
-
-\clearpage
 \section{Supporting figures}\label{app:supp_info_figures}
@@
 \label{fig:figA1}
+\end{figure}
+
+\begin{figure}[h!]
+\centering
+\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA6a.pdf}
+\end{figure}
+
+\begin{figure}[h!]
+\centering
+\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA6b.pdf}
+\end{figure}
+
+\begin{figure}[h!]
+\centering
+\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA6c.pdf}
+\caption{Effects size on the correlation between growth and traits of plant stage (mod1), growth measurement (mod2), vegetation type (mod3), and experiment type (mod4).
+a) Specific leaf area (SLA), b) Wood density (WD),c) Assimilation rate of CO2 (Aarea), d) Seed mass, and e) Asymptotic maximum height (Hmax).
+The effect size (z + 95\%CI) is reported for each class, and models are fitted by restricted max likelihood (REML).
+Abbreviation: GR = growth rate and RGR = relative growth rate, measured in diameter (D), height (H), mass(M), cross section area (CSA) and volume (V), across GF: coefficient of correlation measured on tree in mixture with other growth form.
+AIC: Akaike information criterion corresponds to the quality of each model, and allow a comparison between models.
+Smallest is the AIC better is the model.
+Results shown here are from ``ideal'' subset of data (for details see ``Material and Methods'').
+``n'' indicates number of correlation r reported.}
+\label{fig:figA6}
+\end{figure}
+
+\begin{figure}[h!]
+\centering
+\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA4.pdf}
+\caption{Mean coefficient correlation r (+SD) between growth and traits measured by stage.
+a) Specific leaf area (SLA), b) Wood density (WD), c) Asymptotic maximum height (Hmax), d) Seed mass (Seedmass) and e) Rate of CO2 assimilation (Aarea).
+The mean coefficients are weighted by sample size and established from 103 articles.
+Results shown here are from the ''ideal'' subset of data (for details see ``Material and Methods''), ``n'' indicates the number of correlations.}
+\label{fig:figA4}
+\end{figure}
+
+\begin{figure}[h!]
+\centering
+\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA8.pdf}
+\caption{Number of correlation extracted by traits, stage, and growth type (absolute vs relative, and measurement).
+a) Specific leaf area (SLA), b) Wood density (WD), c) Asymptotic maximum height (Hmax), d) Seed mass and e) Assimilation rate of CO2 (Aarea).
+Absolute growth rate (AGR) is on the left and relative growth rate (RGR) on the right of each plot.
+Results shown here are from the "ideal" subset of the data (for details see ``Material and Methods'').
+}
+\label{fig:figA8}
 \end{figure}
@@
 \centering
-\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA4.pdf}
-\caption{Mean coefficient correlation r (+SD) between growth and traits measured by stage.
-a) Specific leaf area (SLA), b) Wood density (WD), c) Asymptotic maximum height (Hmax), d) Seed mass (Seedmass) and e) Rate of CO2 assimilation (Aarea).
-The mean coefficients are weighted by sample size and established from 103 articles.
-Results shown here are from the ''ideal'' subset of data (for details see ``Material and Methods''), ``n'' indicates the number of correlations.}
-\label{fig:figA4}
-\end{figure}
-
-\begin{figure}[h!]
-\centering
-\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA5.pdf}
-\caption{Effect size ($\pm$95\% confidence intervals, CI) of plant stage on the correlations between growth rate and five functional traits across species, with a data set averaging multiple comparisons by trait and by study.
-In the case of multiple comparisons within a study, effect sizes were calculated using the mean correlation coefficient by trait and by study.
-a) Specific leaf area (SLA), b) Wood density (WD), c) Asymptotic maximum height (Hmax) , d) Seed mass and e) Assimilation rate of CO2 (Aarea).
-Effect size is a standardized measure of the magnitude of the relationship between a particular stage and the correlation coefficient z (Fisher's z-transformed).
-Effects are significant if CIs do not overlap with zero.
-LRT: likelihood Ratio Test compared the fit between null model and stage model, both models are fitted by Maximum Likelihood.
-Black point: ideal data , grey points: all the data (for details see ``Material and Methods'').
-``n'' indicates the number of independent comparisons for each effect.}
-\label{fig:figA5}
-\end{figure}
-
-\begin{figure}[h!]
-\centering
-\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA6a.pdf}
-\end{figure}
-
-\begin{figure}[h!]
-\centering
-\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA6b.pdf}
-\end{figure}
-
-\begin{figure}[h!]
-\centering
-\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA6c.pdf}
-\caption{Effects size on the correlation between growth and traits of plant stage (mod1), growth measurement (mod2), vegetation type (mod3), and experiment type (mod4).
-a) Specific leaf area (SLA), b) Wood density (WD),c) Assimilation rate of CO2 (Aarea), d) Seed mass, and e) Asymptotic maximum height (Hmax).
-The effect size (z + 95\%CI) is reported for each class, and models are fitted by restricted max likelihood (REML).
-Abbreviation: GR = growth rate and RGR = relative growth rate, measured in diameter (D), height (H), mass(M), cross section area (CSA) and volume (V), across GF: coefficient of correlation measured on tree in mixture with other growth form.
-AIC: Akaike information criterion corresponds to the quality of each model, and allow a comparison between models.
-Smallest is the AIC better is the model.
-Results shown here are from ``ideal'' subset of data (for details see ``Material and Methods'').
-``n'' indicates number of correlation r reported.}
-\label{fig:figA6}
-\end{figure}
-
-\begin{figure}[h!]
-\centering
-\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA8.pdf}
-\caption{Number of correlation extracted by traits, stage, and growth type (absolute vs relative, and measurement).
-a) Specific leaf area (SLA), b) Wood density (WD), c) Asymptotic maximum height (Hmax), d) Seed mass and e) Assimilation rate of CO2 (Aarea).
-Absolute growth rate (AGR) is on the left and relative growth rate (RGR) on the right of each plot.
-Results shown here are from the "ideal" subset of the data (for details see ``Material and Methods'').
-}
-\label{fig:figA8}
-\end{figure}
-
-\begin{figure}[h!]
-\centering
 \includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA7.pdf}
@@
 
-\clearpage
-\section{Supporting Analyses}\label{app:supp_info_analyses}
-
-\subsection{Literature coverage by trait}\label{app:literature-snapshot}
-
-\input{ms_snapshotinfo}
+\begin{figure}[h!]
+\centering
+\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA5.pdf}
+\caption{Effect size ($\pm$95\% confidence intervals, CI) of plant stage on the correlations between growth rate and five functional traits across species, with a data set averaging multiple comparisons by trait and by study.
+In the case of multiple comparisons within a study, effect sizes were calculated using the mean correlation coefficient by trait and by study.
+a) Specific leaf area (SLA), b) Wood density (WD), c) Asymptotic maximum height (Hmax) , d) Seed mass and e) Assimilation rate of CO2 (Aarea).
+Effect size is a standardized measure of the magnitude of the relationship between a particular stage and the correlation coefficient z (Fisher's z-transformed).
+Effects are significant if CIs do not overlap with zero.
+LRT: likelihood Ratio Test compared the fit between null model and stage model, both models are fitted by Maximum Likelihood.
+Black point: ideal data , grey points: all the data (for details see ``Material and Methods'').
+``n'' indicates the number of independent comparisons for each effect.}
+\label{fig:figA5}
+\end{figure}
 
@@
 
-\subsection{Simplified growth equations for seedlings of similar size}
+\section{Supporting Tables}\label{app:supp_info_table}
+
+\linespread{1}
+
+\begin{table}[h!]
+\centering
+\caption{List of the nineteen traits targeted. Abbreviation,
+definition and search term used in the meta-analysis}
+\label{tab:lit_search}
+\vspace{0.5cm}
+{\footnotesize
+\begin{tabular}{p{3cm}p{3cm}p{8cm}}
+  \hline
+Trait & Definition & Search terms \\
+  \hline
+Aarea & Photosynthetic rate per area & ``photosynthetic rate per area'' OR ``rate of CO2 assimilation per area'' OR ``Aarea'' OR ``Amax'' OR ``photosynthetic capacity per area'' \\
+  Amass & Photosynthetic rate per mass & ``photosynthetic rate per mass'' OR ``rate of CO2 assimilation per mass'' OR ``Amass'' OR ``Amax'' \\
+  Hmax & Maximum height & ``potential height'' OR ``maximum height'' OR ``Hmax'' \\
+  Ks & Stem specific conductance & ``Ks'' OR ``stem specific conductance'' OR ``stem hydraulic conductance'' OR ``sapwood conductance'' \\
+  LA & Leaf lamina area & ``leaf length'' OR ``leaf lamina area'' OR ``leaf width'' OR ``leaf size'' \\
+  LAR & Leaf area ratio & ``leaf area ratio'' \\
+  LMR & Leaf mass ratio & ``leaf mass ratio'' OR ``leaf mass fraction'' \\
+  NARarea & Net assimilation rate per area &  ``net assimilation rate per area'' OR ``rate of dry mass increament per area'' OR ``NARarea'' OR ``NAR'' \\
+  Narea & Leaf nitrogen content per area & ``Narea'' OR ``nitrogen per area'' OR ``N/area'' OR ``leaf nitrogen content per area'' OR ``LNCarea'' OR ``leaf nitrogen content" \\
+  Nmass & Leaf nitrogen content per mass & ``Nmass'' OR ``nitrogen per mass'' OR ``N/mass'' OR ``leaf nitrogen content per mass'' OR ``LNCmass'' OR ``leaf nitrogen content" \\
+  Parea & Leaf phosphorus content per area & ``Parea'' OR ``leaf P'' OR  ``leaf phosphorus content per area''  OR ``leaf phosphorus content'' \\
+  Pmass & Leaf phosphorus content per mass & ``Pmass'' OR ``leaf P'' OR  ``leaf phosphorus content per mass'' OR ``leaf phosphorus content'' \\
+  SA/LA & Sapwood area per leaf area & ``sapwood area per leaf area'' OR ``huber value'' OR ``leaf area per sapwood area'' \\
+  Seed mass & Seed mass & ``seed mass'' OR ``seed size'' OR ``seed volume'' \\
+  SLA & Specific Leaf Area & ``leaf mass per area'' OR ``specific leaf area'' OR ``leaf construction cost'' \\
+  Thickness & Leaf thickness & ``leaf thickness''  OR ``leaf tissue density'' \\
+  Vessel density & Vessel density & ``vessel density'' OR ``stem conduit density'' \\
+  Vessel size & Vessel area or diameter & ``conduit area'' OR ``stem conduit area'' OR ``vessel diameter'' OR ``vessel size'' OR ``conduit size''   \\
+  WD & Wood density & ``wood density'' OR``WD'' OR ``wood specific gravity'' OR ``stem density'' OR ``stem specific density'' OR ``SSD'' \\
+   \hline
+\end{tabular}
+}
+\end{table}
+
+\clearpage
+
+\section{Supporting Analyses}\label{app:supp_info_analyses}
+
+\subsection{Simplified growth equations for seedlings of similar size}\label{app:growth-equation}
 
@@
 
-\subsection{Quantifying and exploring the cause of heterogeneity in effect sizes}
+\clearpage
+
+\subsection{Literature coverage by trait}\label{app:literature-snapshot}
+
+\input{ms_snapshotinfo}
+
+\subsection{Full list of all articles evaluated}\label{app:literature-list}
+
+In total we inspected the full text of 583 articles. The full list of these artciles is in the "read.bib" file available at
+\smurl{github.com/AnaisGibert/Growth\_trait\_metaanalysis}.
+
+\clearpage
+
+\subsection{Quantifying and exploring the cause of heterogeneity in effect sizes}\label{app:heterogeneity}
 

### 2016-01-22 ms_snapshotinfo.Rnw
Small editing in abstract Add comments in footnotes for theoritical expectation Small rewriting of results (add results for SLA RGR vs AGR in mass) Rewriting of "measurements under 'ideal' conditions Move paragraph about stage representativity among traits as a new subsection in results
Add section for table in Appendix Reorder Fig Appendix to match the ms Add section in Appendix with direction to "read.bib" file in github

@@
 And it was \Sexpr{round(fun_snapshot(Snapshot)$all.traits ,0)}\% of the literature that would be captured by SLA and WD for the total 19 traits.
-These results allow us to narrow our search considerably.
-
-\linespread{1}
-
-\begin{table}[h!]
-\centering
-\caption{List of the nineteen traits targeted. Abbreviation,
-definition and search term used in the meta-analysis}
-\label{tab:lit_search}
-\vspace{0.5cm}
-{\footnotesize
-\begin{tabular}{p{3cm}p{3cm}p{8cm}}
-  \hline
-Trait & Definition & Search terms \\
-  \hline
-Aarea & Photosynthetic rate per area & ``photosynthetic rate per area'' OR ``rate of CO2 assimilation per area'' OR ``Aarea'' OR ``Amax'' OR ``photosynthetic capacity per area'' \\
-  Amass & Photosynthetic rate per mass & ``photosynthetic rate per mass'' OR ``rate of CO2 assimilation per mass'' OR ``Amass'' OR ``Amax'' \\
-  Hmax & Maximum height & ``potential height'' OR ``maximum height'' OR ``Hmax'' \\
-  Ks & Stem specific conductance & ``Ks'' OR ``stem specific conductance'' OR ``stem hydraulic conductance'' OR ``sapwood conductance'' \\
-  LA & Leaf lamina area & ``leaf length'' OR ``leaf lamina area'' OR ``leaf width'' OR ``leaf size'' \\
-  LAR & Leaf area ratio & ``leaf area ratio'' \\
-  LMR & Leaf mass ratio & ``leaf mass ratio'' OR ``leaf mass fraction'' \\
-  NARarea & Net assimilation rate per area &  ``net assimilation rate per area'' OR ``rate of dry mass increament per area'' OR ``NARarea'' OR ``NAR'' \\
-  Narea & Leaf nitrogen content per area & ``Narea'' OR ``nitrogen per area'' OR ``N/area'' OR ``leaf nitrogen content per area'' OR ``LNCarea'' OR ``leaf nitrogen content" \\
-  Nmass & Leaf nitrogen content per mass & ``Nmass'' OR ``nitrogen per mass'' OR ``N/mass'' OR ``leaf nitrogen content per mass'' OR ``LNCmass'' OR ``leaf nitrogen content" \\
-  Parea & Leaf phosphorus content per area & ``Parea'' OR ``leaf P'' OR  ``leaf phosphorus content per area''  OR ``leaf phosphorus content'' \\
-  Pmass & Leaf phosphorus content per mass & ``Pmass'' OR ``leaf P'' OR  ``leaf phosphorus content per mass'' OR ``leaf phosphorus content'' \\
-  SA/LA & Sapwood area per leaf area & ``sapwood area per leaf area'' OR ``huber value'' OR ``leaf area per sapwood area'' \\
-  Seed mass & Seed mass & ``seed mass'' OR ``seed size'' OR ``seed volume'' \\
-  SLA & Specific Leaf Area & ``leaf mass per area'' OR ``specific leaf area'' OR ``leaf construction cost'' \\
-  Thickness & Leaf thickness & ``leaf thickness''  OR ``leaf tissue density'' \\
-  Vessel density & Vessel density & ``vessel density'' OR ``stem conduit density'' \\
-  Vessel size & Vessel area or diameter & ``conduit area'' OR ``stem conduit area'' OR ``vessel diameter'' OR ``vessel size'' OR ``conduit size''   \\
-  WD & Wood density & ``wood density'' OR``WD'' OR ``wood specific gravity'' OR ``stem density'' OR ``stem specific density'' OR ``SSD'' \\
-   \hline
-\end{tabular}
-}
-\end{table}
+Thus we narrow our search to only cover these two main traits.

### 2016-01-22 ms_snapshotinfo.tex
Small editing in abstract Add comments in footnotes for theoritical expectation Small rewriting of results (add results for SLA RGR vs AGR in mass) Rewriting of "measurements under 'ideal' conditions Move paragraph about stage representativity among traits as a new subsection in results
Add section for table in Appendix Reorder Fig Appendix to match the ms Add section in Appendix with direction to "read.bib" file in github

@@
 And it was 70\% of the literature that would be captured by SLA and WD for the total 19 traits.
-These results allow us to narrow our search considerably.
-
-\linespread{1}
-
-\begin{table}[h!]
-\centering
-\caption{List of the nineteen traits targeted. Abbreviation,
-definition and search term used in the meta-analysis}
-\label{tab:lit_search}
-\vspace{0.5cm}
-{\footnotesize
-\begin{tabular}{p{3cm}p{3cm}p{8cm}}
-  \hline
-Trait & Definition & Search terms \\
-  \hline
-Aarea & Photosynthetic rate per area & ``photosynthetic rate per area'' OR ``rate of CO2 assimilation per area'' OR ``Aarea'' OR ``Amax'' OR ``photosynthetic capacity per area'' \\
-  Amass & Photosynthetic rate per mass & ``photosynthetic rate per mass'' OR ``rate of CO2 assimilation per mass'' OR ``Amass'' OR ``Amax'' \\
-  Hmax & Maximum height & ``potential height'' OR ``maximum height'' OR ``Hmax'' \\
-  Ks & Stem specific conductance & ``Ks'' OR ``stem specific conductance'' OR ``stem hydraulic conductance'' OR ``sapwood conductance'' \\
-  LA & Leaf lamina area & ``leaf length'' OR ``leaf lamina area'' OR ``leaf width'' OR ``leaf size'' \\
-  LAR & Leaf area ratio & ``leaf area ratio'' \\
-  LMR & Leaf mass ratio & ``leaf mass ratio'' OR ``leaf mass fraction'' \\
-  NARarea & Net assimilation rate per area &  ``net assimilation rate per area'' OR ``rate of dry mass increament per area'' OR ``NARarea'' OR ``NAR'' \\
-  Narea & Leaf nitrogen content per area & ``Narea'' OR ``nitrogen per area'' OR ``N/area'' OR ``leaf nitrogen content per area'' OR ``LNCarea'' OR ``leaf nitrogen content" \\
-  Nmass & Leaf nitrogen content per mass & ``Nmass'' OR ``nitrogen per mass'' OR ``N/mass'' OR ``leaf nitrogen content per mass'' OR ``LNCmass'' OR ``leaf nitrogen content" \\
-  Parea & Leaf phosphorus content per area & ``Parea'' OR ``leaf P'' OR  ``leaf phosphorus content per area''  OR ``leaf phosphorus content'' \\
-  Pmass & Leaf phosphorus content per mass & ``Pmass'' OR ``leaf P'' OR  ``leaf phosphorus content per mass'' OR ``leaf phosphorus content'' \\
-  SA/LA & Sapwood area per leaf area & ``sapwood area per leaf area'' OR ``huber value'' OR ``leaf area per sapwood area'' \\
-  Seed mass & Seed mass & ``seed mass'' OR ``seed size'' OR ``seed volume'' \\
-  SLA & Specific Leaf Area & ``leaf mass per area'' OR ``specific leaf area'' OR ``leaf construction cost'' \\
-  Thickness & Leaf thickness & ``leaf thickness''  OR ``leaf tissue density'' \\
-  Vessel density & Vessel density & ``vessel density'' OR ``stem conduit density'' \\
-  Vessel size & Vessel area or diameter & ``conduit area'' OR ``stem conduit area'' OR ``vessel diameter'' OR ``vessel size'' OR ``conduit size''   \\
-  WD & Wood density & ``wood density'' OR``WD'' OR ``wood specific gravity'' OR ``stem density'' OR ``stem specific density'' OR ``SSD'' \\
-   \hline
-\end{tabular}
-}
-\end{table}
+Thus we narrow our search to only cover these two main traits.

### 2016-01-22 MS.tex
Separate SuppMat into another document. Full reference list from read.bib

--- 2016-01-21 MS.tex
@@
 \usepackage[]{natbib}
-\definecolor{grey}{rgb}{0.5, 0.5, 0.5}
 
@@
 
-\newcommand{\smurl}[1]{\url{#1}}
-\newcommand{\ud}{\ensuremath{\rm{d}}}
-\newcommand{\tabitem}{~~\llap{\textbullet}~~}
 \usepackage{graphicx}
-\usepackage[title,titletoc,toc]{appendix}
 
-\title{On the link between functional traits and growth rate: meta-analysis shows effects change with plant size, as predicted}
-\author{Ana{\"i}s Gibert\textasteriskcentered, Emma F. Gray, Mark Westoby, Ian J. Wright, Daniel S. Falster}
-\affiliation{Biological Sciences, Macquarie University NSW 2109, Australia\\
-\textasteriskcentered Email for correspondence: \texttt{anais.gibert@gmail.com}\\
-Word count: ~8211 words /9600 (without supplementary material, Fig and ref)}
+% Enable cross referencing to Evidence document
+\usepackage{xr}
+\externaldocument{ms-suppinfo}
+
+\input{ms-common-defs}
+
 \date{}
@@
 % - seach on XXX, footnote
-% - check refs to appendices in main text
 
 \bibliographystyle{mee}
-
 \mstype{Research Article}
-\runninghead{Influence of traits on growth changes with size}
 \keywords{maximum height, photosynthetic rate, ontogenetic stage, functional trait, growth strategy, seed mass, specific leaf area, wood density}
@@
 Note that the live biomass $B = M_{\rm t} + M_{\rm f}$.
-Applying the product rule of differential calculus, the \textbf{growth rate in plant mass}, ($M_{\rm t}$), can be decomposed as
+Applying the chain rule of differential calculus, the \textbf{growth rate in plant mass}, ($M_{\rm t}$), can be decomposed as
 \begin{equation}\label{eq:eq1}
@@
 
-\bibliography{output/refs}\label{references}
+\bibliography{output/refs-main}\label{references}
 
@@
 
-\clearpage
-\setcounter{secnumdepth}{1}
-\begin{appendices}\label{sec:appendices}
-\renewcommand{\thefigure}{S\arabic{figure}}
-\renewcommand{\thetable}{S\arabic{table}}
-
-\setcounter{figure}{0}
-\setcounter{table}{0}
-
-\clearpage
-
-\clearpage
-\section{Supporting figures}\label{app:supp_info_figures}
-
-\begin{figure}[h!]
-\centering
-\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA1.pdf}
-\caption{Relationships between a) age and diameter (m), b) age and height (m), and c) diameter and height among plants in the Biomass and Allometry Database.
-Lines indicate the cut-offs between stage categories used in this study: blue lines indicate limit between seedlings and saplings, red lines indicate limits between saplings and adults.}
-\label{fig:figA1}
-\end{figure}
-
-\begin{figure}[h!]
-\centering
-\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA2.pdf}
-\caption{Geographical distribution of site locations from studies performed in the field used in the meta-analysis.
-Results shown here are from the entire dataset (for details see ``Material and Methods'').}
-\label{fig:figA2}
-\end{figure}
-
-\begin{figure}[h!]
-\centering
-\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA3.pdf}
-\caption{Range of correlations (r) between
-growth and traits reported in the literature. Plots show the coefficients of correlation (r)
-between plant growth and a) Specific leaf area (SLA, n =
-111), b) Wood density (WD, n = 64), c) Asymptotic
-maximum height (Hmax, n = 23), d) Seed mass (Seedmass, n = 36 and
-e) Rate of CO2 assimilation (Aarea, n = 24) reported from 103
-articles.
-The x axis represents the article ID sorted by the average reported coefficient value r.
-Each bubble represents an r value, the diameter of the bubble is proportional to its weight in the meta-analysis (i.e.
-number of species).
-The colours correspond to the stage for which the r values have been recorded: red points correspond to adult stage, orange points to saplings, and blue points to seedlings.
-Results shown here are from the entire dataset (for details see ``Material and Methods'').
-}
-\label{fig:figA3}
-\end{figure}
-
-\begin{figure}[h!]
-\centering
-\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA4.pdf}
-\caption{Mean coefficient correlation r (+SD) between growth and traits measured by stage.
-a) Specific leaf area (SLA), b) Wood density (WD), c) Asymptotic maximum height (Hmax), d) Seed mass (Seedmass) and e) Rate of CO2 assimilation (Aarea).
-The mean coefficients are weighted by sample size and established from 103 articles.
-Results shown here are from the ''ideal'' subset of data (for details see ``Material and Methods''), ``n'' indicates the number of correlations.}
-\label{fig:figA4}
-\end{figure}
-
-\begin{figure}[h!]
-\centering
-\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA5.pdf}
-\caption{Effect size ($\pm$95\% confidence intervals, CI) of plant stage on the correlations between growth rate and five functional traits across species, with a data set averaging multiple comparisons by trait and by study.
-In the case of multiple comparisons within a study, effect sizes were calculated using the mean correlation coefficient by trait and by study.
-a) Specific leaf area (SLA), b) Wood density (WD), c) Asymptotic maximum height (Hmax) , d) Seed mass and e) Assimilation rate of CO2 (Aarea).
-Effect size is a standardized measure of the magnitude of the relationship between a particular stage and the correlation coefficient z (Fisher's z-transformed).
-Effects are significant if CIs do not overlap with zero.
-LRT: likelihood Ratio Test compared the fit between null model and stage model, both models are fitted by Maximum Likelihood.
-Black point: ideal data , grey points: all the data (for details see ``Material and Methods'').
-``n'' indicates the number of independent comparisons for each effect.}
-\label{fig:figA5}
-\end{figure}
-
-\begin{figure}[h!]
-\centering
-\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA6a.pdf}
-\end{figure}
-
-\begin{figure}[h!]
-\centering
-\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA6b.pdf}
-\end{figure}
-
-\begin{figure}[h!]
-\centering
-\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA6c.pdf}
-\caption{Effects size on the correlation between growth and traits of plant stage (mod1), growth measurement (mod2), vegetation type (mod3), and experiment type (mod4).
-a) Specific leaf area (SLA), b) Wood density (WD),c) Assimilation rate of CO2 (Aarea), d) Seed mass, and e) Asymptotic maximum height (Hmax).
-The effect size (z + 95\%CI) is reported for each class, and models are fitted by restricted max likelihood (REML).
-Abbreviation: GR = growth rate and RGR = relative growth rate, measured in diameter (D), height (H), mass(M), cross section area (CSA) and volume (V), across GF: coefficient of correlation measured on tree in mixture with other growth form.
-AIC: Akaike information criterion corresponds to the quality of each model, and allow a comparison between models.
-Smallest is the AIC better is the model.
-Results shown here are from ``ideal'' subset of data (for details see ``Material and Methods'').
-``n'' indicates number of correlation r reported.}
-\label{fig:figA6}
-\end{figure}
-
-\begin{figure}[h!]
-\centering
-\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA8.pdf}
-\caption{Number of correlation extracted by traits, stage, and growth type (absolute vs relative, and measurement).
-a) Specific leaf area (SLA), b) Wood density (WD), c) Asymptotic maximum height (Hmax), d) Seed mass and e) Assimilation rate of CO2 (Aarea).
-Absolute growth rate (AGR) is on the left and relative growth rate (RGR) on the right of each plot.
-Results shown here are from the "ideal" subset of the data (for details see ``Material and Methods'').
-}
-\label{fig:figA8}
-\end{figure}
-
-\begin{figure}[h!]
-\centering
-\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA7.pdf}
-\caption{Funnel plots with filled in data based on the trim and fill method, showing transformed correlation coefficient z between growth and a) Specific leaf area (SLA), b) Wood density (WD), c) Asymptotic maximum height (Hmax), d) Seed mass and e) Assimilation rate of CO2 (Aarea).
-Note that in these plots the y axis is 1/number of species included in the correlation, not the replication for the correlation.
-The open points correspond to the estimated missing studies.
-The number of missing values is 4 for SLA,0 for WD, 0 for Hmax, 11 for seed mass and 0 for Aarea.
-Results shown here are from the entire dataset.
-Results with the "ideal" subset of data (for details see ``Material and Methods''), shown no missing values for all traits.}
-\label{fig:figA7}
-\end{figure}
-
-\begin{figure}[h!]
-\centering
-\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA9.pdf}
-\caption{Temporal changes in coefficient of correlation between growth and traits.
-a) Specific leaf area (SLA), b) Wood density (WD), c) Asymptotic maximum height (Hmax), d) Seed mass, and e) Assimilation rate of CO2 (Aarea).
-The colours correspond to the stage for which the r values have been recorded: red points corresponds to adult stage, orange points to saplings, and grey points to seedlings.
-Results shown here are from the entire dataset.}
-\label{fig:figA9}
-\end{figure}
-
-\clearpage
-\section{Supporting Analyses}\label{app:supp_info_analyses}
-
-\subsection{Literature coverage by trait}\label{app:literature-snapshot}
-
-\input{ms_snapshotinfo}
-
-\clearpage
-
-\subsection{Simplified growth equations for seedlings of similar size}
-
-For the case of seedlings, eqs.
-\ref{eq:eq0}-\ref{eq:eq1} can be simplified considerably.
-Turnover of all tissues and allocation to reproduction have not yet begun.
-It is also common to assume all respiration rates are proportional to leaf area.
-Biomass growth rate in seedling then becomes a linear function of leaf area:
-\begin{equation}\label{eq:eq1_seedlings}
-{\frac{\ud M_{\rm t}}{\ud t}}  \approx  A_{\rm l} \, y \, (p - r_{\rm l}).
-\end{equation}
-
-The \textbf{relative growth rate in mass} $({\rm RGR}_{{\rm mass}})$ in seedlings can be obtained by dividing both sides of this simplified eq \ref{eq:eq1_seedlings} by the total mass of living tissues $M_{\rm t}$.
-The outcome is equivalent to the classical partitioning of RGR \citep{Lambers:1992bj, Cornelissen:1998ta}:
-\begin{equation}\label{eq:eq1_seedlings_RGR}
-{\rm RGR}_{{\rm mass}}  \approx {\rm NAR} \times  {\rm SLA} \times  {\rm LMF},
-\end{equation}
-where net assimilation rate NAR = $y \, (p - r)$, SLA = $A_{\rm l}/ M_{\rm l}$ and leaf mass fraction LMF = $M_{\rm l}/ M_{\rm t}$.
-
-\subsection{Quantifying and exploring the cause of heterogeneity in effect sizes}
-
-\input{ms_suppinfo}
-
-\end{appendices}
 \end{document}

### 2016-01-22 ms-common-defs.tex
Separate SuppMat into another document. Full reference list from read.bib

\definecolor{grey}{rgb}{0.5, 0.5, 0.5}
\newcommand{\smurl}[1]{\url{#1}}
\newcommand{\ud}{\ensuremath{\rm{d}}}
\newcommand{\tabitem}{~~\llap{\textbullet}~~}
\newcommand{\email}[1]{\href{mailto:#1}{\texttt{#1}}}

\title{On the link between functional traits and growth rate: meta-analysis shows effects change with plant size, as predicted}
\author{Ana{\"i}s Gibert\textasteriskcentered, Emma F. Gray, Mark Westoby, Ian J. Wright, Daniel S. Falster}
\affiliation{Department of Biological Sciences, Macquarie University,
  Sydney, Australia \\
\textasteriskcentered Email for correspondence: \texttt{anais.gibert@gmail.com}
}
\runninghead{Influence of traits on growth changes with size}

### 2016-01-22 ms-suppinfo.Rnw
Separate SuppMat into another document. Full reference list from read.bib

--- 2016-01-19 ms_suppinfo.Rnw
@@
-<<preload, echo=FALSE>>=
-library(knitr)
-opts_chunk$set(echo=FALSE)
-@
+\documentclass[10pt,twoside]{article}
+
+\usepackage{suppmat}
+\usepackage{listings}
+\usepackage[T1]{fontenc} % Better underscores, shockingly.
+\usepackage{graphicx}
+
+\input{ms-common-defs}
+
+% We will generate all images so they have a width \maxwidth. This means
+% that they will get their normal width if they fit onto the page, but
+% are scaled down if they would overflow the margins.
+\makeatletter
+\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
+\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
+\makeatother
+\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
+
+\titleprefix{Supporting information for:}
+
+\date{}
+
+\usepackage[]{natbib}
+\bibliographystyle{mee}
+
+\begin{document}
+
+\maketitle
+
+\tableofcontents
+
+\renewcommand{\thefigure}{S\arabic{figure}}
+\renewcommand{\thetable}{S\arabic{table}}
+
+\section{Supporting Figures}\label{app:supp_info_figures}
+
+\begin{figure}[h!]
+\centering
+\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA1.pdf}
+\caption{Relationships between a) age and diameter (m), b) age and height (m), and c) diameter and height among plants in the Biomass and Allometry Database.
+Lines indicate the cut-offs between stage categories used in this study: blue lines indicate limit between seedlings and saplings, red lines indicate limits between saplings and adults.}
+\label{fig:figA1}
+\end{figure}
+
+\begin{figure}[h!]
+\centering
+\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA6a.pdf}
+\end{figure}
+
+\begin{figure}[h!]
+\centering
+\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA6b.pdf}
+\end{figure}
+
+\begin{figure}[h!]
+\centering
+\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA6c.pdf}
+\caption{Effects size on the correlation between growth and traits of plant stage (mod1), growth measurement (mod2), vegetation type (mod3), and experiment type (mod4).
+a) Specific leaf area (SLA), b) Wood density (WD),c) Assimilation rate of CO2 (Aarea), d) Seed mass, and e) Asymptotic maximum height (Hmax).
+The effect size (z + 95\%CI) is reported for each class, and models are fitted by restricted max likelihood (REML).
+Abbreviation: GR = growth rate and RGR = relative growth rate, measured in diameter (D), height (H), mass(M), cross section area (CSA) and volume (V), across GF: coefficient of correlation measured on tree in mixture with other growth form.
+AIC: Akaike information criterion corresponds to the quality of each model, and allow a comparison between models.
+Smallest is the AIC better is the model.
+Results shown here are from ``ideal'' subset of data (for details see ``Material and Methods'').
+``n'' indicates number of correlation r reported.}
+\label{fig:figA6}
+\end{figure}
+
+\begin{figure}[h!]
+\centering
+\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA4.pdf}
+\caption{Mean coefficient correlation r (+SD) between growth and traits measured by stage.
+a) Specific leaf area (SLA), b) Wood density (WD), c) Asymptotic maximum height (Hmax), d) Seed mass (Seedmass) and e) Rate of CO2 assimilation (Aarea).
+The mean coefficients are weighted by sample size and established from 103 articles.
+Results shown here are from the ''ideal'' subset of data (for details see ``Material and Methods''), ``n'' indicates the number of correlations.}
+\label{fig:figA4}
+\end{figure}
+
+\begin{figure}[h!]
+\centering
+\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA8.pdf}
+\caption{Number of correlation extracted by traits, stage, and growth type (absolute vs relative, and measurement).
+a) Specific leaf area (SLA), b) Wood density (WD), c) Asymptotic maximum height (Hmax), d) Seed mass and e) Assimilation rate of CO2 (Aarea).
+Absolute growth rate (AGR) is on the left and relative growth rate (RGR) on the right of each plot.
+Results shown here are from the "ideal" subset of the data (for details see ``Material and Methods'').
+}
+\label{fig:figA8}
+\end{figure}
+
+\begin{figure}[h!]
+\centering
+\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA2.pdf}
+\caption{Geographical distribution of site locations from studies performed in the field used in the meta-analysis.
+Results shown here are from the entire dataset (for details see ``Material and Methods'').}
+\label{fig:figA2}
+\end{figure}
+
+\begin{figure}[h!]
+\centering
+\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA3.pdf}
+\caption{Range of correlations (r) between
+growth and traits reported in the literature. Plots show the coefficients of correlation (r)
+between plant growth and a) Specific leaf area (SLA, n =
+111), b) Wood density (WD, n = 64), c) Asymptotic
+maximum height (Hmax, n = 23), d) Seed mass (Seedmass, n = 36 and
+e) Rate of CO2 assimilation (Aarea, n = 24) reported from 103
+articles.
+The x axis represents the article ID sorted by the average reported coefficient value r.
+Each bubble represents an r value, the diameter of the bubble is proportional to its weight in the meta-analysis (i.e.
+number of species).
+The colours correspond to the stage for which the r values have been recorded: red points correspond to adult stage, orange points to saplings, and blue points to seedlings.
+Results shown here are from the entire dataset (for details see ``Material and Methods'').
+}
+\label{fig:figA3}
+\end{figure}
+
+\begin{figure}[h!]
+\centering
+\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA7.pdf}
+\caption{Funnel plots with filled in data based on the trim and fill method, showing transformed correlation coefficient z between growth and a) Specific leaf area (SLA), b) Wood density (WD), c) Asymptotic maximum height (Hmax), d) Seed mass and e) Assimilation rate of CO2 (Aarea).
+Note that in these plots the y axis is 1/number of species included in the correlation, not the replication for the correlation.
+The open points correspond to the estimated missing studies.
+The number of missing values is 4 for SLA,0 for WD, 0 for Hmax, 11 for seed mass and 0 for Aarea.
+Results shown here are from the entire dataset.
+Results with the "ideal" subset of data (for details see ``Material and Methods''), shown no missing values for all traits.}
+\label{fig:figA7}
+\end{figure}
+
+\begin{figure}[h!]
+\centering
+\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA9.pdf}
+\caption{Temporal changes in coefficient of correlation between growth and traits.
+a) Specific leaf area (SLA), b) Wood density (WD), c) Asymptotic maximum height (Hmax), d) Seed mass, and e) Assimilation rate of CO2 (Aarea).
+The colours correspond to the stage for which the r values have been recorded: red points corresponds to adult stage, orange points to saplings, and grey points to seedlings.
+Results shown here are from the entire dataset.}
+\label{fig:figA9}
+\end{figure}
+
+\begin{figure}[h!]
+\centering
+\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA5.pdf}
+\caption{Effect size ($\pm$95\% confidence intervals, CI) of plant stage on the correlations between growth rate and five functional traits across species, with a data set averaging multiple comparisons by trait and by study.
+In the case of multiple comparisons within a study, effect sizes were calculated using the mean correlation coefficient by trait and by study.
+a) Specific leaf area (SLA), b) Wood density (WD), c) Asymptotic maximum height (Hmax) , d) Seed mass and e) Assimilation rate of CO2 (Aarea).
+Effect size is a standardized measure of the magnitude of the relationship between a particular stage and the correlation coefficient z (Fisher's z-transformed).
+Effects are significant if CIs do not overlap with zero.
+LRT: likelihood Ratio Test compared the fit between null model and stage model, both models are fitted by Maximum Likelihood.
+Black point: ideal data , grey points: all the data (for details see ``Material and Methods'').
+``n'' indicates the number of independent comparisons for each effect.}
+\label{fig:figA5}
+\end{figure}
+
+\clearpage
+
+\section{Supporting Tables}\label{app:supp_info_table}
+
+\linespread{1}
+
+\begin{table}[h!]
+\centering
+\caption{List of the nineteen traits targeted. Abbreviation,
+definition and search term used in the meta-analysis}
+\label{tab:lit_search}
+\vspace{0.5cm}
+{\footnotesize
+\begin{tabular}{p{3cm}p{3cm}p{8cm}}
+  \hline
+Trait & Definition & Search terms \\
+  \hline
+Aarea & Photosynthetic rate per area & ``photosynthetic rate per area'' OR ``rate of CO2 assimilation per area'' OR ``Aarea'' OR ``Amax'' OR ``photosynthetic capacity per area'' \\
+  Amass & Photosynthetic rate per mass & ``photosynthetic rate per mass'' OR ``rate of CO2 assimilation per mass'' OR ``Amass'' OR ``Amax'' \\
+  Hmax & Maximum height & ``potential height'' OR ``maximum height'' OR ``Hmax'' \\
+  Ks & Stem specific conductance & ``Ks'' OR ``stem specific conductance'' OR ``stem hydraulic conductance'' OR ``sapwood conductance'' \\
+  LA & Leaf lamina area & ``leaf length'' OR ``leaf lamina area'' OR ``leaf width'' OR ``leaf size'' \\
+  LAR & Leaf area ratio & ``leaf area ratio'' \\
+  LMR & Leaf mass ratio & ``leaf mass ratio'' OR ``leaf mass fraction'' \\
+  NARarea & Net assimilation rate per area &  ``net assimilation rate per area'' OR ``rate of dry mass increament per area'' OR ``NARarea'' OR ``NAR'' \\
+  Narea & Leaf nitrogen content per area & ``Narea'' OR ``nitrogen per area'' OR ``N/area'' OR ``leaf nitrogen content per area'' OR ``LNCarea'' OR ``leaf nitrogen content" \\
+  Nmass & Leaf nitrogen content per mass & ``Nmass'' OR ``nitrogen per mass'' OR ``N/mass'' OR ``leaf nitrogen content per mass'' OR ``LNCmass'' OR ``leaf nitrogen content" \\
+  Parea & Leaf phosphorus content per area & ``Parea'' OR ``leaf P'' OR  ``leaf phosphorus content per area''  OR ``leaf phosphorus content'' \\
+  Pmass & Leaf phosphorus content per mass & ``Pmass'' OR ``leaf P'' OR  ``leaf phosphorus content per mass'' OR ``leaf phosphorus content'' \\
+  SA/LA & Sapwood area per leaf area & ``sapwood area per leaf area'' OR ``huber value'' OR ``leaf area per sapwood area'' \\
+  Seed mass & Seed mass & ``seed mass'' OR ``seed size'' OR ``seed volume'' \\
+  SLA & Specific Leaf Area & ``leaf mass per area'' OR ``specific leaf area'' OR ``leaf construction cost'' \\
+  Thickness & Leaf thickness & ``leaf thickness''  OR ``leaf tissue density'' \\
+  Vessel density & Vessel density & ``vessel density'' OR ``stem conduit density'' \\
+  Vessel size & Vessel area or diameter & ``conduit area'' OR ``stem conduit area'' OR ``vessel diameter'' OR ``vessel size'' OR ``conduit size''   \\
+  WD & Wood density & ``wood density'' OR``WD'' OR ``wood specific gravity'' OR ``stem density'' OR ``stem specific density'' OR ``SSD'' \\
+   \hline
+\end{tabular}
+}
+\end{table}
+
+\clearpage
+
+\section{Supporting Analyses}\label{app:supp_info_analyses}
+
+\subsection{Simplified growth equations for seedlings of similar size}\label{app:growth-equation}
+
+For the case of seedlings, the growth equations can be simplified considerably.
+Turnover of all tissues and allocation to reproduction have not yet begun.
+It is also common to assume all respiration rates are proportional to leaf area.
+Biomass growth rate in seedling then becomes a linear function of leaf area:
+\begin{equation}\label{eq:eq1_seedlings}
+{\frac{\ud M_{\rm t}}{\ud t}}  \approx  A_{\rm l} \, y \, (p - r_{\rm l}).
+\end{equation}
+
+The \textbf{relative growth rate in mass} $({\rm RGR}_{{\rm mass}})$ in seedlings can be obtained by dividing both sides of this simplified eq \ref{eq:eq1_seedlings} by the total mass of living tissues $M_{\rm t}$.
+The outcome is equivalent to the classical partitioning of RGR \citep{Lambers:1992bj, Cornelissen:1998ta}:
+\begin{equation}\label{eq:eq1_seedlings_RGR}
+{\rm RGR}_{{\rm mass}}  \approx {\rm NAR} \times  {\rm SLA} \times  {\rm LMF},
+\end{equation}
+where net assimilation rate NAR = $y \, (p - r)$, SLA = $A_{\rm l}/ M_{\rm l}$ and leaf mass fraction LMF = $M_{\rm l}/ M_{\rm t}$.
+
+\subsection{Literature coverage by trait}\label{app:literature-snapshot}
+
+We developed a snapshot of the literature, to assess the potential to recover useful data from the wide corpus of literature available by searching exclusively on SLA and WD.
+This snapshot was obtained via Web of Science database (Thomson Reuters), between March and June 2014, using a range of Boolean search terms in English.
+Search terms were as follows: (``trait'' AND (``growth rate'' OR ``relative growth rate'')) AND (``tree*'' OR ``woody*''), where ``trait'' was allowed to be any of the trait names listed in Table \ref{tab:lit_search}.
+This snapshot indicated that \Sexpr{round(fun_snapshot(Snapshot)$main.traits ,0)}\% of the reported correlations linking growth to any of our five core traits would be recovered by searching only on SLA and WD.
+And it was \Sexpr{round(fun_snapshot(Snapshot)$all.traits ,0)}\% of the literature that would be captured by SLA and WD for the total 19 traits.
+Thus we narrow our search to only cover these two main traits.
+
+\subsection{Full list of all articles evaluated}\label{app:literature-list}
+
+In total we inspected the full text of 583 articles, including \citet{\Sexpr{paste(names(read_bib), collapse=",")}}.
+
+A corresponding bibtex file is available in the file `references/read.bib`, available at
+\smurl{github.com/AnaisGibert/Growth\_trait\_metaanalysis}.
+
+\subsection{Quantifying and exploring the cause of heterogeneity in effect sizes}\label{app:heterogeneity}
 
@@
 Finally, since between study variation is significant, as indicated by heterogeneity analyses, the use of the random effect model was appropriate in our meta-analysis.
+\clearpage
 
@@
 
+\clearpage
 \subsection{Exploring temporal changes in effect size}
@@
 The conclusions of a meta-analysis conducted in different years should not differ from those reported here.
+
+\clearpage
+
+\bibliography{output/refs-suppmat}
+
+\end{document}

### 2016-01-22 ms-suppinfo.tex
Separate SuppMat into another document. Full reference list from read.bib

--- 2016-01-22 ms-suppinfo.Rnw
@@
-\documentclass[10pt,twoside]{article}
+\documentclass[10pt,twoside]{article}\usepackage[]{graphicx}\usepackage[]{color}
+%% maxwidth is the original width if it is less than linewidth
+%% otherwise use linewidth (to make sure the graphics do not exceed the margin)
+\makeatletter
+\def\maxwidth{ %
+  \ifdim\Gin@nat@width>\linewidth
+    \linewidth
+  \else
+    \Gin@nat@width
+  \fi
+}
+\makeatother
+
+\definecolor{fgcolor}{rgb}{0.345, 0.345, 0.345}
+\newcommand{\hlnum}[1]{\textcolor[rgb]{0.686,0.059,0.569}{#1}}%
+\newcommand{\hlstr}[1]{\textcolor[rgb]{0.192,0.494,0.8}{#1}}%
+\newcommand{\hlcom}[1]{\textcolor[rgb]{0.678,0.584,0.686}{\textit{#1}}}%
+\newcommand{\hlopt}[1]{\textcolor[rgb]{0,0,0}{#1}}%
+\newcommand{\hlstd}[1]{\textcolor[rgb]{0.345,0.345,0.345}{#1}}%
+\newcommand{\hlkwa}[1]{\textcolor[rgb]{0.161,0.373,0.58}{\textbf{#1}}}%
+\newcommand{\hlkwb}[1]{\textcolor[rgb]{0.69,0.353,0.396}{#1}}%
+\newcommand{\hlkwc}[1]{\textcolor[rgb]{0.333,0.667,0.333}{#1}}%
+\newcommand{\hlkwd}[1]{\textcolor[rgb]{0.737,0.353,0.396}{\textbf{#1}}}%
+
+\usepackage{framed}
+\makeatletter
+\newenvironment{kframe}{%
+ \def\at@end@of@kframe{}%
+ \ifinner\ifhmode%
+  \def\at@end@of@kframe{\end{minipage}}%
+  \begin{minipage}{\columnwidth}%
+ \fi\fi%
+ \def\FrameCommand##1{\hskip\@totalleftmargin \hskip-\fboxsep
+ \colorbox{shadecolor}{##1}\hskip-\fboxsep
+     % There is no \\@totalrightmargin, so:
+     \hskip-\linewidth \hskip-\@totalleftmargin \hskip\columnwidth}%
+ \MakeFramed {\advance\hsize-\width
+   \@totalleftmargin\z@ \linewidth\hsize
+   \@setminipage}}%
+ {\par\unskip\endMakeFramed%
+ \at@end@of@kframe}
+\makeatother
+
+\definecolor{shadecolor}{rgb}{.97, .97, .97}
+\definecolor{messagecolor}{rgb}{0, 0, 0}
+\definecolor{warningcolor}{rgb}{1, 0, 1}
+\definecolor{errorcolor}{rgb}{1, 0, 0}
+\newenvironment{knitrout}{}{} % an empty environment to be redefined in TeX
+
+\usepackage{alltt}
 
@@
 \bibliographystyle{mee}
-
+\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
 \begin{document}
@@
 Search terms were as follows: (``trait'' AND (``growth rate'' OR ``relative growth rate'')) AND (``tree*'' OR ``woody*''), where ``trait'' was allowed to be any of the trait names listed in Table \ref{tab:lit_search}.
-This snapshot indicated that \Sexpr{round(fun_snapshot(Snapshot)$main.traits ,0)}\% of the reported correlations linking growth to any of our five core traits would be recovered by searching only on SLA and WD.
-And it was \Sexpr{round(fun_snapshot(Snapshot)$all.traits ,0)}\% of the literature that would be captured by SLA and WD for the total 19 traits.
+This snapshot indicated that 84\% of the reported correlations linking growth to any of our five core traits would be recovered by searching only on SLA and WD.
+And it was 70\% of the literature that would be captured by SLA and WD for the total 19 traits.
 Thus we narrow our search to only cover these two main traits.
@@
 
-In total we inspected the full text of 583 articles, including \citet{\Sexpr{paste(names(read_bib), collapse=",")}}.
+In total we inspected the full text of 583 articles, including \citet{Ackerly:1996vo,Adler:2014jw,Agren:1985kl,Agren:1988fc,Agren:1996gl,Agren:2003ee,Agren:2004el,Agyeman:1999ef,aiba_tree_1996,Aiba:1997ho,Aiba:2005gl,Aiba:2009ft,AlmeidaCortez:1999jn,AlvarezClare:2009ht,anekonda_selection_1996,Anonymous:kmGgY8eO,Antunez:2001gk,Arendonk:1994kv,arendt_adaptive_1997,Arnqvist:1995es,Atkin:1996ug,Atkin:1996uy,Atkin:1998in,Atkin:2006kx,augspurger_light_1984,Augspurger:1984ct,Baker:2004jy,baltzer_determinants_2007,baltzer_physiological_2007,BarajasMorales:1987vz,baraloto_differential_2006,baraloto_seed_2005,Baraloto:2005er,Baraloto:2010fd,barberis_gaps_2005,Barigah:1998bi,Barot:2014hb,Beckmann:2012hn,Bellingham:2004kd,bicknell_development_1982,Blackman:1951ux,Bloor:2003fa,Bohlman:2006eo,Bonal:2007kf,bond_tortoise_1989,Bond:2001ti,Bond:2003bb,Bond:2005gn,Bongers:1990jl,Boogaard:1996hz,Boot:1996ug,Borchert:1994kj,Borenstein:2009um,Boring:1981ic,Botkin:1972tk,Bouffier:2008do,Bowman:2005ds,Bowman:2013cb,Brink:2011hi,Broncano:1998ck,Brouillette:2014hq,Brown:1996ks,Bruhn:2000jz,Buckley:2006ga,Burns:1997jy,Butterfield:1993uc,Cai:2007ie,Cai:2007vs,Cai:2008tu,Callaway:1994kk,CamaraZapata:2003df,CamaraZapata:2004up,Canadell:2007ij,Carmona:2010kp,Carnicer:2013el,caspersen_how_2011,Castro:2008wq,CastroDiez:1998gz,CastroDiez:2003jd,CastroDiez:2006gv,CastroDiez:2006gva,Catoni:2014bs,Causton:1994bk,Cebrian:1994jo,Cernusak:2008ds,Chacon:2005kn,Chambers:2001uw,Chao:2008hg,Chapin:1980gz,Chapin:1989il,Chaturvedi:2011jx,Chaturvedi:2014ie,Chave:2006tu,Chave:2009iy,Chen:2014jt,Chiariello:1989bl,clark_assessing_1999,clark_life_1992,Clark:1994kx,Clark:1999ed,Cochard:2007bn,Coleman:1994hm,coley_resource_1985,Coley:1983hk,Coley:1988wq,Comas:2002wt,Comas:2004jz,Comas:2004jza,Condit:1993hd,connell_subcanopy_1997,Conover:2009gj,Coombe:1962kz,coomes_comparison_1998,coomes_effects_2007,coomes_greater_2009,Cordero:2003wk,cornelissen_generalities_1999,cornelissen_interactive_1996,cornelissen_seedling_1996,Cornelissen:1996hf,Cornelissen:1997fd,Cornelissen:1998ta,Cornelissen:1999fq,Cornelissen:2001jr,Cornelissen:2003gw,Cornelissen:2008ge,Cregg:1988te,curran_wood_2008,dalling_seed_2002,Dalling:2004gs,darling_evaluating_2012,davies_tree_2001,DeBell:1994ix,DeDeyn:2008hv,DeLucia:1989kj,Delucia:1998vz,doncaster_non-linear_2008,Durand:2001fh,Duval:2000dg,Dyer:2001jw,Easdale:2009gv,edwards_allometric_2012,Edwards:2014db,Ellison:1993fz,Emmanuel:2014cz,Enquist:2007ek,Erickson:1974el,Evans:1998ug,Falagas:2008gtb,Falster:2005bw,Falster:2011ii,Falster:2015,Falster:2015bd,fan_hydraulic_2012,Farnsworth:1995im,Farrar:1989wt,Farrar:1998wx,Fayolle:2012bx,Fenner:1999ev,Fetene:2001kc,finegan_diameter_1999,FitzJohn:2014cf,Fortunel:2014gz,Fujimoto:2006fg,Galmes:2005fa,Garnier:1991kp,Garnier:1992kn,Garnier:1995fc,Garnier:1997ba,Garnier:1997fi,Garnier:1998wm,Garnier:2001fk,Gibert:2013bo,gilbert_life_2006,Givnish:1995ta,gleeson_plant_1994,Goldberg:1982cf,GonzalezMunoz:2013ie,Goudriaan:1990tl,Gower:1993jo,Grattapaglia:1996tq,Gregorczyk:1996fv,Grime:1975gr,Grime:1975kk,Grime:1977kc,Grime:1997wm,Grime:2012gt,grime1979plant,Groninger:1996bu,grotkopp_toward_2002,Grotkopp:2007di,Grubb:1977ki,Grubb:1996kr,Grubb:1996kra,Gulias:2009ja,Gunatilleke:1997hd,Gusewell:2004kc,gutsell_accurately_2002,Hannrup:2004ke,Hattenschwiler:2001eu,HDBradshaw:1995tu,Hellgren:1996by,Hempson:2014ir,Herault:2010db,Herault:2011dd,Higgins:2002iq,Higgins:2003hz,Hilbert:1990vo,Hipps:1995tu,Hirose:1988jl,HOFFLAND:1996gk,Hoffmann:2003ga,Holzwarth:2015dg,Hoshika:2014gv,houghton_does_2013,Houter:2014gu,Huante:1992jg,Huante:1995fd,Huante:1995tl,Huante:1998bk,Huante:1998ft,Huante:1998hx,Hubbell:2005dm,Hummel:2006ko,Hunt:1987wc,HUNT:1997ge,HUNT:1997gf,Huxley:1967gk,Iida:2012jb,Iida:2014ep,Iida:2014hq,Imaji:2010ik,Ingestad:1979fi,Ingestad:1995kw,Ishii:2000et,Ivancich:2012iu,Jennions:2013ta,Johnson:2009iz,Jurado:1992fh,Karlsson:1987il,Ke:1999bk,Khurana:2004wv,Kidd:1921bp,king_correlations_1991,king_influence_1994,king_relationships_1997,king_size-related_2011,king_tree_2005,King:2006dg,King:2006he,Kitajima:1994ez,Kitajima:2002fm,Kitajima:2013hb,Kneeshaw:2006bd,kobe_carbohydrate_1997,Kobe:1999ha,Koch:2004br,Kohyama:2003dk,Konings:1989we,Koricheva:2013hy,Koricheva:2013tz,Koricheva:2014ku,Korner:2005dh,korning_growth_1994,Kraft:2008un,Kruger:2006fq,Kruger:2006fqb,Kumar:2014iz,Kunstler:2009dt,Kunstler:2010ei,Kwesiga:1986tk,Lachapelle:2012kl,Lacourse:2009wg,Lajeunesse:2013tm,Lamarque:2011im,Lambers:1992bj,Lambers:2004bj,Lamers:2006dl,Larjavaara:2010bn,Larjavaara:2014ur,Lasky:2013iq,Lasky:2015wu,Latham:1992ei,Lavorel:2002ff,Lavorel:2002tw,Leao:2014hw,Lee:1996bh,Leoni:2009jx,Li:2005ww,Li:2013bi,Limpens:2014cm,lind_life-history_2013,Loach:1970gp,loehle_height_1998,loehle_tree_1988,Loehle:1988je,Long:1996vp,Long:2011er,LopezIglesias:2014dk,Loveys:2002hj,Loveys:2003kl,Lu:2014kb,lusk_leaf_2002,lusk_leaf_2004,lusk_ontogenetic_2006,lusk_whole-plant_2013,Lusk:1997ga,Lusk:2002fm,Lusk:2002fma,Lusk:2008fo,Lusk:2011cf,Lusk:2013bq,Lusk:2013hz,MadrigalGonzalez:2014go,Maranon:1993iv,Markesteijn:2009if,Marron:2005cm,Martin:2011ij,MartinezVilalta:2010iq,Matias:2011fq,Mayfield:2006gn,McCormack:2012ch,mccormick_larval_2004,McIntyre:1999go,McMillin:1973iv,Mediavilla:2003cg,Meinzer:2011br,Menaut:1990dl,MendesRodrigues:2011bc,Metcalfe:1997jy,Meziane:1999ci,Milberg:1998hv,Moles:2006ft,Montgomery:2004wq,Mooney:1978dl,Morin:2011ih,Moya:2008ep,Muller-landau_interspecific_2004,Muller:1990di,MullerLandau:2004dc,MullerLandau:2008eo,Mundim:2012eo,MunneBosch:2004ki,Murphy:1986vw,Murray:2013hd,MYERS:2007fo,myster_tree_2009,Nascimento:2005kl,Niemann:1995by,Niinemets:1999tw,Niinemets:2006jy,Niklas:2010bd,Nikula:2011ke,Norby:1989jc,Norby:2001go,OBERBAUER:1986ib,OKALI:1972uf,Oren:1986he,Osada:2001cq,Osada:2011ds,Osone:2008dr,Osone:2014hb,Osunkoya:1991en,Osunkoya:1994ip,Osunkoya:2010ef,Pages:2003ke,Paine:2015df,palik_vertical_1993,Paz:2005kx,Pere:2013gr,Pietsch:2014he,Piper:1986el,Pliura:2007we,POLLARD:1968wv,poorter_relationships_2008,Poorter:1986bb,Poorter:1989tx,Poorter:1990bt,Poorter:1990ku,Poorter:1991cf,Poorter:1991ki,Poorter:1992hg,Poorter:1994em,Poorter:1995jn,Poorter:1996kt,Poorter:1998uf,Poorter:1999fp,Poorter:1999wd,Poorter:2001fj,Poorter:2002uj,Poorter:2003dn,Poorter:2005dj,Poorter:2006kw,Poorter:2006vb,Poorter:2008iu,Poorter:2009ia,Poorter:2010co,Poorter:2012if,Popma:1988tv,PORTSMUTH:2007kn,Prentice:1991dz,primack_growth_1985,Prior:2004cv,Pugnaire:1999ww,Queenborough:2013jf,Quero:2008jg,Ralanguageanden:2014wf,Read:2011du,Reed:2003cx,Rees:2010gk,Reich:1987fh,Reich:1991kf,Reich:1992wm,Reich:1994bt,Reich:1995cb,Reich:1998ir,Reich:1998ja,Reich:1998ti,Reich:1998vb,Reich:1999gp,Reich:2003gm,Reich:2003jy,Reich:2014ho,Rice:1989ex,Rincon:1993cp,Rincon:1994da,Roderick:2000id,Rohula:2014cp,Rosenberg:2005hk,Rosenthal:1979do,Rossatto:2009gq,Rossi:2006ky,Roumet:1996jb,Rowland:2014bw,Rozendall:2006hm,Ruger:2011kv,Ruger:2012jv,Ruger:2012jva,RuizRobleto:2005hc,russo_interspecific_2008,Ryser:1996fo,Ryser:2014vo,Sack:2001ev,Sack:2004hm,Sack:2013ku,saldana-acosta_seedling_2009,SaldanaAcosta:2008jv,SalgadoLuarte:2010gg,SalgadoLuarte:2012ci,SanchezGomez:2006kg,Santiago:2004bn,Santiago:2007dw,Santiago:2007wi,Santos:2012gt,Saverimuttu:1996ih,Scheiter:2013ed,Schererlorenzen:2007ie,Schlapfer:1996fs,Scholes:1997vz,Schulze:2006ww,schumacher_influence_2009,Sellin:2013fi,Senevirathna:2003un,Shen:2014fw,Shinano:2001wr,Shipley:1990js,Shipley:2000jv,Shipley:2002ek,Shipley:2002fs,Shipley:2006dx,Shipley:2006ie,Sillett:2010ck,Soriano:2011ep,South:1991wn,Srivastava:2009we,stahl_whole-plant_2013,Stephenson:2014ek,sterck_plasticity_2013,sterck_sapling_2014,Sterck:2001ii,Sterck:2006wk,Sterck:2011eh,StGermain:2008fi,Stratton:2001ck,Sugiura:2011kc,Sugiyama:2005gx,Sungpalee:2009bh,Suzuki:1999id,svenning_seedling_2008,Swanborough:1996im,Swenson:2007iv,Swenson:2008ij,Syvertsen:1981uv,Tamme:2014wl,TanakaOda:2010dg,Taub:2002ku,Taylor:2001ur,terSteege:2001hy,Thomas:1996do,Thomas:1999bv,Thomas:2011br,Tjoelker:1998em,Tjoelker:1999gp,Tobner:2013cv,Tolley:1984ge,Tomlinson:2014im,Tullus:2012kw,turnbull_growth_2008,Turnbull:2012ew,Valentine:2012dz,Valio:2001tz,Valladares:2000bd,Valladares:2006bb,van_der_werf_importance_1998,van_dooren_delayed_1998,VanAndel:1989vq,vanderHeijden:2007kj,vanderWerf:1993by,VEENENDAAL:td,Veneklaas:1998uk,Veneklaas:2002dt,Venus:1979vd,Venus:1979wh,Vieira:2014cd,Vigl:2014hw,Villagra:2013do,Villar:1998iz,Villar:2006cf,VillarSalvador:2004th,Violle:2007jw,Vitasse:2009ke,Vogel:1988ux,Walczynska:2012hv,Wallentin:2008iw,WALTER:2008hc,walters_are_1996,walters_low-light_1999,Walters:1993eu,Walters:1993hf,Walters:2000tk,Wang:1998cs,Waring:1985ii,Warren:2005bc,Watling:1997ep,Watling:1997id,Weber:2008im,Weedon:2009ko,Weiher:1999js,West:2003fo,Westbrook:2011ja,Westoby:1998ug,Westoby:2002ft,Westoby:2006dm,Westoby:2009ch,Whale:1985to,White:2007gs,Wikberg:2004hl,Wikstrom:1995dc,Wilson:1999dm,Wright:1998ub,Wright:1999ds,Wright:1999eha,Wright:2000kw,Wright:2001gb,Wright:2003kb,Wright:2004jb,Wright:2005iv,Wright:2010tp,Xiong:2000hw,Xiong:2001ep,Xiong:2001es,Xu:2014cn,Yan:2008vk,Yang:1994cf,Yang:2010ek,Yang:2014js,yavitt_seedling_2008,Yeboah:2013jh,yetter_height_1986,Zhang:1995bh,Zhang:1995dz,Zhang:2011fe,Zvereva:2008jm}.
 

### 2016-01-22 analysis.R

@@ -19,8 +19,7 @@ library("downloader")
 download_baad("downloads/baad.rds")
 paper_bib <- read.bib("references/paper.bib")
 meta_bib <- read.bib("references/metaanalyses.bib")
-combined_bib <- merge_bib_files(meta_bib, paper_bib)
-write.bib(combined_bib, file = "output/refs.bib")
+read_bib <- read.bib("references/read.bib")
 AllData <- clean_raw_data("data/CompileData.csv")
 CleanData <- standardise_data(AllData)
 CompleteData <- build_complete_data(CleanData)
@@ -33,13 +32,12 @@ CompleteData_rgr <- subset_growth(CompleteData_inter, "RGR")
 CompleteData_agr <- subset_growth(CompleteData_inter, "AbGR")
 GCi <- list_by_trait(CompleteData_inter)
 GIi <- list_by_trait(IdealData)
-knitr::knit("ms_suppinfo.Rnw", "ms_suppinfo.tex")
 GIrgr <- list_by_trait(IdealData_rgr)
 GIagr <- list_by_trait(IdealData_agr)
 GCrgr <- list_by_trait(CompleteData_rgr)
 GCagr <- list_by_trait(CompleteData_agr)
 Snapshot <- snapshot_websci("data/ref.traits/WebSci_all.csv")
-knitr::knit("ms_snapshotinfo.Rnw", "ms_snapshotinfo.tex")
+knitr::knit("ms-suppinfo.Rnw", "ms-suppinfo.tex")
 pdf("output/Fig1.pdf", height = 3L, width = 4L)
 figure_1(CleanData)
 dev.off()
@@ -83,6 +81,9 @@ dev.off()
 pdf("output/FigA9.pdf")
 figure_A9(GCi)
 dev.off()
+`combined_bib{1}` <- merge_bib_files(meta_bib, paper_bib)
+combined_bib <- merge_bib_files(`combined_bib{1}`, read_bib)
+write.bib(combined_bib, file = "output/refs.bib")
 `RCi{1}` <- EffectSizeSum(CompleteData_inter)
 RCi <- list_by_trait(`RCi{1}`)
 `RIi{1}` <- EffectSizeSum(IdealData_rgr)
@@ -90,4 +91,5 @@ RIi <- list_by_trait(`RIi{1}`)
 pdf("output/FigA5.pdf", height = 6L, width = 5L)
 figure_A5(RIi, RCi)
 dev.off()
[…]

### 2016-01-22 MS.tex
clarify list of outsanding issues, including in the theoretical sections

@@
 \input{ms-common-defs}
-
 \date{}
-
-% Todo:
-% Ditch abbrvos for SLA, wood density, Hmax?
-% Fix plots
-%   -- major revision of code -- > lots of repetition, hard to follow
-%   -- Figure 2: add * against traits used in meta-analysis: no
-% - seach on XXX, footnote
 
@@
 \mstype{Research Article}
-\keywords{maximum height, photosynthetic rate, ontogenetic stage, functional trait, growth strategy, seed mass, specific leaf area, wood density}
+\keywords{maximum height, photosynthetic rate, ontogenetic stage, growth strategy, seed mass, specific leaf area, wood density}
 
@@
 \item We propose that traits should influence growth in a way that depends on the size of individual plants.
-We outline mechanisms and hypotheses based on new theoritical work, and test these predictions in tree species using a meta-analysis of 103 studies ($>$ 500 correlations) for five traits (specific leaf area, wood density, maximum height, seed mass and maximum assimilation rate).
+We outline mechanisms and hypotheses based on new theoretical work, and test these predictions in tree species using a meta-analysis of 103 studies ($>$ 500 correlations) for five traits (specific leaf area, wood density, maximum height, seed mass and maximum assimilation rate).
 We also recorded data for 14 others traits commonly used in the trait literature.
-To capture the effects of plant size, we tested for a shift in the direction of correlation between growth rates and traits across three ontogenic stages: seedling, sapling and adult.
+To capture the effects of plant size, we tested for a shift in the direction of correlation between growth rates and traits across three ontogenetic stages: seedling, sapling and adult.
 
-% Recent theoretical work ? instead of new theory?
-
-\item Results were consistent with predictions, even with some limitations arising from unequal numbers of observation across stages.
+\item Results were consistent with predictions, even with some limitations arising from unequal numbers of observation across ontogenetic stages.
 Specific leaf area was correlated with relative growth rate (RGR) in seedlings but not in adult plants.
 Correlations of growth with wood density and assimilation rate were not affected by stage.
-Seed mass and maximum height were correlated with RGR only in one plant stage category: seedlings and adults, respectively.
-\item Despite a sizeable literature on traits and growth, major knowledge gaps across size still exist; for one-third of traits the majority ($>$ 75\%) of correlations with growth come from a single stage.
-Clearly, there is scope for strengthening our understanding on the link between traits and growth through adding further empirical studies for traits and size classes underrepresented in the literature.
+Seed mass and maximum height were correlated with RGR only in one ontogenetic stage category: seedlings and adults, respectively.
 
-% not sure to keep the end of this sentence
+\item Although we were able to confirm several of our theoretical predictions, major knowledge gaps size still exist, despite a sizeable literature on traits and growth.
+For example, for one-third of the trait considered, the majority ($>$ 75\%) of reported correlations with growth came from a single ontogenetic stage.
 
@@
 Our understanding of plant strategies should shift away from attributing species as having slow or fast growth throughout their life, in favour of attributing growth trajectories.
-
-%Clearly, there is scope for strengthening our understanding on the link between traits and growth through adding further empirical studies for traits and size-classes underrepresented in the literature.
-
 \end{enumerate}
-
-\clearpage
 
@@
 
-Meanwhile the possibility has been raised that trait-growth correlations may change systematically with size \citep{King-1999,Falster:2011ii, Ruger:2012jv, Iida:2014ep, Iida:2014hq}.
-Size has long been known to play a central role in organismal design and function \citep{Vogel:1988ux, Vogel:2003wb}, including that of trees \citep{Farnsworth:1995im, Givnish:1995ta}.
-As plants grow larger, a greater amount of the energy is devoted towards building and maintaining non-photosynthetic tissues \citep{Givnish:1995ta}.
+Meanwhile the possibility has been raised that trait-growth correlations may change systematically with size \citep{King-1999, Falster:2011ii, Ruger:2012jv, Iida:2014ep, Iida:2014hq}.
+Size has long been known to play a central role in organism design and function \citep{Vogel:1988ux, Vogel:2003wb}, including that of trees \citep{Farnsworth:1995im, Givnish:1995ta, King-2011}.
+As plants grow larger, a greater amount of the energy is devoted towards building and maintaining non-photosynthetic tissues \citep{Givnish:1995ta,King-2011}.
 A recent model by \citet{Falster:2011ii} suggests this change shifts the benefits and costs of some trait-based trade-offs, such that the net effect of the trait on growth changes with size.
@@
 To address these questions we used a meta-analytic approach, compiling data from diverse studies reporting correlation coefficients between traits and growth.
-While most studies investigating the link between traits and growth have not primarily been concerned with the effects of plant size, they have generally reported trait-growth correlations for identifiable stage classes (i.e.
+While most studies investigating the link between traits and growth have not primarily been concerned with the effects of plant size, they have generally reported trait-growth correlations for identifiable ontogenetic stages (i.e.
 seedling, sapling, and adult).
-We therefore used plant stage as a surrogate for plant size.
+We therefore used ontogenetic stage as a surrogate for plant size.
 We focused on tree and woody species since the mechanistic model used to assess our predictions is most applicable to these growth forms.
@@
 
-Based on the above model and this single assumption about growth, we outline five hypotheses, which arise by considering the influence of trait variation on elements of equations  \ref{eq:eq0}-\ref{eq:eq4} (see Table \ref{tab:trade-offs}) and how these may interact with plant size.
+Based on the above model and this single assumption about growth, we outline five hypotheses that arise by considering the influence of trait variation on elements of equations  \ref{eq:eq0}-\ref{eq:eq4} and how these may interact with plant size (see Table \ref{tab:trade-offs}).
 These hypotheses reflect a direct mechanistic causation between traits and growth rate.
 It is possible that other correlations may arise indirectly.
-Nevertheless, for purposes of this paper we adopt working hypotheses arising only from direct mechanistic causation.
-With only XXX exception, the predicted effects of the trait are also similar when growth is expressed on relative of absolute terms, and as diameter, height or mass growth (Table \ref{tab:trade-offs} (TRUE XXXX?).
-
-\footnote{The correlation with RGR$_{\rm mass}$ is negative but becomes positive with AGR$_{\rm mass}$.
-For SLA, WD, Hmax, and Aarea, the direction of the predicted relationship is not affected by the growth measurement used.
-However RGR and AGR are fundamentally different for a lot of ecologists.
-So we adopted a two steps approach, first we were conservative by focusing exclusively on RGR, then we compared results with those of a more inclusive dataset with both RGR and AGR.
-=> We have different expectation for SLA in AGRmass for seedling: but none of our data are in AGRmass, they are mainly in RGRmass (Fig.
-\ref{fig:figA8}).
-Why a change with WD when it is measured in mass?
-All WD seedling are measured in RGRmass, and there are some mass data for both other stages too.
-}
+Nevertheless, for purposes of this paper we adopt as working hypotheses only those arising from direct mechanistic causation.
+Moreover, we consider how predictions may vary when expressed on absolute and relative terms, for each of height, diameter, and mass-based growth (see Table \ref{tab:trade-offs}).
+For many trait and growth combinations, the predicted effect of the trait on growth is similar when expressed on relative and absolute terms.
+However, this is not true for all traits (details given below).
+We therefore adopted a two-stage approach to our analysis, whereby we first assess patterns based on measurements of relative growth rate.
 
@@
 \ref{eq:daldmt}.
-For mass growth, cheaper leaf construction (high SLA) translates directly into faster relative growth rate in seedlings (See Appendix \ref{app:growth-equation} eq.
-\ref{eq:eq1_seedlings_RGR}).
 As plants increase in size, however, the cost of building sapwood ($\frac{\ud M_{\rm s}}{\ud A_{\rm l}}$) increases disproportionately, decreasing the benefit of cheaper leaf construction in eq.
@@
 Consequently, the relative effect of leaf turnover comes to dominate at larger sizes, and as such, the effect of SLA on height and diameter growth shifts from positive to negative as plants increase in size.
+A similar shift is expected for growth in mass when expressed in relative terms.
+However, when expressed as absolute growth, the predicted relationship is negative.
+This occurs because of the increased turnover of high SLA species.
 
@@
 
-Cheaper stem construction (low WD or stem density) increases the marginal rate of leaf deployment per total mass increment ($\frac{\ud A_{\rm l}}{\ud M_{\rm t}}$), and consequently increases growth rate in leaf area, height, and diameter (eqs.
+Cheaper stem construction (low WD or stem density) increases the marginal rate of leaf deployment per total mass increment ($\frac{\ud A_{\rm l}}{\ud M_{\rm t}}$), and consequently increases growth rate in height and diameter (eqs.
 \ref{eq:eq2}-\ref{eq:eq4}; Table \ref{tab:trade-offs}).
 Disadvantages associated with cheap stem construction take the form of higher mortality and so are not reflected in growth equations.
-Under this scenario, wood density is negatively correlated to growth rate across all plant stages.
+Under this scenario, wood density is negatively correlated to growth rate across all ontogenetic stages.
 Because the relative expenditure on stem compared to leaf increases as plants grow larger, the relationship between WD and growth may also strengthen in larger plants.
+A similar shift is expected for growth in mass when expressed in relative terms.
+However, when expressed as absolute growth, the predicted relationship is non-significant \citep[see also][]{Enquist-1999}.
 
@@
 But once some species begin to produce seed, then species closer to their Hmax value are expected to be allocating more to seed production and less to vegetative growth.
-Hence when comparing across plants at a given size, species with smaller Hmax are expected to show slower vegetative growth rates (Table \ref{tab:trade-offs}).
+Hence when comparing across plants at a given size, species with smaller Hmax are expected to show slower vegetative growth rates.
+Similar correlations are expected no matter what measure of  growth is used (Table \ref{tab:trade-offs}).
 
@@
 The main effect of increased seed size is to produce a larger overall seedling.
-Under similar light conditions, RGR decreases with size because the ratio of leaf area to total biomass decreases along plant size.
-Thus, larger seedlings are predicted to have a lower RGR during the earliest phases of growth \citep{Turnbull:2012ew}.
-However, as plants are growing we expect the effect of this initial size to be minimal, and the correlation between seed size and growth rate should disappear.
+Under similar light conditions, larger seedlings are therefore predicted to have larger absolute growth rates.
+However, because the ratio of leaf area to total biomass decreases with plant size, larger seedlings are predicted to have lower mass-based growth rates during the earliest phases of growth \citep{Turnbull:2012ew}.
+Yet, as plants grow, we expect the effect of this initial size difference to be minimal, and the correlation between seed size and growth rate should therfore disappear.
 Thus for larger plants, seed mass is not expected to have any distinct influence on growth rates  (Table \ref{tab:trade-offs}).
-However, the predicted relationship between growth and seed mass in seedlings reverses if AGR$_{\rm mass}$ is used instead of RGR$_{\rm mass}$.
 
@@
 
-We expect greater photosynthetic capacity to translate into faster growth rates by increasing the rate of biomass production (Table \ref{tab:trade-offs}), at least at high light where Aarea is measured.
+We expect greater photosynthetic capacity to translate into faster growth rates by increasing the rate of biomass production (Table \ref{tab:trade-offs}), at least at high light where Aarea is typically measured.
 This effects occurs within the term  $\frac{\ud B}{\ud t} $ in the above model.
@@
 It is uncertain how much this effect might translate to faster growth in low light.
-It might greatly depend on the level of light available.
-
-\clearpage
 
@@
 
-% bib <- bibtex::read.bib("references/metaanalyses.bib")
-% paste(sort(names(x$keys)), collapse = ', ')
-% These studies dropped because not in list of top traits:
-% Bohlman:2006eo, Cochard:2007bn, Coley:1983hk,  Comas:2002wt, Comas:2004jza, King:2006dg, Poorter:2001fj, Schulze:2006ww,  Tjoelker:1999gp, Tobner:2013cv,
+\subsubsection*{Ontogenetic stage categories}
 
-\subsubsection*{Plant stage categories}\label{plant-stage-categories}
-
-We used categorical groupings by plant ``stage'' to test our hypotheses regarding the effects of traits on growth rates.
+We used categorical groupings by ontogenetic ``stage'' to test our hypotheses regarding the effects of traits on growth rates.
 The authors of the 103 articles used in this analysis reported their plants as belonging to any of five different stages: ``seedling'', ``juvenile'', ``sapling'', ``adult'', ``mixed''.
@@
 \ref{fig:fig2}).
-Only 7 of 103 articles were ambiguous on their plant stage attribution.
+Only 7 of 103 articles were ambiguous on their ontogenetic stage attribution.
 Half of these equivocal cases involved the juvenile category.
@@
 
-We tested an effect of plant stage on the relationship between growth rate and traits using a mixed-effect model, in which it was assumed that studies within a stage shared a common mean effect, but that there was also random variation among studies, in addition to sampling variation \citep{Zuur:2009cfa}.
+We tested an effect of ontogenetic stage on the relationship between growth rate and traits using a mixed-effect model, in which it was assumed that studies within a stage shared a common mean effect, but that there was also random variation among studies, in addition to sampling variation \citep{Zuur:2009cfa}.
 Inclusion of this random effect allowed us to account for heterogeneity among studies, for example in experimental type, and vegetation type.
@@
 
-\clearpage
-
 \section*{Results}\label{results}
@@
 \ref{fig:fig1}).
-We had thought it likely that for some traits correlations would be reported only for one size class.
+We had thought it likely that for some traits, correlations would be reported only for one growth stage.
 But this limitation applied only for LAR and NARmass, where studies appeared confined to seedling stages.
-However, for a majority of traits the number of observations across stage was higthly unbalanced; for one-third of the 19 traits $>$ 75\% of correlations with growth reported come from a single stage (Fig.
+However, for a majority of traits the number of observations across stage was highly unbalanced; for one-third of the 19 traits $>$ 75\% of correlations with growth reported come from a single stage (Fig.
 \ref{fig:fig1}).
@@
 For Aarea, results were consistent with a positive correlation with RGR at seedling stage.
-However, no conclusion can be drawn about a change along plant stages; as only four correlation coefficients were reported for this trait, and three of these were measured at the seedling stage (Fig.
+However, no conclusion can be drawn about a change along ontogenetic stages; as only four correlation coefficients were reported for this trait, and three of these were measured at the seedling stage (Fig.
 \ref{fig:fig3}e).
@@
 
-We now report results from the entire dataset to determine if additional data would alter or reinforce our conclusions, drawn sometimes with limited replicates.
+We now report results from the entire dataset.
+Our aim is to determine if additional data alters or reinforce the above conclusions, by increasing replication.
 This entire dataset included correlations measured with both AGR and RGR (Fig.
 \ref{fig:fig4}), across at least two species (but measured using several individuals), and did not control for the source of trait or growth (i.e.
-trait could be measured on a different stage) or environmental conditions.
+trait could be measured on a different ontogenetic stage to growth data) or environmental conditions.
 The relaxed criteria considerably increased the number of replicates, from $n = 137$ to $n = 267$ correlations across 93 articles.
@@
 
-Results from the entire dataset reinforced our conclusions for both SLA and WD, set appart alternative explanations for seed mass, and allowed to compare correlations with growth along plant stages for Aarea.
+Results from the entire dataset reinforced our conclusions for both SLA and WD, set apart alternative explanations for seed mass, and allowed us to compare correlations with growth along ontogenetic stages for Aarea.
 For SLA and WD, the number of replicates doubled by using the entire dataset, and effect sizes and overall results were similar to those reported above using the ''ideal'' subset (Fig.
@@
 \ref{fig:fig4}c, and model fit improved when stage was incorporated).
-For Aarea, the additional replicates in the entire dataset allowed us to compare the effect size across plant stage.
+For Aarea, the additional replicates in the entire dataset allowed us to compare the effect size across ontogenetic stage.
 The results were consistent with the prediction for a positive correlation with RGR across adult and seedling stages (Fig \ref{fig:fig4}e; CI not overlapping zero).
@@
 For other traits, effect size were generally consistent between RGR and AGR when both measurement were available.
-Some differences occured but they were not easily attributed to any single cause.
+Some differences occurred but they were not easily attributed to any single cause.
 For instance for WD, the correlation at juvenile stage shifted from negative with RGR to non significant with AGR (i.e CI included zero, Fig.
@@
 
-In total, 103 articles published between 1983 and 2014, and containing 551 correlations linking growth rate to any of the 19 traits across a range of plant stages were identified.
+In total, 103 articles published between 1983 and 2014, and containing 551 correlations linking growth rate to any of the 19 traits across a range of ontogenetic stages were identified.
 Data reported here were variable in multiple ways.
@@
 \ref{fig:figA7}).
-The extent of heterogeneity was high, but was substantially explained by our core hypothesis of a plant stage effect for SLA and seed mass (Appendix \ref{app:supp_info_analyses}).
+The extent of heterogeneity was high, but was substantially explained by our core hypothesis of an effect of ontogenetic stage for SLA and seed mass (Appendix \ref{app:supp_info_analyses}).
 There was no indication of a temporal change in the effect size being reported within stages (Appendix \ref{app:supp_info_analyses}, Fig.
@@
 While the possibility has been raised recently that trait-growth correlations may change systematically with size \citep{Falster:2011ii, Ruger:2012jv, Iida:2014ep, Iida:2014hq}, this is the first time that specific mechanistic hypotheses have been corroborated against a wide array of existing studies.
-Meta-analysis allowed us to generalize and thus to reach a consensus about the effect of traits on growth.
+Meta-analysis allowed us to generalize and thus to reach a consensus about the effect of traits on growth, even if our conclusions were at times biased toward a particular growth stage, due to uneven coverage of the empirical literature across trait-growth-stage combinations.
 Growth rates were already known to change with size through ontogeny \citep{Condit:1993hd, Clark:1999ed, Herault:2011dd}, in other words individual plants follow a growth trajectory.
@@
 This is a shift in outlook compared to much present thinking, whereby traits are seen as rendering species fast-growing or slow-growing throughout life.
-
-TODO: XXXX Something about limited amount of data (add the following arguments:)
-Despite a sizeable literature on traits and growth, there are major knowledge gaps on the link between trait and growth.
-The number of correlations reported for each 19 traits is generally unbalanced in favor of a particular stage, either for historical or practical reasons.
-This means that the knowledge we have on each trait is often biased toward a particular size-classe.
-
-TODO: XXX some thing about qualitative predictions \ref{Falster-2016}
 
@@
 
-It has previously been noted that the correlation of SLA with growth disappears among saplings and larger trees (\citealt{Wright:2010tp} for Barro Colorado Island forest, Panama), and this meta-analysis generalises that result.
-Several authors have suggested that the disappearance of SLA's influence on growth might be due to a disproportionate accumulation of leaf area by low SLA species \citep{Reich:1992wm,Poorter:2008iu,Wright:2010tp}, yet it remains unclear whether such a mechanism works as intended.
-\footnote{R3:  It is difficult to figure out what this statement is referring to.
-Were these publications referring to an increase in LAI and hence self-shading in large plants with high SLA as compared to large plants with low SLA?} Further, the assumed empirical relationship between SLA and total leaf area does not hold true as a generalisation across large number of species \citep{Duursma-2015}.
+While it has previously been noted that the correlation of SLA with growth rate disappears among saplings and larger trees (\citealt{Wright:2010tp} for Barro Colorado Island forest, Panama), our meta-analysis generalises that result.
+Several authors have suggested that the disappearance of SLA's influence on growth might be due to a disproportionate accumulation of leaf area individuals with low SLA \citep{Reich:1992wm, Poorter:2008iu,Wright:2010tp}, yet it remains unclear whether such a mechanism works as intended.
+Further, the assumed empirical relationship between SLA and total leaf area does not hold true as a generalisation across large number of species \citep{Duursma-2015}.
+In another modelling study, the SLA optimising growth rate was found to decrease with plant size, because of cross connections with the amount of self-shading in the crown and the increase in support costs in larger plants.
 In the model described here, the mechanism is slightly different: high-SLA species incur faster leaf turnover, the cost of which outweighs the benefits of cheap leaf construction at larger sizes.
-\footnote{TODO XXX R3:That field-grown seedlings generally have higher SLAs than do trees of the same species under similar high-light environments (King 1999) is consistent with both our observed and predicted growth benefits of high SLA for seedlings.}
 
@@
 
-For WD the meta-analysis showed negative correlation with RGR across all plant stages, as previously reported from individual studies \citep{Wright:2010tp,Ruger:2012jv}.
+For WD the meta-analysis showed negative correlation with RGR across all ontogenetic stages, as previously reported from individual studies \citep{Wright:2010tp,Ruger:2012jv}.
 It should be noted however that there are few data available to test this proposition at seedling stage (n=1-5).
@@
 For example, several papers have suggested that correlations between Hmax and growth rate may arise via cross-correlation with other traits such as WD \citep{Thomas:1996do, Poorter:2006vb, Wright:2010tp}.
+These studies also suggest species towards one end of a trait spectrum may generally be found in better light.
 Similarly, effects of seed mass on growth have been suspected to be mediated via other traits \citep{Shipley:1990js,Westoby:2002ft,Poorter:2006vb}.
@@
 For example, instead of a positive relationship that disappeared with plant size, \citet{Iida:2014ep} found SLA was negatively correlated with RGR at small size and positively correlated with RGR at larger sizes.
-Similarly, instead of a negative correlation between WD and growth across all plant stages, some studies found a negative correlation at small size that disappeared when trees were larger \citep{Iida:2014ep,Iida:2014hq}.
+Similarly, instead of a negative correlation between WD and growth across all ontogenetic stages, some studies found a negative correlation at small size that disappeared when trees were larger \citep{Iida:2014ep,Iida:2014hq}.
 The authors explained the switch in directionality by changes in light and water condition up the vertical profile within a forest: larger trees reached a position in the canopy where they were released from light limitations, other resources such as water may have become limiting, and the performance of trees may then have been regulated by different traits.
@@
 
-Clearly there is much scope for strengthening our understanding of correlations between traits and growth through (1) adding further empirical studies for traits and size-classes with weaker representation, (2) accounting more satisfactorily for variables such as light, and (3) expressing plant sizes on continuous scales of mass or height rather than through the approximate and partly subjective categories unavoidably adopted here.
+Clearly there is much scope for strengthening our understanding of correlations between traits and growth through (1) adding further empirical studies for traits and size-classes with weaker representation, (2) accounting more satisfactorily for variables such as light, (3) expressing plant sizes on continuous scales of mass or height, rather than through the approximate and partly subjective categories unavoidably adopted here, and (4) moving beyond the qualitative model predictions evaluated here towards quantitative predictions, e.g.
+via the recently published \texttt{plant} model \citep{Falster-2016}.
 Additional data are specifically required in small plants (seedling and sapling) for WD and Hmax, and in large plants (adult and sapling) for Aarea and more broadly for all traits requiring a measure of whole plant biomass (e.g.
@@
 
-\clearpage
 \linespread{1}
-
 \bibliography{output/refs-main}\label{references}
@@
 \includegraphics[width=15cm,height=20cm,keepaspectratio]{output/Fig3.pdf}
-\caption{The relationship between relative growth rates (RGR) and traits changes with plant stage and trait.
-Plots show the effect size (+ 95\% confidence intervals; CI) for the average correlation across $>$10 species, by plant stage.
+\caption{The relationship between relative growth rates (RGR) and traits changes with ontogenetic stage and trait.
+Plots show the effect size (+ 95\% confidence intervals; CI) for the average correlation across $>$10 species, by ontogenetic stage.
 Effect size is a standardized measure of the deviation of correlation coefficient from zero (Fisher's z-transformed).
@@
 \includegraphics[width=15cm,height=20cm,keepaspectratio]{output/Fig4.pdf}
-\caption{Relationships between relative (RGR) and/or absolute (AGR) growth rates and traits along plant stage.
+\caption{Relationships between relative (RGR) and/or absolute (AGR) growth rates and traits along ontogenetic stage.
 The legend is identical to Fig 3, with two exceptions.
@@
 \caption{Hypothesised effects of traits on key elements of plant function determining growth rate, as described in eq.
-\ref{eq:eq0}-\ref{eq:eq4}.
+\ref{eq:eq0} -- \ref{eq:eq4}.
 Arrows indicate the effect an increase in trait value would have on each element of the equations, with dashes indicating no effect.
@@
   \begin{tabular}{lllcccccc}
-  & & & & SLA & WD & Hmax & Seed mass & Aarea \\ \hline
+  \hline
+  & & & {\bf Symbol} & {\bf SLA} & {\bf WD} & {\bf Hmax} & {\bf Seed mass} & {\bf Aarea} \\ \hline
   \\
-  \multicolumn{9}{ l } {\textbf{Elements of equations \ref{eq:eq0}-\ref{eq:eq4}}}  \\
-  & \multicolumn{2}{ l } {Leaf deployment per mass}  & $\frac{\ud A_{\rm l}}{\ud M_{\rm t}}$ & \\
+  \multicolumn{9}{ l } {\textbf{Elements of equations \ref{eq:eq0} -- \ref{eq:eq4}}}  \\
+  & \multicolumn{2}{ l } {Leaf deployment per mass}  & $\ud A_{\rm l} / \ud M_{\rm t}$ & \\
     & &     \tabitem leaf  &  & $\uparrow$ & - & - & - & - \\
@@
     & &     \tabitem root & & - & - & - & - & - \\
-  & \multicolumn{2}{ c } {Allocation to vegetative growth} & $\frac{\ud M_{\rm t}}{\ud B}$ & - & - & $\uparrow$ & - & - \\
+  & \multicolumn{2}{ c } {Allocation to vegetative growth} & $\ud M_{\rm t} / \ud B$ & - & - & $\uparrow$ & - & - \\
   & & & & & & \\
-  & \multicolumn{2}{ l } {Net live biomass production} & $\frac{\ud B}{\ud t}$ & & & & & \\
+  & \multicolumn{2}{ l } {Net live biomass production} & $\ud B / \ud t$ & & & & & \\
   & &     \tabitem photosynthesis & & - & - & - & - & $\uparrow$  \\
@@
   & &     \tabitem leaf turnover & & $\downarrow$ & - & - & - & - \\
-  & \multicolumn{2}{ l } {Architecture} & $\frac{\ud H}{\ud A_{\rm l}}$ & - & - & - & - & - \\
-  & \multicolumn{2}{ l } {Sapwood area per leaf} & $\frac{\ud A_{\rm ss}}{\ud A_{\rm l}}$ & - & - & - & - & - \\
-  & \multicolumn{2}{ l } {Sapwood turnover} & $k_{\rm ss}$ & - & - & - & - & - \\ \hline
+  & \multicolumn{2}{ l } {Architecture} & $\ud H / \ud A_{\rm l}$ & - & - & - & - & - \\
+  & \multicolumn{2}{ l } {Sapwood area per leaf} & $ \ud A_{\rm ss} / \ud A_{\rm l}$ & - & - & - & - & - \\
+  & \multicolumn{2}{ l } {Sapwood turnover} & $k_{\rm ss} \, A_{\rm ss}$ & - & - & - & - & - \\ \hline
   \\
   \multicolumn{9}{ l } {\textbf{Predicted effect on plant growth rate} (small plant {\sepp} large plant)} \\
-  & \multicolumn{2}{ l } {in mass, $M_{\rm t}$} \\
-  & & \tabitem{Absolute} & & $-$\sepp$\downarrow$ & $-$\sepp$-$ &  $-${\sepp}$\uparrow$ & $\uparrow${\sepp}$-$ & $\uparrow${\sepp}$\uparrow$ \\
-  & & \tabitem{Relative} & & $\uparrow${\sepp}$\downarrow$ & $-${\sepp}$-$ &  $-${\sepp}$\uparrow$ & $\downarrow${\sepp}$-$ & $\uparrow${\sepp}$\uparrow$ \\
-  & \multicolumn{2}{ l } {in height, $H$} \\
-  & & \tabitem{Absolute} & & $\uparrow${\sepp}$\downarrow$ & $\downarrow${\sepp}$\downarrow$ & $-${\sepp}$\uparrow$ & $\uparrow${\sepp}$-$ & $\uparrow${\sepp}$\uparrow$ \\
-  & & \tabitem{Relative} & & $\uparrow${\sepp}$\downarrow$ & $\downarrow${\sepp}$\downarrow$ & $-${\sepp}$\uparrow$ & $\downarrow${\sepp}$-$ & $\uparrow${\sepp}$\uparrow$ \\
-  & \multicolumn{2}{ l } {in diameter, $D$} \\
-  & & \tabitem{Absolute} & & $\uparrow${\sepp}$\downarrow$ & $\downarrow${\sepp}$\downarrow$ & $-${\sepp}$\uparrow$ & $\uparrow${\sepp}$-$ & $\uparrow${\sepp}$\uparrow$ \\
-  & & \tabitem{Relative} & & $\uparrow${\sepp}$\downarrow$ & $\downarrow${\sepp}$\downarrow$ & $-${\sepp}$\uparrow$ & $\downarrow${\sepp}$-$ & $\uparrow${\sepp}$\uparrow$ \\
+  & \multicolumn{2}{ l } {in mass} \\
+  & & \tabitem{Absolute} & $\ud M_{\rm t} / \ud t$ & $\downarrow$\sepp$\downarrow$ & $-$\sepp$-$ &  $-${\sepp}$\uparrow$ & $\uparrow${\sepp}$-$ & $\uparrow${\sepp}$\uparrow$ \\
+  & & \tabitem{Relative} & $\ud M_{\rm t} / \ud t / M_{\rm t}$ & $\uparrow${\sepp}$\downarrow$ & $\downarrow${\sepp}$\downarrow$ &  $-${\sepp}$\uparrow$ & $\downarrow${\sepp}$-$ & $\uparrow${\sepp}$\uparrow$ \\
+  & \multicolumn{2}{ l } {in height} \\
+  & & \tabitem{Absolute} & $\ud H / \ud t$ & $\uparrow${\sepp}$\downarrow$ & $\downarrow${\sepp}$\downarrow$ & $-${\sepp}$\uparrow$ & $\uparrow${\sepp}$-$ & $\uparrow${\sepp}$\uparrow$ \\
+  & & \tabitem{Relative} & $\ud H / \ud t / H$ & $\uparrow${\sepp}$\downarrow$ & $\downarrow${\sepp}$\downarrow$ & $-${\sepp}$\uparrow$ & $\downarrow${\sepp}$-$ & $\uparrow${\sepp}$\uparrow$ \\
+  & \multicolumn{2}{ l } {in diameter} \\
+  & & \tabitem{Absolute} & $\ud D / \ud t$ & $\uparrow${\sepp}$\downarrow$ & $\downarrow${\sepp}$\downarrow$ & $-${\sepp}$\uparrow$ & $\uparrow${\sepp}$-$ & $\uparrow${\sepp}$\uparrow$ \\
+  & & \tabitem{Relative} & $\ud D / \ud t / D$ & $\uparrow${\sepp}$\downarrow$ & $\downarrow${\sepp}$\downarrow$ & $-${\sepp}$\uparrow$ & $\downarrow${\sepp}$-$ & $\uparrow${\sepp}$\uparrow$ \\
 \hline

### 2016-01-22 ms-suppinfo.Rnw
clarify list of outsanding issues, including in the theoretical sections

@@
 
-For SLA, seed mass and Hmax, \Sexpr{round(fun_Heterogeneity.H(GCi[["SLA"]], ~stageRGR)$Hexplained,1)}\%, \Sexpr{round(fun_Heterogeneity.H(GCi[["Seedmass"]], ~stage)$Hexplained,1)}\% and \Sexpr{round(fun_Heterogeneity.H(GCi[["Hmax"]], ~stageRGR)$Hexplained, 0)}\% respectively of the total amount of heterogeneity were accounted for by including the plant stage as a moderator.
-For the other traits, the plant stage explained little or no part of the heterogeneity observed across studies ( WD: \Sexpr{round(fun_Heterogeneity.H(GCi[["WD"]], ~stage)$Hexplained, 0)}\% and Aarea: \Sexpr{round(fun_Heterogeneity.H(GCi[["Aarea"]], ~stage)$Hexplained, 1)}\% ).
+For SLA, seed mass and Hmax, \Sexpr{round(fun_Heterogeneity.H(GCi[["SLA"]], ~stageRGR)$Hexplained,1)}\%, \Sexpr{round(fun_Heterogeneity.H(GCi[["Seedmass"]], ~stage)$Hexplained,1)}\% and \Sexpr{round(fun_Heterogeneity.H(GCi[["Hmax"]], ~stageRGR)$Hexplained, 0)}\% respectively of the total amount of heterogeneity were accounted for by including the ontogenetic stage as a moderator.
+For the other traits, the ontogenetic stage explained little or no part of the heterogeneity observed across studies ( WD: \Sexpr{round(fun_Heterogeneity.H(GCi[["WD"]], ~stage)$Hexplained, 0)}\% and Aarea: \Sexpr{round(fun_Heterogeneity.H(GCi[["Aarea"]], ~stage)$Hexplained, 1)}\% ).
 These results were consistent with our expectations about a shift in the relationship between growth and traits across plant size for SLA, seed mass and Hmax, and the absence of an effect for WD and Aarea (see Theoretical expectation section).
@@
 Fig.
-\ref{fig:figA9} shows that for these three traits the publication years may be confounded with plant stage; correlation coefficients have been reported since 1993, but studies started to report data on adult stage only ten years later (around 2000-2007).
+\ref{fig:figA9} shows that for these three traits the publication years may be confounded with ontogenetic stage; correlation coefficients have been reported since 1993, but studies started to report data on adult stage only ten years later (around 2000-2007).
 
@@
 
-The temporal changes were confounded with a plant stage effect in our meta-analysis, but they did not jeopardize the stability of our conclusions.
+The temporal changes were confounded with a ontogenetic stage effect in our meta-analysis, but they did not jeopardize the stability of our conclusions.
 The conclusions of a meta-analysis conducted in different years should not differ from those reported here.

### 2016-01-22 ms-suppinfo.tex
clarify list of outsanding issues, including in the theoretical sections

@@
 
-For SLA, seed mass and Hmax, 41\%, 20.2\% and 17\% respectively of the total amount of heterogeneity were accounted for by including the plant stage as a moderator.
-For the other traits, the plant stage explained little or no part of the heterogeneity observed across studies ( WD: 9\% and Aarea: 0.1\% ).
+For SLA, seed mass and Hmax, 41\%, 20.2\% and 17\% respectively of the total amount of heterogeneity were accounted for by including the ontogenetic stage as a moderator.
+For the other traits, the ontogenetic stage explained little or no part of the heterogeneity observed across studies ( WD: 9\% and Aarea: 0.1\% ).
 These results were consistent with our expectations about a shift in the relationship between growth and traits across plant size for SLA, seed mass and Hmax, and the absence of an effect for WD and Aarea (see Theoretical expectation section).

### 2016-01-22 MS.tex
Remove abbreviations: RGR, AGR, WD, Hmax

@@
 \item Results were consistent with predictions, even with some limitations arising from unequal numbers of observation across ontogenetic stages.
-Specific leaf area was correlated with relative growth rate (RGR) in seedlings but not in adult plants.
+Specific leaf area was correlated with relative growth rate in seedlings but not in adult plants.
 Correlations of growth with wood density and assimilation rate were not affected by stage.
-Seed mass and maximum height were correlated with RGR only in one ontogenetic stage category: seedlings and adults, respectively.
+Seed mass and maximum height were correlated with relative growth rate only in one ontogenetic stage category: seedlings and adults, respectively.
 
@@
 The phrase ``plant ecological strategy'' refers to how species face common challenges of acquiring sufficient water, nutrients, and light for growth; and then ultimately replacing themselves with offspring.
-The idea that a strategy differences among species might involve fast versus slow growth goes back at least to \citet{Grime:1975gr}, who observed a wide spread of relative growth rate (RGR) among seedlings growing under favourable conditions.
-Seedling potential RGR has continued to be used as a major strategy indicator within Grime's CSR (Competitor -- Stress tolerator -- Ruderal) classification (e.g.
+The idea that a strategy differences among species might involve fast versus slow growth goes back at least to \citet{Grime:1975gr}, who observed a wide spread of relative growth rate  among seedlings growing under favourable conditions.
+Seedling potential relative growth rate has continued to be used as a major strategy indicator within Grime's CSR (Competitor -- Stress tolerator -- Ruderal) classification (e.g.
 \citealt{grime1979plant, Grime:1997wm}).
-Meanwhile partitioning of seedling RGR into different components showed that the trait specific leaf area (SLA) was typically the strongest source of variation between species \citep{Poorter:1989tx, Rees:2010gk}.
-From the 1990s a new style of ``trait ecology'' arose whereby measurable traits, including SLA, were used directly as strategy axes \citep{Westoby:2002ft}.
+Meanwhile partitioning of seedling relative growth rate into different components showed that the trait specific leaf area (SLA) was typically the strongest source of variation between species \citep{Poorter:1989tx, Rees:2010gk}.
+From the 1990's a new style of ``trait ecology'' arose whereby measurable traits, including SLA, were used directly as strategy axes \citep{Westoby:2002ft}.
 An approach via measurable traits made broad comparisons possible across continents, latitudes, and thousands of species.
@@
 
-In this paper, we investigate for five prominent traits (specific leaf area = SLA, wood or stem tissue density = WD, maximum leaf photosynthetic capacity per unit area = Aarea, asymptotic or maximum height = Hmax, and seed mass):
+In this paper, we investigate for five prominent traits (specific leaf area = SLA, wood (or stem) tissue density, maximum leaf photosynthetic capacity per unit area = Aarea, maximum (or asymptotic height), and seed mass):
 \begin{enumerate}
@@
 This model extends earlier efforts to model growth as a function of traits \citep{Lambers:1992bj,Cornelissen:1996hf,Wright:2000kw,Enquist:2007ek}.
-However, whereas earlier models focused solely on mass-based RGR and did not predict a change in effect of traits with size, the revised equations do allow for these effects, while also making predictions for both absolute and relative growth in any of mass (eq.
+However, whereas earlier models focused solely on mass-based relative growth rate and did not predict a change in effect of traits with size, the revised equations do allow for these effects, while also making predictions for both absolute and relative growth in any of mass (eq.
 \ref{eq:eq1}), height (eq.
@@
 
-\subsection*{H2: The relationship between WD and growth rate is expected to be negative across all plant sizes}
+\subsection*{H2: The relationship between wood density and growth rate is expected to be negative across all plant sizes}
 
-Cheaper stem construction (low WD or stem density) increases the marginal rate of leaf deployment per total mass increment ($\frac{\ud A_{\rm l}}{\ud M_{\rm t}}$), and consequently increases growth rate in height and diameter (eqs.
+Cheaper stem construction (low wood density or stem density) increases the marginal rate of leaf deployment per total mass increment ($\frac{\ud A_{\rm l}}{\ud M_{\rm t}}$), and consequently increases growth rate in height and diameter (eqs.
 \ref{eq:eq2}-\ref{eq:eq4}; Table \ref{tab:trade-offs}).
@@
 Under this scenario, wood density is negatively correlated to growth rate across all ontogenetic stages.
-Because the relative expenditure on stem compared to leaf increases as plants grow larger, the relationship between WD and growth may also strengthen in larger plants.
+Because the relative expenditure on stem compared to leaf increases as plants grow larger, the relationship between wood density and growth may also strengthen in larger plants.
 A similar shift is expected for growth in mass when expressed in relative terms.
@@
 
-\subsection*{H3: The relationship between Hmax and growth rate is expected to be absent in seedlings but to strengthen with increasing plant size}
+\subsection*{H3: The relationship between maximum height and growth rate is expected to be absent in seedlings but to strengthen with increasing plant size}
 
@@
 (\ref{eq:eq2}-\ref{eq:eq4}).
-For seedlings, where all individuals are investing solely in growth, we expect no influence of Hmax on growth (i.e.
+For seedlings, where all individuals are investing solely in growth, we expect no influence of maximum height on growth (i.e.
 $\frac{\ud M_{\rm t}}{\ud B} =1$).
-But once some species begin to produce seed, then species closer to their Hmax value are expected to be allocating more to seed production and less to vegetative growth.
-Hence when comparing across plants at a given size, species with smaller Hmax are expected to show slower vegetative growth rates.
+But once some species begin to produce seed, then species closer to their maximum height value are expected to be allocating more to seed production and less to vegetative growth.
+Hence when comparing across plants at a given size, species with smaller maximum height are expected to show slower vegetative growth rates.
 Similar correlations are expected no matter what measure of  growth is used (Table \ref{tab:trade-offs}).
 
-\subsection*{H4: The relationship between seed mass and RGR is negative in seedlings, but weakens with increasing size}
+\subsection*{H4: The relationship between seed mass and relative growth rate is negative in seedlings, but weakens with increasing size}
 
@@
 Initially we were interested to know whether data existed for a variety of traits; however the number of potential search terms made systemic searching for all these terms in Google Scholar impractical.
-A preliminary investigation of search results for a variety of traits on the Web of Science platform suggested that searching only on SLA and WD -- two of the most widely measured traits -- would capture $\sim$80\% of search records that would be returned by searching for a wider range of traits (see Appendix \ref{app:literature-snapshot}).
+A preliminary investigation of search results for a variety of traits on the Web of Science platform suggested that searching only on SLA and wood density -- two of the most widely measured traits -- would capture $\sim$80\% of search records that would be returned by searching for a wider range of traits (see Appendix \ref{app:literature-snapshot}).
 We therefore narrowed our searching to only cover these two main traits.
 
-Both Web of Science and Google Scholar databases were searched for records linking SLA and WD to growth rate.
+Both Web of Science and Google Scholar databases were searched for records linking SLA and wood density to growth rate.
 On Web of Science, we searched using  search terms: (``trait'' AND (``growth rate'' OR ``relative growth rate'')) AND (``tree*'' OR ``woody*''), where ``trait'' was either (``leaf mass per area'' OR ``specific leaf area'' OR ``leaf construction cost'') or (``wood density'' OR``WD'' OR ``wood specific gravity'' OR ``stem density'' OR ``stem specific density'' OR ``SSD'' ).
@@
 Individual studies had to report the following information to be included in our dataset: i) the relationship between growth and trait as a correlation coefficient, ii) the sample size and the number of species used to perform the correlation, and iii) the size or stage of plants.
-Despite searching only on SLA and WD, we recorded coefficient correlations for a list of 19 traits in total: the five for which we had prior expectations, plus any of 14 others commonly used in the trait literature.
-Where available, we also recorded the geographic coordinates, number of sites, experiment type (greenhouse, field experiment, forest, shade-house etc.), growth measure (relative or AGR measured using plant diameter, height or mass), vegetation type, life form (tree, woody or mixed with herbaceous species etc.), biological scale (interspecific, intraspecific or intragenus), and experimental treatments (e.g.
+Despite searching only on SLA and wood density, we recorded coefficient correlations for a list of 19 traits in total: the five for which we had prior expectations, plus any of 14 others commonly used in the trait literature.
+Where available, we also recorded the geographic coordinates, number of sites, experiment type (greenhouse, field experiment, forest, shade-house etc.), growth measure (relative or absolute growth rate measured using plant diameter, height or mass), vegetation type, life form (tree, woody or mixed with herbaceous species etc.), biological scale (interspecific, intraspecific or intragenus), and experimental treatments (e.g.
 fertilization, shade, salt stress).
@@
 SLA, leaf area, leaf nitrogen and phosphorus concentration, net (mass) assimilation rates (NAR), and Aarea are traits involved in species leaf economic strategy \citep{Wright:2004jb,Wright:2010tp}.
-Seed mass and Hmax capture information about reproductive strategy \citep{Falster:2005bw,Moles:2006ft}.
-WD and sapwood area per leaf area (SA/LA), vessel size and density, and stem specific conductance are all involved in species wood economic strategy  \citep{Chave:2009iy}.
-Here WD and SA/LA are also considered as indicators of stem construction cost \citep{Falster:2011ii}, whereas SLA and leaf thickness capture crucial information about leaf construction cost \citep{Wright:2004jb}.
+Seed mass and maximum height capture information about reproductive strategy \citep{Falster:2005bw,Moles:2006ft}.
+Wood density and sapwood area per leaf area (SA/LA), vessel size and density, and stem specific conductance are all involved in species wood economic strategy  \citep{Chave:2009iy}.
+Here wood density and SA/LA are also considered as indicators of stem construction cost \citep{Falster:2011ii}, whereas SLA and leaf thickness capture crucial information about leaf construction cost \citep{Wright:2004jb}.
 Finally, the leaf area ratio and leaf mass ratio are indicators of resource distribution to leaf \citep{Lambers:1992bj}.
@@
 
-\subsubsection*{Measurements under 'ideal' conditions}\label{ideal-vs-entire-dataset}
+\subsubsection*{Measurements under ``ideal'' conditions}\label{ideal-vs-entire-dataset}
 
-The entire dataset included studies differing in the growth measurement used (RGR or AGR), the number of species, the experimental conditions (stressed vs unstressed), and the concordance between stages used to measure trait and growth rate.
-However RGR and AGR are fundamentally different for a lot of ecologists.
+The entire dataset included studies differing in the growth measurement used (relative of absolute), the number of species, the experimental conditions (stressed vs unstressed), and the concordance between stages used to measure trait and growth rate.
+However relative growth rate and absolute growth rate are fundamentally different for a lot of ecologists.
 And the number of species used to perform the correlation, the experimental conditions, and the concordance between stages used to measure trait and growth are clear criteria for assessing the quality of the data for addressing our hypotheses.
-So we adopted a two steps approach, first we were conservative by focusing exclusively on RGR, across \underline{\textgreater} 10 species, under unstressed conditions, and where the source of the trait and growth is the same (expect for Hmax and seed mass, where a particular stage is by definition required to measure the trait).
-This dataset is called the "ideal" dataset.
-Then we compared results with those of a more inclusive dataset - the entire dataset- with both RGR and AGR, and all others criteria relaxed.
+So we adopted a two steps approach, first we were conservative by focusing exclusively on relative growth rate, across \underline{\textgreater} 10 species, under unstressed conditions, and where the source of the trait and growth is the same (expect for maximum height and seed mass, where a particular stage is by definition required to measure the trait).
+This dataset is called the ``ideal'' dataset.
+Then we compared results with those of a more inclusive dataset - the entire dataset- with both relative growth rate and absolute growth rate, and all others criteria relaxed.
 
@@
 
-\subsection*{Main effects under 'ideal' conditions}
+\subsection*{Main effects under ``ideal'' conditions}
 
 Overall, results were consistent with predictions, although with limitations arising for some traits due to very unequal (and limited) numbers of observations between growth stages.
-We identified only 55 studies with 137 correlations reporting data measured under ``ideal'' conditions: unstressed growth, growth measured as RGR, traits and growth recorded in same stage, and correlation coefficient calculated across \underline{\textgreater} 10 species.
+We identified only 55 studies with 137 correlations reporting data measured under ``ideal'' conditions: unstressed growth, growth measured as relative growth rate, traits and growth recorded in same stage, and correlation coefficient calculated across \underline{\textgreater} 10 species.
 
-For SLA, the correlation between RGR and the trait changed significantly with plant size in the manner expected (Fig.
+For SLA, the correlation between relative growth rate and the trait changed significantly with plant size in the manner expected (Fig.
 \ref{fig:fig3}a).
-The correlation between RGR and SLA shifted from strongly positive at seedling stage ($\bar{r}=0.6 \pm 0.08$, Mean $\pm$ SD) to not significantly different from zero at adult stage ($\bar{r}= -0.01 \pm 0.07$, CI 95\% overlapping zero).
+The correlation between relative growth rate and SLA shifted from strongly positive at seedling stage ($\bar{r}=0.6 \pm 0.08$, Mean $\pm$ SD) to not significantly different from zero at adult stage ($\bar{r}= -0.01 \pm 0.07$, CI 95\% overlapping zero).
 The correlation coefficients recorded at sapling stage were intermediate between seedling and adult stages.
@@
 
-For WD, Hmax, and seed mass, correlations with RGR were also consistent with expectations but our ability to test all hypotheses was at times limited due to low sample size.
+For wood density, maximum height, and seed mass, correlations with relative growth rate were also consistent with expectations but our ability to test all hypotheses was at times limited due to low sample size.
 Indeed, while meta-analysis are possible even with few observations, strong conclusions are generally precluded by very large CIs of the effect size (i.e CI often spanned zero).
-For WD, results were consistent with the prediction for negative correlations with RGR across all plant sizes (Fig.
+For wood density, results were consistent with the prediction for negative correlations with relative growth rate across all plant sizes (Fig.
 \ref{fig:fig3}b).
-Accordingly, model fits were marginaly improved when stage was incorporated (p.value = 0.049).
+Accordingly, model fits were marginally improved when stage was incorporated (p.value = 0.049).
 Note that the CIs were not crossing zero for seedling and sapling stage despite the small sample sizes (n= 1 and 4 respectively), meaning a strong correlation and/or a good consistency in the coefficient reported for each stage across studies.
 
-For Hmax, the expectation was for a correlation with growth to be present for large plants but absent for smaller sizes, the mechanism being increased relative allocation to reproduction as Hmax is approached.
-Here, Hmax was positively correlated with growth at adult stage ($\bar{r}= 0.38 \pm 0.05$), not correlated at sapling stage (Fig \ref{fig:fig3}c, CIs overlapping zero) and no data were recorded for seedling stage.
-While these results were consistent with expectation, we could not distinguish with another alternative: Hmax was correlated to growth for adult stage, but the correlation between Hmax and growth at sapling stage was not significantly different from that observed at adult stage (model fit not improved when stage was incorporated, see log likelihood ratio tests in Fig.
+For maximum height, the expectation was for a correlation with growth to be present for large plants but absent for smaller sizes, the mechanism being increased relative allocation to reproduction as maximum height is approached.
+Here, maximum height was positively correlated with growth at adult stage ($\bar{r}= 0.38 \pm 0.05$), not correlated at sapling stage (Fig \ref{fig:fig3}c, CIs overlapping zero) and no data were recorded for seedling stage.
+While these results were consistent with expectation, we could not distinguish with another alternative: maximum height was correlated to growth for adult stage, but the correlation between maximum height and growth at sapling stage was not significantly different from that observed at adult stage (model fit not improved when stage was incorporated, see log likelihood ratio tests in Fig.
 \ref{fig:fig3}c, and CIs overlapping between sapling and adult stages).
-Due to small numbers of replicate studies for sapling stage and no replicates for seedling stage, we could not conclude on the absence of correlation between Hmax and growth at small plant size.
+Due to small numbers of replicate studies for sapling stage and no replicates for seedling stage, we could not conclude on the absence of correlation between maximum height and growth at small plant size.
 
-As expected for seed mass, the correlation with RGR shifted from negative at seedling stage ($\bar{r}= -0.5 \pm 0.07$) to not significantly different from zero at adult and sapling stages (Fig \ref{fig:fig3}c, CIs overlapping zero).
-However, the correlation between seed mass and RGR at adult and sapling stages were also not significantly different from that observed at seedling stage (see log likelihood ratio tests and CIs overlapping in Fig.
+As expected for seed mass, the correlation with relative growth rate shifted from negative at seedling stage ($\bar{r}= -0.5 \pm 0.07$) to not significantly different from zero at adult and sapling stages (Fig \ref{fig:fig3}c, CIs overlapping zero).
+However, the correlation between seed mass and relative growth rate at adult and sapling stages were also not significantly different from that observed at seedling stage (see log likelihood ratio tests and CIs overlapping in Fig.
 \ref{fig:fig3}c).
 Again we could not distinguish between these alternatives.
-But unlike Hmax, the number of coefficient reported for seed mass was almost similar between adult (n= 7) and seedling (n= 10) stages, suggesting that CIs overlapping zero at adult stage were due to variation in correlation coefficient reported rather than to a much smaller numbers of replicates.
+But unlike maximum height, the number of coefficient reported for seed mass was almost similar between adult (n= 7) and seedling (n= 10) stages, suggesting that CIs overlapping zero at adult stage were due to variation in correlation coefficient reported rather than to a much smaller numbers of replicates.
 
-For Aarea, results were consistent with a positive correlation with RGR at seedling stage.
+For Aarea, results were consistent with a positive correlation with relative growth rate at seedling stage.
 However, no conclusion can be drawn about a change along ontogenetic stages; as only four correlation coefficients were reported for this trait, and three of these were measured at the seedling stage (Fig.
@@
 Our aim is to determine if additional data alters or reinforce the above conclusions, by increasing replication.
-This entire dataset included correlations measured with both AGR and RGR (Fig.
+This entire dataset included correlations measured with both absolute growth rate and relative growth rate (Fig.
 \ref{fig:fig4}), across at least two species (but measured using several individuals), and did not control for the source of trait or growth (i.e.
@@
 from 25 to 59 correlation coefficients reported for SLA at seedling stage), while others still had few replicates.
-On the 13 traits-stage combinations studied in total, six had $\le$ five correlation coefficients: WD-seedling, Hmax-sapling, Hmax-seedling, Seed mass-sapling, Aarea-adult and Aarea-sapling.
+On the 13 traits-stage combinations studied in total, six had $\le$ five correlation coefficients: Wood density-seedling, maximum height-sapling, maximum height-seedling, Seed mass-sapling, Aarea-adult and Aarea-sapling.
 
@@
 
-Results from the entire dataset reinforced our conclusions for both SLA and WD, set apart alternative explanations for seed mass, and allowed us to compare correlations with growth along ontogenetic stages for Aarea.
-For SLA and WD, the number of replicates doubled by using the entire dataset, and effect sizes and overall results were similar to those reported above using the ''ideal'' subset (Fig.
+Results from the entire dataset reinforced our conclusions for both SLA and wood density, set apart alternative explanations for seed mass, and allowed us to compare correlations with growth along ontogenetic stages for Aarea.
+For SLA and wood density, the number of replicates doubled by using the entire dataset, and effect sizes and overall results were similar to those reported above using the ``ideal'' subset (Fig.
 \ref{fig:fig4})).
@@
 For Aarea, the additional replicates in the entire dataset allowed us to compare the effect size across ontogenetic stage.
-The results were consistent with the prediction for a positive correlation with RGR across adult and seedling stages (Fig \ref{fig:fig4}e; CI not overlapping zero).
+The results were consistent with the prediction for a positive correlation with relative growth rate across adult and seedling stages (Fig \ref{fig:fig4}e; CI not overlapping zero).
 Comparison of Aarea effect between the ``ideal'' subset (Fig.
 \ref{fig:fig3}d) and entire dataset (Fig.
-\ref{fig:fig4}d), indicated little effect of stress (here mainly low light) on the correlation with RGR at seedling stage; as the correlation was still positive when 8 correlations measured under low light conditions were added.
-For Hmax, there were still too few replicates to conclude undoubtely on the correlation to be absent for smaller sizes.
+\ref{fig:fig4}d), indicated little effect of stress (here mainly low light) on the correlation with relative growth rate at seedling stage; as the correlation was still positive when 8 correlations measured under low light conditions were added.
+For maximum height, there were still too few replicates to conclude undoubtedly on the correlation to be absent for smaller sizes.
 
-We had hypotheses for seed mass and SLA, about a change in the correlation between trait and growth as AGR was used instead of RGR, or as mass was used instead of dimater and height.
-For seed mass, effects size differed significantly between RGR and AGR at seedling stage; as expected the correlation with RGR was positive and shifted to non significant with AGR (Fig \ref{fig:fig4}d; CI not overlapping).
-For SLA, the correlation was expected to shift from positive to non significant if AGRmass was used instead of RGRmass for seedling stage; here none of the data have been measured with AGRmass at seedling stage (Fig.
+We had hypotheses for seed mass and SLA, about a change in the correlation between trait and absolute growth rate was used instead of relative growth rate, or as mass was used instead of diameter and height.
+For seed mass, effects size differed significantly between relative growth rate and absolute growth rate at seedling stage; as expected the correlation with relative growth rate was positive and shifted to non significant with absolute growth rate (Fig \ref{fig:fig4}d; CI not overlapping).
+For SLA, the correlation was expected to shift from positive to non significant if growth in mass was measured on absolute instead of relative terms; however, here none of the data have been measured with absolute rates in the seedling stage (Fig.
 \ref{fig:figA8}).
-% Why a change with WD when it is measured in mass? All WD seedling are measured in RGRmass, and there are some mass data for both other stages too.  
-For other traits, effect size were generally consistent between RGR and AGR when both measurement were available.
+For other traits, effect size were generally consistent between relative growth rate and absolute growth rate when both measurement were available.
 Some differences occurred but they were not easily attributed to any single cause.
-For instance for WD, the correlation at juvenile stage shifted from negative with RGR to non significant with AGR (i.e CI included zero, Fig.
+For instance for wood density, the correlation at juvenile stage shifted from negative with relative growth rate to non significant with absolute growth rate (i.e CI included zero, Fig.
 \ref{fig:fig4}b).
-The correlation coefficients recorded for AGR came from \citet{Augspurger:1984ct} and unlike others they used wood density values from adult plants together with growth from juveniles.
+The correlation coefficients recorded for absolute growth rate came from \citet{Augspurger:1984ct} and unlike others they used wood density values from adult plants together with growth from juveniles.
 
@@
 Given this variety, it was not surprising to find a wide range of $r$ reported for each trait.
-For instance, $r$ varied from -0.98 to 0.99 for SLA, and from -0.74 to 0.74 for WD (Fig.
+For instance, $r$ varied from -0.98 to 0.99 for SLA, and from -0.74 to 0.74 for wood density (Fig.
 \ref{fig:figA3}).
@@
 For SLA the meta-analysis confirmed quite strongly the predicted influence of plant size on the trait-growth correlation.
-For WD, Aarea, seed mass and Hmax results were consistent with predictions, but coverage was limited and additional studies would be helpful for some trait-growth-stage relationships.
+For wood density, Aarea, seed mass and maximum height results were consistent with predictions, but coverage was limited and additional studies would be helpful for some trait-growth-stage relationships.
 
@@
 
-For seedlings our study showed, as expected, a negative relationship between seed mass and RGR (in mass or height or volume) for small plants, that dissipated as plants grew larger.
+For seedlings our study showed, as expected, a negative relationship between seed mass and relative growth rate (in mass or height or volume) for small plants, that dissipated as plants grew larger.
 This negative relationship arises because seedlings from larger seeds begin life larger themselves, as has been extensively discussed in the literature \citep[reviewed by][]{Turnbull:2012ew}.
 
-For WD the meta-analysis showed negative correlation with RGR across all ontogenetic stages, as previously reported from individual studies \citep{Wright:2010tp,Ruger:2012jv}.
+For wood density the meta-analysis showed negative correlation with relative growth rate across all ontogenetic stages, as previously reported from individual studies \citep{Wright:2010tp,Ruger:2012jv}.
 It should be noted however that there are few data available to test this proposition at seedling stage (n=1-5).
@@
 Lower xylem conductance and associated lower photosynthetic potential have also been suggested \citep[reviewed by][]{Chave:2009iy}.
-For seedlings a negative correlation arose regardless WD was measured on adult plants, or calculated as seedling stem segment dry weight over its volume (i.e.
+For seedlings a negative correlation arose regardless wood density was measured on adult plants, or calculated as seedling stem segment dry weight over its volume (i.e.
 stem density in  \citealt{CastroDiez:1998gz}), suggesting that both measurements could be used.
@@
 
-Meta-analysis showed a positive correlation between Hmax and RGR for adult stage, but not for saplings and seedlings.
+Meta-analysis showed a positive correlation between maximum height and relative growth rate for adult stage, but not for saplings and seedlings.
 The trend for tall stature species to grow faster at a given tree size than small stature species has been noted across several tree size classes and forest types (e.g.
 \citealt{Thomas:1996do,Poorter:2008iu,Wright:2010tp,Herault:2011dd,Ruger:2012jv,Iida:2014ep}).
-In \citet{Wright:2010tp}, Hmax was considered a weak predictor of growth rates of saplings; however it was the strongest predictor of growth rates of large trees.
-\citet{Poorter:2008iu} speculated that the Hmax-RGR relationship among large trees might arise from including small tree species with maximum size not much larger than the 10cm dbh lower threshold used to define large trees.
-In our growth equations, Hmax affects growth via the fraction of energy diverted to reproduction.
-At a given tree size, species closer to their Hmax are expected to be allocating relatively less to vegetative growth.
+In \citet{Wright:2010tp}, maximum height was considered a weak predictor of growth rates of saplings; however it was the strongest predictor of growth rates of large trees.
+\citet{Poorter:2008iu} speculated that the maximum height-relative growth rate relationship among large trees might arise from including small tree species with maximum size not much larger than the 10cm dbh lower threshold used to define large trees.
+In our growth equations, maximum height affects growth via the fraction of energy diverted to reproduction.
+At a given tree size, species closer to their maximum height are expected to be allocating relatively less to vegetative growth.
 However this applies only at sizes where some of the species have begun to reproduce, and should not affect sapling and seedling growth rates.
-While the results of the meta-analysis were consistent with the expected pattern for Hmax, we noted that a limited number of replicates were available for both saplings (n=4) and seedling stages (n=1).
+While the results of the meta-analysis were consistent with the expected pattern for maximum height, we noted that a limited number of replicates were available for both saplings (n=4) and seedling stages (n=1).
 Consequently, subsequent research are welcomed to validate this result.
@@
 A recurring issue in trait ecology is how many of the observed correlations arise directly from mechanisms, versus how many from secondary cross-correlation.
-For example, several papers have suggested that correlations between Hmax and growth rate may arise via cross-correlation with other traits such as WD \citep{Thomas:1996do, Poorter:2006vb, Wright:2010tp}.
+For example, several papers have suggested that correlations between maximum height and growth rate may arise via cross-correlation with other traits such as wood density \citep{Thomas:1996do, Poorter:2006vb, Wright:2010tp}.
 These studies also suggest species towards one end of a trait spectrum may generally be found in better light.
@@
 A lot of biotic and abiotic conditions such as light and water micro-environments can affect growth rates, and might modify correlations with traits in relation to plant size.
-For example, instead of a positive relationship that disappeared with plant size, \citet{Iida:2014ep} found SLA was negatively correlated with RGR at small size and positively correlated with RGR at larger sizes.
-Similarly, instead of a negative correlation between WD and growth across all ontogenetic stages, some studies found a negative correlation at small size that disappeared when trees were larger \citep{Iida:2014ep,Iida:2014hq}.
+For example, instead of a positive relationship that disappeared with plant size, \citet{Iida:2014ep} found SLA was negatively correlated with relative growth rate at small size and positively correlated with relative growth rate at larger sizes.
+Similarly, instead of a negative correlation between wood density and growth across all ontogenetic stages, some studies found a negative correlation at small size that disappeared when trees were larger \citep{Iida:2014ep,Iida:2014hq}.
 The authors explained the switch in directionality by changes in light and water condition up the vertical profile within a forest: larger trees reached a position in the canopy where they were released from light limitations, other resources such as water may have become limiting, and the performance of trees may then have been regulated by different traits.
-Note that in \citet{Iida:2014hq}, the shift in the correlation between growth and WD occurred for trees larger than 22-26 cm dbh.
+Note that in \citet{Iida:2014hq}, the shift in the correlation between growth and wood density occurred for trees larger than 22-26 cm dbh.
 This points to one of the possible limitations in our meta-analysis, where trees with diameter above 10 cm were pooled as ``adult''.
@@
 via the recently published \texttt{plant} model \citep{Falster-2016}.
-Additional data are specifically required in small plants (seedling and sapling) for WD and Hmax, and in large plants (adult and sapling) for Aarea and more broadly for all traits requiring a measure of whole plant biomass (e.g.
+Additional data are specifically required in small plants (seedling and sapling) for wood density and maximum height, and in large plants (adult and sapling) for Aarea and more broadly for all traits requiring a measure of whole plant biomass (e.g.
 LMR, LAR).
@@
 \includegraphics[width=15cm,height=20cm,keepaspectratio]{output/Fig3.pdf}
-\caption{The relationship between relative growth rates (RGR) and traits changes with ontogenetic stage and trait.
+\caption{The relationship between relative growth rates and traits changes with ontogenetic stage and trait.
 Plots show the effect size (+ 95\% confidence intervals; CI) for the average correlation across $>$10 species, by ontogenetic stage.
@@
 i) Results shown are from the entire dataset (see methods for details).
-ii) Likelihood Ratio Tests were calculated on effect size combining RGR and AGR exclusively.}
+ii) Likelihood Ratio Tests were calculated on effect size combining relative growth rate and absolute growth rate exclusively.}
 \label{fig:fig4}
@@
 Arrows indicate the effect an increase in trait value would have on each element of the equations, with dashes indicating no effect.
-For further details, see main text.}
+Traits are: specific leaf area (= SLA), wood density (= WD), Maximum height (= Hmax), Seed mass, and Maximum photosynthesis per unit leaf area (= Area) For further details, see main text.}
 {\footnotesize

### 2016-01-22 ms-suppinfo.Rnw
Remove abbreviations: RGR, AGR, WD, Hmax

@@
 The mean coefficients are weighted by sample size and established from 103 articles.
-Results shown here are from the ''ideal'' subset of data (for details see ``Material and Methods''), ``n'' indicates the number of correlations.}
+Results shown here are from the ``ideal'' subset of data (for details see ``Material and Methods''), ``n'' indicates the number of correlations.}
 \label{fig:figA4}
@@
 Absolute growth rate (AGR) is on the left and relative growth rate (RGR) on the right of each plot.
-Results shown here are from the "ideal" subset of the data (for details see ``Material and Methods'').
+Results shown here are from the ``ideal'' subset of the data (for details see ``Material and Methods'').
 }
@@
 111), b) Wood density (WD, n = 64), c) Asymptotic
-maximum height (Hmax, n = 23), d) Seed mass (Seedmass, n = 36 and
+maximum height (Hmax, n = 23), d) Seed mass (n = 36) and
 e) Rate of CO2 assimilation (Aarea, n = 24) reported from 103
@@
 The open points correspond to the estimated missing studies.
-The number of missing values is 4 for SLA,0 for WD, 0 for Hmax, 11 for seed mass and 0 for Aarea.
+The number of missing values is 4 for SLA, 0 for wood density, 0 for maximum height, 11 for seed mass and 0 for Aarea.
 Results shown here are from the entire dataset.
@@
 
-We developed a snapshot of the literature, to assess the potential to recover useful data from the wide corpus of literature available by searching exclusively on SLA and WD.
+We developed a snapshot of the literature, to assess the potential to recover useful data from the wide corpus of literature available by searching exclusively on SLA and wood density.
 This snapshot was obtained via Web of Science database (Thomson Reuters), between March and June 2014, using a range of Boolean search terms in English.
 Search terms were as follows: (``trait'' AND (``growth rate'' OR ``relative growth rate'')) AND (``tree*'' OR ``woody*''), where ``trait'' was allowed to be any of the trait names listed in Table \ref{tab:lit_search}.
-This snapshot indicated that \Sexpr{round(fun_snapshot(Snapshot)$main.traits ,0)}\% of the reported correlations linking growth to any of our five core traits would be recovered by searching only on SLA and WD.
-And it was \Sexpr{round(fun_snapshot(Snapshot)$all.traits ,0)}\% of the literature that would be captured by SLA and WD for the total 19 traits.
+This snapshot indicated that \Sexpr{round(fun_snapshot(Snapshot)$main.traits ,0)}\% of the reported correlations linking growth to any of our five core traits would be recovered by searching only on SLA and wood density.
+And it was \Sexpr{round(fun_snapshot(Snapshot)$all.traits ,0)}\% of the literature that would be captured by SLA and wood density for the total 19 traits.
 Thus we narrow our search to only cover these two main traits.
@@
 
-\noindent\textbf{Results:} We observed high levels of heterogeneity for all traits (SLA :$I^{2}$ \Sexpr{round(fun_Heterogeneity.H(GCi[["SLA"]], ~stageRGR)$Hlevel,0)}\% CI: \Sexpr{round(fun_Heterogeneity.CI(GCi[["SLA"]])$random[7], 0)}-\Sexpr{round(fun_Heterogeneity.CI(GCi[["SLA"]])$random[11],0)}\%, WD :$I^{2}$ \Sexpr{round(fun_Heterogeneity.H(GCi[["WD"]], ~stage)$Hlevel,0)}\% CI: \Sexpr{round(fun_Heterogeneity.CI(GCi[["WD"]])$random[7], 0)}-\Sexpr{round(fun_Heterogeneity.CI(GCi[["WD"]])$random[11],0)}, Hmax: $I^{2}$ \Sexpr{round(fun_Heterogeneity.H(GCi[["Hmax"]], ~stageRGR)$Hlevel,0)}\% CI: \Sexpr{round(fun_Heterogeneity.CI(GCi[["Hmax"]])$random[7], 0)}-\Sexpr{round(fun_Heterogeneity.CI(GCi[["Hmax"]])$random[11],0)}, seed mass: $I^{2}$ \Sexpr{round(fun_Heterogeneity.H(GCi[["Seedmass"]], ~stage)$Hlevel,0)}\%, CI \Sexpr{round(fun_Heterogeneity.CI(GCi[["Seedmass"]])$random[7], 1)}-\Sexpr{round(fun_Heterogeneity.CI(GCi[["Seedmass"]])$random[11],1)}, Aarea: $I^{2}$ \Sexpr{round(fun_Heterogeneity.H(GCi[["Aarea"]], ~stage)$Hlevel,1)}\% CI: \Sexpr{round(fun_Heterogeneity.CI(GCi[["Aarea"]])$random[7], 0)}-\Sexpr{round(fun_Heterogeneity.CI(GCi[["Aarea"]])$random[11],0)}) which suggests that the correlations coefficient r between growth and traits are not uniform across the range of studies investigated.
+\noindent\textbf{Results:} We observed high levels of heterogeneity for all traits (SLA :$I^{2}$ \Sexpr{round(fun_Heterogeneity.H(GCi[["SLA"]], ~stageRGR)$Hlevel,0)}\% CI: \Sexpr{round(fun_Heterogeneity.CI(GCi[["SLA"]])$random[7], 0)}-\Sexpr{round(fun_Heterogeneity.CI(GCi[["SLA"]])$random[11],0)}\%, wood density :$I^{2}$ \Sexpr{round(fun_Heterogeneity.H(GCi[["WD"]], ~stage)$Hlevel,0)}\% CI: \Sexpr{round(fun_Heterogeneity.CI(GCi[["WD"]])$random[7], 0)}-\Sexpr{round(fun_Heterogeneity.CI(GCi[["WD"]])$random[11],0)}, maximum height: $I^{2}$ \Sexpr{round(fun_Heterogeneity.H(GCi[["Hmax"]], ~stageRGR)$Hlevel,0)}\% CI: \Sexpr{round(fun_Heterogeneity.CI(GCi[["Hmax"]])$random[7], 0)}-\Sexpr{round(fun_Heterogeneity.CI(GCi[["Hmax"]])$random[11],0)}, seed mass: $I^{2}$ \Sexpr{round(fun_Heterogeneity.H(GCi[["Seedmass"]], ~stage)$Hlevel,0)}\%, CI \Sexpr{round(fun_Heterogeneity.CI(GCi[["Seedmass"]])$random[7], 1)}-\Sexpr{round(fun_Heterogeneity.CI(GCi[["Seedmass"]])$random[11],1)}, Aarea: $I^{2}$ \Sexpr{round(fun_Heterogeneity.H(GCi[["Aarea"]], ~stage)$Hlevel,1)}\% CI: \Sexpr{round(fun_Heterogeneity.CI(GCi[["Aarea"]])$random[7], 0)}-\Sexpr{round(fun_Heterogeneity.CI(GCi[["Aarea"]])$random[11],0)}) which suggests that the correlations coefficient r between growth and traits are not uniform across the range of studies investigated.
 This result suggested that a large part of the variance is not explained by sampling error.
 
-For SLA, seed mass and Hmax, \Sexpr{round(fun_Heterogeneity.H(GCi[["SLA"]], ~stageRGR)$Hexplained,1)}\%, \Sexpr{round(fun_Heterogeneity.H(GCi[["Seedmass"]], ~stage)$Hexplained,1)}\% and \Sexpr{round(fun_Heterogeneity.H(GCi[["Hmax"]], ~stageRGR)$Hexplained, 0)}\% respectively of the total amount of heterogeneity were accounted for by including the ontogenetic stage as a moderator.
-For the other traits, the ontogenetic stage explained little or no part of the heterogeneity observed across studies ( WD: \Sexpr{round(fun_Heterogeneity.H(GCi[["WD"]], ~stage)$Hexplained, 0)}\% and Aarea: \Sexpr{round(fun_Heterogeneity.H(GCi[["Aarea"]], ~stage)$Hexplained, 1)}\% ).
-These results were consistent with our expectations about a shift in the relationship between growth and traits across plant size for SLA, seed mass and Hmax, and the absence of an effect for WD and Aarea (see Theoretical expectation section).
+For SLA, seed mass and maximum height, \Sexpr{round(fun_Heterogeneity.H(GCi[["SLA"]], ~stageRGR)$Hexplained,1)}\%, \Sexpr{round(fun_Heterogeneity.H(GCi[["Seedmass"]], ~stage)$Hexplained,1)}\% and \Sexpr{round(fun_Heterogeneity.H(GCi[["Hmax"]], ~stageRGR)$Hexplained, 0)}\% respectively of the total amount of heterogeneity were accounted for by including the ontogenetic stage as a moderator.
+For the other traits, the ontogenetic stage explained little or no part of the heterogeneity observed across studies (wood density: \Sexpr{round(fun_Heterogeneity.H(GCi[["WD"]], ~stage)$Hexplained, 0)}\% and Aarea: \Sexpr{round(fun_Heterogeneity.H(GCi[["Aarea"]], ~stage)$Hexplained, 1)}\% ).
+These results were consistent with our expectations about a shift in the relationship between growth and traits across plant size for SLA, seed mass and maximum height, and the absence of an effect for wood density and Aarea (see Theoretical expectation section).
 
@@
 
-The Rosenberg's Fail-safe (N) were \Sexpr{fun_fsn(GCi[["SLA"]])[2]}, \Sexpr{fun_fsn(GCi[["WD"]])[2]}, \Sexpr{fun_fsn(GCi[["Hmax"]])[2]}, \Sexpr{fun_fsn(GCi[["Seedmass"]])[2]}, \Sexpr{fun_fsn(GCi[["Aarea"]])[2]} for SLA, WD, Hmax, Seedmass, and Aarea, suggesting that a large number of studies with a mean correlation coefficient of 0 need to be added to the analysis before the cumulative correlation would become non-significant.
+The Rosenberg's Fail-safe (N) were \Sexpr{fun_fsn(GCi[["SLA"]])[2]}, \Sexpr{fun_fsn(GCi[["WD"]])[2]}, \Sexpr{fun_fsn(GCi[["Hmax"]])[2]}, \Sexpr{fun_fsn(GCi[["Seedmass"]])[2]}, \Sexpr{fun_fsn(GCi[["Aarea"]])[2]} for SLA, wood density, maximum height, Seedmass, and Aarea, suggesting that a large number of studies with a mean correlation coefficient of 0 need to be added to the analysis before the cumulative correlation would become non-significant.
 N was greater than 5k+10 for all traits (120 $< N <$ 455).

### 2016-01-22 ms-suppinfo.tex
Remove abbreviations: RGR, AGR, WD, Hmax

@@
 
-We developed a snapshot of the literature, to assess the potential to recover useful data from the wide corpus of literature available by searching exclusively on SLA and WD.
+We developed a snapshot of the literature, to assess the potential to recover useful data from the wide corpus of literature available by searching exclusively on SLA and wood density.
 This snapshot was obtained via Web of Science database (Thomson Reuters), between March and June 2014, using a range of Boolean search terms in English.
 Search terms were as follows: (``trait'' AND (``growth rate'' OR ``relative growth rate'')) AND (``tree*'' OR ``woody*''), where ``trait'' was allowed to be any of the trait names listed in Table \ref{tab:lit_search}.
-This snapshot indicated that 84\% of the reported correlations linking growth to any of our five core traits would be recovered by searching only on SLA and WD.
-And it was 70\% of the literature that would be captured by SLA and WD for the total 19 traits.
+This snapshot indicated that 84\% of the reported correlations linking growth to any of our five core traits would be recovered by searching only on SLA and wood density.
+And it was 70\% of the literature that would be captured by SLA and wood density for the total 19 traits.
 Thus we narrow our search to only cover these two main traits.
@@
 
-\noindent\textbf{Results:} We observed high levels of heterogeneity for all traits (SLA :$I^{2}$ 84\% CI: 80-91\%, WD :$I^{2}$ 63\% CI: 48-85, Hmax: $I^{2}$ 81\% CI: 70-93, seed mass: $I^{2}$ 90\%, CI 84.9-94.9, Aarea: $I^{2}$ 71.5\% CI: 42-86) which suggests that the correlations coefficient r between growth and traits are not uniform across the range of studies investigated.
+\noindent\textbf{Results:} We observed high levels of heterogeneity for all traits (SLA :$I^{2}$ 84\% CI: 80-91\%, wood density :$I^{2}$ 63\% CI: 48-85, maximum height: $I^{2}$ 81\% CI: 70-93, seed mass: $I^{2}$ 90\%, CI 84.9-94.9, Aarea: $I^{2}$ 71.5\% CI: 42-86) which suggests that the correlations coefficient r between growth and traits are not uniform across the range of studies investigated.
 This result suggested that a large part of the variance is not explained by sampling error.
 
-For SLA, seed mass and Hmax, 41\%, 20.2\% and 17\% respectively of the total amount of heterogeneity were accounted for by including the ontogenetic stage as a moderator.
-For the other traits, the ontogenetic stage explained little or no part of the heterogeneity observed across studies ( WD: 9\% and Aarea: 0.1\% ).
-These results were consistent with our expectations about a shift in the relationship between growth and traits across plant size for SLA, seed mass and Hmax, and the absence of an effect for WD and Aarea (see Theoretical expectation section).
+For SLA, seed mass and maximum height, 41\%, 20.2\% and 17\% respectively of the total amount of heterogeneity were accounted for by including the ontogenetic stage as a moderator.
+For the other traits, the ontogenetic stage explained little or no part of the heterogeneity observed across studies (wood density: 9\% and Aarea: 0.1\% ).
+These results were consistent with our expectations about a shift in the relationship between growth and traits across plant size for SLA, seed mass and maximum height, and the absence of an effect for wood density and Aarea (see Theoretical expectation section).
 
@@
 
-The Rosenberg's Fail-safe (N) were 10617, 3344, 1138, 2261, 643 for SLA, WD, Hmax, Seedmass, and Aarea, suggesting that a large number of studies with a mean correlation coefficient of 0 need to be added to the analysis before the cumulative correlation would become non-significant.
+The Rosenberg's Fail-safe (N) were 10617, 3344, 1138, 2261, 643 for SLA, wood density, maximum height, Seedmass, and Aarea, suggesting that a large number of studies with a mean correlation coefficient of 0 need to be added to the analysis before the cumulative correlation would become non-significant.
 N was greater than 5k+10 for all traits (120 $< N <$ 455).

### 2016-01-22 ms-suppinfo.tex
remove seedling model, no longer needed

@@
 
-\subsection{Simplified growth equations for seedlings of similar size}\label{app:growth-equation}
-
-For the case of seedlings, the growth equations can be simplified considerably.
-Turnover of all tissues and allocation to reproduction have not yet begun.
-It is also common to assume all respiration rates are proportional to leaf area.
-Biomass growth rate in seedling then becomes a linear function of leaf area:
-\begin{equation}\label{eq:eq1_seedlings}
-{\frac{\ud M_{\rm t}}{\ud t}}  \approx  A_{\rm l} \, y \, (p - r_{\rm l}).
-\end{equation}
-
-The \textbf{relative growth rate in mass} $({\rm RGR}_{{\rm mass}})$ in seedlings can be obtained by dividing both sides of this simplified eq \ref{eq:eq1_seedlings} by the total mass of living tissues $M_{\rm t}$.
-The outcome is equivalent to the classical partitioning of RGR \citep{Lambers:1992bj, Cornelissen:1998ta}:
-\begin{equation}\label{eq:eq1_seedlings_RGR}
-{\rm RGR}_{{\rm mass}}  \approx {\rm NAR} \times  {\rm SLA} \times  {\rm LMF},
-\end{equation}
-where net assimilation rate NAR = $y \, (p - r)$, SLA = $A_{\rm l}/ M_{\rm l}$ and leaf mass fraction LMF = $M_{\rm l}/ M_{\rm t}$.
-
 \subsection{Literature coverage by trait}\label{app:literature-snapshot}

### 2016-01-25 MS.tex
remove seedling model, no longer needed
small editing in abstract and results

@@
 \linenumbers
-\section{Summary 327/350}\label{abstract}
+\section{Summary 307/350}\label{abstract}
 \begin{enumerate}
@@
 
-\item Although we were able to confirm several of our theoretical predictions, major knowledge gaps size still exist, despite a sizeable literature on traits and growth.
+\item Although we were able to confirm several of our theoretical predictions, major knowledge gaps still exist in the trait literature.
 For example, for one-third of the trait considered, the majority ($>$ 75\%) of reported correlations with growth came from a single ontogenetic stage.
@@
 A similar shift is expected for growth in mass when expressed in relative terms.
-However, when expressed as absolute growth, the predicted relationship is non-significant \citep[see also][]{Enquist-1999}.
+However, when expressed as absolute growth, the predicted relationship is non-significant along all plant size\citep[see also][]{Enquist-1999}.
 
@@
 
-We had hypotheses for seed mass and SLA, about a change in the correlation between trait and absolute growth rate was used instead of relative growth rate, or as mass was used instead of diameter and height.
+We had hypotheses for seed mass, SLA and wood density, about a change in the correlation between trait and absolute growth rate was used instead of relative growth rate, or as mass was used instead of diameter and height.
 For seed mass, effects size differed significantly between relative growth rate and absolute growth rate at seedling stage; as expected the correlation with relative growth rate was positive and shifted to non significant with absolute growth rate (Fig \ref{fig:fig4}d; CI not overlapping).
@@
 \ref{fig:figA8}).
+For wood density, some differences occurred but they were not easily attributed to any single cause.
+In particular, the correlation at juvenile stage shifted from negative with relative growth rate to non significant with absolute growth rate (i.e CI included zero, Fig.
+\ref{fig:fig4}b).
+Yet, the correlation coefficients recorded for absolute growth rate came from \citet{Augspurger:1984ct}, and unlike others they used wood density values from adult plants together with growth from juveniles.
+So it was not possible to distangle the effect of growth measurement from the effect of trait origine.
 For other traits, effect size were generally consistent between relative growth rate and absolute growth rate when both measurement were available.
-Some differences occurred but they were not easily attributed to any single cause.
-For instance for wood density, the correlation at juvenile stage shifted from negative with relative growth rate to non significant with absolute growth rate (i.e CI included zero, Fig.
-\ref{fig:fig4}b).
-The correlation coefficients recorded for absolute growth rate came from \citet{Augspurger:1984ct} and unlike others they used wood density values from adult plants together with growth from juveniles.
 
@@
 Overall our study met quality criteria expected for meta-analysis in ecology (Table \ref{tab:meta}).
-The impact of publication bias was seemingly trivial (See Appendix \ref{app:growth-equation}, Fig.
+The impact of publication bias was seemingly trivial (See Appendix \ref{app:heterogeneity}, Fig.
 \ref{fig:figA7}).

### 2016-02-19 MS.tex
Address comments from Mark Westoby and Freya Thomas

@@
 We outline mechanisms and hypotheses based on new theoretical work, and test these predictions in tree species using a meta-analysis of 103 studies ($>$ 500 correlations) for five traits (specific leaf area, wood density, maximum height, seed mass and maximum assimilation rate).
-We also recorded data for 14 others traits commonly used in the trait literature.
+We also recorded data for 14 other traits commonly used in the trait literature.
 To capture the effects of plant size, we tested for a shift in the direction of correlation between growth rates and traits across three ontogenetic stages: seedling, sapling and adult.
 
-\item Results were consistent with predictions, even with some limitations arising from unequal numbers of observation across ontogenetic stages.
+\item Results were consistent with predictions, although there were some limitations arising from unequal numbers of observation across ontogenetic stages.
 Specific leaf area was correlated with relative growth rate in seedlings but not in adult plants.
-Correlations of growth with wood density and assimilation rate were not affected by stage.
+Correlations of growth with wood density and assimilation rate were not affected by ontogenetic stage.
 Seed mass and maximum height were correlated with relative growth rate only in one ontogenetic stage category: seedlings and adults, respectively.
@@
 \item Although we were able to confirm several of our theoretical predictions, major knowledge gaps still exist in the trait literature.
-For example, for one-third of the trait considered, the majority ($>$ 75\%) of reported correlations with growth came from a single ontogenetic stage.
+For example, for one-third of the traits considered, the majority ($>$ 75\%) of reported correlations with growth came from the same ontogenetic stage.
 
@@
 The phrase ``plant ecological strategy'' refers to how species face common challenges of acquiring sufficient water, nutrients, and light for growth; and then ultimately replacing themselves with offspring.
-The idea that a strategy differences among species might involve fast versus slow growth goes back at least to \citet{Grime:1975gr}, who observed a wide spread of relative growth rate  among seedlings growing under favourable conditions.
+The idea that strategy differences among species might involve fast versus slow growth goes back at least to \citet{Grime:1975gr}, who observed a wide spread of relative growth rate  among seedlings growing under favourable conditions.
 Seedling potential relative growth rate has continued to be used as a major strategy indicator within Grime's CSR (Competitor -- Stress tolerator -- Ruderal) classification (e.g.
 \citealt{grime1979plant, Grime:1997wm}).
-Meanwhile partitioning of seedling relative growth rate into different components showed that the trait specific leaf area (SLA) was typically the strongest source of variation between species \citep{Poorter:1989tx, Rees:2010gk}.
-From the 1990's a new style of ``trait ecology'' arose whereby measurable traits, including SLA, were used directly as strategy axes \citep{Westoby:2002ft}.
-An approach via measurable traits made broad comparisons possible across continents, latitudes, and thousands of species.
-Since then, traits have been seen as constructive approaches to understanding plant growth strategies \citep{Westoby:2002ft}, community composition \citep{Lavorel:2002ff,Shipley:2006ie}, global vegetation dynamics \citep{Scheiter:2013ed} and ecosystem processes \citep{Lavorel:2002ff}.
+Meanwhile partitioning of seedling relative growth rate into different components showed that specific leaf area (SLA) was typically the strongest source of variation between species \citep{Poorter:1989tx, Rees:2010gk}.
+During the 1990's a new style of ``trait ecology'' arose whereby measurable traits, including SLA, were used directly as strategy axes \citep{Westoby:2002ft}.
+This approach, using measurable traits, made broad comparisons possible across continents, latitudes, and thousands of species.
+Since then, functional traits have been seen as constructive tools to understanding plant growth strategies \citep{Westoby:2002ft}, community composition \citep{Lavorel:2002ff,Shipley:2006ie}, global vegetation dynamics \citep{Scheiter:2013ed} and ecosystem processes \citep{Lavorel:2002ff}.
 
@@
 It has been widely expected that species with low tissue construction cost will typically have fast growth rates, at least in favourable physical environments \citep[e.g.][]{MullerLandau:2004dc,Poorter:2008iu,Chave:2009iy,Larjavaara:2010bn,Iida:2012jb,Paine:2015df}.
-Yet, recently a number of empirical studies indicate the correlation between traits and growth is not as consistent as that.
+Yet, recently a number of empirical studies indicate the correlation between traits and growth is not consistent.
 Consider SLA as an example.
@@
 Size has long been known to play a central role in organism design and function \citep{Vogel:1988ux, Vogel:2003wb}, including that of trees \citep{Farnsworth:1995im, Givnish:1995ta, King-2011}.
-As plants grow larger, a greater amount of the energy is devoted towards building and maintaining non-photosynthetic tissues \citep{Givnish:1995ta,King-2011}.
+As plants grow larger, a greater amount of energy is devoted towards building and maintaining non-photosynthetic tissues \citep{Givnish:1995ta,King-2011}.
 A recent model by \citet{Falster:2011ii} suggests this change shifts the benefits and costs of some trait-based trade-offs, such that the net effect of the trait on growth changes with size.
@@
 
-In this paper, we investigate for five prominent traits (specific leaf area = SLA, wood (or stem) tissue density, maximum leaf photosynthetic capacity per unit area = Aarea, maximum (or asymptotic height), and seed mass):
+In this paper, we consider five prominent traits (specific leaf area = SLA, wood (or stem) tissue density, maximum leaf photosynthetic capacity per unit area = Aarea, maximum (or asymptotic height), and seed mass) and we investigate:
 \begin{enumerate}
@@
 \end{enumerate}
-To address these questions we used a meta-analytic approach, compiling data from diverse studies reporting correlation coefficients between traits and growth.
+To address these questions we used a meta-analytic approach, compiling data from studies reporting correlation coefficients between traits and growth.
 While most studies investigating the link between traits and growth have not primarily been concerned with the effects of plant size, they have generally reported trait-growth correlations for identifiable ontogenetic stages (i.e.
@@
 We focused on tree and woody species since the mechanistic model used to assess our predictions is most applicable to these growth forms.
-We chose to assess our hypotheses via a meta-analysis because there already exist a considerable number of studies with salient information.
-Using these studies, we were able to assess our hypotheses across a much broader number of species and vegetation types than would have been possible in an experiential study.
-While, we anticipated a reasonably-sizeable literature on trait and growth to be available, we were uncertain about the representation of all trait-stages combinations.
-An additional goal of our study was therefore to identify gaps in the knowledge needed to improve our understanding of the link between trait and growth.
+Using a meta-analysis approach, we were able to assess our hypotheses across a much broader number of species and vegetation types than would have been possible in an experiential study.
+We anticipated a sizeable literature on traits and growth to be available but we were uncertain about the representation of all trait-stage combinations.
+An additional goal of our study was therefore to identify gaps in the knowledge needed to improve our understanding of the link between functional traits and plant growth.
 
@@
 
-Below we first outline equations for the new growth model, adapted from \citet{Falster:2011ii}.
-We then use this model to generate qualitative predictions on how the effect of traits on growth rate changes with plant size.
+We first outline equations for the new growth model, adapted from \citet{Falster:2011ii}.
+We then use this model to generate qualitative predictions for how the effect of traits on growth rate changes with plant size.
 These hypotheses are summarised in Table \ref{tab:trade-offs}.
@@
 where $\alpha_{\rm y}$ is the ratio of carbon fixed in mass per carbon assimilated, and $p$ is the assimilation rate of CO$_{2}$ per leaf area.
-Here, and in the following equations, $M_i$ denotes the \textbf{live mass on the plant}, $r_i$ the mass-specific \textbf{respiration rate}, and $k_i$ the \textbf{turnover rate} of different plant tissues; the subscripts $i = \rm{l,s,r,t,f}$ referring to leaves, sapwood and bark, roots, total of these vegetative tissues, and to the reproductive tissues (fruits, flowers etc.)  Similarly $A_i$ denotes \textbf{areas}, of leaves ($i = l$) and of cross-sections of total stem and sapwood ($i =\rm{st,ss}$) respectively.
-Note that the live biomass $B = M_{\rm t} + M_{\rm f}$.
-Applying the chain rule of differential calculus, the \textbf{growth rate in plant mass}, ($M_{\rm t}$), can be decomposed as
+Here, and in the following equations, $M_i$ denotes the \textbf{live mass on the plant}, $r_i$ the mass-specific \textbf{respiration rate}, and $k_i$ the \textbf{turnover rate} of different plant tissues; the subscripts $i = \rm{l,s,r,a,f}$ referring to leaves, sapwood and bark, roots, total of these vegetative tissues, and to the reproductive tissues (fruits, flowers etc.)  Similarly $A_i$ denotes \textbf{areas}, of leaves ($i = l$) and of cross-sections of total stem and sapwood ($i =\rm{st,ss}$) respectively.
+Note that the live biomass $B = M_{\rm a} + M_{\rm f}$.
+Applying the chain rule of differential calculus, the \textbf{growth rate in plant mass}, ($M_{\rm a} $), can be decomposed as
 \begin{equation}\label{eq:eq1}
-\underbrace{{\frac{\ud M_{\rm t}}{\ud t}}}_{\text{growth rate in mass}} = \underbrace{\frac{\ud M_{\rm t}}{\ud B}}_{\text{allocation to vegetative growth}}  \times \underbrace{\frac{\ud B}{\ud t}}_{\text{net live biomass production}},
+\underbrace{{\frac{\ud M_{\rm a} }{\ud t}}}_{\text{growth rate in mass}} = \underbrace{\frac{\ud M_{\rm a} }{\ud B}}_{\text{allocation to vegetative growth}}  \times \underbrace{\frac{\ud B}{\ud t}}_{\text{net live biomass production}},
 \end{equation}
-where $\frac{\ud M_{\rm t}}{\ud B}$ is the fraction of net live biomass increase that goes to vegetative growth rather than to production of reproductive tissues.
+where $\frac{\ud M_{\rm a} }{\ud B}$ is the fraction of net live biomass increase that goes to vegetative growth rather than to production of reproductive tissues.
 
@@
 \begin{equation}\label{eq:eq2}
-\underbrace{\frac{\ud H}{\ud t}}_{\text{growth rate in height}} = \underbrace{\frac{\ud H}{\ud A_{\rm l}}}_{\text{architecture layout}} \times \underbrace{{\frac{\ud A_{\rm l}}{\ud M_{\rm t}}}}_{\text{leaf deployment per mass}} \times {\frac{\ud M_{\rm t}}{\ud B}} \times {\frac{\ud B}{\ud t}}.
+\underbrace{\frac{\ud H}{\ud t}}_{\text{growth rate in height}} = \underbrace{\frac{\ud H}{\ud A_{\rm l}}}_{\text{architecture layout}} \times \underbrace{{\frac{\ud A_{\rm l}}{\ud M_{\rm a} }}}_{\text{leaf deployment per mass}} \times {\frac{\ud M_{\rm a} }{\ud B}} \times {\frac{\ud B}{\ud t}}.
 \end{equation}
 where $\ud H / \ud A_{\rm l}$, is the growth in plant height
-per unit growth in total leaf area -- accounting for the architectural
-strategy of the plant. We assume this function is unrelated to the traits considered in the current paper. The second term, $\ud A_{\rm l} / \ud M_{\rm t}$,
+per unit growth in total leaf area. This term expresses the architectural
+strategy of the plant.
+We assume it is unrelated to the traits considered in the current paper, in other words that it does not automatically change in response to changes in the traits.
+The second term, $\ud A_{\rm l} / \ud M_{\rm a} $,
 accounts for the marginal cost of deploying an additional unit of leaf
 area, including construction of the leaf itself and various support
-structures. As such, $\ud A_{\rm l} / \ud M_{\rm t}$
+structures.  $\ud A_{\rm l} / \ud M_{\rm a} $
 can itself be expressed as a sum of construction costs per unit leaf
@@
 \begin{equation}\label{eq:daldmt}
-\frac{\ud A_{\rm l}}{\ud M_{\rm t}}
+\frac{\ud A_{\rm l}}{\ud M_{\rm a} }
 = \left(\frac{\ud M_{\rm l}}{\ud A_{\rm l}}
@@
 \underbrace{{\frac{\ud A_{\rm st}}{\ud t}}}_{\text{basal area growth rate}} &=& \frac{\ud A_{\rm ss}}{\ud t} &+& \frac{\ud A_{\rm sh}}{\ud t} \\
-&=& \underbrace{\frac{\ud A_{\rm ss}}{\ud A_{\rm l}}  \times {\frac{\ud A_{\rm l}}{\ud M_{\rm t}}} \times  {\frac{\ud M_{\rm t}}{\ud B}} \times {\frac{\ud B}{\ud t}}}_{\text{increase in total sapwood}} &+&  \underbrace{k_{\rm ss} \times \frac{\ud A_{\rm ss}}{\ud t}}_{\text{sapwood turnover}},\\
+&=& \underbrace{\frac{\ud A_{\rm ss}}{\ud A_{\rm l}}  \times {\frac{\ud A_{\rm l}}{\ud M_{\rm a} }} \times  {\frac{\ud M_{\rm a} }{\ud B}} \times {\frac{\ud B}{\ud t}}}_{\text{increase in total sapwood}} &+&  \underbrace{k_{\rm ss} \times \frac{\ud A_{\rm ss}}{\ud t}}_{\text{sapwood turnover}},\\
 \end{array}
@@
 they do not depend on detailed assumptions about plant construction.
-To make qualitative predictions with respect to traits such as specific leaf area and wood density, however, we require one additional assumption: that the mass of sapwood tissue ($M_{\rm ss}$) increases disproportionately with respect to the plants leaf area ($A_{\rm l}$).
-This assumption, which is included in nearly every model of plant growth that has been developed, has the effect of changing the relative importance of different components within equations for $\frac{\ud B}{\ud t}$ and $\frac{\ud A_{\rm l}}{\ud M_{\rm t}}$ above as a plant increases in size.
+To make qualitative predictions with respect to traits such as specific leaf area and wood density we require one additional assumption: that the mass of sapwood tissue ($M_{\rm ss}$) increases disproportionately with respect to the plant's leaf area ($A_{\rm l}$).
+This assumption is included in nearly every model of plant growth that has been developed, on the basis that as stems grow longer the sapwood associated with each leaf must be increasing.
+It has the effect of changing the relative importance of different components within equations for $\frac{\ud B}{\ud t}$ (net live biomass production) and $\frac{\ud A_{\rm l}}{\ud M_{\rm a} }$ (marginal cost of deploying additional leaf area) as a plant increases in size.
 Specifically, in eq.
@@
 Similarly, in eq.
-\ref{eq:daldmt}, the costs of constructing sapwood support to support a given unit of leaf area, $\frac{\ud M_{\rm s}}{\ud A_{\rm l}}$, increases faster the cost of producing a unit of leaf area, $\frac{\ud M_{\rm l}}{\ud A_{\rm l}}$ which is simply the inverse of specific leaf area.
-Whether plant growth rate increases with a specific trait, therefore depends on how the trait effects the different elements of \ref{eq:eq0}-\ref{eq:eq4} and how those effects change with size (Table \ref{tab:trade-offs}).
+\ref{eq:daldmt}, the costs of constructing sapwood to support a given unit of leaf area, $\frac{\ud M_{\rm s}}{\ud A_{\rm l}}$, increases faster than the cost of producing a unit of leaf area, $\frac{\ud M_{\rm l}}{\ud A_{\rm l}}$ which is simply the inverse of specific leaf area.
+Whether plant growth rate increases with a specific trait, therefore depends on how the trait affects the different elements of \ref{eq:eq0}-\ref{eq:eq4} and how those effects change with size (Table \ref{tab:trade-offs}).
 
 Based on the above model and this single assumption about growth, we outline five hypotheses that arise by considering the influence of trait variation on elements of equations  \ref{eq:eq0}-\ref{eq:eq4} and how these may interact with plant size (see Table \ref{tab:trade-offs}).
-These hypotheses reflect a direct mechanistic causation between traits and growth rate.
 It is possible that other correlations may arise indirectly.
-Nevertheless, for purposes of this paper we adopt as working hypotheses only those arising from direct mechanistic causation.
-Moreover, we consider how predictions may vary when expressed on absolute and relative terms, for each of height, diameter, and mass-based growth (see Table \ref{tab:trade-offs}).
-For many trait and growth combinations, the predicted effect of the trait on growth is similar when expressed on relative and absolute terms.
+Nevertheless, for the purposes of this paper we adopt as working hypotheses only those arising from direct mechanistic causation.
+We consider predictions for each of height, diameter, and mass-based growth, and how they  may vary depending whether growth is expressed in absolute or relative terms, (see Table \ref{tab:trade-offs}).
+For many trait and growth combinations, the predicted effect of the trait on growth is similar when expressed in relative and absolute terms.
 However, this is not true for all traits (details given below).
-We therefore adopted a two-stage approach to our analysis, whereby we first assess patterns based on measurements of relative growth rate.
-
 \subsubsection*{H1: The relationship between SLA and growth rate is expected to shift from positive in seedlings to non-significant or negative in adult plants}
@@
 However, high-SLA species also have shorter leaf lifespan, and must use more energy replacing leaves lost via turnover \citep{Wright:2004jb}.
-These two effects occur within the terms  $\frac{\ud B}{\ud t}$ and $\frac{\ud A_{\rm l}}{\ud M_{\rm t}}$ in the above model.
-Whether plant growth rate increases with SLA depends on how the relative magnitude of the benefit (cheap leaf construction, via $\frac{\ud A_{\rm l}}{\ud M_{\rm t}}$ ) and cost (higher leaf turnover, via $\frac{\ud B}{\ud t}$) of increased SLA change with size (Table \ref{tab:trade-offs}).
-During early life, when leaf comprises a large part of the plant, decreasing SLA has an overwhelmingly positive effect on height and diameter growth rate, because the effect of reducing $\frac{\ud M_{\rm l}}{\ud A_{\rm l}}$ has a large effect compared to the other terms in eq.
+These two effects occur within the terms  $\frac{\ud B}{\ud t}$ (net live biomass production) and $\frac{\ud A_{\rm l}}{\ud M_{\rm a} }$ (marginal cost of deploying additional leaf area), appearing on the right side in the equations for growth rate (\ref{eq:eq1}, \ref{eq:eq2}, \ref{eq:eq03}).
+Whether plant growth rate increases with SLA depends on how the relative magnitude of the benefit (cheap leaf construction, via $\frac{\ud A_{\rm l}}{\ud M_{\rm a} }$ ) and cost (higher leaf turnover, via $\frac{\ud B}{\ud t}$) of increased SLA changes with size (Table \ref{tab:trade-offs}).
+During early life, when leaves comprise a large part of the plant, increasing SLA has an overwhelmingly positive effect on height and diameter growth rate, because the effect of reducing $\frac{\ud M_{\rm l}}{\ud A_{\rm l}}$ (the cost of producing a unit of leaf area) has a large effect compared to the other terms in eq.
 \ref{eq:daldmt}.
@@
 
-Cheaper stem construction (low wood density or stem density) increases the marginal rate of leaf deployment per total mass increment ($\frac{\ud A_{\rm l}}{\ud M_{\rm t}}$), and consequently increases growth rate in height and diameter (eqs.
+Assuming plants otherwise maintain a similar cross section of conducting tissue, cheaper stem construction (low wood density or stem density) will increase the marginal rate of leaf deployment per total mass increment ($\frac{\ud A_{\rm l}}{\ud M_{\rm a} }$), and consequently growth rate in height and diameter (eqs.
 \ref{eq:eq2}-\ref{eq:eq4}; Table \ref{tab:trade-offs}).
@@
 A similar shift is expected for growth in mass when expressed in relative terms.
-However, when expressed as absolute growth, the predicted relationship is non-significant along all plant size\citep[see also][]{Enquist-1999}.
+However, when expressed as absolute growth, the predicted relationship is non-significant along all plant size \citep[see also][]{Enquist-1999}.
 
@@
 As plants approach maximum height they increasingly divert energy away from growth and into reproduction (see \citealt{Thomas:1996do,Thomas-2011, Wenk:2015jz}).
-This effect occurs in the term $\frac{\ud M_{\rm t}}{\ud B}$ in the above model eqs.
-(\ref{eq:eq2}-\ref{eq:eq4}).
+This effect occurs in the term $\frac{\ud M_{\rm a} }{\ud B}$ (the allocation to vegetative growth) in eqs.
+(\ref{eq:eq2}-\ref{eq:3}).
 For seedlings, where all individuals are investing solely in growth, we expect no influence of maximum height on growth (i.e.
-$\frac{\ud M_{\rm t}}{\ud B} =1$).
+$\frac{\ud M_{\rm a} }{\ud B} =1$).
 But once some species begin to produce seed, then species closer to their maximum height value are expected to be allocating more to seed production and less to vegetative growth.
@@
 
-The main effect of increased seed size is to produce a larger overall seedling.
-Under similar light conditions, larger seedlings are therefore predicted to have larger absolute growth rates.
+The only effect of increased seed size in the above model is to produce a larger overall seedling.
+Under similar light conditions, larger seedlings are therefore predicted to have faster absolute growth rates.
 However, because the ratio of leaf area to total biomass decreases with plant size, larger seedlings are predicted to have lower mass-based growth rates during the earliest phases of growth \citep{Turnbull:2012ew}.
-Yet, as plants grow, we expect the effect of this initial size difference to be minimal, and the correlation between seed size and growth rate should therfore disappear.
-Thus for larger plants, seed mass is not expected to have any distinct influence on growth rates  (Table \ref{tab:trade-offs}).
+Yet, as plants grow, we expect the effect of this initial size difference to be minimal, and the correlation between seed size and growth rate should therefore disappear.
+For larger plants, seed mass is not expected to have any distinct influence on growth rates  (Table \ref{tab:trade-offs}).
 
-\subsection*{H5: The relationship between Aarea and growth rate is expected to be positive across all plant sizes, at least under high-light conditions}
+\subsection*{H5: The relationship between Aarea and growth rate is expected to be positive across all plant sizes, particularly under high-light conditions}
 
 We expect greater photosynthetic capacity to translate into faster growth rates by increasing the rate of biomass production (Table \ref{tab:trade-offs}), at least at high light where Aarea is typically measured.
-This effects occurs within the term  $\frac{\ud B}{\ud t} $ in the above model.
-The effects of benefits (higher assimilation) and costs (higher respiration) of increased Area occur within the same element of eq.
-\ref{eq:eq0}, and because assimilation is typically higher than respiration in high light, the net effect will be positive (Table \ref{tab:trade-offs}).
+This effect occurs by increasing  $\frac{\ud B}{\ud t} $ in eqs.
+(\ref{eq:eq1}-\ref{eq:eq3}).
+The positive effect of increasing Aarea (higher assimilation) may be offset by the costs (higher respiration), however, assuming both increase in proportion, and because assimilation is typically higher than respiration in high light, the net effect will be positive (Table \ref{tab:trade-offs}).
 It is uncertain how much this effect might translate to faster growth in low light.
@@
 
-We aimed to identify studies reporting a correlation across species, between traits and growth rate (e.g.
+We aimed to identify studies reporting a correlation across species, between traits and growth rates (e.g.
 relative or absolute growth, in diameter, height or mass, see Table \ref{tab:trade-offs}).
 Systematic searches were conducted across the two most comprehensive bibliographic platforms: Google scholar and Web of Science (Thomson Reuters).
-While Web of Science guarantees a relatively stable and reproducible search environment, with clearly defined lists of indexed journals, its searches are limited to meta-data (i.e.
+While Web of Science guarantees a relatively stable and reproducible search environment, with clearly defined lists of indexed journals, the searches are limited to meta-data (i.e.
 title, keywords, and abstracts, \citealt{Beckmann:2012hn}).
@@
 The authors of the 103 articles used in this analysis reported their plants as belonging to any of five different stages: ``seedling'', ``juvenile'', ``sapling'', ``adult'', ``mixed''.
-While these categories have been established according to the expertise of the authors, we were concerned about the risk of assigning plants of similar size to different categories when compiling data across multiple studies and vegetation types.
+Because these categories were established according to the expertise of the authors, we were concerned about the risk of assigning plants of similar size to different categories when compiling data across multiple studies and vegetation types.
 This risk turned out to be small: overall, we found that the original thresholds in size/age used by the authors to distinguish different stages were relatively compatible (Fig.
@@
 
-The entire dataset included studies differing in the growth measurement used (relative of absolute), the number of species, the experimental conditions (stressed vs unstressed), and the concordance between stages used to measure trait and growth rate.
-However relative growth rate and absolute growth rate are fundamentally different for a lot of ecologists.
-And the number of species used to perform the correlation, the experimental conditions, and the concordance between stages used to measure trait and growth are clear criteria for assessing the quality of the data for addressing our hypotheses.
-So we adopted a two steps approach, first we were conservative by focusing exclusively on relative growth rate, across \underline{\textgreater} 10 species, under unstressed conditions, and where the source of the trait and growth is the same (expect for maximum height and seed mass, where a particular stage is by definition required to measure the trait).
+The entire dataset included studies differing in the growth measurement used (relative or absolute), the number of species, the experimental conditions (stressed vs unstressed), and the concordance between stages used to measure trait and growth rate.
+However, these differences are clear criteria for assessing the quality of the data for addressing our hypotheses.
+Consequently, we adopted a two-stage approach where at first we were conservative by focusing exclusively on relative growth rate, across \underline{\textgreater} 10 species, under unstressed conditions, and where the source of the trait and growth is the same (expect for maximum height and seed mass, where a particular stage is by definition required to measure the trait).
 This dataset is called the ``ideal'' dataset.
-Then we compared results with those of a more inclusive dataset - the entire dataset- with both relative growth rate and absolute growth rate, and all others criteria relaxed.
+Then we compared results with those of a more inclusive dataset - the “entire” dataset- with both relative growth rate and absolute growth rate, and all other criteria relaxed.
 
@@
 
-\subsubsection*{Stage effect}\label{stage-effect}
+\subsubsection*{Ontogenetic stage effect}\label{stage-effect}
 
-We tested an effect of ontogenetic stage on the relationship between growth rate and traits using a mixed-effect model, in which it was assumed that studies within a stage shared a common mean effect, but that there was also random variation among studies, in addition to sampling variation \citep{Zuur:2009cfa}.
+We tested an effect of ontogenetic stage on the relationship between growth rate and traits using a mixed-effect model.
+In this model, the response variable corresponds to the z-transformed coefficients of correlation calculated above, and it was assumed that studies within a stage shared a common mean effect, but that there was also random variation among studies, in addition to sampling variation \citep{Zuur:2009cfa}.
 Inclusion of this random effect allowed us to account for heterogeneity among studies, for example in experimental type, and vegetation type.
-For each trait, we established whether stage could additional explain variance in $z$ by comparing models with a without a stage effect  using log-likelihood ratios \citep{Zuur:2009cfa}.
+For each trait, we performed a separate model and we established whether stage could explain additional variance in $z$ by comparing models with and without a stage effect using log-likelihood ratios \citep{Zuur:2009cfa}.
 If the log-likelihood test returned a significant p-value, the stage model fitted the data better than the model without.
 Estimates of the effect size for each stage were considered significant if the CIs did not overlap with zero.
+Non-overlapping CIs across stages highlighted significant differences in effect sizes.
 
@@
 We also tested how robust our results were to the decisions made in the analysis.
-Specifically, we assessed the sensitivity of our results to inclusion of studies reporting multiple trait-growth correlation across different conditions (e.g.
+Specifically, we assessed the sensitivity of our results to inclusion of studies reporting multiple trait-growth correlations across different conditions (e.g.
 vegetation type, sites, environmental treatment).
@@
 
-% x <- remake::make("CleanData")
-% unqiue(x$ref)
-% nrow(x)
-% x <- remake::make("CompleteData")
-% unique(x$ref)
-% nrow(x)
-% x <- remake::make("IdealData")
-% unique(x$ref)
-% nrow(x)
-\subsection*{Representation of stages among 19 traits}
-In total, correlations had been reported for at least two different stages across 18 traits out of the 19 targeted (Fig.
+\subsection*{Representation of ontogenetic stages among 19 traits}
+In total, correlations had been reported for at least two different stages across 17 traits out of the 19 targeted (Fig.
 \ref{fig:fig1}).
 We had thought it likely that for some traits, correlations would be reported only for one growth stage.
-But this limitation applied only for LAR and NARmass, where studies appeared confined to seedling stages.
-However, for a majority of traits the number of observations across stage was highly unbalanced; for one-third of the 19 traits $>$ 75\% of correlations with growth reported come from a single stage (Fig.
+But this limitation applied only for NARmass and vessel density, where studies appeared confined to seedling and adult stages respectively.
+However, for a majority of traits the number of observations across stage was highly unbalanced; for one-third of the 19 traits $>$ 75\% of correlations with growth reported come from a same stage (Fig.
 \ref{fig:fig1}).
@@
 Overall, results were consistent with predictions, although with limitations arising for some traits due to very unequal (and limited) numbers of observations between growth stages.
-We identified only 55 studies with 137 correlations reporting data measured under ``ideal'' conditions: unstressed growth, growth measured as relative growth rate, traits and growth recorded in same stage, and correlation coefficient calculated across \underline{\textgreater} 10 species.
+We identified only 55 studies containing 137 correlations reporting data measured under ``ideal'' conditions: unstressed growth, growth measured as relative growth rate, traits and growth recorded in same stage, and correlation coefficient calculated across \underline{\textgreater} 10 species.
 
@@
 For wood density, maximum height, and seed mass, correlations with relative growth rate were also consistent with expectations but our ability to test all hypotheses was at times limited due to low sample size.
-Indeed, while meta-analysis are possible even with few observations, strong conclusions are generally precluded by very large CIs of the effect size (i.e CI often spanned zero).
+Indeed, while meta-analysis is possible even with few observations, strong conclusions are generally precluded by very large CIs of the effect size (i.e highly uncertain estimates and CI often spanned zero).
+
 For wood density, results were consistent with the prediction for negative correlations with relative growth rate across all plant sizes (Fig.
@@
 Accordingly, model fits were marginally improved when stage was incorporated (p.value = 0.049).
-Note that the CIs were not crossing zero for seedling and sapling stage despite the small sample sizes (n= 1 and 4 respectively), meaning a strong correlation and/or a good consistency in the coefficient reported for each stage across studies.
+Note that the CIs did not cross zero for seedling and sapling stage despite the small sample sizes (n= 1 and 4 respectively), meaning a strong correlation and/or a good consistency in the coefficient reported for each stage across studies.
 
@@
 Here, maximum height was positively correlated with growth at adult stage ($\bar{r}= 0.38 \pm 0.05$), not correlated at sapling stage (Fig \ref{fig:fig3}c, CIs overlapping zero) and no data were recorded for seedling stage.
-While these results were consistent with expectation, we could not distinguish with another alternative: maximum height was correlated to growth for adult stage, but the correlation between maximum height and growth at sapling stage was not significantly different from that observed at adult stage (model fit not improved when stage was incorporated, see log likelihood ratio tests in Fig.
+While these results were consistent with our expectation that maximum height would be correlated with growth at adult stage, they did not differ significantly across ontogenetic stages (model fit not improved when stage was incorporated, see log likelihood ratio tests in Fig.
 \ref{fig:fig3}c, and CIs overlapping between sapling and adult stages).
@@
 Again we could not distinguish between these alternatives.
-But unlike maximum height, the number of coefficient reported for seed mass was almost similar between adult (n= 7) and seedling (n= 10) stages, suggesting that CIs overlapping zero at adult stage were due to variation in correlation coefficient reported rather than to a much smaller numbers of replicates.
+But unlike maximum height, the number of coefficients reported for seed mass was almost similar between adult (n= 7) and seedling (n= 10) stages, suggesting that CIs overlapping zero at adult stage were due to variation in correlation coefficients reported rather than to a much smaller numbers of replicates.
 
 For Aarea, results were consistent with a positive correlation with relative growth rate at seedling stage.
-However, no conclusion can be drawn about a change along ontogenetic stages; as only four correlation coefficients were reported for this trait, and three of these were measured at the seedling stage (Fig.
+However, no conclusion can be drawn about a change along ontogenetic stages as only four correlation coefficients were reported for this trait, and three of these were measured at the seedling stage (Fig.
 \ref{fig:fig3}e).
@@
 We now report results from the entire dataset.
-Our aim is to determine if additional data alters or reinforce the above conclusions, by increasing replication.
+Our aim is to determine if additional data alters or reinforces the above conclusions, by increasing replication.
 This entire dataset included correlations measured with both absolute growth rate and relative growth rate (Fig.
 \ref{fig:fig4}), across at least two species (but measured using several individuals), and did not control for the source of trait or growth (i.e.
-trait could be measured on a different ontogenetic stage to growth data) or environmental conditions.
+traits could be measured on a different ontogenetic stage to growth data) or environmental conditions.
 The relaxed criteria considerably increased the number of replicates, from $n = 137$ to $n = 267$ correlations across 93 articles.
@@
 On the 13 traits-stage combinations studied in total, six had $\le$ five correlation coefficients: Wood density-seedling, maximum height-sapling, maximum height-seedling, Seed mass-sapling, Aarea-adult and Aarea-sapling.
-
-% x <- remake::make("CompleteData")
-% nrow(x)
 
@@
 \ref{fig:fig3}d) and entire dataset (Fig.
-\ref{fig:fig4}d), indicated little effect of stress (here mainly low light) on the correlation with relative growth rate at seedling stage; as the correlation was still positive when 8 correlations measured under low light conditions were added.
-For maximum height, there were still too few replicates to conclude undoubtedly on the correlation to be absent for smaller sizes.
+\ref{fig:fig4}d), indicated little effect of stress (here mainly low light) on the correlation with relative growth rate at seedling stage as the correlation was still positive when 8 correlations measured under low light conditions were added.
+For maximum height, there were still too few replicates to conclude undoubtedly that the correlation is absent for smaller sizes.
 
-We had hypotheses for seed mass, SLA and wood density, about a change in the correlation between trait and absolute growth rate was used instead of relative growth rate, or as mass was used instead of diameter and height.
-For seed mass, effects size differed significantly between relative growth rate and absolute growth rate at seedling stage; as expected the correlation with relative growth rate was positive and shifted to non significant with absolute growth rate (Fig \ref{fig:fig4}d; CI not overlapping).
-For SLA, the correlation was expected to shift from positive to non significant if growth in mass was measured on absolute instead of relative terms; however, here none of the data have been measured with absolute rates in the seedling stage (Fig.
+We had hypotheses for seed mass, SLA and wood density, about a change in the correlation between trait and growth rate if absolute growth rate was used instead of relative growth rate, or if mass was used instead of diameter and height.
+For seed mass, effect size differed significantly between relative growth rate and absolute growth rate at seedling stage; as expected the correlation with relative growth rate was positive and shifted to non significant with absolute growth rate (Fig \ref{fig:fig4}d; CI not overlapping).
+For SLA, the correlation was expected to shift from positive to non significant if growth in mass was measured on absolute instead of relative terms; however, none of the data were measured with absolute rates in the seedling stage (Fig.
 \ref{fig:figA8}).
@@
 Yet, the correlation coefficients recorded for absolute growth rate came from \citet{Augspurger:1984ct}, and unlike others they used wood density values from adult plants together with growth from juveniles.
-So it was not possible to distangle the effect of growth measurement from the effect of trait origine.
-For other traits, effect size were generally consistent between relative growth rate and absolute growth rate when both measurement were available.
+So it was not possible to disentangle the effect of growth measurement from the effect of trait origin.
+For other traits, effect sizes were generally consistent between relative growth rate and absolute growth rate when both measurements were available.
 
@@
 Growth form, experiment type and growth measurement type were not strong predictors in general (Fig.
-\ref{fig:figA6}); suggesting confounding with these factors is not a likely explanation of the major results reported.
+\ref{fig:figA6}); suggesting that these factors are not like explanations for the  major results reported.
 
@@
 For five prominent traits, the patterns observed were consistent with specific predictions from a mechanistic growth model.
-This suggests the mechanisms through which traits affect growth may be correctly understood in the model.
-For SLA the meta-analysis confirmed quite strongly the predicted influence of plant size on the trait-growth correlation.
-For wood density, Aarea, seed mass and maximum height results were consistent with predictions, but coverage was limited and additional studies would be helpful for some trait-growth-stage relationships.
+This suggests the mechanisms through which traits affect growth are correctly represented in the model.
+For SLA the meta-analysis strongly confirmed the predicted influence of plant size on the trait-growth correlation.
+For wood density, Aarea, seed mass and maximum height results were consistent with predictions, but data was limited and additional studies would be helpful for these trait-growth-stage relationships.
 
 While it has previously been noted that the correlation of SLA with growth rate disappears among saplings and larger trees (\citealt{Wright:2010tp} for Barro Colorado Island forest, Panama), our meta-analysis generalises that result.
-Several authors have suggested that the disappearance of SLA's influence on growth might be due to a disproportionate accumulation of leaf area individuals with low SLA \citep{Reich:1992wm, Poorter:2008iu,Wright:2010tp}, yet it remains unclear whether such a mechanism works as intended.
+Several authors have suggested that the disappearance of SLA's influence on growth might be due to a disproportionate accumulation of leaf area by individuals with low SLA \citep{Reich:1992wm, Poorter:2008iu,Wright:2010tp}, yet it remains unclear whether such a mechanism works as intended.
 Further, the assumed empirical relationship between SLA and total leaf area does not hold true as a generalisation across large number of species \citep{Duursma-2015}.
-In another modelling study, the SLA optimising growth rate was found to decrease with plant size, because of cross connections with the amount of self-shading in the crown and the increase in support costs in larger plants.
+In another modelling study, the SLA optimising growth rate was found to decrease with plant size, because of cross connections with the amount of self-shading in the crown and the increase in support costs in larger plants \citep{King-1999}.
 In the model described here, the mechanism is slightly different: high-SLA species incur faster leaf turnover, the cost of which outweighs the benefits of cheap leaf construction at larger sizes.
@@
 Lower xylem conductance and associated lower photosynthetic potential have also been suggested \citep[reviewed by][]{Chave:2009iy}.
-For seedlings a negative correlation arose regardless wood density was measured on adult plants, or calculated as seedling stem segment dry weight over its volume (i.e.
+For seedlings a negative correlation arose regardless of whether wood density was measured on adult plants, or calculated as seedling stem segment dry weight over its volume (i.e.
 stem density in  \citealt{CastroDiez:1998gz}), suggesting that both measurements could be used.
@@
 Meta-analyses showed a positive correlation for adult and seedling but not for saplings (n=3).
-In the seedling stage, where most of data were available, we noted no signal of an effect of low light on the positive correlation between Aarea and growth rate.
+In the seedling stage, where most data were available, we noted no signal of an effect of low light on the positive correlation between Aarea and growth rate.
 
@@
 While the results of the meta-analysis were consistent with the expected pattern for maximum height, we noted that a limited number of replicates were available for both saplings (n=4) and seedling stages (n=1).
-Consequently, subsequent research are welcomed to validate this result.
+Consequently, subsequent research is welcomed to validate this result.
 
@@
 For example, several papers have suggested that correlations between maximum height and growth rate may arise via cross-correlation with other traits such as wood density \citep{Thomas:1996do, Poorter:2006vb, Wright:2010tp}.
-These studies also suggest species towards one end of a trait spectrum may generally be found in better light.
+These studies also suggest species towards one end of a trait spectrum may generally be found in higher light.
 Similarly, effects of seed mass on growth have been suspected to be mediated via other traits \citep{Shipley:1990js,Westoby:2002ft,Poorter:2006vb}.
@@
 
-A lot of biotic and abiotic conditions such as light and water micro-environments can affect growth rates, and might modify correlations with traits in relation to plant size.
+Many biotic and abiotic conditions such as light and water micro-environments can affect growth rates, and might modify correlations with traits in relation to plant size.
 For example, instead of a positive relationship that disappeared with plant size, \citet{Iida:2014ep} found SLA was negatively correlated with relative growth rate at small size and positively correlated with relative growth rate at larger sizes.
@@
 We thank Andrea Stephens for helpful comments on the meta-analyses, and Sean Gleason et al for pre-publication access to their data.
-Charles Warren and Jordi Mart{\'i}nez-Vilalta kindly provided additional information about their published results.
-This work was funded by the Australian Research Council through a fellowship to M.W, a discovery grant to D.S.F and a Macquarie University Research Fellowships to E.F.G.
+Charles Warren and Jordi Mart{\'{i}}nez-Vilalta kindly provided additional information about their published results.
+This work was funded by the Australian Research Council through a fellowship to M.W, a discovery grant to D.S.F and a Macquarie University Research Excellence Scholarship and L’Oreal UNESCO FWIS Fellowship to E.F.G.
 
@@
 \includegraphics[width=15cm,height=20cm,keepaspectratio]{output/Fig2.pdf}
-\caption{The range of plant sizes and stage recoded in original publications (horizontal coloured lines), compared to standardised thresholds used in the analysis (vertical black lines).
-Horizontal line segments indicate the size range (max., min.) for the plants used to measure growth.
-The solid vertical lines indicate the thresholds used to classify plants in one of three stages in our meta-anlyses.
-Studies mark with a ''*'' were those where stage was changed or assigned, compared to the original publication.
-}
+\caption{ The range of plant sizes and stages recorded in original publications (horizontal coloured lines), compared to standardised thresholds used in the analysis (vertical black lines).
+Horizontal line segments indicate the size range (max., min.) of the plants used to measure growth.
+Horizontal line colours refer to the original stage attributed by the authors .The solid vertical lines indicate the thresholds used to classify plants in one of three stages in our meta-analyses.
+Studies marked with a “*” were those where stage was changed or assigned, compared to the original publication.}
 \label{fig:fig2}
@@
   \multicolumn{9}{ l } {\textbf{Elements of equations \ref{eq:eq0} -- \ref{eq:eq4}}}  \\
-  & \multicolumn{2}{ l } {Leaf deployment per mass}  & $\ud A_{\rm l} / \ud M_{\rm t}$ & \\
+  & \multicolumn{2}{ l } {Leaf deployment per mass}  & $\ud A_{\rm l} / \ud M_{\rm a} $ & \\
     & &     \tabitem leaf  &  & $\uparrow$ & - & - & - & - \\
@@
     & &     \tabitem root & & - & - & - & - & - \\
-  & \multicolumn{2}{ c } {Allocation to vegetative growth} & $\ud M_{\rm t} / \ud B$ & - & - & $\uparrow$ & - & - \\
+  & \multicolumn{2}{ c } {Allocation to vegetative growth} & $\ud M_{\rm a} / \ud B$ & - & - & $\uparrow$ & - & - \\
   & & & & & & \\
@@
   & \multicolumn{2}{ l } {in mass} \\
-  & & \tabitem{Absolute} & $\ud M_{\rm t} / \ud t$ & $\downarrow$\sepp$\downarrow$ & $-$\sepp$-$ &  $-${\sepp}$\uparrow$ & $\uparrow${\sepp}$-$ & $\uparrow${\sepp}$\uparrow$ \\
-  & & \tabitem{Relative} & $\ud M_{\rm t} / \ud t / M_{\rm t}$ & $\uparrow${\sepp}$\downarrow$ & $\downarrow${\sepp}$\downarrow$ &  $-${\sepp}$\uparrow$ & $\downarrow${\sepp}$-$ & $\uparrow${\sepp}$\uparrow$ \\
+  & & \tabitem{Absolute} & $\ud M_{\rm a} / \ud t$ & $\downarrow$\sepp$\downarrow$ & $-$\sepp$-$ &  $-${\sepp}$\uparrow$ & $\uparrow${\sepp}$-$ & $\uparrow${\sepp}$\uparrow$ \\
+  & & \tabitem{Relative} & $\ud M_{\rm a} / (\ud t .
+M_{\rm a} )$ & $\uparrow${\sepp}$\downarrow$ & $\downarrow${\sepp}$\downarrow$ &  $-${\sepp}$\uparrow$ & $\downarrow${\sepp}$-$ & $\uparrow${\sepp}$\uparrow$ \\
   & \multicolumn{2}{ l } {in height} \\
   & & \tabitem{Absolute} & $\ud H / \ud t$ & $\uparrow${\sepp}$\downarrow$ & $\downarrow${\sepp}$\downarrow$ & $-${\sepp}$\uparrow$ & $\uparrow${\sepp}$-$ & $\uparrow${\sepp}$\uparrow$ \\
-  & & \tabitem{Relative} & $\ud H / \ud t / H$ & $\uparrow${\sepp}$\downarrow$ & $\downarrow${\sepp}$\downarrow$ & $-${\sepp}$\uparrow$ & $\downarrow${\sepp}$-$ & $\uparrow${\sepp}$\uparrow$ \\
+  & & \tabitem{Relative} & $\ud H / (\ud t . H)$ & $\uparrow${\sepp}$\downarrow$ & $\downarrow${\sepp}$\downarrow$ & $-${\sepp}$\uparrow$ & $\downarrow${\sepp}$-$ & $\uparrow${\sepp}$\uparrow$ \\
   & \multicolumn{2}{ l } {in diameter} \\
   & & \tabitem{Absolute} & $\ud D / \ud t$ & $\uparrow${\sepp}$\downarrow$ & $\downarrow${\sepp}$\downarrow$ & $-${\sepp}$\uparrow$ & $\uparrow${\sepp}$-$ & $\uparrow${\sepp}$\uparrow$ \\
-  & & \tabitem{Relative} & $\ud D / \ud t / D$ & $\uparrow${\sepp}$\downarrow$ & $\downarrow${\sepp}$\downarrow$ & $-${\sepp}$\uparrow$ & $\downarrow${\sepp}$-$ & $\uparrow${\sepp}$\uparrow$ \\
+  & & \tabitem{Relative} & $\ud D / (\ud t . D)$ & $\uparrow${\sepp}$\downarrow$ & $\downarrow${\sepp}$\downarrow$ & $-${\sepp}$\uparrow$ & $\downarrow${\sepp}$-$ & $\uparrow${\sepp}$\uparrow$ \\
 \hline

### 2016-02-19 MS.tex
Clarify predictions for mass-based growth, plus minor edits throughout

@@
 As plants grow larger, a greater amount of energy is devoted towards building and maintaining non-photosynthetic tissues \citep{Givnish:1995ta,King-2011}.
-A recent model by \citet{Falster:2011ii} suggests this change shifts the benefits and costs of some trait-based trade-offs, such that the net effect of the trait on growth changes with size.
-Thus the absence of a correlation between SLA and growth at larger sizes may in fact be expected, when potential influences of traits on plant function are considered \citep{Falster:2011ii}.
-While recent empirical studies support the idea that the relationship between traits and growth rates may change with size (\citealt{Iida:2014ep, Iida:2014hq}), the trend and mechanisms behind this variation remain unclear.
+A recent model by \citet{Falster:2011ii} suggests that increased size shifts the benefits and costs of some trait-based trade-offs, such that the net effect of the trait on growth changes with size.
+Thus the absence of a correlation between SLA and growth at larger sizes may in fact be expected, when the potential influences of traits on plant function are properly considered \citep{Falster:2011ii}.
+While some recent empirical studies support the idea that the relationship between traits and growth rates may change with size (\citealt{Iida:2014ep, Iida:2014hq}), the generality of the trend and mechanisms behind this variation remain unclear.
 
@@
 Specific predictions arise from considering the influence of traits on elements of these equations and how these effects may vary with size.
-This model extends earlier efforts to model growth as a function of traits \citep{Lambers:1992bj,Cornelissen:1996hf,Wright:2000kw,Enquist:2007ek}.
+This model extends earlier efforts to model mass-based growth of seedlings as a function of traits \citep{Lambers:1992bj,Cornelissen:1996hf,Wright:2000kw,Enquist:2007ek}.
 However, whereas earlier models focused solely on mass-based relative growth rate and did not predict a change in effect of traits with size, the revised equations do allow for these effects, while also making predictions for both absolute and relative growth in any of mass (eq.
@@
 \begin{equation}\label{eq:eq2}
-\underbrace{\frac{\ud H}{\ud t}}_{\text{growth rate in height}} = \underbrace{\frac{\ud H}{\ud A_{\rm l}}}_{\text{architecture layout}} \times \underbrace{{\frac{\ud A_{\rm l}}{\ud M_{\rm a} }}}_{\text{leaf deployment per mass}} \times {\frac{\ud M_{\rm a} }{\ud B}} \times {\frac{\ud B}{\ud t}}.
+\underbrace{\frac{\ud H}{\ud t}}_{\text{growth rate in height}} = \underbrace{\frac{\ud H}{\ud A_{\rm l}}}_{\text{architecture layout}} \times \underbrace{{\frac{\ud A_{\rm l}}{\ud M_{\rm a} }}}_{\text{leaf deployment per mass}} \times {\frac{\ud M_{\rm a} }{\ud B}} \times {\frac{\ud B}{\ud t}},
 \end{equation}
-where $\ud H / \ud A_{\rm l}$, is the growth in plant height
+where $\ud H / \ud A_{\rm l}$ is the growth in plant height
 per unit growth in total leaf area. This term expresses the architectural
@@
 We assume it is unrelated to the traits considered in the current paper, in other words that it does not automatically change in response to changes in the traits.
-The second term, $\ud A_{\rm l} / \ud M_{\rm a} $,
+The term $\ud A_{\rm l} / \ud M_{\rm a} $
 accounts for the marginal cost of deploying an additional unit of leaf
@@
 structures.  $\ud A_{\rm l} / \ud M_{\rm a} $
-can itself be expressed as a sum of construction costs per unit leaf
-area,
+can itself be expressed as a sum of costs per unit leaf
+area for constructing various support tissues,
 \begin{equation}\label{eq:daldmt}
@@
 \underbrace{{\frac{\ud A_{\rm st}}{\ud t}}}_{\text{basal area growth rate}} &=& \frac{\ud A_{\rm ss}}{\ud t} &+& \frac{\ud A_{\rm sh}}{\ud t} \\
-&=& \underbrace{\frac{\ud A_{\rm ss}}{\ud A_{\rm l}}  \times {\frac{\ud A_{\rm l}}{\ud M_{\rm a} }} \times  {\frac{\ud M_{\rm a} }{\ud B}} \times {\frac{\ud B}{\ud t}}}_{\text{increase in total sapwood}} &+&  \underbrace{k_{\rm ss} \times \frac{\ud A_{\rm ss}}{\ud t}}_{\text{sapwood turnover}},\\
+&=& \underbrace{\frac{\ud A_{\rm ss}}{\ud A_{\rm l}}  \times {\frac{\ud A_{\rm l}}{\ud M_{\rm a} }} \times  {\frac{\ud M_{\rm a} }{\ud B}} \times {\frac{\ud B}{\ud t}}}_{\text{increase in total sapwood}} &+&  \underbrace{k_{\rm ss} \times \frac{\ud A_{\rm ss}}{\ud t}}_{\text{sapwood turnover}}.\\
 \end{array}
 \end{equation}
-where $\frac{\ud A_{\rm ss}}{\ud A_{\rm l}} $ is the  sapwood area per leaf area.
+Here $\frac{\ud A_{\rm ss}}{\ud A_{\rm l}} $ is the  sapwood area per leaf area.
 The \textbf{growth rate in diameter} is then obtained via the geometric relationship between stem diameter and stem area,
 \begin{equation}\label{eq:eq4}
-\underbrace{\frac{\ud D}{\ud t}}_{\text{growth rate in diameter}} = \sqrt[]{\frac{\Pi}{A_{\rm st}}} \times {\frac{\ud A_{\rm st}}{\ud t}}.
+\underbrace{\frac{\ud D}{\ud t}}_{\text{growth rate in diameter}} = \left(\Pi \, A_{\rm st}\right)^{-0.5} \times {\frac{\ud A_{\rm st}}{\ud t}}.
 \end{equation}
@@
 To make qualitative predictions with respect to traits such as specific leaf area and wood density we require one additional assumption: that the mass of sapwood tissue ($M_{\rm ss}$) increases disproportionately with respect to the plant's leaf area ($A_{\rm l}$).
-This assumption is included in nearly every model of plant growth that has been developed, on the basis that as stems grow longer the sapwood associated with each leaf must be increasing.
+This assumption is included in nearly every model of plant growth that has been developed, on the basis that as stems grow longer the total mass of sapwood associated with each leaf must be increasing \citep[e.g.][]{Falster:2011ii,King-1999,Enquist:2007ek}.
 It has the effect of changing the relative importance of different components within equations for $\frac{\ud B}{\ud t}$ (net live biomass production) and $\frac{\ud A_{\rm l}}{\ud M_{\rm a} }$ (marginal cost of deploying additional leaf area) as a plant increases in size.
@@
 Nevertheless, for the purposes of this paper we adopt as working hypotheses only those arising from direct mechanistic causation.
-We consider predictions for each of height, diameter, and mass-based growth, and how they  may vary depending whether growth is expressed in absolute or relative terms, (see Table \ref{tab:trade-offs}).
+We consider predictions for each of height, diameter, and mass-based growth, and how they  may vary depending whether growth is expressed in absolute or relative terms (see Table \ref{tab:trade-offs}).
 For many trait and growth combinations, the predicted effect of the trait on growth is similar when expressed in relative and absolute terms.
@@
 
-Plants with high SLA can deploy a unit of leaf area more cheaply.
+By definition, plants with high SLA can deploy a unit of leaf area more cheaply.
 However, high-SLA species also have shorter leaf lifespan, and must use more energy replacing leaves lost via turnover \citep{Wright:2004jb}.
-These two effects occur within the terms  $\frac{\ud B}{\ud t}$ (net live biomass production) and $\frac{\ud A_{\rm l}}{\ud M_{\rm a} }$ (marginal cost of deploying additional leaf area), appearing on the right side in the equations for growth rate (\ref{eq:eq1}, \ref{eq:eq2}, \ref{eq:eq03}).
+These two effects occur within the terms  $\frac{\ud B}{\ud t}$ (net live biomass production) and $\frac{\ud A_{\rm l}}{\ud M_{\rm a} }$ (marginal cost of deploying additional leaf area), appearing on the right side in the equations for growth rate (\ref{eq:eq1}, \ref{eq:eq2}, \ref{eq:eq3}).
 Whether plant growth rate increases with SLA depends on how the relative magnitude of the benefit (cheap leaf construction, via $\frac{\ud A_{\rm l}}{\ud M_{\rm a} }$ ) and cost (higher leaf turnover, via $\frac{\ud B}{\ud t}$) of increased SLA changes with size (Table \ref{tab:trade-offs}).
@@
 \ref{eq:daldmt}.
-Consequently, the relative effect of leaf turnover comes to dominate at larger sizes, and as such, the effect of SLA on height and diameter growth shifts from positive to negative as plants increase in size.
-A similar shift is expected for growth in mass when expressed in relative terms.
-However, when expressed as absolute growth, the predicted relationship is negative.
-This occurs because of the increased turnover of high SLA species.
+Consequently, the effect of leaf turnover becomes relatively stronger at larger sizes, and as such, the effect of SLA on height, diameter and, mass growth shifts from positive to negative as plants increase in size.
+Note in the case of mass growth, the effect of cheaper leaf construction is realised not in the $\frac{\ud A_{\rm l}}{\ud M_{\rm a} }$ term , but as a greater total leaf area at a given mass, i.e.
+the accumulated effect of past reductions in  $\frac{\ud A_{\rm l}}{\ud M_{\rm a} }$.
 
@@
 Because the relative expenditure on stem compared to leaf increases as plants grow larger, the relationship between wood density and growth may also strengthen in larger plants.
-A similar shift is expected for growth in mass when expressed in relative terms.
-However, when expressed as absolute growth, the predicted relationship is non-significant along all plant size \citep[see also][]{Enquist-1999}.
+A similar shift is expected for growth in mass growth, in either absolute or relative terms.
+Note in the case of mass growth, the effect of cheaper stem construction is realised not in the $\frac{\ud A_{\rm l}}{\ud M_{\rm a} }$ term , but via greater total leaf area at a given mass, i.e.
+the accumulated effect of past reductions in  $\frac{\ud A_{\rm l}}{\ud M_{\rm a} }$.
 
@@
 This effect occurs in the term $\frac{\ud M_{\rm a} }{\ud B}$ (the allocation to vegetative growth) in eqs.
-(\ref{eq:eq2}-\ref{eq:3}).
+(\ref{eq:eq2}-\ref{eq:eq3}).
 For seedlings, where all individuals are investing solely in growth, we expect no influence of maximum height on growth (i.e.
@@
 This dataset is called the ``ideal'' dataset.
-Then we compared results with those of a more inclusive dataset - the “entire” dataset- with both relative growth rate and absolute growth rate, and all other criteria relaxed.
+We then compared the results from the ``ideal'' dataset with those from the entire dataset - with both relative growth rate and absolute growth rates, and all other criteria relaxed.
 
@@
   & \multicolumn{2}{ l } {Net live biomass production} & $\ud B / \ud t$ & & & & & \\
-  & &     \tabitem photosynthesis & & - & - & - & - & $\uparrow$  \\
-  & &     \tabitem respiration   & & - & - & - & - & $\uparrow$  \\
-  & &     \tabitem leaf turnover & & $\downarrow$ & - & - & - & - \\
+  & &     \tabitem photosynthetic rate & & - & - & - & - & $\uparrow$  \\
+  & &     \tabitem respiration rate  & & - & - & - & - & $\uparrow$  \\
+  & &     \tabitem leaf turnover rate & & $\downarrow$ & - & - & - & - \\
   & \multicolumn{2}{ l } {Architecture} & $\ud H / \ud A_{\rm l}$ & - & - & - & - & - \\
@@
   & \multicolumn{2}{ l } {in mass} \\
-  & & \tabitem{Absolute} & $\ud M_{\rm a} / \ud t$ & $\downarrow$\sepp$\downarrow$ & $-$\sepp$-$ &  $-${\sepp}$\uparrow$ & $\uparrow${\sepp}$-$ & $\uparrow${\sepp}$\uparrow$ \\
+  & & \tabitem{Absolute} & $\ud M_{\rm a} / \ud t$ & $\uparrow$\sepp$\downarrow$ & $\downarrow${\sepp}$\downarrow$ &  $-${\sepp}$\uparrow$ & $\uparrow${\sepp}$-$ & $\uparrow${\sepp}$\uparrow$ \\
   & & \tabitem{Relative} & $\ud M_{\rm a} / (\ud t .

### 2016-02-21 MS.tex
Change in references

--- 2016-01-25 MS.tex
@@
   & & \tabitem{Absolute} &  $\ud M_{\rm t} / \ud t$ & $\downarrow$\sepp$\downarrow$ & $-$\sepp$-$ &  $-${\sepp}$\uparrow$ & $\uparrow${\sepp}$-$ & $\uparrow${\sepp}$\uparrow$ \\
-  & & \tabitem{Relative} & $\ud M_{\rm t} / \ud t / M_{\rm t}$ & $\uparrow${\sepp}$\downarrow$ & $\downarrow${\sepp}$\downarrow$ &  $-${\sepp}$\uparrow$ & $\downarrow${\sepp}$-$ & $\uparrow${\sepp}$\uparrow$ \\
+  & & \tabitem{Relative} & $\ud M_{\rm t} / \ud t .
+M_{\rm t}$ & $\uparrow${\sepp}$\downarrow$ & $\downarrow${\sepp}$\downarrow$ &  $-${\sepp}$\uparrow$ & $\downarrow${\sepp}$-$ & $\uparrow${\sepp}$\uparrow$ \\
   & \multicolumn{2}{ l } {in height} \\

### 2016-02-21 analysis.R

@@ -19,6 +19,9 @@ library("downloader")
 download_baad("downloads/baad.rds")
 paper_bib <- read.bib("references/paper.bib")
 meta_bib <- read.bib("references/metaanalyses.bib")
+combined_bib <- merge_bib_files(meta_bib, paper_bib)
+write.bib(combined_bib, file = "output/refs-main.bib")
+write.bib(combined_bib, file = "output/refs-suppmat.bib")
 read_bib <- read.bib("references/read.bib")
 AllData <- clean_raw_data("data/CompileData.csv")
 CleanData <- standardise_data(AllData)
@@ -81,9 +84,6 @@ dev.off()
 pdf("output/FigA9.pdf")
 figure_A9(GCi)
 dev.off()
-`combined_bib{1}` <- merge_bib_files(meta_bib, paper_bib)
-combined_bib <- merge_bib_files(`combined_bib{1}`, read_bib)
-write.bib(combined_bib, file = "output/refs.bib")
 `RCi{1}` <- EffectSizeSum(CompleteData_inter)
 RCi <- list_by_trait(`RCi{1}`)
 `RIi{1}` <- EffectSizeSum(IdealData_rgr)
@@ -91,5 +91,5 @@ RIi <- list_by_trait(`RIi{1}`)
 pdf("output/FigA5.pdf", height = 6L, width = 5L)
 figure_A5(RIi, RCi)
 dev.off()
-latex_build("ms-suppinfo.tex", bibliography = "output/refs.bib", clean = TRUE)
-latex_build("MS.tex", bibliography = "output/refs.bib", clean = TRUE)
+latex_build("ms-suppinfo.tex", bibliography = "output/refs-suppmat.bib", clean = FALSE)
+latex_build("MS.tex", bibliography = "output/refs-main.bib", clean = TRUE)

### 2016-02-21 MS.tex

--- 2016-02-19 MS.tex
@@
 Charles Warren and Jordi Mart{\'{i}}nez-Vilalta kindly provided additional information about their published results.
-This work was funded by the Australian Research Council through a fellowship to M.W, a discovery grant to D.S.F and a Macquarie University Research Excellence Scholarship and L’Oreal UNESCO FWIS Fellowship to E.F.G.
+This work was funded by the Australian Research Council through a fellowship to M.W, a discovery grant to D.S.F and a Macquarie University Research Excellence Scholarship and L'Oreal UNESCO FWIS Fellowship to E.F.G.
 
@@
 Horizontal line colours refer to the original stage attributed by the authors .The solid vertical lines indicate the thresholds used to classify plants in one of three stages in our meta-analyses.
-Studies marked with a “*” were those where stage was changed or assigned, compared to the original publication.}
+Studies marked with a ``*'' were those where stage was changed or assigned, compared to the original publication.}
 \label{fig:fig2}

### 2016-02-21 ms-suppinfo.Rnw

@@
 AIC: Akaike information criterion corresponds to the quality of each model, and allow a comparison between models.
-Smallest is the AIC better is the model.
+The smaller the AIC, the better the model is.
 Results shown here are from ``ideal'' subset of data (for details see ``Material and Methods'').
@@
 \begin{equation}\label{eq:eq1_seedlings}
-{\frac{\ud M_{\rm t}}{\ud t}}  \approx  A_{\rm l} \, y \, (p - r_{\rm l}).
+{\frac{\ud M_{\rm a} }{\ud t}}  \approx  A_{\rm l} \, y \, (p - r_{\rm l}).
 \end{equation}
 
-The \textbf{relative growth rate in mass} $({\rm RGR}_{{\rm mass}})$ in seedlings can be obtained by dividing both sides of this simplified eq \ref{eq:eq1_seedlings} by the total mass of living tissues $M_{\rm t}$.
+The \textbf{relative growth rate in mass} $({\rm RGR}_{{\rm mass}})$ in seedlings can be obtained by dividing both sides of this simplified eq \ref{eq:eq1_seedlings} by the total mass of living tissues $M_{\rm a} $.
 The outcome is equivalent to the classical partitioning of RGR \citep{Lambers:1992bj, Cornelissen:1998ta}:
@@
 \end{equation}
-where net assimilation rate NAR = $y \, (p - r)$, SLA = $A_{\rm l}/ M_{\rm l}$ and leaf mass fraction LMF = $M_{\rm l}/ M_{\rm t}$.
+where net assimilation rate NAR = $y \, (p - r)$, SLA = $A_{\rm l}/ M_{\rm l}$ and leaf mass fraction LMF = $M_{\rm l}/ M_{\rm a} $.
 

### 2016-02-21 MS.tex
Change prediction for RGR vs AGR in results section

@@
 \ref{eq:daldmt}.
-Consequently, the effect of leaf turnover becomes relatively stronger at larger sizes, and as such, the effect of SLA on height, diameter and, mass growth shifts from positive to negative as plants increase in size.
+Consequently, the effect of leaf turnover becomes relatively stronger at larger sizes, and as such, the effect of SLA on height, diameter and, mass growth shifts from positive to negative as plants increase in size (Table \ref{tab:trade-offs}).
 Note in the case of mass growth, the effect of cheaper leaf construction is realised not in the $\frac{\ud A_{\rm l}}{\ud M_{\rm a} }$ term , but as a greater total leaf area at a given mass, i.e.
@@
 The only effect of increased seed size in the above model is to produce a larger overall seedling.
-Under similar light conditions, larger seedlings are therefore predicted to have faster absolute growth rates.
-However, because the ratio of leaf area to total biomass decreases with plant size, larger seedlings are predicted to have lower mass-based growth rates during the earliest phases of growth \citep{Turnbull:2012ew}.
+Under similar light conditions, larger seedlings are therefore predicted to have faster absolute growth rates .
+However, because the ratio of leaf area to total biomass decreases with plant size, larger seedlings are predicted to have lower mass-based relative growth rates during the earliest phases of growth \citep{Turnbull:2012ew}(Table \ref{tab:trade-offs}).
 Yet, as plants grow, we expect the effect of this initial size difference to be minimal, and the correlation between seed size and growth rate should therefore disappear.
@@
 
-We had hypotheses for seed mass, SLA and wood density, about a change in the correlation between trait and growth rate if absolute growth rate was used instead of relative growth rate, or if mass was used instead of diameter and height.
-For seed mass, effect size differed significantly between relative growth rate and absolute growth rate at seedling stage; as expected the correlation with relative growth rate was positive and shifted to non significant with absolute growth rate (Fig \ref{fig:fig4}d; CI not overlapping).
-For SLA, the correlation was expected to shift from positive to non significant if growth in mass was measured on absolute instead of relative terms; however, none of the data were measured with absolute rates in the seedling stage (Fig.
-\ref{fig:figA8}).
-For wood density, some differences occurred but they were not easily attributed to any single cause.
+We had hypotheses for seed mass about a change in the correlation between trait and growth rate if absolute growth rate was used instead of relative growth rate.
+Effect size for seed mass differed significantly between relative growth rate and absolute growth rate at seedling stage; as expected the correlation with relative growth rate was positive and shifted to non significant with absolute growth rate (Fig \ref{fig:fig4}d; CI not overlapping).
+For wood density, some differences occurred according to the growth measurement used but they were not easily attributed to any single cause.
 In particular, the correlation at juvenile stage shifted from negative with relative growth rate to non significant with absolute growth rate (i.e CI included zero, Fig.

### 2016-02-23 MS.tex
Discussion: clarify mechanism, as requested

@@
 
+A single feature of plant growth underpins to the patterns associated with SLA, wood density, and seed size: the decrease in the ratio of leaf area to support tissue biomass with increasing plant size.
+Size-dependent requirements for mechanical and hydraulic support result in a substantial decline in the ratio of leaf biomass to total biomass with increasing plant size.
+Hence, the ratio of biomass production to total biomass and therefore relative growth rate must decline with increasing plant size \citep{Givnish:1995ta, Enquist:2007ek}, resulting in lower relative growth rates for large seedlings of large-seeded species than for small seedlings of small-seeded species \citep[reviewed by][]{Turnbull:2012ew}.
+For seedlings our study showed, as expected, a negative relationship between seed mass and relative growth rate (in mass, height, or volume) for small plants, that dissipated as plants grew larger.
+
+Increasing support costs also devalue the benefits of cheap leaf construction (low SLA), because as plant's grow larger, an increasing amount of total biomass production is devoted to building and maintaining support tissues \citep{Givnish:1995ta,King-2011}.
+The net result is that the growth advantage experienced by high SLA species at small sizes, dissapates among larger plants.
 While it has previously been noted that the correlation of SLA with growth rate disappears among saplings and larger trees (\citealt{Wright:2010tp} for Barro Colorado Island forest, Panama), our meta-analysis generalises that result.
@@
 In the model described here, the mechanism is slightly different: high-SLA species incur faster leaf turnover, the cost of which outweighs the benefits of cheap leaf construction at larger sizes.
-
-For seedlings our study showed, as expected, a negative relationship between seed mass and relative growth rate (in mass or height or volume) for small plants, that dissipated as plants grew larger.
-This negative relationship arises because seedlings from larger seeds begin life larger themselves, as has been extensively discussed in the literature \citep[reviewed by][]{Turnbull:2012ew}.
 

### 2016-02-24 MS.tex
LIzzy comments 1

--- 2016-02-21 MS.tex
@@
 \linenumbers
-\section{Summary 307/350}\label{abstract}
+\section{Summary 309/350}\label{abstract}
 \begin{enumerate}
@@
 We also recorded data for 14 other traits commonly used in the trait literature.
-To capture the effects of plant size, we tested for a shift in the direction of correlation between growth rates and traits across three ontogenetic stages: seedling, sapling and adult.
+To capture the effects of plant size, we tested for a shift in the direction of correlation between growth rates and each trait across three ontogenetic stages: seedling, sapling and adult.
 
@@
 
-\item Synthesis: We show how trait-growth correlations change in a predictable way with plant size.
-Our understanding of plant strategies should shift away from attributing species as having slow or fast growth throughout their life, in favour of attributing growth trajectories.
+\item Synthesis: We show for some traits, how trait-growth correlations change in a predictable way with plant size.
+Our understanding of plant strategies should shift away from categorizing species as having slow or fast growth throughout their life, in favour of attributing growth trajectories.
 \end{enumerate}
@@
 The phrase ``plant ecological strategy'' refers to how species face common challenges of acquiring sufficient water, nutrients, and light for growth; and then ultimately replacing themselves with offspring.
-The idea that strategy differences among species might involve fast versus slow growth goes back at least to \citet{Grime:1975gr}, who observed a wide spread of relative growth rate  among seedlings growing under favourable conditions.
+The idea that strategy differences among species might involve fast versus slow growth goes back at least to \citet{Grime:1975gr}, who observed a wide spread of relative growth rates among seedlings growing under favourable conditions.
 Seedling potential relative growth rate has continued to be used as a major strategy indicator within Grime's CSR (Competitor -- Stress tolerator -- Ruderal) classification (e.g.
@@
 
-In this paper, we consider five prominent traits (specific leaf area = SLA, wood (or stem) tissue density, maximum leaf photosynthetic capacity per unit area = Aarea, maximum (or asymptotic height), and seed mass) and we investigate:
+In this paper, we consider five prominent traits (specific leaf area = SLA, wood or stem tissue density, maximum leaf photosynthetic capacity per unit area = Aarea, maximum or asymptotic height, and seed mass) and we investigate:
 \begin{enumerate}
@@
 
-Assuming plants otherwise maintain a similar cross section of conducting tissue, cheaper stem construction (low wood density or stem density) will increase the marginal rate of leaf deployment per total mass increment ($\frac{\ud A_{\rm l}}{\ud M_{\rm a} }$), and consequently growth rate in height and diameter (eqs.
+Assuming plants maintain a similar cross section of conducting tissue, cheaper stem construction (low wood density or stem density) will increase the marginal rate of leaf deployment per total mass increment ($\frac{\ud A_{\rm l}}{\ud M_{\rm a} }$), and consequently growth rate in height and diameter (eqs.
 \ref{eq:eq2}-\ref{eq:eq4}; Table \ref{tab:trade-offs}).
@@
 Because the relative expenditure on stem compared to leaf increases as plants grow larger, the relationship between wood density and growth may also strengthen in larger plants.
-A similar shift is expected for growth in mass growth, in either absolute or relative terms.
+A similar shift is expected for growth in mass, in either absolute or relative terms.
 Note in the case of mass growth, the effect of cheaper stem construction is realised not in the $\frac{\ud A_{\rm l}}{\ud M_{\rm a} }$ term , but via greater total leaf area at a given mass, i.e.
@@
 The only effect of increased seed size in the above model is to produce a larger overall seedling.
-Under similar light conditions, larger seedlings are therefore predicted to have faster absolute growth rates .
+Under similar light conditions, larger seedlings are therefore predicted to have faster absolute growth rates.
 However, because the ratio of leaf area to total biomass decreases with plant size, larger seedlings are predicted to have lower mass-based relative growth rates during the earliest phases of growth \citep{Turnbull:2012ew}(Table \ref{tab:trade-offs}).
@@
 Because these categories were established according to the expertise of the authors, we were concerned about the risk of assigning plants of similar size to different categories when compiling data across multiple studies and vegetation types.
-This risk turned out to be small: overall, we found that the original thresholds in size/age used by the authors to distinguish different stages were relatively compatible (Fig.
+This risk turned out to be small: overall, we found that the original thresholds in size/age used by the authors to distinguish different stages were relatively compatible with thresholds we defined (Fig.
 \ref{fig:fig2}).
@@
 Charles Warren and Jordi Mart{\'{i}}nez-Vilalta kindly provided additional information about their published results.
+Elizabeth Wenk and Freya Thomas for their friendly review of our manuscript.
 This work was funded by the Australian Research Council through a fellowship to M.W, a discovery grant to D.S.F and a Macquarie University Research Excellence Scholarship and L'Oreal UNESCO FWIS Fellowship to E.F.G.

### 2016-02-24 R/figures.R

@@ -1,5 +1,6 @@
 ## Figure main text
 figure_1 <- function(RawData) {
+
   p2 <- my_plot_1("", ggplot(RawData, aes(x = reorder(factor(trait), factor(trait),
     function(x) length(x) * 1), fill = stage, order = stage)))
   p2
@@ -334,7 +335,7 @@ figure_3.4 <- function(GCi, GCrgr , GCagr) {
                        vjust.value = 2, limit.x.text = -0.6, limit.y.text.l1 , limit.y.text.l2 )
   
   p2 <- coeff.plot.gr3(data = CoefModel.WD, data1=CoefModel.WD2, data.RGR = CoefModel.WD.s, data.AGR = CoefModel.WD.opt, 
-                       LRT=LRT.wd, PVAL=PVAL.wd, round.value = 2, significativite = "ns", title = "b) WD",
+                       LRT=LRT.wd, PVAL=PVAL.wd, round.value = 2, significativite = "ns", title = "b) Wood density",
                        limit.x.min = -1, limit.x.max = 1, limit.x.n = 0.84,
                        vjust.value = 2, limit.x.text = -0.73, limit.y.text.l1 , limit.y.text.l2)
   
@@ -415,7 +416,7 @@ figure_3 <- function(GIrgr) {
                        limit.x.min = -1, limit.x.max = 1.5, limit.x.n = 1.3,
                        vjust.value = 2, limit.x.text = -0.6, limit.y.text.l1 , limit.y.text.l2 )
   
-  p2 <- coeff.plot.rgr(data = CoefModel.WD,title = "b) WD", LRT=LRT.wd, PVAL=PVAL.wd, round.value = 3, significativite = "*",
+  p2 <- coeff.plot.rgr(data = CoefModel.WD,title = "b) Wood density", LRT=LRT.wd, PVAL=PVAL.wd, round.value = 3, significativite = "*",
                        limit.x.min = -1, limit.x.max = 1, limit.x.n = 0.84,
                        vjust.value = 2, limit.x.text = -0.73, limit.y.text.l1 , limit.y.text.l2)
   
@@ -655,7 +656,7 @@ figure_A4 <- function(GIi, GIrgr, GIagr) {
   # annotation_custom(grobA)
 
   p1 <- my_plot_overall(SLA, title = "a) SLA") 
[…]

### 2016-02-24 MS.tex
Lizzy comments part 2

@@
 However, these differences are clear criteria for assessing the quality of the data for addressing our hypotheses.
-Consequently, we adopted a two-stage approach where at first we were conservative by focusing exclusively on relative growth rate, across \underline{\textgreater} 10 species, under unstressed conditions, and where the source of the trait and growth is the same (expect for maximum height and seed mass, where a particular stage is by definition required to measure the trait).
+Consequently, we adopted a two-stage approach where at first we were conservative by focusing exclusively on relative growth rate, across strudies that included \underline{\textgreater} 10 species, under unstressed conditions, and where the source of the trait and growth is the same (expect for maximum height and seed mass, where a particular stage is by definition required to measure the trait).
 This dataset is called the ``ideal'' dataset.
@@
 \ref{fig:fig3}a).
-The correlation between relative growth rate and SLA shifted from strongly positive at seedling stage ($\bar{r}=0.6 \pm 0.08$, Mean $\pm$ SD) to not significantly different from zero at adult stage ($\bar{r}= -0.01 \pm 0.07$, CI 95\% overlapping zero).
+The correlation between relative growth rate and SLA shifted from strongly positive at seedling stage ($\bar{r}=0.60 \pm 0.08$, Mean $\pm$ SD) to not significantly different from zero at adult stage ($\bar{r}= -0.01 \pm 0.07$, CI 95\% overlapping zero).
 The correlation coefficients recorded at sapling stage were intermediate between seedling and adult stages.
@@
 However, the additional replicates were unequally distributed across trait-stage combinations.
-Some trait-stage combinations already with a lot of data got even more support (e.g.
+Some trait-stage combinations that already had a lot of data got even more support (e.g.
 from 25 to 59 correlation coefficients reported for SLA at seedling stage), while others still had few replicates.
@@
 
-Results from the entire dataset reinforced our conclusions for both SLA and wood density, set apart alternative explanations for seed mass, and allowed us to compare correlations with growth along ontogenetic stages for Aarea.
-For SLA and wood density, the number of replicates doubled by using the entire dataset, and effect sizes and overall results were similar to those reported above using the ``ideal'' subset (Fig.
+Results from the entire dataset reinforced our conclusions for both SLA and wood density and allowed us to compare correlations with growth across ontogenetic stages for Aarea and seed mass.
+For SLA and wood density, although the number of replicates doubled by using the entire dataset, and effect sizes and overall results were similar to those reported above using the ``ideal'' subset (Fig.
 \ref{fig:fig4})).
@@
 
-We had hypotheses for seed mass about a change in the correlation between trait and growth rate if absolute growth rate was used instead of relative growth rate.
+For seed mass, we had hypothesized that the correlation between trait and growth rate would change if absolute growth rate was used instead of relative growth rate.
 Effect size for seed mass differed significantly between relative growth rate and absolute growth rate at seedling stage; as expected the correlation with relative growth rate was positive and shifted to non significant with absolute growth rate (Fig \ref{fig:fig4}d; CI not overlapping).
-For wood density, some differences occurred according to the growth measurement used but they were not easily attributed to any single cause.
+For wood density, some differences occurred according to the growth measurement used, but they were not easily attributed to any single cause.
 In particular, the correlation at juvenile stage shifted from negative with relative growth rate to non significant with absolute growth rate (i.e CI included zero, Fig.
@@
 
-Given our basic conclusion that reported correlations responded to plant size in a manner consistent with expectations from theory, we assessed the coverage of the available data, to determine if biased sampling could have erroneously generated the above results.
+Given our basic conclusion that reported correlations shifted with plant size in a manner consistent with expectations from theory, we assessed the coverage of the available data, to determine if biased sampling could have erroneously generated the above results.
 
@@
 Meta-analysis allowed us to generalize and thus to reach a consensus about the effect of traits on growth, even if our conclusions were at times biased toward a particular growth stage, due to uneven coverage of the empirical literature across trait-growth-stage combinations.
-Growth rates were already known to change with size through ontogeny \citep{Condit:1993hd, Clark:1999ed, Herault:2011dd}, in other words individual plants follow a growth trajectory.
+Growth rates were already known to change with size \citep{Condit:1993hd, Clark:1999ed, Herault:2011dd}, in other words individual plants follow a growth trajectory.
 Our results suggest species traits should be understood as influencing this trajectory and potentially re-ranking growth rates between individuals from different species as their size increases.
@@
 \citet{Poorter:2008iu} speculated that the maximum height-relative growth rate relationship among large trees might arise from including small tree species with maximum size not much larger than the 10cm dbh lower threshold used to define large trees.
-In our growth equations, maximum height affects growth via the fraction of energy diverted to reproduction.
+A possible mechanism  for Poorter et al's observation is captured by our growth equations: maximum height affects growth via the fraction of energy diverted to reproduction.
 At a given tree size, species closer to their maximum height are expected to be allocating relatively less to vegetative growth.
@@
 Many biotic and abiotic conditions such as light and water micro-environments can affect growth rates, and might modify correlations with traits in relation to plant size.
-For example, instead of a positive relationship that disappeared with plant size, \citet{Iida:2014ep} found SLA was negatively correlated with relative growth rate at small size and positively correlated with relative growth rate at larger sizes.
+For example, for SLA, instead of a positive relationship with growth rates that disappeared with plant size, \citet{Iida:2014ep} found SLA was negatively correlated with relative growth rate at small size and positively correlated with relative growth rate at larger sizes.
 Similarly, instead of a negative correlation between wood density and growth across all ontogenetic stages, some studies found a negative correlation at small size that disappeared when trees were larger \citep{Iida:2014ep,Iida:2014hq}.

### 2016-02-26 MS.tex
Change fig 3: RGR ideal vs RGR relaxed criteria Change fig4: RGR vs AGR under relaxed criteria Start change text

@@
 
-\subsection*{Main effects under ``ideal'' conditions}
+\subsection*{Main effects for relative growth rate under ``ideal'' conditions}
 
+We identified only 55 studies containing 137 correlations reporting data measured under ``ideal'' conditions: unstressed growth, growth measured as relative growth rate, traits and growth recorded in same stage, and correlation coefficient calculated across \underline{\textgreater} 10 species.
 Overall, results were consistent with predictions, although with limitations arising for some traits due to very unequal (and limited) numbers of observations between growth stages.
-We identified only 55 studies containing 137 correlations reporting data measured under ``ideal'' conditions: unstressed growth, growth measured as relative growth rate, traits and growth recorded in same stage, and correlation coefficient calculated across \underline{\textgreater} 10 species.
 
@@
 
-\subsection*{Main effects under relaxed criteria}
+\subsection*{Main effects for relative growth rate under relaxed criteria}
 
-We now report results from the entire dataset.
+We now report results for relative growth rate from the entire dataset.
 Our aim is to determine if additional data alters or reinforces the above conclusions, by increasing replication.
@@
 
+\subsection*{Comparisons of relative and absolute growth rates under relaxed criteria}
+
+For a majority of traits, effect sizes were generally consistent between relative growth rate and absolute growth rate when both measurements were available. Indeed for SLA
 For seed mass, we had hypothesized that the correlation between trait and growth rate would change if absolute growth rate was used instead of relative growth rate.
@@
 So it was not possible to disentangle the effect of growth measurement from the effect of trait origin.
-For other traits, effect sizes were generally consistent between relative growth rate and absolute growth rate when both measurements were available.
 

### 2016-02-26 R/figures.R

@@ -184,89 +184,87 @@ figure_2 <- function(CompleteData_inter) {
 # 
 #   grid.arrange(p1, p2, p3, p4, p5, ncol = 2, nrow = 3, widths = c(1.2, 1))
 # }
-# 
 
-# figure_3.2 <- function(GCrgr , GCagr) {
-#   CoefModel.SLA <- fun_model1(GCrgr[["SLA"]],GCagr[["SLA"]])
-#   CoefModel.SLA["trait"] <- "SLA"
-#   CoefModel.SLA.s <- subset(CoefModel.SLA, growth == "RGR")
-#   CoefModel.SLA.opt <- subset(CoefModel.SLA, growth == "AGR")
-# 
-#   
-#   CoefModel.WD <- fun_model1( GCrgr[["WD"]], GCagr[["WD"]])
-#   CoefModel.WD["trait"] <- "WD"
-#   CoefModel.WD.s <- subset(CoefModel.WD, growth == "RGR")
-#   CoefModel.WD.opt <- subset(CoefModel.WD, growth == "AGR")
-#   
-#   
-#   CoefModel.Hmax <- fun_model1(GCrgr[["Hmax"]], GCagr[["Hmax"]])
-#   CoefModel.Hmax["trait"] <- "Hmax"
-#   CoefModel.Hmax.s <- subset(CoefModel.Hmax, growth == "RGR")
-#   CoefModel.Hmax.opt <- subset(CoefModel.Hmax, growth == "AGR")
-#   
-#   
-#   CoefModel.Seedmass <- fun_model1(GCrgr[["Seedmass"]], GCagr[["Seedmass"]])
-#   CoefModel.Seedmass["trait"] <- "Seedmass"
-#   CoefModel.Seedmass.s <- subset(CoefModel.Seedmass, growth == "RGR")
-#   CoefModel.Seedmass.opt <- subset(CoefModel.Seedmass, growth == "AGR")
-#   
-#   
-#   CoefModel.Aarea <- fun_model1(GCrgr[["Aarea"]], GCagr[["Aarea"]])
-#   CoefModel.Aarea["trait"] <- "Aarea"
-#   CoefModel.Aarea.s <- subset(CoefModel.Aarea, growth == "RGR")
-#   CoefModel.Aarea.opt <- subset(CoefModel.Aarea, growth == "AGR")
-#   
-#   
[…]

### 2016-02-26 R/plots.R

@@ -130,6 +130,7 @@ coeff.plot.gr3 <- function(data, data1, data.RGR, data.AGR, title = "",LRT, PVAL
 #   data1["x.coord"] <- limit.x.n
   data["x.coord"] <- limit.x.n
   
+  
     plot1 <- function(title, ggobj, xlab = "Effect size", ylab = "Stage") {
     
     p <- ggobj + labs(title = title) + xlab(xlab) + ylab(ylab) +
@@ -155,10 +156,11 @@ coeff.plot.gr3 <- function(data, data1, data.RGR, data.AGR, title = "",LRT, PVAL
 
 
 coeff.plot.gr2 <- function(data, data.RGR, data.AGR, title = "", limit.x.min, limit.x.max, limit.x.text,
-                          limit.x.n, limit.y.text.l1, limit.y.text.l2, vjust.value, color1="#9E5F3A", color2="black") {
+                          limit.x.n, limit.y.text.l1, limit.y.text.l2, vjust.value, color1="#9E5F3A", color2="black", labels.table =c("RGR ideal", "RGR complete")) {
   
   data.RGR["x.coord"] <- limit.x.n
   data.AGR["x.coord"] <- limit.x.n
+  data["x.coord"] <- limit.x.n
   
   plot1 <- function(title, ggobj, xlab = "Effect size", ylab = "Stage") {
     
@@ -176,9 +178,10 @@ coeff.plot.gr2 <- function(data, data.RGR, data.AGR, title = "", limit.x.min, li
   plot1(title, ggplot(data, aes(stage, Inte, ymin = Inte - 1.96 * SE, ymax = Inte +1.96 * SE, color = factor(growth)))) +
     geom_point(aes(x = stage, y = Inte),position = dodge) + geom_errorbar(aes(x = stage, y = Inte), size = 0.4,width = 0.2, position = dodge) +
     scale_y_continuous("Effect size",limits = c(limit.x.min, limit.x.max)) +
-    geom_text(aes(stage,x.coord, label = paste("n=", N), color = factor(growth), group = "AGR"),size = 2, data = data.AGR, parse = F, position = "identity", vjust = +vjust.value, hjust = 0) + 
-    geom_text(aes(stage, x.coord, label = paste("n=",N), color = factor(growth), group = "RGR"), size = 2, data = data.RGR, parse = F, position = "identity", vjust = -vjust.value, hjust = 0) +
[…]

### 2016-03-01 MS.tex
Change the results part to include a clear comparison of RGR vs AGR Re-read and modify slightly the abstract and the discussion to include the new results.

@@
 \usepackage[]{natbib}
+\usepackage{floatpag}
+\floatpagestyle{empty}
 
@@
 Specific leaf area was correlated with relative growth rate in seedlings but not in adult plants.
-Correlations of growth with wood density and assimilation rate were not affected by ontogenetic stage.
-Seed mass and maximum height were correlated with relative growth rate only in one ontogenetic stage category: seedlings and adults, respectively.
+Correlations of growth with wood density were not affected by ontogenetic stage.
+Seed mass, assimilation rate and maximum height were correlated with relative growth rate only in one ontogenetic stage category: seedlings, seedlings and adults, respectively.
 
@@
 
-\subsubsection*{Measurements under ``ideal'' conditions}\label{ideal-vs-entire-dataset}
+\subsubsection*{Analyses of relative and absolute growth rates under conservative and relaxed criteria}\label{conservative-vs-entire-dataset}
 
-The entire dataset included studies differing in the growth measurement used (relative or absolute), the number of species, the experimental conditions (stressed vs unstressed), and the concordance between stages used to measure trait and growth rate.
+The dataset included studies differing in the growth measurement used (relative or absolute), the number of species, the experimental conditions (stressed vs unstressed), and the concordance between stages used to measure trait and growth rate.
 However, these differences are clear criteria for assessing the quality of the data for addressing our hypotheses.
-Consequently, we adopted a two-stage approach where at first we were conservative by focusing exclusively on relative growth rate, across strudies that included \underline{\textgreater} 10 species, under unstressed conditions, and where the source of the trait and growth is the same (expect for maximum height and seed mass, where a particular stage is by definition required to measure the trait).
-This dataset is called the ``ideal'' dataset.
-We then compared the results from the ``ideal'' dataset with those from the entire dataset - with both relative growth rate and absolute growth rates, and all other criteria relaxed.
+Consequently, we adopted a three-stage approach where at first we were conservative by focusing exclusively on relative growth rate, across studies that included \underline{\textgreater} 10 species, under unstressed conditions, and where the source of the trait and growth is the same (expect for maximum height and seed mass, where a particular stage is by definition required to measure the trait).
+We then compared these results with those focusing on relative growth rate from the entire dataset - with all criteria relaxed excepted the growth measurement used.
+Finally, we compared results from both relative and absolute growth rates from the entire dataset.
 
@@
 
-\subsection*{Main effects for relative growth rate under ``ideal'' conditions}
+\subsection*{Main effect for relative growth rates under conservative criteria}
 
-We identified only 55 studies containing 137 correlations reporting data measured under ``ideal'' conditions: unstressed growth, growth measured as relative growth rate, traits and growth recorded in same stage, and correlation coefficient calculated across \underline{\textgreater} 10 species.
+We identified only 55 studies containing 137 correlations reporting data measured under conservative criteria: unstressed growth, growth measured as relative growth rate, traits and growth recorded in same stage, and correlation coefficient calculated across \underline{\textgreater} 10 species.
 Overall, results were consistent with predictions, although with limitations arising for some traits due to very unequal (and limited) numbers of observations between growth stages.
@@
 Our aim is to determine if additional data alters or reinforces the above conclusions, by increasing replication.
-This entire dataset included correlations measured with both absolute growth rate and relative growth rate (Fig.
-\ref{fig:fig4}), across at least two species (but measured using several individuals), and did not control for the source of trait or growth (i.e.
+This entire dataset included correlations measured with relative growth rate exclusively (Fig.
+\ref{fig:fig3}), across at least two species (but measured using several individuals), and did not control for the source of trait or growth (i.e.
 traits could be measured on a different ontogenetic stage to growth data) or environmental conditions.
-The relaxed criteria considerably increased the number of replicates, from $n = 137$ to $n = 267$ correlations across 93 articles.
+The relaxed criteria increased the number of replicates, from $n = 137$ to $n = 167$ correlations across 93 articles.
 However, the additional replicates were unequally distributed across trait-stage combinations.
@@
 
-Results from the entire dataset reinforced our conclusions for both SLA and wood density and allowed us to compare correlations with growth across ontogenetic stages for Aarea and seed mass.
-For SLA and wood density, although the number of replicates doubled by using the entire dataset, and effect sizes and overall results were similar to those reported above using the ``ideal'' subset (Fig.
-\ref{fig:fig4})).
-As expected for seed mass, the correlation with growth at adult stage was significantly different from that observed at seedling stage (see CIs in Fig.
-\ref{fig:fig4}c, and model fit improved when stage was incorporated).
-For Aarea, the additional replicates in the entire dataset allowed us to compare the effect size across ontogenetic stage.
-The results were consistent with the prediction for a positive correlation with relative growth rate across adult and seedling stages (Fig \ref{fig:fig4}e; CI not overlapping zero).
-Comparison of Aarea effect between the ``ideal'' subset (Fig.
-\ref{fig:fig3}d) and entire dataset (Fig.
-\ref{fig:fig4}d), indicated little effect of stress (here mainly low light) on the correlation with relative growth rate at seedling stage as the correlation was still positive when 8 correlations measured under low light conditions were added.
-For maximum height, there were still too few replicates to conclude undoubtedly that the correlation is absent for smaller sizes.
+Results from the entire dataset reinforced our conclusions for both SLA and wood density, and did not altered them for the others traits.
+For SLA and wood density, although the number of replicates doubled by using the entire dataset, effect sizes and overall results were similar to those reported above using the conservative crieteria (Fig.
+\ref{fig:fig3})).
+For seed mass and Aarea, the additional replicates in the entire dataset allowed us to be more confident of the effect size for seedling stage (Fig \ref{fig:fig3}d, e).
+Comparison of Aarea effect between the conservative and relaxed criteria (Fig.
+\ref{fig:fig3}d), indicated little effect of stress (here mainly low light) on the correlation with relative growth rate at seedling stage as the correlation was still positive when 8 correlations measured under low light conditions were added.
+For maximum height, there were no additional replicates in the entire dataset; we still cannot conclude undoubtedly that the correlation is absent for smaller sizes.
 
-\subsection*{Comparisons of relative and absolute growth rates under relaxed criteria}
+\subsection*{Comparisons between relative and absolute growth rates under relaxed criteria}
 
-For a majority of traits, effect sizes were generally consistent between relative growth rate and absolute growth rate when both measurements were available. Indeed for SLA
-For seed mass, we had hypothesized that the correlation between trait and growth rate would change if absolute growth rate was used instead of relative growth rate.
-Effect size for seed mass differed significantly between relative growth rate and absolute growth rate at seedling stage; as expected the correlation with relative growth rate was positive and shifted to non significant with absolute growth rate (Fig \ref{fig:fig4}d; CI not overlapping).
+We had hypothesized only for seed mass that the correlation between trait and growth rate would change if absolute growth rate was used instead of relative growth rate.
+Overall, the models fit did not improve when growth measurement was incorporated (see log likelihood ratio tests in Fig.
+\ref{fig:fig4}).
+For a majority of traits, effect sizes were generally consistent between relative growth rate and absolute growth rate when both measurements were available (e.g.
+effect size for relative and absolute growth rate of Hmax and Wood density at adult stage in Fig.
+\ref{fig:fig4} b and c).
+However, for seed mass and wood density at seedling stage, the direction of effect sizes changed when correlations were measured with either abolute or relative growth rate.
+For seed mass, effect size at seedling stage with relative growth rate was positive and shifted to non significant with absolute growth rate (Fig \ref{fig:fig4}d; CI overlapping zero).
+While these results were consistent with expectations, our ability to conclude was limited due to low sample size for correlation with absolute growth rate (i.e CIs overlapping, Fig.
+\ref{fig:fig4}d).
 For wood density, some differences occurred according to the growth measurement used, but they were not easily attributed to any single cause.
@@
 
-The meta-analysis reported here demonstrates that for several key traits, the influence of the trait on growth rate changes as plants grow from small to large.
+The meta-analysis reported here demonstrates that for several key traits, the influence of the trait on growth rate change as plants grow from small to large.
 While the possibility has been raised recently that trait-growth correlations may change systematically with size \citep{Falster:2011ii, Ruger:2012jv, Iida:2014ep, Iida:2014hq}, this is the first time that specific mechanistic hypotheses have been corroborated against a wide array of existing studies.
@@
 
-For five prominent traits, the patterns observed were consistent with specific predictions from a mechanistic growth model.
+For five prominent traits, the patterns observed were consistent with specific predictions from a mechanistic growth model, although there were some limitations arising from unequal numbers of observation across ontogenetic stages.
 This suggests the mechanisms through which traits affect growth are correctly represented in the model.
@@
 For wood density the meta-analysis showed negative correlation with relative growth rate across all ontogenetic stages, as previously reported from individual studies \citep{Wright:2010tp,Ruger:2012jv}.
-It should be noted however that there are few data available to test this proposition at seedling stage (n=1-5).
+It should be noted however that there are few data available to test this proposition at seedling stage (n=1-4).
 In our model, cheaper stem construction is responsible for the predicted negative correlation.
@@
 In the growth model, a consistent correlation irrespective of size arises from a direct effect of Aarea on plant growth rate.
-Meta-analyses showed a positive correlation for adult and seedling but not for saplings (n=3).
+Meta-analyses showed a positive correlation for seedling but not for saplings and adult (n=1).
 In the seedling stage, where most data were available, we noted no signal of an effect of low light on the positive correlation between Aarea and growth rate.
 
-Meta-analysis showed a positive correlation between maximum height and relative growth rate for adult stage, but not for saplings and seedlings.
+Meta-analysis showed a positive correlation between maximum height and relative growth rate for adult stage.
 The trend for tall stature species to grow faster at a given tree size than small stature species has been noted across several tree size classes and forest types (e.g.
@@
 However this applies only at sizes where some of the species have begun to reproduce, and should not affect sapling and seedling growth rates.
-While the results of the meta-analysis were consistent with the expected pattern for maximum height, we noted that a limited number of replicates were available for both saplings (n=4) and seedling stages (n=1).
-Consequently, subsequent research is welcomed to validate this result.
+While the results of the meta-analysis not countered with the expected pattern for maximum height, we noted that a limited number of replicates were available for both saplings (n=4) and seedling stages (n=1).
+Consequently, subsequent research is welcomed to demonstrate this result on small plant sizes.
 
@@
 LMR, LAR).
-However, the existing published evidence is consistent with qualitative predictions of a simple model that assesses the effects of plant size on growth.
+However, the existing published evidence is consistent with several qualitative predictions of a simple model that assesses the effects of plant size on growth.
 Thus, the linkage of growth to the mechanisms outlined here can shed light on tree growth trajectories and the size-dependent effects of functional traits on the changing species growth rate rankings as individuals grow larger.
@@
 \includegraphics[width=15cm,height=20cm,keepaspectratio]{output/Fig2.pdf}
-\caption{ The range of plant sizes and stages recorded in original publications (horizontal coloured lines), compared to standardised thresholds used in the analysis (vertical black lines).
+\caption{The range of plant sizes and stages recorded in original publications (horizontal coloured lines), compared to standardised thresholds used in the analysis (vertical black lines).
 Horizontal line segments indicate the size range (max., min.) of the plants used to measure growth.
@@
 \includegraphics[width=15cm,height=20cm,keepaspectratio]{output/Fig3.pdf}
-\caption{The relationship between relative growth rates and traits changes with ontogenetic stage and trait.
-Plots show the effect size (+ 95\% confidence intervals; CI) for the average correlation across $>$10 species, by ontogenetic stage.
+\caption{The relationship between relative growth rates (RGR) and traits changes with ontogenetic stage and trait.
+Plots show the effect size (+ 95\% confidence intervals; CI) for the average correlation by ontogenetic stage.
 Effect size is a standardized measure of the deviation of correlation coefficient from zero (Fisher's z-transformed).
@@
 $n$ indicates number of correlations contributing to each effect.
-Likelihood Ratio Tests (LRT) compared maximum-likelihood fits between a pooled model and one separated by stage.
-A significant p-value means adding a stage effect to the model significantly improved model fit.
-Results shown are from the ideal dataset (see methods for details).}
+Results shown are for the "conservative dataset" (i.e.
+correlations that included \underline{\textgreater} 10 species, under unstressed conditions, and where the source of the trait and growth is the same) and for the entire dataset (i.e.
+with all criteria relaxed, see methods for details).
+Likelihood Ratio Tests (LRT) compared maximum-likelihood fits between a pooled model and one separated by stage for the conservative dataset.
+A significant p-value means adding a stage effect to the model significantly improved model fit.}
 \label{fig:fig3}
@@
 i) Results shown are from the entire dataset (see methods for details).
-ii) Likelihood Ratio Tests were calculated on effect size combining relative growth rate and absolute growth rate exclusively.}
+ii) Likelihood Ratio Tests compared maximum-likelihood fits between a model separated by stage and one separared by stage and growth measurement (RGR vs AGR).}
 \label{fig:fig4}

### 2016-03-01 ms-suppinfo.tex
LIzzy comments 1
Change the results part to include a clear comparison of RGR vs AGR Re-read and modify slightly the abstract and the discussion to include the new results.

@@
 The smaller the AIC, the better the model is.
-Results shown here are from ``ideal'' subset of data (for details see ``Material and Methods'').
+Results shown here are from ``conservative'' subset of data (for details see ``Material and Methods'').
 ``n'' indicates number of correlation r reported.}
@@
 The mean coefficients are weighted by sample size and established from 103 articles.
-Results shown here are from the ``ideal'' subset of data (for details see ``Material and Methods''), ``n'' indicates the number of correlations.}
+Results shown here are from the ``conservative'' subset of data (for details see ``Material and Methods''), ``n'' indicates the number of correlations.}
 \label{fig:figA4}
@@
 Absolute growth rate (AGR) is on the left and relative growth rate (RGR) on the right of each plot.
-Results shown here are from the ``ideal'' subset of the data (for details see ``Material and Methods'').
+Results shown here are from the ``conservative'' subset of the data (for details see ``Material and Methods'').
 }
@@
 Results shown here are from the entire dataset.
-Results with the "ideal" subset of data (for details see ``Material and Methods''), shown no missing values for all traits.}
+Results with the "conservative" subset of data (for details see ``Material and Methods''), shown no missing values for all traits.}
 \label{fig:figA7}
@@
 LRT: likelihood Ratio Test compared the fit between null model and stage model, both models are fitted by Maximum Likelihood.
-Black point: ideal data , grey points: all the data (for details see ``Material and Methods'').
+Black point: conservative data , grey points: all the data (for details see ``Material and Methods'').
 ``n'' indicates the number of independent comparisons for each effect.}
@@
 \ref{fig:figA7}).
-The ``trim and fill'' method detected some missing values in the entire dataset (but no missing values in the "ideal" dataset).
+The ``trim and fill'' method detected some missing values in the entire dataset (but no missing values in the "conservative" dataset).
 In the entire dataset, the estimated number of missing value ranges from 0 to 11 depending on the trait considered (Fig.

### 2016-03-01 R/figures.R

@@ -190,7 +190,7 @@ figure_3.1 <- function(GIrgr , GCrgr) {
   CoefModel.SLA["trait"] <- "SLA"
   CoefModel.SLA.s <- subset(CoefModel.SLA, growth == "RGR")
   CoefModel.SLA.opt <- subset(CoefModel.SLA, growth == "AGR")
-  
+ 
   
   CoefModel.WD <- fun_model1( GIrgr[["WD"]], GCrgr[["WD"]])
   CoefModel.WD["trait"] <- "WD"
@@ -215,37 +215,53 @@ figure_3.1 <- function(GIrgr , GCrgr) {
   CoefModel.Aarea.s <- subset(CoefModel.Aarea, growth == "RGR")
   CoefModel.Aarea.opt <- subset(CoefModel.Aarea, growth == "AGR")
   
+  LRT.sla <- fun_OneLR(GIrgr[["SLA"]])
+  PVAL.sla <- fun_Onepvalue(GIrgr[["SLA"]])
   
-  p1 <- coeff.plot.gr2(data = CoefModel.SLA, data.RGR = CoefModel.SLA.s, data.AGR = CoefModel.SLA.opt, title = "a) SLA",
-    limit.x.min = -1, limit.x.max = 1.5, limit.x.n = 1.3,
-    vjust.value = 1, limit.x.text = -0.1, limit.y.text.l1 = 0.25, limit.y.text.l2 = 0.25)
+  LRT.wd <- fun_OneLR(GIrgr[["WD"]])
+  PVAL.wd <- fun_Onepvalue(GIrgr[["WD"]])
+ 
+  LRT.hmax <- fun_OneLR(GIrgr[["Hmax"]])
+  PVAL.hmax <- fun_Onepvalue(GIrgr[["Hmax"]])
+
+  LRT.sm <- fun_OneLR(GIrgr[["Seedmass"]])
+  PVAL.sm <- fun_Onepvalue(GIrgr[["Seedmass"]])
+    
+  LRT.aarea<- fun_OneLR(GIrgr[["Aarea"]])
+  PVAL.aarea <- fun_Onepvalue(GIrgr[["Aarea"]])
   
-  p2 <- coeff.plot.gr2(data = CoefModel.WD, data.RGR = CoefModel.WD.s, data.AGR = CoefModel.WD.opt,title = "b) Wood density",
-    limit.x.min = -1.5, limit.x.max = 1, limit.x.n = 0.85,
[…]

### 2016-03-01 R/model.R

@@ -100,6 +100,8 @@ fun_model <- function(x, y) {
 }
 
 fun_model1 <- function(x, y) {
+#   y <- data2
+#   x <- data1
   # models for x ('ideal' dataset) and y ('complete' datatset)
   null <- lmer(corr.z ~ 1 + (1 | id), data = x, weights = nb.sp, REML = TRUE,
                control = lmerControl(check.nobs.vs.nlev = "ignore", check.nobs.vs.rankZ = "ignore",
@@ -158,15 +160,15 @@ fun_model1 <- function(x, y) {
   for (i in 1:l1) {
     CoefModel[i, 3] <- FP[i, 1]
     CoefModel[i, 4] <- FixSE[i, 1]
-    CoefModel[i, 5] <- CoefModel[i, 4] * 1.96 + CoefModel[i, 3]
-    CoefModel[i, 6] <- CoefModel[i, 4] * 1.96 - CoefModel[i, 3]
+    CoefModel[i, 5] <- CoefModel[i, 3] + CoefModel[i, 4] * 1.96 
+    CoefModel[i, 6] <- CoefModel[i, 3] - CoefModel[i, 4] * 1.96
   }
   
   for (j in a:l) {
     CoefModel[j, 3] <- FP.s[j - l1, 1]
     CoefModel[j, 4] <- FixSE.s[j - l1, 1]
-    CoefModel[j, 5] <- CoefModel[j, 4] * 1.96 + CoefModel[j, 3]
-    CoefModel[j, 6] <- CoefModel[j, 4] * 1.96 - CoefModel[j, 3]
+    CoefModel[j, 5] <- CoefModel[j, 3] + CoefModel[j, 4] * 1.96 
+    CoefModel[j, 6] <- CoefModel[j, 3] - CoefModel[j, 4] * 1.96
   }
   
   CoefModel$stage[CoefModel$stage == "stageseedling"] <- "seedling"
@@ -501,6 +503,90 @@ fun_model_multiple3.1 <- function(x) {
   dat
 }
 
+
+fun_model_growth <- function(x) {
+  x[["stagegrowth"]] <- NA
+  x$stagegrowth <- do.call(paste, c(x[c("stage", "growth")], sep = "")) 
+
+  # models for x ('ideal' dataset) and y ('complete' datatset)
+  null <- lmer(corr.z ~ stage + (1 | id), data = x, weights = nb.sp, REML = FALSE,
[…]

### 2016-03-01 R/plots.R

@@ -85,7 +85,7 @@ coeff.plot <- function(data, data.complete, data.ideal, LRT, PVAL, title = "",
 #     x.coord, label = paste("n=", N), color = factor(stress), group = "ideal"),
 #     size = 2, data = data.ideal, parse = F, position = "identity", vjust = -vjust.value,
 #     hjust = 0) + 
-    scale_color_manual(name = "", values=c(color1, color2), breaks = c("ideal", "complete"), labels = c(ideal = "ideal", complete = "entire")) +
+    scale_color_manual(name = "", values=c(color1, color2), breaks = c("ideal", "complete"), labels = c(ideal = "conservative dataset", complete = "entire dataset")) +
        annotate("text", x = limit.y.text.l1, y = limit.x.text, label = paste("LRT:", round(LRT,
       2)), size = 2) + annotate("text", x = limit.y.text.l2, y = limit.x.text,
     label = paste("p.value =", round(PVAL, round.value), significativite),
@@ -155,8 +155,7 @@ coeff.plot.gr3 <- function(data, data1, data.RGR, data.AGR, title = "",LRT, PVAL
 }
 
 
-coeff.plot.gr2 <- function(data, data.RGR, data.AGR, title = "", limit.x.min, limit.x.max, limit.x.text,
-                          limit.x.n, limit.y.text.l1, limit.y.text.l2, vjust.value, color1="#9E5F3A", color2="black", labels.table =c("RGR ideal", "RGR complete")) {
+coeff.plot.gr2 <- function(data, data.RGR, data.AGR, title = "", LRT, PVAL,round.value,significativite = "", limit.x.min, limit.x.max, limit.x.text, limit.x.n, limit.y.text.l1, limit.y.text.l2, vjust.value, color1="#9E5F3A", color2="black", labels.table =c("RGR from conservative dataset", "RGR from entire dataset")) {
   
   data.RGR["x.coord"] <- limit.x.n
   data.AGR["x.coord"] <- limit.x.n
@@ -181,7 +180,9 @@ coeff.plot.gr2 <- function(data, data.RGR, data.AGR, title = "", limit.x.min, li
     geom_text(aes(stage, x.coord, label = paste("n =", N), color = factor(growth)),size = 2, data = data, parse = F, position = dodge, hjust = 0) +
[…]

### 2016-03-01 analysis.R

@@ -21,8 +21,9 @@ paper_bib <- read.bib("references/paper.bib")
 meta_bib <- read.bib("references/metaanalyses.bib")
 combined_bib <- merge_bib_files(meta_bib, paper_bib)
 write.bib(combined_bib, file = "output/refs-main.bib")
-write.bib(combined_bib, file = "output/refs-suppmat.bib")
 read_bib <- read.bib("references/read.bib")
+suppmat_bib <- merge_bib_files(combined_bib, read_bib)
+write.bib(suppmat_bib, file = "output/refs-suppmat.bib")
 AllData <- clean_raw_data("data/CompileData.csv")
 CleanData <- standardise_data(AllData)
 CompleteData <- build_complete_data(CleanData)
@@ -48,10 +49,10 @@ pdf("output/Fig2.pdf", height = 9L, width = 4L)
 figure_2(CompleteData_inter)
 dev.off()
 pdf("output/Fig3.pdf", height = 6L, width = 5L)
-figure_3(GIrgr)
+figure_3.1(GIrgr, GCrgr)
 dev.off()
 pdf("output/Fig4.pdf", height = 6L, width = 5L)
-figure_3.4(GCi, GCrgr, GCagr)
+figure_3.2(GCrgr, GCagr)
 dev.off()
 baad <- readRDS("downloads/baad.rds")
 pdf("output/FigA1.pdf", height = 3L, width = 9L)

### 2016-03-01 MS.tex
Add Lizzy comments on the new version of the results and the mat & met

@@
 The dataset included studies differing in the growth measurement used (relative or absolute), the number of species, the experimental conditions (stressed vs unstressed), and the concordance between stages used to measure trait and growth rate.
-However, these differences are clear criteria for assessing the quality of the data for addressing our hypotheses.
-Consequently, we adopted a three-stage approach where at first we were conservative by focusing exclusively on relative growth rate, across studies that included \underline{\textgreater} 10 species, under unstressed conditions, and where the source of the trait and growth is the same (expect for maximum height and seed mass, where a particular stage is by definition required to measure the trait).
-We then compared these results with those focusing on relative growth rate from the entire dataset - with all criteria relaxed excepted the growth measurement used.
+These differences provide good criteria for assessing the quality of the data for addressing our hypotheses.
+We adopted a three-stage approach where at first we were conservative by focusing exclusively on relative growth rate, across studies that included \underline{\textgreater} 10 species, under unstressed conditions, and where the trait and growth were measured at the same stage (expect for maximum height and seed mass, where a particular stage is by definition required to measure the trait).
+We then compared these results with those from the subset of the dataset using relative growth rate, but with all other criteria relaxed.
 Finally, we compared results from both relative and absolute growth rates from the entire dataset.
@@
 
-Results from the entire dataset reinforced our conclusions for both SLA and wood density, and did not altered them for the others traits.
+Results from the entire dataset reinforced our conclusions for both SLA and wood density, and did not alter them for the others traits.
 For SLA and wood density, although the number of replicates doubled by using the entire dataset, effect sizes and overall results were similar to those reported above using the conservative crieteria (Fig.
@@
 
-We had hypothesized only for seed mass that the correlation between trait and growth rate would change if absolute growth rate was used instead of relative growth rate.
+The only correlation that we hypothesized would change if absolute growth rate was used instead of relative growth rate, was for eed mass.
 Overall, the models fit did not improve when growth measurement was incorporated (see log likelihood ratio tests in Fig.
@@
 \ref{fig:fig4} b and c).
-However, for seed mass and wood density at seedling stage, the direction of effect sizes changed when correlations were measured with either abolute or relative growth rate.
+However, for seed mass and wood density at seedling stage, the direction of effect sizes changed when correlations were measured with abolute versus relative growth rate.
 For seed mass, effect size at seedling stage with relative growth rate was positive and shifted to non significant with absolute growth rate (Fig \ref{fig:fig4}d; CI overlapping zero).
@@
 Results shown are for the "conservative dataset" (i.e.
-correlations that included \underline{\textgreater} 10 species, under unstressed conditions, and where the source of the trait and growth is the same) and for the entire dataset (i.e.
+correlations that included \underline{\textgreater} 10 species, under unstressed conditions, and where the trait and growth were measured at the same stage) and for the entire dataset (i.e.
 with all criteria relaxed, see methods for details).

### 2016-03-06 MS.tex
typo
Add Ian's comments

@@
 We focused on tree and woody species since the mechanistic model used to assess our predictions is most applicable to these growth forms.
-Using a meta-analysis approach, we were able to assess our hypotheses across a much broader number of species and vegetation types than would have been possible in an experiential study.
+Using a meta-analysis approach, we were able to assess our hypotheses across a much broader number of species and vegetation types than would have been possible in an experimental study.
 We anticipated a sizeable literature on traits and growth to be available but we were uncertain about the representation of all trait-stage combinations.
@@
 
-Assuming plants maintain a similar cross section of conducting tissue, cheaper stem construction (low wood density or stem density) will increase the marginal rate of leaf deployment per total mass increment ($\frac{\ud A_{\rm l}}{\ud M_{\rm a} }$), and consequently growth rate in height and diameter (eqs.
+Assuming plants with a similar cross section of conducting tissue, cheaper stem construction (low wood density or stem density) will increase the marginal rate of leaf deployment per total mass increment ($\frac{\ud A_{\rm l}}{\ud M_{\rm a} }$), and consequently growth rate in height and diameter (eqs.
 \ref{eq:eq2}-\ref{eq:eq4}; Table \ref{tab:trade-offs}).
@@
 (\ref{eq:eq2}-\ref{eq:eq3}).
-For seedlings, where all individuals are investing solely in growth, we expect no influence of maximum height on growth (i.e.
+For seedlings, where individuals are investing solely in growth, we expect no influence of maximum height on growth (i.e.
 $\frac{\ud M_{\rm a} }{\ud B} =1$).
@@
 For maximum height, the expectation was for a correlation with growth to be present for large plants but absent for smaller sizes, the mechanism being increased relative allocation to reproduction as maximum height is approached.
-Here, maximum height was positively correlated with growth at adult stage ($\bar{r}= 0.38 \pm 0.05$), not correlated at sapling stage (Fig \ref{fig:fig3}c, CIs overlapping zero) and no data were recorded for seedling stage.
+Here, maximum height was positively correlated with growth at adult stage ($\bar{r}= 0.38 \pm 0.05$), not significantly correlated at sapling stage (Fig \ref{fig:fig3}c, CIs overlapping zero) and no data were recorded for seedling stage.
 While these results were consistent with our expectation that maximum height would be correlated with growth at adult stage, they did not differ significantly across ontogenetic stages (model fit not improved when stage was incorporated, see log likelihood ratio tests in Fig.
@@
 For SLA and wood density, although the number of replicates doubled by using the entire dataset, effect sizes and overall results were similar to those reported above using the conservative crieteria (Fig.
-\ref{fig:fig3})).
+\ref{fig:fig3}).
 For seed mass and Aarea, the additional replicates in the entire dataset allowed us to be more confident of the effect size for seedling stage (Fig \ref{fig:fig3}d, e).
@@
 
-The only correlation that we hypothesized would change if absolute growth rate was used instead of relative growth rate, was for eed mass.
+The only correlation that we hypothesized would change if absolute growth rate was used instead of relative growth rate, was for seed mass.
 Overall, the models fit did not improve when growth measurement was incorporated (see log likelihood ratio tests in Fig.

### 2016-03-06 MS.tex
Add Ian suggestion (2/2)

@@
 The only effect of increased seed size in the above model is to produce a larger overall seedling.
-Under similar light conditions, larger seedlings are therefore predicted to have faster absolute growth rates.
+Under similar light conditions, larger seedlings are predicted to have faster absolute growth rates.
 However, because the ratio of leaf area to total biomass decreases with plant size, larger seedlings are predicted to have lower mass-based relative growth rates during the earliest phases of growth \citep{Turnbull:2012ew}(Table \ref{tab:trade-offs}).
@@
 Here wood density and SA/LA are also considered as indicators of stem construction cost \citep{Falster:2011ii}, whereas SLA and leaf thickness capture crucial information about leaf construction cost \citep{Wright:2004jb}.
-Finally, the leaf area ratio and leaf mass ratio are indicators of resource distribution to leaf \citep{Lambers:1992bj}.
+Finally, the leaf area ratio and leaf mass ratio are indicators of resource allocation to leaf versus other tissue types \citep{Lambers:1992bj}.
 
-Ultimately, data was recorded from 103 different articles \citep{Aiba:1997ho, Aiba:2009ft, Antunez:2001gk, Atkin:1998in, augspurger_light_1984, baltzer_physiological_2007, baraloto_differential_2006, baraloto_seed_2005, Bloor:2003fa,  Broncano:1998ck, Brown:1996ks, Bruhn:2000jz, Cai:2007ie, CamaraZapata:2003df, CastroDiez:1998gz, CastroDiez:2003jd, Cernusak:2008ds, Chao:2008hg, Chaturvedi:2011jx, Chaturvedi:2014ie, Chave:2009iy,  coomes_comparison_1998, coomes_greater_2009, Cornelissen:1996hf, Cornelissen:1997fd, Cornelissen:1998ta, Dalling:2004gs, DeBell:1994ix, Easdale:2009gv, fan_hydraulic_2012, Fayolle:2012bx, Fujimoto:2006fg, Galmes:2005fa, Gleason:2016, gleeson_plant_1994, grotkopp_toward_2002, Grubb:1996kr, Herault:2011dd, Hoffmann:2003ga, Huante:1995fd, Huante:1995tl, Huante:1998bk, HUNT:1997ge, Iida:2014ep, Iida:2014hq, king_influence_1994, king_tree_2005,  King:2006he, Kitajima:1994ez, Kohyama:2003dk, Kruger:2006fq, Lamers:2006dl, LopezIglesias:2014dk, Loveys:2002hj, Lusk:1997ga, Lusk:2002fma, Lusk:2013bq, Lusk:2013hz, MartinezVilalta:2010iq, McCormack:2012ch, Moya:2008ep, Muller-landau_interspecific_2004, Nascimento:2005kl, Osone:2008dr, Osunkoya:1994ip, Osunkoya:2010ef, Paz:2005kx, Poorter:1999fp, Poorter:2006vb, Poorter:2008iu, Poorter:2010co, Popma:1988tv, Prior:2004cv, Quero:2008jg, Read:2011du, Reich:1998ir, Reich:1998ja, Rossatto:2009gq, RuizRobleto:2005hc, Sack:2004hm, saldana-acosta_seedling_2009, SalgadoLuarte:2012ci, Saverimuttu:1996ih, Shen:2014fw, Shipley:2002fs, Stratton:2001ck, Thomas:1996do, Tomlinson:2014im, Veneklaas:2002dt, Villagra:2013do, Villar:2006cf, walters_are_1996, Walters:1993eu, Walters:1993hf, Wang:1998cs, Warren:2005bc, Westbrook:2011ja, Wright:1999ds, Wright:2000kw, Wright:2001gb, Wright:2003kb, Wright:2010tp, Zhang:1995bh}.
+Ultimately, data were recorded from 103 different articles \citep{Aiba:1997ho, Aiba:2009ft, Antunez:2001gk, Atkin:1998in, augspurger_light_1984, baltzer_physiological_2007, baraloto_differential_2006, baraloto_seed_2005, Bloor:2003fa,  Broncano:1998ck, Brown:1996ks, Bruhn:2000jz, Cai:2007ie, CamaraZapata:2003df, CastroDiez:1998gz, CastroDiez:2003jd, Cernusak:2008ds, Chao:2008hg, Chaturvedi:2011jx, Chaturvedi:2014ie, Chave:2009iy,  coomes_comparison_1998, coomes_greater_2009, Cornelissen:1996hf, Cornelissen:1997fd, Cornelissen:1998ta, Dalling:2004gs, DeBell:1994ix, Easdale:2009gv, fan_hydraulic_2012, Fayolle:2012bx, Fujimoto:2006fg, Galmes:2005fa, Gleason:2016, gleeson_plant_1994, grotkopp_toward_2002, Grubb:1996kr, Herault:2011dd, Hoffmann:2003ga, Huante:1995fd, Huante:1995tl, Huante:1998bk, HUNT:1997ge, Iida:2014ep, Iida:2014hq, king_influence_1994, king_tree_2005,  King:2006he, Kitajima:1994ez, Kohyama:2003dk, Kruger:2006fq, Lamers:2006dl, LopezIglesias:2014dk, Loveys:2002hj, Lusk:1997ga, Lusk:2002fma, Lusk:2013bq, Lusk:2013hz, MartinezVilalta:2010iq, McCormack:2012ch, Moya:2008ep, Muller-landau_interspecific_2004, Nascimento:2005kl, Osone:2008dr, Osunkoya:1994ip, Osunkoya:2010ef, Paz:2005kx, Poorter:1999fp, Poorter:2006vb, Poorter:2008iu, Poorter:2010co, Popma:1988tv, Prior:2004cv, Quero:2008jg, Read:2011du, Reich:1998ir, Reich:1998ja, Rossatto:2009gq, RuizRobleto:2005hc, Sack:2004hm, saldana-acosta_seedling_2009, SalgadoLuarte:2012ci, Saverimuttu:1996ih, Shen:2014fw, Shipley:2002fs, Stratton:2001ck, Thomas:1996do, Tomlinson:2014im, Veneklaas:2002dt, Villagra:2013do, Villar:2006cf, walters_are_1996, Walters:1993eu, Walters:1993hf, Wang:1998cs, Warren:2005bc, Westbrook:2011ja, Wright:1999ds, Wright:2000kw, Wright:2001gb, Wright:2003kb, Wright:2010tp, Zhang:1995bh}.
 
@@
 Because these categories were established according to the expertise of the authors, we were concerned about the risk of assigning plants of similar size to different categories when compiling data across multiple studies and vegetation types.
-This risk turned out to be small: overall, we found that the original thresholds in size/age used by the authors to distinguish different stages were relatively compatible with thresholds we defined (Fig.
+This risk turned out to be small: overall, we found that the original thresholds in size/age used by the authors to distinguish different stages were relatively compatible with thresholds we defined ourselves (Fig.
 \ref{fig:fig2}).
 In particular, there was a clear break between seedlings and saplings in both age (at 1 yr) and height (at 0.5 m).
-There was also a clear break between saplings and adults in diameter (at 10 cm).
+There was also a clear break between saplings and adults in steam diameter (at 10 cm).
 Comparing these values to the bivariate relationships observed between variables (age, height, diameter) in the ``Biomass And Allometry Database'' \citep{Falster:2015}, demonstrated that the thresholds identified above for each stage transition also aligned relatively well with one another (Fig.
@@
 We then compared these results with those from the subset of the dataset using relative growth rate, but with all other criteria relaxed.
-Finally, we compared results from both relative and absolute growth rates from the entire dataset.
+Finally, we compared results from both relative and absolute growth rates, from the entire dataset.
 
@@
 Inclusion of this random effect allowed us to account for heterogeneity among studies, for example in experimental type, and vegetation type.
-For each trait, we performed a separate model and we established whether stage could explain additional variance in $z$ by comparing models with and without a stage effect using log-likelihood ratios \citep{Zuur:2009cfa}.
+For each trait, we ran a separate model and established whether stage could explain additional variance in $z$ by comparing models with and without a stage effect using log-likelihood ratios \citep{Zuur:2009cfa}.
 If the log-likelihood test returned a significant p-value, the stage model fitted the data better than the model without.
@@
 
-All analyses were conducted with \texttt{R} software \citep{Ralanguageanden:2014wf} using packages \texttt{lme4} \citep{Bates-2014}.
-\texttt{metafor} \citep{Viechtbauer-2010}, and \texttt{gpplot2} \citep{Wickham:2009}.
+All analyses were conducted with \texttt{R} software \citep{Ralanguageanden:2014wf} using packages \texttt{lme4} \citep{Bates-2014}, \texttt{metafor} \citep{Viechtbauer-2010}, and \texttt{gpplot2} \citep{Wickham:2009}.
 
@@
 But this limitation applied only for NARmass and vessel density, where studies appeared confined to seedling and adult stages respectively.
-However, for a majority of traits the number of observations across stage was highly unbalanced; for one-third of the 19 traits $>$ 75\% of correlations with growth reported come from a same stage (Fig.
+However, for a majority of traits the number of observations across stage was highly unbalanced; for one-third of the 19 traits $>$ 75\% of correlations with growth reported come from the same stage (Fig.
 \ref{fig:fig1}).
@@
 \ref{fig:fig3}b).
-Accordingly, model fits were marginally improved when stage was incorporated (p.value = 0.049).
+Accordingly, model fits were marginally improved when stage was incorporated (p-value = 0.049).
 Note that the CIs did not cross zero for seedling and sapling stage despite the small sample sizes (n= 1 and 4 respectively), meaning a strong correlation and/or a good consistency in the coefficient reported for each stage across studies.
@@
 
-As expected for seed mass, the correlation with relative growth rate shifted from negative at seedling stage ($\bar{r}= -0.5 \pm 0.07$) to not significantly different from zero at adult and sapling stages (Fig \ref{fig:fig3}c, CIs overlapping zero).
-However, the correlation between seed mass and relative growth rate at adult and sapling stages were also not significantly different from that observed at seedling stage (see log likelihood ratio tests and CIs overlapping in Fig.
+As expected, for seed mass the correlation with relative growth rate shifted from negative at seedling stage ($\bar{r}= -0.5 \pm 0.07$) to not significantly different from zero at adult and sapling stages (Fig \ref{fig:fig3}c, CIs overlapping zero).
+However, the correlations between seed mass and relative growth rate at adult and sapling stages were also not significantly different from that observed at seedling stage (see log likelihood ratio tests and CIs overlapping in Fig.
 \ref{fig:fig3}c).
@@
 We now report results for relative growth rate from the entire dataset.
-Our aim is to determine if additional data alters or reinforces the above conclusions, by increasing replication.
-This entire dataset included correlations measured with relative growth rate exclusively (Fig.
-\ref{fig:fig3}), across at least two species (but measured using several individuals), and did not control for the source of trait or growth (i.e.
+Our aim here was to determine if additional data alters or reinforces the above conclusions, by increasing replication.
+For this analysis our dataset included correlations concerning relative growth rate exclusively (Fig.
+\ref{fig:fig3}), measured across at least two species (but using several individuals), and did not control for the source of trait or growth (i.e.
 traits could be measured on a different ontogenetic stage to growth data) or environmental conditions.
@@
 The only correlation that we hypothesized would change if absolute growth rate was used instead of relative growth rate, was for seed mass.
-Overall, the models fit did not improve when growth measurement was incorporated (see log likelihood ratio tests in Fig.
+Overall, the model fits did not improve when information about growth measurement used (relative vs absolute growth rates) was incorporated in the model (see log likelihood ratio tests in Fig.
 \ref{fig:fig4}).
 For a majority of traits, effect sizes were generally consistent between relative growth rate and absolute growth rate when both measurements were available (e.g.
-effect size for relative and absolute growth rate of Hmax and Wood density at adult stage in Fig.
+effect size for relative and absolute growth rate of Hmax and wood density at adult stage in Fig.
 \ref{fig:fig4} b and c).
@@
 For seed mass, effect size at seedling stage with relative growth rate was positive and shifted to non significant with absolute growth rate (Fig \ref{fig:fig4}d; CI overlapping zero).
-While these results were consistent with expectations, our ability to conclude was limited due to low sample size for correlation with absolute growth rate (i.e CIs overlapping, Fig.
-\ref{fig:fig4}d).
+While these results were consistent with expectations, our ability to draw any firm conclusions was limited due to low sample size for correlation with absolute growth rate (i.e CIs overlapping, Fig.
+\ref{fig:fig4} d).
 For wood density, some differences occurred according to the growth measurement used, but they were not easily attributed to any single cause.
-In particular, the correlation at juvenile stage shifted from negative with relative growth rate to non significant with absolute growth rate (i.e CI included zero, Fig.
+In particular, the correlation at juvenile stage shifted from negative with relative growth rate to non-significant with absolute growth rate (i.e CI included zero, Fig.
 \ref{fig:fig4}b).
@@
 
-The meta-analysis reported here demonstrates that for several key traits, the influence of the trait on growth rate change as plants grow from small to large.
+The meta-analysis reported here demonstrates that for several key traits, the influence of the trait on growth rate changes as plants grow from small to large.
 While the possibility has been raised recently that trait-growth correlations may change systematically with size \citep{Falster:2011ii, Ruger:2012jv, Iida:2014ep, Iida:2014hq}, this is the first time that specific mechanistic hypotheses have been corroborated against a wide array of existing studies.
@@
 Increasing support costs also devalue the benefits of cheap leaf construction (low SLA), because as plant's grow larger, an increasing amount of total biomass production is devoted to building and maintaining support tissues \citep{Givnish:1995ta,King-2011}.
-The net result is that the growth advantage experienced by high SLA species at small sizes, dissapates among larger plants.
+The net result is that the growth advantage experienced by high SLA species at small sizes, dissipates by the time large plante size are attained.
 While it has previously been noted that the correlation of SLA with growth rate disappears among saplings and larger trees (\citealt{Wright:2010tp} for Barro Colorado Island forest, Panama), our meta-analysis generalises that result.
@@
 Further, the assumed empirical relationship between SLA and total leaf area does not hold true as a generalisation across large number of species \citep{Duursma-2015}.
-In another modelling study, the SLA optimising growth rate was found to decrease with plant size, because of cross connections with the amount of self-shading in the crown and the increase in support costs in larger plants \citep{King-1999}.
+In another modelling study, the SLA that lead to optimal growth rate was found to decrease with plant size, because of the interplay with the degree of self-shading in the crown and the fact that support costs are greater in larger plants \citep{King-1999}.
 In the model described here, the mechanism is slightly different: high-SLA species incur faster leaf turnover, the cost of which outweighs the benefits of cheap leaf construction at larger sizes.
 
-For wood density the meta-analysis showed negative correlation with relative growth rate across all ontogenetic stages, as previously reported from individual studies \citep{Wright:2010tp,Ruger:2012jv}.
+For wood density the meta-analysis showed negative correlations with relative growth rate at all ontogenetic stages, as previously reported from individual studies \citep{Wright:2010tp,Ruger:2012jv}.
 It should be noted however that there are few data available to test this proposition at seedling stage (n=1-4).
 In our model, cheaper stem construction is responsible for the predicted negative correlation.
-Lower xylem conductance and associated lower photosynthetic potential have also been suggested \citep[reviewed by][]{Chave:2009iy}.
-For seedlings a negative correlation arose regardless of whether wood density was measured on adult plants, or calculated as seedling stem segment dry weight over its volume (i.e.
+Lower xylem conductance in higher density sapwood and the associated lower photosynthetic potential, has also been suggested \citep[reviewed by][]{Chave:2009iy}.
+For seedlings a negative correlation arose regardless of whether wood density was inferred from measurements made on adult or measured in fact in seedlings (e.g.
 stem density in  \citealt{CastroDiez:1998gz}), suggesting that both measurements could be used.

### 2016-03-06 MS.tex
Add Ian suggestion (2/2)

--- 2016-03-06 MS.tex
@@
 The only correlation that we hypothesized would change if absolute growth rate was used instead of relative growth rate, was for seed mass.
-Overall, the models fit did not improve when growth measurement was incorporated (see log likelihood ratio tests in Fig.
+Overall, the models fit did not improve when information about growth measurement used (relative vs absolute growth rates) was incorporated in the models (see log likelihood ratio tests in Fig.
 \ref{fig:fig4}).
 For a majority of traits, effect sizes were generally consistent between relative growth rate and absolute growth rate when both measurements were available (e.g.
-effect size for relative and absolute growth rate of Hmax and Wood density at adult stage in Fig.
+effect size for relative and absolute growth rate of Hmax and wood density at adult stage in Fig.
 \ref{fig:fig4} b and c).

### 2016-03-07 MS.tex

--- 2016-03-06 MS.tex
@@
 The only correlation that we hypothesized would change if absolute growth rate was used instead of relative growth rate, was for seed mass.
-Overall, the model fits did not improve when information about growth measurement used (relative vs absolute growth rates) was incorporated in the model (see log likelihood ratio tests in Fig.
+Overall, the model fits did not improve when information about growth measurement (relative vs absolute growth rates) was incorporated in the model (see log likelihood ratio tests in Fig.
 \ref{fig:fig4}).

### 2016-03-07 MS.tex
Changes some sentences in the result part to better fit with the cover letter

@@
 
-For wood density, maximum height, and seed mass, correlations with relative growth rate were also consistent with expectations but our ability to test all hypotheses was at times limited due to low sample size.
+For wood density and seed mass the available results are consistent with expectation from theory but it would be desirable to have substantially more data.
 Indeed, while meta-analysis is possible even with few observations, strong conclusions are generally precluded by very large CIs of the effect size (i.e highly uncertain estimates and CI often spanned zero).
@@
 
+As expected, for seed mass the correlation with relative growth rate shifted from negative at seedling stage ($\bar{r}= -0.5 \pm 0.07$) to not significantly different from zero at adult and sapling stages (Fig \ref{fig:fig3}c, CIs overlapping zero).
+However, the correlations between seed mass and relative growth rate at adult and sapling stages were also not significantly different from that observed at seedling stage (see log likelihood ratio tests and CIs overlapping in Fig.
+\ref{fig:fig3}c).
+Again we could not distinguish between these alternatives.
+But the number of coefficients reported for seed mass was almost similar between adult (n= 7) and seedling (n= 10) stages, suggesting that CIs overlapping zero at adult stage were due to variation in correlation coefficients reported rather than to a much smaller numbers of replicates.
+
+For maximum height and assimilation rates, correlations with relative growth rate were also consistent with expectations but our ability to test all hypotheses was at times limited due to low or no sample size.
+
 For maximum height, the expectation was for a correlation with growth to be present for large plants but absent for smaller sizes, the mechanism being increased relative allocation to reproduction as maximum height is approached.
@@
 Due to small numbers of replicate studies for sapling stage and no replicates for seedling stage, we could not conclude on the absence of correlation between maximum height and growth at small plant size.
-
-As expected, for seed mass the correlation with relative growth rate shifted from negative at seedling stage ($\bar{r}= -0.5 \pm 0.07$) to not significantly different from zero at adult and sapling stages (Fig \ref{fig:fig3}c, CIs overlapping zero).
-However, the correlations between seed mass and relative growth rate at adult and sapling stages were also not significantly different from that observed at seedling stage (see log likelihood ratio tests and CIs overlapping in Fig.
-\ref{fig:fig3}c).
-Again we could not distinguish between these alternatives.
-But unlike maximum height, the number of coefficients reported for seed mass was almost similar between adult (n= 7) and seedling (n= 10) stages, suggesting that CIs overlapping zero at adult stage were due to variation in correlation coefficients reported rather than to a much smaller numbers of replicates.
 

### 2016-03-07 MS.tex
Changes some sentences in the result part to better fit with the cover letter

@@
 
-For wood density and seed mass the available results are consistent with expectation from theory but it would be desirable to have substantially more data.
+For wood density and seed mass, the available results are consistent with expectation from theory but it would be desirable to have substantially more data.
 Indeed, while meta-analysis is possible even with few observations, strong conclusions are generally precluded by very large CIs of the effect size (i.e highly uncertain estimates and CI often spanned zero).

### 2016-03-08 MS.tex
Small editing changes
Minor edits to text

--- 2016-03-07 MS.tex
@@
 
-Assuming plants with a similar cross section of conducting tissue, cheaper stem construction (low wood density or stem density) will increase the marginal rate of leaf deployment per total mass increment ($\frac{\ud A_{\rm l}}{\ud M_{\rm a} }$), and consequently growth rate in height and diameter (eqs.
+Assuming plants maintain a similar cross section of conducting tissue per unit leaf area, cheaper stem construction (low wood density or stem density) will increase the marginal rate of leaf deployment per total mass increment ($\frac{\ud A_{\rm l}}{\ud M_{\rm a} }$), and consequently growth rate in height and diameter (eqs.
 \ref{eq:eq2}-\ref{eq:eq4}; Table \ref{tab:trade-offs}).
@@
 This effect occurs in the term $\frac{\ud M_{\rm a} }{\ud B}$ (the allocation to vegetative growth) in eqs.
-(\ref{eq:eq2}-\ref{eq:eq3}).
+\ref{eq:eq2}-\ref{eq:eq3}.
 For seedlings, where individuals are investing solely in growth, we expect no influence of maximum height on growth (i.e.
@@
 The only effect of increased seed size in the above model is to produce a larger overall seedling.
-Under similar light conditions, larger seedlings are predicted to have faster absolute growth rates.
-However, because the ratio of leaf area to total biomass decreases with plant size, larger seedlings are predicted to have lower mass-based relative growth rates during the earliest phases of growth \citep{Turnbull:2012ew}(Table \ref{tab:trade-offs}).
-Yet, as plants grow, we expect the effect of this initial size difference to be minimal, and the correlation between seed size and growth rate should therefore disappear.
-For larger plants, seed mass is not expected to have any distinct influence on growth rates (Table \ref{tab:trade-offs}).
+Under similar light conditions, larger seedlings are predicted to have faster absolute growth rates (in diameter, height, and mass), because of their greater total leaf area.
+At the same time, relative growth rate is predicted to decrease with size, because the ratio of leaf area to support mass decreases with plant size \citep[see also][]{Turnbull:2012ew}.
+We therefore expect a positive correlation between seed size and absolute growth rate and a negative correlation between seed size and relative growth rate, at the seedling stage (Table \ref{tab:trade-offs}).
+As plants grow, differences in initial mass will decrease in importance, relative to other factors influencing growth through the life-cycle.
+We therefore expect the correlations between seed size and growth rate observed for seedlings to disappear among larger plants (Table \ref{tab:trade-offs}).
 
@@
 In particular, there was a clear break between seedlings and saplings in both age (at 1 yr) and height (at 0.5 m).
-There was also a clear break between saplings and adults in steam diameter (at 10 cm).
+There was also a clear break between saplings and adults in stem diameter (at 10 cm).
 Comparing these values to the bivariate relationships observed between variables (age, height, diameter) in the ``Biomass And Allometry Database'' \citep{Falster:2015}, demonstrated that the thresholds identified above for each stage transition also aligned relatively well with one another (Fig.
@@
 
-We identified only 55 studies containing 137 correlations reporting data measured under conservative criteria: unstressed growth, growth measured as relative growth rate, traits and growth recorded in same stage, and correlation coefficient calculated across \underline{\textgreater} 10 species.
+We identified only 55 studies containing 137 correlations reporting data measured under conservative criteria, i.e.
+unstressed growth, growth measured as relative growth rate, traits and growth recorded in same stage, and correlation coefficient calculated across \underline{\textgreater} 10 species.
 Overall, results were consistent with predictions, although with limitations arising for some traits due to very unequal (and limited) numbers of observations between growth stages.
@@
 
-For wood density and seed mass the available results are consistent with expectation from theory but it would be desirable to have substantially more data.
-Indeed, while meta-analysis is possible even with few observations, strong conclusions are generally precluded by very large CIs of the effect size (i.e highly uncertain estimates and CI often spanned zero).
+For wood density and seed mass, the available results are consistent with our theoretical expectations, but it would be desirable to have substantially more data.
+Indeed, while it is possible to conduct a meta-analysis even with few observations, strong conclusions are generally precluded by very large CIs of the effect size (i.e highly uncertain estimates and CI often spanned zero).
 
@@
 Accordingly, model fits were marginally improved when stage was incorporated (p-value = 0.049).
-Note that the CIs did not cross zero for seedling and sapling stage despite the small sample sizes (n= 1 and 4 respectively), meaning a strong correlation and/or a good consistency in the coefficient reported for each stage across studies.
+Note that the CIs did not cross zero for seedling and sapling stage, despite the small sample sizes (n= 1 and 4 respectively), meaning a strong correlation and/or a good consistent effect in the coefficient reported for each stage across studies.
 
@@
 \ref{fig:fig3}c).
-Again we could not distinguish between these alternatives.
+We could not distinguish between these alternatives.
 But the number of coefficients reported for seed mass was almost similar between adult (n= 7) and seedling (n= 10) stages, suggesting that CIs overlapping zero at adult stage were due to variation in correlation coefficients reported rather than to a much smaller numbers of replicates.
 
-For maximum height and assimilation rates, correlations with relative growth rate were also consistent with expectations but our ability to test all hypotheses was at times limited due to low or no sample size.
+For maximum height and Aarea, correlations with relative growth rate were also consistent with expectations, but our ability to test all hypotheses was at times limited due to low or no sample size.
 
@@
 For Aarea, results were consistent with a positive correlation with relative growth rate at seedling stage.
-However, no conclusion can be drawn about a change along ontogenetic stages as only four correlation coefficients were reported for this trait, and three of these were measured at the seedling stage (Fig.
+However, no conclusion can be drawn about a change along ontogenetic stages, as only four correlation coefficients were reported for this trait, and three of these were measured at the seedling stage (Fig.
 \ref{fig:fig3}e).
@@
 from 25 to 59 correlation coefficients reported for SLA at seedling stage), while others still had few replicates.
-On the 13 traits-stage combinations studied in total, six had $\le$ five correlation coefficients: Wood density-seedling, maximum height-sapling, maximum height-seedling, Seed mass-sapling, Aarea-adult and Aarea-sapling.
+On the 13 traits-stage combinations studied in total, six had $\le$ five correlation coefficients: wood density-seedling, maximum height-sapling, maximum height-seedling, seed mass-sapling, Aarea-adult and Aarea-sapling.
 
 Results from the entire dataset reinforced our conclusions for both SLA and wood density, and did not alter them for the others traits.
-For SLA and wood density, although the number of replicates doubled by using the entire dataset, effect sizes and overall results were similar to those reported above using the conservative crieteria (Fig.
+For SLA and wood density, although the number of replicates doubled by using the entire dataset, effect sizes and overall results were similar to those reported above using the conservative criteria (Fig.
 \ref{fig:fig3}).
@@
 Overall, the model fits did not improve when information about growth measurement (relative vs absolute growth rates) was incorporated in the model (see log likelihood ratio tests in Fig.
-\ref{fig:fig4}).
+\ref{fig:fig4}), thus supporting this claim.
 For a majority of traits, effect sizes were generally consistent between relative growth rate and absolute growth rate when both measurements were available (e.g.
@@
 \ref{fig:fig4} b and c).
-However, for seed mass and wood density at seedling stage, the direction of effect sizes changed when correlations were measured with abolute versus relative growth rate.
-For seed mass, effect size at seedling stage with relative growth rate was positive and shifted to non significant with absolute growth rate (Fig \ref{fig:fig4}d; CI overlapping zero).
+However, for seed mass and wood density at seedling stage, the direction of effect sizes changed when correlations were measured with absolute versus relative growth rate.
+For seed mass, effect size at seedling stage with relative growth rate was negative and shifted to non-significant with absolute growth rate (Fig \ref{fig:fig4}d; CI overlapping zero).
 While these results were consistent with expectations, our ability to draw any firm conclusions was limited due to low sample size for correlation with absolute growth rate (i.e CIs overlapping, Fig.
 \ref{fig:fig4} d).
-For wood density, some differences occurred according to the growth measurement used, but they were not easily attributed to any single cause.
-In particular, the correlation at juvenile stage shifted from negative with relative growth rate to non-significant with absolute growth rate (i.e CI included zero, Fig.
+For wood density, some differences were observed between studies reporting relative and absolute growth rates: in particular, the correlation at juvenile stage shifted from negative with relative growth rate to non-significant with absolute growth rate (i.e CI included zero, Fig.
 \ref{fig:fig4}b).
-Yet, the correlation coefficients recorded for absolute growth rate came from \citet{Augspurger:1984ct}, and unlike others they used wood density values from adult plants together with growth from juveniles.
-So it was not possible to disentangle the effect of growth measurement from the effect of trait origin.
+There may be several reasons for this difference, however, we note that the only available correlation coefficients recorded for absolute growth rate came from \citet{Augspurger:1984ct}, and unlike most other studies, they used wood density values estimated on adult plants together with growth data taken from seedlings.
+This suggest possible confounding between the type of growth measurement and origin of the trait data.
 

### 2016-03-08 MS.tex
Lower case pi
Enable png figures to be used over pdf
Removing extension in tex means that latex will take any of a number of graphic extensions
By default, tex preferences png over pdf, so if the png is present that will be used
Instead of changing our figures from pdf in R code, we can instead generate pngs using ImageMagikk's convert function, e.g.  `convert -density 300 -background white -quality 100 "$i" "${i%.*}.png"`

@@
 \begin{equation}\label{eq:eq4}
-\underbrace{\frac{\ud D}{\ud t}}_{\text{growth rate in diameter}} = \left(\Pi \, A_{\rm st}\right)^{-0.5} \times {\frac{\ud A_{\rm st}}{\ud t}}.
+\underbrace{\frac{\ud D}{\ud t}}_{\text{growth rate in diameter}} = \left(\pi \, A_{\rm st}\right)^{-0.5} \times {\frac{\ud A_{\rm st}}{\ud t}}.
 \end{equation}
@@
 \centering
-\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/Fig1.pdf}
+\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/Fig1}
 \caption{Number of recorded correlations between trait and growth rate in our dataset, by stage and trait.
@@
 \centering
-\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/Fig2.pdf}
+\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/Fig2}
 \caption{The range of plant sizes and stages recorded in original publications (horizontal coloured lines), compared to standardised thresholds used in the analysis (vertical black lines).
@@
 \centering
-\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/Fig3.pdf}
+\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/Fig3}
 \caption{The relationship between relative growth rates (RGR) and traits changes with ontogenetic stage and trait.
@@
 \centering
-\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/Fig4.pdf}
+\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/Fig4}
 \caption{Relationships between relative (RGR) and/or absolute (AGR) growth rates and traits along ontogenetic stage.

### 2016-03-08 ms-suppinfo.Rnw
LIzzy comments 1
Enable png figures to be used over pdf
Removing extension in tex means that latex will take any of a number of graphic extensions
By default, tex preferences png over pdf, so if the png is present that will be used
Instead of changing our figures from pdf in R code, we can instead generate pngs using ImageMagikk's convert function, e.g.  `convert -density 300 -background white -quality 100 "$i" "${i%.*}.png"`

@@
 \centering
-\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA1.pdf}
+\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA1}
 \caption{Relationships between a) age and diameter (m), b) age and height (m), and c) diameter and height among plants in the Biomass and Allometry Database.
@@
 \centering
-\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA6a.pdf}
+\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA6a}
 \end{figure}
@@
 \centering
-\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA6b.pdf}
+\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA6b}
 \end{figure}
@@
 \centering
-\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA6c.pdf}
+\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA6c}
 \caption{Effects size on the correlation between growth and traits of plant stage (mod1), growth measurement (mod2), vegetation type (mod3), and experiment type (mod4).
@@
 \centering
-\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA4.pdf}
+\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA4}
 \caption{Mean coefficient correlation r (+SD) between growth and traits measured by stage.
@@
 \centering
-\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA8.pdf}
+\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA8}
 \caption{Number of correlation extracted by traits, stage, and growth type (absolute vs relative, and measurement).
@@
 \centering
-\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA2.pdf}
+\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA2}
 \caption{Geographical distribution of site locations from studies performed in the field used in the meta-analysis.
@@
 \centering
-\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA3.pdf}
+\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA3}
 \caption{Range of correlations (r) between
@@
 \centering
-\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA7.pdf}
+\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA7}
 \caption{Funnel plots with filled in data based on the trim and fill method, showing transformed correlation coefficient z between growth and a) Specific leaf area (SLA), b) Wood density (WD), c) Asymptotic maximum height (Hmax), d) Seed mass and e) Assimilation rate of CO2 (Aarea).
@@
 \centering
-\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA9.pdf}
+\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA9}
 \caption{Temporal changes in coefficient of correlation between growth and traits.
@@
 \centering
-\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA5.pdf}
+\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA5}
 \caption{Effect size ($\pm$95\% confidence intervals, CI) of plant stage on the correlations between growth rate and five functional traits across species, with a data set averaging multiple comparisons by trait and by study.

### 2016-03-08 MS.tex
Editing in Results part: Comparison RGR AGR Change Fig 3 and 4: "n" were overlapping CI

@@
 \ref{fig:fig4}), thus supporting this claim.
-For a majority of traits, effect sizes were generally consistent between relative growth rate and absolute growth rate when both measurements were available (e.g.
-effect size for relative and absolute growth rate of Hmax and wood density at adult stage in Fig.
+For all traits, effect sizes were non significantly different between relative growth rate and absolute growth rate when both measurements were available (e.g.
+CIs overlapping between relative and abolute growth rates for each stage, Fig.
+\ref{fig:fig4}).
+Effect sizes measured with a same number of observations for relative and absolute growth rate were generally very consistent (i.e.
+Hmax and wood density at adult stage in Fig.
 \ref{fig:fig4} b and c).
 However, for seed mass and wood density at seedling stage, the direction of effect sizes changed when correlations were measured with absolute versus relative growth rate.
-For seed mass, effect size at seedling stage with relative growth rate was negative and shifted to non-significant with absolute growth rate (Fig \ref{fig:fig4}d; CI overlapping zero).
+For seed mass, effect size at seedling stage with relative growth rate was negative and shifted to positive (but non-significant; CI included zero, Fig \ref{fig:fig4}d) with absolute growth rate.
 While these results were consistent with expectations, our ability to draw any firm conclusions was limited due to low sample size for correlation with absolute growth rate (i.e CIs overlapping, Fig.
 \ref{fig:fig4} d).
-For wood density, some differences were observed between studies reporting relative and absolute growth rates: in particular, the correlation at juvenile stage shifted from negative with relative growth rate to non-significant with absolute growth rate (i.e CI included zero, Fig.
-\ref{fig:fig4}b).
-There may be several reasons for this difference, however, we note that the only available correlation coefficients recorded for absolute growth rate came from \citet{Augspurger:1984ct}, and unlike most other studies, they used wood density values estimated on adult plants together with growth data taken from seedlings.
-This suggest possible confounding between the type of growth measurement and origin of the trait data.
+For wood density, some differences were observed between studies reporting relative and absolute growth rates: in particular, the correlation at seedling stage shifted from negative with relative growth rate to positive (but non-significant; CI included zero, Fig.
+\ref{fig:fig4}b) with absolute growth rate.
+There may be several reasons for this difference, however, we note that the only available correlation coefficients recorded for absolute growth rate at seedling stage came from \citet{Augspurger:1984ct}, and unlike most other studies, they used wood density values estimated on adult plants together with growth data taken from seedlings.
+This suggests possible confounding between the type of growth measurement and origin of the trait data.
 
@@
 See Appendix \ref{app:supp_info_analyses} for details.\\
-  9.& Sensitivity analysis &  yes &See ``Material and Methods'' for details, results in Figs \ref{fig:fig4} \& \ref{fig:figA5}.\\
+  9.& Sensitivity analysis &  yes &See ``Material and Methods'' for details, results in Figs \ref{fig:fig3} \& \ref{fig:figA5}.\\
   10.& Exploring temporal changes in effect size &  yes & See Appendix \ref{app:supp_info_analyses} for details.\\

### 2016-03-08 R/figures.R

@@ -110,7 +110,7 @@ figure_panels_traits_model <- function(fits, ...) {
 
     data[["by"]] <- as.factor(data[[category_variable]])
 
-    label.n.x <- limit.x.min + 0.85*(limit.x.max - limit.x.min)
+    label.n.x <- limit.x.min + 0.885*(limit.x.max - limit.x.min)
 
     dodge <- position_dodge(width = width)
 

### 2016-03-16 MS.tex
Small editing

@@
 \ref{fig:fig2}).
-Only 7 of 103 articles were ambiguous on their ontogenetic stage attribution.
+Only 6 of 103 articles were ambiguous on their ontogenetic stage attribution.
 Half of these equivocal cases involved the juvenile category.
@@
 These differences provide good criteria for assessing the quality of the data for addressing our hypotheses.
-We adopted a three-stage approach where at first we were conservative by focusing exclusively on relative growth rate, across studies that included \underline{\textgreater} 10 species, under unstressed conditions, and where the trait and growth were measured at the same stage (expect for maximum height and seed mass, where a particular stage is by definition required to measure the trait).
+We adopted a three-stage approach where at first we were conservative by focusing exclusively on relative growth rate, across studies that included \underline{\textgreater} 10 species, under unstressed conditions, and where the trait and growth were measured at the same stage (except for maximum height and seed mass, where a particular stage is by definition required to measure the trait).
 We then compared these results with those from the subset of the dataset using relative growth rate, but with all other criteria relaxed.
@@
 Indeed, while it is possible to conduct a meta-analysis even with few observations, strong conclusions are generally precluded by very large CIs of the effect size (i.e highly uncertain estimates and CI often spanned zero).
-
 For wood density, results were consistent with the prediction for negative correlations with relative growth rate across all plant sizes (Fig.
@@
 Note that the CIs did not cross zero for seedling and sapling stage, despite the small sample sizes (n= 1 and 4 respectively), meaning a strong correlation and/or a good consistent effect in the coefficient reported for each stage across studies.
-
 As expected, for seed mass the correlation with relative growth rate shifted from negative at seedling stage ($\bar{r}= -0.5 \pm 0.07$) to not significantly different from zero at adult and sapling stages (Fig \ref{fig:fig3}c, CIs overlapping zero).
@@
 For maximum height and Aarea, correlations with relative growth rate were also consistent with expectations, but our ability to test all hypotheses was at times limited due to low or no sample size.
-
 For maximum height, the expectation was for a correlation with growth to be present for large plants but absent for smaller sizes, the mechanism being increased relative allocation to reproduction as maximum height is approached.
@@
 Due to small numbers of replicate studies for sapling stage and no replicates for seedling stage, we could not conclude on the absence of correlation between maximum height and growth at small plant size.
-
 For Aarea, results were consistent with a positive correlation with relative growth rate at seedling stage.
@@
 This suggests the mechanisms through which traits affect growth are correctly represented in the model.
-For SLA the meta-analysis strongly confirmed the predicted influence of plant size on the trait-growth correlation.
+For SLA, the meta-analysis strongly confirmed the predicted influence of plant size on the trait-growth correlation.
 For wood density, Aarea, seed mass and maximum height results were consistent with predictions, but data was limited and additional studies would be helpful for these trait-growth-stage relationships.
@@
 \caption{Number of recorded correlations between trait and growth rate in our dataset, by stage and trait.
-Traits are: Aarea (or Amass) = rate of CO$_{2}$ assimilation per unit leaf area (or leaf mass) = maximum photosynthetic rate, Hmax = asymptotic or maximum height, Ks = stem hydraulic conductance, LA = leaf area, LMR = leaf mass ratio, NARarea = net mass assimilation rate per unit of leaf area, Nmass (or Narea) = nitrogen content per unit of leaf mass (or leaf area), Pmass = phosphorus content per unit of leaf mass, SA/LA = sapwood area per leaf area, SLA = specific leaf area, Thickness = leaf thickness, Vessel size = stem conduit size, Vessel density = stem conduit density, WD = wood density.
+Traits are: Aarea (or Amass) = rate of CO$_{2}$ assimilation per unit leaf area (or leaf mass) = maximum photosynthetic rate, Hmax = asymptotic or maximum height, Ks = stem hydraulic conductance, LA = leaf area, LMR = leaf mass ratio, NARarea  (or NARmass) = net mass assimilation rate per unit of leaf area (or leaf mass), Nmass (or Narea) = nitrogen content per unit of leaf mass (or leaf area), Pmass = phosphorus content per unit of leaf mass, SA/LA = sapwood area per leaf area, SLA = specific leaf area, Thickness = leaf thickness, Vessel size = stem conduit size, Vessel density = stem conduit density, WD = wood density.
 Results shown are from the entire dataset (see methods for details).}

### 2016-03-16 MS.tex
Fixed a ref Homogenized: "Fig."

@@
 
-Ultimately, data were recorded from 103 different articles \citep{Aiba:1997ho, Aiba:2009ft, Antunez:2001gk, Atkin:1998in, augspurger_light_1984, baltzer_physiological_2007, baraloto_differential_2006, baraloto_seed_2005, Bloor:2003fa,  Broncano:1998ck, Brown:1996ks, Bruhn:2000jz, Cai:2007ie, CamaraZapata:2003df, CastroDiez:1998gz, CastroDiez:2003jd, Cernusak:2008ds, Chao:2008hg, Chaturvedi:2011jx, Chaturvedi:2014ie, Chave:2009iy,  coomes_comparison_1998, coomes_greater_2009, Cornelissen:1996hf, Cornelissen:1997fd, Cornelissen:1998ta, Dalling:2004gs, DeBell:1994ix, Easdale:2009gv, fan_hydraulic_2012, Fayolle:2012bx, Fujimoto:2006fg, Galmes:2005fa, Gleason:2016, gleeson_plant_1994, grotkopp_toward_2002, Grubb:1996kr, Herault:2011dd, Hoffmann:2003ga, Huante:1995fd, Huante:1995tl, Huante:1998bk, HUNT:1997ge, Iida:2014ep, Iida:2014hq, king_influence_1994, king_tree_2005,  King:2006he, Kitajima:1994ez, Kohyama:2003dk, Kruger:2006fq, Lamers:2006dl, LopezIglesias:2014dk, Loveys:2002hj, Lusk:1997ga, Lusk:2002fma, Lusk:2013bq, Lusk:2013hz, MartinezVilalta:2010iq, McCormack:2012ch, Moya:2008ep, Muller-landau_interspecific_2004, Nascimento:2005kl, Osone:2008dr, Osunkoya:1994ip, Osunkoya:2010ef, Paz:2005kx, Poorter:1999fp, Poorter:2006vb, Poorter:2008iu, Poorter:2010co, Popma:1988tv, Prior:2004cv, Quero:2008jg, Read:2011du, Reich:1998ir, Reich:1998ja, Rossatto:2009gq, RuizRobleto:2005hc, Sack:2004hm, saldana-acosta_seedling_2009, SalgadoLuarte:2012ci, Saverimuttu:1996ih, Shen:2014fw, Shipley:2002fs, Stratton:2001ck, Thomas:1996do, Tomlinson:2014im, Veneklaas:2002dt, Villagra:2013do, Villar:2006cf, walters_are_1996, Walters:1993eu, Walters:1993hf, Wang:1998cs, Warren:2005bc, Westbrook:2011ja, Wright:1999ds, Wright:2000kw, Wright:2001gb, Wright:2003kb, Wright:2010tp, Zhang:1995bh}.
+Ultimately, data were recorded from 103 different articles \citep{Aiba:1997ho, Aiba:2009ft, Antunez:2001gk, Atkin:1998in, augspurger_light_1984, baltzer_physiological_2007, baraloto_differential_2006, baraloto_seed_2005, Bloor:2003fa,  Broncano:1998ck, Brown:1996ks, Bruhn:2000jz, Cai:2007ie, CamaraZapata:2003df, CastroDiez:1998gz, CastroDiez:2003jd, Cernusak:2008ds, Chao:2008hg, Chaturvedi:2011jx, Chaturvedi:2014ie, Chave:2009iy,  coomes_comparison_1998, coomes_greater_2009, Cornelissen:1996hf, Cornelissen:1997fd, Cornelissen:1998ta, Dalling:2004gs, DeBell:1994ix, Easdale:2009gv, fan_hydraulic_2012, Fayolle:2012bx, Fujimoto:2006fg, Galmes:2005fa, Gleason:2016, gleeson_plant_1994, grotkopp_toward_2002, Grubb:1996kr, Herault:2011dd, Hoffmann:2003ga, Huante:1995fd, Huante:1995tl, Huante:1998bk, HUNT:1997ge, Iida:2014ep, Iida:2014hq, king_influence_1994, king_tree_2005,  King:2006he, Kitajima:1994ez, Kohyama:2003dk, Kruger:2006fq, Lamers:2006dl, LopezIglesias:2014dk, Loveys:2002hj, Lusk:1997ga, Lusk:2002fma, Lusk:2013bq, Lusk:2013hz, MartinezVilalta:2010iq, McCormack:2012ch, Moya:2008ep, MullerLandau:2004dc, Nascimento:2005kl, Osone:2008dr, Osunkoya:1994ip, Osunkoya:2010ef, Paz:2005kx, Poorter:1999fp, Poorter:2006vb, Poorter:2008iu, Poorter:2010co, Popma:1988tv, Prior:2004cv, Quero:2008jg, Read:2011du, Reich:1998ir, Reich:1998ja, Rossatto:2009gq, RuizRobleto:2005hc, Sack:2004hm, saldana-acosta_seedling_2009, SalgadoLuarte:2012ci, Saverimuttu:1996ih, Shen:2014fw, Shipley:2002fs, Stratton:2001ck, Thomas:1996do, Tomlinson:2014im, Veneklaas:2002dt, Villagra:2013do, Villar:2006cf, walters_are_1996, Walters:1993eu, Walters:1993hf, Wang:1998cs, Warren:2005bc, Westbrook:2011ja, Wright:1999ds, Wright:2000kw, Wright:2001gb, Wright:2003kb, Wright:2010tp, Zhang:1995bh}.
 
@@
 The transformation was achieved via Fisher's z-transformation,
-\[ z = \frac{1}{2} \ln \frac{1+r}{1-r},\]
+\[ z = \frac{1}{2} \ln \frac{1+r}{1-r}\]
 which has a variance estimate of
-\[ v_z= \frac{1}{n-3},\]
+\[ v_z= \frac{1}{n-3}\]
 where $n$ is the number of species.
@@
 Note that the CIs did not cross zero for seedling and sapling stage, despite the small sample sizes (n= 1 and 4 respectively), meaning a strong correlation and/or a good consistent effect in the coefficient reported for each stage across studies.
-As expected, for seed mass the correlation with relative growth rate shifted from negative at seedling stage ($\bar{r}= -0.5 \pm 0.07$) to not significantly different from zero at adult and sapling stages (Fig \ref{fig:fig3}c, CIs overlapping zero).
+As expected, for seed mass the correlation with relative growth rate shifted from negative at seedling stage ($\bar{r}= -0.5 \pm 0.07$) to not significantly different from zero at adult and sapling stages (Fig.
+\ref{fig:fig3}c, CIs overlapping zero).
 However, the correlations between seed mass and relative growth rate at adult and sapling stages were also not significantly different from that observed at seedling stage (see log likelihood ratio tests and CIs overlapping in Fig.
@@
 For maximum height, the expectation was for a correlation with growth to be present for large plants but absent for smaller sizes, the mechanism being increased relative allocation to reproduction as maximum height is approached.
-Here, maximum height was positively correlated with growth at adult stage ($\bar{r}= 0.38 \pm 0.05$), not significantly correlated at sapling stage (Fig \ref{fig:fig3}c, CIs overlapping zero) and no data were recorded for seedling stage.
+Here, maximum height was positively correlated with growth at adult stage ($\bar{r}= 0.38 \pm 0.05$), not significantly correlated at sapling stage (Fig.
+\ref{fig:fig3}c, CIs overlapping zero) and no data were recorded for seedling stage.
 While these results were consistent with our expectation that maximum height would be correlated with growth at adult stage, they did not differ significantly across ontogenetic stages (model fit not improved when stage was incorporated, see log likelihood ratio tests in Fig.
@@
 \ref{fig:fig3}).
-For seed mass and Aarea, the additional replicates in the entire dataset allowed us to be more confident of the effect size for seedling stage (Fig \ref{fig:fig3}d, e).
+For seed mass and Aarea, the additional replicates in the entire dataset allowed us to be more confident of the effect size for seedling stage (Fig.
+\ref{fig:fig3}d and e).
 Comparison of Aarea effect between the conservative and relaxed criteria (Fig.
@@
 Hmax and wood density at adult stage in Fig.
-\ref{fig:fig4} b and c).
+\ref{fig:fig4}b and c).
 However, for seed mass and wood density at seedling stage, the direction of effect sizes changed when correlations were measured with absolute versus relative growth rate.
-For seed mass, effect size at seedling stage with relative growth rate was negative and shifted to positive (but non-significant; CI included zero, Fig \ref{fig:fig4}d) with absolute growth rate.
+For seed mass, effect size at seedling stage with relative growth rate was negative and shifted to positive (but non-significant; CI included zero, Fig.
+\ref{fig:fig4}d) with absolute growth rate.
 While these results were consistent with expectations, our ability to draw any firm conclusions was limited due to low sample size for correlation with absolute growth rate (i.e CIs overlapping, Fig.
-\ref{fig:fig4} d).
+\ref{fig:fig4}d).
 For wood density, some differences were observed between studies reporting relative and absolute growth rates: in particular, the correlation at seedling stage shifted from negative with relative growth rate to positive (but non-significant; CI included zero, Fig.

### 2016-03-16 MS.tex
Fixed ref: not using abbrev anymore, Fixed comma in equation 3, and in effect sizes

@@
 \begin{equation}\label{eq:eq2}
-\underbrace{\frac{\ud H}{\ud t}}_{\text{growth rate in height}} = \underbrace{\frac{\ud H}{\ud A_{\rm l}}}_{\text{architecture layout}} \times \underbrace{{\frac{\ud A_{\rm l}}{\ud M_{\rm a} }}}_{\text{leaf deployment per mass}} \times {\frac{\ud M_{\rm a} }{\ud B}} \times {\frac{\ud B}{\ud t}},
+\underbrace{\frac{\ud H}{\ud t}}_{\text{growth rate in height}} = \underbrace{\frac{\ud H}{\ud A_{\rm l}}}_{\text{architecture layout}} \times \underbrace{{\frac{\ud A_{\rm l}}{\ud M_{\rm a} }}}_{\text{leaf deployment per mass}} \times {\frac{\ud M_{\rm a} }{\ud B}} \times {\frac{\ud B}{\ud t}}
 \end{equation}

### 2016-04-15 MS.tex
Editorial changes Add Graphical Abstract Change color chart

@@
 \mstype{Research Article}
-\keywords{maximum height, photosynthetic rate, ontogenetic stage, growth strategy, seed mass, specific leaf area, wood density}
+\keywords{growth strategy, life-history traits, maximum height, ontogenetic stage, photosynthetic rate, plant development, seed mass, specific leaf area, wood density}
 
@@
 \linenumbers
-\section{Summary 309/350}\label{abstract}
+\section{Summary}\label{abstract}
 \begin{enumerate}
@@
 
-\item Synthesis: We show for some traits, how trait-growth correlations change in a predictable way with plant size.
-Our understanding of plant strategies should shift away from categorizing species as having slow or fast growth throughout their life, in favour of attributing growth trajectories.
+\item {\it Synthesis}: We show for some traits, how trait-growth correlations change in a predictable way with plant size.
+Our understanding of plant strategies should shift away from describing species as having a fixed growth strategy throughout their life (on a continuous axis from slow to fast growth), in favour of a size-dependent growth trajectories.
 \end{enumerate}
@@
 
-The phrase ``plant ecological strategy'' refers to how species face common challenges of acquiring sufficient water, nutrients, and light for growth; and then ultimately replacing themselves with offspring.
+The phrase ``plant ecological strategy'' refers to how species face common challenges of acquiring sufficient water, nutrients, and light for growth, and then ultimately replacing themselves with offspring.
 The idea that strategy differences among species might involve fast versus slow growth goes back at least to \citet{Grime:1975gr}, who observed a wide spread of relative growth rates among seedlings growing under favourable conditions.
@@
 It has been widely expected that species with low tissue construction cost will typically have fast growth rates, at least in favourable physical environments \citep[e.g.][]{MullerLandau:2004dc,Poorter:2008iu,Chave:2009iy,Larjavaara:2010bn,Iida:2012jb,Paine:2015df}.
+
 Yet, recently a number of empirical studies indicate the correlation between traits and growth is not consistent.
@@
 
-In this paper, we consider five prominent traits (specific leaf area = SLA, wood or stem tissue density, maximum leaf photosynthetic capacity per unit area = Aarea, maximum or asymptotic height, and seed mass) and we investigate:
+In this paper, we consider five prominent traits (specific leaf area = SLA, wood or stem tissue density, maximum leaf photosynthetic capacity per unit area = $A_{area}$, maximum or asymptotic height, and seed mass) and we investigate:
 \begin{enumerate}
@@
 
-The rate at which \textbf{live biomass} $B$ is produced by a plant is given by
+The rate at which live biomass $B$ is produced by a plant is given by
 \begin{equation}\label{eq:eq0}
@@
 where $\alpha_{\rm y}$ is the ratio of carbon fixed in mass per carbon assimilated, and $p$ is the assimilation rate of CO$_{2}$ per leaf area.
-Here, and in the following equations, $M_i$ denotes the \textbf{live mass on the plant}, $r_i$ the mass-specific \textbf{respiration rate}, and $k_i$ the \textbf{turnover rate} of different plant tissues; the subscripts $i = \rm{l,s,r,a,f}$ referring to leaves, sapwood and bark, roots, total of these vegetative tissues, and to the reproductive tissues (fruits, flowers etc.)  Similarly $A_i$ denotes \textbf{areas}, of leaves ($i = l$) and of cross-sections of total stem and sapwood ($i =\rm{st,ss}$) respectively.
+Here, and in the following equations, $M_i$ denotes the live mass on the plant, $r_i$ the mass-specific respiration rate, and $k_i$ the turnover rate of different plant tissues; the subscripts $i = \rm{l,s,r,a,f}$ referring to leaves, sapwood and bark, roots, total of these vegetative tissues, and to the reproductive tissues (fruits, flowers etc.)  Similarly $A_i$ denotes areas, of leaves ($i = l$) and of cross-sections of total stem and sapwood ($i =\rm{st,ss}$) respectively.
 Note that the live biomass $B = M_{\rm a} + M_{\rm f}$.
-Applying the chain rule of differential calculus, the \textbf{growth rate in plant mass}, ($M_{\rm a} $), can be decomposed as
+Applying the chain rule of differential calculus, the growth rate in plant mass, ($M_{\rm a} $), can be decomposed as
 \begin{equation}\label{eq:eq1}
@@
 
-The \textbf{growth rate in height} can likewise be decomposed as the product of several meaningful terms:
+The growth rate in height can likewise be decomposed as the product of several meaningful terms:
 \begin{equation}\label{eq:eq2}
@@
 
-Similarly \textbf{growth rate in basal area} can be expressed as the sum of growth in sapwood and heartwood, with the former term again decomposed as a product:
+Similarly growth rate in basal area can be expressed as the sum of growth in sapwood and heartwood, with the former term again decomposed as a product:
 \begin{equation}\label{eq:eq3}
@@
 \end{equation}
-Here $\frac{\ud A_{\rm ss}}{\ud A_{\rm l}} $ is the  sapwood area per leaf area.
-The \textbf{growth rate in diameter} is then obtained via the geometric relationship between stem diameter and stem area,
+Here $\frac{\ud A_{\rm ss}}{\ud A_{\rm l}} $ is the  sapwood area per leaf area. The growth rate in diameter is then obtained via the geometric relationship between stem diameter and stem area,
 \begin{equation}\label{eq:eq4}
@@
 To make qualitative predictions with respect to traits such as specific leaf area and wood density we require one additional assumption: that the mass of sapwood tissue ($M_{\rm ss}$) increases disproportionately with respect to the plant's leaf area ($A_{\rm l}$).
-This assumption is included in nearly every model of plant growth that has been developed, on the basis that as stems grow longer the total mass of sapwood associated with each leaf must be increasing \citep[e.g.][]{Falster:2011ii,King-1999,Enquist:2007ek}.
+This assumption is included in nearly every model of plant growth that has been developed, on the basis that as stems grow longer the total mass of sapwood associated with each leaf must be increasing \citep[e.g.][]{King-1999,Enquist:2007ek,Falster:2011ii}.
 It has the effect of changing the relative importance of different components within equations for $\frac{\ud B}{\ud t}$ (net live biomass production) and $\frac{\ud A_{\rm l}}{\ud M_{\rm a} }$ (marginal cost of deploying additional leaf area) as a plant increases in size.
@@
 
-\subsection*{H5: The relationship between Aarea and growth rate is expected to be positive across all plant sizes, particularly under high-light conditions}
+\subsection*{H5: The relationship between $A_{area}$ and growth rate is expected to be positive across all plant sizes, particularly under high-light conditions}
 
-We expect greater photosynthetic capacity to translate into faster growth rates by increasing the rate of biomass production (Table \ref{tab:trade-offs}), at least at high light where Aarea is typically measured.
+We expect greater photosynthetic capacity to translate into faster growth rates by increasing the rate of biomass production (Table \ref{tab:trade-offs}), at least at high light where $A_{area}$ is typically measured.
 This effect occurs by increasing  $\frac{\ud B}{\ud t} $ in eqs.
 (\ref{eq:eq1}-\ref{eq:eq3}).
-The positive effect of increasing Aarea (higher assimilation) may be offset by the costs (higher respiration), however, assuming both increase in proportion, and because assimilation is typically higher than respiration in high light, the net effect will be positive (Table \ref{tab:trade-offs}).
+The positive effect of increasing $A_{area}$ (higher assimilation) may be offset by the costs (higher respiration), however, assuming both increase in proportion, and because assimilation is typically higher than respiration in high light, the net effect will be positive (Table \ref{tab:trade-offs}).
 It is uncertain how much this effect might translate to faster growth in low light.
@@
 Initially we were interested to know whether data existed for a variety of traits; however the number of potential search terms made systemic searching for all these terms in Google Scholar impractical.
-A preliminary investigation of search results for a variety of traits on the Web of Science platform suggested that searching only on SLA and wood density -- two of the most widely measured traits -- would capture $\sim$80\% of search records that would be returned by searching for a wider range of traits (see Appendix \ref{app:literature-snapshot}).
+A preliminary investigation of search results for a variety of traits on the Web of Science platform suggested that searching only on SLA and wood density -- two of the most widely measured traits -- would capture $\sim$80\% of search records that would be returned by searching for a wider range of traits (see Appendix \ref{app:literature-snapshot} in Supporting Information).
 We therefore narrowed our searching to only cover these two main traits.
@@
 \ref{fig:fig1}) capture different components of plant ecological strategies.
-SLA, leaf area, leaf nitrogen and phosphorus concentration, net (mass) assimilation rates (NAR), and Aarea are traits involved in species leaf economic strategy \citep{Wright:2004jb,Wright:2010tp}.
+SLA, leaf area, leaf nitrogen and phosphorus concentration, net (mass) assimilation rates (NAR), and $A_{area}$ are traits involved in species leaf economic strategy \citep{Wright:2004jb,Wright:2010tp}.
 Seed mass and maximum height capture information about reproductive strategy \citep{Falster:2005bw,Moles:2006ft}.
@@
 Because these categories were established according to the expertise of the authors, we were concerned about the risk of assigning plants of similar size to different categories when compiling data across multiple studies and vegetation types.
-This risk turned out to be small: overall, we found that the original thresholds in size/age used by the authors to distinguish different stages were relatively compatible with thresholds we defined ourselves (Fig.
+This risk turned out to be small: overall, we found that the original thresholds in sizeor age used by the authors to distinguish different stages were relatively compatible with thresholds we defined ourselves (Fig.
 \ref{fig:fig2}).
@@
 We had thought it likely that for some traits, correlations would be reported only for one growth stage.
-But this limitation applied only for NARmass and vessel density, where studies appeared confined to seedling and adult stages respectively.
+But this limitation applied only for the net (mass) assimilation rates ($NAR_{mass}$) and vessel density, where studies appeared confined to seedling and adult stages respectively.
 However, for a majority of traits the number of observations across stage was highly unbalanced; for one-third of the 19 traits $>$ 75\% of correlations with growth reported come from the same stage (Fig.
@@
 Accordingly, model fits were marginally improved when stage was incorporated (p-value = 0.049).
-Note that the CIs did not cross zero for seedling and sapling stage, despite the small sample sizes (n= 1 and 4 respectively), meaning a strong correlation and/or a good consistent effect in the coefficient reported for each stage across studies.
+Note that the CIs did not cross zero for seedling and sapling stage, despite the small sample sizes (n= 1 and 4 respectively), meaning a strong correlation or a good consistent effect in the coefficient reported for each stage across studies.
 As expected, for seed mass the correlation with relative growth rate shifted from negative at seedling stage ($\bar{r}= -0.5 \pm 0.07$) to not significantly different from zero at adult and sapling stages (Fig.
@@
 
-For maximum height and Aarea, correlations with relative growth rate were also consistent with expectations, but our ability to test all hypotheses was at times limited due to low or no sample size.
+For maximum height and $A_{area}$, correlations with relative growth rate were also consistent with expectations, but our ability to test all hypotheses was at times limited due to low or no sample size.
 For maximum height, the expectation was for a correlation with growth to be present for large plants but absent for smaller sizes, the mechanism being increased relative allocation to reproduction as maximum height is approached.
@@
 Due to small numbers of replicate studies for sapling stage and no replicates for seedling stage, we could not conclude on the absence of correlation between maximum height and growth at small plant size.
-For Aarea, results were consistent with a positive correlation with relative growth rate at seedling stage.
+For $A_{area}$, results were consistent with a positive correlation with relative growth rate at seedling stage.
 However, no conclusion can be drawn about a change along ontogenetic stages, as only four correlation coefficients were reported for this trait, and three of these were measured at the seedling stage (Fig.
@@
 from 25 to 59 correlation coefficients reported for SLA at seedling stage), while others still had few replicates.
-On the 13 traits-stage combinations studied in total, six had $\le$ five correlation coefficients: wood density-seedling, maximum height-sapling, maximum height-seedling, seed mass-sapling, Aarea-adult and Aarea-sapling.
+On the 13 traits-stage combinations studied in total, six had $\le$ five correlation coefficients: wood density-seedling, maximum height-sapling, maximum height-seedling, seed mass-sapling, $A_{area}$-adult and $A_{area}$-sapling.
 
@@
 \ref{fig:fig3}).
-For seed mass and Aarea, the additional replicates in the entire dataset allowed us to be more confident of the effect size for seedling stage (Fig.
+For seed mass and $A_{area}$, the additional replicates in the entire dataset allowed us to be more confident of the effect size for seedling stage (Fig.
 \ref{fig:fig3}d and e).
-Comparison of Aarea effect between the conservative and relaxed criteria (Fig.
+Comparison of $A_{area}$ effect between the conservative and relaxed criteria (Fig.
 \ref{fig:fig3}d), indicated little effect of stress (here mainly low light) on the correlation with relative growth rate at seedling stage as the correlation was still positive when 8 correlations measured under low light conditions were added.
@@
 
-The only correlation that we hypothesized would change if absolute growth rate was used instead of relative growth rate, was for seed mass.
+The only correlation that we hypothesized would change if absolute growth rate was used instead of relative growth rate was for seed mass.
 Overall, the model fits did not improve when information about growth measurement (relative vs absolute growth rates) was incorporated in the model (see log likelihood ratio tests in Fig.
@@
 Effect sizes measured with a same number of observations for relative and absolute growth rate were generally very consistent (i.e.
-Hmax and wood density at adult stage in Fig.
+$H_{max}$ and wood density at adult stage in Fig.
 \ref{fig:fig4}b and c).
@@
 For seed mass, effect size at seedling stage with relative growth rate was negative and shifted to positive (but non-significant; CI included zero, Fig.
-\ref{fig:fig4}d) with absolute growth rate.
+\ref{fig:fig4}d) for absolute growth rate.
 While these results were consistent with expectations, our ability to draw any firm conclusions was limited due to low sample size for correlation with absolute growth rate (i.e CIs overlapping, Fig.
@@
 For SLA, the meta-analysis strongly confirmed the predicted influence of plant size on the trait-growth correlation.
-For wood density, Aarea, seed mass and maximum height results were consistent with predictions, but data was limited and additional studies would be helpful for these trait-growth-stage relationships.
+For wood density, $A_{area}$, seed mass and maximum height results were consistent with predictions, but data was limited and additional studies would be helpful for these trait-growth-stage relationships.
 
@@
 
-As far as we are aware, our study is the first to compare Aarea and growth correlations between small and large plants.
-In the growth model, a consistent correlation irrespective of size arises from a direct effect of Aarea on plant growth rate.
+As far as we are aware, our study is the first to compare $A_{area}$ and growth correlations between small and large plants.
+In the growth model, a consistent correlation irrespective of size arises from a direct effect of $A_{area}$ on plant growth rate.
 Meta-analyses showed a positive correlation for seedling but not for saplings and adult (n=1).
-In the seedling stage, where most data were available, we noted no signal of an effect of low light on the positive correlation between Aarea and growth rate.
+In the seedling stage, where most data were available, we noted no signal of an effect of low light on the positive correlation between $A_{area}$ and growth rate.
 
@@
 via the recently published \texttt{plant} model \citep{Falster-2016}.
-Additional data are specifically required in small plants (seedling and sapling) for wood density and maximum height, and in large plants (adult and sapling) for Aarea and more broadly for all traits requiring a measure of whole plant biomass (e.g.
+Additional data are specifically required in small plants (seedling and sapling) for wood density and maximum height, and in large plants (adult and sapling) for $A_{area}$ and more broadly for all traits requiring a measure of whole plant biomass (e.g.
 LMR, LAR).
@@
 Elizabeth Wenk and Freya Thomas for their friendly review of our manuscript.
+We thank Timothy Paine and two anonymous reviewers for their careful reading of our manuscript and their many insightful comments and suggestions.
 This work was funded by the Australian Research Council through a fellowship to M.W, a discovery grant to D.S.F and a Macquarie University Research Excellence Scholarship and L'Oreal UNESCO FWIS Fellowship to E.F.G.
 
-\subsection*{Availability of code and data}\label{code}
+\subsection*{Data Accessibility}\label{code}
 
-The code and data for producing all figures and results in this paper is available at \smurl{github.com/AnaisGibert/Growth\_trait\_metaanalysis}.
-Prior to publication, the data set will also be made available in the Dryad Digital Repository.
+The code and data for producing all figures and results in this paper is available at \smurl{github.com/AnaisGibert/Growth\_trait\_metaanalysis}. Data were also deposited in the Dryad repository:
+
+\subsection{Supporting Information}
+Additional supporting information may be found in the online version of this article:
+
+{\bf JEcol-A1.pdf}: {\it Supporting figures, tables, analyses and references}
 
@@
 \caption{Number of recorded correlations between trait and growth rate in our dataset, by stage and trait.
-Traits are: Aarea (or Amass) = rate of CO$_{2}$ assimilation per unit leaf area (or leaf mass) = maximum photosynthetic rate, Hmax = asymptotic or maximum height, Ks = stem hydraulic conductance, LA = leaf area, LMR = leaf mass ratio, NARarea  (or NARmass) = net mass assimilation rate per unit of leaf area (or leaf mass), Nmass (or Narea) = nitrogen content per unit of leaf mass (or leaf area), Pmass = phosphorus content per unit of leaf mass, SA/LA = sapwood area per leaf area, SLA = specific leaf area, Thickness = leaf thickness, Vessel size = stem conduit size, Vessel density = stem conduit density, WD = wood density.
+Traits are: $A_{area}$ (or $A_{mass}$) = rate of CO$_{2}$ assimilation per unit leaf area (or leaf mass) = maximum photosynthetic rate, $H_{max}$ = asymptotic or maximum height, Ks = stem hydraulic conductance, LA = leaf area, LMR = leaf mass ratio, $NAR_{area}$  (or $NAR_{mass}$) = net mass assimilation rate per unit of leaf area (or leaf mass), $N_{mass}$ (or $N_{area}$) = nitrogen content per unit of leaf mass (or leaf area), $P_{mass}$ = phosphorus content per unit of leaf mass, SA/LA = sapwood area per leaf area, SLA = specific leaf area, Thickness = leaf thickness, Vessel size = stem conduit size, Vessel density = stem conduit density, WD = wood density.
 Results shown are from the entire dataset (see methods for details).}
@@
 Arrows indicate the effect an increase in trait value would have on each element of the equations, with dashes indicating no effect.
-Traits are: specific leaf area (= SLA), wood density (= WD), Maximum height (= Hmax), Seed mass, and Maximum photosynthesis per unit leaf area (= Area) For further details, see main text.}
+Traits are: specific leaf area (= SLA), wood density (= WD), Maximum height (= $H_{max}$), Seed mass, and Maximum photosynthesis per unit leaf area (= Area) For further details, see main text.}
 {\footnotesize
@@
   \hline
-  & & & {\bf Symbol} & {\bf SLA} & {\bf WD} & {\bf Hmax} & {\bf Seed mass} & {\bf Aarea} \\ \hline
+  & & & {\bf Symbol} & {\bf SLA} & {\bf WD} & {$\bf H_{max}$} & {\bf Seed mass} & {$\bf A_{area}$} \\ \hline
   \\
@@
 
-\clearpage
-\begin{table}[h!]
-\centering
-\caption{Check-list of criteria for meta-analysis in ecology developed by \citet{Koricheva:2014ku}.}
-{\footnotesize
-\vspace{0.5cm}
-\begin{tabular}{p{0.2cm}p{4cm}p{0.8cm}p{7cm}}
-  \hline
-  & Quality criteria & Check & How and where is it addressed?\\
-  \hline
-  1.& Reporting full details of bibliographic searches & yes  & Complete details of bibliographic searches (i.e.
-electronic reference data bases that were searched, keywords, language, and search dates) are available in the ``Material and Methods''.\\
-  2.& Reporting inclusion or exclusion criteria & yes & Inclusion criteria are specified in the ``Material and Methods''.
-A full list of all articles evaluated is available in the Appendix \ref{app:literature-list}.\\
-  3.& Weighting effect sizes by study precision & yes & Effects sizes were weighted by number of species. See ``Material and Methods'' for details.\\
- 4.& Specifying meta-analytical model & yes & We use a mixed-effect model with a study ID as a random variable, and stage as a fixed effect.
-See ``Material and Methods'' for details.
-Results are shown in Fig.
-\ref{fig:fig3} \& \ref{fig:fig4}.\\
- 5.& Quantifying heterogeneity in effect sizes &  yes & We estimate the extent of heterogeneity for each trait using the $I^{2}$ statistic. See Appendix \ref{app:supp_info_analyses} for details.\\
- 6.& Exploring causes of heterogeneity & yes &  We explore the effect of stage, and the year of publication (see points 4 and 10 in this list).\\
- 7.& Multifactorial analysis of explanatory variable  & yes & We check whether several other explanatory moderators (i.e.
-growth measurement, experiment type or growth form) are consistently the strongest predictors of the data.
-We do not test the multiple variables in a hierarchical fashion, because of the limited size of our dataset.
-See in Figs \ref{fig:figA6}.\\
-  8.& Testing for publication bias &  yes & We used several methods (i.e.
-funnel plots, the ``trim and fill'' method, and Rosenberg's fail-safe number).
-See Appendix \ref{app:supp_info_analyses} for details.\\
-  9.& Sensitivity analysis &  yes &See ``Material and Methods'' for details, results in Figs \ref{fig:fig3} \& \ref{fig:figA5}.\\
-  10.& Exploring temporal changes in effect size &  yes & See Appendix \ref{app:supp_info_analyses} for details.\\
-  11.& Controlling for phylogeny &  no &  It was not possible to control by the phylogeny, since the number of species used to measured each coefficient of correlation ranged from 2 to 300 species.\\
-  12.& Specifying the software used & yes & See sections in ``Material and Methods'' and ``Availability of code and data''.\\
- 13.& Providing reference list of primary studies included in the analysis &  yes & All articles from which data were extracted are cited in the paper.\\
-  14.& Providing the data set used for meta-analysis  & yes & A copy of the data set is available. See ``Availability of code and data'' for details.\\
-   \hline
-\end{tabular}
-}
-\label{tab:meta}
-\end{table}
-
 \end{document}

### 2016-04-15 R/figures.R

@@ -55,9 +55,11 @@ figure_2 <- function(CompleteData_inter) {
     data <- data[order(data$size.max, data$size.min), ]
     data["growthf"] <- -0.02
 
+
+    
     n <- nrow(data)
     y <- rev(seq_len(n))
-    cols <- c("#13519E", "#73005C", "#F57C34", "#E6224C", "grey")[data$stageRGR]
+    cols <- c( "#D5C9B1", "orange", "#805A3B", "#C60000", "black")[data$stageRGR]
     plot(NA, xlim = c(0, 3), ylim = c(0, n+1), yaxt = "n", xaxt = "n", xlab = "",
       ylab = "", yaxs="i")
     mtext(xlab, 1, line = 2, cex = 0.75)
@@ -78,7 +80,7 @@ figure_2 <- function(CompleteData_inter) {
 
   plotCI2(sa, c(0, 1, 5, 10), "Age (yrs)", "a)")
   legend(2.3, 42, c("seedling", "juvenile", "sapling", "adult", "mix"), lwd = 1,  title = "Original stage:",
-    col = c("#13519E", "#73005C", "#F57C34", "#E6224C", "grey"), pch = NA, bty = "n", cex = 0.75,
+    col = c("#D5C9B1", "orange", "#805A3B", "#C60000", "black"), pch = NA, bty = "n", cex = 0.75,
    x.intersp = 0.3, y.intersp = 1, seg.len = 0.5,  title.adj = 0)
   legend(2.3, 32, c("reassigned"), lwd = NA, col = "black",
     pch = c( "*"), title = "Flag:", bty = "n", cex = 0.75,
@@ -99,7 +101,7 @@ figure_panels_traits_model <- function(fits, ...) {
   coeff.plot <- function(x, title = "",
     limit.x.min = -1, limit.x.max = 1.5,
     vjust.value = 2, width = 0.4,
-    colors = c("#9E5F3A", "black"),
+    colors = c("grey", "black"),
     category_variable = "growth",
     labels = c("RGR, conservative dataset", "RGR, entire dataset"),
     breaks = c("RGR", "AGR")) {
@@ -151,7 +153,7 @@ figure_panels_traits_model <- function(fits, ...) {
         theme(axis.text.y = element_blank(), axis.title.y = element_blank(),
               plot.margin  = unit(c(2.5, 0, 1.5, 1), "mm"), axis.title.x = element_blank())
 
[…]

### 2016-04-15 R/plots.R

@@ -5,18 +5,19 @@ mytheme <- function() {
     hjust = 0.5), axis.text = element_text(size = 8), axis.line = element_line(colour = "black"),
   panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.border = element_blank(),
   panel.background = element_blank(), legend.justification = c(1, 0), legend.position = c(1,
-    0))}
+    0), legend.key = element_rect(colour = "white"))}
 
 my_plot_1 <- function(title, ggobj, xlab = expression(paste("")), ylab = "Number of correlations recorded") {
   p <- ggobj + geom_bar(alpha = 0.95) + coord_cartesian(ylim = ylim) + coord_flip() +
     labs(title = title) + xlab(xlab) + ylab(ylab) + scale_x_discrete() + theme(text = element_text(size = 9),
     axis.text.x = element_text(size = 9, angle = 0, vjust = 1)) + mytheme() +
-    theme(axis.title = element_text(size = 10, hjust = 0.5)) + scale_fill_manual(values = c(seedling = "#13519E",
-    sapling = "#F57C34", adult = "#E6224C"), breaks = c("seedling", "sapling",
+    theme(axis.title = element_text(size = 10, hjust = 0.5)) + scale_fill_manual(values = c(seedling = "#D5C9B1",
+    sapling = "#805A3B", adult = "#C60000"), breaks = c("seedling", "sapling",
     "adult"), labels = c("seedling", "sapling", "adult"))
   p
 
 }
+
 
 coeff.plot.ideal <- function(data.ideal, LRT, PVAL, title = "", significativite = "",
   round.value, limit.x.min, limit.x.max, limit.x.text, limit.x.n, limit.y.text.l1,
@@ -53,7 +54,7 @@ my_plot_corr.r <- function(data1, title = "", xlab = "Case studies ranked by coe
     p <- ggobj + labs(title = title) + xlab(xlab) + ylab(ylab) + guides(fill = guide_legend(reverse = TRUE)) +
       mytheme() + scale_y_continuous("Correlation coefficient r", limits = c(-1,
       1)) + scale_colour_manual(limits = c("seedling", "sapling", "adult"),
-      values = c(seedling = "#13519E", sapling = "#F57C34", adult = "#E6224C"),
+      values = c(seedling = "#D5C9B1", sapling = "#805A3B", adult = "#C60000"),
[…]

### 2016-04-15 MS.tex
Tick on the INSIDE of the axis Reference: dryad added

@@
 Ultimately, data were recorded from 103 different articles \citep{Aiba:1997ho, Aiba:2009ft, Antunez:2001gk, Atkin:1998in, augspurger_light_1984, baltzer_physiological_2007, baraloto_differential_2006, baraloto_seed_2005, Bloor:2003fa,  Broncano:1998ck, Brown:1996ks, Bruhn:2000jz, Cai:2007ie, CamaraZapata:2003df, CastroDiez:1998gz, CastroDiez:2003jd, Cernusak:2008ds, Chao:2008hg, Chaturvedi:2011jx, Chaturvedi:2014ie, Chave:2009iy,  coomes_comparison_1998, coomes_greater_2009, Cornelissen:1996hf, Cornelissen:1997fd, Cornelissen:1998ta, Dalling:2004gs, DeBell:1994ix, Easdale:2009gv, fan_hydraulic_2012, Fayolle:2012bx, Fujimoto:2006fg, Galmes:2005fa, Gleason:2016, gleeson_plant_1994, grotkopp_toward_2002, Grubb:1996kr, Herault:2011dd, Hoffmann:2003ga, Huante:1995fd, Huante:1995tl, Huante:1998bk, HUNT:1997ge, Iida:2014ep, Iida:2014hq, king_influence_1994, king_tree_2005,  King:2006he, Kitajima:1994ez, Kohyama:2003dk, Kruger:2006fq, Lamers:2006dl, LopezIglesias:2014dk, Loveys:2002hj, Lusk:1997ga, Lusk:2002fma, Lusk:2013bq, Lusk:2013hz, MartinezVilalta:2010iq, McCormack:2012ch, Moya:2008ep, MullerLandau:2004dc, Nascimento:2005kl, Osone:2008dr, Osunkoya:1994ip, Osunkoya:2010ef, Paz:2005kx, Poorter:1999fp, Poorter:2006vb, Poorter:2008iu, Poorter:2010co, Popma:1988tv, Prior:2004cv, Quero:2008jg, Read:2011du, Reich:1998ir, Reich:1998ja, Rossatto:2009gq, RuizRobleto:2005hc, Sack:2004hm, saldana-acosta_seedling_2009, SalgadoLuarte:2012ci, Saverimuttu:1996ih, Shen:2014fw, Shipley:2002fs, Stratton:2001ck, Thomas:1996do, Tomlinson:2014im, Veneklaas:2002dt, Villagra:2013do, Villar:2006cf, walters_are_1996, Walters:1993eu, Walters:1993hf, Wang:1998cs, Warren:2005bc, Westbrook:2011ja, Wright:1999ds, Wright:2000kw, Wright:2001gb, Wright:2003kb, Wright:2010tp, Zhang:1995bh}.
+The dataset is in open access \citep{Gibert:2016}.
 
@@
 
-The code and data for producing all figures and results in this paper is available at \smurl{github.com/AnaisGibert/Growth\_trait\_metaanalysis}. Data were also deposited in the Dryad repository:
+The code and data for producing all figures and results in this paper is available at \smurl{github.com/AnaisGibert/Growth\_trait\_metaanalysis}.
+Data available from the Dryad Digital Repository: \smurl{http://dx.doi.org/10.5061/dryad.701q8}
 
@@
 \caption{Number of recorded correlations between trait and growth rate in our dataset, by stage and trait.
-Traits are: $A_{area}$ (or $A_{mass}$) = rate of CO$_{2}$ assimilation per unit leaf area (or leaf mass) = maximum photosynthetic rate, $H_{max}$ = asymptotic or maximum height, Ks = stem hydraulic conductance, LA = leaf area, LMR = leaf mass ratio, $NAR_{area}$  (or $NAR_{mass}$) = net mass assimilation rate per unit of leaf area (or leaf mass), $N_{mass}$ (or $N_{area}$) = nitrogen content per unit of leaf mass (or leaf area), $P_{mass}$ = phosphorus content per unit of leaf mass, SA/LA = sapwood area per leaf area, SLA = specific leaf area, Thickness = leaf thickness, Vessel size = stem conduit size, Vessel density = stem conduit density, WD = wood density.
+Traits are: $A_{area}$ (or $A_{mass}$) = rate of CO$_{2}$ assimilation per unit leaf area (or leaf mass) = maximum photosynthetic rate, $H_{max}$ = asymptotic or maximum height, Ks = stem hydraulic conductance, LAR = leaf area ratio, LMR = leaf mass ratio, $NAR_{area}$  (or $NAR_{mass}$) = net mass assimilation rate per unit of leaf area (or leaf mass), $N_{mass}$ (or $N_{area}$) = nitrogen content per unit of leaf mass (or leaf area), $P_{mass}$ = phosphorus content per unit of leaf mass, SA/LA = sapwood area per leaf area, SLA = specific leaf area, Thickness = leaf thickness, Vessel size = stem conduit size, Vessel density = stem conduit density.
 Results shown are from the entire dataset (see methods for details).}

### 2016-04-15 R/figures.R

@@ -70,8 +70,8 @@ figure_2 <- function(CompleteData_inter) {
     j <- data$stageRGR != data$stage
     points(data$size.max[j] + 0.05, y[j], col = "black", pch = "*", cex=1.5)
 
-    axis(1, at = 0:3, labels = cuts, las = 1)
-    axis(2, at = y, labels = data$ref, las = 1, cex.axis = 0.6)
+    axis(1, at = 0:3, labels = cuts, las = 1, tck=0.02)
+    axis(2, at = y, labels = data$ref, las = 1, cex.axis = 0.6, tck=0.02)
     abline(v = 1, col = "black", lty = 1, lwd = 0.5)
     abline(v = 2, col = "black", lty = 1, lwd = 0.5)
 
@@ -220,7 +220,7 @@ figure_A1 <- function(baad) {
   single_plot <- function(px, py, data) {
 
     plot(data[[px$var]], data[[py$var]], log = "xy", xlim = px$lim, ylim = py$lim,
-      xlab = px$lab, ylab = py$lab, col = "grey", pch = 16)
+      xlab = px$lab, ylab = py$lab, col = "grey", pch = 16, tck=+0.02)
     abline(v = px$sap, col = "#805A3B", lty = 5)
     abline(h = py$sap, col = "#805A3B", lty = 5)
     abline(v = px$adult, col = "#C60000", lty = 5)
@@ -269,15 +269,15 @@ figure_A3 <- function(GC) {
 
   p1 <- my_plot_corr.r(GC[["SLA"]], title = "a) SLA") + theme(plot.margin = unit(c(0,
     0, 0, 0), "mm"), legend.position = "none")
-  p2 <- my_plot_corr.r(GC[["WD"]], title = "b)WD") + theme(axis.text.y = element_blank(),
+  p2 <- my_plot_corr.r(GC[["WD"]], title = "b) WD") + theme(axis.text.y = element_blank(),
     axis.title.y = element_blank(), plot.margin = unit(c(0, 0, 0, 0), "mm"),
     legend.position = "none")
-  p3 <- my_plot_corr.r(GC[["Hmax"]], title = "c) Hmax") + theme(plot.margin = unit(c(0,
+  p3 <- my_plot_corr.r(GC[["Hmax"]], title = expression("c) H"[max])) + theme(plot.margin = unit(c(0,
     0, 0, 0), "mm"), legend.position = "none")
[…]

### 2016-04-15 R/plots.R

@@ -5,15 +5,21 @@ mytheme <- function() {
     hjust = 0.5), axis.text = element_text(size = 8), axis.line = element_line(colour = "black"),
   panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.border = element_blank(),
   panel.background = element_blank(), legend.justification = c(1, 0), legend.position = c(1,
-    0), legend.key = element_rect(colour = "white"))}
+    0), legend.key = element_rect(colour = "white"), axis.text.x = element_text(margin=margin(9,5,5,5,"pt")),
+    axis.text.y = element_text(margin=margin(9,5,5,5,"pt")),
+    axis.ticks = element_line (colour = "black", size = 0.5), # sets the thickness and colour of axis ticks
+    axis.ticks.length = unit(-0.08 , "cm"))
+  }
 
 my_plot_1 <- function(title, ggobj, xlab = expression(paste("")), ylab = "Number of correlations recorded") {
   p <- ggobj + geom_bar(alpha = 0.95) + coord_cartesian(ylim = ylim) + coord_flip() +
-    labs(title = title) + xlab(xlab) + ylab(ylab) + scale_x_discrete() + theme(text = element_text(size = 9),
-    axis.text.x = element_text(size = 9, angle = 0, vjust = 1)) + mytheme() +
+    labs(title = title) + xlab(xlab) + ylab(ylab) + theme(text = element_text(size = 9),
+    axis.text.x = element_text(size = 9, angle = 0, vjust = 1)) + 
     theme(axis.title = element_text(size = 10, hjust = 0.5)) + scale_fill_manual(values = c(seedling = "#D5C9B1",
     sapling = "#805A3B", adult = "#C60000"), breaks = c("seedling", "sapling",
-    "adult"), labels = c("seedling", "sapling", "adult"))
+    "adult"), labels = c("seedling", "sapling", "adult")) +
[…]

### 2016-04-15 analysis.R

@@ -83,6 +83,9 @@ dev.off()
 pdf("output/FigA9.pdf")
 figure_A9(GCi)
 dev.off()
+pdf("output/GraphicalAbstract.pdf", height = 3L, width = 4L)
+figure_graphical_abstract(GIi, GIrgr, GIagr)
+dev.off()
 `RCi{1}` <- EffectSizeSum(CompleteData_rgr)
 RCi <- list_by_trait(`RCi{1}`)
 `RIi{1}` <- EffectSizeSum(IdealData_rgr)

### 2016-04-17 ms-suppinfo.Rnw
Editorial change: end of results moved in discussion Table 2 moved to supplementary material

@@
 \clearpage
+ \begin{table}[h!]
+ \centering
+ \caption{Check-list of criteria for meta-analysis in ecology developed by \citet{Koricheva:2014ku}.}
+ {\footnotesize
+ \vspace{0.5cm}
+ \begin{tabular}{p{0.2cm}p{4cm}p{0.8cm}p{7cm}}
+   \hline
+   & Quality criteria & Check & How and where is it addressed?\\
+   \hline
+   1.& Reporting full details of bibliographic searches & yes  & Complete details of bibliographic searches (i.e.
+electronic reference data bases that were searched, keywords, language, and search dates) are available in the ``Material and Methods''.\\
+   2.& Reporting inclusion or exclusion criteria & yes & Inclusion criteria are specified in the ``Material and Methods''.
+A full list of all articles evaluated is available in the Appendix \ref{app:literature-list}.\\
+   3.& Weighting effect sizes by study precision & yes & Effects sizes were weighted by number of species. See ``Material and Methods'' for details.\\
+  4.& Specifying meta-analytical model & yes & We use a mixed-effect model with a study ID as a random variable, and stage as a fixed effect.
+See ``Material and Methods'' for details.
+Results are shown in Fig.
+\ref{fig:fig3} \& \ref{fig:fig4}.\\
+  5.& Quantifying heterogeneity in effect sizes &  yes & We estimate the extent of heterogeneity for each trait using the $I^{2}$ statistic. See Appendix \ref{app:supp_info_analyses} for details.\\
+  6.& Exploring causes of heterogeneity & yes &  We explore the effect of stage, and the year of publication (see points 4 and 10 in this list).\\
+  7.& Multifactorial analysis of explanatory variable  & yes & We check whether several other explanatory moderators (i.e.
+growth measurement, experiment type or growth form) are consistently the strongest predictors of the data.
+We do not test the multiple variables in a hierarchical fashion, because of the limited size of our dataset.
+See in Figs \ref{fig:figA6}.\\
+   8.& Testing for publication bias &  yes & We used several methods (i.e.
+funnel plots, the ``trim and fill'' method, and Rosenberg's fail-safe number).
+See Appendix \ref{app:supp_info_analyses} for details.\\
+   9.& Sensitivity analysis &  yes &See ``Material and Methods'' for details, results in Figs \ref{fig:fig3} \& \ref{fig:figA5}.\\
+   10.& Exploring temporal changes in effect size &  yes & See Appendix \ref{app:supp_info_analyses} for details.\\
+   11.& Controlling for phylogeny &  no &  It was not possible to control by the phylogeny, since the number of species used to measured each coefficient of correlation ranged from 2 to 300 species.\\
+   12.& Specifying the software used & yes & See sections in ``Material and Methods'' and ``Availability of code and data''.\\
+  13.& Providing reference list of primary studies included in the analysis &  yes & All articles from which data were extracted are cited in the paper.\\
+   14.& Providing the data set used for meta-analysis  & yes & A copy of the data set is available. See ``Availability of code and data'' for details.\\
+    \hline
+ \end{tabular}
+ }
+ \label{tab:meta}
+ \end{table}
+
+\clearpage
 
